### 2013-01-22 limits/ms.tex
First commit of glass paper discussing what will be possible with upcoming surveys.

\documentclass[onecolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
%\usepackage{myaasmacros}
\usepackage{amsmath}
\usepackage{graphicx}

\newcommand{\kpc}{\ensuremath{\mathrm{kpc}}}
\newcommand{\Msun}{\ensuremath{\mathrm{M}_\odot}}
\newcommand{\tabref}[1] {Table~\ref{#1}}
\newcommand{\figref}[1] {Figure~\ref{#1}}
\newcommand{\eqnref}[1] {Eq.~(\ref{#1})}
\newcommand{\secref}[1] {Section~\ref{#1}}
\newcommand{\Rmap}{\ensuremath{R_m}}
\newcommand{\Rpix}{\ensuremath{R_p}}
\newcommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}}

% From aastex.cls
\newcommand\plotone[1]{%
 \centering
 \leavevmode
 \includegraphics[width={\columnwidth}]{#1}%
}%
\newcommand\plottwo[2]{{%
 \centering
 \leavevmode
 \columnwidth=.45\columnwidth
 \includegraphics[width={\columnwidth}]{#1}%
 \hfil
 \includegraphics[width={\columnwidth}]{#2}%
}}%

\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
\author{%
Jonathan Coles 
\and 
Justin Read
\and 
Prasenjit Saha 
}

\begin{document}
\maketitle

\tableofcontents

\begin{abstract}
We study the effectiveness of a variety of strong lensing scenarios to inform
the reconstruction of four simulated triaxial halos with stellar and dark
matter components. We conclude that 
1) lenses with multiple sources and high redshift contrast perform very well
2) lenses where the images are already probing the stellar dominated region 
   of a galaxy can be constrained by an estimate of the stellar mass and
   suggest the fraction of dark matter
3) if velocity dispersion measurements are to be used then a sufficiently large aperture 
   is necessary
4) lensing can be used to infer the velocity anisotropy.
We also introduce GLASS, an extensible framework for lens modeling and analysis.

%We attempt to reconstruct the mass profile and distribution of a dark and
%stellar matter triaxial halo using a variety of strong lens configurations,
%stellar mass estimates, and stellar velocity dispersions. The lens
%configurations test quads with small to large image separations (radial
%sampling), extended source information ranging from point images to Einstein
%rings (angular sampling), and multiple sources located at the same and
%differing redshifts (redshift contrast).

%We conclude that redshift contrast can significantly constrain the mass
%profiles.  Stellar mass estimates can also lead to better reconstructions by
%placing lower bounds on the mass distribution in the inner regions of galaxies.
%Velocity dispersions alone are unlikely to usefully constrain the profile
%because the profile is highly sensitive to the dispersion measurement.  
%Combined with other techniques, however, velocity dispersions can help to
%constrain the range of possible reconstructed solutions. We also introduce
%GLASS, an extensible framework for lens modeling and analysis.  
\end{abstract}
\section{Introduction}

2022 - LSST - ~5000 multiply-imaged galaxies, ~150 AGN or quasars.
2020 - SKA - 10,000 lenses possibly with central images

\subsection{Future} %-----------------------------------------------------------
    \begin{itemize}
    \item New satellites will find many new lenses.
    \item LSST, DES, PanSTARRS?, SKA
    \item What is the most important data to have?
    \end{itemize}

\subsection{Present} %----------------------------------------------------------
    \begin{itemize}
    \item SLACS, CASTLES, CosmoGrail, CLASS, CFHTLS, SNAP?
    \end{itemize}

\subsection{Why do we need accurate galaxy models?} %---------------------------
    \begin{itemize}
    \item Galaxy formation
    \item Cusp/Core problem
    \item Universal halos?
    \item Adiabatic contraction
    \item DM fraction
    \end{itemize}

\subsection{Past work on constraining profiles.} %------------------------------
    \begin{itemize}
    \item Much of the early literature used simple SIS and SIE parametric models. Understandable.
    \item Bayesian model fitting
    \item Free-form modeling
    \item Keeton has a good review.
    \end{itemize}

\subsection{What are the problems?} %------------------------------
    \begin{itemize}
    \item Very little data per lens.
    \item Several well-known degeneracies.
    \item Velocity dispersions: aperture too small
    \end{itemize}

\subsection{Goals of the paper} %------------------------------
    \begin{itemize}
    \item Perform a parameter study over lens morphologies and quantify what they can tell us about profiles.
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Theoretical Background}

\subsection{Lensing}

The lensing equation
%
\begin{equation}
\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
\label{lensing equation}
\end{equation}
%
maps an observed image position $\vec\theta$ to a source position $\vec\beta$
via the correction term 
%
\begin{equation}
\vec\alpha(\vec\theta) = \frac{4G}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}
%
which accounts for the gravitational lensing effect of an intervening mass. For
our purposes we make use of the thin mass sheet approximation and assume that
the lensing mass is infinitely thin compared with the distance between the
source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These
distances are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
a dimensionless number that depends on cosmology.  The lens can then be thought
of as a projected surface density $\Sigma$ which diverts the path of a photon
instantaneously through the bending angle $\vec\alpha$.

Since we will later want to model the mass distribution with a computer it will
be convenient to choose units that make the relevant quantities of order unity.
We therefore measure lengths in light years, time in years, positions in
arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to 
define a proxy to the Hubble constant $\nu \equiv N^2 H_0$.

The arrival (or travel) time $t$ of a photon depends not only on the geometric
path it takes, but also on the general relativistic gravitational time dilation
due to the lens at a redshift of $z_L$.  In its complete form, with all units
and cosmology included we can write the arrival time as
%
\begin{equation}
N^2ct(\vec\theta) = (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
\label{full arrival time}
\end{equation}
%
The non-standard factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
delay 
%
\begin{equation}
\tau = \left[(1+z_L)D_{L}\right]^{-1}ctN^2 = \left[ (1+z_L) \frac{c}{H_0}d_L\right]^{-1}ctN^2 = \left[ (1+z_L) d_L\right]^{-1}\nu t
\label{tau}
\end{equation}
%
in terms of our previous definitions. If we
further define a dimensionless density
%
\begin{equation}
\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
              = \frac{d_L}{\nu}\Sigma
\end{equation}
%
and a lensing potential
%
\begin{equation}
\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
\end{equation}
%
we can express \eqnref{full arrival time} very compactly as
%
\begin{equation}
\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
\label{arrival time}
\end{equation}
%
where $\xi \equiv D_{S}/D_{LS}$. We explicitly write $\kappa_\infty$ to remind ourselves
that there is no source distance factor involved. This will be useful later when we consider
multiple sources.

If we think of $\tau$ as a surface then images will be observed where ever
$\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
extremums of the surface. From this we arrive back at \eqnref{lensing
equation}.

The only observables from \eqnref{arrival time} are the image positions, and
perhaps the stellar contribution to $\kappa_\infty$.  If the source object is
variable, however, then the observed light curves of each image will be
identical, but possibly shifted in time due to the different arrival times.
The time difference between identical portions of the light curves is called
the time delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
$\Delta t_{21}$ between two images $\theta_1$ and $\theta_2$, where $\theta_2$
arrives after $\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
\nu$. If $\beta$ and $\kappa_\infty$ were known exactly this would allow one
to precisely infer the Hubble constant. However, the source position is not
observable and the mass distribution is highly degenerate.

\subsection{Degeneracies} %-----------------------------------------------------

The steepness degeneracy arbitrarily rescales the arrival time surface. Image
positions are left alone but the density profile will become shallower or
steeper. This is particularly bad for inferring the Hubble constant, as the
lens profile will tend to become steeper for larger values of $H_0$.

Other degeneracies include ring degeneracies, where one is allowed to build
up a mass distribution as a series of mass rings; the presence of substructure;
and the effects of merging galaxies.

Shape degeneracy---a twisting in the mass.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}

The lens configurations were generated within the new lens modeling framework
GLASS, described in Appendix \ref{GLASS Description}.

With this generated data, or data taken from real observations, GLASS can produce
an ensemble of possible mass distributions drawn from the space of solutions by
using a MCMC algorithm.  The technique is similar to that used in PixeLens
(cite Saha, Coles) but with an improved sampling algorithm.

As we have done in previous work, we imposed several priors on the reconstruction to
make it more physical, namely,
%
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope $\le 0$. This prevents hollow rings.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity.
\item The density is radially symmetric.
\end{enumerate}
%
Since lensing in this case is highly degenerate, many possible realizations are
produced. Each run produced an ensemble of 10000 models.

The quality of a model $M_i$ in an ensemble is judged by computing
\begin{equation}
\chi_i^2 = \frac{\sum_j (M_{ij} - G_j)^2}{\sum_j G_j^2}
\end{equation}
where $M$ and $G$ are the radial profiles of the model and galaxy, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Test Data}

\subsection{Four galaxies and their properties} %--------------------------------------------------------------

We consider four different triaxial galaxies, shown in \figref{test galaxies},
where we have varied the slope index of the stars and the dark matter. We
explore the cases were the stars follow either a $\gamma_\star=1$ or
$\gamma_\star=1.5$ profile and where the dark matter profile is cusped or
cored. The enclosed mass $M(a_\star)= 0.18\e{11}$ at the stellar scale
radius $a_\star=2$ kpc is fixed for all galaxies in order to resemble B1115. We
therefore place the galaxy at a redshift $z_L = 0.31$ in a cosmology with
$H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$.

\begin{figure}
\plotone{cmp_simulations.pdf}
\caption{
\textbf{(Left)} 
Three-dimensional density of the galaxies showing the stellar, dark matter,
and total densities with dotted, dashed, and solid lines, respectively. The
grey lines show the analytic forms from \eqnref{Dehnen profile}. 
\textbf{(Middle)} 
The radially averaged two-dimensional projected density in terms of the
critical density for lensing. At $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
\textbf{(Right)}
The enclosed projected mass.
}
\label{test galaxies}
\end{figure}

%\tabref{source data} summarizes
%each source and image system and \tabref{source time delays} lists the time
%delays.

Each galaxy was generated using the tool DEHNEN with the dark matter and stellar
densities roughly described by Dehnen profiles
%
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\alpha){(r/a)^{-\alpha}(1 + r/a)^{\alpha-4}}
\label{Dehnen profile}
\end{equation}
%
The individual parameters are shown in \tabref{Lens profile params}.

\begin{table}
\begin{tabular}{clllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
AC & 1 & 4 & 1 & $11^2$ \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
\end{tabular}
\caption{Profile parameters for the four test galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

\subsection{Test scenarios} %--------------------------------------------------------------

For each galaxy we constructed ten test scenarios:
\begin{enumerate}
\item Two double imaged systems with a single point source,
\item Two quadruply imaged systems with a single point source,
\item One extended source, 
\item A two-source system with one source varying across five redshifts. 
%will provide a robust estimate of the enclosed mass at
%several radii, suggesting that given a large enough separation, redshift
%constrast will provide the most robust constraint on the mass profile of a
%halo.
\end{enumerate}

%\tabref{Test configurations} summarizes how each of the configurations is composed.  
\figref{Test reconstructions} shows the reconstructed lens.

\begin{figure}
\plotone{AAarrival_surfaces}
\plotone{BBarrival_surfaces}
\plotone{BCarrival_surfaces}
\caption{Average reconstructions of each test case assuming time delays and no central image
using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
\label{Test reconstructions}
\end{figure}

\begin{table}
\begin{tabular}{lccccc}
Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
\hline
AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
 & & & B & -3.15, -4.62 & 37.09\\
 & & & C & -5.72, -0.67 & 33.58\\
 & & & D & 4.26, -0.20 & 259.75\\
 & & & E & 0.22, -0.02 & 104.48\\
AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
 & & & B & 0.87, 4.91 & 228.69\\
 & & & C & 4.80, 1.57 & 31.83\\
 & & & D & -4.58, 1.40 & 56.15\\
 & & & E & -0.09, 0.11 & 180.09\\
AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
 & & & B & -1.26, 5.19 & 66.27\\
 & & & C & -5.31, 0.49 & 74.72\\
 & & & D & 4.72, 0.33 & 99.26\\
 & & & E & 0.04, 0.02 & 174.11\\
AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
 & & & B & -1.93, -5.13 & 14.76\\
 & & & C & -5.53, -0.27 & 75.45\\
 & & & D & 4.56, -0.05 & 160.47\\
 & & & E & 0.09, -0.01 & 147.24\\
AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
 & & & B & -3.47, 4.36 & 60.96\\
 & & & C & -5.66, 0.92 & 17.14\\
 & & & D & 4.13, 0.23 & 270.45\\
 & & & E & 0.40, 0.06 & 83.81\\
AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
 & & & B & 0.98, 4.67 & 227.84\\
 & & & C & 4.48, 1.70 & 27.39\\
 & & & D & -4.34, 1.34 & 54.57\\
 & & & E & -0.12, 0.21 & 144.98\\
AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
 & & & B & 0.92, 3.98 & 226.30\\
 & & & C & 3.70, 1.67 & 19.74\\
 & & & D & -3.55, 1.20 & 53.34\\
 & & & E & -0.12, 0.15 & 96.33\\
AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
 & & & B & 0.93, 3.38 & 223.14\\
 & & & C & 2.98, 1.69 & 9.75\\
 & & & D & -2.82, 1.09 & 48.86\\
 & & & E & -0.15, 0.18 & 52.90\\
AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
 & & & B & 1.02, 2.94 & 219.75\\
 & & & C & 2.51, 1.69 & 4.63\\
 & & & D & -2.36, 1.03 & 44.24\\
 & & & E & -0.16, 0.20 & 32.56
\end{tabular}
\end{table}

\subsection{With/without time delays and central image} %--------------------------------------------------------------

We also considered the effect of having time delays or a central image. The
central image is usually highly demagnified and obscured by the lensing galaxy,
but in clusters the central image is observable. In this case we can imagine
the galaxies to be clusters since the problem is scale-free. A recontruction of
AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
which combination of time delays (T) and central image (M) was used. An
uppercase letter indicates the feature is turned on, and a lowercase letter
that it is turned off.

\begin{figure}
%\plotone{AASingleQuadR1a_Tm.png}
\caption{The reconstruction of AASingleQuadR1a\_Tm.}
\end{figure}

%\begin{table}
%\begin{tabular}{lccccccc}
%Source name & $z$ & $\beta$ & $A$ (min) & $B$ (min) & $C$ (saddle) & $D$ (saddle) & $E$ (max)\\
%\hline
%SingleQuad1 & 2.50 & -0.37,0.08 & -2.40,10.40 & -2.55,-10.26 & -10.93,-0.39 & 10.37,-0.23 & 0.03,-0.01\\
%SingleQuad2 & 0.40 & 0.08,-0.51 & 0.32,-7.23 & 0.70,6.40 & 6.30,1.74 & -6.22,1.59 & -0.03,0.08\\
%SingleQuad3 & 0.60 & 0.08,-0.51 & 0.27,-8.86 & 0.74,8.08 & 8.13,1.93 & -8.05,1.72 & -0.03,0.06\\
%SingleQuad4 & 0.80 & 0.08,-0.51 & 0.36,-9.58 & 0.70,8.82 & 8.92,2.05 & -8.87,1.76 & -0.02,0.05\\
%SingleQuad5 & 1.00 & 0.08,-0.51 & 0.38,-10.00 & 0.68,9.24 & 9.40,1.99 & -9.34,1.79 & -0.02,0.05\\
%ExtendedSource0 & 0.40 & 0.20,0.57 & 0.79,7.25 & 1.51,-6.25 & 6.29,-2.07 & -6.12,-1.55 & -0.06,-0.08\\
%ExtendedSource1 & 0.40 & -0.15,0.17 & -0.64,6.96 & -0.84,-6.66 & -6.67,-0.56 & 6.39,-0.52 & 0.02,-0.03\\
%ExtendedSource2 & 0.40 & 0.06,-0.33 & 0.24,-7.09 & 0.44,6.56 & 6.47,1.18 & -6.43,0.98 & -0.03,0.05
%\end{tabular}
%\caption{Source data.}
%\label{source data}
%\end{table}
%
%\begin{table}
%\begin{tabular}{lrrrr}
%Source name & $\Delta t_{AB}$ & $\Delta t_{BC}$ & $\Delta t_{CD}$ & $\Delta t_{DE}$\\
%\hline
%SingleQuad1 & 38.97 & 171.07 & 207.10 & 1314.05\\
%SingleQuad2 & 335.01 & 97.91 & 50.78 & 623.95\\
%SingleQuad3 & 312.86 & 122.63 & 47.83 & 951.56\\
%SingleQuad4 & 303.39 & 128.81 & 46.63 & 1102.50\\
%SingleQuad5 & 298.27 & 131.32 & 45.70 & 1188.64\\
%ExtendedSource0 & 360.17 & 62.16 & 115.30 & 588.15\\
%ExtendedSource1 & 109.28 & 169.77 & 91.20 & 620.78\\
%ExtendedSource2 & 217.40 & 148.57 & 36.52 & 642.27
%\end{tabular}
%\caption{Time delays for each image system.}
%\label{source time delays}
%\end{table}
%
%\begin{table}
%\begin{tabular}{ll}
%\label{test systems}
%Test name & Source name\\
%\hline
%SingleQuad & SingleQuad1\\
%SingleQuad2 & SingleQuad2\\
%ExtendedSource & ExtendedSource0 + ExtendedSource1 + ExtendedSource2\\
%ZContrastDoubleQuad0 & SingleQuad1 + SingleQuad2\\
%ZContrastDoubleQuad1 & SingleQuad1 + SingleQuad3\\
%ZContrastDoubleQuad2 & SingleQuad1 + SingleQuad4\\
%ZContrastDoubleQuad3 & SingleQuad1 + SingleQuad5
%\end{tabular}
%\caption{Test configurations}
%\label{Test configurations}
%\end{table}

\section{Results} %--------------------------------------------------------------

\begin{figure}
\plotone{AAZContrastR1R5_Tm.pdf}
\caption{A typical reconstructed lens. The first panel on the left shows the
arrival time surface. In this case, there are two sources at different
redshifts with galaxy AA. The next three panels show the radial density,
average enclosed density, and enclosed mass profiles, respectively.  The grey
curve is from the galaxy and the vertical lines show the positions of the
images for the two sources.}
\end{figure}

\begin{figure}
\label{chi2}
\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
\caption{
Goodness of fit plots for the reconstruction of each of the four galaxies given
the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
profile with data points at the median value and the error bars showing the 68\% confidence
interval.
}
\end{figure}

%\begin{figure}
%\plotone{SingleQuad_TmC.png}
%\caption{SingleQuad}
%\label{SingleQuad}
%\end{figure}
%
%\begin{figure}
%\plotone{SingleQuad2_TmC.png}
%\caption{SingleQuad2}
%\label{SingleQuad2}
%\end{figure}
%
%\figref{SingleQuad}
%\figref{SingleQuad2}
%
%\begin{figure}
%\plotone{ExtendedSource_TmC.png}
%\caption{ExtendedSource}.
%\label{ExtendedSource}
%\end{figure}
%
%\figref{ExtendedSource}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad0_TmC.png}
%\caption{ZContrastDoubleQuad0}
%\label{ZContrastDoubleQuad0}
%\end{figure}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad1_TmC.png}
%\caption{ZContrastDoubleQuad1}
%\label{ZContrastDoubleQuad1}
%\end{figure}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad2_TmC.png}
%\caption{ZContrastDoubleQuad2}
%\label{ZContrastDoubleQuad2}
%\end{figure}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad3_TmC.png}
%\caption{ZContrastDoubleQuad3}
%\label{ZContrastDoubleQuad3}
%\end{figure}
%
%\figref{ZContrastDoubleQuad0}
%\figref{ZContrastDoubleQuad1}
%\figref{ZContrastDoubleQuad2}
%\figref{ZContrastDoubleQuad3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Stellar mass}
\begin{itemize}
\item Assume perfect knowledge of the stellar mass distribution.
\item Construct a lens system where the images are probing the stellar region.
\item Add stellar mass as a minimum constraint on the pixels.
\item Requires more pixels in the middle to correctly and efficiently be resolved
\item Stellar mass improves the reconstruction. Need to explain how.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Velocity dispersions}
\begin{itemize}
\item Can they predict radial profiles?
\item Can we constrain lensing models from predicted velocity dispersions?
\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
\item Vary $z$ of the halo, possibly orientation.
\item Should be able to recover $\gamma$ very well.
\item Use G1. Show problems with recovering $\gamma$.
\end{itemize}

\begin{figure}
\plotone{sigma_beta.pdf}
\caption{}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PCA of the models to uncover degeneracies}

%\begin{figure}
%\plotone{SingleQuad_Tmc_eig.png}
%\plotone{SingleQuad2_Tmc_eig.png}
%\plotone{ExtendedSource_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad0_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad1_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad2_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad3_Tmc_eig.png}
%\end{figure}

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Choice of modeling parameters}
%
%
%\begin{itemize}
%\item \figref{raytracing convergence tests}
%\item Why do we choose {\texttt maprad}=20 arcsec when generating test cases?
%We need to enclose most of the mass for the time delays to be stable.  
%\item Why do we choose {\texttt pixrad}=45 when generating the test cases? We
%need sufficient resolution for the image positions to be stable.  
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
\label{GLASS Description}
\begin{itemize} 
\item Framework that incorporates lens modeling, analysis, and plotting.
\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
\item Allows for post processing and criteria matching on a per model basis.
\item Input files are python programs but from within the framework that aspect may be ignored.

\item Lens reconstruction. Based on PixeLens. Express data constraints and
priors as linear equations. Sample the resulting simplex.
\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.

\item Raytracing. Use a fine grid to sample the 2d function mapping position on
the image plane to distance from the source on the source plane. From those
points that are near the source, use a 2d root finder to locate the exact
positions. Merge nearly identical solutions.

\end{itemize}

\subsection{Raytracing}
Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
the change in time delays as we increase $\Rmap$.  The image system is a quad
with the central maximum image. When the projected mass begins to fall off the
time delays stabilize. In the right panel we see the effect of changing the
resolution of the map.  Increasing the resolution allows for more accurate
placement of the images and after about $\Rpix=40$ the image positions change
by less than 0.04 arcsec. The one image that continues to change is near to a
caustic.

%\begin{figure}
%\label{raytracing convergence tests}
%\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
%\caption{(left) Test for predicted time delay convergence as $\Rmap$ changes.
%$\Rpix=45$. After about $\Rmap=20$ most of the asymmetric mass is in the map.
%(right) Test for predicted image position $\theta$ convergence as $\Rpix$
%changes. $\Rmap=20$ arcsec.}
%\end{figure}

\bibliographystyle{mn2e}
\bibliography{ms}

\end{document}

### 2013-02-14 limits/ms.tex
Wrote introduction.

@@
 \usepackage{graphicx}
+
+\newcommand{\Glass}{{\sc Glass}}
 
@@
 \begin{abstract}
-We study the effectiveness of a variety of strong lensing scenarios to inform
-the reconstruction of four simulated triaxial halos with stellar and dark
-matter components. We conclude that 
-1) lenses with multiple sources and high redshift contrast perform very well
-2) lenses where the images are already probing the stellar dominated region 
-   of a galaxy can be constrained by an estimate of the stellar mass and
-   suggest the fraction of dark matter
-3) if velocity dispersion measurements are to be used then a sufficiently large aperture 
-   is necessary
-4) lensing can be used to infer the velocity anisotropy.
-We also introduce GLASS, an extensible framework for lens modeling and analysis.
+We show the effectiveness of reconstructing the mass distribution of four mock galaxies using
+a range of strong gravitational lensing assumptions. In particular, we study
+the affects of the lens morphology (double or quad) with and without a central
+image, angular image distribution, and red shift contrast between two sources.
+The lens modeling is performed using a new free-form framework called \Glass.
+We conclude that 
+1) Time delays are unnecessary with strong red shift contrast,
+2)
+
+%We study the effectiveness of a variety of strong lensing scenarios to inform
+%the reconstruction of four simulated triaxial halos with stellar and dark
+%matter components. We conclude that 
+%1) lenses with multiple sources and high redshift contrast perform very well
+%2) lenses where the images are already probing the stellar dominated region 
+%   of a galaxy can be constrained by an estimate of the stellar mass and
+%   suggest the fraction of dark matter
+%3) if velocity dispersion measurements are to be used then a sufficiently large aperture 
+%   is necessary
+%4) lensing can be used to infer the velocity anisotropy.
+%We also introduce GLASS, an extensible framework for lens modeling and analysis.
 
@@
 \end{abstract}
+
 \section{Introduction}
 
-2022 - LSST - ~5000 multiply-imaged galaxies, ~150 AGN or quasars.
-2020 - SKA - 10,000 lenses possibly with central images
+To date only about 100 strong lenses are known, but within the next ten years
+new surveys will discover thousands of gravitational lenses. For example, SKA
+in 2020 estimates about 10,000 lenses and the LSST in 2022 expects to find
+about 5,000 multiply-imaged galaxies and about 150 AGNs or quasar lenses.
+
+A typical lens, where only the measured observables are the image positions,
+can been used to estimate the total mass of a galaxy including parts of the
+dark matter halo. The enclosed mass inside the Einstein radius is simple to
+calculate and quite robust given the observed image positions. The exact mass
+distribution is more difficult to determine, however, as there are typically
+not enough constraints of the mass profile. The known degeneracies have been
+discussed at length in the literature. At the very least, one would like to
+have a measure of the enclosed mass at at least two distinct radii to be able
+to distinguish between analytic mass models. This would break the steepness
+degeneracy, also known as the mass sheet degeneracy.
+
+Other than using the Einstein radius, the enclosed mass can be estimated
+from stellar velocity dispersions. If the radius from this measurement
+is sufficiently different from the Einstein radius, then this provides the
+necessary data. Another solution, is to find a galaxy that is lensing two
+sources. The images from each source would provide an enclosed mass. The
+extent to which the radii differ is dependent upon the redshifts of the
+two sources: the larger the difference the larger the difference in radii.
+
+If one assumes knowledge of the Hubble constant $H_0$ and time delays have been
+observed for a lens. In principle, this determines that mass, but in practice
+this can only place strong constraints on the mass distribution, as it does not
+solve the problem that the exact distribution is highly degenerate. One can
+choose to postpone this problem and simply fit models to the given data.  The
+earliest examples were singular isothermal sphere models (SIS) but have since
+evolved to multi-component models include separate models for the stars and
+dark matter. Other methods that do not ignore this problem use genetic
+algorithms or linear programming to explore the large space of solutions.
+
+Worse, though, is when only time delays are known and $H_0$ is to be inferred.
+In this case, one is again free to change the mass and $H_0$ while keeping
+all observables fixed. A single lens can say almost nothing about the actual
+value of $H_0$. However, it has been shown that combining the modeling results
+of several strong lenses with time delays can significantly reduce the allowed
+values and provides a measure to within 10 percent.
 

### 2013-02-14 limits/ms.tex
More in the intro.

@@
 
-\tableofcontents
+%\tableofcontents
 
@@
 choose to postpone this problem and simply fit models to the given data.  The
-earliest examples were singular isothermal sphere models (SIS) but have since
-evolved to multi-component models include separate models for the stars and
-dark matter. Other methods that do not ignore this problem use genetic
-algorithms or linear programming to explore the large space of solutions.
+earliest examples were singular isothermal sphere (SIS) or elliptical (SIE)
+models but have since evolved to multi-component models include separate models
+for the stars and dark matter. Other methods that do not ignore this problem
+use genetic algorithms or linear programming to explore the large space of
+solutions.
 
@@
 
-\subsection{Future} %-----------------------------------------------------------
-    \begin{itemize}
-    \item New satellites will find many new lenses.
-    \item LSST, DES, PanSTARRS?, SKA
-    \item What is the most important data to have?
-    \end{itemize}
+Despite these difficulties lensing is a direct probe of the gravitating
+mass in a halo and there are a number of open problems in galaxy formation
+that lensing can help address. For instance, the debate remains as to what
+form the inner slope of the density profile takes. Numerical simulations of
+dark matter suggest a cusp, while observations from lensing and stellar dynamics
+suggest cores. This may, however, be only a matter of scale, as both theory
+and observations agree that clusters have cuspy profiles.
 
-\subsection{Present} %----------------------------------------------------------
-    \begin{itemize}
-    \item SLACS, CASTLES, CosmoGrail, CLASS, CFHTLS, SNAP?
-    \end{itemize}
+Lensing may also be useful in measuring possible adiabatic contraction of the 
+dark matter halo due to the central stars in a galaxy. For this, one needs
+high resolution mass models of the stellar profile combined with accurate models
+of the total mass. Indeed, with such models, one may also improve the statistics
+of the dark matter fraction in a galaxies over many different mass scales.
 
-\subsection{Why do we need accurate galaxy models?} %---------------------------
-    \begin{itemize}
-    \item Galaxy formation
-    \item Cusp/Core problem
-    \item Universal halos?
-    \item Adiabatic contraction
-    \item DM fraction
-    \end{itemize}
+These open problems suggest what kind of lensing data will be required in the
+future.  Future surveys will provide many lenses but time delays will require a
+long follow up. Stellar mass maps, however, take a known, fixed observation
+time and can be performed for many lenses. It will be important not only to
+measure the stellar velocity dispersion at an arbitrary radius, but to ensure
+that the measurement is taken at a radius different to the Einstein radius.
+For the radio surveys like SKA it will be important to detect the central image
+of the lens. This can provide mass information all the way to the center of the
+galaxy.
 
-\subsection{Past work on constraining profiles.} %------------------------------
-    \begin{itemize}
-    \item Much of the early literature used simple SIS and SIE parametric models. Understandable.
-    \item Bayesian model fitting
-    \item Free-form modeling
-    \item Keeton has a good review.
-    \end{itemize}
+In this paper we perform a parameter study using four mock galaxies that differ
+in their dark matter and stellar profiles. We consider double and quad lensing
+morphologies, time delays, the presence of a central image, red shift contrast
+between multiple sources, and image configuration.  We also consider the
+effects of adding stellar mass models as lower bound constraints on the mass
+distribution.  The modeling and analysis is performed using a new free form
+lens modeling framework called \Glass.
 
-\subsection{What are the problems?} %------------------------------
-    \begin{itemize}
-    \item Very little data per lens.
-    \item Several well-known degeneracies.
-    \item Velocity dispersions: aperture too small
-    \end{itemize}
+We first review the basic lensing theory we will need and then describe how
+\Glass is used to generate lensing models. The mock data and how it was
+generated is described in \secref{}. In section{} we discuss the lensing
+configurations in the parameter study and present some example output. Our
+finals results are presented in \secref{}.
 
-\subsection{Goals of the paper} %------------------------------
-    \begin{itemize}
-    \item Perform a parameter study over lens morphologies and quantify what they can tell us about profiles.
-    \end{itemize}
+%\subsection{Future} %-----------------------------------------------------------
+    %\begin{itemize}
+    %\item New satellites will find many new lenses.
+    %\item LSST, DES, PanSTARRS?, SKA
+    %\item What is the most important data to have?
+    %\end{itemize}
+
+%\subsection{Present} %----------------------------------------------------------
+%    \begin{itemize}
+%    \item SLACS, CASTLES, CosmoGrail, CLASS, CFHTLS, SNAP?
+%    \end{itemize}
+
+%\subsection{Why do we need accurate galaxy models?} %---------------------------
+    %\begin{itemize}
+    %\item Galaxy formation
+    %\item Cusp/Core problem
+    %\item Universal halos?
+    %\item Adiabatic contraction
+    %\item DM fraction
+    %\end{itemize}
+
+%\subsection{Past work on constraining profiles.} %------------------------------
+    %\begin{itemize}
+    %\item Much of the early literature used simple SIS and SIE parametric models. Understandable.
+    %\item Bayesian model fitting
+    %\item Free-form modeling
+    %\item Keeton has a good review.
+    %\end{itemize}
+
+%\subsection{What are the problems?} %------------------------------
+    %\begin{itemize}
+    %\item Very little data per lens.
+    %\item Several well-known degeneracies.
+    %\item Velocity dispersions: aperture too small
+    %\end{itemize}
+
+%\subsection{Goals of the paper} %------------------------------
+%    \begin{itemize}
+%    \item Perform a parameter study over lens morphologies and quantify what they can tell us about profiles.
+%    \end{itemize}
 

### 2013-02-15 limits/ms.tex
Wrote numerical methods section.

@@
 %\usepackage{myaasmacros}
+\usepackage{mathrsfs}
 \usepackage{amsmath}
@@
 \newcommand{\Glass}{{\sc Glass}}
+\newcommand{\PixeLens}{{\sc PixeLens}}
+\newcommand{\Rmap}{\ensuremath{R_\mathrm{map}}}
+\newcommand{\Rpix}{\ensuremath{R_\mathrm{pix}}}
+\newcommand{\M}{\ensuremath{\mathscr{M}}}
+\newcommand{\E}{\ensuremath{\mathscr{E}}}
 
@@
 \newcommand{\secref}[1] {Section~\ref{#1}}
-\newcommand{\Rmap}{\ensuremath{R_m}}
-\newcommand{\Rpix}{\ensuremath{R_p}}
+\newcommand{\appref}[1] {Appendix~\ref{#1}}
 \newcommand{\e}[1]{\ensuremath{\times 10^{#1}}}
@@
 maps an observed image position $\vec\theta$ to a source position $\vec\beta$
-via the correction term 
+via the correction factor 
 %
@@
 
-Since we will later want to model the mass distribution with a computer it will
+Since we will later want to model the density distribution with a computer it will
 be convenient to choose units that make the relevant quantities of order unity.
@@
 \psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
+\label{lensing potential}
 \end{equation}
@@
 $\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
-extremums of the surface. From this we arrive back at \eqnref{lensing
-equation}.
+extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation}.
 
@@
 the time delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
-$\Delta t_{21}$ between two images $\theta_1$ and $\theta_2$, where $\theta_2$
-arrives after $\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
+$\Delta t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where $\vec\theta_2$
+arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
 \nu$. If $\beta$ and $\kappa_\infty$ were known exactly this would allow one
 to precisely infer the Hubble constant. However, the source position is not
-observable and the mass distribution is highly degenerate.
+observable and the density distribution is highly degenerate.
 
@@
 Other degeneracies include ring degeneracies, where one is allowed to build
-up a mass distribution as a series of mass rings; the presence of substructure;
+up a density distribution as a series of mass rings; the presence of substructure;
 and the effects of merging galaxies.
 
-Shape degeneracy---a twisting in the mass.
+Shape degeneracy---a twisting in the density.
 
@@
 
-The lens configurations were generated within the new lens modeling framework
-GLASS, described in Appendix \ref{GLASS Description}.
+\subsection{A new lens modeling framework: \Glass}
 
-With this generated data, or data taken from real observations, GLASS can produce
-an ensemble of possible mass distributions drawn from the space of solutions by
-using a MCMC algorithm.  The technique is similar to that used in PixeLens
-(cite Saha, Coles) but with an improved sampling algorithm.
+\Glass\ is an evolution of the concepts employed by the free form modeling tool
+\PixeLens\ but completely rewritten in Python and C. The key improvements are:
+\begin{enumerate}
+  \item A modular framework allows new priors to be added and modified easily;
+  \item The basis functions approximating a model can be changed; 
+  \item Non-linear constraints can be imposed in an automated post-processing step; 
+  \item The central region can be have a higher resolution to capture steep models; 
+  \item Stellar density can be used as an additional constraint.  
+  \item Point or extended mass objects in the field.
+\end{enumerate}
+At its heart lies a new algorithm for sampling high dimensional linear spaces
+that is used to generate lensing models. This algorithm was described and
+tested in \cite{}. \Glass\ is also multi-threaded allowing it to run
+efficiently on many-cored machines.  The software is freely available for
+download. In our tests we will take advantage of each of these new features.
 
-As we have done in previous work, we imposed several priors on the reconstruction to
-make it more physical, namely,
+\subsection{Discrete models}
+
+For this paper we will restrict ourselves to using the pixelated basis set that
+has been employed in previous work and is implemented in \PixeLens. Here we will
+briefly review the main ideas. The algorithm for generating models in \Glass\
+samples a convex polytope in a high dimensional space whose interior points are
+solutions to the lensing equation and satisfy other physically motivated linear
+priors. We must therefore formulate all of our equations as equations linear in the
+unknowns. We describe the density distribution
+$\kappa$ as a set of discrete grid cells or pixels $\kappa_i$.
+In this way, we rewrite the potential (\eqnref{lensing potential}) as
 %
+\begin{equation}
+  \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
+\end{equation}
+%
+where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
+over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
+The pixels only cover a finite circular area with physical radius $\Rmap$ and 
+pixel radius $\Rpix$. To account for any global shearing outside this region
+from, e.g., a neighboring galaxy, we also add two shearing terms
+%
+\begin{equation}
+\gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
+\end{equation}
+%
+We can continue adding terms to account for assumed potentials or potentials
+induced from the presence of other galaxy in the field. If the stellar density
+has been estimated we can use this as a lower bound where the stellar potential
+is a known constant
+%
+\begin{equation}
+  \psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
+\end{equation}
+%
+We can find the discretized lens equation by simply taking the gradient of the
+above equations.
+
+The solution space constrained by the lens equation and the arrival times are
+not enough to form a closed volume. We have not imposed any strong constraints
+on the density even so much as to ensure that it is non-negative everywhere. We
+must therefore provide additonal linear constraints so that we generate physical
+models. The explicit implementation for these priors has been explained in. In
+summary, we require that
 \begin{enumerate}
 \item The density must be non-negative everywhere.
-\item The density profile must have a slope $\le 0$. This prevents hollow rings.
+\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
 \item The local gradient everywhere must point within $45^{\circ}$ of the center.
 \item Density variations must be smooth.
-\item Image parity.
-\item The density is radially symmetric.
+\item Image parity is enforced.
+\item The density is radially symmetric. (Optional)
 \end{enumerate}
-%
-Since lensing in this case is highly degenerate, many possible realizations are
-produced. Each run produced an ensemble of 10000 models.
 
-The quality of a model $M_i$ in an ensemble is judged by computing
-\begin{equation}
-\chi_i^2 = \frac{\sum_j (M_{ij} - G_j)^2}{\sum_j G_j^2}
-\end{equation}
-where $M$ and $G$ are the radial profiles of the model and galaxy, respectively.
+In the simplest form a single model for a lens is a tuple of the form
+$\M = (\vec\kappa, \beta, \gamma_1, \gamma_2)$. A single model represents a 
+single point in the solution space polytope. Using the MCMC sampling strategy
+described in \cite{} we uniformly sample this space. Collectively, the sampled
+models are referred to as an ensemble $\E = \{\M_i\}$, where we typically
+generate 1000 models. We will typically show the ensemble average $|\E|$ in the
+plots to follow.
 
@@
 
-\section{Test Data}
+\section{Mock Galaxy Data}
 
@@
 
+\subsection{Model quality}
+We estimate of the quality of a model $\M_i$ by comparing the recovered
+density profile $\rho_\M(r)$ against the profile of the mock galaxy $\rho_G(r)$.
+In particular, the plots show the RMS quantity
+%
+\begin{equation}
+  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
+  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
+\end{equation}
+
 \begin{figure}
@@
 
+\section{Derivation of pixelated density coefficients}
+\label{Q derivation}
+When the lens plane is pixelized we need a discrete form of the integral
+%
+\[\int \kappa(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta' \]
+%
+In particular we want
+%
+\[\sum_n \kappa_n Q_n(\vec\theta - \vec\theta_n)\]
+%
+where $Q_n$ is the logarithm evaluated over the $n$th pixel at position $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.
+Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates such that
+%
+$|\vec\theta| = r = \sqrt{x^2 + y^2}$. The integral now becomes
+%
+\[Q_n(x,y) = \frac12 \int_{y_-}^{y_+}\int_{x_-}^{x_+} \ln (x'^2+y'^2) dx' dy'\]
+%
+where $x_\pm = x_n \pm (a/2)$ and similarly for $y_\pm$.
+Using the identity
+%
+\[\int \ln(x^2+y^2) dx = x \ln(x^2+y^2) - 2x + 2y\arctan(x/a) \]
+%
+we can express $Q_n$ as the sum of four parts
+%
+\[Q_n(x,y) = \frac12 \left[ \tilde Q_n(x_+,y_+)
+        + \tilde Q_n(x_-,y_-)
+        - \tilde Q_n(x_-,y_+)
+        - \tilde Q_n(x_+,y_-) \right]\]
+%
+where
+%
+\[\tilde Q_n(x,y) = xy(\ln r^2 - 3) + x^2\arctan(y/x) + y^2\arctan(x/y)\]
+
 \bibliographystyle{mn2e}

### 2013-02-16 limits/ms.tex
Wrote mock data section and raytracing.

@@
 \newcommand{\E}{\ensuremath{\mathscr{E}}}
+\newcommand{\eps}{\ensuremath{\varepsilon}}
 
@@
 
-\section{Mock Galaxy Data}
+\subsection{Raytracing}
+\Glass\ can also determine the position of images and time delays from 
+particle-based simulation output given a source position $\vec\beta$. This is
+used to generate the lens configurations used in the parameter study.  The
+particles are first projected onto a very high resolution grid representing the
+lens plane. The centers of each of the grid cells are mapped back onto the
+source plane using \eqnref{lensing equation}. If the location on the source
+plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
+point on the image plane is accepted and further refined using a root finding
+algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
+converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
+Care must be taken that the grid resolution is high enough that the resulting
+image position error is below the equivalent observational error. Time delays
+are the calculated in order from the arrival time at each image (\eqnref{tau}).
 
-\subsection{Four galaxies and their properties} %--------------------------------------------------------------
+\section{Parameter study}
 
-We consider four different triaxial galaxies, shown in \figref{test galaxies},
-where we have varied the slope index of the stars and the dark matter. We
-explore the cases were the stars follow either a $\gamma_\star=1$ or
-$\gamma_\star=1.5$ profile and where the dark matter profile is cusped or
-cored. The enclosed mass $M(a_\star)= 0.18\e{11}$ at the stellar scale
-radius $a_\star=2$ kpc is fixed for all galaxies in order to resemble B1115. We
-therefore place the galaxy at a redshift $z_L = 0.31$ in a cosmology with
-$H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$.
+\subsection{Mock galaxy data}
+
+The four mock galaxies we consider have been designed to test our 
+recovery procedure on galaxies that have steep and shallow dark matter
+and stellar profiles. The enclosed mass in all cases is fixed at $M(a_\star)=
+0.18\e{11}$ at the scale radius $a_\star=2$ kpc. These values were chosen to
+closely resemble B1115. We therefore also place the galaxy at a redshift of
+$z_L = 0.31$. Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
+and $\Omega_\Lambda=0.72$.
+
+The models were
+first generated as three dimensional particle distributions with the
+tool DEHNEN, where each component follows the profile
+\begin{equation}
+\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
+\label{Dehnen profile}
+\end{equation}
+and where $\gamma$ is the profile index and $a$ is the scale radius. The
+four combinations of profile indices are shown in \tabref{Lens profile params}.
+
+\begin{table}
+\begin{tabular}{clllllll}
+Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
+\hline
+AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
+AC & 1 & 4 & 1 & $11^2$ \\
+BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
+BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
+\end{tabular}
+\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
+\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
+all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
+$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
+\label{Lens profile params}
+\end{table}
+
+In \figref{mock galaxies} we show the 3D radial density, 
+the 2D projected density, and the 2D enclosed mass for each
+galaxy. Solid lines represent the total mass, dashed lines the dark 
+matter, and dotted lines the stellar mass. The projected plot has
+been normalized to the critical density 
+$\kappa_\mathrm{crit}\sim 1.8\e{9}$.
 
@@
 }
-\label{test galaxies}
+\label{mock galaxies}
 \end{figure}
-
-%\tabref{source data} summarizes
-%each source and image system and \tabref{source time delays} lists the time
-%delays.
-
-Each galaxy was generated using the tool DEHNEN with the dark matter and stellar
-densities roughly described by Dehnen profiles
-%
-\begin{equation}
-\rho(r) = \frac{M}{4\pi a^3}(3-\alpha){(r/a)^{-\alpha}(1 + r/a)^{\alpha-4}}
-\label{Dehnen profile}
-\end{equation}
-%
-The individual parameters are shown in \tabref{Lens profile params}.
-
-\begin{table}
-\begin{tabular}{clllllll}
-Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
-\hline
-AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
-AC & 1 & 4 & 1 & $11^2$ \\
-BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
-BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
-\end{tabular}
-\caption{Profile parameters for the four test galaxies. The resulting profiles only roughly follow
-\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
-all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
-$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
-\label{Lens profile params}
-\end{table}
 
@@
 \end{figure}
+
+\subsection{Recovery} %--------------------------------------------------------------
 

### 2013-02-19 limits/ms.tex
Mostly restructuring of the order of sections.

@@
 \newcommand{\eps}{\ensuremath{\varepsilon}}
+
+\newcommand{\Eavg}{\ensuremath{\langle \E \rangle}}
 
@@
 
-\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
+%\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
+\title[GLASS]{Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework}
 \author{%
-Jonathan Coles 
+Jonathan P. Coles 
 \and 
-Justin Read
+Justin I. Read
 \and 
@@
 The lens modeling is performed using a new free-form framework called \Glass.
-We conclude that 
-1) Time delays are unnecessary with strong red shift contrast,
-2)
+We conclude that \dots
+%1) Time delays are unnecessary with strong red shift contrast,
+%2)
 
@@
 
-To date only about 100 strong lenses are known, but within the next ten years
-new surveys will discover thousands of gravitational lenses. For example, SKA
-in 2020 estimates about 10,000 lenses and the LSST in 2022 expects to find
-about 5,000 multiply-imaged galaxies and about 150 AGNs or quasar lenses.
+To date only about 400 strong lenses are known, but within the next ten years
+new surveys will discover thousands of gravitational lenses. The SKA estimates
+that after its start in 2020 about 10,000 lenses will be found. The LSST
+expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or
+quasar lenses after 2022.
 
@@
 \begin{equation}
-\vec\alpha(\vec\theta) = \frac{4G}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
+\vec\alpha(\vec\theta) = \frac{4GD_L}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
 \end{equation}
@@
 $\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
-extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation}.
+extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation} or
+\begin{equation}
+  \xi \vec\beta = \xi \vec\theta - \frac 1\pi\int \kappa_\infty\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
+\end{equation}
 
@@
 
-The steepness degeneracy arbitrarily rescales the arrival time surface. Image
-positions are left alone but the density profile will become shallower or
-steeper. This is particularly bad for inferring the Hubble constant, as the
-lens profile will tend to become steeper for larger values of $H_0$.
+\begin{itemize}
+  \item Steepness
+  \item Shape
+  \item $H_0$
+  \item Rings
+  \item Cosmology
+\end{itemize}
 
-Other degeneracies include ring degeneracies, where one is allowed to build
-up a density distribution as a series of mass rings; the presence of substructure;
-and the effects of merging galaxies.
-
-Shape degeneracy---a twisting in the density.
+%
+%The steepness degeneracy arbitrarily rescales the arrival time surface. Image
+%positions are left alone but the density profile will become shallower or
+%steeper. This is particularly bad for inferring the Hubble constant, as the
+%lens profile will tend to become steeper for larger values of $H_0$.
+%
+%Other degeneracies include ring degeneracies, where one is allowed to build
+%up a density distribution as a series of mass rings; the presence of substructure;
+%and the effects of merging galaxies. 
+%
+%Shape degeneracy---a twisting in the density.
 
@@
 \begin{enumerate}
-  \item A modular framework allows new priors to be added and modified easily;
-  \item The basis functions approximating a model can be changed; 
-  \item Non-linear constraints can be imposed in an automated post-processing step; 
-  \item The central region can be have a higher resolution to capture steep models; 
+  \item A modular framework allows new priors to be added and modified easily.
+  \item The basis functions approximating a model can be changed. 
+  \item Non-linear constraints can be imposed in an automated post-processing step. 
+  \item The central region can be have a higher resolution to capture steep models. 
   \item Stellar density can be used as an additional constraint.  
-  \item Point or extended mass objects in the field.
+  \item Point or extended mass objects can be placed in the field.
 \end{enumerate}
-At its heart lies a new algorithm for sampling high dimensional linear spaces
-that is used to generate lensing models. This algorithm was described and
-tested in \cite{}. \Glass\ is also multi-threaded allowing it to run
-efficiently on many-cored machines.  The software is freely available for
-download. In our tests we will take advantage of each of these new features.
+In our tests we will take advantage of each of these new features.  At its
+heart lies a new algorithm for sampling high dimensional linear spaces that is
+used to generate lensing models. This algorithm was described and tested in
+\cite{}. \Glass\ is also multi-threaded allowing it to run efficiently on
+many-cored machines.  The software is freely available for download. One
+interesting aspect is that the input files are themselves Python programs. This
+allows a large amount of sophistication in setting up a lens at runtime and
+also allows \Glass\ to be used as an external library from another user written
+program.
 
@@
   \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
+  \label{discrete potential}
 \end{equation}
@@
 over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
+We can find the discretized lens equation by simply taking the gradient of the
+above equations.
+
 The pixels only cover a finite circular area with physical radius $\Rmap$ and 
@@
 has been estimated we can use this as a lower bound where the stellar potential
-is a known constant
+is a known constant of the form \eqnref{discrete potential}.
 %
-\begin{equation}
-  \psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
-\end{equation}
+%\begin{equation}
+  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
+%\end{equation}
 %
-We can find the discretized lens equation by simply taking the gradient of the
-above equations.
 
-The solution space constrained by the lens equation and the arrival times are
-not enough to form a closed volume. We have not imposed any strong constraints
+Unfortunately, the lens equation and the arrival times are not enough to form a
+closed volume in the solution space. We have not imposed any strong constraints
 on the density even so much as to ensure that it is non-negative everywhere. We
-must therefore provide additonal linear constraints so that we generate physical
-models. The explicit implementation for these priors has been explained in. In
-summary, we require that
+must therefore provide additonal linear constraints so that we generate
+physical models. The explicit implementation for these priors has been
+explained in \cite{}. In summary, we require that
 \begin{enumerate}
@@
 
-In the simplest form a single model for a lens is a tuple of the form
-$\M = (\vec\kappa, \beta, \gamma_1, \gamma_2)$. A single model represents a 
-single point in the solution space polytope. Using the MCMC sampling strategy
-described in \cite{} we uniformly sample this space. Collectively, the sampled
-models are referred to as an ensemble $\E = \{\M_i\}$, where we typically
-generate 1000 models. We will typically show the ensemble average $|\E|$ in the
-plots to follow.
+In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
+\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
+solution space polytope. Using the MCMC sampling strategy described in \cite{}
+we uniformly sample this space. Collectively, the sampled models are referred
+to as an ensemble $\E = \{\M_i\}$, where we usually generate $\sim$1000 models. We
+will typically show the ensemble average $\Eavg$ in the plots to
+follow.
 
@@
 \subsection{Raytracing}
+\label{Raytracing}
 \Glass\ can also determine the position of images and time delays from 
@@
 
-The four mock galaxies we consider have been designed to test our 
-recovery procedure on galaxies that have steep and shallow dark matter
-and stellar profiles. The enclosed mass in all cases is fixed at $M(a_\star)=
-0.18\e{11}$ at the scale radius $a_\star=2$ kpc. These values were chosen to
-closely resemble B1115. We therefore also place the galaxy at a redshift of
-$z_L = 0.31$. Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
-and $\Omega_\Lambda=0.72$.
+The four mock galaxies we consider have been designed to test our recovery
+procedure on galaxies that have steep and shallow dark matter and stellar
+profiles. The enclosed mass in all cases is fixed at $M(a_\star)= 0.18\e{11}$
+at the scale radius $a_\star=2$ kpc. These values were chosen to closely
+resemble B1115. We therefore place the galaxy at a redshift of $z_L = 0.31$.
+Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
+and $\Omega_\Lambda=0.72$. The critical density is $\kappa_\mathrm{crit}\sim
+1.8\e{9}$\Msun/kpc$^2$.
 
@@
 \begin{table}
-\begin{tabular}{clllllll}
-Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
+\begin{tabular}{cllllllll}
+Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & Notes\\
 \hline
-AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
-AC & 1 & 4 & 1 & $11^2$ \\
-BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
-BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
+AA & 1 & 4 & 0.05 & $11^{2.95}$ & \\
+AC & 1 & 4 & 1 & $11^2$ & \\
+BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & \\
+BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 
 \end{tabular}
@@
 \end{table}
-
-In \figref{mock galaxies} we show the 3D radial density, 
-the 2D projected density, and the 2D enclosed mass for each
-galaxy. Solid lines represent the total mass, dashed lines the dark 
-matter, and dotted lines the stellar mass. The projected plot has
-been normalized to the critical density 
-$\kappa_\mathrm{crit}\sim 1.8\e{9}$.
 
@@
 
-\subsection{Test scenarios} %--------------------------------------------------------------
+In \figref{mock galaxies} we show the 3D radial density, 
+the 2D projected density, and the 2D enclosed mass for each
+galaxy. Solid lines represent the total mass, dashed lines the dark 
+matter, and dotted lines the stellar mass. The projected plot has
+been normalized to the critical density.
 
-For each galaxy we constructed ten test scenarios:
+\subsection{Lens configurations} %--------------------------------------------------------------
+
+For each of the four galaxies, we used the raytracing feature of \Glass\
+described in \secref{Raytracing} to construct 12 lensing scenarios:
+
 \begin{enumerate}
-\item Two double imaged systems with a single point source,
-\item Two quadruply imaged systems with a single point source,
-\item One extended source, 
-\item A two-source system with one source varying across five redshifts. 
-%will provide a robust estimate of the enclosed mass at
-%several radii, suggesting that given a large enough separation, redshift
-%constrast will provide the most robust constraint on the mass profile of a
-%halo.
+\item Two double imaged systems with a single point source.
+\item Two quadruply imaged systems with a small and large annulus.
+\item Two quadruply imaged systems with a single point source.
+\item One extended source. 
+\item A two-source quad system with one source varying across five redshifts. 
 \end{enumerate}
 
+Each of these configurations were modeled with and without time delays and with
+and without a central image. We assumed for all tests that the lensing mass was
+symmetric.
+
+\subsection{Stellar mass}
+\begin{itemize}
+\item Assume perfect knowledge of the stellar mass distribution.
+\item Construct a lens system where the images are probing the stellar region.
+\item Add stellar mass as a minimum constraint on the pixels.
+\item Requires more pixels in the middle to correctly and efficiently be resolved
+\item Stellar mass improves the reconstruction. Need to explain how.
+\end{itemize}
+
+\subsection{Velocity dispersions}
+
+\begin{itemize}
+\item Can they predict radial profiles?
+\item Can we constrain lensing models from predicted velocity dispersions?
+\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
+\item Vary $z$ of the halo, possibly orientation.
+\item Should be able to recover $\gamma$ very well.
+\item Use G1. Show problems with recovering $\gamma$.
+\end{itemize}
+
 %\tabref{Test configurations} summarizes how each of the configurations is composed.  
-\figref{Test reconstructions} shows the reconstructed lens.
+%\figref{Test reconstructions} shows the reconstructed lens.
 
-\begin{figure}
-\plotone{AAarrival_surfaces}
-\plotone{BBarrival_surfaces}
-\plotone{BCarrival_surfaces}
-\caption{Average reconstructions of each test case assuming time delays and no central image
-using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
-\label{Test reconstructions}
-\end{figure}
+%\begin{figure}
+%\plotone{AAarrival_surfaces}
+%\plotone{BBarrival_surfaces}
+%\plotone{BCarrival_surfaces}
+%\caption{Average reconstructions of each test case assuming time delays and no central image
+%using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
+%\label{Test reconstructions}
+%\end{figure}
 
-\subsection{Recovery} %--------------------------------------------------------------
+%\subsection{Recovery} %--------------------------------------------------------------
 
-\begin{table}
-\begin{tabular}{lccccc}
-Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
-\hline
-AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
- & & & B & -3.15, -4.62 & 37.09\\
- & & & C & -5.72, -0.67 & 33.58\\
- & & & D & 4.26, -0.20 & 259.75\\
- & & & E & 0.22, -0.02 & 104.48\\
-AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
- & & & B & 0.87, 4.91 & 228.69\\
- & & & C & 4.80, 1.57 & 31.83\\
- & & & D & -4.58, 1.40 & 56.15\\
- & & & E & -0.09, 0.11 & 180.09\\
-AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
- & & & B & -1.26, 5.19 & 66.27\\
- & & & C & -5.31, 0.49 & 74.72\\
- & & & D & 4.72, 0.33 & 99.26\\
- & & & E & 0.04, 0.02 & 174.11\\
-AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
- & & & B & -1.93, -5.13 & 14.76\\
- & & & C & -5.53, -0.27 & 75.45\\
- & & & D & 4.56, -0.05 & 160.47\\
- & & & E & 0.09, -0.01 & 147.24\\
-AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
- & & & B & -3.47, 4.36 & 60.96\\
- & & & C & -5.66, 0.92 & 17.14\\
- & & & D & 4.13, 0.23 & 270.45\\
- & & & E & 0.40, 0.06 & 83.81\\
-AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
- & & & B & 0.98, 4.67 & 227.84\\
- & & & C & 4.48, 1.70 & 27.39\\
- & & & D & -4.34, 1.34 & 54.57\\
- & & & E & -0.12, 0.21 & 144.98\\
-AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
- & & & B & 0.92, 3.98 & 226.30\\
- & & & C & 3.70, 1.67 & 19.74\\
- & & & D & -3.55, 1.20 & 53.34\\
- & & & E & -0.12, 0.15 & 96.33\\
-AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
- & & & B & 0.93, 3.38 & 223.14\\
- & & & C & 2.98, 1.69 & 9.75\\
- & & & D & -2.82, 1.09 & 48.86\\
- & & & E & -0.15, 0.18 & 52.90\\
-AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
- & & & B & 1.02, 2.94 & 219.75\\
- & & & C & 2.51, 1.69 & 4.63\\
- & & & D & -2.36, 1.03 & 44.24\\
- & & & E & -0.16, 0.20 & 32.56
-\end{tabular}
-\end{table}
+%\begin{table}
+%\begin{tabular}{lccccc}
+%Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
+%\hline
+%AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
+% & & & B & -3.15, -4.62 & 37.09\\
+% & & & C & -5.72, -0.67 & 33.58\\
+% & & & D & 4.26, -0.20 & 259.75\\
+% & & & E & 0.22, -0.02 & 104.48\\
+%AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
+% & & & B & 0.87, 4.91 & 228.69\\
+% & & & C & 4.80, 1.57 & 31.83\\
+% & & & D & -4.58, 1.40 & 56.15\\
+% & & & E & -0.09, 0.11 & 180.09\\
+%AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
+% & & & B & -1.26, 5.19 & 66.27\\
+% & & & C & -5.31, 0.49 & 74.72\\
+% & & & D & 4.72, 0.33 & 99.26\\
+% & & & E & 0.04, 0.02 & 174.11\\
+%AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
+% & & & B & -1.93, -5.13 & 14.76\\
+% & & & C & -5.53, -0.27 & 75.45\\
+% & & & D & 4.56, -0.05 & 160.47\\
+% & & & E & 0.09, -0.01 & 147.24\\
+%AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
+% & & & B & -3.47, 4.36 & 60.96\\
+% & & & C & -5.66, 0.92 & 17.14\\
+% & & & D & 4.13, 0.23 & 270.45\\
+% & & & E & 0.40, 0.06 & 83.81\\
+%AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
+% & & & B & 0.98, 4.67 & 227.84\\
+% & & & C & 4.48, 1.70 & 27.39\\
+% & & & D & -4.34, 1.34 & 54.57\\
+% & & & E & -0.12, 0.21 & 144.98\\
+%AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
+% & & & B & 0.92, 3.98 & 226.30\\
+% & & & C & 3.70, 1.67 & 19.74\\
+% & & & D & -3.55, 1.20 & 53.34\\
+% & & & E & -0.12, 0.15 & 96.33\\
+%AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
+% & & & B & 0.93, 3.38 & 223.14\\
+% & & & C & 2.98, 1.69 & 9.75\\
+% & & & D & -2.82, 1.09 & 48.86\\
+% & & & E & -0.15, 0.18 & 52.90\\
+%AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
+% & & & B & 1.02, 2.94 & 219.75\\
+% & & & C & 2.51, 1.69 & 4.63\\
+% & & & D & -2.36, 1.03 & 44.24\\
+% & & & E & -0.16, 0.20 & 32.56
+%\end{tabular}
+%\end{table}
 
-\subsection{With/without time delays and central image} %--------------------------------------------------------------
+%\subsection{With/without time delays and central image} %--------------------------------------------------------------
 
-We also considered the effect of having time delays or a central image. The
-central image is usually highly demagnified and obscured by the lensing galaxy,
-but in clusters the central image is observable. In this case we can imagine
-the galaxies to be clusters since the problem is scale-free. A recontruction of
-AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
-which combination of time delays (T) and central image (M) was used. An
-uppercase letter indicates the feature is turned on, and a lowercase letter
-that it is turned off.
+%We also considered the effect of having time delays or a central image. The
+%central image is usually highly demagnified and obscured by the lensing galaxy,
+%but in clusters the central image is observable. In this case we can imagine
+%the galaxies to be clusters since the problem is scale-free. A recontruction of
+%AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
+%which combination of time delays (T) and central image (M) was used. An
+%uppercase letter indicates the feature is turned on, and a lowercase letter
+%that it is turned off.
 
-\begin{figure}
+%\begin{figure}
 %\plotone{AASingleQuadR1a_Tm.png}
-\caption{The reconstruction of AASingleQuadR1a\_Tm.}
-\end{figure}
+%\caption{The reconstruction of AASingleQuadR1a\_Tm.}
+%\end{figure}
 
@@
 
-\subsection{Model quality}
-We estimate of the quality of a model $\M_i$ by comparing the recovered
+\figref{AAZContrastR1R5_Tm reconstruction} shows a typical reconstruction of a
+lens. The far left plot shows the arrival time surface with image marked as
+circles and the inferred source position as a diamond. The center plot shows
+the radial density profile. The error bars cover the full range of models
+generated by \Glass. The true density profile from the mock data is also
+plotted for comparison. The vertical lines mark the radial position of the
+images. The final plot on the right is of the enclosed mass. As expected the
+error bars are smallest in the region of the images where the most information
+about the lens is present. The dip in the profile at the end of the profile
+is due to the cut off in mass in the lensing map. This is of little importance,
+though, as there is no lensing information there.
+
+\begin{figure}
+\plotone{AAZContrastR1R5_Tm.pdf}
+\caption{A typical reconstructed lens. 
+\textbf{(Left)}
+The arrival time surface. In this case, there are two sources at different
+redshifts with galaxy AA. The next three panels show the radial density,
+average enclosed density, and enclosed mass profiles, respectively.  The grey
+curve is from the galaxy and the vertical lines show the positions of the
+images for the two sources.}
+\label{AAZContrastR1R5_Tm reconstruction}
+\end{figure}
+
+\begin{figure}
+\plotone{AAresults.pdf}
+\end{figure}
+
+%\subsection{Model quality}
+We estimate the quality of a model $\M_i$ by comparing the recovered
 density profile $\rho_\M(r)$ against the profile of the mock galaxy $\rho_G(r)$.
@@
 
-\begin{figure}
-\plotone{AAZContrastR1R5_Tm.pdf}
-\caption{A typical reconstructed lens. The first panel on the left shows the
-arrival time surface. In this case, there are two sources at different
-redshifts with galaxy AA. The next three panels show the radial density,
-average enclosed density, and enclosed mass profiles, respectively.  The grey
-curve is from the galaxy and the vertical lines show the positions of the
-images for the two sources.}
-\end{figure}
+\subsection{Using principle component analysis to find new degeneracies}
 
-\begin{figure}
-\label{chi2}
-\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
-\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
-\caption{
-Goodness of fit plots for the reconstruction of each of the four galaxies given
-the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
-profile with data points at the median value and the error bars showing the 68\% confidence
-interval.
-}
-\end{figure}
+%\begin{figure}
+%\label{chi2}
+%\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
+%\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
+%\caption{
+%Goodness of fit plots for the reconstruction of each of the four galaxies given
+%the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
+%profile with data points at the median value and the error bars showing the 68\% confidence
+%interval.
+%}
+%\end{figure}
 
@@
 
-\section{Stellar mass}
-\begin{itemize}
-\item Assume perfect knowledge of the stellar mass distribution.
-\item Construct a lens system where the images are probing the stellar region.
-\item Add stellar mass as a minimum constraint on the pixels.
-\item Requires more pixels in the middle to correctly and efficiently be resolved
-\item Stellar mass improves the reconstruction. Need to explain how.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Velocity dispersions}
-\begin{itemize}
-\item Can they predict radial profiles?
-\item Can we constrain lensing models from predicted velocity dispersions?
-\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
-\item Vary $z$ of the halo, possibly orientation.
-\item Should be able to recover $\gamma$ very well.
-\item Use G1. Show problems with recovering $\gamma$.
-\end{itemize}
+\subsection{Aperture}
 
@@
 
+\section{Discussion} %--------------------------------------------------------------
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{PCA of the models to uncover degeneracies}
 
@@
 
-\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
-\label{GLASS Description}
-\begin{itemize} 
-\item Framework that incorporates lens modeling, analysis, and plotting.
-\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
-\item Allows for post processing and criteria matching on a per model basis.
-\item Input files are python programs but from within the framework that aspect may be ignored.
+%\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
+%\label{GLASS Description}
+%\begin{itemize} 
+%\item Framework that incorporates lens modeling, analysis, and plotting.
+%\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
+%\item Allows for post processing and criteria matching on a per model basis.
+%\item Input files are python programs but from within the framework that aspect may be ignored.
+%
+%\item Lens reconstruction. Based on PixeLens. Express data constraints and
+%priors as linear equations. Sample the resulting simplex.
+%\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
+%\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
+%\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.
+%
+%\item Raytracing. Use a fine grid to sample the 2d function mapping position on
+%the image plane to distance from the source on the source plane. From those
+%points that are near the source, use a 2d root finder to locate the exact
+%positions. Merge nearly identical solutions.
 
-\item Lens reconstruction. Based on PixeLens. Express data constraints and
-priors as linear equations. Sample the resulting simplex.
-\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
-\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
-\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.
+%\end{itemize}
 
-\item Raytracing. Use a fine grid to sample the 2d function mapping position on
-the image plane to distance from the source on the source plane. From those
-points that are near the source, use a 2d root finder to locate the exact
-positions. Merge nearly identical solutions.
-
-\end{itemize}
-
-\subsection{Raytracing}
+\section{Raytracing convergence test}
 Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
@@
 
-%\begin{figure}
-%\label{raytracing convergence tests}
-%\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
-%\caption{(left) Test for predicted time delay convergence as $\Rmap$ changes.
-%$\Rpix=45$. After about $\Rmap=20$ most of the asymmetric mass is in the map.
-%(right) Test for predicted image position $\theta$ convergence as $\Rpix$
-%changes. $\Rmap=20$ arcsec.}
-%\end{figure}
+\begin{figure}
+\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
+\caption{(left) Test for predicted time delay convergence as $\Rmap$ changes.
+$\Rpix=45$. After about $\Rmap=20$ most of the asymmetric mass is in the map.
+(right) Test for predicted image position $\theta$ convergence as $\Rpix$
+changes. $\Rmap=20$ arcsec.}
+\label{raytracing convergence tests}
+\end{figure}
 
@@
 %
-\[\sum_n \kappa_n Q_n(\vec\theta - \vec\theta_n)\]
+\[\sum_n \kappa_n Q_n(\vec\theta)\]
 %
@@
 %
-where $x_\pm = x_n \pm (a/2)$ and similarly for $y_\pm$.
+where $x_\pm = x + x_n \pm (a/2)$ and similarly for $y_\pm$.
 Using the identity

### 2013-02-19 shapes/thesis.tex

\documentclass[10pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{multirow}
\usepackage{lscape}

\usepackage{natbib}
\usepackage{natbibmnfix}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{subfigure}

\usepackage[small]{titlesec} % make section heading small

\newcommand{\apj}{ApJ}
\newcommand{\apjs}{ApJS}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\araa}{ARA\&A}
\newcommand{\apjl}{ApJL}
\newcommand{\aj}{AJ}
\newcommand{\nat}{Nature}

%%%%%%%%%%% Still to change: Dominiks PhD!
\title{ALIGNMENT OF LIGHT AND MASS IN LENSING GALAXIES}
\author{Claudio Bruderer}

\begin{document}
\maketitle

\begin{abstract}
\noindent Something
\end{abstract}

%\tableofcontents

\section{Introduction}

\subsection{Context/Background/Motivation}
\begin{itemize}
\item Why interesting (lensing can constrain mass distribution (enclosed mass constraint independent from model with only few percent uncertainty e.g. Kochanek 1991?, Wambsganss \& Paczyński 1994?), insights into structure formation)
\item What is to be expected from theory (dm, alternative gravity)
\end{itemize}

\subsection{Anything done before?}
\textbf{\cite{1997ApJ...482..604K}}: Look at 17 lenses at redshifts ranging between 0.1 and $\sim1$. Sample consists of mainly passively evolving elliptical galaxies and a few spirals. Claim that generally projected light and dark matter distributions are strongly correlated and are not far out of alignment ($\lesssim10^{\circ}$), except in cases where there are strong external tidal perturbations (although misalignments are not necessary in these cases). 'Dark matter halos can be significantly flatter than the light (e.g., Sackett et al. 1994; Buote \& Canizares 1994, 1996; also see the review by Sackett 1996)'. To reconstruct the mass they fit singular isothermal ellipsoid (SIE) lens models, which immediately give them the shape. Another model they use is a singular isothermal sphere (SIS) and some external tidal perturbation (shear). As already stated in \cite{1998ApJ...509..561K}, these models sometimes give a bad fit. To obtain a good fit, an another independent source of external shear is needed (external tidal perturbation). They also state that it is known that the lenses Q0957 + 561 (Young et al. 1980, Grogin \& Narayan 1996), PG 1115 + 080 (Keeton \& Kochanek 1997, Kundic et al. 1997a, Schechter et al. 1997, Tonry 1998), B1422 + 231 (Hogg \& Blandford 1994, Kormann et al. 1994, Kundic et al 1997b, Tonry 1998) are subject to significant tidal perturbations by a nearby cluster, group or galaxy (also line-of-sight structure) (--> All lying in a environment? Ask Prasenjit).

\textbf{\cite{1998ApJ...509..561K}}: They used SIEs for the reconstruction of 6 lenses. They find that for many lenses a model with two independent shears (e.g. SIE + 1 external shear) gives a much better fit. Additionally, the fits are much better than just trying to fit different radial mass distributions with the same number of degrees of freedom. Numerical simulations generally produce more elliptical and more triaxial dark matter halos than luminous galaxies (e.g. Warren et al. 1992; Dubinski 1992, 1994). They can however only compare 3 galaxies with eachother.

\textbf{\cite{1998PhDT.........6K}}: Not sure whether everything was already covered in previous papers or not. He modelled observed lenses to determine their shapes and finds that the dark matter halos are generally aligned with the luminous part. Exceptions are however lenses with known tidal disruptions, where there can be a misalignment. He concludes that the halos were modified by interactions with the galaxies. He however does not state in the abstract how he modelled the lenses.

\textbf{\cite{2000ApJ...538L.113N}}:

\textbf{\cite{2002sgdh.conf...62K}}:

\textbf{\cite{2005MNRAS.360.1333W}}:

\textbf{\cite{2008MNRAS.383..857F}}:

\textbf{\cite{2011AstRv...6f..43B}}:

\textbf{\cite{2012ApJ...761..170G}}:

\textbf{\cite{2000ApJ...536..584L}}:

\subsection{New here}
\begin{itemize}
\item Statistics
\item Free-form (explain advantages of free-form over parametric modelling (\cite{2004AJ....127.2604S}, \cite{2012MNRAS.425.3077L}, \cite{2008ApJ...681..814C}), cite GLASS (\cite{2012MNRAS.425.3077L})
\item group versus stellar misalignment with dm halo
\end{itemize}

\section{Data}
\begin{itemize}
\item SPS (Ignacio Ferreras, Dominik, etc. (\cite{2011ApJ...740...97L}))
\item Bundle information in tables (especially what input data was used for the lenses)
\end{itemize}

\begin{landscape}
 \begin{center}
  \begin{tabular}{l c c c c c c c c c}
	\hline
	\multirow{2}{*}{Lens} & \multirow{2}{*}{$z_{L}$} & \multicolumn{2}{c}{Group/Cluster centroid} & & \multicolumn{2}{c}{Other galaxy} & \multirow{2}{*}{Galaxy type} & \multirow{2}{*}{Environment} & \multirow{2}{*}{References}\\ \cline{3-4} \cline{6-7}
	 & & $\Delta\alpha$ ('') & $\Delta\delta$ ('') & & $\Delta\alpha$ ('') & $\Delta\delta$ ('') & & & \\ \hline \hline
	Q0047 & 0.48 & $3.6\pm15.6$ & $43.2\pm28.8$ &   & & & Early-type & G(9) & \cite{2011ApJ...726...84W}\\
	Q0142 & 0.49 & & &   & & & Early-type & - & \cite{2000ApJ...536..584L}\\
	MG0414 & 0.96 & & &   & $-0.385$ & $1.457$ & Early-type & 1 & \cite{1993AJ....105....1S}\\
	B0712 & 0.41 & & &   & $47$ & $-91$ & Early-type & 1 & \cite{2002AJ....123..627F}\\
	HS0818 & 0.39 & & &   & & & see below & 1 & aaaaaaaaa\\%\cite{2000A&A...357L..29H}\\
	RXJ0911 & 0.77 & $-12.0$ & $-39.8$ &    & & & Early-type & C & \cite{2001ApJ...555....1M}\\
	BRI0952 & 0.63 & &   & & & & Early-type & - & aaaaaaaaa\\%\cite{2007A&A...465...51E}\\
	Q0957 & 0.36 & $4.8$ & $2.1$ &   & & & Early-type & C & \cite{1998ApJ...504..661C}\\
	LBQS1009 & 0.87 & & &   & & & Early-type & - & aaaaaaaaa\\%\cite{2004A&A...428..741F}\\
	B1030 & 0.60 & & &   & $-9.78$ & $8.54$ & Early-type & 1 & \cite{2000ApJ...536..584L}\\
	HE1104 & 0.73 & & &   & & & Early-type & - & aaaaaaaaa\\%\cite{2004A&A...428..741F}\\
	PG1115 & 0.31 & $-10.8\pm21$ & $-3.6\pm15.6$ &   & & & Early-type & G(13) & \cite{2011ApJ...726...84W}\\
	B1152 & 0.439 & & &   & & & Unknown & - & see below\\
	B1422 & 0.34 & $61.2\pm25.2$ & $-10.8\pm23.4$ &   & & & Early-type & G(17) & \cite{2011ApJ...726...84W}\\
	SBS1520 & 0.72 & & &   & & & Early-type & G(4) & see below\\
	B1600 & 0.41 & $-8.44286$ & $-1.48571$ &   & & & Late-type & G(7) & \cite{2007AJ....134..668A}\\
	B1608 & 0.63 & $-0.697246$ & $7.96956$ &   & & & Both & G(8) & \cite{2006ApJ...642...30F}\\
	MG2016 & 1.01 & & &   & & & Early-type & C(69) & \cite{2003MNRAS.344..337T}\\
	B2045 & 0.87 & & &   & & & Early-type & - & \cite{1999AJ....117..658F}\\
	HE2149 & 0.60 & $-36.6$ & $14.2$ &   & & & Early-type & G & \cite{2006ApJ...646...85W}\\
	Q2237 & 0.04 & & &   & & & Late-type & - & see below\\ 
	\hline
  \end{tabular}
 \end{center}
\end{landscape}

The pixelated stellar mass maps we use here was reconstructed by \cite{leier11phd}. For each pixel the surface brightness was compared with stellar mass-to-light ratios, which were determined by populations synthesis model. Details for this method can be found in \cite{leier11phd}, \cite{2005ApJ...623L...5F}, \cite{2008MNRAS.383..857F}.

Here some comments about the environments of the lenses in the sample.

\textbf{Q0047-2808}: \cite{2011ApJ...726...84W} find a group of 9 members, spectroscopically confirmed. According to \cite{1996MNRAS.278..139W} it is a luminous early-type galaxy.

\textbf{Q0142-100}: The required external shear is comparable to the cosmic LSS-contribution, and it also seems to be a passively evolving early-type galaxy according to \cite{2000ApJ...536..584L} and confirmed by \cite{2007A&A...465...51E}.

\textbf{MG0414+0534}: According to \cite{1999AJ....117.2034T} the lens seems to be a passively evolving early-type galaxy. \cite{1993AJ....105....1S} find a luminous satellite galaxy north-west of the lens. The position data of this object was taken from CASTLES.

\textbf{B0712+472}: According to \cite{2002AJ....123..627F} potentially only one other galaxy 102'' to the south-east at a similar redshift. There is however a group of 10 galaxies at a lower redshift. According to \cite{1998AJ....115..377F} the spectrum is typical for an early-type galaxy.

\textbf{HS0818+1227}: According to \cite{2000A&A...357L..29H} one galaxy, which seems to be at the same redshift, can be found near the lens. In roughly the same direction, two other brighter galaxies can be found a bit farther away. However, no further inquiries were made whether they all belong to the same group or not. There are also a couple of fainter ones, which could potentially be group members. \underline{TO DO}: Get relative position of nearest galaxy! More or less everybody lists HS0818 as an early-type, however noone states a source for their belief.

\textbf{RXJ0911+0551}: According to \cite{2001ApJ...555....1M} the lens lies on the outskirts of a cluster environment. The cluster seems to be rather complex and not spherical, and it possibly is not dynamically relaxed. The X-ray emission analysis yields a temperature of 2.3 keV. There is also a satellite galaxy to the north-west direction (\cite{2000ApJ...544L..35K}). The lens is a almost circular early-type galaxy (\cite{2012A&A...538A..99S}). Time delay: $\Delta t_{BA}=146\pm4$ (\cite{2002ApJ...572L..11H}; CASTLES: BD-delay, here BA-delay).

\textbf{BRI0952-0115}: Lens possibly part of smaller system (of 2 or 3 other galaxies), which is found at a slightly higher redshift, according to \cite{2007A&A...465...51E}. Surely group found in \cite{2006ApJ...641..169M} is at a lower redshift than the lens as the redshift estimate $z=0.41$ was used. \cite{2007A&A...465...51E} however find that the redshift is more likely to be $z=0.632$. In \cite{2000ApJ...536..584L} it is found that required external shear can be explained easily by a cosmic contribution. \cite{2000ApJ...536..584L}, and later on confirmed by \cite{2007A&A...465...51E}, find that it seems to be a typical early-type galaxy. \underline{TO DO}: Why is the such a hugely different redshift estimate in Table 4 of \cite{2006ApJ...641..169M}? Reason: In \cite{2000ApJ...536..584L} this redshift is listed as the lens redshift. --> Correct redshift used in analysis?

\textbf{Q0957+561}: The lens is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g. \cite{1992MNRAS.254P..27G}, \cite{1994A&A...291..411A}, \cite{1998ApJ...504..661C}). As listed in table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east. Judging 'by hand' from the center of the X-ray emission measured by \cite{1998ApJ...504..661C}, we find $\Delta\alpha=4.8''$ and $\Delta\delta=2.1''$, which corresponds to a position angle of 66.4 deg, consistent with the values listed above. \cite{2012A&A...540A.132S} measure the time delay in the g- and r-band. They find $\Delta t_{BA}=416.5\pm1.0$ in the g-band, $\Delta t_{BA}=420.6\pm1.9$ in the r-band. So, they find a three-day lag between these two bands and the two estimates do not agree at the 2$\sigma$-level. They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion (light propagation time increases with decreasing wavelength). \underline{TO DO}: Better measure of the cluster center? Time delay?

\textbf{LBQS1009-0252}: \cite{2000ApJ...536..584L} find that it is probably an early-type galaxy. According to \cite{2004A&A...428..741F}, there is no significant galaxy overdensity near the lens.

\textbf{B1030+074}: As noted by \cite{1998MNRAS.300..649X} it appears to have some substructure. \cite{2000ApJ...536..584L} conclude that they are two distinct galaxies. The main one is an red, early-type galaxy. The other component seems to be fitted well by an exponential disk galaxy. They also conclude that no firm statements about the environment can be made. Although there is another galaxy nearby, it is too blue to be an early-type galaxy and thus they cannot estimate its shear contribution. \underline{TO DO}: No error on position of G1 in \cite{2000ApJ...536..584L}?

\textbf{HE1104-1805}: \cite{2000ApJ...536..584L} find that it is probably an early-type galaxy (also \cite{2000A&A...360..853C}). They also seem to find a group environment. \cite{2004A&A...428..741F} however rather think that their photometric redshift measurement indicate that these galaxies are at a higher redshift and rather associated with the source. As it is also listed in \cite{2004A&A...428..741F}, modelling of the lens, parametric and free-form, requires strong external shear. Time delay: $\Delta t_{AB}=162.2^{+6.3}_{-5.9}$ (\cite{2008ApJ...676...80M}; here BA-delay).

\textbf{PG1115+080}: Environments analyzed by \cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W}. Lying in a small group of 13 members. The lens is an early-type galaxy (\cite{2005ApJ...626...51Y}). \cite{2004ApJ...610..686G} detect X-ray emission from the corresponding group at temperature 0.8 keV. Time delays: \cite{1997ApJ...489...21B} find $\Delta t_{AC}=13.3^{+0.9}_{-1.0}$ and $\Delta t_{BA}=11.7^{+1.5}_{-1.6}$, \cite{2010MNRAS.406.2764T} find however $\Delta t_{AC}=12.0^{+2.4}_{-2.0}$ and $\Delta t_{BA}=4.4^{+3.2}_{-2.4}$ (here actually BA- and CD-delay).

\textbf{B1152+200}: Not much seems to be known about the environment. The lens galaxy type is not known. According to \cite{2000A&A...357..115T} however, its color is consistent with a late-type or an irregular galaxy.

\textbf{B1422+231}: \cite{2006ApJ...641..169M} find totally 16 spectroscopically confirmed member galaxies of the group. Using newer data, \cite{2011ApJ...726...84W} find an additional member. \cite{2004ApJ...610..686G} detect X-ray emission from the corresponding group at temperature 1.0 keV. According to \cite{1996ApJ...462L..53I} the lens is an early-type galaxy. Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to trust too much as they deviate quite a bit from theoretical expectations in \cite{2003AJ....126...29R}. An accurate measurement of the time delays probably requires time delay measurements on the scale of hours.

\textbf{SBS1520+530}: There is some uncertainty about the redshift of the galaxy. \cite{2002A&A...391..481B} find that their spectroscopic redshift estimate of the galaxy is consistent with $z=0.71$, which was measured first by \cite{1997A&A...318L..67C}. Both however also measured a system at $z=0.82$. \cite{2002A&A...391..481B} however conclude that it does not seem to be associated with the lens. \cite{2008ApJ...673..778A} find another system at $z=0.76$. They argue that this system is more likely to be the lens, and the foreground system at $z=0.71$ just a local perturber. The data however does not seem to be conclusive. \cite{2008ApJ...673..778A} also find and spectroscopically confirm 3 groups in the line of sight. One is at $z=0.716$, with 5 members and the centroid position: $\alpha=15:21:48.16$, $\delta=52:53:19.5$. Another one at $z=0.758$, with 13 members and $\alpha=12:21:38.22$, $\delta=52:55:23.1$. Another one is at the higher redshift $z=0.818$ with 10 members. Including the lens would change these positions. The lens seems to be an early-type galaxy, possibly with a disc (\cite{2008ApJ...673..778A}). Time delay: $\Delta t_{BA}=125.8\pm2.1$ (\cite{2011A&A...536A..44E}; here also BA-delay). \underline{TO DO}: Dominik has used a lower redshift. Implications for the stellar population synthesis? Redo analysis at a higher redshift.

\textbf{B1600+434}: The lens is a nearly edge-on late-type galaxy (\cite{1997A&A...317L..39J}). No significant X-ray emission was detected from the surrounding group (\cite{2005ApJ...625..633D}). According to \cite{2007AJ....134..668A}, the lens lies in a group with at least seven members, which all seem to be late-type galaxies. The centroid of the group is not luminosity-weighted in the table. Time delay: $\Delta t_{AB}=51\pm2$ (\cite{2000ApJ...544..117B}; here BA-delay). \underline{TO DO}: No error on position estimate in paper? --> What should the error estimate for the centroid be? Add environment image?

\textbf{B1608+656}: The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}. All data points to a galaxy merger, so we could as well talk about 9 group members. A luminosity weighted measure was taken to find the group centroid. No errors are given, but as a comparision the median centroid is listed: $\Delta\alpha = 12.5$, $\Delta\delta = 21.6506$. Along the line of sight, there seem to be four other groups. No significant X-ray emission was detected from the surrounding group (\cite{2005ApJ...625..633D}). According to \cite{2003ApJ...584..100S} the galaxy G1 is an early-type galaxy which disrupted probably a late-type galaxy G2. Time delays: $\Delta t_{AB}=31.5^{+2}_{-1}$, $\Delta t_{CB}=36.0\pm1.5$, $\Delta t_{DB}=77.0^{+2}_{-1}$ (\cite{2002ApJ...581..823F}; here BA-, CA-, DA-delay). \underline{TO DO}: Errors? Add environment image?

\textbf{MG2016+112}: The environments were analyzed by \cite{2003MNRAS.344..337T}. They find a cluster-environment with photometrically 69 probable galaxies. Most galaxies are close to the lens and many lie in a south-east direction. It seems to be a giant elliptical (e.g. \cite{1984Sci...223...46L}, \cite{1986AJ.....91..991S}). \underline{TO DO}: Add environment image?

\textbf{B2045+265}: To the west of the lens, \cite{1999AJ....117..658F} find that there may be galaxies in a group at the same redshift as the lens \cite{2007MNRAS.378..109M} find evidence for a dwarf satellite galaxy, which would be needed to be included in the analysis. Although \cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, \cite{2007MNRAS.378..109M} find that it is more probable to be an elliptical galaxy as the velocity dispersion is higher than the characteristic velocity dispersion. Furthermore, the source redshift is relatively low compared to the lens redshift, which requires the deflector to have a large dark matter halo. The galaxy is well fitted by a de Vaucouleurs profile. \underline{TO DO}: Add environment image? Get position of the group?

\textbf{HE2149-2745}: According to \cite{2007A&A...465...51E} the spectrum is typical for an early-type galaxy. Although initial redshift estimations of \cite{1996A&A...315L.405W} found a probable redshift rang of $\equiv0.2-0.5$ (also see \cite{2000ApJ...543..131K}). \cite{2002A&A...383...71B} find by cross-correlating the lens spectrum with a template spectrum of an elliptical galaxy that the redshift probably lies in the range $0.49\leq z \leq 0.60$. They then conclude that the most likely redshift is $z=0.495\pm0.01$. \cite{2007A&A...465...51E} however find, that it is more likely to be $z=0.603\pm0.001$. This would make the lens part of a group at this redshift found by \cite{2006ApJ...641..169M} of probably 3 other members (kinematically not confirmed). They also find 2 groups at lower redshifts. \cite{2006ApJ...646...85W} calculated a luminosity weighted centroid position. Time delay: $\Delta t_{BA}=103\pm12$ (\cite{2002A&A...383...71B}; here also BA-delay). \underline{TO DO}: Change redshift from 0.50 to 0.60 in the calculations.

\textbf{Q2237+030}: There seems to be no information available on the environment. According to \cite{1988AJ.....95.1331Y} the lens is a barred spiral.

Further information about the sample can be found in \cite{leier11phd}, \cite{2011ApJ...740...97L}, and \cite{2012A&A...538A..99S}.

\section{Methods}
\subsection{GLASS}
\begin{itemize}
\item Explain GLASS briefly
\end{itemize}

We use the new free-form lens modelling framework \textit{GLASS} (\cite{2012MNRAS.425.3077L}). As its predecessor \textit{PixeLens} (\cite{2004AJ....127.2604S}), it reconstructs a pixelated mass map of a lens reproducing the image positions perfectly. In this case, the arrival time surface for a source at position $\boldsymbol\theta_{S}$ taking the geometric and Shapiro contributions into account can be calculated using (\cite{1997MNRAS.292..148S})
\begin{equation}
\tau(\boldsymbol\theta)=\frac{1}{2}|\boldsymbol\theta |^{2}-\boldsymbol\theta\cdot\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\psi_{n}(\boldsymbol\theta),
\end{equation}
where $\kappa_{n}$ is the surface mass density in the n-th pixel rescaled by the critical density $\Sigma_{crit}$ and $\psi_{n}$ is the contribution to the gravitational potential by this pixel.

According to Fermat's principle, lensed images appear where the arrival time surface takes on extremal values $\nabla\tau(\boldsymbol\theta)=0$. Thus we have to solve the following equation
\begin{equation}
\boldsymbol\theta-\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\alpha_{n}=0,
\end{equation}
where $\alpha_{n}$ is the contribution to the bending angle of the n-th pixel. Therefore, to reconstruct the lens, i.e. finding $\{\kappa_{n}\}$, this linear equation has to be solved. Additional constraints on the lens like individual time delays between images and all priors are also linear. The problem is highly underconstrained, so the solution domain is a high-dimensional polytope.

The dimension of the solution space usually exceeds $\gtrsim100$ why sophisticated sampling methods are required. Here \textit{GLASS} and \textit{PixeLens} differ. \cite{2008ApJ...679...17C} and \cite{2012MNRAS.425.3077L} show that \textit{PixeLens} does not produce uncorrelated random samples. They propose a new sampling algorithm. They prove that generic high-dimensional volumes indeed are sampled in a much more uniform way. Models in \textit{GLASS} are generated using a MCMC-method with a Metropolis-Hastings algorithm. A new step $x_{i+1}$ of the Markov chain is accepted with the probability
\begin{equation}
\alpha = \mathrm{min}\left(1,\frac{P(x_{i+1})Q(x_{i},x_{i+1})}{P(x_{i})Q(x_{i+1},x_{i})}\right),
\end{equation}
where $P(x)$ is the probability distribution samples are drawn from, and $Q(x_{i},x_{i+1})$ is the proposal density. It is special in mass modelling that all the valid mass configurations have the same probability, thus $P$ is a constant $\equiv1$. For Markov chains $Q$ has to be symmetric. It is usually taken to be a multivariate Gaussian $\mathcal{N}(x,\hat{\boldsymbol\Sigma})$, where $\hat{\boldsymbol\Sigma}$ is an estimate of the true covariance matrix $\boldsymbol\Sigma$. In principle it could be estimated by an adaptive chain during the random walk, but then the chain is no longer Markovian as it loses the reversibility property. Therefore, first an initial adaptive burn-in phase is run to get an good estimate $\hat{\boldsymbol\Sigma}$, before the real MCMC random walk. Many models can thus be generated and the solution space sampled. The estimation of the covariance matrix is refined in \textit{GLASS} such that models are much less correlated. Further details and tests of the method can be found in \cite{2012MNRAS.425.3077L} and (((citation needed of Jonathan's fake data paper))).

Priors: Reference cosmology, chosen priors, etc.

\subsection{Shape measure}
\begin{itemize}
\item Explain shape measure
\item Link to tests on fake data
\item Include one plot of fake data test
\end{itemize}

To get a rough estimate of the shape we use the inverse of the moment of inertia tensor we can compute of the mass map. Its eigenvectors and eigenvalues track the shape of the mass distribution. This seemingly crude measure was tested on fake data.

--- Need to expand ---

\section{Results}
\begin{itemize}
\item Show some examples (stellar and dm contour plots, image of lens, arrival time surface, included mass)
\item Show money plots
\item Comment on a few lenses
\end{itemize}

\section{Conclusion}

\nocite{*}
\bibliographystyle{mnras} % this is one type of author-year style
\bibliography{thesis.bib} % this prints the bibliography section based on the \cite commands
\end{document}

### 2013-02-20 shapes/thesis.tex
thesis update

@@
 Ask Prasenjit).
+They find no obvious correlation in the axis ratios of the distributions.
 
@@
 
-\textbf{\cite{2000ApJ...538L.113N}}:
-
-\textbf{\cite{2002sgdh.conf...62K}}:
-
-\textbf{\cite{2005MNRAS.360.1333W}}:
-
-\textbf{\cite{2008MNRAS.383..857F}}:
-
 \textbf{\cite{2011AstRv...6f..43B}}:
 
-\textbf{\cite{2012ApJ...761..170G}}:
+\textbf{\cite{2006ApJ...649..599K}}: They use 15 massive field early-type galaxies selected from the SLACS Survey.
+To reconstruct the mass distribution (for total mass) they use a SIE mass model (Kormann et al.
+1994) without external shear (they justify it by stating that an external shear was not required and also in hindsight as a small $\Delta\theta$ rms spread was reconstructed).
+The light distribution is based on the nonparametric source reconstruction method by Warren & Dye 2003 and is described in Treu & Koopmans 2004 and Koopmans 2005.
+They analyze then the misalignment between light and mass and find that the average difference is $\left<\Delta\theta\right>=0^{\circ}\pm3^{\circ}$ with a rms spread of $10^{\circ}$.
+For almost spherical SIEs, i.e.
+$q_{\mathrm{SIE}}>0.75$ the rms spread is $13^{\circ}$, for less spherical distributions, $q_{\mathrm{SIE}}<0.75$, it is only $3^{\circ}$.
+They conclude that this implies that dark matter is aligned with the stellar component on scales $\lesssim4$ kpc.
+They also find using a theoretical formula for the external shear from \cite{1997ApJ...482..604K} and assuming that there is no correlation between the galaxies and external shear orientations, they find that the average external shear has an upper limit of $\left<\gamma_{\mathrm{ext}}\right>\lesssim0.035$.
+They conclude therefore that the alignment of mass and light confirms that the external shear is very small and can be neglected.
+They state that significant external shear would in general cause a spread in $\Delta\theta$ if not accounted for in the models.
+
+\textbf{\cite{2009ApJ...690..670T}}: They look at 70 lenses from the SLACS Survey, mostly early-type galaxies (62), 6 disk galaxies, and 2 have ambiguos morphology.
+They again fit a SIE without external shear and compare the position angles of the distributions.
+They argue that the stellar contribution is significant at the scales they test and therefore they expect no misalignment if there is no significant external potential.
+Also the contrary should hold that the rms amplitude of the misalignment is a measure of the external perturbing potential (\cite{1997ApJ...482..604K}; \cite{2006ApJ...649..599K}).
+They find that the correlation between alignment and local resp.
+global environment is significant.
+They do not expect a simple relation between these.
+However, in general lenses in overdense environments will be more likely to be affected by nearby companions, which causes a misalignment (external perturber located in a random direction).
+They estimate again that external shear of order 0.05-0.06 is needed to match the results.
+
+\textbf{\cite{2012ApJ...761..170G}}: They use 16 massive early-type galaxies from SL2S (only 2 are quads).
+They reconstruct the lens mass with a SIE.
+They only add an external shear when more information is available.
+To find the intrinsic source light distribution they try to minimize a $\chi^{2}$ (they have an observed, pixelated light distribution).
+All in all, they use a MCMC technique to find the best-fitting 9-parameter-model  (6 from light, 3 from SIE (ellipticity, position angle, Einstein radius).
+They find that stellar and mass ellipticities are tightly correlated (think it is reasonable as light makes up a significant part) with the exception of a few outliers (some basically spherical mass distributions, and one case where the stars are almost round and the mass is flatte -> state that source of ellipticities seems to be external shear associated with a satellite).
+The scatter they find in the ellipticities ratio is however larger than it is in the SLACS sample, which is also at a lower redshift.
+This is probably due to a much more significant role played by external shear.
+They also find reasonable alignment between light and mass, the scatter is however larger than for the SLACS sample.
+For almost round mass distributions the scatter is $25^{\circ}$, for less round distributions it is still $18^{\circ}$.
+Again the calculate the required average external shear and find (independent of including the round lenses or not) $\left<\gamma_{\mathrm{ext}}\right>=0.12\pm0.05$.
+This is significantly larger than what they found for the SLACS lenses.
+They think that it is likely due to the environment of the lenses (\cite{2007AJ....134..668A}; \cite{2009ApJ...690..670T}; Auger 2008; \cite{2011ApJ...726...84W}).
 
@@
 \item SPS (Ignacio Ferreras, Dominik, etc. (\cite{2011ApJ...740...97L}))
+\item Write why specifically these lenses were chosen, where they're from
 \item Bundle information in tables (especially what input data was used for the lenses)

### 2013-03-25 shapes/paper.tex
paper outline and plots

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{myaasmacros}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{amsmath}

% Some definitions of things I always use here:
\def\ltsima{$\; \buildrel < \over \sim \;$}
\def\simlt{\lower.5ex\hbox{\ltsima}}   
\def\gtsima{$\; \buildrel > \over \sim \;$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\newcommand\bcite[1]{\citeauthor{#1} \citeyear{#1}}

% Some definitions for the priors:
\def\gprior{{\tt gprior}}
\def\cprior{{\tt cprior}}
\def\bprior{{\tt bprior}}
\def\lbprior{{\tt lbprior}}

%Some definitions for rhodm etc:
\def\vztwo{\overline{v_z^2}}
\def\vztwoi{\overline{v_{z,i}^2}}
\def\rhodisc{\rho_\mathrm{disc}(z)}
\def\rhodmext{\rho_\mathrm{dm,ext}}
\def\rhodm{\rho_\mathrm{dm}}
\def\rhoeff{\rho_\mathrm{dm}^\mathrm{eff}}
\def\nuobs{\nu_\mathrm{obs}(z)}

\title[Alignment of Light and Mass in Lensing Galaxies]{Alignment of Light and Mass in Lensing Galaxies}

\author[Bruderer]{Claudio Bruderer$^1$\thanks{E-mail: claudio.bruderer@phys.ethz.ch}, J. I. Read$^{1,2}$, P. Saha$^3$, J. Coles$^3$\\
$^1$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
$^2$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
$^3$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland
}

\begin{document}

\maketitle

\begin{abstract}
Abstract here. 
\end{abstract}

\begin{keywords}
\end{keywords}

\section{Introduction}

\subsection{Context/Background/Motivation}
\begin{itemize}
\item Why interesting (lensing can constrain mass distribution (enclosed mass constraint independent from model with only few percent uncertainty e.g. Kochanek 1991?, Wambsganss \& Paczyński 1994?), insights into structure formation)
\item What is to be expected from theory (dm, alternative gravity)
\end{itemize}

\subsection{Anything done before?}
\begin{itemize}
\item Surely cite: \cite{1997ApJ...482..604K,1998ApJ...509..561K,2006ApJ...649..599K,2009ApJ...690..670T,2012ApJ...761..170G}
\end{itemize}

\subsection{New here}
\begin{itemize}
\item Statistics
\item Free-form modelling
\item group versus stellar misalignment with dm halo
\end{itemize}

\section{Data}
\begin{itemize}
\item SPS (Ignacio Ferreras, Dominik, etc. \citep{2011ApJ...740...97L})
\item Write why specifically these lenses were chosen, where they're from
\end{itemize}

\begin{table}
 \begin{center}
  \begin{tabular}{l c c l | l c c l}
   Lens & $z_{L}$ & $z_{S}$ & Type & Lens & $z_{L}$ & $z_{S}$ & Type\\ \hline \hline
   Q0047 & 0.48 & 3.60 & Quad & HE1104 & 0.73 & 2.32 & Double\\
   Q0142 & 0.49 & 2.72 & Double & PG1115 & 0.31 & 1.72 & Quad\\
   MG0414 & 0.96 & 2.64 & Quad & B1152 & 0.44 & 1.02 & Double\\
   B0712 & 0.41 & 1.34 & Quad & B1422 & 0.34 & 3.62 & Quad\\
   RXJ0911 & 0.77 & 2.80 & Quad & B1608 & 0.63 & 1.39 & Quad\\
   BRI0952 & 0.63 & 4.50 & Double & MG2016 & 1.01 & 3.27 & Quad$^{1}$\\
   Q0957 & 0.36 & 1.41 & Double & B2045 & 0.87 & 1.28 & Quad\\
   LBQS1009 & 0.87 & 2.74 & Double & HE2149 & 0.60 & 2.03 & Double\\
   B1030 & 0.60 & 1.54 & Double & Q2237 & 0.04 & 1.69 & Quad\\
%   SBS1520 & 0.72 & 1.86 & Double
%	B1600 & 0.41 & 1.59 & Double\\
  \end{tabular}
  \caption{List of all the lenses in the sample and their properties. Data is taken from \textit{CASTLES} and \cite{leier11phd}. The angles are measured north-through-east. \newline $^{1}$ Two images merge, thus only three images can be resolved.}
  \label{tab:overview}
 \end{center}
\end{table}

\begin{table}
 \begin{center}
  \begin{tabular}{l c c c c c c c}
   \multirow{2}{*}{Lens} & \multirow{2}{*}{Environment$^{a}$} & \multicolumn{2}{c}{Group/Cluster centroid$^{b}$} & & \multicolumn{2}{c}{Other galaxy} & \multirow{2}{*}{References$^{c}$}\\ \cline{3-4} \cline{6-7}
    & & $\Delta\alpha$ [''] & $\Delta\delta$ [''] & & $\Delta\alpha$ [''] & $\Delta\delta$ ['']\\ \hline \hline
   Q0047 & G(9) & $3.6\pm15.6$ & $43.2\pm28.8$ &   & ... & ... & 1\\
   MG0414 & 2 & ... & ... &   & $-0.4$ & $1.5$ & 2\\
   B0712 & 2 & ... & ... &   & $47$ & $-91$ & 3\\
   RXJ0911 & C & $-12.0$ & $-39.8$ &    & ... & ... & 4\\
   Q0957 & C & ... & ... &   & ... & ... & 5\\
   B1030 & 2 & ... & ... &   & $-9.8$ & $8.5$ & 6\\
   PG1115 & G(13) & $-10.8\pm21.0$ & $-3.6\pm15.6$ &   & ... & ... & 1\\
   B1422 & G(17) & $61.2\pm25.2$ & $-10.8\pm23.4$ &   & ... & ... & 1\\
%   SBS1520 & G(5) & ... & ... &   & ... & ... & 7\\
%   B1600 & G(17) & $-8.4^{d}$ & $-1.5^{d}$ &   & ... & ... & 8\\
   B1608 & G(8) & $-0.7$ & $8.0$ &   & ... & ... & 9\\
   MG2016 & C(69) & ... & ... &   & ... & ... & 10\\
   HE2149 & G & $-36.6$ & $14.2$ &   & ... & ... & 11\\
  \end{tabular}
  \caption{List of lenses lying in a group or cluster environment, or that have a companion. \newline $^{a}$ G stands for group, C for cluster, and 2 means that the lens has a companion galaxy. If known, the number of member galaxies including the lens is given. \newline $^{b}$ If not stated differently, the centroid positions are luminosity-weighted estimates. \newline $^{c}$ References for the centroid estimates we used. \newline $^{d}$ Only number-weighted estimates are available. \newline 1: \cite{2011ApJ...726...84W}; 2: \cite{1993AJ....105....1S}; 3: \cite{2002AJ....123..627F}; 4: \cite{2001ApJ...555....1M}; 5: \cite{1998ApJ...504..661C}; 6: \cite{2000ApJ...536..584L}; 7: \cite{2008ApJ...673..778A}; 8: \cite{2007AJ....134..668A}; 9: \cite{2003MNRAS.344..337T}; 10: \cite{2006ApJ...646...85W}; 11: \cite{2006ApJ...646...85W}}
  \label{tab:environment}
 \end{center}
\end{table}

\begin{table}
 \begin{center}
  \begin{tabular}{l c c c c}
   Lens & \multicolumn{3}{c}{Time delays [d]} & References\\ \hline \hline
   RXJ0911 & $\Delta t_{BA}=146\pm4$ & ... & ... & 1\\
   Q0957 & $\Delta t_{BA}=416.5\pm1.0^{a}$ & $\Delta t_{BA}=420.6\pm1.9^{b}$ & ... & 2\\
   HE1104 & $\Delta t_{BA}=162.2^{+6.3}_{-5.9}$ & ...  & ...  & 3\\
   PG1115 & $\Delta t_{BA}=12.0^{+2.4}_{-2.0}$ & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & ... & 4\\
%   SBS1520 & $\Delta t_{BA}=125.8\pm2.1$ & ... & ... & 5\\
%   B1600 & $\Delta t_{BA}=51\pm2$ & ... & ... & 6\\
   B1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & $\Delta t_{CA}=36.0\pm1.5$ & $\Delta t_{DA}=77.0^{+2}_{-1}$ & 7\\
   HE2149 & $\Delta t_{BA}=103\pm12$ & ... & ... & 8\\
  \end{tabular}
  \caption{Lenses with measured time delays. $\Delta t_{BA}$ corresponds to the time delay between the images A and B with A leading. \newline $^{a}$ measured in the g-band \newline $^{b}$ measured in the r-band \newline 1: \cite{2002ApJ...572L..11H}; 2: \cite{2012A&A...540A.132S}; 3: \cite{2008ApJ...676...80M}; 4: \cite{2010MNRAS.406.2764T}; 5: \cite{2011A&A...536A..44E}; 6: \cite{2000ApJ...544..117B}; 7: \cite{2002ApJ...581..823F}; 8: \cite{2002A&A...383...71B}}
  \label{tab:timedelays}
 \end{center}
\end{table}

The pixelated stellar mass maps we use, were reconstructed by \cite{leier11phd}. For each pixel the surface brightness was compared with stellar mass-to-light ratios, which were determined by stellar population synthesis models. This technique allows estimating the stellar mass in these pixels. Further details on this method can be found in \cite{leier11phd}, \cite{2005ApJ...623L...5F}, \cite{2008MNRAS.383..857F}.

Our sample consists of 20 galaxies. The sample is identical to the one as in \cite{leier11phd} and \cite{2011ApJ...740...97L} except that \textit{HS0818+1227} proved too difficult to reconstruct and therefore was left out. Most of the lens galaxies are early-type galaxies, except \textit{B1030+074}, \textit{B1152+200}, \textit{B1600+434}, \textit{B1608+656}, and \textit{Q2237+030}. All lenses can also be found in the gravitational lens database \textit{CASTLES}. Characteristics and references of each lens in the sample are listed below. Table \ref{tab:overview} contains of all the redshifts and the type of the lenses, Table \ref{tab:environment} lenses with environment information, and Table \ref{tab:timedelays} lenses with measured time delays.

\textit{Q0047-2808} (hereafter \textit{Q0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}. \cite{2011ApJ...726...84W} find a group of 9 members all of which they spectroscopically confirm.

\textit{Q0142-100} (hereafter \textit{Q0142}) is a passively evolving early-type galaxy according to \citep{2000ApJ...536..584L,2007A&A...465...51E}.

\textit{MG0414+0534} (hereafter \textit{MG0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}. \cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens. Due to the proximity of this satellite, we include it as a point mass in our analysis.

\textit{B0712+472} (hereafter \textit{B0712}) is an early-type galaxy \citep{1998AJ....115..377F}. Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}. There is also a group of 10 galaxies at a lower redshift.

\textit{RXJ0911+0551} (hereafter \textit{RXJ0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}. It has measured time delays \citep{2002ApJ...572L..11H}. It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}. This cluster seems to be rather complex and especially it is not spherical. Possibly it is not dynamically relaxed, although X-ray emission can be detected. Analysis of this emission yields a temperature of 2.3 keV. There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.

\textit{BRI0952-0115} (hereafter \textit{BRI0952}) is an early-type galaxy \citep{2000ApJ...536..584L,2007A&A...465...51E}. \cite{2006ApJ...641..169M} find that the lens lies in a poor group of 5 members. However, a redshift of $z=0.41$ was used. According to \cite{2007A&A...465...51E}, the redshift is more likely to be $z=0.632$. They also find a system of 2 or 3 other galaxies at a slightly higher redshift of which the lens could be part of. The required external shear could be explained easily by a cosmic contribution \citep{2000ApJ...536..584L}. Therefore, we treat this lens as an isolated object.

\textit{Q0957+561} (hereafter \textit{Q0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g. \cite{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}). Due to the large image separation, large physical scales are probed. As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east. These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}. The lens has a measured time delay, e.g. \citep{2012A&A...540A.132S}. They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level. They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion. We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.

\textit{LBQS1009-0252} (hereafter \textit{LBQS1009}) is probably an early-type galaxy \citep{2000ApJ...536..584L}. \cite{2004A&A...428..741F} find no significant galaxy overdensity near the lens.

\textit{B1030+074} (hereafter \textit{B1030}) appears to have some substructure \citep{1998MNRAS.300..649X}. \cite{2000ApJ...536..584L} conclude that there are two distinct galaxies. The main one is a red, early-type galaxy. The other component seems to be fitted well by an exponential disk galaxy. They also conclude that no firm statements about the environment can be made. Although there is another galaxy nearby, it is too blue to be an early-type galaxy and thus they cannot estimate its shear contribution.

\textit{HE1104-1805} (hereafter \textit{HE1104}) is probably an early-type galaxy \citep{2000ApJ...536..584L,2000A&A...360..853C}. It has measured time delays \citep{2008ApJ...676...80M}. \cite{2000ApJ...536..584L} also seem to find a group environment. \cite{2004A&A...428..741F} however conclude that the photometric redshift measurements of these galaxies indicate that they are at a higher redshift and rather associated with the source. Nonetheless, their lens models, parametric and free-form, all require strong external shear.

\textit{PG1115+080} (hereafter \textit{PG1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}. It has measured time delays. We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ significantly from traditional values by e.g. \cite{1997ApJ...489...21B}. \cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W} analyzed the environment of the lens thouroughly. It is part of a small group of 13 members. \cite{2004ApJ...610..686G} detect also X-ray emission from the corresponding group, which yields a temperature of 0.8 keV.

\textit{B1152+200} (hereafter \textit{B1152}) seems to have a color consistent with a late-type or an irregular galaxy \citep{2000A&A...357..115T}. Not much seems to be known about the environment of the lens.

\textit{B1422+231} (hereafter \textit{B1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}. Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to be trusted too much as they deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}. An accurate measurement of the time delays would require time delay measurements on the scale of hours. \cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies. Using newer data, \cite{2011ApJ...726...84W} find an additional member. \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.

%\textit{SBS1520+530} (hereafter \textit{SBS1520}) is an early-type galaxy, possibly with a disc \citep{2008ApJ...673..778A}. It has measured time delays \citep{2011A&A...536A..44E}. There is some uncertainty about the redshift of the galaxy. \cite{2002A&A...391..481B} find that their spectroscopic redshift estimate is consistent with $z=0.71$, which was measured first by \cite{1997A&A...318L..67C}. Both however also find a system at $z=0.82$, which could be the main lens. \cite{2002A&A...391..481B} however conclude that it is not associated with the lens. \cite{2008ApJ...673..778A} argue that a system they find at $z=0.76$ is more likely to be the lens, and the foreground system at $z=0.71$ is just a local perturber. Data seems however not conclusive. \cite{2008ApJ...673..778A} find and spectroscopically confirm a total of 3 groups along the line of sight. A poor group of 5 members is at $z=0.716$, another one with 13 members is at $z=0.758$, and a third group with 10 members is at a higher redshift $z=0.818$.

%\textit{B1600+434} (hereafter \textit{B1600}) is a nearly edge-on viewed late-type galaxy \citep{1997A&A...317L..39J}. The lens lies in a group with at least seven members, which all seem to be late-type galaxies \citep{2007AJ....134..668A}.

\textit{B1608+656} (hereafter \textit{B1608}) consists of two merging galaxies. The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}. The system has measured time delays \citep{2002ApJ...581..823F}. The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}. They find a group with 8 resp. 9 members if the merging galaxies are counted as 2. No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}. Along the line of sight seem to be four other groups.

\textit{MG2016+112} (hereafter \textit{MG2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}. It is the farthest lens we consider in this sample. It lies in a cluster which consists of 69 probable galaxies \citep{2003MNRAS.344..337T}. The clusters shows a high density of galaxies close to the lens in a south-east direction.

\textit{B2045+265} (hereafter \textit{B2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}. \cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high. As the source redshift is rather low, a large lens mass is needed. \cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy. To the west of the lens, \cite{1999AJ....117..658F} find that a group at a similar redshift as the lens. \cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy.

\textit{HE2149-2745} (hereafter \textit{HE2149}) is an early-type galaxy \citep{2007A&A...465...51E}. It has a measured time delay \citep{2002A&A...383...71B}. There is some uncertainty in estimating the lens' redshift. Initial estimates by \cite{1996A&A...315L.405W,2000ApJ...543..131K} found a probable redshift range of $\sim0.2-0.5$. By cross-correlating the lens spectrum with a template spectrum of an elliptical galaxy, \cite{2002A&A...383...71B} find that the redshift probably lies in the range $0.49\leq z \leq 0.60$, with the most likely redshift $z=0.495\pm0.01$. \cite{2007A&A...465...51E} however find that the redshift is more likely to be $z=0.603\pm0.001$. This would probably make the lens part of a poor group found by \cite{2006ApJ...641..169M} and \cite{2006ApJ...646...85W}. They also find two other groups at lower redshifts.

\textit{Q2237+030} (hereafter \textit{Q2237} or \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}. With only a redshift of $z=0.04$, it is the closest lens of the sample. Due to the low redshift, the probed physical scales are quite small. No further inquiries into the environment were made.

Further information about the sample can be found in \cite{leier11phd}, \cite{2011ApJ...740...97L}, and \cite{2012A&A...538A..99S}.

NOTE: Cannot use B1608, but I still left it in the sample as Fei probably will use the lens.

\section{Methods}
\subsection{GLASS}
\begin{itemize}
\item Explain GLASS briefly and link to fake data tests
\end{itemize}

\subsection{Priors and assumptions}
\begin{itemize}
\item Explain what priors were chosen to model the lenses
\end{itemize}

Basically always pixrad 12, shear left free for quads, shear limited for doubles to 0.01, local gradient 50 degrees, smoothening prior 2, time delays if known. Exceptions are few. For some quads symmetry prior, for one double 0.01 was not possible therefore chose 0.1.

\subsection{Shape measure}
\begin{itemize}
\item Explain shape measure
\item Link to tests on fake data
\item Include one plot of fake data test -> Jonathan
\item Illustrate everything with example lens PG1115.
\end{itemize}

\section{Results}
\begin{itemize}
\item Show some examples (stellar and dm contour plots, image of lens, arrival time surface, included mass)
\item Show money plots
\item Comment on a few lenses special lenses
\item Environmental effect?
\end{itemize}

\begin{figure}
 \begin{center}
  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_a.eps}
  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_b.eps}
  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_c.eps}
  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_d.eps}
  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_h.eps}\\
  \caption{Reconstruction of lens \textit{PG1115}}
  \label{fig:1115rec}
 \end{center}
\end{figure}

\begin{figure}
 \begin{center}
 \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/b.eps}
 \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/d.eps}
 \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/e.eps}
 \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
 \label{fig:moneyplots}
 \end{center}
\end{figure}

\begin{figure}
 \begin{center}
 \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/g.eps}
 \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
 \label{fig:environmentmisalign}
 \end{center}
\end{figure}

\section{Conclusion}
\begin{itemize}
\item Recapitulate what were the main results
\item Answer whether this method is promising
\item What is needed to understand such misalignments better (-> Surely need to understand environment effects better, ...)
\end{itemize}

\section{Acknowledgements}
Acknowledge Dominik Leier...
JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.

\bibliographystyle{mn2e}
\bibliography{paper.bib}

\end{document}

### 2013-05-07 shapes/paper.tex
update on paper

@@
+% Open Tasks
+%
+% --- Keywords ---
+% - Add keaywords
+%
+% --- Introduction ---
+% - Citiations needed in parametric vs. nonparametric comparison part
+% - Citiations needed on effect of environment
+% - Section on how this work might be able to rule out certain alternative gravity models
+% - Describe theoretical expectations (ellipticities of dm halo and luminous part, misalignments, effect of environment)
+% - ...
+%
+%
+% --- Data ---
+% - More detailed description how the baryionic mass distribution was measured
+% - ...
+%
+%
+% --- Method ---
+% - Maybe more details on GLASS and how it works (cite Jonathan's upcoming paper)
+% - Plot showing how well the shape informations is recovered when applied to fake data
+% - ...
+%
+%
+% --- Results ---
+% - Interpretation of 
+% - Interpretation of ellipticities plot (why it is relevant that dm halos are significantly rounder)
+% - Interpretation of misalignment versus ellipticity plot ('forbidden region', alignment with semi-minor axis, very elliptical galaxies well aligned)
+
 \documentclass[useAMS,usenatbib]{mn2e}
@@
 \usepackage{amsmath}
+\usepackage{multirow}
 
 % Some definitions of things I always use here:
-\def\ltsima{$\; \buildrel < \over \sim \;$}
-\def\simlt{\lower.5ex\hbox{\ltsima}}   
-\def\gtsima{$\; \buildrel > \over \sim \;$}
-\def\simgt{\lower.5ex\hbox{\gtsima}}
 \newcommand\bcite[1]{\citeauthor{#1} \citeyear{#1}}
-
-% Some definitions for the priors:
-\def\gprior{{\tt gprior}}
-\def\cprior{{\tt cprior}}
-\def\bprior{{\tt bprior}}
-\def\lbprior{{\tt lbprior}}
-
-%Some definitions for rhodm etc:
-\def\vztwo{\overline{v_z^2}}
-\def\vztwoi{\overline{v_{z,i}^2}}
-\def\rhodisc{\rho_\mathrm{disc}(z)}
-\def\rhodmext{\rho_\mathrm{dm,ext}}
-\def\rhodm{\rho_\mathrm{dm}}
-\def\rhoeff{\rho_\mathrm{dm}^\mathrm{eff}}
-\def\nuobs{\nu_\mathrm{obs}(z)}
 
@@
 
-\author[Bruderer]{Claudio Bruderer$^1$\thanks{E-mail: claudio.bruderer@phys.ethz.ch}, J. I. Read$^{1,2}$, P. Saha$^3$, J. Coles$^3$\\
-$^1$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
-$^2$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
-$^3$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland
+\author[Bruderer]{Claudio Bruderer$^{1}$\thanks{E-mail: claudio.bruderer@phys.ethz.ch}, J. I. Read$^{2}$, P. Saha$^{3}$, J. Coles$^{4}$\\
+$^{1}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
+$^{2}$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
+$^{3}$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
+$^{4}$Somewhere in France, France
 }
@@
 \begin{abstract}
-Abstract here. 
+Understanding the structure and properties of galaxies today is essential to understand how galaxies formed.
+This poses a larger problem to us than one might imagine.
+Especially constraining the dark matter distribution in galaxy halos is not trivial.
+There are only a few methods to directly estimate this distribution.
+One of them is strong gravitational lensing, an effect caused by all of mass.
+This phenomenon allows constraining the gravitational potential of lens galaxies and thus the mass distribution.
+With knowledge of the light distribution it is possible to disentangle the dark matter and baryonic mass components and study their properties.
+We use the newly-developped nonparametric framework \textit{GLASS} to model the mass distribution of a total of 15 strong gravitational lensing galaxies, most of which are early-type galaxies, for which we have information on the baryonic mass distribution.
+We are thus able to separate the mass components.
+By using a simple shape measure, namely the inverse of the moment of inertia tensor, we can analyze the shapes of the distributions.
+Analyzing the alignments between the semi-major axes of the distributions, we find that there can be significant misalignments and also cases of alignment between the semi-minor and semi-major axes.
+Mass thus need not follow light.
+Furthermore, the ellipticities of the dark matter distributions are always smaller than the baryonic mass distributions.
+Dark matter halos tend to be more spherical than the light distribution of the galaxy.
+We also consider the environment of the lenses.
+We find that lenses in denser environments tend to be more misaligned with either the semi-major or semi-minor axis.
+Additionally, the semi-major axis of lenses lying in groups or clusters of the dark matter halo might be oriented in direction of the centroid.
 \end{abstract}
@@
 \begin{keywords}
+asdf....
 \end{keywords}
 
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 
@@
 
-\section{Data}
+Gravitational lensing is one of the few phenomena that allow probing the matter distribution directly.
+It makes no distinction between baryonic and dark matter, both components act on light rays in the same way.
+Gravitational lensing is therefore somewhat special as it allows to \textit{see} dark matter, if we are able to separate the two components.
+Therefore studying these effects allows us to probe dark matter and its properties.
+We are typically interested in measuring its distribution, how it clusters, its connection to structure formation, and of course its nature.
+With strong gravitational lensing galaxies we are effectively probing the matter distribution on relatively small scales.
+Thus, much insight could be gained in how galaxies form and how they are structured.
+
+The main challenges are however first, estimating the baryonic mass distribution such that the two components can be disentangled (see e.g.
+\cite{leier11phd}), and second, modelling the lens, i.e.
+the mass distribution.
+This work focuses purely on the second aspect.
+There are in general two classes of methods to reconstruct gravitational lenses, parametric and nonparametric methods.
+A comparison of these two classes of methods can be found in \cite{2008ApJ...681..814C}.
+Parametric methods assume a distribution, which depends only on few parameters, such that the problem is well constrained and a best-fitting model can be found.
+They are computationally cheap, but on the other hand the assumption of a distribution might bias the result (CITATION NEEDED!).
+Nonparamatric (or free-form) methods assume a set of basis functions and find valid solutions in terms of linear superpositions of these functions.
+The problem is largely underconstrained.
+Due to the fact that there is no a priori reason to prefer specific mass models, given that they all satisfy certain prior conditions and reproduce the same gravitational lensing effects, over others, the best-fitting model is of little interest.
+Much more important is to explore many models and look at the properties of all the models in the ensemble.
+Typically high-dimensional parameter spaces, which describe all allowed models, need to be sampled in a uniform and uncorrelated way to generate a representative ensemble of solutions.
+The computational cost of these methods is usually much higher \citep{2008ApJ...679...17C,2012MNRAS.425.3077L}.
+
+With these tools, we can start answering the long-standing question whether mass follows light.
+It is a well-known fact that for observations to match for example rotation curves of galaxies, the radial density profiles of baryonic mass and dark matter differ.
+The question is however whether baryonic mass and dark matter need to be aligned and the ellipticities need to agree.
+If this is not the case, then this needs to be explained by mechanism and effects that produce and sustain these different properties.
+Especially the environment of lenses might play a significant role (CITATION NEEDED!).
+It is furthermore unclear whether modified gravity theories could explain possible misalignments between mass and light.
+
+There were already attempts to analyze the alignment of light and mass.
+\cite{1997ApJ...482..604K} use Singular Isothermal Spheres (SIS) with an external shear term and Singular Isothermal Ellipsoids (SIE) (e.g.
+\cite{1994A&A...284..285K}) without external shear to model the mass distribution.
+Applying this to a sample of 17 lenses, they find a strong correlation between light and dark matter distributions, if there is no strong external perturbation, with only a small scatter of less than $10^{\circ}$.
+They find however no correlation between the axis ratios of the distributions.
+
+Later on, \cite{2006ApJ...649..599K} and \cite{2012ApJ...761..170G} analyzing lens samples of similar sizes and \cite{2009ApJ...690..670T} analyzing a lens sample containing even 70 galaxies also looked for misalignments.
+They all use SIEs to model the mass distributions.
+Only \cite{2012ApJ...761..170G} however include an external shear contribution in case more information is available.
+They neglect the external shear although \cite{1998ApJ...509..561K} find that SIEs with an independent external shear term fit the data better.
+They find reasonable alignments, the scatter is however larger than the one found in \cite{1997ApJ...482..604K}.
+\cite{2012ApJ...761..170G} find a rms scatter of $25^{\circ}$ for the whole sample.
+Even after dropping the almost spherical lenses, the rms scatter is still $18^{\circ}$.
+They attribute this to a significant external shear contribution.
+\cite{2009ApJ...690..670T} even find a significant correlation between the misalignment and the local and global environment.
+In general, lenses in overdense environments seem to be more likely to be misaligned.
+\cite{2009ApJ...690..670T} and \cite{2012ApJ...761..170G} also find a correlation with a large scatter between the ellipticities of the light and dark matter distributions.
+
+Contrary to earlier approaches, we choose to use a non-parametric modelling technique.
+We use a pixel-based (see e.g.
+\cite{1997MNRAS.292..148S}) lens reconstruction framework called \textit{GLASS} \citep{2012MNRAS.425.3077L}.
+We apply this successfully on a sample of 15 strong gravitational lensing galaxies using stellar mass data of \cite{leier11phd}.
+Thus, we can disentangle dark and luminous matter and look at the shapes and alignments of these distributions.
+We can also look at the ellipticities of the reconstructed lenses and compare them to the ones of the stellar distribution.
+Furthermore, we discuss the environments of these lenses, as they might affect some properties of gravitational lenses in a significant way \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
+We think that we have enough statistics to make claims about misalignments between the dark matter halo and the stellar mass distribution, and how the halo is oriented compared to the environment.
+
+In Section \ref{sec:data} we present the lens sample and important properties of each lens.
+In Section \ref{sec:method} we present the reconstruction method we use and our shape measure.
+Section \ref{sec:results} consists of the results of this analysis.
+We show the relations we find between misalignment, ellipticities, and the environment.
+
+\section{Data}\label{sec:data}
 \begin{itemize}
@@
 
-\begin{table}
+\begin{table*}
  \begin{center}
@@
    B0712 & 0.41 & 1.34 & Quad & B1422 & 0.34 & 3.62 & Quad\\
-   RXJ0911 & 0.77 & 2.80 & Quad & B1608 & 0.63 & 1.39 & Quad\\
-   BRI0952 & 0.63 & 4.50 & Double & MG2016 & 1.01 & 3.27 & Quad$^{1}$\\
-   Q0957 & 0.36 & 1.41 & Double & B2045 & 0.87 & 1.28 & Quad\\
-   LBQS1009 & 0.87 & 2.74 & Double & HE2149 & 0.60 & 2.03 & Double\\
-   B1030 & 0.60 & 1.54 & Double & Q2237 & 0.04 & 1.69 & Quad\\
+   RXJ0911 & 0.77 & 2.80 & Quad & MG2016 & 1.01 & 3.27 & Quad$^{1}$\\
+   BRI0952 & 0.63 & 4.50 & Double & B2045 & 0.87 & 1.28 & Quad\\
+   Q0957 & 0.36 & 1.41 & Double & HE2149 & 0.60 & 2.03 & Double\\
+   LBQS1009 & 0.87 & 2.74 & Double & Q2237 & 0.04 & 1.69 & Quad\\
+   B1030 & 0.60 & 1.54 & Double & & & & \\
 %   SBS1520 & 0.72 & 1.86 & Double
@@
  \end{center}
-\end{table}
+\end{table*}
 
-\begin{table}
+\begin{table*}
  \begin{center}
@@
  \end{center}
-\end{table}
+\end{table*}
 
@@
 
-Our sample consists of 20 galaxies.
-The sample is identical to the one as in \cite{leier11phd} and \cite{2011ApJ...740...97L} except that \textit{HS0818+1227} proved too difficult to reconstruct and therefore was left out.
-Most of the lens galaxies are early-type galaxies, except \textit{B1030+074}, \textit{B1152+200}, \textit{B1600+434}, \textit{B1608+656}, and \textit{Q2237+030}.
+Our sample originally consisted of 21 galaxies.
+The sample is identical to the one as in \cite{leier11phd} and \cite{2011ApJ...740...97L}.
+As the lenses \textit{HS0818+1227}, \textit{SBS1520+530}, \textit{B1600+434}, \textit{B1608+656} proved too difficult to reconstruct, we dropped them from this analysis.
+The final sample consists thus of 17 galaxies.
+Most of these lenses are early-type galaxies except \textit{B1030+074}, \textit{B1152+200}, and \textit{Q2237+030}.
 All lenses can also be found in the gravitational lens database \textit{CASTLES}.
 Characteristics and references of each lens in the sample are listed below.
-Table \ref{tab:overview} contains of all the redshifts and the type of the lenses, Table \ref{tab:environment} lenses with environment information, and Table \ref{tab:timedelays} lenses with measured time delays.
+Table \ref{tab:overview} contains all the redshifts and the type of the lenses, Table \ref{tab:environment} lenses with environment information, and Table \ref{tab:timedelays} lenses with measured time delays.
 
@@
 
-\textit{B1608+656} (hereafter \textit{B1608}) consists of two merging galaxies.
+%\textit{B1608+656} (hereafter \textit{B1608}) consists of two merging galaxies.
 The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
@@
 
-NOTE: Cannot use B1608, but I still left it in the sample as Fei probably will use the lens.
-
-\section{Methods}
+\section{Method}\label{sec:method}
 \subsection{GLASS}
@@
 
-\section{Results}
+We use the new free-form lens modelling framework \textit{GLASS} \citep{2012MNRAS.425.3077L}.
+As its predecessor \textit{PixeLens} \citep{2004AJ....127.2604S}, it generates a pixelated mass map of a lens reproducing the image positions perfectly.
+Using pixels the arrival time surface for a source at position $\boldsymbol\theta_{S}$, taking the geometric and Shapiro contributions into account, can be expressed in terms of the surface mass density $\kappa_{n}$ of the n-th pixel rescaled by the critical density $\Sigma_{crit}$ and the contribution to the gravitational potential by this pixel $\psi_{n}$ \citep{1997MNRAS.292..148S}
+\begin{equation}\label{eq:arrival}
+\tau(\boldsymbol\theta)=\frac{1}{2}|\boldsymbol\theta |^{2}-\boldsymbol\theta\cdot\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\psi_{n}(\boldsymbol\theta).
+\end{equation}
+
+According to Fermat's principle, lensed images appear where the arrival time surface takes on extremal values $\nabla\tau(\boldsymbol\theta)=0$. Thus, the image positions fulfil
+\begin{equation}
+\boldsymbol\theta-\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\alpha_{n}=0,
+\end{equation}
+where $\alpha_{n}$ is the contribution to the bending angle of the n-th pixel.
+For pixels, $\alpha_{n}$ and also $\psi_{n}$ can be described by analytic formulae \citep{1997MNRAS.292..148S}.
+Reconstructing the lens, i.e.
+describing the surface mass density in every pixel, reduces thus to finding sets of coefficients $\left\{\kappa_{n}\right\}$ of these functions.
+As the number of pixels sets the resolution, this problem is however highly underconstrained.
+The number of pixels is typically $\gtrsim100$.
+The solution to this is noticing that the equation is linear in $\kappa_{n}$.
+Additional constraints on the lens such as individual time delays between images and their order and all the priors we impose are also linear.
+The solution space is thus a high-dimensional polytope.
+
+A difficulty in mass modelling is the nonuniqueness of solutions.
+They are not only not unique, every configuration which fulfils the equation is also equally probable.
+Therefore, this polytope needs to be sampled in a uniform way to analyze the full range of solutions.
+has Due to the high dimensionality, sophisticated sampling methods of such volumes are required.
+Here \textit{GLASS} and \textit{PixeLens} differ in the method they use.
+\cite{2008ApJ...679...17C} and \cite{2012MNRAS.425.3077L} show that \textit{PixeLens} does not produce uncorrelated random samples.
+They propose a new sampling algorithm.
+They prove that generic high-dimensional polytopes indeed are sampled in a much more uniform way.
+Models in \textit{GLASS} are generated using a MCMC-method with a Metropolis-Hastings algorithm.
+A new step $x_{i+1}$ of the Markov chain is accepted with the probability
+\begin{equation}
+ \alpha = \mathrm{min}\left(1,\frac{P(x_{i+1})Q(x_{i},x_{i+1})}{P(x_{i})Q(x_{i+1},x_{i})}\right),
+\end{equation}
+where $P(x)$ is the probability distribution samples are drawn from, and $Q(x_{i},x_{i+1})$ is the proposal density.
+It is special in mass modelling that all the valid mass configurations have the same probability, thus $P$ is a constant $\equiv1$.
+For Markov chains $Q$ has to be symmetric.
+It is usually taken to be a multivariate Gaussian $\mathcal{N}(x,\hat{\boldsymbol\Sigma})$, where $\hat{\boldsymbol\Sigma}$ is an estimate of the true covariance matrix $\boldsymbol\Sigma$.
+In principle it could be estimated by an adaptive chain during the random walk, but then the chain is no longer Markovian as it loses the reversibility property.
+Therefore, first an initial adaptive burn-in phase is run to get an good estimate $\hat{\boldsymbol\Sigma}$, before the real MCMC random walk.
+Many models can thus be generated and the solution space sampled.
+The estimation of the covariance matrix is refined in \textit{GLASS} such that models are much less correlated.
+Further details and tests of the method can be found in \cite{2012MNRAS.425.3077L}.
+
+\subsection{Priors and assumptions}
+We use different priors and assumptions to eliminate unphysical mass reconstructions of the lens.
+First of all, the densities $\kappa_{n}$ need to be always positive.
+The density must always increase towards the center, why we chose to require the local density gradient in every pixel except the central one to point within an angle of $50^{\circ}$ towards the center.
+Also, the radial density profile has to decrease monotonically.
+
+To avoid large fluctuations in the density, we choose to add a smoothing prior.
+The density in any pixel except the central one is at most twice the average density of its neighboring pixels.
+If there is reason to expect an invariant distribution under a rotation by $180^{\circ}$ (e.g.
+for doubles), we impose such a symmetry prior.
+
+We also choose to include external shear. Thus, there is an additional term
+\begin{equation}
+  \gamma_{1}\left(\theta_{x}^{2}-\theta_{y}^{2}\right)+2\gamma_{2}\theta_{x}\theta_{y}
+\end{equation}
+in (\ref{eq:arrival}) and the subsequent equations.
+We allow $\gamma_{1}$ and $\gamma_{2}$ to vary, while fixing the maximum absolute value of the shear parameters.
+For doubles we fix the absolute value to be at most $10^{-2}$ (resp.
+$10^{-1}$ if no model could be generated for lower values).
+
+We further assume that we know the positions of the images and the lens perfectly.
+As the range of possible models is much larger than the errors on these quantities \citep{2006ApJ...650L..17S}, this assumption is justified.
+We also fix a time order of the images.
+Furthermore, we chose a flat concordance cosmology with $\Omega_{m}=0.28$, $\Omega_{\Lambda}=0.72$, and $H_{0}^{-1}=13.7$.
+
+\subsection{Shape measure}
+
+To get a rough estimate of the shape of the surface mass distribution we use the inverse of the moment of inertia tensor of the mass map.
+Its eigenvectors and eigenvalues track the shape of the mass distribution.
+There are thus two quantities which define the shape, the ratio of the eigenvalues $\lambda_{1}/\lambda_{2}$, which describes the ellipticity, and the angle of the semi-major axis $\theta$.
+This seemingly crude measure was tested on fake data and found to be working well.
+
+Figure \ref{fig:exampleplots} shows example plots of the reconstruction of the lens \textit{PG1115}.
+They illustrate this shape measure.
+In this case, there is a significant misalignment between the two mass distributions.
+Also the uncertainties on the angle estimate are shown.
+Errors are purely statistical.
+Figure \ref{fig:exampleplots} also shows the arrival time surface and total, dark, and baryonic mass distributions.
+
+\section{Results}\label{sec:results}
 \begin{itemize}
@@
 
-\begin{figure}
- \begin{center}
-  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_a.eps}
-  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_b.eps}
-  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_c.eps}
-  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_d.eps}
-  \hspace{-7mm}\includegraphics[height=0.1\textwidth]{Figures/1115_h.eps}\\
-  \caption{Reconstruction of lens \textit{PG1115}}
+\begin{figure*}
+ \begin{center}%\hspace{-7mm}\hspace{0.8\textwidth}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_a.eps}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_b.eps}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_c.eps}\\
+  \includegraphics[height=0.32\textwidth]{Figures/1115_d.eps}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_h.eps}\\
+  \caption{Reconstruction of lens \textit{PG1115}.
+The plots show the mean model of the generated ensemble of models.
+The coordinate system is centered on the lens galaxy.
+(a) shows the arrival time surface.
+The green dots are the images, the red curves are isochrones, and the black curve are the lemniscate resp.
+the lima\c{c}on.
+(b) shows the total matter distribution.
+The red circle marks the circle of the outermost image.
+The green resp.
+cyan ellipses mark the shape of the dark matter resp.
+stellar distribution.
+This shape is measured as described in Section 3.3.
+In this case, the shape of the total matter distribution (black) is indistinguishable from the dark matter distribution.
+(c) shows the dark matter distribution.
+The black lines show the median semi-major resp.
+semi-minor axis with 1$\sigma$- and 2$\sigma$- uncertainties.
+The solid pink line points to the group centroid with $1\sigma$-uncertainties (dashed).
+(d) shows the luminous matter distribution.}
   \label{fig:1115rec}
  \end{center}
-\end{figure}
+\end{figure*}
+
+\begin{figure*}
+ \begin{center}
+ \includegraphics[height=0.49\textwidth]{Figures/b.eps}
+ \includegraphics[height=0.49\textwidth]{Figures/d.eps}
+ \includegraphics[height=0.49\textwidth]{Figures/e.eps}\\
+ \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
+ \label{fig:moneyplots}
+ \end{center}
+\end{figure*}
 
@@
  \begin{center}
- \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/b.eps}
- \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/d.eps}
- \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/e.eps}
- \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
- \label{fig:moneyplots}
- \end{center}
-\end{figure}
-
-\begin{figure}
- \begin{center}
- \hspace{-7mm}\includegraphics[height=0.29\textwidth]{Figures/g.eps}
+ \includegraphics[height=\linewidth]{Figures/g.eps}
  \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
@@
 
-\section{Conclusion}
+For every lens a total number of 10000 models were generated. This number we've chosen gives reasonable statistics, while not being computationally too expensive.
+
+In general an external shear of $\left|\gamma_{i}\right|\lesssim10^{-1}$ is required to model the lenses.
+\textit{RXJ0911}, \textit{B1608}, and \textit{MG2016} however need a significantly larger external shear of $\left|\gamma_{i}\right|\sim2\cdot10^{-1}$.
+This probably can be attributed to the cluster environment resp.
+the merging process in the system \textit{B1608}, which makes it hard to model.
+Furthermore, an external shear of at most $\left|\gamma_{i}\right|\lesssim10^{-1}$ is needed to be assumed to model \textit{SBS1520}.
+
+The masses $M_{dm}$ and $M_{tot}=M_{dm}+M_{stellar}$ we define in this analysis, are always the mass included up to the radius of the outermost image.
+Our mass modelling shows that \textit{BRI0952} \textit{B1608}, and \textit{Q2237} seem to have a significant amount of the total mass in baryonic mass.
+This can be explained for \textit{Q2237} and \textit{B1608}.
+Due to the galaxy merger, the outermost image for the lens \textit{B1608} includes mainly the central parts of the two galaxies.
+In \textit{Q2237} only the inner parts of the lens, where the baryonic mass dominates, are probed.
+Also the two very massive, very dark matter dominated lenses \textit{Q0957} and \textit{MG2016} should be mentioned.
+\textit{Q0957} is a cD-galaxy and \textit{MG2016} a giant elliptical, so this result was to be expected.
+
+Surprisingly, the shape measure we define yields results that are constrained quite well, as can be seen in Figures \ref{fig:exampleplots}, \ref{fig:47}-\ref{fig:2237}.
+The errors, which are purely statistical, on the ellipticities and the angles of the semi-major axis do not dominate the result.
+Lenses with almost spherical halos, i.e.
+$\lambda_{1}/\lambda_{2}\sim1$, should however be treated with caution.
+
+As mentioned in Section \ref{sec:data}, there are different time delay estimates for \textit{PG1115}.
+We find that the results do not change much when changing the time delays.
+As can be seen in Figure \ref{fig:exampleplots} resp.
+Figure \ref{fig:tsvetkova} and Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
+The misalignment we see is thus not affected by different time delays.
+
+The dark matter distribution in \textit{SBS1520} shows a very interesting behaviour.
+As can be seen in Figure \ref{fig:1520}, the dark matter seems to follow the baryonic mass distribution.
+Further out however, the dark matter distribution is rotated slightly.
+There is a significant misalignment between the dark matter distribution and the baryonic distribution.
+Without the central part, the misalignment would be even larger.
+This behaviour could be due to the potential disc \cite{2008ApJ...673..778A}, or caused by the many structures on the line of sight.
+
+\subsection{Misalignments between stellar and dark matter distributions}
+Figure \ref{fig:misalignment} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
+For lenses with a significant stellar component inside the outermost image radius, the distributions seem to be rather aligned.
+It seems that if the luminous mass is comparable to the dark matter mass, then the distributions align.
+For a smaller stellar contribution this is not necessarily the case.
+The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figures \ref{fig:exampleplots} or \ref{fig:tsvetkova})) and \textit{RXJ0911} (Figure \ref{fig:911}).
+While alignments between the distributions are preferred, they do not seem to be a necessary condition.
+
+The environment might also play a role.
+Red are the systems, which are isolated or no group resp.
+cluster environment has been found, green the ones in such an environment.
+The misaligned systems are mainly the lenses with a known environment.
+Therefore, this misalignment could be caused by the external effects.
+
+\subsection{Ellipticities of stellar and dark matter distributions}
+The ellipticities of the distributions versus the mass ratio are shown in Figure \ref{fig:ellipticities}.
+We see, that every dark matter halo has a lower ellipticity $\lambda_{1}/\lambda_{2}$ and is thus closer to sphericity than the luminous galaxy.
+The systems \textit{HE1104} (Figure \ref{fig:1104}) and \textit{MG2016} (Figure \ref{fig:2016}) show especially large differences.
+It is not clear what could cause these
+
+Figure \ref{fig:misalignmentellipticities} shows the misalignment versus the ellipticity of the dark matter halo.
+There seem to be five different regions.
+Almost spherical halos with good alignment of the semi-major axes, almost spherical halos with good alignment of semi-major and semi-minor axes (maximum misalignment between the semi-major axes), more elliptical, alligned halos, a seemingly 'forbidden' region for misalignments in between, and the upper right triangle, i.e.
+larger ellipticities and misalignments, which also seems forbidden.
+Understanding Figure \ref{fig:misalignmentellipticities} is certainly not trivial.
+Alignment with the semi-minor axis might be a stable configuration for almost spherical halos, while slightly smaller misalignments are unstable.
+There also seem to be some outliers as \textit{PG1115}, \textit{SBS1520}, and \textit{HE2149}.
+
+\subsection{Misalignments between the dark matter distributions and environment}
+Figure \ref{fig:environment} shows the misalignment between the direction to the group or cluster centroid resp.
+the companion galaxy with the dark matter halo.
+Although the error bars are huge, we immediately see that three lenses are basically aligned with the environment.
+The four other systems show slight misalignment.
+Having a closer look at these lenses shows however that at least two of them might in fact be aligned.
+For \textit{RXJ0911} and \textit{HE2149} there are no errors on the estimates of the centroid.
+Otherwise they would probably agree very well.
+\textit{Q0047} does not seem to be aligned with the direction of the group centroid.
+This could be due to the fact that the lens itself is quite far away from the centroid.
+The halo of \textit{B1030} is almost spherical, so the apparent misalignment could maybe be explained.
+It is also the only lens with only one companion galaxy.
+It is possible that in this case the effect of the environment is not strong enough.
+We however certainly lack data to make any claims for the systems with just one companion galaxy.
+Then, there is also \textit{MG2016}, which is not shown here, as the centroid was not measured in this cluster.
+There is however a high galaxy density towards the south-east, where also the cluster centroid probably lies.
+Judging from Figure \ref{fig:2016}, the halo seems to be aligned with the cluster centroid.
+
+We conclude that lenses in groups or cluster are maybe aligned with the centroid.
+However, as we lack the statistics and as the errors on the centroid positions are huge, this claim might be disproved.
+It is not possible at this point to make a similar statement for lenses with just one companion galaxy.
+
+\section{Conclusion}\label{sec:conclusion}
 \begin{itemize}
@@
 
-\section{Acknowledgements}
+We used a nonparametric modelling method to reconstruct a total of 15 lenses.
+Using previously measured light maps, then converted to luminous mass maps \cite{leier11phd}, we were able to isolate the dark matter distribution.
+We used the eigenvalues and eigenvectors of the inverse of the moment of inertia tensor to characterize the shape of the light and mass distributions.
+This allowed us to analyze the alignment between these distributions and the relation between the ellipticities.
+Furthermore, we included environment information, which we related the to the misalignment.
+
+Our results can be summarized in the following way.
+If lenses lie in dense environments, mass and light need not be aligned.
+This might also be the case for lenses without known environments.
+We found more scatter than previous analyses by \cite{1997ApJ...482..604K}, \cite{2006ApJ...649..599K}, \cite{2009ApJ...690..670T}, and \cite{2012ApJ...761..170G} which all used SIEs mostly neglecting external shear to model the lenses.
+We also found that the semi-major and semi-minor axes of the distributions can be aligned, if the dark matter halos are close to sphericity.
+Up to our knowledge, this result was not obtained in other analyses.
+
+We found that dark matter halos are rounder than the luminous galaxies, i.e.
+they have a lower eigenvalue ratio $\lambda_{1}/\lambda_{2}$.
+Previous analyses found a correlation between the ellipticities \citep{2009ApJ...690..670T,2012ApJ...761..170G}, which we do not see.
+They also found a couple of cases, where the stellar distribution is more spherical than the dark matter halo.
+We claim that certain combinations of ellipticity of the dark matter halo and misalignment between light and mass seem to be forbidden.
+However, more lens systems are needed to support this claim.
+
+We suspect that the dark matter halo might be aligned with the centroid of the group or cluster it lies in.
+Due to the large uncertainties in the centroid positions however, such alignments might as well be coincidences.
+
+We want to stress again that the systems \textit{SBS1520} and \textit{PG1115}, which both show some misalignment and have time delay measurements, seem interesting enough to investigate further.
+In \textit{SBS1520} we found that the outer parts of the dark matter distribution is rotated respective to the central, which displays an interesting feature possibly due a disc.
+It is on the other hand a very complicated system with a lot of structures along the line of sight.
+\textit{PG1115} is easy to model, but still shows a clear misalignment.
+Thus, it could serve as a test for other methods that try to reproduce these misalignments.
+
+\section{Acknowledgements}\label{sec:acknowledgements}
 Acknowledge Dominik Leier...
+
 JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
@@
 \bibliographystyle{mn2e}
-\bibliography{paper.bib}
+\bibliography{paper}
+
+%\clearpage
+\appendix
+\section{Reconstructed Lenses}\label{sec:reconstructions}
+
+\begin{table*}
+ \begin{center}
+  \begin{tabular}{l c c c c l l}
+   Lens & A & B & C & D & Symmetry & Point Masses\\ \hline \hline
+   Q0047 & 1.083 & 1.083 & 1.083 & 1.083 & Yes & $-\Delta\alpha = 2.301$ , $-\Delta\delta = 2.301$ , Mass range: $10^{7}-10^{9} \mathrm{M_{Sun}}$\\
+   Q0142 & & & & & & \\
+   MG0414 & & & & & & \\
+   B0712 & & & & & & \\
+   RXJ0911 & & & & & & \\
+   BRI0952 & & & & & & \\
+   Q0957 & & & & & & \\
+   LBQS1009 & & & & & & \\
+   B1030 & & & & & & \\
+   HE1104 & & & & & & \\
+   PG1115 & & & & & \\
+   B1152 & & & & & \\
+   B1422 & & & & & \\
+   B1608 & & & & & \\
+   MG2016 & & & & & \\
+   B2045 & & & & & \\
+   HE2149 & & & & & \\
+   Q2237 & & & & & \\
+  \end{tabular}
+  \caption{...}
+  \label{tab:lensparameters}
+ \end{center}
+\end{table*}
 

### 2013-05-13 shapes/paper.tex
update on paper

@@
 %
-% --- Keywords ---
-% - Add keaywords
+% --- General ---
+% - Add keywords
+% - Check universities' names
+% - Correct typos and reformulate some paragraphs
+% - ...
+%
 %
@@
 $^{3}$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
-$^{4}$Somewhere in France, France
+$^{4}$Department of Biology and Health, Versailles Saint-Quentin-en-Yvelines University, France
 }
@@
 
-\subsection{Context/Background/Motivation}
+\textbf{Context/Background/Motivation}
 \begin{itemize}
@@
 
-\subsection{Anything done before?}
+\textbf{Anything done before?}
 \begin{itemize}
@@
 
-\subsection{New here}
+\textbf{New here}
 \begin{itemize}
@@
   \end{tabular}
+  %$^{d}$ Only number-weighted estimates are available. \newline 
   \caption{List of lenses lying in a group or cluster environment, or that have a companion.
@@
 \newline $^{c}$ References for the centroid estimates we used.
-\newline $^{d}$ Only number-weighted estimates are available.
 \newline 1: \cite{2011ApJ...726...84W}; 2: \cite{1993AJ....105....1S}; 3: \cite{2002AJ....123..627F}; 4: \cite{2001ApJ...555....1M}; 5: \cite{1998ApJ...504..661C}; 6: \cite{2000ApJ...536..584L}; 7: \cite{2008ApJ...673..778A}; 8: \cite{2007AJ....134..668A}; 9: \cite{2003MNRAS.344..337T}; 10: \cite{2006ApJ...646...85W}; 11: \cite{2006ApJ...646...85W}}
@@
 
-Our sample originally consisted of 21 galaxies.
-The sample is identical to the one as in \cite{leier11phd} and \cite{2011ApJ...740...97L}.
+Our sample originally consisted of 21 galaxies, identical to the one in \cite{leier11phd} and \cite{2011ApJ...740...97L}.
 As the lenses \textit{HS0818+1227}, \textit{SBS1520+530}, \textit{B1600+434}, \textit{B1608+656} proved too difficult to reconstruct, we dropped them from this analysis.
@@
 \textit{RXJ0911+0551} (hereafter \textit{RXJ0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}.
-It has measured time delays \citep{2002ApJ...572L..11H}.
-It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
-This cluster seems to be rather complex and especially it is not spherical.
+It has measured time delays \citep{2002ApJ...572L..11H} and lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
+This cluster seems to be rather complex.
 Possibly it is not dynamically relaxed, although X-ray emission can be detected.
@@
 These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
-The lens has a measured time delay, e.g.
-\citep{2012A&A...540A.132S}.
+The lens has a measured time delay (e.g.
+\cite{2012A&A...540A.132S}).
 They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level.
@@
 
-\textit{HE1104-1805} (hereafter \textit{HE1104}) is probably an early-type galaxy \citep{2000ApJ...536..584L,2000A&A...360..853C}.
-It has measured time delays \citep{2008ApJ...676...80M}.
+\textit{HE1104-1805} (hereafter \textit{HE1104}) is probably an early-type galaxy \citep{2000ApJ...536..584L,2000A&A...360..853C} and has measured time delays \citep{2008ApJ...676...80M}.
 \cite{2000ApJ...536..584L} also seem to find a group environment.
@@
 \cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies.
-Using newer data, \cite{2011ApJ...726...84W} find an additional member.
+Using newer data \cite{2011ApJ...726...84W} find an additional member.
 \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
@@
 It is the farthest lens we consider in this sample.
-It lies in a cluster which consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
+It lies in a cluster which consists of 69 probable member galaxies \citep{2003MNRAS.344..337T}.
 The clusters shows a high density of galaxies close to the lens in a south-east direction.
@@
 
-\textit{HE2149-2745} (hereafter \textit{HE2149}) is an early-type galaxy \citep{2007A&A...465...51E}.
-It has a measured time delay \citep{2002A&A...383...71B}.
+\textit{HE2149-2745} (hereafter \textit{HE2149}) is an early-type galaxy \citep{2007A&A...465...51E} and has a measured time delay \citep{2002A&A...383...71B}.
 There is some uncertainty in estimating the lens' redshift.
-Initial estimates by \cite{1996A&A...315L.405W,2000ApJ...543..131K} found a probable redshift range of $\sim0.2-0.5$.
+Initial estimates by \cite{1996A&A...315L.405W} and \cite{2000ApJ...543..131K} found a probable redshift range of $\sim0.2-0.5$.
 By cross-correlating the lens spectrum with a template spectrum of an elliptical galaxy, \cite{2002A&A...383...71B} find that the redshift probably lies in the range $0.49\leq z \leq 0.60$, with the most likely redshift $z=0.495\pm0.01$.
@@
 \textit{Q2237+030} (hereafter \textit{Q2237} or \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
-With only a redshift of $z=0.04$, it is the closest lens of the sample.
+With only a redshift of $z=0.04$ it is the closest lens of the sample.
 Due to the low redshift, the probed physical scales are quite small.

### 2013-05-14 shapes/paper.tex
paper update

@@
 % - More detailed description how the baryionic mass distribution was measured
+% - More details needed on galaxies in the sample? I don't think so though
 % - ...
@@
 % - Plot showing how well the shape informations is recovered when applied to fake data
+% - Citation on why not monotonically decreasing radial density profiles are instable
+% - Generally look through method part
 % - ...
@@
 \section{Method}\label{sec:method}
-\subsection{GLASS}
+\textbf{GLASS}
 \begin{itemize}
@@
 \begin{itemize}
-\item Explain what priors were chosen to model the lenses
+\item Explain what priors were chosen to model the lenses (Basically always pixrad 12, shear left free for quads, shear limited for doubles to 0.01, local gradient 50 degrees, smoothening prior 2, time delays if known.
+Exceptions are few.
+For some quads symmetry prior, for one double 0.01 was not possible therefore chose 0.1.)
 \end{itemize}
 
-Basically always pixrad 12, shear left free for quads, shear limited for doubles to 0.01, local gradient 50 degrees, smoothening prior 2, time delays if known.
-Exceptions are few.
-For some quads symmetry prior, for one double 0.01 was not possible therefore chose 0.1.
-
-\subsection{Shape measure}
+\textbf{Shape measure}
 \begin{itemize}
@@
 
-We use the new free-form lens modelling framework \textit{GLASS} \citep{2012MNRAS.425.3077L}.
+In this work we use the new free-form lens modelling framework \textit{GLASS} \citep{2012MNRAS.425.3077L}.
 As its predecessor \textit{PixeLens} \citep{2004AJ....127.2604S}, it generates a pixelated mass map of a lens reproducing the image positions perfectly.
-Using pixels the arrival time surface for a source at position $\boldsymbol\theta_{S}$, taking the geometric and Shapiro contributions into account, can be expressed in terms of the surface mass density $\kappa_{n}$ of the n-th pixel rescaled by the critical density $\Sigma_{crit}$ and the contribution to the gravitational potential by this pixel $\psi_{n}$ \citep{1997MNRAS.292..148S}
+Using pixels the arrival time surface for a source at position $\boldsymbol\theta_{S}$, taking the geometric and Shapiro contributions to the time delay into account, can be expressed in terms of the surface mass density rescaled by the critical density $\Sigma_{crit}$ of the n-th pixel $\kappa_{n}$ and the contribution to the gravitational potential of this pixel $\psi_{n}$ \citep{1997MNRAS.292..148S}
 \begin{equation}\label{eq:arrival}
@@
 where $\alpha_{n}$ is the contribution to the bending angle of the n-th pixel.
-For pixels, $\alpha_{n}$ and also $\psi_{n}$ can be described by analytic formulae \citep{1997MNRAS.292..148S}.
+For pixels, $\alpha_{n}$ and $\psi_{n}$ can be described by analytic formulae \citep{1997MNRAS.292..148S}.
 Reconstructing the lens, i.e.
 describing the surface mass density in every pixel, reduces thus to finding sets of coefficients $\left\{\kappa_{n}\right\}$ of these functions.
-As the number of pixels sets the resolution, this problem is however highly underconstrained.
-The number of pixels is typically $\gtrsim100$.
-The solution to this is noticing that the equation is linear in $\kappa_{n}$.
-Additional constraints on the lens such as individual time delays between images and their order and all the priors we impose are also linear.
-The solution space is thus a high-dimensional polytope.
+As the number of pixels, which sets the resolution, is by far larger than the number of constraint equations in free-form modelling, this problem is highly underconstrained.
+The number of pixels is typically $\gtrsim 100$.
+We note that the equation is linear in $\kappa_{n}$.
+Also additional constraints on the lens such as individual time delays between images and their order and other priors we impose are linear.
+The volume of allowed solution is thus a high-dimensional polytope.
 
-A difficulty in mass modelling is the nonuniqueness of solutions.
+A fundamental difficulty in mass modelling is the non-uniqueness of solutions.
 They are not only not unique, every configuration which fulfils the equation is also equally probable.
 Therefore, this polytope needs to be sampled in a uniform way to analyze the full range of solutions.
-has Due to the high dimensionality, sophisticated sampling methods of such volumes are required.
-Here \textit{GLASS} and \textit{PixeLens} differ in the method they use.
+Due to the high dimensionality, sophisticated sampling methods of such volumes are required.
+\textit{GLASS} and \textit{PixeLens} differ in the method they use to sample such spaces.
 \cite{2008ApJ...679...17C} and \cite{2012MNRAS.425.3077L} show that \textit{PixeLens} does not produce uncorrelated random samples.
-They propose a new sampling algorithm.
+They propose therefore a new sampling algorithm.
 They prove that generic high-dimensional polytopes indeed are sampled in a much more uniform way.
@@
 \end{equation}
-where $P(x)$ is the probability distribution samples are drawn from, and $Q(x_{i},x_{i+1})$ is the proposal density.
-It is special in mass modelling that all the valid mass configurations have the same probability, thus $P$ is a constant $\equiv1$.
-For Markov chains $Q$ has to be symmetric.
+where $P(x)$ is the probability distribution samples are drawn from and $Q(x_{i},x_{i+1})$ is the proposal density.
+As mentioned, all the valid mass configurations have the same probability, thus $P$ is a constant $\equiv1$.
+$Q$ has to be symmetric for Markov chains.
 It is usually taken to be a multivariate Gaussian $\mathcal{N}(x,\hat{\boldsymbol\Sigma})$, where $\hat{\boldsymbol\Sigma}$ is an estimate of the true covariance matrix $\boldsymbol\Sigma$.
@@
 Therefore, first an initial adaptive burn-in phase is run to get an good estimate $\hat{\boldsymbol\Sigma}$, before the real MCMC random walk.
-Many models can thus be generated and the solution space sampled.
+In this way, a large ensemble of models can be generated.
 The estimation of the covariance matrix is refined in \textit{GLASS} such that models are much less correlated.
@@
 
-\subsection{Priors and assumptions}
+\textbf{Priors and assumptions}
 We use different priors and assumptions to eliminate unphysical mass reconstructions of the lens.
-First of all, the densities $\kappa_{n}$ need to be always positive.
-The density must always increase towards the center, why we chose to require the local density gradient in every pixel except the central one to point within an angle of $50^{\circ}$ towards the center.
-Also, the radial density profile has to decrease monotonically.
+First of all, the densities $\kappa_{n}$ need to be positive.
+As mass distributions with positive radial gradients are instable (CITATION NEEDED!), the density must always increase towards the center.
+Therefore, we require the local density gradient in every pixel except the central one to point towards the center within an angle of $50^{\circ}$.
+The radial density profile decreases monotonically, as required.
 
@@
 
-We also choose to include external shear. Thus, there is an additional term
+We also choose to include an additional external shear
 \begin{equation}
-  \gamma_{1}\left(\theta_{x}^{2}-\theta_{y}^{2}\right)+2\gamma_{2}\theta_{x}\theta_{y}
+  \gamma_{1}\left(\theta_{x}^{2}-\theta_{y}^{2}\right)+2\gamma_{2}\theta_{x}\theta_{y},
 \end{equation}
-in (\ref{eq:arrival}) and the subsequent equations.
-We allow $\gamma_{1}$ and $\gamma_{2}$ to vary, while fixing the maximum absolute value of the shear parameters.
+which is added to (\ref{eq:arrival}) and the subsequent equations.
+We allow $\gamma_{1}$ and $\gamma_{2}$ to vary while fixing the maximum absolute value of the shear parameters.
 For doubles we fix the absolute value to be at most $10^{-2}$ (resp.
-$10^{-1}$ if no model could be generated for lower values).
+$10^{-1}$ if no model could be generated for lower values ---> find out which galaxy and write this in more detail).
 
-We further assume that we know the positions of the images and the lens perfectly.
-As the range of possible models is much larger than the errors on these quantities \citep{2006ApJ...650L..17S}, this assumption is justified.
+We further assume that the lens and image positions are perfectly known.
+As the range of possible models is much larger than the errors on these quantities, this assumption is justified \citep{2006ApJ...650L..17S}.
 We also fix a time order of the images.
-Furthermore, we chose a flat concordance cosmology with $\Omega_{m}=0.28$, $\Omega_{\Lambda}=0.72$, and $H_{0}^{-1}=13.7$.
+Furthermore, we choose a flat concordance cosmology with $\Omega_{m}=0.28$, $\Omega_{\Lambda}=0.72$, and $H_{0}^{-1}=13.7$.
 
-\subsection{Shape measure}
+\textbf{Shape measure}
 
@@
 Its eigenvectors and eigenvalues track the shape of the mass distribution.
-There are thus two quantities which define the shape, the ratio of the eigenvalues $\lambda_{1}/\lambda_{2}$, which describes the ellipticity, and the angle of the semi-major axis $\theta$.
+Thus, the shape is defined by two quantities; the ratio of the eigenvalues $\lambda_{1}/\lambda_{2}$, which describes the ellipticity, and the angle of the semi-major axis $\theta$.
 This seemingly crude measure was tested on fake data and found to be working well.
+(INPUT HERE FAKE DATA TEST)
 
-Figure \ref{fig:exampleplots} shows example plots of the reconstruction of the lens \textit{PG1115}.
-They illustrate this shape measure.
-In this case, there is a significant misalignment between the two mass distributions.
-Also the uncertainties on the angle estimate are shown.
-Errors are purely statistical.
-Figure \ref{fig:exampleplots} also shows the arrival time surface and total, dark, and baryonic mass distributions.
+Figure \ref{fig:1115rec} shows example plots of the reconstruction of the lens \textit{PG1115} illustrating this shape measure.
+In this lens system, there is a significant misalignment between the two mass distributions.
+1$\sigma$- and 2$\sigma$-uncertainties on the angle estimates are shown.
+These errors are purely statistical, estimated by the ensemble of models.
+Figure \ref{fig:1115rec} also shows the arrival time surface and total, dark, and baryonic mass distributions.
 
@@
 
-Surprisingly, the shape measure we define yields results that are constrained quite well, as can be seen in Figures \ref{fig:exampleplots}, \ref{fig:47}-\ref{fig:2237}.
+Surprisingly, the shape measure we define yields results that are constrained quite well, as can be seen in Figures \ref{fig:1115rec}, \ref{fig:47}-\ref{fig:2237}.
 The errors, which are purely statistical, on the ellipticities and the angles of the semi-major axis do not dominate the result.
@@
 We find that the results do not change much when changing the time delays.
-As can be seen in Figure \ref{fig:exampleplots} resp.
+As can be seen in Figure \ref{fig:1115rec} resp.
 Figure \ref{fig:tsvetkova} and Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
@@
 For a smaller stellar contribution this is not necessarily the case.
-The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figures \ref{fig:exampleplots} or \ref{fig:tsvetkova})) and \textit{RXJ0911} (Figure \ref{fig:911}).
+The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figures \ref{fig:1115rec} or \ref{fig:tsvetkova})) and \textit{RXJ0911} (Figure \ref{fig:911}).
 While alignments between the distributions are preferred, they do not seem to be a necessary condition.

### 2013-05-21 shapes/paper.tex
update on shapes paper

@@
  \begin{center}
-  \begin{tabular}{l c c l | l c c l}
+  \begin{tabular}{l c c l || l c c l}
    Lens & $z_{L}$ & $z_{S}$ & Type & Lens & $z_{L}$ & $z_{S}$ & Type\\ \hline \hline
@@
 \begin{figure*}
+ \begin{center}%\hspace{-7mm}\hspace{0.8\textwidth}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_a.eps}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_b.eps}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_c.eps}\\
+  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_d.eps}
+  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_h.eps}\\
+  \caption{Same as Figure \ref{fig:1115rec} but using time delay estimates from \cite{1997ApJ...489...21B}.}
+  \label{fig:barkana}
+ \end{center}
+\end{figure*}
+
+\begin{figure*}
  \begin{center}
@@
  \includegraphics[height=0.49\textwidth]{Figures/e.eps}\\
- \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
+ \caption{Plots of stellar and dark matter misalignments, ellipticities of the baryonic mass and dark matter distribution and a plot showing the ellipticity of the dark matter halo against the misalignment.
+Red symbols mark isolated objects or such without environment information, green symbols mark objects with at least one companion galaxy.
+In the second plot, stars denote the ellipticitie of the baryonic mass distribution, squares the ones of the dark matter halo.}
  \label{fig:moneyplots}
@@
  \includegraphics[height=\linewidth]{Figures/g.eps}
- \caption{Plots of stellar and dark matter misalignments, ellipticities and composed plot.}
+ \caption{Misalignment of the dark matter halo and the direction of the centroid of the environment.}
  \label{fig:environmentmisalign}
@@
 
-For every lens a total number of 10000 models were generated. This number we've chosen gives reasonable statistics, while not being computationally too expensive.
+For every lens 10000 models were generated.
+This number allows for reasonable statistics, while not being computationally too expensive.
+In general an external shear of $\left|\gamma_{i}\right| \lesssim 10^{-1}$ is required to model quads.
+\textit{RXJ0911} and \textit{MG2016} however, need a significantly larger external shear of $\left|\gamma_{i}\right|\sim2\cdot10^{-1}$.
+This probably can be attributed to the cluster environments.
+As mentioned, the shear was limited to be $\left|\gamma_{i}\right| < 10^{-1}$ for doubles.
+The masses $M_{dm}$ and $M_{tot}=M_{dm}+M_{stellar}$ are always the masses included up to the radius of the outermost image.
 
-In general an external shear of $\left|\gamma_{i}\right|\lesssim10^{-1}$ is required to model the lenses.
-\textit{RXJ0911}, \textit{B1608}, and \textit{MG2016} however need a significantly larger external shear of $\left|\gamma_{i}\right|\sim2\cdot10^{-1}$.
-This probably can be attributed to the cluster environment resp.
-the merging process in the system \textit{B1608}, which makes it hard to model.
-Furthermore, an external shear of at most $\left|\gamma_{i}\right|\lesssim10^{-1}$ is needed to be assumed to model \textit{SBS1520}.
-
-The masses $M_{dm}$ and $M_{tot}=M_{dm}+M_{stellar}$ we define in this analysis, are always the mass included up to the radius of the outermost image.
-Our mass modelling shows that \textit{BRI0952} \textit{B1608}, and \textit{Q2237} seem to have a significant amount of the total mass in baryonic mass.
-This can be explained for \textit{Q2237} and \textit{B1608}.
-Due to the galaxy merger, the outermost image for the lens \textit{B1608} includes mainly the central parts of the two galaxies.
-In \textit{Q2237} only the inner parts of the lens, where the baryonic mass dominates, are probed.
+%Our mass modelling shows that \textit{BRI0952} and \textit{Q2237} seem to have a rather large amount of mass in baryonic mass (e.g.
+Figure \ref{fig:moneyplots}).
 Also the two very massive, very dark matter dominated lenses \textit{Q0957} and \textit{MG2016} should be mentioned.
 \textit{Q0957} is a cD-galaxy and \textit{MG2016} a giant elliptical, so this result was to be expected.
+%This can be explained for \textit{Q2237}. In \textit{Q2237} only the inner parts of the lens, where the baryonic mass dominates, are probed.
 
-Surprisingly, the shape measure we define yields results that are constrained quite well, as can be seen in Figures \ref{fig:1115rec}, \ref{fig:47}-\ref{fig:2237}.
+Surprisingly, the shape measure we define yields are well-constrained results, as can be seen in Figures \ref{fig:1115rec} and \ref{fig:moneyplots}.
 The errors, which are purely statistical, on the ellipticities and the angles of the semi-major axis do not dominate the result.
@@
 As mentioned in Section \ref{sec:data}, there are different time delay estimates for \textit{PG1115}.
-We find that the results do not change much when changing the time delays.
+We find that the results do not change much when using different estimates.
 As can be seen in Figure \ref{fig:1115rec} resp.
-Figure \ref{fig:tsvetkova} and Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
+Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
 The misalignment we see is thus not affected by different time delays.
 
-The dark matter distribution in \textit{SBS1520} shows a very interesting behaviour.
+% The dark matter distribution in \textit{SBS1520} shows a very interesting behaviour.
 As can be seen in Figure \ref{fig:1520}, the dark matter seems to follow the baryonic mass distribution.
@@
 
-\subsection{Misalignments between stellar and dark matter distributions}
+\textbf{Misalignments between stellar and dark matter distributions}
 Figure \ref{fig:misalignment} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
@@
 
-\subsection{Ellipticities of stellar and dark matter distributions}
+\textbf{Ellipticities of stellar and dark matter distributions}
 The ellipticities of the distributions versus the mass ratio are shown in Figure \ref{fig:ellipticities}.
@@
 
-\subsection{Misalignments between the dark matter distributions and environment}
+\textbf{Misalignments between the dark matter distributions and environment}
 Figure \ref{fig:environment} shows the misalignment between the direction to the group or cluster centroid resp.

### 2013-05-27 limits/ms.tex
New plots of sigma/beta and sample reconstruction. Beginnings of stellar mass and vel disp sections.

@@
 \documentclass[onecolumn,galley]{mn2e}
+%\documentclass[twocolumn,galley]{mn2e}
 %\documentclass[onecolumn,galley,draft]{mn2e}
@@
 distribution is more difficult to determine, however, as there are typically
-not enough constraints of the mass profile. The known degeneracies have been
+not enough constraints on the mass profile. The known degeneracies have been
 discussed at length in the literature. At the very least, one would like to
-have a measure of the enclosed mass at at least two distinct radii to be able
-to distinguish between analytic mass models. This would break the steepness
-degeneracy, also known as the mass sheet degeneracy.
+have a measure of the enclosed mass at two distinct radii to be able
+to properly distinguish between analytic mass models. 
+%This would break the steepness degeneracy, also known as the mass sheet degeneracy.
 
-Other than using the Einstein radius, the enclosed mass can be estimated
-from stellar velocity dispersions. If the radius from this measurement
-is sufficiently different from the Einstein radius, then this provides the
-necessary data. Another solution, is to find a galaxy that is lensing two
-sources. The images from each source would provide an enclosed mass. The
-extent to which the radii differ is dependent upon the redshifts of the
-two sources: the larger the difference the larger the difference in radii.
+Lensing is not the only technique that can measure enclosed mass. The enclosed
+mass can also be estimated from stellar velocity dispersions. If the radius
+from this measurement is sufficiently different from the Einstein radius, then
+combining this measurement with lensing provides the necessary constraint.
+Another solution is to find a galaxy that is lensing two sources. The images
+from each source provide an enclosed mass. The extent to which the radii
+differ is dependent upon the redshifts of the two sources: the larger the
+redshift difference the larger the radial separation.
 
-If one assumes knowledge of the Hubble constant $H_0$ and time delays have been
-observed for a lens. In principle, this determines that mass, but in practice
-this can only place strong constraints on the mass distribution, as it does not
-solve the problem that the exact distribution is highly degenerate. One can
-choose to postpone this problem and simply fit models to the given data.  The
-earliest examples were singular isothermal sphere (SIS) or elliptical (SIE)
-models but have since evolved to multi-component models include separate models
-for the stars and dark matter. Other methods that do not ignore this problem
-use genetic algorithms or linear programming to explore the large space of
-solutions.
+Lensing is known to be sensitive to cosmology and, in principle, can be used to
+estimate such quantities as the Hubble constant $H_0$ when the lens has
+measurable time delays. However, due to strong degeneracies such as the
+steepness degeneracy there is often little one can learn from a single lens. 
+In this case, one is free to change the mass and $H_0$ while keeping
+all observables fixed. A single lens can say almost nothing about the actual
+value of $H_0$. However, it has been shown that combining modeling results
+of several strong lenses with time delays can significantly reduce the allowed
+values and provides a measure to within 10 percent \cite{}.
 
-Worse, though, is when only time delays are known and $H_0$ is to be inferred.
-In this case, one is again free to change the mass and $H_0$ while keeping
-all observables fixed. A single lens can say almost nothing about the actual
-value of $H_0$. However, it has been shown that combining the modeling results
-of several strong lenses with time delays can significantly reduce the allowed
-values and provides a measure to within 10 percent.
+If one assumes a Hubble constant $H_0$ and time delays have been observed for a
+lens this will break the steepness degeneracy but will not help in
+constraining the mass profile at two radii.  One can choose to postpone this
+problem and simply fit models to the given data.  The earliest examples were
+singular isothermal sphere (SIS) or elliptical (SIE) models but have since
+evolved to multi-component models include separate models for the stars and
+dark matter. Other methods that do not ignore this problem use genetic
+algorithms or linear programming to explore the large space of solutions.
 
-Despite these difficulties lensing is a direct probe of the gravitating
-mass in a halo and there are a number of open problems in galaxy formation
-that lensing can help address. For instance, the debate remains as to what
-form the inner slope of the density profile takes. Numerical simulations of
-dark matter suggest a cusp, while observations from lensing and stellar dynamics
-suggest cores. This may, however, be only a matter of scale, as both theory
-and observations agree that clusters have cuspy profiles.
+Despite such difficulties lensing is a direct probe of the gravitating mass in
+a halo and there are a number of open problems in galaxy formation that lensing
+can help address. For instance, the debate remains as to what form the inner
+slope of the density profile takes. Numerical simulations of dark matter
+suggest a cusp, while observations from lensing and stellar dynamics suggest
+cores. This may, however, be only a matter of scale, as both theory and
+observations agree that clusters have cuspy profiles.
 
@@
   \item Point or extended mass objects can be placed in the field.
+  \item Additional levels of pixel refinement.
 \end{enumerate}
-In our tests we will take advantage of each of these new features.  At its
-heart lies a new algorithm for sampling high dimensional linear spaces that is
-used to generate lensing models. This algorithm was described and tested in
-\cite{}. \Glass\ is also multi-threaded allowing it to run efficiently on
-many-cored machines.  The software is freely available for download. One
-interesting aspect is that the input files are themselves Python programs. This
-allows a large amount of sophistication in setting up a lens at runtime and
-also allows \Glass\ to be used as an external library from another user written
-program.
+At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
+linear space that represents the modeling solution space. This algorithm was
+described and tested in \cite{}. \Glass\ is also multi-threaded allowing it to
+run efficiently on many-cored machines.  The software is freely available for
+download. One interesting aspect is that the input files are themselves Python
+programs. This allows a large amount of sophistication in setting up a lens at
+runtime and also allows \Glass\ to be used as an external library from another
+user written program.
 
@@
 For this paper we will restrict ourselves to using the pixelated basis set that
-has been employed in previous work and is implemented in \PixeLens. Here we will
-briefly review the main ideas. The algorithm for generating models in \Glass\
-samples a convex polytope in a high dimensional space whose interior points are
-solutions to the lensing equation and satisfy other physically motivated linear
-priors. We must therefore formulate all of our equations as equations linear in the
-unknowns. We describe the density distribution
-$\kappa$ as a set of discrete grid cells or pixels $\kappa_i$.
-In this way, we rewrite the potential (\eqnref{lensing potential}) as
+has been employed in previous work and is implemented in \PixeLens. Here we
+will briefly review the main ideas. The algorithm for generating models in
+\Glass\ samples a convex polytope in a high dimensional space whose interior
+points are solutions to the lensing equation and satisfy other physically
+motivated linear priors (the sampling algorithm in \Glass\ is not the same as
+employed in \PixeLens).  We therefore formulate all of our equations as
+equations linear in the unknowns. We describe the density distribution $\kappa$
+as a set of discrete grid cells or pixels $\kappa_i$ and rewrite the potential
+(\eqnref{lensing potential}) as
 %
@@
 The pixels only cover a finite circular area with physical radius $\Rmap$ and
-pixel radius $\Rpix$. To account for any global shearing outside this region
-from, e.g., a neighboring galaxy, we also add two shearing terms
+pixel radius $\Rpix$ centered on the lensing galaxy. To account for any global
+shearing outside this region from, e.g., a neighboring galaxy, we also add to
+\eqnref{discrete potential} two shearing terms
 %
@@
 
-Unfortunately, the lens equation and the arrival times are not enough to form a
+Unfortunately, the lens equation and the arrival times alone are not enough to form a
 closed volume in the solution space. We have not imposed any strong constraints
 on the density even so much as to ensure that it is non-negative everywhere. We
-must therefore provide additonal linear constraints so that we generate
+must therefore provide additonal linear constraints so that we only sample
 physical models. The explicit implementation for these priors has been
-explained in \cite{}. In summary, we require that
+explained in \cite{}, be can be summarized as
 \begin{enumerate}
@@
 image position error is below the equivalent observational error. Time delays
-are the calculated in order from the arrival time at each image (\eqnref{tau}).
+are then calculated in order from the arrival time at each image (\eqnref{tau}).
 
@@
 The four mock galaxies we consider have been designed to test our recovery
-procedure on galaxies that have steep and shallow dark matter and stellar
-profiles. The enclosed mass in all cases is fixed at $M(a_\star)= 0.18\e{11}$
-at the scale radius $a_\star=2$ kpc. These values were chosen to closely
-resemble B1115. We therefore place the galaxy at a redshift of $z_L = 0.31$.
-Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
-and $\Omega_\Lambda=0.72$. The critical density is $\kappa_\mathrm{crit}\sim
-1.8\e{9}$\Msun/kpc$^2$.
+procedure. They are two component models where the dark matter and stellar
+profiles are allowed to be steep and shallow.  The enclosed mass in all cases
+is fixed at $M(a_\star)= 1.8\e{10}$ at the scale radius $a_\star=2$ kpc. These
+values were chosen to closely resemble B1115. We therefore place the galaxy at
+a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
+where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
+critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
 
-The models were
+The galaxies were
 first generated as three dimensional particle distributions with the
-tool DEHNEN, where each component follows the profile
+tool DEHNEN-TOOL. Each component follows the profile
 \begin{equation}
@@
 \end{equation}
-and where $\gamma$ is the profile index and $a$ is the scale radius. The
-four combinations of profile indices are shown in \tabref{Lens profile params}.
+where $\gamma$ is the profile index and $a$ is the scale radius.  In the
+case $\gamma=1$ this is the Hernquist profile.  The four combinations of
+profile indices are shown in \tabref{Lens profile params}.  Note that two of
+the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
+more accurate approximation would be an NFW or Einasto profile we are not
+probing the outer regions of the halo where the difference would be most
+extreme.  The Hernquist profile is easier to generate as it has finite mass.
 
@@
 \begin{tabular}{cllllllll}
-Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & Notes\\
+Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ & Notes\\
 \hline
-AA & 1 & 4 & 0.05 & $11^{2.95}$ & \\
-AC & 1 & 4 & 1 & $11^2$ & \\
-BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & \\
-BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 
+AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & \\
+AC & 1 & 4 & 1 & $11^2$ & 50 kpc & \\
+BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc & \\
+BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & 
 \end{tabular}
 \caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
-\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
+\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
 all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
@@
 \begin{enumerate}
-\item Two double imaged systems with a single point source.
-\item Two quadruply imaged systems with a small and large annulus.
-\item Two quadruply imaged systems with a single point source.
-\item One extended source. 
-\item A two-source quad system with one source varying across five redshifts. 
+\item One double and one extended double.
+\item One quad and one extended quad.
+\item Three 2-source quads with varying redshift contrast.
 \end{enumerate}
 
+The extended configurations use extra sources to generate extra images that
+simulate an arc. \figref{config ex.} shows the configuration for the extended
+quad.
+
 Each of these configurations were modeled with and without time delays and with
-and without a central image. We assumed for all tests that the lensing mass was
-symmetric.
+and without a central image. We assumed for all our tests that the lensing mass
+was radially symmetric. By construction, this is known to be true and this is
+most often the case with real galaxies, unless there is an obvious observed
+asymmetry. The central pixel was refined into a further nine pixels to capture
+any steep rise in the profile. Two of the four mock galaxies have a steeply rising
+inner profile.
+
+\figref{reconstruction} shows a typical reconstruction of a
+lens. The far left plot shows the ensemble average arrival time surface with
+image marked as circles and the inferred source position as a diamond. The
+center plot shows the radial density profile. The error bars cover the full
+range of models generated by \Glass. The true density profile from the mock
+data is also plotted for comparison. The vertical lines mark the radial
+position of the images. The final plot on the right is of the enclosed mass. As
+expected the error bars are smallest in the region of the images where the most
+information about the lens is present. The dip in the profile at the end of the
+profile is due to the cut off in mass in the lensing map. This is of little
+importance, though, as there is no lensing information there.
+
+\begin{figure}
+%\plotone{AAZContrastR1R5_Tm.pdf}
+\plotone{BCQuadR1a_TmS.pdf}
+\caption{A typical reconstructed lens. Here we present a single quad lens from 
+the BC mock galaxy.
+\textbf{(Left)}
+The arrival time surface. 
+\textbf{(Middle)}
+The surface density. The magenta curve represents the dark matter component,
+the yellow curve the stellar component, and the blue curve is the sum of the two.
+The black curve comes from the original mass model used to create the lens.
+The green vertical lines mark the radial positions of the images. The higher
+resolution feature of \Glass\ has been used on the central pixel allowing the
+steep profile to be captured.
+\textbf{(Right)}
+The cumulative mass.}
+\label{reconstruction}
+\end{figure}
+
+The main results from modeling these different configuration are shown black in
+\figref{Test reconstructions}. Each subplot corresponds to a different galaxy and
+the vertical axis shows the range of quality.  The quality of a
+model $\M_i$ by comparing the recovered density profile $\rho_\M(r)$ against
+the profile of the mock galaxy $\rho_G(r)$.  In particular, the plots show the
+RMS quantity
+%
+\begin{equation}
+  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
+  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
+\end{equation}
+%
+\begin{figure}
+%\plotone{AAarrival_surfaces}
+%\plotone{BBarrival_surfaces}
+\plotone{BCarrival_surfaces}
+\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
+the central image is shown, although not all tests include it. The central image belongs
+to only one set of images to avoid overconstraining the models. Similar colors group
+images that share a common source. In the case of the extended image systems the source
+is at the same redshift, while the redshift is varied between the systems in the 
+ZConstrast cases. Grey circles are a visual aid to help determine radial separation
+between images. The axes are measure in arcseconds.}
+\label{Test reconstructions}
+\end{figure}
+
+The morphological complexity increases from left to right within each plot. As
+a result, there is a general trend for the reconstruction quality to increase
+(and for $\chi$ to decrease). By adding more measurable information to each
+configuration the quality can also be affected. When both time delays and a
+central image are present the quality is highest. A double is known to provide
+very little constraint on the mass distribution. This is particular evident in
+galaxies AC and BC where the mass profile is steepest and the reconstruction of
+the double is poorest. However, the addition of an arc is sufficient to correct
+this.
 
 \subsection{Stellar mass}
-\begin{itemize}
-\item Assume perfect knowledge of the stellar mass distribution.
-\item Construct a lens system where the images are probing the stellar region.
-\item Add stellar mass as a minimum constraint on the pixels.
-\item Requires more pixels in the middle to correctly and efficiently be resolved
-\item Stellar mass improves the reconstruction. Need to explain how.
-\end{itemize}
 
-\subsection{Velocity dispersions}
+The previous tests have been conducted to show that \Glass\ performs as expected.
+Here, we present a novel constraint that can significantly improve the models. 
+The stellar mass distribution is a lower bound on the total mass and in the
+central region of a galaxy is also the dominant component. It can therefore be
+used to constrain the innermost profile. We took the stellar mass directly from
+the generated galaxies and projected the particles onto the pixels. \Glass\
+also offers an option to interpolate any map of stellar mass (e.g., from an
+observation) onto the pixels. The linear constraint is added to \Glass\ by
+writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the
+dark matter and stellar mass components in the potential (\eqnref{discrete
+potential}). Since each $\kappa_{s,n}$ is just a constant we do not add new,
+separate equations for each pixel.
 
-\begin{itemize}
-\item Can they predict radial profiles?
-\item Can we constrain lensing models from predicted velocity dispersions?
-\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
-\item Vary $z$ of the halo, possibly orientation.
-\item Should be able to recover $\gamma$ very well.
-\item Use G1. Show problems with recovering $\gamma$.
-\end{itemize}
+With the stellar mass lower bound, the improvement of the reconstruction
+quality shown in \figref{Test reconstructions} is quite dramatic for the
+steepest mock galaxies (AC and BC). This is because these models are dominated
+by stars in the inner region. The other two galaxies are unaffected because the
+models were already well modeled by the dark matter alone.
+
+\subsection{Velocity anisotropy}
+
+In addition to the lens model aspects, \Glass\ can also run post processing
+routines to analyze each model as it is produced. We have developed a number of
+routines for fitting analytic models to the lensing mass profiles. One in
+particular deprojects the 2d profile assuming a Hernquist profile for the
+light. By fixing the velocity anisotropy $\beta$ we can determine the velocity
+dispersion of the model. Of course, the true velocity dispersion is known for
+the mock galaxies and we can compare our method to those measurements.  In
+\figref{sigma-beta} we plot the recovered velocity dispersion for $\beta=0$ and $\beta=1$
+over a range of aperture sizes for the BC Quad with time delays and stellar
+mass. The stellar half mass radius is plotted in yellow and the Einstein radius
+in black. For this configuration the two radii are well separated. This plot
+demonstrates that the velocity anisotropy can be inferred by combining lens
+modeling and independent velocity dispersion measurements. The lens breaks
+the anisotropy degeneracy at a given aperture.
+
+\begin{figure}
+\plotone{BCQuadR1a_TmS-sb.pdf}
+\caption{Estimated velocity dispersion as a function of the aperture size. The
+single quad lens model for the BC mock galaxy was deprojected and the mass
+profile fit assuming a Hernquist profile for the light. The top curve (blue)
+assumes a velocity anisotropy $\beta=1$, while the lower curve (green)
+assumes $\beta=0$. Given an independent estimate of the velocity dispersion,
+lensing can be used to place constraints on the velocity anisotropy.}
+\label{sigma-beta}
+\end{figure}
+
+%\subsection{Velocity dispersions}
+%
+%\begin{itemize}
+%\item Can they predict radial profiles?
+%\item Can we constrain lensing models from predicted velocity dispersions?
+%\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
+%\item Vary $z$ of the halo, possibly orientation.
+%\item Should be able to recover $\gamma$ very well.
+%\item Use G1. Show problems with recovering $\gamma$.
+%\end{itemize}
 
@@
 %\figref{Test reconstructions} shows the reconstructed lens.
-
-%\begin{figure}
-%\plotone{AAarrival_surfaces}
-%\plotone{BBarrival_surfaces}
-%\plotone{BCarrival_surfaces}
-%\caption{Average reconstructions of each test case assuming time delays and no central image
-%using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
-%\label{Test reconstructions}
-%\end{figure}
 
@@
 
-\section{Results} %--------------------------------------------------------------
+%\section{Results} %--------------------------------------------------------------
 
-\figref{AAZContrastR1R5_Tm reconstruction} shows a typical reconstruction of a
-lens. The far left plot shows the arrival time surface with image marked as
-circles and the inferred source position as a diamond. The center plot shows
-the radial density profile. The error bars cover the full range of models
-generated by \Glass. The true density profile from the mock data is also
-plotted for comparison. The vertical lines mark the radial position of the
-images. The final plot on the right is of the enclosed mass. As expected the
-error bars are smallest in the region of the images where the most information
-about the lens is present. The dip in the profile at the end of the profile
-is due to the cut off in mass in the lensing map. This is of little importance,
-though, as there is no lensing information there.
-
-\begin{figure}
-\plotone{AAZContrastR1R5_Tm.pdf}
-\caption{A typical reconstructed lens. 
-\textbf{(Left)}
-The arrival time surface. In this case, there are two sources at different
-redshifts with galaxy AA. The next three panels show the radial density,
-average enclosed density, and enclosed mass profiles, respectively.  The grey
-curve is from the galaxy and the vertical lines show the positions of the
-images for the two sources.}
-\label{AAZContrastR1R5_Tm reconstruction}
-\end{figure}
-
-\begin{figure}
-\plotone{AAresults.pdf}
-\end{figure}
+%\begin{figure}
+%\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
+%\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
+%\end{figure}
 
 %\subsection{Model quality}
-We estimate the quality of a model $\M_i$ by comparing the recovered
-density profile $\rho_\M(r)$ against the profile of the mock galaxy $\rho_G(r)$.
-In particular, the plots show the RMS quantity
-%
-\begin{equation}
-  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
-  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
-\end{equation}
 
-\subsection{Using principle component analysis to find new degeneracies}
+%\subsection{Shape fitting}
+
+%\subsection{Using principle component analysis to find new degeneracies}
 
@@
 
-\subsection{Aperture}
+%\subsection{Aperture}
 
-\begin{figure}
-\plotone{sigma_beta.pdf}
-\caption{}
-\end{figure}
+%\begin{figure}
+%\plotone{sigma_beta.pdf}
+%\caption{}
+%\end{figure}
 

### 2013-05-27 shapes/thesis.tex

--- 2013-02-19 shapes/thesis.tex
@@
 
-\usepackage[margin=0.5in]{geometry}
+\usepackage[margin=0.8in]{geometry}
 \usepackage{multirow}
@@
 \usepackage{mathrsfs}
-\usepackage{subfigure}
+
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-%%%%%%%%%%% Still to change: Dominiks PhD!
 \title{ALIGNMENT OF LIGHT AND MASS IN LENSING GALAXIES}
 \author{Claudio Bruderer}
+\date{}
 
@@
 \begin{abstract}
-\noindent Something
+\noindent Understanding the structure and properties of galaxies today is essential to understand how galaxies formed.
+This poses a larger problem to us than one might imagine.
+Especially constraining the dark matter distribution in galaxy halos is not trivial.
+There are only a few methods to directly estimate this distribution.
+One of them is strong gravitational lensing, an effect caused by all of mass.
+This phenomenon allows constraining the gravitational potential of lens galaxies and thus the mass distribution.
+With knowledge of the light distribution it is possible to disentangle the dark matter and baryonic mass components and study their properties.
+We use the newly-developped nonparametric framework \textit{GLASS} to model the mass distribution of a total of 15 strong gravitational lensing galaxies, most of which are early-type galaxies, for which we have information on the baryonic mass distribution.
+We are thus able to separate the mass components.
+By using a simple shape measure, namely the inverse of the moment of inertia tensor, we can analyze the shapes of the distributions.
+Analyzing the alignments between the semi-major axes of the distributions, we find that there can be significant misalignments and also cases of alignment between the semi-minor and semi-major axes.
+Mass thus need not follow light.
+Furthermore, the ellipticities of the dark matter distributions are always smaller than the baryonic mass distributions.
+Dark matter halos tend to be more spherical than the light distribution of the galaxy.
+We also consider the environment of the lenses.
+We find that lenses in denser environments tend to be more misaligned with either the semi-major or semi-minor axis.
+Additionally, the semi-major axis of lenses lying in groups or clusters of the dark matter halo might be oriented in direction of the centroid.
 \end{abstract}
 
-%\tableofcontents
+\tableofcontents
 
-\section{Introduction}
+\clearpage
+\section{Introduction}\label{sec:introduction}
 
-\subsection{Context/Background/Motivation}
-\begin{itemize}
-\item Why interesting (lensing can constrain mass distribution (enclosed mass constraint independent from model with only few percent uncertainty e.g.
-Kochanek 1991?, Wambsganss \& Paczyński 1994?), insights into structure formation)
-\item What is to be expected from theory (dm, alternative gravity)
-\end{itemize}
+Gravitational lensing is one of the few phenomena that allow probing the matter distribution directly.
+It makes no distinction between baryonic and dark matter, both components act on light rays in the same way.
+Gravitational lensing is therefore somewhat special as it allows to 'see' dark matter, if we are able to separate the two components.
+Therefore studying these effects allows us to probe dark matter and its properties.
+We are typically interested in measuring its distribution, how it clusters, its connection to structure formation, and of course its nature.
+With strong gravitational lensing galaxies we are effectively probing the matter distribution on relatively small scales.
+Thus, much insight could be gained in how galaxies form and how they are structured.
 
-\subsection{Anything done before?}
-\textbf{\cite{1997ApJ...482..604K}}: Look at 17 lenses at redshifts ranging between 0.1 and $\sim1$.
-Sample consists of mainly passively evolving elliptical galaxies and a few spirals.
-Claim that generally projected light and dark matter distributions are strongly correlated and are not far out of alignment ($\lesssim10^{\circ}$), except in cases where there are strong external tidal perturbations (although misalignments are not necessary in these cases).
-'Dark matter halos can be significantly flatter than the light (e.g., Sackett et al.
-1994; Buote \& Canizares 1994, 1996; also see the review by Sackett 1996)'.
-To reconstruct the mass they fit singular isothermal ellipsoid (SIE) lens models, which immediately give them the shape.
-Another model they use is a singular isothermal sphere (SIS) and some external tidal perturbation (shear).
-As already stated in \cite{1998ApJ...509..561K}, these models sometimes give a bad fit.
-To obtain a good fit, an another independent source of external shear is needed (external tidal perturbation).
-They also state that it is known that the lenses Q0957 + 561 (Young et al.
-1980, Grogin \& Narayan 1996), PG 1115 + 080 (Keeton \& Kochanek 1997, Kundic et al.
-1997a, Schechter et al.
-1997, Tonry 1998), B1422 + 231 (Hogg \& Blandford 1994, Kormann et al.
-1994, Kundic et al 1997b, Tonry 1998) are subject to significant tidal perturbations by a nearby cluster, group or galaxy (also line-of-sight structure) (--> All lying in a environment?
-Ask Prasenjit).
+The main challenges are however estimating first, the baryonic mass distribution, such that the two componantes can be disentangled, and second, modelling the lens, i.e.
+the mass distribution.
+We do not elaborate the first problem (see e.g.
+\cite{leier11phd}) further but skip right ahead to the second problem.
+There are in general two classes of methods to reconstruct gravitational lenses, parametric and nonparametric methodes.
+A comparison of these two classes of methods can be found in \cite{2008ApJ...681..814C}.
+Parametric methods assume a distribution, which depends only on few parameters, such that a best-fitting model can be found.
+Nonparamatric (or free-form) methods chose a specific base set.
+Due to the fact that there is no \textit{a priori} reason to prefer certain mass models over others, given that they all satisfy certain prior conditions and reproduce the same gravitational lensing effects, there is no best-fitting model.
+It is therefore important to explore many models and look at the properties of all the models in the ensemble.
+We typically need to sample high-dimensional parameter spaces, which describe all allowed models, in a uniform and uncorrelated way to generate a representative sample.
+This is a computational challenge and certainly not trivial \citep{2008ApJ...679...17C,2012MNRAS.425.3077L}.
+Parametric methods are usually computationally cheaper, but as the distributions are assumed beforehand, they might bias the result too much.
 
-\textbf{\cite{1998ApJ...509..561K}}: They used SIEs for the reconstruction of 6 lenses.
-They find that for many lenses a model with two independent shears (e.g.
-SIE + 1 external shear) gives a much better fit.
-Additionally, the fits are much better than just trying to fit different radial mass distributions with the same number of degrees of freedom.
-Numerical simulations generally produce more elliptical and more triaxial dark matter halos than luminous galaxies (e.g.
-Warren et al.
-1992; Dubinski 1992, 1994).
-They can however only compare 3 galaxies with eachother.
+With these tools, we can start answering the question whether mass follows light.
+It is a well-known fact that for observations to match e.g.
+rotation curves and simulations, the radial density profiles of baryonic mass and dark matter differ.
+As we know that galaxies can be quite triaxial, the next question to ask is whether dark matter and baryonic matter need to be aligned and have similar ellipticities.
+If this is not the case, then this needs to be explained by mechanism and effects (e.g.
+environment of the lenses) that produce and sustain these different properties.
+It is furthermore unclear whether modified gravity theories introduced to explain the 'missing matter' could explain misalignments between mass and light.
 
-\textbf{\cite{1998PhDT.........6K}}: Not sure whether everything was already covered in previous papers or not.
-He modelled observed lenses to determine their shapes and finds that the dark matter halos are generally aligned with the luminous part.
-Exceptions are however lenses with known tidal disruptions, where there can be a misalignment.
-He concludes that the halos were modified by interactions with the galaxies.
-He however does not state in the abstract how he modelled the lenses.
+There were already attempts to analyze the alignment of light and mass.
+\cite{1997ApJ...482..604K} started looking at misalignments quite early on.
+They use Singular Isothermal Spheres (SIS) with an external shear term and Singular Isothermal Ellipsoids (SIE) (e.g.
+\cite{1994A&A...284..285K}) without external shear to model the mass distribution.
+Applying this to a sample of 17 lenses, they find a strong correlation between light and dark matter distributions, while there is only a small scatter of less than $10^{\circ}$, if there is no strong external perturbation.
+They find however no correlation between the axis ratios of the distributions.
 
-\textbf{\cite{2000ApJ...538L.113N}}:
+Later on, \cite{2006ApJ...649..599K} and \cite{2012ApJ...761..170G} analyzing lens samples of similar sizes and \cite{2009ApJ...690..670T} analyzing a lens sample containing even 70 galaxies also looked for misalignments.
+They all use SIEs to model the mass distributions.
+Only \cite{2012ApJ...761..170G} however include an external shear contribution in case more information is available.
+They neglecht the external shear although \cite{1998ApJ...509..561K} find that SIEs with an independent external shear term fit the data better.
+They find reasonable alignments, the scatter is however larger than the one they find in \cite{1997ApJ...482..604K}.
+\cite{2012ApJ...761..170G} find a rms scatter of $25^{\circ}$ for the whole sample.
+Even after dropping the almost spherical lenses, the rms scatter is still $18^{\circ}$.
+They attribute this to a significant external shear contribution.
+\cite{2009ApJ...690..670T} even find a significant correlation between the misalignment and the local resp.
+global environment.
+In general, lenses in overdense environment seem to be more likely to be misaligned.
+\cite{2009ApJ...690..670T} and \cite{2012ApJ...761..170G} also find a correlation with a large scatter between the ellipticities of the light and dark matter distributions.
 
-\textbf{\cite{2002sgdh.conf...62K}}:
+Contrary to earlier approaches, we choose to use a non-parametric modelling technique.
+We use a pixel-based (see e.g.
+\cite{1997MNRAS.292..148S}) lens reconstruction framework called \textit{GLASS} \citep{2012MNRAS.425.3077L}.
+We apply this successfully on a sample of 15 strong gravitational lensing galaxies using stellar mass data of \cite{leier11phd}.
+Thus, we can disentangle dark and luminous matter and look at the shapes and alignments of these distributions.
+We can also look at the ellipticities of the reconstructed lenses and compare them to the ones of the stellar distribution.
+Furthermore, we discuss the environments of these lenses, as they might affect some properties of gravitational lenses in a significant way \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
+We think that we have enough statistics to make claims about misalignments between the dark matter halo and the stellar mass distribution, and how the halo is oriented compared to the environment.
 
-\textbf{\cite{2005MNRAS.360.1333W}}:
+In Section \ref{sec:data} we present the lens sample and important properties of each lens.
+In Section \ref{sec:method} we present the reconstruction method we use and our shape measure.
+Section \ref{sec:results} consists of the results of this analysis.
+We show the relations we find between misalignment, ellipticities, and the environment.
 
-\textbf{\cite{2008MNRAS.383..857F}}:
+\section{Data}\label{sec:data}
+\begin{table}[t]
+ \centering
+ \begin{minipage}{.64\textwidth} %.63
+  \begin{tabular}{l c c l | l c c l}
+   Lens & $z_{L}$ & $z_{S}$ & Type & Lens & $z_{L}$ & $z_{S}$ & Type\\ \hline \hline
+   Q0047 & 0.48 & 3.60 & Quad & PG1115 & 0.31 & 1.72 & Quad\\
+   Q0142 & 0.49 & 2.72 & Double & B1152 & 0.44 & 1.02 & Double\\
+   MG0414 & 0.96 & 2.64 & Quad & B1422 & 0.34 & 3.62 & Quad\\
+   B0712 & 0.41 & 1.34 & Quad & SBS1520 & 0.72 & 1.86 & Double\\
+   RXJ0911 & 0.77 & 2.80 & Quad & B1600 & 0.41 & 1.59 & Double\\
+   BRI0952 & 0.63 & 4.50 & Double & B1608 & 0.63 & 1.39 & Quad\\
+   Q0957 & 0.36 & 1.41 & Double & MG2016 & 1.01 & 3.27 & Quad$^{1}$\\
+   LBQS1009 & 0.87 & 2.74 & Double & B2045 & 0.87 & 1.28 & Quad\\
+   B1030 & 0.60 & 1.54 & Double & HE2149 & 0.60 & 2.03 & Double\\
+   HE1104 & 0.73 & 2.32 & Double & Q2237 & 0.04 & 1.69 & Quad\\
+  \end{tabular}
+  \captionsetup{width=\linewidth}
+  \captionof{table}{List of all the lenses in the sample and their properties.
+Data is taken from \textit{CASTLES} and \cite{leier11phd}.
+The angles are measured north-through-east.
+\newline $^{1}$ Two images merge, thus only three images can be resolved.}
+  \label{tab:overview}
+ \end{minipage}
+\end{table}
 
-\textbf{\cite{2011AstRv...6f..43B}}:
+\begin{table}[t]
+ \centering
+ \begin{minipage}{.83\textwidth} %.8
+  \begin{tabular}{l c c c c c c c}
+   \multirow{2}{*}{Lens} & \multirow{2}{*}{Environment$^{a}$} & \multicolumn{2}{c}{Group/Cluster centroid$^{b}$} & & \multicolumn{2}{c}{Other galaxy} & \multirow{2}{*}{References$^{c}$}\\ \cline{3-4} \cline{6-7}
+    & & $\Delta\alpha$ [''] & $\Delta\delta$ [''] & & $\Delta\alpha$ [''] & $\Delta\delta$ ['']\\ \hline \hline
+   Q0047 & G(9) & $3.6\pm15.6$ & $43.2\pm28.8$ &   & ... & ... & 1\\
+   MG0414 & 2 & ... & ... &   & $-0.4$ & $1.5$ & 2\\
+   B0712 & 2 & ... & ... &   & $47$ & $-91$ & 3\\
+   RXJ0911 & C & $-12.0$ & $-39.8$ &    & ... & ... & 4\\
+   Q0957 & C & ... & ... &   & ... & ... & 5\\
+   B1030 & 2 & ... & ... &   & $-9.8$ & $8.5$ & 6\\
+   PG1115 & G(13) & $-10.8\pm21.0$ & $-3.6\pm15.6$ &   & ... & ... & 1\\
+   B1422 & G(17) & $61.2\pm25.2$ & $-10.8\pm23.4$ &   & ... & ... & 1\\
+   SBS1520 & G(5) & ... & ... &   & ... & ... & 7\\
+   B1600 & G(17) & $-8.4^{d}$ & $-1.5^{d}$ &   & ... & ... & 8\\
+   B1608 & G(8) & $-0.7$ & $8.0$ &   & ... & ... & 9\\
+   MG2016 & C(69) & ... & ... &   & ... & ... & 10\\
+   HE2149 & G & $-36.6$ & $14.2$ &   & ... & ... & 11\\
+  \end{tabular}
+  \captionsetup{width=\linewidth}
+  \captionof{table}{List of lenses lying in a group or cluster environment, or that have a companion.
+\newline $^{a}$ G stands for group, C for cluster, and 2 means that the lens has a companion galaxy.
+If known, the number of member galaxies including the lens is given.
+\newline $^{b}$ If not stated differently, the centroid positions are luminosity-weighted estimates.
+\newline $^{c}$ References for the centroid estimates we used.
+\newline $^{d}$ Only number-weighted estimates are available.
+\newline 1: \cite{2011ApJ...726...84W}; 2: \cite{1993AJ....105....1S}; 3: \cite{2002AJ....123..627F}; 4: \cite{2001ApJ...555....1M}; 5: \cite{1998ApJ...504..661C}; 6: \cite{2000ApJ...536..584L}; 7: \cite{2008ApJ...673..778A}; 8: \cite{2007AJ....134..668A}; 9: \cite{2003MNRAS.344..337T}; 10: \cite{2006ApJ...646...85W}; 11: \cite{2006ApJ...646...85W}}
+  \label{tab:environment}
+ \end{minipage}
+\end{table}
 
-\textbf{\cite{2012ApJ...761..170G}}:
+\begin{table}[t]
+ \centering
+ \begin{minipage}{.79\textwidth} %.77
+  \begin{tabular}{l c c c c}
+   Lens & \multicolumn{3}{c}{Time delays [d]} & References\\ \hline \hline
+   RXJ0911 & $\Delta t_{BA}=146\pm4$ & ... & ... & 1\\
+   Q0957 & $\Delta t_{BA}=416.5\pm1.0^{a}$ & $\Delta t_{BA}=420.6\pm1.9^{b}$ & ... & 2\\
+   HE1104 & $\Delta t_{BA}=162.2^{+6.3}_{-5.9}$ & ...  & ...  & 3\\
+   PG1115 & $\Delta t_{BA}=12.0^{+2.4}_{-2.0}$ & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & ... & 4\\
+   SBS1520 & $\Delta t_{BA}=125.8\pm2.1$ & ... & ... & 5\\
+   B1600 & $\Delta t_{BA}=51\pm2$ & ... & ... & 6\\
+   B1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & $\Delta t_{CA}=36.0\pm1.5$ & $\Delta t_{DA}=77.0^{+2}_{-1}$ & 7\\
+   HE2149 & $\Delta t_{BA}=103\pm12$ & ... & ... & 8\\
+  \end{tabular}
+  \captionsetup{width=\linewidth}
+  \captionof{table}{Lenses with measured time delays.
+$\Delta t_{BA}$ corresponds to the time delay between the images A and B with A leading.
+\newline $^{a}$ measured in the g-band \newline $^{b}$ measured in the r-band \newline 1: \cite{2002ApJ...572L..11H}; 2: \cite{2012A&A...540A.132S}; 3: \cite{2008ApJ...676...80M}; 4: \cite{2010MNRAS.406.2764T}; 5: \cite{2011A&A...536A..44E}; 6: \cite{2000ApJ...544..117B}; 7: \cite{2002ApJ...581..823F}; 8: \cite{2002A&A...383...71B}}
+  \label{tab:timedelays}
+ \end{minipage}
+\end{table}
 
-\textbf{\cite{2000ApJ...536..584L}}:
+The pixelated stellar mass maps we use, were reconstructed by \cite{leier11phd}.
+For each pixel the surface brightness was compared with stellar mass-to-light ratios, which were determined by stellar population synthesis models.
+This technique allows estimating the stellar mass in these pixels.
+Further details on this method can be found in \cite{leier11phd}, \cite{2005ApJ...623L...5F}, \cite{2008MNRAS.383..857F}.
 
-\subsection{New here}
-\begin{itemize}
-\item Statistics
-\item Free-form (explain advantages of free-form over parametric modelling (\cite{2004AJ....127.2604S}, \cite{2012MNRAS.425.3077L}, \cite{2008ApJ...681..814C}), cite GLASS (\cite{2012MNRAS.425.3077L})
-\item group versus stellar misalignment with dm halo
-\end{itemize}
+Our sample consists of 20 galaxies.
+The sample is identical to the one as in \cite{leier11phd} and \cite{2011ApJ...740...97L} except that \textit{HS0818+1227} proved too difficult to reconstruct and therefore was left out.
+Most of the lens galaxies are early-type galaxies, except \textit{B1030+074}, \textit{B1152+200}, \textit{B1600+434}, \textit{B1608+656}, and \textit{Q2237+030}.
+All lenses can also be found in the gravitational lens database \textit{CASTLES}.
+Characteristics and references of each lens in the sample are listed below.
+Table \ref{tab:overview} contains of all the redshifts and the type of the lenses, Table \ref{tab:environment} lenses with environment information, and Table \ref{tab:timedelays} lenses with measured time delays.
 
-\section{Data}
-\begin{itemize}
-\item SPS (Ignacio Ferreras, Dominik, etc. (\cite{2011ApJ...740...97L}))
-\item Bundle information in tables (especially what input data was used for the lenses)
-\end{itemize}
+\textit{Q0047-2808} (hereafter \textit{Q0047} or \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
+\cite{2011ApJ...726...84W} find a group of 9 members all of which they spectroscopically confirm.
 
-\begin{landscape}
- \begin{center}
-  \begin{tabular}{l c c c c c c c c c}
-	\hline
-	\multirow{2}{*}{Lens} & \multirow{2}{*}{$z_{L}$} & \multicolumn{2}{c}{Group/Cluster centroid} & & \multicolumn{2}{c}{Other galaxy} & \multirow{2}{*}{Galaxy type} & \multirow{2}{*}{Environment} & \multirow{2}{*}{References}\\ \cline{3-4} \cline{6-7}
-	 & & $\Delta\alpha$ ('') & $\Delta\delta$ ('') & & $\Delta\alpha$ ('') & $\Delta\delta$ ('') & & & \\ \hline \hline
-	Q0047 & 0.48 & $3.6\pm15.6$ & $43.2\pm28.8$ &   & & & Early-type & G(9) & \cite{2011ApJ...726...84W}\\
-	Q0142 & 0.49 & & &   & & & Early-type & - & \cite{2000ApJ...536..584L}\\
-	MG0414 & 0.96 & & &   & $-0.385$ & $1.457$ & Early-type & 1 & \cite{1993AJ....105....1S}\\
-	B0712 & 0.41 & & &   & $47$ & $-91$ & Early-type & 1 & \cite{2002AJ....123..627F}\\
-	HS0818 & 0.39 & & &   & & & see below & 1 & aaaaaaaaa\\%\cite{2000A&A...357L..29H}\\
-	RXJ0911 & 0.77 & $-12.0$ & $-39.8$ &    & & & Early-type & C & \cite{2001ApJ...555....1M}\\
-	BRI0952 & 0.63 & &   & & & & Early-type & - & aaaaaaaaa\\%\cite{2007A&A...465...51E}\\
-	Q0957 & 0.36 & $4.8$ & $2.1$ &   & & & Early-type & C & \cite{1998ApJ...504..661C}\\
-	LBQS1009 & 0.87 & & &   & & & Early-type & - & aaaaaaaaa\\%\cite{2004A&A...428..741F}\\
-	B1030 & 0.60 & & &   & $-9.78$ & $8.54$ & Early-type & 1 & \cite{2000ApJ...536..584L}\\
-	HE1104 & 0.73 & & &   & & & Early-type & - & aaaaaaaaa\\%\cite{2004A&A...428..741F}\\
-	PG1115 & 0.31 & $-10.8\pm21$ & $-3.6\pm15.6$ &   & & & Early-type & G(13) & \cite{2011ApJ...726...84W}\\
-	B1152 & 0.439 & & &   & & & Unknown & - & see below\\
-	B1422 & 0.34 & $61.2\pm25.2$ & $-10.8\pm23.4$ &   & & & Early-type & G(17) & \cite{2011ApJ...726...84W}\\
-	SBS1520 & 0.72 & & &   & & & Early-type & G(4) & see below\\
-	B1600 & 0.41 & $-8.44286$ & $-1.48571$ &   & & & Late-type & G(7) & \cite{2007AJ....134..668A}\\
-	B1608 & 0.63 & $-0.697246$ & $7.96956$ &   & & & Both & G(8) & \cite{2006ApJ...642...30F}\\
-	MG2016 & 1.01 & & &   & & & Early-type & C(69) & \cite{2003MNRAS.344..337T}\\
-	B2045 & 0.87 & & &   & & & Early-type & - & \cite{1999AJ....117..658F}\\
-	HE2149 & 0.60 & $-36.6$ & $14.2$ &   & & & Early-type & G & \cite{2006ApJ...646...85W}\\
-	Q2237 & 0.04 & & &   & & & Late-type & - & see below\\ 
-	\hline
-  \end{tabular}
- \end{center}
-\end{landscape}
+\textit{Q0142-100} (hereafter \textit{Q0142} or \textit{0142}) is a passively evolving early-type galaxy according to \citep{2000ApJ...536..584L,2007A&A...465...51E}.
 
-The pixelated stellar mass maps we use here was reconstructed by \cite{leier11phd}.
-For each pixel the surface brightness was compared with stellar mass-to-light ratios, which were determined by populations synthesis model.
-Details for this method can be found in \cite{leier11phd}, \cite{2005ApJ...623L...5F}, \cite{2008MNRAS.383..857F}.
+\textit{MG0414+0534} (hereafter \textit{MG0414} or \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
+\cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens.
+Due to the proximity of this satellite, we include it as a point mass in our analysis.
 
-Here some comments about the environments of the lenses in the sample.
+\textit{B0712+472} (hereafter \textit{B0712} or \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}.
+Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}.
+There is also a group of 10 galaxies at a lower redshift.
 
-\textbf{Q0047-2808}: \cite{2011ApJ...726...84W} find a group of 9 members, spectroscopically confirmed. According to \cite{1996MNRAS.278..139W} it is a luminous early-type galaxy.
+\textit{RXJ0911+0551} (hereafter \textit{RXJ0911} or \textit{0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}.
+It has measured time delays \citep{2002ApJ...572L..11H}.
+It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
+This cluster seems to be rather complex and especially it is not spherical.
+Possibly it is not dynamically relaxed, although X-ray emission can be detected.
+Analysis of this emission yields a temperature of 2.3 keV.
+There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
 
-\textbf{Q0142-100}: The required external shear is comparable to the cosmic LSS-contribution, and it also seems to be a passively evolving early-type galaxy according to \cite{2000ApJ...536..584L} and confirmed by \cite{2007A&A...465...51E}.
+\textit{BRI0952-0115} (hereafter \textit{BRI0952} or \textit{0952}) is an early-type galaxy \citep{2000ApJ...536..584L,2007A&A...465...51E}.
+\cite{2006ApJ...641..169M} find that the lens lies in a poor group of 5 members.
+However, a redshift of $z=0.41$ was used.
+According to \cite{2007A&A...465...51E}, the redshift is more likely to be $z=0.632$.
+They also find a system of 2 or 3 other galaxies at a slightly higher redshift of which the lens could be part of.
+The required external shear could be explained easily by a cosmic contribution \citep{2000ApJ...536..584L}.
+Therefore, we treat this lens as an isolated object.
 
-\textbf{MG0414+0534}: According to \cite{1999AJ....117.2034T} the lens seems to be a passively evolving early-type galaxy.
-\cite{1993AJ....105....1S} find a luminous satellite galaxy north-west of the lens.
-The position data of this object was taken from CASTLES.
+\textit{Q0957+561} (hereafter \textit{Q0957} or \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g.
+\cite{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}).
+Due to the large image separation, large physical scales are probed.
+As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
+These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
+The lens has a measured time delay, e.g.
+\citep{2012A&A...540A.132S}.
+They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level.
+They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
+We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
 
-\textbf{B0712+472}: According to \cite{2002AJ....123..627F} potentially only one other galaxy 102'' to the south-east at a similar redshift.
-There is however a group of 10 galaxies at a lower redshift.
-According to \cite{1998AJ....115..377F} the spectrum is typical for an early-type galaxy.
+\textit{LBQS1009-0252} (hereafter \textit{LBQS1009} or \textit{1009}) is probably an early-type galaxy \citep{2000ApJ...536..584L}.
+\cite{2004A&A...428..741F} find no significant galaxy overdensity near the lens.
 
-\textbf{HS0818+1227}: According to \cite{2000A&A...357L..29H} one galaxy, which seems to be at the same redshift, can be found near the lens.
-In roughly the same direction, two other brighter galaxies can be found a bit farther away.
-However, no further inquiries were made whether they all belong to the same group or not.
-There are also a couple of fainter ones, which could potentially be group members.
-\underline{TO DO}: Get relative position of nearest galaxy!
-More or less everybody lists HS0818 as an early-type, however noone states a source for their belief.
-
-\textbf{RXJ0911+0551}: According to \cite{2001ApJ...555....1M} the lens lies on the outskirts of a cluster environment.
-The cluster seems to be rather complex and not spherical, and it possibly is not dynamically relaxed.
-The X-ray emission analysis yields a temperature of 2.3 keV.
-There is also a satellite galaxy to the north-west direction (\cite{2000ApJ...544L..35K}).
-The lens is a almost circular early-type galaxy (\cite{2012A&A...538A..99S}).
-Time delay: $\Delta t_{BA}=146\pm4$ (\cite{2002ApJ...572L..11H}; CASTLES: BD-delay, here BA-delay).
-
-\textbf{BRI0952-0115}: Lens possibly part of smaller system (of 2 or 3 other galaxies), which is found at a slightly higher redshift, according to \cite{2007A&A...465...51E}.
-Surely group found in \cite{2006ApJ...641..169M} is at a lower redshift than the lens as the redshift estimate $z=0.41$ was used.
-\cite{2007A&A...465...51E} however find that the redshift is more likely to be $z=0.632$.
-In \cite{2000ApJ...536..584L} it is found that required external shear can be explained easily by a cosmic contribution.
-\cite{2000ApJ...536..584L}, and later on confirmed by \cite{2007A&A...465...51E}, find that it seems to be a typical early-type galaxy.
-\underline{TO DO}: Why is the such a hugely different redshift estimate in Table 4 of \cite{2006ApJ...641..169M}?
-Reason: In \cite{2000ApJ...536..584L} this redshift is listed as the lens redshift.
---> Correct redshift used in analysis?
-
-\textbf{Q0957+561}: The lens is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g.
-\cite{1992MNRAS.254P..27G}, \cite{1994A&A...291..411A}, \cite{1998ApJ...504..661C}).
-As listed in table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
-Judging 'by hand' from the center of the X-ray emission measured by \cite{1998ApJ...504..661C}, we find $\Delta\alpha=4.8''$ and $\Delta\delta=2.1''$, which corresponds to a position angle of 66.4 deg, consistent with the values listed above.
-\cite{2012A&A...540A.132S} measure the time delay in the g- and r-band.
-They find $\Delta t_{BA}=416.5\pm1.0$ in the g-band, $\Delta t_{BA}=420.6\pm1.9$ in the r-band.
-So, they find a three-day lag between these two bands and the two estimates do not agree at the 2$\sigma$-level.
-They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion (light propagation time increases with decreasing wavelength).
-\underline{TO DO}: Better measure of the cluster center?
-Time delay?
-
-\textbf{LBQS1009-0252}: \cite{2000ApJ...536..584L} find that it is probably an early-type galaxy. According to \cite{2004A&A...428..741F}, there is no significant galaxy overdensity near the lens.
-
-\textbf{B1030+074}: As noted by \cite{1998MNRAS.300..649X} it appears to have some substructure.
-\cite{2000ApJ...536..584L} conclude that they are two distinct galaxies.
-The main one is an red, early-type galaxy.
+\textit{B1030+074} (hereafter \textit{B1030} or \textit{1030}) appears to have some substructure \citep{1998MNRAS.300..649X}.
+\cite{2000ApJ...536..584L} conclude that there are two distinct galaxies.
+The main one is a red, early-type galaxy.
 The other component seems to be fitted well by an exponential disk galaxy.
@@
 Although there is another galaxy nearby, it is too blue to be an early-type galaxy and thus they cannot estimate its shear contribution.
-\underline{TO DO}: No error on position of G1 in \cite{2000ApJ...536..584L}?
 
-\textbf{HE1104-1805}: \cite{2000ApJ...536..584L} find that it is probably an early-type galaxy (also \cite{2000A&A...360..853C}).
-They also seem to find a group environment.
-\cite{2004A&A...428..741F} however rather think that their photometric redshift measurement indicate that these galaxies are at a higher redshift and rather associated with the source.
-As it is also listed in \cite{2004A&A...428..741F}, modelling of the lens, parametric and free-form, requires strong external shear.
-Time delay: $\Delta t_{AB}=162.2^{+6.3}_{-5.9}$ (\cite{2008ApJ...676...80M}; here BA-delay).
+\textit{HE1104-1805} (hereafter \textit{HE1104} or \textit{1104}) is probably an early-type galaxy \citep{2000ApJ...536..584L,2000A&A...360..853C}.
+It has measured time delays \citep{2008ApJ...676...80M}.
+\cite{2000ApJ...536..584L} also seem to find a group environment.
+\cite{2004A&A...428..741F} however conclude that the photometric redshift measurements of these galaxies indicate that they are at a higher redshift and rather associated with the source.
+Nonetheless, their lens models, parametric and free-form, all require strong external shear.
 
-\textbf{PG1115+080}: Environments analyzed by \cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W}.
-Lying in a small group of 13 members.
-The lens is an early-type galaxy (\cite{2005ApJ...626...51Y}).
-\cite{2004ApJ...610..686G} detect X-ray emission from the corresponding group at temperature 0.8 keV.
-Time delays: \cite{1997ApJ...489...21B} find $\Delta t_{AC}=13.3^{+0.9}_{-1.0}$ and $\Delta t_{BA}=11.7^{+1.5}_{-1.6}$, \cite{2010MNRAS.406.2764T} find however $\Delta t_{AC}=12.0^{+2.4}_{-2.0}$ and $\Delta t_{BA}=4.4^{+3.2}_{-2.4}$ (here actually BA- and CD-delay).
+\textit{PG1115+080} (hereafter \textit{PG1115} or \textit{1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}.
+It has measured time delays.
+We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ significantly from traditional values by e.g.
+\cite{1997ApJ...489...21B}.
+\cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W} analyzed the environment of the lens thouroughly.
+It is part of a small group of 13 members.
+\cite{2004ApJ...610..686G} detect also X-ray emission from the corresponding group, which yields a temperature of 0.8 keV.
 
-\textbf{B1152+200}: Not much seems to be known about the environment.
-The lens galaxy type is not known.
-According to \cite{2000A&A...357..115T} however, its color is consistent with a late-type or an irregular galaxy.
+\textit{B1152+200} (hereafter \textit{B1152} or \textit{1152}) seems to have a color consistent with a late-type or an irregular galaxy \citep{2000A&A...357..115T}.
+Not much seems to be known about the environment of the lens.
 
-\textbf{B1422+231}: \cite{2006ApJ...641..169M} find totally 16 spectroscopically confirmed member galaxies of the group.
+\textit{B1422+231} (hereafter \textit{B1422} or \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}.
+Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to be trusted too much as they deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}.
+An accurate measurement of the time delays would require time delay measurements on the scale of hours.
+\cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies.
 Using newer data, \cite{2011ApJ...726...84W} find an additional member.
-\cite{2004ApJ...610..686G} detect X-ray emission from the corresponding group at temperature 1.0 keV.
-According to \cite{1996ApJ...462L..53I} the lens is an early-type galaxy.
-Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to trust too much as they deviate quite a bit from theoretical expectations in \cite{2003AJ....126...29R}.
-An accurate measurement of the time delays probably requires time delay measurements on the scale of hours.
+\cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
 
-\textbf{SBS1520+530}: There is some uncertainty about the redshift of the galaxy.
-\cite{2002A&A...391..481B} find that their spectroscopic redshift estimate of the galaxy is consistent with $z=0.71$, which was measured first by \cite{1997A&A...318L..67C}.
-Both however also measured a system at $z=0.82$.
-\cite{2002A&A...391..481B} however conclude that it does not seem to be associated with the lens.
-\cite{2008ApJ...673..778A} find another system at $z=0.76$.
-They argue that this system is more likely to be the lens, and the foreground system at $z=0.71$ just a local perturber.
-The data however does not seem to be conclusive.
-\cite{2008ApJ...673..778A} also find and spectroscopically confirm 3 groups in the line of sight.
-One is at $z=0.716$, with 5 members and the centroid position: $\alpha=15:21:48.16$, $\delta=52:53:19.5$.
-Another one at $z=0.758$, with 13 members and $\alpha=12:21:38.22$, $\delta=52:55:23.1$.
-Another one is at the higher redshift $z=0.818$ with 10 members.
-Including the lens would change these positions.
-The lens seems to be an early-type galaxy, possibly with a disc (\cite{2008ApJ...673..778A}).
-Time delay: $\Delta t_{BA}=125.8\pm2.1$ (\cite{2011A&A...536A..44E}; here also BA-delay).
-\underline{TO DO}: Dominik has used a lower redshift.
-Implications for the stellar population synthesis?
-Redo analysis at a higher redshift.
+\textit{SBS1520+530} (hereafter \textit{SBS1520} or \textit{1520}) is an early-type galaxy, possibly with a disc \citep{2008ApJ...673..778A}.
+It has measured time delays \citep{2011A&A...536A..44E}.
+There is some uncertainty about the redshift of the galaxy.
+\cite{2002A&A...391..481B} find that their spectroscopic redshift estimate is consistent with $z=0.71$, which was measured first by \cite{1997A&A...318L..67C}.
+Both however also find a system at $z=0.82$, which could be the main lens.
+\cite{2002A&A...391..481B} however conclude that it is not associated with the lens.
+\cite{2008ApJ...673..778A} argue that a system they find at $z=0.76$ is more likely to be the lens, and the foreground system at $z=0.71$ is just a local perturber.
+Data seems however not conclusive.
+\cite{2008ApJ...673..778A} find and spectroscopically confirm a total of 3 groups along the line of sight.
+A poor group of 5 members is at $z=0.716$, another one with 13 members is at $z=0.758$, and a third group with 10 members is at a higher redshift $z=0.818$.
 
-\textbf{B1600+434}: The lens is a nearly edge-on late-type galaxy (\cite{1997A&A...317L..39J}).
-No significant X-ray emission was detected from the surrounding group (\cite{2005ApJ...625..633D}).
-According to \cite{2007AJ....134..668A}, the lens lies in a group with at least seven members, which all seem to be late-type galaxies.
-The centroid of the group is not luminosity-weighted in the table.
-Time delay: $\Delta t_{AB}=51\pm2$ (\cite{2000ApJ...544..117B}; here BA-delay).
-\underline{TO DO}: No error on position estimate in paper?
---> What should the error estimate for the centroid be?
-Add environment image?
+\textit{B1600+434} (hereafter \textit{B1600} or \textit{1600}) is a nearly edge-on viewed late-type galaxy \citep{1997A&A...317L..39J}.
+The lens lies in a group with at least seven members, which all seem to be late-type galaxies \citep{2007AJ....134..668A}.
 
-\textbf{B1608+656}: The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}.
-All data points to a galaxy merger, so we could as well talk about 9 group members.
-A luminosity weighted measure was taken to find the group centroid.
-No errors are given, but as a comparision the median centroid is listed: $\Delta\alpha = 12.5$, $\Delta\delta = 21.6506$.
-Along the line of sight, there seem to be four other groups.
-No significant X-ray emission was detected from the surrounding group (\cite{2005ApJ...625..633D}).
-According to \cite{2003ApJ...584..100S} the galaxy G1 is an early-type galaxy which disrupted probably a late-type galaxy G2.
-Time delays: $\Delta t_{AB}=31.5^{+2}_{-1}$, $\Delta t_{CB}=36.0\pm1.5$, $\Delta t_{DB}=77.0^{+2}_{-1}$ (\cite{2002ApJ...581..823F}; here BA-, CA-, DA-delay).
-\underline{TO DO}: Errors?
-Add environment image?
+\textit{B1608+656} (hereafter \textit{B1608} or \textit{1608}) consists of two merging galaxies.
+The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
+The system has measured time delays \citep{2002ApJ...581..823F}.
+The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}.
+They find a group with 8 resp.
+9 members if the merging galaxies are counted as 2.
+No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
+Along the line of sight seem to be four other groups.
 
-\textbf{MG2016+112}: The environments were analyzed by \cite{2003MNRAS.344..337T}.
-They find a cluster-environment with photometrically 69 probable galaxies.
-Most galaxies are close to the lens and many lie in a south-east direction.
-It seems to be a giant elliptical (e.g.
-\cite{1984Sci...223...46L}, \cite{1986AJ.....91..991S}).
-\underline{TO DO}: Add environment image?
+\textit{MG2016+112} (hereafter \textit{MG2016} or \textit{2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
+It is the farthest lens we consider in this sample.
+It lies in a cluster which consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
+The clusters shows a high density of galaxies close to the lens in a south-east direction.
 
-\textbf{B2045+265}: To the west of the lens, \cite{1999AJ....117..658F} find that there may be galaxies in a group at the same redshift as the lens \cite{2007MNRAS.378..109M} find evidence for a dwarf satellite galaxy, which would be needed to be included in the analysis.
-Although \cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, \cite{2007MNRAS.378..109M} find that it is more probable to be an elliptical galaxy as the velocity dispersion is higher than the characteristic velocity dispersion.
-Furthermore, the source redshift is relatively low compared to the lens redshift, which requires the deflector to have a large dark matter halo.
-The galaxy is well fitted by a de Vaucouleurs profile.
-\underline{TO DO}: Add environment image?
-Get position of the group?
+\textit{B2045+265} (hereafter \textit{B2045} or \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
+\cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high.
+As the source redshift is rather low, a large lens mass is needed.
+\cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
+To the west of the lens, \cite{1999AJ....117..658F} find that a group at a similar redshift as the lens.
+\cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy.
+As the measurements are not conclusive, we chose to treat the lens as an isolated object.
 
-\textbf{HE2149-2745}: According to \cite{2007A&A...465...51E} the spectrum is typical for an early-type galaxy.
-Although initial redshift estimations of \cite{1996A&A...315L.405W} found a probable redshift rang of $\equiv0.2-0.5$ (also see \cite{2000ApJ...543..131K}).
-\cite{2002A&A...383...71B} find by cross-correlating the lens spectrum with a template spectrum of an elliptical galaxy that the redshift probably lies in the range $0.49\leq z \leq 0.60$.
-They then conclude that the most likely redshift is $z=0.495\pm0.01$.
-\cite{2007A&A...465...51E} however find, that it is more likely to be $z=0.603\pm0.001$.
-This would make the lens part of a group at this redshift found by \cite{2006ApJ...641..169M} of probably 3 other members (kinematically not confirmed).
-They also find 2 groups at lower redshifts.
-\cite{2006ApJ...646...85W} calculated a luminosity weighted centroid position.
-Time delay: $\Delta t_{BA}=103\pm12$ (\cite{2002A&A...383...71B}; here also BA-delay).
-\underline{TO DO}: Change redshift from 0.50 to 0.60 in the calculations.
+\textit{HE2149-2745} (hereafter \textit{HE2149} or \textit{2149}) is an early-type galaxy \citep{2007A&A...465...51E}.
+It has a measured time delay \citep{2002A&A...383...71B}.
+There is some uncertainty in estimating the lens' redshift.
+Initial estimates by \cite{1996A&A...315L.405W,2000ApJ...543..131K} found a probable redshift range of $\sim0.2-0.5$.
+By cross-correlating the lens spectrum with a template spectrum of an elliptical galaxy, \cite{2002A&A...383...71B} find that the redshift probably lies in the range $0.49\leq z \leq 0.60$, with the most likely redshift $z=0.495\pm0.01$.
+\cite{2007A&A...465...51E} however find that the redshift is more likely to be $z=0.603\pm0.001$.
+This would probably make the lens part of a poor group found by \cite{2006ApJ...641..169M} and \cite{2006ApJ...646...85W}.
+They also find two other groups at lower redshifts.
 
-\textbf{Q2237+030}: There seems to be no information available on the environment. According to \cite{1988AJ.....95.1331Y} the lens is a barred spiral.
+\textit{Q2237+030} (hereafter \textit{Q2237} or \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
+With only a redshift of $z=0.04$, it is the closest lens of the sample.
+Due to the low redshift, the probed physical scales are quite small.
+No further inquiries into the environment were made.
 
@@
 
-\section{Methods}
+\section{Method}\label{sec:method}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_a}
+  \caption{}
+  \label{fig:exampleplots1}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_b}
+  \caption{}
+  \label{fig:exampleplots2}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_c}
+  \caption{}
+  \label{fig:exampleplots3}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_d}
+  \caption{}
+  \label{fig:exampleplots4}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{PG1115}.
+The plots show the mean model of the generated ensemble of models.
+The coordinate system is centered on the lens galaxy.
+(a) shows the arrival time surface.
+The green dots are the images, the red curves are isochrones, and the black curve are the lemniscate resp.
+the lima\c{c}on.
+(b) shows the total matter distribution.
+The red circle marks the circle of the outermost image.
+The green resp.
+cyan ellipses mark the shape of the dark matter resp.
+stellar distribution.
+This shape is measured as described in Section 3.3.
+In this case, the shape of the total matter distribution (black) is indistinguishable from the dark matter distribution.
+(c) shows the dark matter distribution.
+The black lines show the median semi-major resp.
+semi-minor axis with 1$\sigma$- and 2$\sigma$- uncertainties.
+The solid pink line points to the group centroid with $1\sigma$-uncertainties (dashed).
+(d) shows the luminous matter distribution.}
+ \label{fig:exampleplots}
+\end{figure}
+
 \subsection{GLASS}
-\begin{itemize}
-\item Explain GLASS briefly
-\end{itemize}
 
-We use the new free-form lens modelling framework \textit{GLASS} (\cite{2012MNRAS.425.3077L}).
-As its predecessor \textit{PixeLens} (\cite{2004AJ....127.2604S}), it reconstructs a pixelated mass map of a lens reproducing the image positions perfectly.
-In this case, the arrival time surface for a source at position $\boldsymbol\theta_{S}$ taking the geometric and Shapiro contributions into account can be calculated using (\cite{1997MNRAS.292..148S})
-\begin{equation}
-\tau(\boldsymbol\theta)=\frac{1}{2}|\boldsymbol\theta |^{2}-\boldsymbol\theta\cdot\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\psi_{n}(\boldsymbol\theta),
+We use the new free-form lens modelling framework \textit{GLASS} \citep{2012MNRAS.425.3077L}.
+As its predecessor \textit{PixeLens} \citep{2004AJ....127.2604S}, it generates a pixelated mass map of a lens reproducing the image positions perfectly.
+Using pixels the arrival time surface for a source at position $\boldsymbol\theta_{S}$, taking the geometric and Shapiro contributions into account, can be expressed in terms of the surface mass density $\kappa_{n}$ of the n-th pixel rescaled by the critical density $\Sigma_{crit}$ and the contribution to the gravitational potential by this pixel $\psi_{n}$ \citep{1997MNRAS.292..148S}
+\begin{equation}\label{eq:arrival}
+\tau(\boldsymbol\theta)=\frac{1}{2}|\boldsymbol\theta |^{2}-\boldsymbol\theta\cdot\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\psi_{n}(\boldsymbol\theta).
 \end{equation}
-where $\kappa_{n}$ is the surface mass density in the n-th pixel rescaled by the critical density $\Sigma_{crit}$ and $\psi_{n}$ is the contribution to the gravitational potential by this pixel.
 
-According to Fermat's principle, lensed images appear where the arrival time surface takes on extremal values $\nabla\tau(\boldsymbol\theta)=0$. Thus we have to solve the following equation
+According to Fermat's principle, lensed images appear where the arrival time surface takes on extremal values $\nabla\tau(\boldsymbol\theta)=0$. Thus, the image positions fulfil
 \begin{equation}
@@
 where $\alpha_{n}$ is the contribution to the bending angle of the n-th pixel.
-Therefore, to reconstruct the lens, i.e.
-finding $\{\kappa_{n}\}$, this linear equation has to be solved.
-Additional constraints on the lens like individual time delays between images and all priors are also linear.
-The problem is highly underconstrained, so the solution domain is a high-dimensional polytope.
+For pixels, $\alpha_{n}$ and also $\psi_{n}$ can be described by analytic formulae \citep{1997MNRAS.292..148S}.
+Reconstructing the lens, i.e.
+describing the surface mass density in every pixel, reduces thus to finding sets of 'coefficients' $\left\{\kappa_{n}\right\}$ of these functions.
+As the number of pixels sets the resolution, this problem is however highly underconstrained.
+The number of pixels is typically $\gtrsim100$.
+The solution to this is noticing that the equation is linear in $\kappa_{n}$.
+Additional constraints on the lens such as individual time delays between images and their order and all the priors we impose are also linear.
+The solution space is thus a high-dimensional polytope.
 
-The dimension of the solution space usually exceeds $\gtrsim100$ why sophisticated sampling methods are required.
-Here \textit{GLASS} and \textit{PixeLens} differ.
+A difficulty in mass modelling is the nonuniqueness of solutions.
+They are not only not unique, every configuration which fulfils the equation is also equally probable.
+Therefore, this polytope needs to be sampled in a uniform way to analyze the full range of solutions.
+has Due to the high dimensionality, sophisticated sampling methods of such volumes are required.
+Here \textit{GLASS} and \textit{PixeLens} differ in the method they use.
 \cite{2008ApJ...679...17C} and \cite{2012MNRAS.425.3077L} show that \textit{PixeLens} does not produce uncorrelated random samples.
 They propose a new sampling algorithm.
-They prove that generic high-dimensional volumes indeed are sampled in a much more uniform way.
+They prove that generic high-dimensional polytopes indeed are sampled in a much more uniform way.
 Models in \textit{GLASS} are generated using a MCMC-method with a Metropolis-Hastings algorithm.
@@
 The estimation of the covariance matrix is refined in \textit{GLASS} such that models are much less correlated.
-Further details and tests of the method can be found in \cite{2012MNRAS.425.3077L} and (((citation needed of Jonathan's fake data paper))).
+Further details and tests of the method can be found in \cite{2012MNRAS.425.3077L}.
 
-Priors: Reference cosmology, chosen priors, etc.
+\subsection{Priors and assumptions}
+We use different priors and assumptions to eliminate unphysical mass reconstructions of the lens.
+First of all, the densities $\kappa_{n}$ need to be always positive.
+The density must always increase towards the center, why we chose to require the local density gradient in every pixel except the central one to point within an angle of $50^{\circ}$ towards the center.
+Also, the radial density profile has to decrease monotonically.
+
+To avoid large fluctuations in the density, we choose to add a smoothing prior.
+The density in any pixel except the central one is at most twice the average density of its neighboring pixels.
+If there is reason to expect an invariant distribution under a rotation by $180^{\circ}$ (e.g.
+for doubles), we impose such a symmetry prior.
+
+We also choose to include external shear. Thus, there is an additional term
+\begin{equation}
+  \gamma_{1}\left(\theta_{x}^{2}-\theta_{y}^{2}\right)+2\gamma_{2}\theta_{x}\theta_{y}
+\end{equation}
+in (\ref{eq:arrival}) and the subsequent equations.
+We allow $\gamma_{1}$ and $\gamma_{2}$ to vary, while fixing the maximum absolute value of the shear parameters.
+For doubles we fix the absolute value to be at most $10^{-2}$ (resp.
+$10^{-1}$ if no model could be generated for lower values).
+
+We further assume that we know the positions of the images and the lens perfectly.
+As the range of possible models is much larger than the errors on these quantities \citep{2006ApJ...650L..17S}, this assumption is justified.
+We also fix a time order of the images.
+Furthermore, we chose a flat concordance cosmology with $\Omega_{m}=0.28$, $\Omega_{\Lambda}=0.72$, and $H_{0}^{-1}=13.7$.
 
 \subsection{Shape measure}
-\begin{itemize}
-\item Explain shape measure
-\item Link to tests on fake data
-\item Include one plot of fake data test
-\end{itemize}
 
-To get a rough estimate of the shape we use the inverse of the moment of inertia tensor we can compute of the mass map.
+To get a rough estimate of the shape of the surface mass distribution we use the inverse of the moment of inertia tensor of the mass map.
 Its eigenvectors and eigenvalues track the shape of the mass distribution.
-This seemingly crude measure was tested on fake data.
+There are thus two quantities which define the shape, the ratio of the eigenvalues $\lambda_{1}/\lambda_{2}$, which describes the ellipticity, and the angle of the semi-major axis $\theta$.
+This seemingly crude measure was tested on fake data and found to be working well.
 
---- Need to expand ---
+Figure \ref{fig:exampleplots} shows example plots of the reconstruction of the lens \textit{PG1115}.
+They illustrate this shape measure.
+In this case, there is a significant misalignment between the two mass distributions.
+Also the uncertainties on the angle estimate are shown.
+Errors are purely statistical.
+Figure \ref{fig:exampleplots} also shows the arrival time surface and total, dark, and baryonic mass distributions.
 
-\section{Results}
-\begin{itemize}
-\item Show some examples (stellar and dm contour plots, image of lens, arrival time surface, included mass)
-\item Show money plots
-\item Comment on a few lenses
-\end{itemize}
+\section{Results}\label{sec:results}
 
-\section{Conclusion}
+\begin{figure}[t]
+ \begin{minipage}[t]{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/MisalignmentEnvironment/20130228_b}
+  \captionsetup{width=\linewidth}
+  \caption{Misalignment between stellar and dark matter distributions versus the ratio of dark matter mass and total mass included in the radius of the outermost image.
+As these angles are $\pi$-periodic, the absolute value of the difference ranges from 0 to $\frac{\pi}{2}$.
+Green squares are the lenses inside a group/cluster or that have a companion, red squares are without.}
+  \label{fig:misalignment}
+ \end{minipage}
+ \hfill
+ \begin{minipage}[t]{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/MisalignmentEnvironment/20130228_d}
+  \captionsetup{width=\linewidth}
+  \caption{Ellipticities of the stellar (stars) and dark matter (squares) distributions versus the ratio of dark matter mass and total mass included in the radius of the outermost image.
+Green squares are the lenses inside a group/cluster or that have a companion, red squares are without.}
+  \label{fig:ellipticities}
+ \end{minipage}
+\end{figure}
 
-\nocite{*}
+\begin{figure}[t]
+ \begin{minipage}[t]{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/MisalignmentEnvironment/20130228_e}
+  \captionsetup{width=\linewidth}
+  \caption{Misalignment between stellar and dark matter distributions versus the ellipticity of the dark matter halo.
+As these angles are $\pi$-periodic, the absolute value of the difference ranges from 0 to $\frac{\pi}{2}$.
+Green squares are the lenses inside a group/cluster or that have a companion, red squares are without.}
+  \label{fig:misalignmentellipticities}
+ \end{minipage}
+ \hfill
+ \begin{minipage}[t]{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/MisalignmentEnvironment/20130228_g}
+  \captionsetup{width=\linewidth}
+  \caption{Misalignment between the dark matter halo of lenses with known environment and the direction of the centroid resp.
+the companion galaxy versus the ratio of dark matter mass and total mass included in the radius of the outermost image.
+Although the angle of the semi-major axis is $\pi$-periodic, the direction of the centroid position is not.
+The absolute value of the difference ranges therefore from 0 to $\pi$.}
+  \label{fig:environment}
+ \end{minipage}
+\end{figure}
+
+\subsection{Lens Reconstruction}
+As it was not possible to reconstruct some lenses, we had to drop the lenses \textit{MG0414}, \textit{B0712}, \textit{B1422}, \textit{B1600}, \textit{B2045}.
+They will however be included in a future paper.
+The sample thus includes a total of 15 greavitational lenses.
+For every lens a total number of 10000 models were generated.
+This number we've chosen gives reasonable statistics, while not being computationally too expensive.
+
+In general an external shear of $\left|\gamma_{i}\right|\lesssim10^{-1}$ is required to model the lenses.
+\textit{RXJ0911}, \textit{B1608}, and \textit{MG2016} however need a significantly larger external shear of $\left|\gamma_{i}\right|\sim2\cdot10^{-1}$.
+This probably can be attributed to the cluster environment resp.
+the merging process in the system \textit{B1608}, which makes it hard to model.
+Furthermore, an external shear of at most $\left|\gamma_{i}\right|\lesssim10^{-1}$ is needed to be assumed to model \textit{SBS1520}.
+
+The masses $M_{dm}$ and $M_{tot}=M_{dm}+M_{stellar}$ we define in this analysis, are always the mass included up to the radius of the outermost image.
+Our mass modelling shows that \textit{BRI0952} \textit{B1608}, and \textit{Q2237} seem to have a significant amount of the total mass in baryonic mass.
+This can be explained for \textit{Q2237} and \textit{B1608}.
+Due to the galaxy merger, the outermost image for the lens \textit{B1608} includes mainly the central parts of the two galaxies.
+In \textit{Q2237} only the inner parts of the lens, where the baryonic mass dominates, are probed.
+Also the two very massive, very dark matter dominated lenses \textit{Q0957} and \textit{MG2016} should be mentioned.
+\textit{Q0957} is a cD-galaxy and \textit{MG2016} a giant elliptical, so this result was to be expected.
+
+Surprisingly, the shape measure we define yields results that are constrained quite well, as can be seen in Figures \ref{fig:exampleplots}, \ref{fig:47}-\ref{fig:2237}.
+The errors, which are purely statistical, on the ellipticities and the angles of the semi-major axis do not dominate the result.
+Lenses with almost spherical halos, i.e.
+$\lambda_{1}/\lambda_{2}\sim1$, should however be treated with caution.
+
+As mentioned in Section \ref{sec:data}, there are different time delay estimates for \textit{PG1115}.
+We find that the results do not change much when changing the time delays.
+As can be seen in Figure \ref{fig:exampleplots} resp.
+Figure \ref{fig:tsvetkova} and Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
+The misalignment we see is thus not affected by different time delays.
+
+The dark matter distribution in \textit{SBS1520} shows a very interesting behaviour.
+As can be seen in Figure \ref{fig:1520}, the dark matter seems to follow the baryonic mass distribution.
+Further out however, the dark matter distribution is rotated slightly.
+There is a significant misalignment between the dark matter distribution and the baryonic distribution.
+Without the central part, the misalignment would be even larger.
+This behaviour could be due to the potential disc \cite{2008ApJ...673..778A}, or caused by the many structures on the line of sight.
+
+\subsection{Misalignments between stellar and dark matter distributions}
+Figure \ref{fig:misalignment} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
+For lenses with a significant stellar component inside the outermost image radius, the distributions seem to be rather aligned.
+It seems that if the luminous mass is comparable to the dark matter mass, then the distributions align.
+For a smaller stellar contribution this is not necessarily the case.
+The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figures \ref{fig:exampleplots} or \ref{fig:tsvetkova})) and \textit{RXJ0911} (Figure \ref{fig:911}).
+While alignments between the distributions are preferred, they do not seem to be a necessary condition.
+
+The environment might also play a role.
+Red are the systems, which are isolated or no group resp.
+cluster environment has been found, green the ones in such an environment.
+The misaligned systems are mainly the lenses with a known environment.
+Therefore, this misalignment could be caused by the external effects.
+
+\subsection{Ellipticities of stellar and dark matter distributions}
+The ellipticities of the distributions versus the mass ratio are shown in Figure \ref{fig:ellipticities}.
+We see, that every dark matter halo has a lower ellipticity $\lambda_{1}/\lambda_{2}$ and is thus closer to sphericity than the luminous galaxy.
+The systems \textit{HE1104} (Figure \ref{fig:1104}) and \textit{MG2016} (Figure \ref{fig:2016}) show especially large differences.
+It is not clear what could cause these
+
+Figure \ref{fig:misalignmentellipticities} shows the misalignment versus the ellipticity of the dark matter halo.
+There seem to be five different regions.
+Almost spherical halos with good alignment of the semi-major axes, almost spherical halos with good alignment of semi-major and semi-minor axes (maximum misalignment between the semi-major axes), more elliptical, alligned halos, a seemingly 'forbidden' region for misalignments in between, and the upper right triangle, i.e.
+larger ellipticities and misalignments, which also seems forbidden.
+Understanding Figure \ref{fig:misalignmentellipticities} is certainly not trivial.
+Alignment with the semi-minor axis might be a stable configuration for almost spherical halos, while slightly smaller misalignments are unstable.
+There also seem to be some outliers as \textit{PG1115}, \textit{SBS1520}, and \textit{HE2149}.
+
+\subsection{Misalignments between the dark matter distributions and environment}
+Figure \ref{fig:environment} shows the misalignment between the direction to the group or cluster centroid resp.
+the companion galaxy with the dark matter halo.
+Although the error bars are huge, we immediately see that three lenses are basically aligned with the environment.
+The four other systems show slight misalignment.
+Having a closer look at these lenses shows however that at least two of them might in fact be aligned.
+For \textit{RXJ0911} and \textit{HE2149} there are no errors on the estimates of the centroid.
+Otherwise they would probably agree very well.
+\textit{Q0047} does not seem to be aligned with the direction of the group centroid.
+This could be due to the fact that the lens itself is quite far away from the centroid.
+The halo of \textit{B1030} is almost spherical, so the apparent misalignment could maybe be explained.
+It is also the only lens with only one companion galaxy.
+It is possible that in this case the effect of the environment is not strong enough.
+We however certainly lack data to make any claims for the systems with just one companion galaxy.
+Then, there is also \textit{MG2016}, which is not shown here, as the centroid was not measured in this cluster.
+There is however a high galaxy density towards the south-east, where also the cluster centroid probably lies.
+Judging from Figure \ref{fig:2016}, the halo seems to be aligned with the cluster centroid.
+
+We conclude that lenses in groups or cluster are maybe aligned with the centroid.
+However, as we lack the statistics and as the errors on the centroid positions are huge, this claim might be disproved.
+It is not possible at this point to make a similar statement for lenses with just one companion galaxy.
+
+\clearpage
+\section{Conclusion}\label{sec:conclusion}
+We used a nonparametric modelling method to reconstruct a total of 15 lenses.
+Using previously measured light maps, then converted to luminous mass maps \cite{leier11phd}, we were able to isolate the dark matter distribution.
+We used the eigenvalues and eigenvectors of the inverse of the moment of inertia tensor to characterize the shape of the light and mass distributions.
+This allowed us to analyze the alignment between these distributions and the relation between the ellipticities.
+Furthermore, we included environment information, which we related the to the misalignment.
+
+Our results can be summarized in the following way.
+If lenses lie in dense environments, mass and light need not be aligned.
+This might also be the case for lenses without known environments.
+We found more scatter than previous analyses by \cite{1997ApJ...482..604K}, \cite{2006ApJ...649..599K}, \cite{2009ApJ...690..670T}, and \cite{2012ApJ...761..170G} which all used SIEs mostly neglecting external shear to model the lenses.
+We also found that the semi-major and semi-minor axes of the distributions can be aligned, if the dark matter halos are close to sphericity.
+Up to our knowledge, this result was not obtained in other analyses.
+
+We found that dark matter halos are rounder than the luminous galaxies, i.e.
+they have a lower eigenvalue ratio $\lambda_{1}/\lambda_{2}$.
+Previous analyses found a correlation between the ellipticities \citep{2009ApJ...690..670T,2012ApJ...761..170G}, which we do not see.
+They also found a couple of cases, where the stellar distribution is more spherical than the dark matter halo.
+We claim that certain combinations of ellipticity of the dark matter halo and misalignment between light and mass seem to be forbidden.
+However, more lens systems are needed to support this claim.
+
+We suspect that the dark matter halo might be aligned with the centroid of the group or cluster it lies in.
+Due to the large uncertainties in the centroid positions however, such alignments might as well be coincidences.
+
+We want to stress again that the systems \textit{SBS1520} and \textit{PG1115}, which both show some misalignment and have time delay measurements, seem interesting enough to investigate further.
+In \textit{SBS1520} we found that the outer parts of the dark matter distribution is rotated respective to the central, which displays an interesting feature possibly due a disc.
+It is on the other hand a very complicated system with a lot of structures along the line of sight.
+\textit{PG1115} is easy to model, but still shows a clear misalignment.
+Thus, it could serve as a test for other methods that try to reproduce these misalignments.
+
+%\nocite{*}
 \bibliographystyle{mnras} % this is one type of author-year style
 \bibliography{thesis.bib} % this prints the bibliography section based on the \cite commands
+%\end{document}
+
+\clearpage
+\appendix
+\section{Reconstructed Lenses}\label{sec:reconstructions}
+
+The reconstructions that were used in the analysis are shown in Figures \ref{fig:47}-\ref{fig:2237}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0047/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0047/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0047/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0047/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{Q0047}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:47}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0142/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0142/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0142/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0142/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{Q0142}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:142}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0911/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0911/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0911/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0911/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{RXJ0911}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:911}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0952/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0952/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0952/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0952/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{BRI0952}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:952}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0957/Doubles/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0957/Doubles/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0957/Doubles/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/0957/Doubles/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{Q0957}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:957}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1009/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1009/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1009/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1009/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{LBQS1009}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:1009}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1030/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1030/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1030/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1030/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{B1030}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:1030}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1104/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1104/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1104/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1104/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{HE1104}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:1104}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Tsvetkova/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{PG1115} with time delays from \cite{2010MNRAS.406.2764T}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:tsvetkova}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Barkana/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Barkana/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Barkana/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1115/Barkana/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{PG1115} with time delays from \cite{1997ApJ...489...21B}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:barkana}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1152/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1152/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1152/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1152/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{B1152}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:1152}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1520/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1520/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1520/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1520/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{SBS1520}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:1520}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1608/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1608/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1608/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/1608/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{B1608}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:1608}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2016/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2016/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2016/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2016/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{MG2016}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:2016}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2149/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2149/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2149/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2149/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{HE2149}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:2149}
+\end{figure}
+
+\begin{figure}[ht!]
+ \centering
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2237/20130220_a}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2237/20130220_b}
+  \caption{}
+ \end{subfigure}
+
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2237/20130220_c}
+  \caption{}
+ \end{subfigure}
+ \begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{Plots/2237/20130220_d}
+  \caption{}
+ \end{subfigure}
+ \captionsetup{width=.93\textwidth}
+ \caption{Reconstruction of lens \textit{Q2237}. Analogous to Figure \ref{fig:exampleplots}.}
+ \label{fig:2237}
+\end{figure}
+
 \end{document}

### 2013-05-27 limits/ms.tex
Added back main results plot. Extended the vel. disp. plot to a larger radius.

@@
 case $\gamma=1$ this is the Hernquist profile.  The four combinations of
-profile indices are shown in \tabref{Lens profile params}.  Note that two of
+profile indices are shown in \tabref{mock galaxy params}.  Note that two of
 the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
@@
 $M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
-\label{Lens profile params}
+\label{mock galaxy params}
 \end{table}
@@
 The main results from modeling these different configuration are shown black in
-\figref{Test reconstructions}. Each subplot corresponds to a different galaxy and
+\figref{main results}. Each subplot corresponds to a different galaxy and
 the vertical axis shows the range of quality.  The quality of a
@@
 %
+
+\begin{figure}
+\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
+\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
+\caption{The main results showing the quality of model recovery. Each panel corresponds to 
+the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
+each panel are six groups of results for each of six lens morphologies. Each morphology
+considered the presence of time delays and a central image. The black markers are for tests
+that did not include the stellar mass as a lower bound constraint, while the red markers
+indicate where the stellar mass has been given.}
+\label{main results}
+\end{figure}
+
 \begin{figure}
@@
 between images. The axes are measure in arcseconds.}
-\label{Test reconstructions}
+\label{reconstruction}
 \end{figure}
@@
 
-%\section{Results} %--------------------------------------------------------------
-
-%\begin{figure}
-%\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
-%\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
-%\end{figure}
+\section{Results} %--------------------------------------------------------------
 

### 2013-05-28 limits/ms.tex
New text describing the features of Glass. Additional plotting macro.

@@
 }}%
+\newcommand\plotthree[3]{{%
+ \centering
+ \leavevmode
+ \columnwidth=.30\columnwidth
+ \includegraphics[width={\columnwidth}]{#1}%
+ \hfil
+ \includegraphics[width={\columnwidth}]{#2}%
+ \hfil
+ \includegraphics[width={\columnwidth}]{#3}%
+}}%
 
@@
 \PixeLens\ but completely rewritten in Python and C. The key improvements are:
+%
 \begin{enumerate}
+  \setcounter{enumi}{0}
   \item A modular framework allows new priors to be added and modified easily.
+\end{enumerate}
+%
+Each prior is a simple function that adds linear constraints that operate on either
+a single lens object or the entire ensemble of objects. \Glass\ comes with a number
+of useful priors, but a user can write their own in the input file.
+%
+\begin{enumerate}
+  \setcounter{enumi}{1}
   \item The basis functions approximating a model can be changed. 
+\end{enumerate}
+%
+\Glass\ currently describes the lens mass as a collection of pixels, but the code
+has been designed to support alternative methods. In particular, it is planned
+to develop a module using Bessel functions. This will require a new set of 
+priors that operate on these functions.
+%
+\begin{enumerate}
+  \setcounter{enumi}{2}
   \item Non-linear constraints can be imposed in an automated post-processing step. 
+\end{enumerate}
+%
+Once \Glass\ has generated an ensemble of models given the linear contraints, any number
+of post processing functions can be applied. Not only can these functions be used to
+derive new quanities from the mass models, they can also be used as a filter to 
+accept or reject a model based on some non-linear constraint. The plotting functions
+within \Glass\ will correctly display models that have been accepted or rejected.
+%
+\begin{enumerate}
+  \setcounter{enumi}{3}
   \item The central region can be have a higher resolution to capture steep models. 
+\end{enumerate}
+%
+By default, the mass distribution of the lens is described by uniform grid. However,
+in the central region of a lensing galaxy where the mass profile may rise steeply,
+a higher resolution can be specified that only applies to the inner pixels. These
+pixels are subdivided into a smaller grid.
+%
+\begin{enumerate}
+  \setcounter{enumi}{4}
   \item Stellar density can be used as an additional constraint.  
+\end{enumerate}
+%
+The mass in inner regions of galaxies is often dominanted by the stellar component
+which one can estimate using standard mass-to-light models. This data can be added
+to the potential as described later in \secref{stellar mass}. By using the stellar
+mass one can place a lower bound on the mass and help constrain the inner most
+mass profile.
+%
+\begin{enumerate}
+  \setcounter{enumi}{5}
   \item Point or extended mass objects can be placed in the field.
-  \item Additional levels of pixel refinement.
 \end{enumerate}
+%
+\PixeLens only allows for a shear term to be added to the potential (as shown
+later in \eqnref{shear}) to account for mass external to model region. This
+is useful to capture the gross effects of a distant neighbour. \Glass\ also
+has a shear term but additional allows for additional analytic potentials to
+be included. This can be used to model substructure or multiple neighbors close
+to the main lens. The substructure may have only a small effect if the lens is
+a single galaxy, but if the lens is group then a potential can be added for
+each of the galaxies.
+%
+\begin{enumerate}
+  \setcounter{enumi}{5}
+  \item A new uniform sampling algorithm for high dimensional spaces.
+\end{enumerate}
+%
 At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
@@
 \begin{equation}
+\label{shear}
 \gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
@@
 all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
-$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
+$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$. $\Rmap$ is the 2d projected radius used to generate the lens configurations.}
 \label{mock galaxy params}
@@
 \begin{figure}
-\plotone{cmp_simulations.pdf}
+\plotthree{MockGalProfile-a.pdf} {MockGalProfile-b.pdf} {MockGalProfile-c.pdf}
 \caption{
@@
 \textbf{(Middle)} 
-The radially averaged two-dimensional projected density in terms of the
-critical density for lensing. At $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
+The radially averaged two-dimensional projected density.
+The critical density for lensing at $z_L=0.31$ is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
 \textbf{(Right)}
@@
 \subsection{Stellar mass}
+\label{stellar mass}
 

### 2013-05-29 limits/ms.tex
Fixed a few typos.

@@
 %
-Once \Glass\ has generated an ensemble of models given the linear contraints, any number
+Once \Glass\ has generated an ensemble of models given the linear constraints, any number
 of post processing functions can be applied. Not only can these functions be used to
-derive new quanities from the mass models, they can also be used as a filter to 
+derive new quantities from the mass models, they can also be used as a filter to 
 accept or reject a model based on some non-linear constraint. The plotting functions
@@
 %
-The mass in inner regions of galaxies is often dominanted by the stellar component
+The mass in inner regions of galaxies is often dominated by the stellar component
 which one can estimate using standard mass-to-light models. This data can be added
@@
 %
-We can continue adding terms to account for assumed potentials or potentials
-induced from the presence of other galaxy in the field. If the stellar density
-has been estimated we can use this as a lower bound where the stellar potential
-is a known constant of the form \eqnref{discrete potential}.
+We can continue adding terms to account for other potentials. For instance,
+we may want to impose a base potential over the field, or add potentials
+from the presence of other galaxies in the field. \Glass\
+already includes potentials for a point mass or an exponential form, but custom
+potentials are straightforward to add and can be included directly in the input file.
+If the stellar density has been estimated we can use this as a lower bound
+where the stellar potential is a known constant of the form \eqnref{discrete
+potential}.
+
 %
@@
 on the density even so much as to ensure that it is non-negative everywhere. We
-must therefore provide additonal linear constraints so that we only sample
+must therefore provide additional linear constraints so that we only sample
 physical models. The explicit implementation for these priors has been
-explained in \cite{}, be can be summarized as
+explained in \cite{}, but can be summarized as
 \begin{enumerate}
@@
 particles are first projected onto a very high resolution grid representing the
-lens plane. The centers of each of the grid cells are mapped back onto the
-source plane using \eqnref{lensing equation}. If the location on the source
-plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
-point on the image plane is accepted and further refined using a root finding
-algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
-converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
-Care must be taken that the grid resolution is high enough that the resulting
-image position error is below the equivalent observational error. Time delays
-are then calculated in order from the arrival time at each image (\eqnref{tau}).
+lens plane. The centers $\vec\theta_i$ of each of the grid cells are mapped
+back onto the source plane using \eqnref{lensing equation}. If the location on
+the source plane $\vec\beta_i$ is within a user specified
+$\eps_\mathrm{accept}$ of $\vec\beta$ then $\vec\theta_i$ is 
+accepted and further refined using a root finding algorithm until the distance
+to $\vec\beta$ is nearly zero. If multiple points converge to an
+$\eps_\mathrm{root}$ of each other then only one point is taken.  Care must be
+taken that the grid resolution is high enough that the resulting image position
+error is below the equivalent observational error. Time delays are then
+calculated in order from the arrival time at each image (\eqnref{tau}).
 
 \section{Parameter study}
+
+We now present a study of four mock galaxies with known analytic forms to
+confirm that \Glass is able to correclty recover the mass profile.
 
@@
 \plotthree{MockGalProfile-a.pdf} {MockGalProfile-b.pdf} {MockGalProfile-c.pdf}
+%\plotone{MockGalProfile-a.pdf} \plotone{MockGalProfile-b.pdf} \plotone{MockGalProfile-c.pdf}
 \caption{
@@
 \item One quad and one extended quad.
-\item Three 2-source quads with varying redshift contrast.
+\item Two 2-source quads with varying redshift contrast.
 \end{enumerate}
@@
 \plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
+
 \plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}

### 2013-06-09 limits/skeleton.tex
skeleton of GLASS paper

--- 2013-05-27 limits/ms.tex
@@
-\documentclass[onecolumn,galley]{mn2e}
-%\documentclass[twocolumn,galley]{mn2e}
-%\documentclass[onecolumn,galley,draft]{mn2e}
-%\usepackage{myaasmacros}
+\documentclass[usenatbib,onecolumn,galley]{mn2e}
+\usepackage{graphicx}
+\usepackage{amsmath}
 \usepackage{mathrsfs}
-\usepackage{amsmath}
-\usepackage{graphicx}
 
@@
 \newcommand{\eps}{\ensuremath{\varepsilon}}
-
 \newcommand{\Eavg}{\ensuremath{\langle \E \rangle}}
-
 \newcommand{\kpc}{\ensuremath{\mathrm{kpc}}}
@@
 
-% From aastex.cls
-\newcommand\plotone[1]{%
- \centering
- \leavevmode
- \includegraphics[width={\columnwidth}]{#1}%
-}%
-\newcommand\plottwo[2]{{%
- \centering
- \leavevmode
- \columnwidth=.45\columnwidth
- \includegraphics[width={\columnwidth}]{#1}%
- \hfil
- \includegraphics[width={\columnwidth}]{#2}%
-}}%
-
-%\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
-\title[GLASS]{Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework}
+\title{Gravitational-Lens Recovery with GLASS}
 \author{%
@@
 
-%\tableofcontents
-
 \begin{abstract}
-We show the effectiveness of reconstructing the mass distribution of four mock galaxies using
-a range of strong gravitational lensing assumptions. In particular, we study
-the affects of the lens morphology (double or quad) with and without a central
-image, angular image distribution, and red shift contrast between two sources.
-The lens modeling is performed using a new free-form framework called \Glass.
-We conclude that \dots
-%1) Time delays are unnecessary with strong red shift contrast,
-%2)
-
-%We study the effectiveness of a variety of strong lensing scenarios to inform
-%the reconstruction of four simulated triaxial halos with stellar and dark
-%matter components. We conclude that 
-%1) lenses with multiple sources and high redshift contrast perform very well
-%2) lenses where the images are already probing the stellar dominated region 
-%   of a galaxy can be constrained by an estimate of the stellar mass and
-%   suggest the fraction of dark matter
-%3) if velocity dispersion measurements are to be used then a sufficiently large aperture 
-%   is necessary
-%4) lensing can be used to infer the velocity anisotropy.
-%We also introduce GLASS, an extensible framework for lens modeling and analysis.
-
-%We attempt to reconstruct the mass profile and distribution of a dark and
-%stellar matter triaxial halo using a variety of strong lens configurations,
-%stellar mass estimates, and stellar velocity dispersions. The lens
-%configurations test quads with small to large image separations (radial
-%sampling), extended source information ranging from point images to Einstein
-%rings (angular sampling), and multiple sources located at the same and
-%differing redshifts (redshift contrast).
-
-%We conclude that redshift contrast can significantly constrain the mass
-%profiles.  Stellar mass estimates can also lead to better reconstructions by
-%placing lower bounds on the mass distribution in the inner regions of galaxies.
-%Velocity dispersions alone are unlikely to usefully constrain the profile
-%because the profile is highly sensitive to the dispersion measurement.  
-%Combined with other techniques, however, velocity dispersions can help to
-%constrain the range of possible reconstructed solutions. We also introduce
-%GLASS, an extensible framework for lens modeling and analysis.  
 \end{abstract}
@@
 
-To date only about 400 strong lenses are known, but within the next ten years
-new surveys will discover thousands of gravitational lenses. The SKA estimates
-that after its start in 2020 about 10,000 lenses will be found. The LSST
-expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or
-quasar lenses after 2022.
+\section{GLASS}
 
-A typical lens, where only the measured observables are the image positions,
-can been used to estimate the total mass of a galaxy including parts of the
-dark matter halo. The enclosed mass inside the Einstein radius is simple to
-calculate and quite robust given the observed image positions. The exact mass
-distribution is more difficult to determine, however, as there are typically
-not enough constraints on the mass profile. The known degeneracies have been
-discussed at length in the literature. At the very least, one would like to
-have a measure of the enclosed mass at two distinct radii to be able
-to properly distinguish between analytic mass models. 
-%This would break the steepness degeneracy, also known as the mass sheet degeneracy.
+Extensible framework, with some new features: (i) sampling algorithm
+from \cite{2012MNRAS.425.3077L}, (ii) stellar mass as lower limit,
+(iii) central high-resolution region, (iv) post-processing using
+kinematics.
 
-Lensing is not the only technique that can measure enclosed mass. The enclosed
-mass can also be estimated from stellar velocity dispersions. If the radius
-from this measurement is sufficiently different from the Einstein radius, then
-combining this measurement with lensing provides the necessary constraint.
-Another solution is to find a galaxy that is lensing two sources. The images
-from each source provide an enclosed mass. The extent to which the radii
-differ is dependent upon the redshifts of the two sources: the larger the
-redshift difference the larger the radial separation.
-
-Lensing is known to be sensitive to cosmology and, in principle, can be used to
-estimate such quantities as the Hubble constant $H_0$ when the lens has
-measurable time delays. However, due to strong degeneracies such as the
-steepness degeneracy there is often little one can learn from a single lens. 
-In this case, one is free to change the mass and $H_0$ while keeping
-all observables fixed. A single lens can say almost nothing about the actual
-value of $H_0$. However, it has been shown that combining modeling results
-of several strong lenses with time delays can significantly reduce the allowed
-values and provides a measure to within 10 percent \cite{}.
-
-If one assumes a Hubble constant $H_0$ and time delays have been observed for a
-lens this will break the steepness degeneracy but will not help in
-constraining the mass profile at two radii.  One can choose to postpone this
-problem and simply fit models to the given data.  The earliest examples were
-singular isothermal sphere (SIS) or elliptical (SIE) models but have since
-evolved to multi-component models include separate models for the stars and
-dark matter. Other methods that do not ignore this problem use genetic
-algorithms or linear programming to explore the large space of solutions.
-
-Despite such difficulties lensing is a direct probe of the gravitating mass in
-a halo and there are a number of open problems in galaxy formation that lensing
-can help address. For instance, the debate remains as to what form the inner
-slope of the density profile takes. Numerical simulations of dark matter
-suggest a cusp, while observations from lensing and stellar dynamics suggest
-cores. This may, however, be only a matter of scale, as both theory and
-observations agree that clusters have cuspy profiles.
-
-Lensing may also be useful in measuring possible adiabatic contraction of the 
-dark matter halo due to the central stars in a galaxy. For this, one needs
-high resolution mass models of the stellar profile combined with accurate models
-of the total mass. Indeed, with such models, one may also improve the statistics
-of the dark matter fraction in a galaxies over many different mass scales.
-
-These open problems suggest what kind of lensing data will be required in the
-future.  Future surveys will provide many lenses but time delays will require a
-long follow up. Stellar mass maps, however, take a known, fixed observation
-time and can be performed for many lenses. It will be important not only to
-measure the stellar velocity dispersion at an arbitrary radius, but to ensure
-that the measurement is taken at a radius different to the Einstein radius.
-For the radio surveys like SKA it will be important to detect the central image
-of the lens. This can provide mass information all the way to the center of the
-galaxy.
-
-In this paper we perform a parameter study using four mock galaxies that differ
-in their dark matter and stellar profiles. We consider double and quad lensing
-morphologies, time delays, the presence of a central image, red shift contrast
-between multiple sources, and image configuration.  We also consider the
-effects of adding stellar mass models as lower bound constraints on the mass
-distribution.  The modeling and analysis is performed using a new free form
-lens modeling framework called \Glass.
-
-We first review the basic lensing theory we will need and then describe how
-\Glass is used to generate lensing models. The mock data and how it was
-generated is described in \secref{}. In section{} we discuss the lensing
-configurations in the parameter study and present some example output. Our
-finals results are presented in \secref{}.
-
-%\subsection{Future} %-----------------------------------------------------------
-    %\begin{itemize}
-    %\item New satellites will find many new lenses.
-    %\item LSST, DES, PanSTARRS?, SKA
-    %\item What is the most important data to have?
-    %\end{itemize}
-
-%\subsection{Present} %----------------------------------------------------------
-%    \begin{itemize}
-%    \item SLACS, CASTLES, CosmoGrail, CLASS, CFHTLS, SNAP?
-%    \end{itemize}
-
-%\subsection{Why do we need accurate galaxy models?} %---------------------------
-    %\begin{itemize}
-    %\item Galaxy formation
-    %\item Cusp/Core problem
-    %\item Universal halos?
-    %\item Adiabatic contraction
-    %\item DM fraction
-    %\end{itemize}
-
-%\subsection{Past work on constraining profiles.} %------------------------------
-    %\begin{itemize}
-    %\item Much of the early literature used simple SIS and SIE parametric models. Understandable.
-    %\item Bayesian model fitting
-    %\item Free-form modeling
-    %\item Keeton has a good review.
-    %\end{itemize}
-
-%\subsection{What are the problems?} %------------------------------
-    %\begin{itemize}
-    %\item Very little data per lens.
-    %\item Several well-known degeneracies.
-    %\item Velocity dispersions: aperture too small
-    %\end{itemize}
-
-%\subsection{Goals of the paper} %------------------------------
-%    \begin{itemize}
-%    \item Perform a parameter study over lens morphologies and quantify what they can tell us about profiles.
-%    \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Theoretical Background}
-
-\subsection{Lensing}
-
-The lensing equation
-%
 \begin{equation}
-\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
+\vec\beta = \vec\theta - \frac{D_{LS}}{D_S} \times \frac{4GD_L}{c^2}
+\int \Sigma(\vec\theta')
+\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}
+d^2\vec\theta'
 \label{lensing equation}
 \end{equation}
-%
-maps an observed image position $\vec\theta$ to a source position $\vec\beta$
-via the correction factor 
-%
+
 \begin{equation}
-\vec\alpha(\vec\theta) = \frac{4GD_L}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
-\end{equation}
-%
-which accounts for the gravitational lensing effect of an intervening mass. For
-our purposes we make use of the thin mass sheet approximation and assume that
-the lensing mass is infinitely thin compared with the distance between the
-source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These
-distances are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
-a dimensionless number that depends on cosmology.  The lens can then be thought
-of as a projected surface density $\Sigma$ which diverts the path of a photon
-instantaneously through the bending angle $\vec\alpha$.
-
-Since we will later want to model the density distribution with a computer it will
-be convenient to choose units that make the relevant quantities of order unity.
-We therefore measure lengths in light years, time in years, positions in
-arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
-arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to 
-define a proxy to the Hubble constant $\nu \equiv N^2 H_0$.
-
-The arrival (or travel) time $t$ of a photon depends not only on the geometric
-path it takes, but also on the general relativistic gravitational time dilation
-due to the lens at a redshift of $z_L$.  In its complete form, with all units
-and cosmology included we can write the arrival time as
-%
-\begin{equation}
-N^2ct(\vec\theta) = (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
+\frac{ct(\vec\theta)}{(1+z_L)D_{L}} =
+\frac{D_{S}}{D_{LS}} \times {\textstyle\frac12} |\vec\theta - \vec\beta|^2
+- \frac{4GD_{L}}{c^2}
+\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
 \label{full arrival time}
 \end{equation}
-%
-The non-standard factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
-has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
-delay 
-%
 \begin{equation}
-\tau = \left[(1+z_L)D_{L}\right]^{-1}ctN^2 = \left[ (1+z_L) \frac{c}{H_0}d_L\right]^{-1}ctN^2 = \left[ (1+z_L) d_L\right]^{-1}\nu t
-\label{tau}
-\end{equation}
-%
-in terms of our previous definitions. If we
-further define a dimensionless density
-%
-\begin{equation}
-\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
-              = \frac{d_L}{\nu}\Sigma
-\end{equation}
-%
-and a lensing potential
-%
-\begin{equation}
-\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
-\label{lensing potential}
-\end{equation}
-%
-we can express \eqnref{full arrival time} very compactly as
-%
-\begin{equation}
-\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
-\label{arrival time}
-\end{equation}
-%
-where $\xi \equiv D_{S}/D_{LS}$. We explicitly write $\kappa_\infty$ to remind ourselves
-that there is no source distance factor involved. This will be useful later when we consider
-multiple sources.
-
-If we think of $\tau$ as a surface then images will be observed where ever
-$\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
-extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation} or
-\begin{equation}
-  \xi \vec\beta = \xi \vec\theta - \frac 1\pi\int \kappa_\infty\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
+D_L, D_S, D_{LS} \propto \frac c{H_0}
 \end{equation}
 
-The only observables from \eqnref{arrival time} are the image positions, and
-perhaps the stellar contribution to $\kappa_\infty$.  If the source object is
-variable, however, then the observed light curves of each image will be
-identical, but possibly shifted in time due to the different arrival times.
-The time difference between identical portions of the light curves is called
-the time delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
-$\Delta t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where $\vec\theta_2$
-arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
-\nu$. If $\beta$ and $\kappa_\infty$ were known exactly this would allow one
-to precisely infer the Hubble constant. However, the source position is not
-observable and the density distribution is highly degenerate.
+\section{Simulated Lenses}
 
-\subsection{Degeneracies} %-----------------------------------------------------
-
-\begin{itemize}
-  \item Steepness
-  \item Shape
-  \item $H_0$
-  \item Rings
-  \item Cosmology
-\end{itemize}
-
-%
-%The steepness degeneracy arbitrarily rescales the arrival time surface. Image
-%positions are left alone but the density profile will become shallower or
-%steeper. This is particularly bad for inferring the Hubble constant, as the
-%lens profile will tend to become steeper for larger values of $H_0$.
-%
-%Other degeneracies include ring degeneracies, where one is allowed to build
-%up a density distribution as a series of mass rings; the presence of substructure;
-%and the effects of merging galaxies. 
-%
-%Shape degeneracy---a twisting in the density.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Methods}
-
-\subsection{A new lens modeling framework: \Glass}
-
-\Glass\ is an evolution of the concepts employed by the free form modeling tool
-\PixeLens\ but completely rewritten in Python and C. The key improvements are:
-\begin{enumerate}
-  \item A modular framework allows new priors to be added and modified easily.
-  \item The basis functions approximating a model can be changed. 
-  \item Non-linear constraints can be imposed in an automated post-processing step. 
-  \item The central region can be have a higher resolution to capture steep models. 
-  \item Stellar density can be used as an additional constraint.  
-  \item Point or extended mass objects can be placed in the field.
-  \item Additional levels of pixel refinement.
-\end{enumerate}
-At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
-linear space that represents the modeling solution space. This algorithm was
-described and tested in \cite{}. \Glass\ is also multi-threaded allowing it to
-run efficiently on many-cored machines.  The software is freely available for
-download. One interesting aspect is that the input files are themselves Python
-programs. This allows a large amount of sophistication in setting up a lens at
-runtime and also allows \Glass\ to be used as an external library from another
-user written program.
-
-\subsection{Discrete models}
-
-For this paper we will restrict ourselves to using the pixelated basis set that
-has been employed in previous work and is implemented in \PixeLens. Here we
-will briefly review the main ideas. The algorithm for generating models in
-\Glass\ samples a convex polytope in a high dimensional space whose interior
-points are solutions to the lensing equation and satisfy other physically
-motivated linear priors (the sampling algorithm in \Glass\ is not the same as
-employed in \PixeLens).  We therefore formulate all of our equations as
-equations linear in the unknowns. We describe the density distribution $\kappa$
-as a set of discrete grid cells or pixels $\kappa_i$ and rewrite the potential
-(\eqnref{lensing potential}) as
-%
+Triaxial models with stars and dark matter.
 \begin{equation}
-  \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
-  \label{discrete potential}
-\end{equation}
-%
-where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
-over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
-We can find the discretized lens equation by simply taking the gradient of the
-above equations.
-
-The pixels only cover a finite circular area with physical radius $\Rmap$ and
-pixel radius $\Rpix$ centered on the lensing galaxy. To account for any global
-shearing outside this region from, e.g., a neighboring galaxy, we also add to
-\eqnref{discrete potential} two shearing terms
-%
-\begin{equation}
-\gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
-\end{equation}
-%
-We can continue adding terms to account for assumed potentials or potentials
-induced from the presence of other galaxy in the field. If the stellar density
-has been estimated we can use this as a lower bound where the stellar potential
-is a known constant of the form \eqnref{discrete potential}.
-%
-%\begin{equation}
-  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
-%\end{equation}
-%
-
-Unfortunately, the lens equation and the arrival times alone are not enough to form a
-closed volume in the solution space. We have not imposed any strong constraints
-on the density even so much as to ensure that it is non-negative everywhere. We
-must therefore provide additonal linear constraints so that we only sample
-physical models. The explicit implementation for these priors has been
-explained in \cite{}, be can be summarized as
-\begin{enumerate}
-\item The density must be non-negative everywhere.
-\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
-\item The local gradient everywhere must point within $45^{\circ}$ of the center.
-\item Density variations must be smooth.
-\item Image parity is enforced.
-\item The density is radially symmetric. (Optional)
-\end{enumerate}
-
-In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
-\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
-solution space polytope. Using the MCMC sampling strategy described in \cite{}
-we uniformly sample this space. Collectively, the sampled models are referred
-to as an ensemble $\E = \{\M_i\}$, where we usually generate $\sim$1000 models. We
-will typically show the ensemble average $\Eavg$ in the plots to
-follow.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Raytracing}
-\label{Raytracing}
-\Glass\ can also determine the position of images and time delays from 
-particle-based simulation output given a source position $\vec\beta$. This is
-used to generate the lens configurations used in the parameter study.  The
-particles are first projected onto a very high resolution grid representing the
-lens plane. The centers of each of the grid cells are mapped back onto the
-source plane using \eqnref{lensing equation}. If the location on the source
-plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
-point on the image plane is accepted and further refined using a root finding
-algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
-converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
-Care must be taken that the grid resolution is high enough that the resulting
-image position error is below the equivalent observational error. Time delays
-are then calculated in order from the arrival time at each image (\eqnref{tau}).
-
-\section{Parameter study}
-
-\subsection{Mock galaxy data}
-
-The four mock galaxies we consider have been designed to test our recovery
-procedure. They are two component models where the dark matter and stellar
-profiles are allowed to be steep and shallow.  The enclosed mass in all cases
-is fixed at $M(a_\star)= 1.8\e{10}$ at the scale radius $a_\star=2$ kpc. These
-values were chosen to closely resemble B1115. We therefore place the galaxy at
-a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
-where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
-critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
-
-The galaxies were
-first generated as three dimensional particle distributions with the
-tool DEHNEN-TOOL. Each component follows the profile
-\begin{equation}
-\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
+\rho(r) = \frac{M}{4\pi a^3}(3-\gamma)
+\left(\frac ra\right)^{-\gamma}\left(1 + \frac ra\right)^{\gamma-4}
 \label{Dehnen profile}
 \end{equation}
-where $\gamma$ is the profile index and $a$ is the scale radius.  In the
-case $\gamma=1$ this is the Hernquist profile.  The four combinations of
-profile indices are shown in \tabref{mock galaxy params}.  Note that two of
-the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
-more accurate approximation would be an NFW or Einasto profile we are not
-probing the outer regions of the halo where the difference would be most
-extreme.  The Hernquist profile is easier to generate as it has finite mass.
+Steep and shallow light, steep and shallow dark-matter: \tabref{mock
+  galaxy params} and \figref{mock galaxies}.
 
 \begin{table}
+\begin{center}
 \begin{tabular}{cllllllll}
@@
 \end{tabular}
+\end{center}
 \caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
@@
 \begin{figure}
-\plotone{cmp_simulations.pdf}
-\caption{
-\textbf{(Left)} 
-Three-dimensional density of the galaxies showing the stellar, dark matter,
-and total densities with dotted, dashed, and solid lines, respectively. The
-grey lines show the analytic forms from \eqnref{Dehnen profile}. 
-\textbf{(Middle)} 
-The radially averaged two-dimensional projected density in terms of the
-critical density for lensing. At $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
-\textbf{(Right)}
-The enclosed projected mass.
-}
+\begin{center}
+\includegraphics[width=.5\columnwidth]{MockGalProfile-a.pdf}
+\end{center}
+\caption{Three-dimensional density of the galaxies showing the
+  stellar, dark matter, and total densities with dotted, dashed, and
+  solid lines, respectively.}
 \label{mock galaxies}
@@
 
-In \figref{mock galaxies} we show the 3D radial density, 
-the 2D projected density, and the 2D enclosed mass for each
-galaxy. Solid lines represent the total mass, dashed lines the dark 
-matter, and dotted lines the stellar mass. The projected plot has
-been normalized to the critical density.
-
-\subsection{Lens configurations} %--------------------------------------------------------------
-
-For each of the four galaxies, we used the raytracing feature of \Glass\
-described in \secref{Raytracing} to construct 12 lensing scenarios:
-
-\begin{enumerate}
-\item One double and one extended double.
-\item One quad and one extended quad.
-\item Three 2-source quads with varying redshift contrast.
-\end{enumerate}
-
-The extended configurations use extra sources to generate extra images that
-simulate an arc. \figref{config ex.} shows the configuration for the extended
-quad.
-
-Each of these configurations were modeled with and without time delays and with
-and without a central image. We assumed for all our tests that the lensing mass
-was radially symmetric. By construction, this is known to be true and this is
-most often the case with real galaxies, unless there is an obvious observed
-asymmetry. The central pixel was refined into a further nine pixels to capture
-any steep rise in the profile. Two of the four mock galaxies have a steeply rising
-inner profile.
-
-\figref{reconstruction} shows a typical reconstruction of a
-lens. The far left plot shows the ensemble average arrival time surface with
-image marked as circles and the inferred source position as a diamond. The
-center plot shows the radial density profile. The error bars cover the full
-range of models generated by \Glass. The true density profile from the mock
-data is also plotted for comparison. The vertical lines mark the radial
-position of the images. The final plot on the right is of the enclosed mass. As
-expected the error bars are smallest in the region of the images where the most
-information about the lens is present. The dip in the profile at the end of the
-profile is due to the cut off in mass in the lensing map. This is of little
-importance, though, as there is no lensing information there.
+Then project galaxies to get lenses, \figref{mock lenses}.
 
 \begin{figure}
-%\plotone{AAZContrastR1R5_Tm.pdf}
-\plotone{BCQuadR1a_TmS.pdf}
-\caption{A typical reconstructed lens. Here we present a single quad lens from 
-the BC mock galaxy.
-\textbf{(Left)}
-The arrival time surface. 
-\textbf{(Middle)}
-The surface density. The magenta curve represents the dark matter component,
-the yellow curve the stellar component, and the blue curve is the sum of the two.
-The black curve comes from the original mass model used to create the lens.
-The green vertical lines mark the radial positions of the images. The higher
-resolution feature of \Glass\ has been used on the central pixel allowing the
-steep profile to be captured.
-\textbf{(Right)}
-The cumulative mass.}
+\begin{center}
+\includegraphics[width=.5\columnwidth]{MockGalProfile-b.pdf}\break
+\includegraphics[width=.5\columnwidth]{MockGalProfile-c.pdf}
+\end{center}
+\caption{The radially averaged two-dimensional projected density and
+  enclosed mass.  The critical density for lensing at $z_L=0.31$ is
+  $\Sigma_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.}
+\label{mock lenses}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=.8\columnwidth]{BCarrival_surfaces}
+\end{center}
+\caption{The lens configurations for the six test cases using the BC
+  mock galaxy.}
+%  Here, the central image is shown, although not all
+% tests include it. The central image belongs to only one set of
+% images to avoid overconstraining the models. Similar colors group
+% imagethat share a common source. In the case of the extended image
+% systems the source is at the same redshift, while the redshift is
+% varied between the systems in the ZConstrast cases. Grey circles are
+% a visual aid to help determine radial separation between images. The
+% axes are measure in arcseconds.}
 \label{reconstruction}
@@
 
-The main results from modeling these different configuration are shown black in
-\figref{main results}. Each subplot corresponds to a different galaxy and
-the vertical axis shows the range of quality.  The quality of a
-model $\M_i$ by comparing the recovered density profile $\rho_\M(r)$ against
-the profile of the mock galaxy $\rho_G(r)$.  In particular, the plots show the
-RMS quantity
-%
-\begin{equation}
-  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
-  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
-\end{equation}
-%
+Convergence test for ray-tracing, \figref{raytracing convergence
+  tests}.
 
 \begin{figure}
-\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
-\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
-\caption{The main results showing the quality of model recovery. Each panel corresponds to 
-the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
-each panel are six groups of results for each of six lens morphologies. Each morphology
-considered the presence of time delays and a central image. The black markers are for tests
-that did not include the stellar mass as a lower bound constraint, while the red markers
-indicate where the stellar mass has been given.}
+\begin{center}
+\includegraphics[width=.4\columnwidth]{tdconv_pr45.pdf}\hfil
+\includegraphics[width=.4\columnwidth]{imgpos_conv_mr20.pdf}
+\end{center}
+\caption{(left) Test for predicted time delay convergence as $\Rmap$
+  changes.  $\Rpix=45$. After about $\Rmap=20$ most of the asymmetric
+  mass is in the map.  (right) Test for predicted image position
+  $\theta$ convergence as $\Rpix$ changes. $\Rmap=20$ arcsec.}
+\label{raytracing convergence tests}
+\end{figure}
+
+\section{Mass reconstruction}
+
+Reconstruct lenses \figref{reconstruction}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=.3\columnwidth]{BCQuadR1a_TmS-a.pdf}\hfil
+\includegraphics[width=.3\columnwidth]{BCQuadR1a_TmS-b.pdf}\hfil
+\includegraphics[width=.3\columnwidth]{BCQuadR1a_TmS-c.pdf}
+\end{center}
+\caption{A typical reconstructed lens.}
+% Here we present a single quad
+%   lens from the BC mock galaxy.  \textbf{(Left)} The arrival time
+%   surface.  \textbf{(Middle)} The surface density. The magenta curve
+%   represents the dark matter component, the yellow curve the stellar
+%   component, and the blue curve is the sum of the two.  The black
+%   curve comes from the original mass model used to create the lens.
+%   The green vertical lines mark the radial positions of the
+%   images. The higher resolution feature of \Glass\ has been used on
+%   the central pixel allowing the steep profile to be captured.
+%   \textbf{(Right)} The cumulative mass.}
+\label{reconstruction}
+\end{figure}
+
+Quantify errors
+\begin{equation}
+\chi = \left(\frac
+       {\Big\langle \int \left|\Delta\Sigma(\vec{\theta})\right|^2 \,
+        d^2 \vec{\theta} \Big\rangle}
+       {\int \Sigma^2(\vec{\theta}) \; d^2 \vec{\theta}}
+       \right)^{1/2}
+\end{equation}
+and draw them, \figref{main results}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=.4\columnwidth]{AAchi2_profile.pdf}\hfil
+\includegraphics[width=.4\columnwidth]{BBchi2_profile.pdf}
+\includegraphics[width=.4\columnwidth]{ACchi2_profile.pdf}\hfil
+\includegraphics[width=.4\columnwidth]{BCchi2_profile.pdf}
+\end{center}
+\caption{The main results showing the quality of model recovery. Each
+  panel corresponds to the named mock galaxy, whose parameters are
+  listed in \tabref{mock galaxy params}. Within each panel are six
+  groups of results for each of six lens morphologies. Each morphology
+  considered the presence of time delays and a central image. The
+  black markers are for tests that did not include the stellar mass as
+  a lower bound constraint, while the red markers indicate where the
+  stellar mass has been given.}
 \label{main results}
@@
 
-\begin{figure}
-%\plotone{AAarrival_surfaces}
-%\plotone{BBarrival_surfaces}
-\plotone{BCarrival_surfaces}
-\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
-the central image is shown, although not all tests include it. The central image belongs
-to only one set of images to avoid overconstraining the models. Similar colors group
-images that share a common source. In the case of the extended image systems the source
-is at the same redshift, while the redshift is varied between the systems in the 
-ZConstrast cases. Grey circles are a visual aid to help determine radial separation
-between images. The axes are measure in arcseconds.}
-\label{reconstruction}
-\end{figure}
+\section{Kinematics}
 
-The morphological complexity increases from left to right within each plot. As
-a result, there is a general trend for the reconstruction quality to increase
-(and for $\chi$ to decrease). By adding more measurable information to each
-configuration the quality can also be affected. When both time delays and a
-central image are present the quality is highest. A double is known to provide
-very little constraint on the mass distribution. This is particular evident in
-galaxies AC and BC where the mass profile is steepest and the reconstruction of
-the double is poorest. However, the addition of an arc is sufficient to correct
-this.
-
-\subsection{Stellar mass}
-
-The previous tests have been conducted to show that \Glass\ performs as expected.
-Here, we present a novel constraint that can significantly improve the models. 
-The stellar mass distribution is a lower bound on the total mass and in the
-central region of a galaxy is also the dominant component. It can therefore be
-used to constrain the innermost profile. We took the stellar mass directly from
-the generated galaxies and projected the particles onto the pixels. \Glass\
-also offers an option to interpolate any map of stellar mass (e.g., from an
-observation) onto the pixels. The linear constraint is added to \Glass\ by
-writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the
-dark matter and stellar mass components in the potential (\eqnref{discrete
-potential}). Since each $\kappa_{s,n}$ is just a constant we do not add new,
-separate equations for each pixel.
-
-With the stellar mass lower bound, the improvement of the reconstruction
-quality shown in \figref{Test reconstructions} is quite dramatic for the
-steepest mock galaxies (AC and BC). This is because these models are dominated
-by stars in the inner region. The other two galaxies are unaffected because the
-models were already well modeled by the dark matter alone.
-
-\subsection{Velocity anisotropy}
-
-In addition to the lens model aspects, \Glass\ can also run post processing
-routines to analyze each model as it is produced. We have developed a number of
-routines for fitting analytic models to the lensing mass profiles. One in
-particular deprojects the 2d profile assuming a Hernquist profile for the
-light. By fixing the velocity anisotropy $\beta$ we can determine the velocity
-dispersion of the model. Of course, the true velocity dispersion is known for
-the mock galaxies and we can compare our method to those measurements.  In
-\figref{sigma-beta} we plot the recovered velocity dispersion for $\beta=0$ and $\beta=1$
-over a range of aperture sizes for the BC Quad with time delays and stellar
-mass. The stellar half mass radius is plotted in yellow and the Einstein radius
-in black. For this configuration the two radii are well separated. This plot
-demonstrates that the velocity anisotropy can be inferred by combining lens
-modeling and independent velocity dispersion measurements. The lens breaks
-the anisotropy degeneracy at a given aperture.
+Velocity dispersion for different anisotropies, \figref{sigma-beta}.
 
 \begin{figure}
-\plotone{BCQuadR1a_TmS-sb.pdf}
-\caption{Estimated velocity dispersion as a function of the aperture size. The
-single quad lens model for the BC mock galaxy was deprojected and the mass
-profile fit assuming a Hernquist profile for the light. The top curve (blue)
-assumes a velocity anisotropy $\beta=1$, while the lower curve (green)
-assumes $\beta=0$. Given an independent estimate of the velocity dispersion,
-lensing can be used to place constraints on the velocity anisotropy.}
+\begin{center}
+\includegraphics[width=.7\columnwidth]{BCQuadR1a_TmS-sb.pdf}
+\end{center}
+\caption{Estimated velocity dispersion as a function of the aperture
+  size. The single quad lens model for the BC mock galaxy was
+  deprojected and the mass profile fit assuming a Hernquist profile
+  for the light. The top curve (blue) assumes a velocity anisotropy
+  $\beta=1$, while the lower curve (green) assumes $\beta=0$. Given an
+  independent estimate of the velocity dispersion, lensing can be used
+  to place constraints on the velocity anisotropy.}
 \label{sigma-beta}
@@
 
-%\subsection{Velocity dispersions}
-%
-%\begin{itemize}
-%\item Can they predict radial profiles?
-%\item Can we constrain lensing models from predicted velocity dispersions?
-%\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
-%\item Vary $z$ of the halo, possibly orientation.
-%\item Should be able to recover $\gamma$ very well.
-%\item Use G1. Show problems with recovering $\gamma$.
-%\end{itemize}
-
-%\tabref{Test configurations} summarizes how each of the configurations is composed.  
-%\figref{Test reconstructions} shows the reconstructed lens.
-
-%\subsection{Recovery} %--------------------------------------------------------------
-
-%\begin{table}
-%\begin{tabular}{lccccc}
-%Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
-%\hline
-%AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
-% & & & B & -3.15, -4.62 & 37.09\\
-% & & & C & -5.72, -0.67 & 33.58\\
-% & & & D & 4.26, -0.20 & 259.75\\
-% & & & E & 0.22, -0.02 & 104.48\\
-%AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
-% & & & B & 0.87, 4.91 & 228.69\\
-% & & & C & 4.80, 1.57 & 31.83\\
-% & & & D & -4.58, 1.40 & 56.15\\
-% & & & E & -0.09, 0.11 & 180.09\\
-%AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
-% & & & B & -1.26, 5.19 & 66.27\\
-% & & & C & -5.31, 0.49 & 74.72\\
-% & & & D & 4.72, 0.33 & 99.26\\
-% & & & E & 0.04, 0.02 & 174.11\\
-%AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
-% & & & B & -1.93, -5.13 & 14.76\\
-% & & & C & -5.53, -0.27 & 75.45\\
-% & & & D & 4.56, -0.05 & 160.47\\
-% & & & E & 0.09, -0.01 & 147.24\\
-%AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
-% & & & B & -3.47, 4.36 & 60.96\\
-% & & & C & -5.66, 0.92 & 17.14\\
-% & & & D & 4.13, 0.23 & 270.45\\
-% & & & E & 0.40, 0.06 & 83.81\\
-%AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
-% & & & B & 0.98, 4.67 & 227.84\\
-% & & & C & 4.48, 1.70 & 27.39\\
-% & & & D & -4.34, 1.34 & 54.57\\
-% & & & E & -0.12, 0.21 & 144.98\\
-%AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
-% & & & B & 0.92, 3.98 & 226.30\\
-% & & & C & 3.70, 1.67 & 19.74\\
-% & & & D & -3.55, 1.20 & 53.34\\
-% & & & E & -0.12, 0.15 & 96.33\\
-%AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
-% & & & B & 0.93, 3.38 & 223.14\\
-% & & & C & 2.98, 1.69 & 9.75\\
-% & & & D & -2.82, 1.09 & 48.86\\
-% & & & E & -0.15, 0.18 & 52.90\\
-%AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
-% & & & B & 1.02, 2.94 & 219.75\\
-% & & & C & 2.51, 1.69 & 4.63\\
-% & & & D & -2.36, 1.03 & 44.24\\
-% & & & E & -0.16, 0.20 & 32.56
-%\end{tabular}
-%\end{table}
-
-%\subsection{With/without time delays and central image} %--------------------------------------------------------------
-
-%We also considered the effect of having time delays or a central image. The
-%central image is usually highly demagnified and obscured by the lensing galaxy,
-%but in clusters the central image is observable. In this case we can imagine
-%the galaxies to be clusters since the problem is scale-free. A recontruction of
-%AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
-%which combination of time delays (T) and central image (M) was used. An
-%uppercase letter indicates the feature is turned on, and a lowercase letter
-%that it is turned off.
-
-%\begin{figure}
-%\plotone{AASingleQuadR1a_Tm.png}
-%\caption{The reconstruction of AASingleQuadR1a\_Tm.}
-%\end{figure}
-
-%\begin{table}
-%\begin{tabular}{lccccccc}
-%Source name & $z$ & $\beta$ & $A$ (min) & $B$ (min) & $C$ (saddle) & $D$ (saddle) & $E$ (max)\\
-%\hline
-%SingleQuad1 & 2.50 & -0.37,0.08 & -2.40,10.40 & -2.55,-10.26 & -10.93,-0.39 & 10.37,-0.23 & 0.03,-0.01\\
-%SingleQuad2 & 0.40 & 0.08,-0.51 & 0.32,-7.23 & 0.70,6.40 & 6.30,1.74 & -6.22,1.59 & -0.03,0.08\\
-%SingleQuad3 & 0.60 & 0.08,-0.51 & 0.27,-8.86 & 0.74,8.08 & 8.13,1.93 & -8.05,1.72 & -0.03,0.06\\
-%SingleQuad4 & 0.80 & 0.08,-0.51 & 0.36,-9.58 & 0.70,8.82 & 8.92,2.05 & -8.87,1.76 & -0.02,0.05\\
-%SingleQuad5 & 1.00 & 0.08,-0.51 & 0.38,-10.00 & 0.68,9.24 & 9.40,1.99 & -9.34,1.79 & -0.02,0.05\\
-%ExtendedSource0 & 0.40 & 0.20,0.57 & 0.79,7.25 & 1.51,-6.25 & 6.29,-2.07 & -6.12,-1.55 & -0.06,-0.08\\
-%ExtendedSource1 & 0.40 & -0.15,0.17 & -0.64,6.96 & -0.84,-6.66 & -6.67,-0.56 & 6.39,-0.52 & 0.02,-0.03\\
-%ExtendedSource2 & 0.40 & 0.06,-0.33 & 0.24,-7.09 & 0.44,6.56 & 6.47,1.18 & -6.43,0.98 & -0.03,0.05
-%\end{tabular}
-%\caption{Source data.}
-%\label{source data}
-%\end{table}
-%
-%\begin{table}
-%\begin{tabular}{lrrrr}
-%Source name & $\Delta t_{AB}$ & $\Delta t_{BC}$ & $\Delta t_{CD}$ & $\Delta t_{DE}$\\
-%\hline
-%SingleQuad1 & 38.97 & 171.07 & 207.10 & 1314.05\\
-%SingleQuad2 & 335.01 & 97.91 & 50.78 & 623.95\\
-%SingleQuad3 & 312.86 & 122.63 & 47.83 & 951.56\\
-%SingleQuad4 & 303.39 & 128.81 & 46.63 & 1102.50\\
-%SingleQuad5 & 298.27 & 131.32 & 45.70 & 1188.64\\
-%ExtendedSource0 & 360.17 & 62.16 & 115.30 & 588.15\\
-%ExtendedSource1 & 109.28 & 169.77 & 91.20 & 620.78\\
-%ExtendedSource2 & 217.40 & 148.57 & 36.52 & 642.27
-%\end{tabular}
-%\caption{Time delays for each image system.}
-%\label{source time delays}
-%\end{table}
-%
-%\begin{table}
-%\begin{tabular}{ll}
-%\label{test systems}
-%Test name & Source name\\
-%\hline
-%SingleQuad & SingleQuad1\\
-%SingleQuad2 & SingleQuad2\\
-%ExtendedSource & ExtendedSource0 + ExtendedSource1 + ExtendedSource2\\
-%ZContrastDoubleQuad0 & SingleQuad1 + SingleQuad2\\
-%ZContrastDoubleQuad1 & SingleQuad1 + SingleQuad3\\
-%ZContrastDoubleQuad2 & SingleQuad1 + SingleQuad4\\
-%ZContrastDoubleQuad3 & SingleQuad1 + SingleQuad5
-%\end{tabular}
-%\caption{Test configurations}
-%\label{Test configurations}
-%\end{table}
-
-\section{Results} %--------------------------------------------------------------
-
-%\subsection{Model quality}
-
-%\subsection{Shape fitting}
-
-%\subsection{Using principle component analysis to find new degeneracies}
-
-%\begin{figure}
-%\label{chi2}
-%\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
-%\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
-%\caption{
-%Goodness of fit plots for the reconstruction of each of the four galaxies given
-%the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
-%profile with data points at the median value and the error bars showing the 68\% confidence
-%interval.
-%}
-%\end{figure}
-
-%\begin{figure}
-%\plotone{SingleQuad_TmC.png}
-%\caption{SingleQuad}
-%\label{SingleQuad}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{SingleQuad2_TmC.png}
-%\caption{SingleQuad2}
-%\label{SingleQuad2}
-%\end{figure}
-%
-%\figref{SingleQuad}
-%\figref{SingleQuad2}
-%
-%\begin{figure}
-%\plotone{ExtendedSource_TmC.png}
-%\caption{ExtendedSource}.
-%\label{ExtendedSource}
-%\end{figure}
-%
-%\figref{ExtendedSource}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad0_TmC.png}
-%\caption{ZContrastDoubleQuad0}
-%\label{ZContrastDoubleQuad0}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad1_TmC.png}
-%\caption{ZContrastDoubleQuad1}
-%\label{ZContrastDoubleQuad1}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad2_TmC.png}
-%\caption{ZContrastDoubleQuad2}
-%\label{ZContrastDoubleQuad2}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad3_TmC.png}
-%\caption{ZContrastDoubleQuad3}
-%\label{ZContrastDoubleQuad3}
-%\end{figure}
-%
-%\figref{ZContrastDoubleQuad0}
-%\figref{ZContrastDoubleQuad1}
-%\figref{ZContrastDoubleQuad2}
-%\figref{ZContrastDoubleQuad3}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{Aperture}
-
-%\begin{figure}
-%\plotone{sigma_beta.pdf}
-%\caption{}
-%\end{figure}
-
-\section{Discussion} %--------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}
-%\plotone{SingleQuad_Tmc_eig.png}
-%\plotone{SingleQuad2_Tmc_eig.png}
-%\plotone{ExtendedSource_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad0_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad1_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad2_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad3_Tmc_eig.png}
-%\end{figure}
-
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Choice of modeling parameters}
-%
-%
-%\begin{itemize}
-%\item \figref{raytracing convergence tests}
-%\item Why do we choose {\texttt maprad}=20 arcsec when generating test cases?
-%We need to enclose most of the mass for the time delays to be stable.  
-%\item Why do we choose {\texttt pixrad}=45 when generating the test cases? We
-%need sufficient resolution for the image positions to be stable.  
-%\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
-%\label{GLASS Description}
-%\begin{itemize} 
-%\item Framework that incorporates lens modeling, analysis, and plotting.
-%\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
-%\item Allows for post processing and criteria matching on a per model basis.
-%\item Input files are python programs but from within the framework that aspect may be ignored.
-%
-%\item Lens reconstruction. Based on PixeLens. Express data constraints and
-%priors as linear equations. Sample the resulting simplex.
-%\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
-%\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
-%\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.
-%
-%\item Raytracing. Use a fine grid to sample the 2d function mapping position on
-%the image plane to distance from the source on the source plane. From those
-%points that are near the source, use a 2d root finder to locate the exact
-%positions. Merge nearly identical solutions.
-
-%\end{itemize}
-
-\section{Raytracing convergence test}
-Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
-$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
-the change in time delays as we increase $\Rmap$.  The image system is a quad
-with the central maximum image. When the projected mass begins to fall off the
-time delays stabilize. In the right panel we see the effect of changing the
-resolution of the map.  Increasing the resolution allows for more accurate
-placement of the images and after about $\Rpix=40$ the image positions change
-by less than 0.04 arcsec. The one image that continues to change is near to a
-caustic.
-
-\begin{figure}
-\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
-\caption{(left) Test for predicted time delay convergence as $\Rmap$ changes.
-$\Rpix=45$. After about $\Rmap=20$ most of the asymmetric mass is in the map.
-(right) Test for predicted image position $\theta$ convergence as $\Rpix$
-changes. $\Rmap=20$ arcsec.}
-\label{raytracing convergence tests}
-\end{figure}
-
-\section{Derivation of pixelated density coefficients}
-\label{Q derivation}
-When the lens plane is pixelized we need a discrete form of the integral
-%
-\[\int \kappa(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta' \]
-%
-In particular we want
-%
-\[\sum_n \kappa_n Q_n(\vec\theta)\]
-%
-where $Q_n$ is the logarithm evaluated over the $n$th pixel at position $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.
-Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates such that
-%
-$|\vec\theta| = r = \sqrt{x^2 + y^2}$. The integral now becomes
-%
-\[Q_n(x,y) = \frac12 \int_{y_-}^{y_+}\int_{x_-}^{x_+} \ln (x'^2+y'^2) dx' dy'\]
-%
-where $x_\pm = x + x_n \pm (a/2)$ and similarly for $y_\pm$.
-Using the identity
-%
-\[\int \ln(x^2+y^2) dx = x \ln(x^2+y^2) - 2x + 2y\arctan(x/a) \]
-%
-we can express $Q_n$ as the sum of four parts
-%
-\[Q_n(x,y) = \frac12 \left[ \tilde Q_n(x_+,y_+)
-        + \tilde Q_n(x_-,y_-)
-        - \tilde Q_n(x_-,y_+)
-        - \tilde Q_n(x_+,y_-) \right]\]
-%
-where
-%
-\[\tilde Q_n(x,y) = xy(\ln r^2 - 3) + x^2\arctan(y/x) + y^2\arctan(x/y)\]
-
 \bibliographystyle{mn2e}
+\def\aap{A\&A}
+\def\araa{ARA\&A}
+\def\mnras{MNRAS}
+\def\nat{Nature}
+\def\nar{New Astr Rev}
 \bibliography{ms}

### 2013-06-11 limits/ms.tex
New plots for results, mock galaxies, and sample reconstruction.
Removed unnecessary commented text and updated main results plots to include split plots for AC and BC mock galaxies.
added points to be emphasized
Justin's made a start. Abstract outline written. Very rough draft intro that still needs references. Will carry on through the rest of the paper tomorrow then add some polish in a second sweep. Hope everyone is happy so far.

@@
-\documentclass[onecolumn,galley]{mn2e}
+\documentclass[galley]{mn2e}
 %\documentclass[twocolumn,galley]{mn2e}
@@
 %\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
-\title[GLASS]{Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework}
+\title[\Glass]{Gravitational Lens Recovery with \Glass: Illustrating the power of free-form lens modelling}
 \author{%
@@
 \begin{abstract}
-We show the effectiveness of reconstructing the mass distribution of four mock galaxies using
-a range of strong gravitational lensing assumptions. In particular, we study
-the affects of the lens morphology (double or quad) with and without a central
-image, angular image distribution, and red shift contrast between two sources.
-The lens modeling is performed using a new free-form framework called \Glass.
-We conclude that \dots
-%1) Time delays are unnecessary with strong red shift contrast,
-%2)
-
-%We study the effectiveness of a variety of strong lensing scenarios to inform
-%the reconstruction of four simulated triaxial halos with stellar and dark
-%matter components. We conclude that 
-%1) lenses with multiple sources and high redshift contrast perform very well
-%2) lenses where the images are already probing the stellar dominated region 
-%   of a galaxy can be constrained by an estimate of the stellar mass and
-%   suggest the fraction of dark matter
-%3) if velocity dispersion measurements are to be used then a sufficiently large aperture 
-%   is necessary
-%4) lensing can be used to infer the velocity anisotropy.
-%We also introduce GLASS, an extensible framework for lens modeling and analysis.
-
-%We attempt to reconstruct the mass profile and distribution of a dark and
-%stellar matter triaxial halo using a variety of strong lens configurations,
-%stellar mass estimates, and stellar velocity dispersions. The lens
-%configurations test quads with small to large image separations (radial
-%sampling), extended source information ranging from point images to Einstein
-%rings (angular sampling), and multiple sources located at the same and
-%differing redshifts (redshift contrast).
-
-%We conclude that redshift contrast can significantly constrain the mass
-%profiles.  Stellar mass estimates can also lead to better reconstructions by
-%placing lower bounds on the mass distribution in the inner regions of galaxies.
-%Velocity dispersions alone are unlikely to usefully constrain the profile
-%because the profile is highly sensitive to the dispersion measurement.  
-%Combined with other techniques, however, velocity dispersions can help to
-%constrain the range of possible reconstructed solutions. We also introduce
-%GLASS, an extensible framework for lens modeling and analysis.  
+{\bf JR. Does \Glass\ stand for something?}\\
+We introduce a new free-form gravitational lens modelling tool \Glass\ that builds on an earlier code \PixeLens.
+Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
+However, \Glass\ improves on \PixeLens\ in a number of important respects: (i) it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors; (ii) it is built on a fully modular framework that can support different basis functions; (iii) non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented); (iv) the stellar mass (if known) can be applied as a prior; and (v) adaptive resolution can be used in regions of interest.
+We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data are required to  measure the circularly averaged mass profile of a lens and its shape.
+We find that for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy.
+However, a single quad with time delays also performs well.
+Folding in additional constraints from stellar population synthesis modelling provides powerful additional constraints for galaxy lenses where the stars dominate the central potential, providing similarly good constraints from a single double without time delays as a quad with time delays in the absence of stellar mass constraints.
+Stellar kinematic data is only useful for probing the mass profile within the half light radius $r_{1/2}$ of the stars provided data are available for $r \gg r_{1/2}$ since this is required to integrate out the unknown velocity anisotropy $\beta(r)$.
+On the other hand, if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right.
+Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to probe cosmology.
+We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
 \end{abstract}
@@
 
-To date only about 400 strong lenses are known, but within the next ten years
-new surveys will discover thousands of gravitational lenses. The SKA estimates
-that after its start in 2020 about 10,000 lenses will be found. The LSST
-expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or
-quasar lenses after 2022.
+Since the discovery of the first gravitational lens (CITE), lensing has become an increasingly important probe of the distribution of mass in the Universe (CITE).
+Strong lensing in particular provides a powerful probe of the mass distribution at the heart of galaxies and galaxy clusters given good enough data (CITE).
+This in turn provides valuable constraints on the nature of dark matter (CITE), on cosmological models (CITE), and on galaxy formation models (CITE).
+To date, some $\sim$400 strong lenses are known (CITE), but with the advent of large ground and space based surveys, this number is set to explode, with thousands of lenses expected to be discovered over the next ten years (CITE).
 
-A typical lens, where only the measured observables are the image positions,
-can been used to estimate the total mass of a galaxy including parts of the
-dark matter halo. The enclosed mass inside the Einstein radius is simple to
-calculate and quite robust given the observed image positions. The exact mass
-distribution is more difficult to determine, however, as there are typically
-not enough constraints on the mass profile. The known degeneracies have been
-discussed at length in the literature. At the very least, one would like to
-have a measure of the enclosed mass at two distinct radii to be able
-to properly distinguish between analytic mass models. 
-%This would break the steepness degeneracy, also known as the mass sheet degeneracy.
+The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data (CITE).
+This is useful in that a simple model provides valuable physical insight (CITE).
+However, as data quality improves and the questions we ask of these data become more refined, it is important to re-asses the impact of our model assumptions.
+`Non-parameteric' methods -- that assume many more parameters than the available data constraints -- are invaluable in this respect.
+In non-parametric mass modelling, the lens inversion problem is deliberately chosen to be under-constrained (CITE).
+Instead of finding one `best-fit' model, we must search for many models consistent with the data, exploring degeneracies between different but plausible mass models.
+This latter word -- {\it plausible} -- encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data are typically required on the solution space in order to make it finite -- priors (CITE).
+However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling.
+The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including addition non-lensing data) are required to measure parameters of interest.
 
-Lensing is not the only technique that can measure enclosed mass. The enclosed
-mass can also be estimated from stellar velocity dispersions. If the radius
-from this measurement is sufficiently different from the Einstein radius, then
-combining this measurement with lensing provides the necessary constraint.
-Another solution is to find a galaxy that is lensing two sources. The images
-from each source provide an enclosed mass. The extent to which the radii
-differ is dependent upon the redshifts of the two sources: the larger the
-redshift difference the larger the radial separation.
+In this paper, we present a new free-form or `non-parametric' strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens (CITE).
+Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
+However, \Glass\ improves on \PixeLens\ in a number of important respects:
 
-Lensing is known to be sensitive to cosmology and, in principle, can be used to
-estimate such quantities as the Hubble constant $H_0$ when the lens has
-measurable time delays. However, due to strong degeneracies such as the
-steepness degeneracy there is often little one can learn from a single lens. 
-In this case, one is free to change the mass and $H_0$ while keeping
-all observables fixed. A single lens can say almost nothing about the actual
-value of $H_0$. However, it has been shown that combining modeling results
-of several strong lenses with time delays can significantly reduce the allowed
-values and provides a measure to within 10 percent \cite{}.
+\begin{enumerate} 
+\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors;
+\item it is built on a fully modular framework that can support different basis functions;
+\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
+\item the stellar mass (if known) can be applied as a prior; and
+\item adaptive resolution can be used in regions of interest. 
+\end{enumerate}
 
-If one assumes a Hubble constant $H_0$ and time delays have been observed for a
-lens this will break the steepness degeneracy but will not help in
-constraining the mass profile at two radii.  One can choose to postpone this
-problem and simply fit models to the given data.  The earliest examples were
-singular isothermal sphere (SIS) or elliptical (SIE) models but have since
-evolved to multi-component models include separate models for the stars and
-dark matter. Other methods that do not ignore this problem use genetic
-algorithms or linear programming to explore the large space of solutions.
+We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data from strong lensing, stellar populations synthesis models and/or stellar kinematics are required to measure the circularly averaged mass profile of a lens and its shape.
+We will consider using strong lensing as a cosmological probe, and present the first results from \Glass\ applied to real data, in forthcoming papers.
 
-Despite such difficulties lensing is a direct probe of the gravitating mass in
-a halo and there are a number of open problems in galaxy formation that lensing
-can help address. For instance, the debate remains as to what form the inner
-slope of the density profile takes. Numerical simulations of dark matter
-suggest a cusp, while observations from lensing and stellar dynamics suggest
-cores. This may, however, be only a matter of scale, as both theory and
-observations agree that clusters have cuspy profiles.
+%(The SKA estimates that after its start in 2020 about 10,000 lenses will be found. The LSST expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or quasar lenses after 2022.)
 
-Lensing may also be useful in measuring possible adiabatic contraction of the 
-dark matter halo due to the central stars in a galaxy. For this, one needs
-high resolution mass models of the stellar profile combined with accurate models
-of the total mass. Indeed, with such models, one may also improve the statistics
-of the dark matter fraction in a galaxies over many different mass scales.
+%A typical lens, where only the measured observables are the image positions, can been used to estimate the total mass of a galaxy including parts of the dark matter halo.
+The enclosed mass inside the Einstein radius is simple to calculate and quite robust given the observed image positions.
+The exact mass distribution is more difficult to determine, however, as there are typically not enough constraints on the mass profile.
+The known degeneracies have been discussed at length in the literature.
+At the very least, one would like to have a measure of the enclosed mass at two distinct radii to be able to properly distinguish between analytic mass models.
+This would break the steepness degeneracy, also known as the mass sheet degeneracy.
 
-These open problems suggest what kind of lensing data will be required in the
-future.  Future surveys will provide many lenses but time delays will require a
-long follow up. Stellar mass maps, however, take a known, fixed observation
-time and can be performed for many lenses. It will be important not only to
-measure the stellar velocity dispersion at an arbitrary radius, but to ensure
-that the measurement is taken at a radius different to the Einstein radius.
-For the radio surveys like SKA it will be important to detect the central image
-of the lens. This can provide mass information all the way to the center of the
-galaxy.
+%Lensing is not the only technique that can measure enclosed mass.
+The enclosed mass can also be estimated from stellar velocity dispersions.
+If the radius from this measurement is sufficiently different from the Einstein radius, then combining this measurement with lensing provides the necessary constraint.
+Another solution is to find a galaxy that is lensing two sources.
+The images from each source provide an enclosed mass.
+The extent to which the radii differ is dependent upon the redshifts of the two sources: the larger the redshift difference the larger the radial separation.
 
-In this paper we perform a parameter study using four mock galaxies that differ
-in their dark matter and stellar profiles. We consider double and quad lensing
-morphologies, time delays, the presence of a central image, red shift contrast
-between multiple sources, and image configuration.  We also consider the
-effects of adding stellar mass models as lower bound constraints on the mass
-distribution.  The modeling and analysis is performed using a new free form
-lens modeling framework called \Glass.
+%Lensing is known to be sensitive to cosmology and, in principle, can be used to estimate such quantities as the Hubble constant $H_0$ when the lens has measurable time delays.
+However, due to strong degeneracies such as the steepness degeneracy there is often little one can learn from a single lens.
+In this case, one is free to change the mass and $H_0$ while keeping all observables fixed.
+A single lens can say almost nothing about the actual value of $H_0$.
+However, it has been shown that combining modeling results of several strong lenses with time delays can significantly reduce the allowed values and provides a measure to within 10 percent \cite{}.
 
-We first review the basic lensing theory we will need and then describe how
-\Glass is used to generate lensing models. The mock data and how it was
-generated is described in \secref{}. In section{} we discuss the lensing
-configurations in the parameter study and present some example output. Our
-finals results are presented in \secref{}.
+%If one assumes a Hubble constant $H_0$ and time delays have been observed for a lens this will break the steepness degeneracy but will not help in constraining the mass profile at two radii.
+One can choose to postpone this problem and simply fit models to the given data.
+The earliest examples were singular isothermal sphere (SIS) or elliptical (SIE) models but have since evolved to multi-component models include separate models for the stars and dark matter.
+Other methods that do not ignore this problem use genetic algorithms or linear programming to explore the large space of solutions.
+
+%Despite such difficulties lensing is a direct probe of the gravitating mass in a halo and there are a number of open problems in galaxy formation that lensing can help address.
+For instance, the debate remains as to what form the inner slope of the density profile takes.
+Numerical simulations of dark matter suggest a cusp, while observations from lensing and stellar dynamics suggest cores.
+This may, however, be only a matter of scale, as both theory and observations agree that clusters have cuspy profiles.
+
+%Lensing may also be useful in measuring possible adiabatic contraction of the dark matter halo due to the central stars in a galaxy.
+For this, one needs high resolution mass models of the stellar profile combined with accurate models of the total mass.
+Indeed, with such models, one may also improve the statistics of the dark matter fraction in a galaxies over many different mass scales.
+
+%These open problems suggest what kind of lensing data will be required in thefuture.
+Future surveys will provide many lenses but time delays will require a long follow up.
+Stellar mass maps, however, take a known, fixed observation time and can be performed for many lenses.
+It will be important not only to measure the stellar velocity dispersion at an arbitrary radius, but to ensure that the measurement is taken at a radius different to the Einstein radius.
+For the radio surveys like SKA it will be important to detect the central image of the lens.
+This can provide mass information all the way to the center of the galaxy.
+
+This paper is organised as follows.
+We first review the basic lensing theory we will need and then describe how \Glass\ is used to generate lensing models.
+The mock data and how it was generated is described in \secref{}.
+In section{} we discuss the lensing configurations in the parameter study and present some example output.
+Our finals results are presented in \secref{}.
 
@@
 \begin{figure}
-%\plotone{AAZContrastR1R5_Tm.pdf}
-\plotone{BCQuadR1a_TmS.pdf}
+\plotthree{BCQuadR1a_TmS-a.pdf}{BCQuadR1a_TmS-b.pdf}{BCQuadR1a_TmS-c.pdf}
 \caption{A typical reconstructed lens. Here we present a single quad lens from 
@@
 \begin{figure}
-%\plotone{AAarrival_surfaces}
-%\plotone{BBarrival_surfaces}
 \plotone{BCarrival_surfaces}
@@
 
-%\tabref{Test configurations} summarizes how each of the configurations is composed.  
-%\figref{Test reconstructions} shows the reconstructed lens.
-
-%\subsection{Recovery} %--------------------------------------------------------------
-
-%\begin{table}
-%\begin{tabular}{lccccc}
-%Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
-%\hline
-%AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
-% & & & B & -3.15, -4.62 & 37.09\\
-% & & & C & -5.72, -0.67 & 33.58\\
-% & & & D & 4.26, -0.20 & 259.75\\
-% & & & E & 0.22, -0.02 & 104.48\\
-%AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
-% & & & B & 0.87, 4.91 & 228.69\\
-% & & & C & 4.80, 1.57 & 31.83\\
-% & & & D & -4.58, 1.40 & 56.15\\
-% & & & E & -0.09, 0.11 & 180.09\\
-%AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
-% & & & B & -1.26, 5.19 & 66.27\\
-% & & & C & -5.31, 0.49 & 74.72\\
-% & & & D & 4.72, 0.33 & 99.26\\
-% & & & E & 0.04, 0.02 & 174.11\\
-%AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
-% & & & B & -1.93, -5.13 & 14.76\\
-% & & & C & -5.53, -0.27 & 75.45\\
-% & & & D & 4.56, -0.05 & 160.47\\
-% & & & E & 0.09, -0.01 & 147.24\\
-%AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
-% & & & B & -3.47, 4.36 & 60.96\\
-% & & & C & -5.66, 0.92 & 17.14\\
-% & & & D & 4.13, 0.23 & 270.45\\
-% & & & E & 0.40, 0.06 & 83.81\\
-%AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
-% & & & B & 0.98, 4.67 & 227.84\\
-% & & & C & 4.48, 1.70 & 27.39\\
-% & & & D & -4.34, 1.34 & 54.57\\
-% & & & E & -0.12, 0.21 & 144.98\\
-%AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
-% & & & B & 0.92, 3.98 & 226.30\\
-% & & & C & 3.70, 1.67 & 19.74\\
-% & & & D & -3.55, 1.20 & 53.34\\
-% & & & E & -0.12, 0.15 & 96.33\\
-%AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
-% & & & B & 0.93, 3.38 & 223.14\\
-% & & & C & 2.98, 1.69 & 9.75\\
-% & & & D & -2.82, 1.09 & 48.86\\
-% & & & E & -0.15, 0.18 & 52.90\\
-%AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
-% & & & B & 1.02, 2.94 & 219.75\\
-% & & & C & 2.51, 1.69 & 4.63\\
-% & & & D & -2.36, 1.03 & 44.24\\
-% & & & E & -0.16, 0.20 & 32.56
-%\end{tabular}
-%\end{table}
-
 %\subsection{With/without time delays and central image} %--------------------------------------------------------------
@@
 
-%\begin{figure}
-%\plotone{AASingleQuadR1a_Tm.png}
-%\caption{The reconstruction of AASingleQuadR1a\_Tm.}
-%\end{figure}
-
-%\begin{table}
-%\begin{tabular}{lccccccc}
-%Source name & $z$ & $\beta$ & $A$ (min) & $B$ (min) & $C$ (saddle) & $D$ (saddle) & $E$ (max)\\
-%\hline
-%SingleQuad1 & 2.50 & -0.37,0.08 & -2.40,10.40 & -2.55,-10.26 & -10.93,-0.39 & 10.37,-0.23 & 0.03,-0.01\\
-%SingleQuad2 & 0.40 & 0.08,-0.51 & 0.32,-7.23 & 0.70,6.40 & 6.30,1.74 & -6.22,1.59 & -0.03,0.08\\
-%SingleQuad3 & 0.60 & 0.08,-0.51 & 0.27,-8.86 & 0.74,8.08 & 8.13,1.93 & -8.05,1.72 & -0.03,0.06\\
-%SingleQuad4 & 0.80 & 0.08,-0.51 & 0.36,-9.58 & 0.70,8.82 & 8.92,2.05 & -8.87,1.76 & -0.02,0.05\\
-%SingleQuad5 & 1.00 & 0.08,-0.51 & 0.38,-10.00 & 0.68,9.24 & 9.40,1.99 & -9.34,1.79 & -0.02,0.05\\
-%ExtendedSource0 & 0.40 & 0.20,0.57 & 0.79,7.25 & 1.51,-6.25 & 6.29,-2.07 & -6.12,-1.55 & -0.06,-0.08\\
-%ExtendedSource1 & 0.40 & -0.15,0.17 & -0.64,6.96 & -0.84,-6.66 & -6.67,-0.56 & 6.39,-0.52 & 0.02,-0.03\\
-%ExtendedSource2 & 0.40 & 0.06,-0.33 & 0.24,-7.09 & 0.44,6.56 & 6.47,1.18 & -6.43,0.98 & -0.03,0.05
-%\end{tabular}
-%\caption{Source data.}
-%\label{source data}
-%\end{table}
-%
-%\begin{table}
-%\begin{tabular}{lrrrr}
-%Source name & $\Delta t_{AB}$ & $\Delta t_{BC}$ & $\Delta t_{CD}$ & $\Delta t_{DE}$\\
-%\hline
-%SingleQuad1 & 38.97 & 171.07 & 207.10 & 1314.05\\
-%SingleQuad2 & 335.01 & 97.91 & 50.78 & 623.95\\
-%SingleQuad3 & 312.86 & 122.63 & 47.83 & 951.56\\
-%SingleQuad4 & 303.39 & 128.81 & 46.63 & 1102.50\\
-%SingleQuad5 & 298.27 & 131.32 & 45.70 & 1188.64\\
-%ExtendedSource0 & 360.17 & 62.16 & 115.30 & 588.15\\
-%ExtendedSource1 & 109.28 & 169.77 & 91.20 & 620.78\\
-%ExtendedSource2 & 217.40 & 148.57 & 36.52 & 642.27
-%\end{tabular}
-%\caption{Time delays for each image system.}
-%\label{source time delays}
-%\end{table}
-%
-%\begin{table}
-%\begin{tabular}{ll}
-%\label{test systems}
-%Test name & Source name\\
-%\hline
-%SingleQuad & SingleQuad1\\
-%SingleQuad2 & SingleQuad2\\
-%ExtendedSource & ExtendedSource0 + ExtendedSource1 + ExtendedSource2\\
-%ZContrastDoubleQuad0 & SingleQuad1 + SingleQuad2\\
-%ZContrastDoubleQuad1 & SingleQuad1 + SingleQuad3\\
-%ZContrastDoubleQuad2 & SingleQuad1 + SingleQuad4\\
-%ZContrastDoubleQuad3 & SingleQuad1 + SingleQuad5
-%\end{tabular}
-%\caption{Test configurations}
-%\label{Test configurations}
-%\end{table}
-
 \section{Results} %--------------------------------------------------------------
-
-%\subsection{Model quality}
 
@@
 
-%\begin{figure}
-%\label{chi2}
-%\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
-%\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
-%\caption{
-%Goodness of fit plots for the reconstruction of each of the four galaxies given
-%the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
-%profile with data points at the median value and the error bars showing the 68\% confidence
-%interval.
-%}
-%\end{figure}
+\section{Discussion}
 
-%\begin{figure}
-%\plotone{SingleQuad_TmC.png}
-%\caption{SingleQuad}
-%\label{SingleQuad}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{SingleQuad2_TmC.png}
-%\caption{SingleQuad2}
-%\label{SingleQuad2}
-%\end{figure}
-%
-%\figref{SingleQuad}
-%\figref{SingleQuad2}
-%
-%\begin{figure}
-%\plotone{ExtendedSource_TmC.png}
-%\caption{ExtendedSource}.
-%\label{ExtendedSource}
-%\end{figure}
-%
-%\figref{ExtendedSource}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad0_TmC.png}
-%\caption{ZContrastDoubleQuad0}
-%\label{ZContrastDoubleQuad0}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad1_TmC.png}
-%\caption{ZContrastDoubleQuad1}
-%\label{ZContrastDoubleQuad1}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad2_TmC.png}
-%\caption{ZContrastDoubleQuad2}
-%\label{ZContrastDoubleQuad2}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{ZContrastDoubleQuad3_TmC.png}
-%\caption{ZContrastDoubleQuad3}
-%\label{ZContrastDoubleQuad3}
-%\end{figure}
-%
-%\figref{ZContrastDoubleQuad0}
-%\figref{ZContrastDoubleQuad1}
-%\figref{ZContrastDoubleQuad2}
-%\figref{ZContrastDoubleQuad3}
+extensible framework
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+accurate reconstructions through better sampling
 
-%\subsection{Aperture}
+where stellar mass significant, including it greatly improves accuracy
 
-%\begin{figure}
-%\plotone{sigma_beta.pdf}
-%\caption{}
-%\end{figure}
-
-\section{Discussion} %--------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}
-%\plotone{SingleQuad_Tmc_eig.png}
-%\plotone{SingleQuad2_Tmc_eig.png}
-%\plotone{ExtendedSource_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad0_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad1_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad2_Tmc_eig.png}
-%\plotone{ZContrastDoubleQuad3_Tmc_eig.png}
-%\end{figure}
+breaking the vdisp/anisotropy degeneracy.
 
 \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Choice of modeling parameters}
-%
-%
-%\begin{itemize}
-%\item \figref{raytracing convergence tests}
-%\item Why do we choose {\texttt maprad}=20 arcsec when generating test cases?
-%We need to enclose most of the mass for the time delays to be stable.  
-%\item Why do we choose {\texttt pixrad}=45 when generating the test cases? We
-%need sufficient resolution for the image positions to be stable.  
-%\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
-%\label{GLASS Description}
-%\begin{itemize} 
-%\item Framework that incorporates lens modeling, analysis, and plotting.
-%\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
-%\item Allows for post processing and criteria matching on a per model basis.
-%\item Input files are python programs but from within the framework that aspect may be ignored.
-%
-%\item Lens reconstruction. Based on PixeLens. Express data constraints and
-%priors as linear equations. Sample the resulting simplex.
-%\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
-%\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
-%\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.
-%
-%\item Raytracing. Use a fine grid to sample the 2d function mapping position on
-%the image plane to distance from the source on the source plane. From those
-%points that are near the source, use a 2d root finder to locate the exact
-%positions. Merge nearly identical solutions.
-
-%\end{itemize}
 

### 2013-06-12 limits/ms.tex
references added to intro (though more are still required); some polish added; theory outline sketched to be worked on this afternoon.

@@
 %\documentclass[onecolumn,galley,draft]{mn2e}
-%\usepackage{myaasmacros}
+\usepackage{myaasmacros}
 \usepackage{mathrsfs}
@@
 \usepackage{graphicx}
+\usepackage{natbib}
 
@@
 
-%\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
 \title[\Glass]{Gravitational Lens Recovery with \Glass: Illustrating the power of free-form lens modelling}
@@
 
-%\tableofcontents
-
 \begin{abstract}
@@
 However, \Glass\ improves on \PixeLens\ in a number of important respects: (i) it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors; (ii) it is built on a fully modular framework that can support different basis functions; (iii) non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented); (iv) the stellar mass (if known) can be applied as a prior; and (v) adaptive resolution can be used in regions of interest.
-We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data are required to  measure the circularly averaged mass profile of a lens and its shape.
-We find that for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy.
-However, a single quad with time delays also performs well.
-Folding in additional constraints from stellar population synthesis modelling provides powerful additional constraints for galaxy lenses where the stars dominate the central potential, providing similarly good constraints from a single double without time delays as a quad with time delays in the absence of stellar mass constraints.
-Stellar kinematic data is only useful for probing the mass profile within the half light radius $r_{1/2}$ of the stars provided data are available for $r \gg r_{1/2}$ since this is required to integrate out the unknown velocity anisotropy $\beta(r)$.
-On the other hand, if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right.
-Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to probe cosmology.
+We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data -- from lensing, stellar kinematics and/or stellar masses -- are required to measure the circularly averaged mass profile of a lens and its shape.
+Our key findings are as follows: (i) for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy; (ii) a single quad with time delays also performs well, giving a good recovery of both the mass profile and its shape; (iii) stellar masses -- for lenses where the stars dominate the central potential -- can also break the steepness degeneracy, giving a recovery almost as good as having time delay data or multiple source redshifts; (iv) stellar kinematics are similarly powerful if the data extend beyond the half light radius of the stars $r \gg r_{1/2}$ (required to integrate out the effect of the unknown velocity anisotropy, $\beta(r)$); and (v) if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right.
+Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to constrain cosmological models.
 We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
+{\bf JR. Lots of references missing here. Need to be added. But this should get us started.}\\
 
-Since the discovery of the first gravitational lens (CITE), lensing has become an increasingly important probe of the distribution of mass in the Universe (CITE).
-Strong lensing in particular provides a powerful probe of the mass distribution at the heart of galaxies and galaxy clusters given good enough data (CITE).
-This in turn provides valuable constraints on the nature of dark matter (CITE), on cosmological models (CITE), and on galaxy formation models (CITE).
-To date, some $\sim$400 strong lenses are known (CITE), but with the advent of large ground and space based surveys, this number is set to explode, with thousands of lenses expected to be discovered over the next ten years (CITE).
+Since the discovery of the first gravitational lens \citep{1979Natur.279..381W}, lensing has become an increasingly important probe of the distribution of mass in the Universe \citep{1937ApJ....86..217Z,2012arXiv1206.1225A}.
+Strong lensing in particular provides a powerful probe of the mass distribution at the heart of galaxies and galaxy clusters given good enough data \citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}.
+This in turn provides valuable constraints on the nature of dark matter \citep{2006ApJ...652L...5S,2013ApJ...765...25N}, on cosmological models \citep{2010Sci...329..924J, 2008ApJ...679...17C}, and on galaxy formation models \citep{2012MNRAS.424..104L}.
+To date, some $\sim$400 strong lenses are known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of large ground and space based surveys, this number is set to explode, with thousands of lenses expected to be discovered over the next ten years \citep{2012arXiv1206.1225A, 2010AAS...21540115M, 2004NewAR..48.1085K}.
 
-The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data (CITE).
-This is useful in that a simple model provides valuable physical insight (CITE).
+The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K, 2010GReGr..42.2151K}.
+This is useful in that a simple model provides valuable physical insight.
 However, as data quality improves and the questions we ask of these data become more refined, it is important to re-asses the impact of our model assumptions.
 `Non-parameteric' methods -- that assume many more parameters than the available data constraints -- are invaluable in this respect.
-In non-parametric mass modelling, the lens inversion problem is deliberately chosen to be under-constrained (CITE).
-Instead of finding one `best-fit' model, we must search for many models consistent with the data, exploring degeneracies between different but plausible mass models.
-This latter word -- {\it plausible} -- encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data are typically required on the solution space in order to make it finite -- priors (CITE).
-However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling.
-The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including addition non-lensing data) are required to measure parameters of interest.
+In non-parametric mass modelling, the lens inversion problem is deliberately chosen to be under-constrained \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}.
+Instead of finding one `best-fit' model, we must search for many models consistent with the data, exploring degeneracies between different but plausible\footnotemark\ mass models \citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}.
+The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including data from stellar population synthesis modelling, stellar kinematics, or other indepedent probes of the mass) are required to measure parameters of interest.
 
-In this paper, we present a new free-form or `non-parametric' strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens (CITE).
+\footnotetext{The word {\it plausible} encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data (priors) are typically required on the solution space in order to make it finite.
+However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling.}
+
+In this paper, we present a new free-form or `non-parametric' strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}.
 Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
@@
 \begin{enumerate} 
-\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors;
+\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
 \item it is built on a fully modular framework that can support different basis functions;
@@
 
-We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data from strong lensing, stellar populations synthesis models and/or stellar kinematics are required to measure the circularly averaged mass profile of a lens and its shape.
+We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data from strong lensing, stellar mass (derived from populations synthesis modelling) and/or stellar kinematics are required to measure the circularly averaged mass profile of a lens and its shape.
 We will consider using strong lensing as a cosmological probe, and present the first results from \Glass\ applied to real data, in forthcoming papers.
 
-%(The SKA estimates that after its start in 2020 about 10,000 lenses will be found. The LSST expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or quasar lenses after 2022.)
+This paper is organised as follows.
+In \S\ref{sec:theory}, we review the basic lensing, stellar population synthesis, and Jeans mass modelling theory we will need.
+We present some simple back-of-the-envelope calculations that illustrate what type and quality of data we are likely to need to measure mass profiles and shapes.
+In \S\ref{sec:glass}, we describe the \Glass\ lens inversion algorithm and its stellar kinematic post-processing module.
+In \S\ref{sec:mockdata}, we describe our mock N-body data and our ray tracing algorithm used to generate the images.
+In \S\ref{sec:results}, we present our results from applying \Glass\ to these mock data.
+Finally, in \S\ref{sec:conclusions} we present our conclusions.
 
-%A typical lens, where only the measured observables are the image positions, can been used to estimate the total mass of a galaxy including parts of the dark matter halo.
-The enclosed mass inside the Einstein radius is simple to calculate and quite robust given the observed image positions.
-The exact mass distribution is more difficult to determine, however, as there are typically not enough constraints on the mass profile.
-The known degeneracies have been discussed at length in the literature.
-At the very least, one would like to have a measure of the enclosed mass at two distinct radii to be able to properly distinguish between analytic mass models.
-This would break the steepness degeneracy, also known as the mass sheet degeneracy.
+\section{Theoretical Background}\label{sec:theory}
 
-%Lensing is not the only technique that can measure enclosed mass.
-The enclosed mass can also be estimated from stellar velocity dispersions.
-If the radius from this measurement is sufficiently different from the Einstein radius, then combining this measurement with lensing provides the necessary constraint.
-Another solution is to find a galaxy that is lensing two sources.
-The images from each source provide an enclosed mass.
-The extent to which the radii differ is dependent upon the redshifts of the two sources: the larger the redshift difference the larger the radial separation.
+\subsection{What can we learn from strong lensing data?}
 
-%Lensing is known to be sensitive to cosmology and, in principle, can be used to estimate such quantities as the Hubble constant $H_0$ when the lens has measurable time delays.
-However, due to strong degeneracies such as the steepness degeneracy there is often little one can learn from a single lens.
-In this case, one is free to change the mass and $H_0$ while keeping all observables fixed.
-A single lens can say almost nothing about the actual value of $H_0$.
-However, it has been shown that combining modeling results of several strong lenses with time delays can significantly reduce the allowed values and provides a measure to within 10 percent \cite{}.
+\subsection{The utility of stellar mass estimates}
 
-%If one assumes a Hubble constant $H_0$ and time delays have been observed for a lens this will break the steepness degeneracy but will not help in constraining the mass profile at two radii.
-One can choose to postpone this problem and simply fit models to the given data.
-The earliest examples were singular isothermal sphere (SIS) or elliptical (SIE) models but have since evolved to multi-component models include separate models for the stars and dark matter.
-Other methods that do not ignore this problem use genetic algorithms or linear programming to explore the large space of solutions.
-
-%Despite such difficulties lensing is a direct probe of the gravitating mass in a halo and there are a number of open problems in galaxy formation that lensing can help address.
-For instance, the debate remains as to what form the inner slope of the density profile takes.
-Numerical simulations of dark matter suggest a cusp, while observations from lensing and stellar dynamics suggest cores.
-This may, however, be only a matter of scale, as both theory and observations agree that clusters have cuspy profiles.
-
-%Lensing may also be useful in measuring possible adiabatic contraction of the dark matter halo due to the central stars in a galaxy.
-For this, one needs high resolution mass models of the stellar profile combined with accurate models of the total mass.
-Indeed, with such models, one may also improve the statistics of the dark matter fraction in a galaxies over many different mass scales.
-
-%These open problems suggest what kind of lensing data will be required in thefuture.
-Future surveys will provide many lenses but time delays will require a long follow up.
-Stellar mass maps, however, take a known, fixed observation time and can be performed for many lenses.
-It will be important not only to measure the stellar velocity dispersion at an arbitrary radius, but to ensure that the measurement is taken at a radius different to the Einstein radius.
-For the radio surveys like SKA it will be important to detect the central image of the lens.
-This can provide mass information all the way to the center of the galaxy.
-
-This paper is organised as follows.
-We first review the basic lensing theory we will need and then describe how \Glass\ is used to generate lensing models.
-The mock data and how it was generated is described in \secref{}.
-In section{} we discuss the lensing configurations in the parameter study and present some example output.
-Our finals results are presented in \secref{}.
-
-%\subsection{Future} %-----------------------------------------------------------
-    %\begin{itemize}
-    %\item New satellites will find many new lenses.
-    %\item LSST, DES, PanSTARRS?, SKA
-    %\item What is the most important data to have?
-    %\end{itemize}
-
-%\subsection{Present} %----------------------------------------------------------
-%    \begin{itemize}
-%    \item SLACS, CASTLES, CosmoGrail, CLASS, CFHTLS, SNAP?
-%    \end{itemize}
-
-%\subsection{Why do we need accurate galaxy models?} %---------------------------
-    %\begin{itemize}
-    %\item Galaxy formation
-    %\item Cusp/Core problem
-    %\item Universal halos?
-    %\item Adiabatic contraction
-    %\item DM fraction
-    %\end{itemize}
-
-%\subsection{Past work on constraining profiles.} %------------------------------
-    %\begin{itemize}
-    %\item Much of the early literature used simple SIS and SIE parametric models. Understandable.
-    %\item Bayesian model fitting
-    %\item Free-form modeling
-    %\item Keeton has a good review.
-    %\end{itemize}
-
-%\subsection{What are the problems?} %------------------------------
-    %\begin{itemize}
-    %\item Very little data per lens.
-    %\item Several well-known degeneracies.
-    %\item Velocity dispersions: aperture too small
-    %\end{itemize}
-
-%\subsection{Goals of the paper} %------------------------------
-%    \begin{itemize}
-%    \item Perform a parameter study over lens morphologies and quantify what they can tell us about profiles.
-%    \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Theoretical Background}
+\subsection{Adding stellar kinematic constraints}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Methods}
+\section{Numerical Methods}\label{sec:glass}
 

### 2013-06-12 limits/ms.tex
More work done on the theory section and general structure. Slowly getting there.

@@
 \usepackage{natbib}
+
+\def\newblock{\hskip .11em plus .33em minus .07em}
 
@@
 
-\title[\Glass]{Gravitational Lens Recovery with \Glass: Illustrating the power of free-form lens modelling}
+\title[\Glass]{Gravitational Lens Recovery with \Glass: Illustrating the power of non-parametric lens modelling}
 \author{%
@@
 {\bf JR. Does \Glass\ stand for something?}\\
-We introduce a new free-form gravitational lens modelling tool \Glass\ that builds on an earlier code \PixeLens.
+We introduce a new non-parametric gravitational lens modelling tool \Glass\ that builds on an earlier code \PixeLens.
 Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
@@
 
-\section{Introduction}\label{sec:intro}
+\section{Introduction}\label{sec:intro} %-----------------------------------------------------
+
 {\bf JR. Lots of references missing here. Need to be added. But this should get us started.}\\
@@
 In non-parametric mass modelling, the lens inversion problem is deliberately chosen to be under-constrained \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}.
-Instead of finding one `best-fit' model, we must search for many models consistent with the data, exploring degeneracies between different but plausible\footnotemark\ mass models \citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}.
+Instead of finding one `best-fit' model, we must then search for many models consistent with the data, exploring degeneracies between different but plausible\footnotemark\ mass models \citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}.
 The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including data from stellar population synthesis modelling, stellar kinematics, or other indepedent probes of the mass) are required to measure parameters of interest.
@@
 
-In this paper, we present a new free-form or `non-parametric' strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}.
+In this paper, we present a new non-parametric strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}.
 Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
@@
 
-\section{Theoretical Background}\label{sec:theory}
+\section{Theoretical Background}\label{sec:theory} %-----------------------------------------------------
 
-\subsection{What can we learn from strong lensing data?}
+\subsection{Lensing basics}\label{sec:lensing_basic} %-----------------------------------------------------
 
-\subsection{The utility of stellar mass estimates}
-
-\subsection{Adding stellar kinematic constraints}
-
-\subsection{Lensing}
-
-The lensing equation
+The lens equation:
 %
@@
 \vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
-\label{lensing equation}
+\label{eqn:lens_equation}
 \end{equation}
@@
 maps an observed image position $\vec\theta$ to a source position $\vec\beta$
-via the correction factor 
+via the correction factor:
 %
@@
 %
-which accounts for the gravitational lensing effect of an intervening mass. For
+which accounts for the gravitational lensing effect of an intervening mass \citep[e.g.][]{1992grle.book.....S}. For
 our purposes we make use of the thin mass sheet approximation and assume that
 the lensing mass is infinitely thin compared with the distance between the
-source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These
-distances are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
+source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
 a dimensionless number that depends on cosmology.  The lens can then be thought
@@
 
-The arrival (or travel) time $t$ of a photon depends not only on the geometric
+One way to understand the lens equation is via Fermat's principle. We can think of light as travelling only 
+along extremum paths; lensed images only occur at the extrema of a virtual photon {\it arrival time surface} 
+\citep{1986ApJ...310..568B}. The arrival (or travel) time $t$ of a virtual photon depends not only on the geometric
 path it takes, but also on the general relativistic gravitational time dilation
 due to the lens at a redshift of $z_L$.  In its complete form, with all units
-and cosmology included we can write the arrival time as
+and cosmology included we can write the arrival time as \citep{1986ApJ...310..568B}:
 %
-\begin{equation}
-N^2ct(\vec\theta) = (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
-\label{full arrival time}
-\end{equation}
+\begin{eqnarray}
+N^2ct(\vec\theta) & = & (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 \nonumber \\
+& & - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
+\label{eqn:full_arrival_time}
+\end{eqnarray}
 %
-The non-standard factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
+where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
 has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
-delay 
+delay:
 %
-\begin{equation}
-\tau = \left[(1+z_L)D_{L}\right]^{-1}ctN^2 = \left[ (1+z_L) \frac{c}{H_0}d_L\right]^{-1}ctN^2 = \left[ (1+z_L) d_L\right]^{-1}\nu t
+\begin{eqnarray}
+\tau & = & \left[(1+z_L)D_{L}\right]^{-1}ctN^2 \nonumber \\
+& = & \left[ (1+z_L) \frac{c}{H_0}d_L\right]^{-1}ctN^2 \nonumber \\
+& = & \left[ (1+z_L) d_L\right]^{-1}\nu t
 \label{tau}
-\end{equation}
+\end{eqnarray}
 %
 in terms of our previous definitions. If we
-further define a dimensionless density
+further define a dimensionless density:
 %
@@
 %
-and a lensing potential
+and a lensing potential:
 %
@@
 %
-we can express \eqnref{full arrival time} very compactly as
+we can express \eqnref{eqn:full_arrival_time} very compactly as:
 %
@@
 
-If we think of $\tau$ as a surface then images will be observed where ever
+If we think of $\tau$ as a surface then images will be observed wherever
 $\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
-extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation} or
+extremums of the surface. Note that $\nabla \tau$ is just equation \ref{eqn:lens_equation} or:
 \begin{equation}
@@
 
-\subsection{Degeneracies} %-----------------------------------------------------
+\subsection{Degeneracies}\label{sec:degen} %-----------------------------------------------------
+
+The trouble with solving the lens equation for the mass distribution is that the solutions are non-unique and degenerate -- many different solutions can give a statistically good reproduction of the data.
+To see why this is, it is instructive to simplify equation \ref{eqn:lens_equation} for a circularly symmetric lens:
 
@@
 
-%
-%The steepness degeneracy arbitrarily rescales the arrival time surface. Image
-%positions are left alone but the density profile will become shallower or
-%steeper. This is particularly bad for inferring the Hubble constant, as the
-%lens profile will tend to become steeper for larger values of $H_0$.
-%
-%Other degeneracies include ring degeneracies, where one is allowed to build
-%up a density distribution as a series of mass rings; the presence of substructure;
-%and the effects of merging galaxies. 
-%
-%Shape degeneracy---a twisting in the density.
+\subsection{The utility of stellar mass estimates}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Adding stellar kinematic constraints}
+
 \section{Numerical Methods}\label{sec:glass}
@@
 \Glass\ samples a convex polytope in a high dimensional space whose interior
-points are solutions to the lensing equation and satisfy other physically
+points are solutions to the lens equation and satisfy other physically
 motivated linear priors (the sampling algorithm in \Glass\ is not the same as
@@
 lens plane. The centers $\vec\theta_i$ of each of the grid cells are mapped
-back onto the source plane using \eqnref{lensing equation}. If the location on
+back onto the source plane using \eqnref{eqn:lens_equation}. If the location on
 the source plane $\vec\beta_i$ is within a user specified
@@
 
-\section{Parameter study}
+\section{The mock data}\label{sec:mockdata}
 
@@
 
-\subsection{Mock galaxy data}
+\subsection{Setting up the triaxial N-body mocks}
 
@@
 
-Each of these configurations were modeled with and without time delays and with
+Each of these configurations were modelled with and without time delays and with
 and without a central image. We assumed for all our tests that the lensing mass
@@
 inner profile.
+
+\section{Results}\label{sec:results}
 
@@
 
-The main results from modeling these different configuration are shown black in
+The main results from modelling these different configuration are shown black in
 \figref{main results}. Each subplot corresponds to a different galaxy and
@@
 
-\section{Results} %--------------------------------------------------------------
-
-%\subsection{Shape fitting}
-
-%\subsection{Using principle component analysis to find new degeneracies}
-
-\section{Discussion}
+\section{Conclusions}\label{sec:conclusions}
 

### 2013-06-12 limits/ms.tex
Edited the abstract along the lines suggested by P.: tone down non-parametric emphasis and connection with PixeLens, and focus instead on the interesting results! Title changed also to reflect this. Will update the introduction accordingly also, but am working on the theory section for the moment.

@@
 
-\title[\Glass]{Gravitational Lens Recovery with \Glass: Illustrating the power of non-parametric lens modelling}
+\title[\Glass]{Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens}
 \author{%
@@
 {\bf JR. Does \Glass\ stand for something?}\\
-We introduce a new non-parametric gravitational lens modelling tool \Glass\ that builds on an earlier code \PixeLens.
-Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
-However, \Glass\ improves on \PixeLens\ in a number of important respects: (i) it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors; (ii) it is built on a fully modular framework that can support different basis functions; (iii) non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented); (iv) the stellar mass (if known) can be applied as a prior; and (v) adaptive resolution can be used in regions of interest.
-We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data -- from lensing, stellar kinematics and/or stellar masses -- are required to measure the circularly averaged mass profile of a lens and its shape.
+We introduce a new non-parametric gravitational lens modelling tool: \Glass.
+\Glass\ uses an adaptive grid of mass pixels to model the lens, searching through hundreds of thousands of models to marginalise over model uncertainties.
+It is built on a fully modular framework that can support different basis functions, while non-lensing data constraints -- for example stellar mass estimates from stellar population synthesis modelling, or stellar kinematic data -- can also be applied.
+As a first application, we apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data -- strong lensing, stellar kinematics, and/or stellar masses -- are required to measure the circularly averaged mass profile of a lens and its shape.
 Our key findings are as follows: (i) for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy; (ii) a single quad with time delays also performs well, giving a good recovery of both the mass profile and its shape; (iii) stellar masses -- for lenses where the stars dominate the central potential -- can also break the steepness degeneracy, giving a recovery almost as good as having time delay data or multiple source redshifts; (iv) stellar kinematics are similarly powerful if the data extend beyond the half light radius of the stars $r \gg r_{1/2}$ (required to integrate out the effect of the unknown velocity anisotropy, $\beta(r)$); and (v) if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right.
@@
 
+%(Linear constraints are applied simultaneously with the lens constraints; non-linear constraints are applied in post-processing, with models accepted or rejected based on their likelihood.) 
+%These are quantities of key interest for probing the dark matter distribution in galaxies and galaxy clusters to test galaxy formation models and cosmology.
+
 \section{Introduction}\label{sec:intro} %-----------------------------------------------------
@@
 {\bf JR. Lots of references missing here. Need to be added. But this should get us started.}\\
+{\bf JR. I updated the abstract to lower the emphasis on non-parametric modelling and the connection with PixeLens. I will perform similar edits on the introduction too (c.f. comment from Prasenjit.}
 
@@
 To see why this is, it is instructive to simplify equation \ref{eqn:lens_equation} for a circularly symmetric lens:
+%
+\begin{equation}
+\vec\beta = \vec\theta - \frac{\theta_E^2}{|\vec\theta|^2}\vec\theta
+\label{eqn:lens_equation_circ}
+\end{equation}
+%
+where $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM}{c^2}$ is the Einstein radius.
 

### 2013-06-12 limits/ms.tex
further improvements on the intro along the lines suggested by P

@@
 {\bf JR. Lots of references missing here. Need to be added. But this should get us started.}\\
-{\bf JR. I updated the abstract to lower the emphasis on non-parametric modelling and the connection with PixeLens. I will perform similar edits on the introduction too (c.f. comment from Prasenjit.}
 
@@
 This in turn provides valuable constraints on the nature of dark matter \citep{2006ApJ...652L...5S,2013ApJ...765...25N}, on cosmological models \citep{2010Sci...329..924J, 2008ApJ...679...17C}, and on galaxy formation models \citep{2012MNRAS.424..104L}.
-To date, some $\sim$400 strong lenses are known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of large ground and space based surveys, this number is set to explode, with thousands of lenses expected to be discovered over the next ten years \citep{2012arXiv1206.1225A, 2010AAS...21540115M, 2004NewAR..48.1085K}.
+To date, some $\sim$400 strong lenses are known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of large ground and space based surveys, many thousands of lenses are expected to be discovered over the next ten years \citep{2012arXiv1206.1225A, 2010AAS...21540115M, 2004NewAR..48.1085K}.
 
-The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K, 2010GReGr..42.2151K}.
+With this coming explosion in lens data, it is timely to re-asses the impact of model degeneracies on quantities of interest like the circularly averaged density profile of a lens or its shape.
+Some significant work has already proceeded in this direction in the literature.
+XXX found that YYY.
+However, most of these studies employed simplified models that assume a specific analytic form for the lens and/or connect the shape of the underlying dark matter halo to its parent galaxy.
+Notable exceptions are XXX.
+As the quality and quantity of data improve, we can afford relax some of our historical model assumptions and attempt to actually {\it image} the distribution of mass in lensing galaxies and clusters.
+We refer to this as `non-parametric' mass modelling, where `non-' means that we deliberately employ far more model parameters than data constraints.
+Searching through our model parameter space, we can then explore model degeneracies and determine which data best break them.
+
+%The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K, 2010GReGr..42.2151K}.
 This is useful in that a simple model provides valuable physical insight.
@@
 The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including data from stellar population synthesis modelling, stellar kinematics, or other indepedent probes of the mass) are required to measure parameters of interest.
-
-\footnotetext{The word {\it plausible} encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data (priors) are typically required on the solution space in order to make it finite.
+%\footnotetext{The word {\it plausible} encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data (priors) are typically required on the solution space in order to make it finite.
 However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling.}
 
-In this paper, we present a new non-parametric strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}.
-Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
-However, \Glass\ improves on \PixeLens\ in a number of important respects:
+%that builds on an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}. Like \PixeLens, we
+
+In this paper, we present a new non-parametric strong lens modelling framework \Glass\ that uses an adaptive grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
+\Glass\ shares some aspects with an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but has important new functionality:
 

### 2013-06-12 limits/ms.tex
theory section largely finished

@@
 maps an observed image position $\vec\theta$ to a source position $\vec\beta$
-via the correction factor:
+via the correction factor \citep[e.g.][]{1992grle.book.....S}:
 %
@@
 %
-which accounts for the gravitational lensing effect of an intervening mass \citep[e.g.][]{1992grle.book.....S}. For
+which accounts for the gravitational lensing effect of an intervening mass (where $G$ is Newton's gravitational constant, and $c$ is the speed of light). For
 our purposes we make use of the thin mass sheet approximation and assume that
@@
 \begin{equation}
-\vec\beta = \vec\theta - \frac{\theta_E^2}{|\vec\theta|^2}\vec\theta
+\vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
 \label{eqn:lens_equation_circ}
@@
 %
-where $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM}{c^2}$ is the Einstein radius.
+where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.
 
-\begin{itemize}
-  \item Steepness
-  \item Shape
-  \item $H_0$
-  \item Rings
-  \item Cosmology
-\end{itemize}
-
-\subsection{The utility of stellar mass estimates}
-
-\subsection{Adding stellar kinematic constraints}
+For sources on-axis (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$.
+Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distances that depend on cosmological parameters (most strongly on the Hubble constant, $D_{L,S} \propto 1/H_0$).
+For fixed cosmology, a single source splitting into images in the most ideal situation gives us only an enclosed mass.
+This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case (CITES).
+Thus, to measure the mass profile of a lens, we require more information.
+This can come in the form of another source at different redshift that has its own Einstein radius, giving $M(<\theta_E')$.
+Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling (CITE), stellar kinematics (CITE), or similar.
+However, even with further information, higher order degeneracies remain.
+XXX showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while YYY find twisting degeneracies exist if ZZZ.
+These higher order degeneracies have a larger effect on shape measurement than the mass profile but remain largely uncharacterised in the literature.
+In \S\ref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
 
@@
 
-\subsection{A new lens modeling framework: \Glass}
+\subsection{A new lens modelling framework: \Glass}
 
-\Glass\ is an evolution of the concepts employed by the free form modeling tool
+\Glass\ is an evolution of the concepts employed by the free form modelling tool
 \PixeLens\ but completely rewritten in Python and C. The key improvements are:
@@
 At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
-linear space that represents the modeling solution space. This algorithm was
+linear space that represents the modelling solution space. This algorithm was
 described and tested in \cite{}. \Glass\ is also multi-threaded allowing it to
@@
 demonstrates that the velocity anisotropy can be inferred by combining lens
-modeling and independent velocity dispersion measurements. The lens breaks
+modelling and independent velocity dispersion measurements. The lens breaks
 the anisotropy degeneracy at a given aperture.

### 2013-06-13 limits/ms.tex
Put usenatbib in \documentclass to avoid variable redefinition problem on Jonathan's machine. Fix duplicate label.
further hacking on the introduciton. Looking more like it now but still a bit clunky ...

@@
 
-With this coming explosion in lens data, it is timely to re-asses the impact of model degeneracies on quantities of interest like the circularly averaged density profile of a lens or its shape.
-Some significant work has already proceeded in this direction in the literature.
-XXX found that YYY.
-However, most of these studies employed simplified models that assume a specific analytic form for the lens and/or connect the shape of the underlying dark matter halo to its parent galaxy.
-Notable exceptions are XXX.
-As the quality and quantity of data improve, we can afford relax some of our historical model assumptions and attempt to actually {\it image} the distribution of mass in lensing galaxies and clusters.
-We refer to this as `non-parametric' mass modelling, where `non-' means that we deliberately employ far more model parameters than data constraints.
-Searching through our model parameter space, we can then explore model degeneracies and determine which data best break them.
-
-%The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K, 2010GReGr..42.2151K}.
+The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K, 2010GReGr..42.2151K}.
 This is useful in that a simple model provides valuable physical insight.
@@
 Instead of finding one `best-fit' model, we must then search for many models consistent with the data, exploring degeneracies between different but plausible\footnotemark\ mass models \citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}.
-The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including data from stellar population synthesis modelling, stellar kinematics, or other indepedent probes of the mass) are required to measure parameters of interest.
-%\footnotetext{The word {\it plausible} encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data (priors) are typically required on the solution space in order to make it finite.
+The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including data from stellar population synthesis modelling, stellar kinematics, or other independent probes of the mass) are required to measure parameters of interest.
+
+\footnotetext{The word {\it plausible} encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data (priors) are typically required on the solution space in order to make it finite.
 However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling.}
 
-%that builds on an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}. Like \PixeLens, we
+In this paper, we use a new non-parametric strong lens modelling framework \Glass\ to determine what quality and combination of lensing, stellar mass, and stellar kinematic constraints best constrain the projected mass profile and shape of a gravitational lens.
+This is particularly timely given the coming explosion in strong lensing and complimentary data.
+Some significant work has already proceeded in this direction in the literature.
+\citet{2007ApJ...667..645R} were the first to test the recovery of strong lensing surface density profiles using mock data generated from N-body models {\bf JR.
+Is this true?}.
+They found that when including time delays, circularly averaged surface density distributions can sufficiently well-recovered to make interesting comparisons with theoretical models\footnote{Cosmological parameters, however, are more sensitive.
+\citet{2007ApJ...667..645R} found that over-restrictive model assumptions can lead to significant bias on the Hubble parameter, $H_0$, for example, explaining earlier tensions reported in the literature \citep[e.g.][]{2002astro.ph..4043K}.}.
+Since then, several groups have used N-body mock data to explore the fidelity of strong lensing reconstruction.
+\citet{2007MNRAS.380.1729L} explore the recovery of N-body models using a new non-parametric genetic algorithm.
+Such comparisons were key in the development of their novel `null-space' constraint that includes information about where there a no images in addition to where there are observed ones.
+XXX did YYY, finding ZZZ {\bf JR.
+I am sure there are many more references that ought to be added here.}.
+Here, we expand on these earlier works by considering not only the circularly averaged surface density profile of a lens, but also its shape, higher order measures of the mass recovery (a pixel-by-pixel comparison), and by considering the utility of wrapping in constraints from stellar mass estimates, or stellar kinematics.
 
-In this paper, we present a new non-parametric strong lens modelling framework \Glass\ that uses an adaptive grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties.
-\Glass\ shares some aspects with an earlier code \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but has important new functionality:
+We use a new lensing tool, \Glass\, that uses an adaptive grid of mass pixels to model the lens, generating thousands of models to marginalise over uncertainties.
+\Glass\ shares some heritage with an earlier code, \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several important respects:
 
@@
 
-We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data from strong lensing, stellar mass (derived from populations synthesis modelling) and/or stellar kinematics are required to measure the circularly averaged mass profile of a lens and its shape.
+This new functionality allows us to use model strong lens systems while wrapping in additional data constraints.
+Linear constraints -- like the stellar mass -- are applied simultaneously with the strong lensing constraints; non-linear constraints are applied in a post-processing step, where models are rejected using a likelihood analysis.
+This latter was prohibitively expensive with \PixeLens\ as only up to $\sim$1000 models could be generated in a reasonable time.
+With \Glass, we can routinely generate hundreds of thousands of models such that we can afford to discard some if they are inconsistent with independent data.
+In this first application of \Glass, we apply it to a suite of dynamically realistic mock N-body data to test the recovery of the circularly averaged mass profile of a lens and its shape.
 We will consider using strong lensing as a cosmological probe, and present the first results from \Glass\ applied to real data, in forthcoming papers.
@@
 These higher order degeneracies have a larger effect on shape measurement than the mass profile but remain largely uncharacterised in the literature.
+Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits (CITES); this {\it shear term} can, in principle, however, be constrained by data (CITES).
 In \S\ref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
+We assume throughout that the shear is negligible.
 
@@
 follow.
+
+\subsection{Removing models with extra images}
+
+\subsection{A post-processing module for stellar kinematics}
 

### 2013-06-13 limits/ms.tex
Switched some latex references to use \secref,\eqnref,etc. Formatting.

@@
-\documentclass[galley]{mn2e}
+\documentclass[galley,usenatbib]{mn2e}
 %\documentclass[twocolumn,galley]{mn2e}
@@
 \usepackage{graphicx}
-\usepackage{natbib}
 
@@
 \newcommand{\eqnref}[1] {Eq.~(\ref{#1})}
-\newcommand{\secref}[1] {Section~\ref{#1}}
+\newcommand{\secref}[1] {\S\ref{#1}}
 \newcommand{\appref}[1] {Appendix~\ref{#1}}
@@
 
-Since the discovery of the first gravitational lens \citep{1979Natur.279..381W}, lensing has become an increasingly important probe of the distribution of mass in the Universe \citep{1937ApJ....86..217Z,2012arXiv1206.1225A}.
-Strong lensing in particular provides a powerful probe of the mass distribution at the heart of galaxies and galaxy clusters given good enough data \citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}.
-This in turn provides valuable constraints on the nature of dark matter \citep{2006ApJ...652L...5S,2013ApJ...765...25N}, on cosmological models \citep{2010Sci...329..924J, 2008ApJ...679...17C}, and on galaxy formation models \citep{2012MNRAS.424..104L}.
-To date, some $\sim$400 strong lenses are known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of large ground and space based surveys, many thousands of lenses are expected to be discovered over the next ten years \citep{2012arXiv1206.1225A, 2010AAS...21540115M, 2004NewAR..48.1085K}.
+Since the discovery of the first gravitational lens
+\citep{1979Natur.279..381W}, lensing has become an increasingly important probe
+of the distribution of mass in the Universe
+\citep{1937ApJ....86..217Z,2012arXiv1206.1225A}. Strong lensing in particular
+provides a powerful probe of the mass distribution at the heart of galaxies and
+galaxy clusters given good enough data
+\citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}.
+This in turn provides valuable constraints on the nature of dark matter
+\citep{2006ApJ...652L...5S,2013ApJ...765...25N}, on cosmological models
+\citep{2010Sci...329..924J, 2008ApJ...679...17C}, and on galaxy formation
+models \citep{2012MNRAS.424..104L}. To date, some $\sim$400 strong lenses are
+known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of
+large ground and space based surveys, many thousands of lenses are expected to
+be discovered over the next ten years \citep{2012arXiv1206.1225A,
+2010AAS...21540115M, 2004NewAR..48.1085K}.
 
-The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K, 2010GReGr..42.2151K}.
-This is useful in that a simple model provides valuable physical insight.
-However, as data quality improves and the questions we ask of these data become more refined, it is important to re-asses the impact of our model assumptions.
-`Non-parameteric' methods -- that assume many more parameters than the available data constraints -- are invaluable in this respect.
-In non-parametric mass modelling, the lens inversion problem is deliberately chosen to be under-constrained \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}.
-Instead of finding one `best-fit' model, we must then search for many models consistent with the data, exploring degeneracies between different but plausible\footnotemark\ mass models \citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}.
-The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including data from stellar population synthesis modelling, stellar kinematics, or other independent probes of the mass) are required to measure parameters of interest.
+The majority of lens modelling efforts to date have focussed on `parametric'
+modelling, where simple theoretically motived models are fit using maximum
+likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K,
+2010GReGr..42.2151K}. This is useful in that a simple model provides valuable
+physical insight. However, as data quality improves and the questions we ask of
+these data become more refined, it is important to re-asses the impact of our
+model assumptions. `Non-parameteric' methods -- that assume many more
+parameters than the available data constraints -- are invaluable in this
+respect. In non-parametric mass modelling, the lens inversion problem is
+deliberately chosen to be under-constrained
+\citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}.
+Instead of finding one `best-fit' model, we must then search for many models
+consistent with the data, exploring degeneracies between different but
+plausible\footnotemark\ mass models
+\citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}. The key
+advantages of non-parametric modelling are that we can: (i) explore model
+degeneracies and marginalise over them; and (ii) we can determine what type and
+quality of data (including data from stellar population synthesis modelling,
+stellar kinematics, or other independent probes of the mass) are required to
+measure parameters of interest.
 
-\footnotetext{The word {\it plausible} encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data (priors) are typically required on the solution space in order to make it finite.
-However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling.}
+\footnotetext{The word {\it plausible} encodes the key hidden gremlin in
+non-parametric methods: constraints extra to the available data (priors) are
+typically required on the solution space in order to make it finite. However,
+even rather restrictive priors are far less restrictive than the implicit
+constraints inherent in parametric mass modelling.}
 
-In this paper, we use a new non-parametric strong lens modelling framework \Glass\ to determine what quality and combination of lensing, stellar mass, and stellar kinematic constraints best constrain the projected mass profile and shape of a gravitational lens.
-This is particularly timely given the coming explosion in strong lensing and complimentary data.
-Some significant work has already proceeded in this direction in the literature.
-\citet{2007ApJ...667..645R} were the first to test the recovery of strong lensing surface density profiles using mock data generated from N-body models {\bf JR.
-Is this true?}.
-They found that when including time delays, circularly averaged surface density distributions can sufficiently well-recovered to make interesting comparisons with theoretical models\footnote{Cosmological parameters, however, are more sensitive.
-\citet{2007ApJ...667..645R} found that over-restrictive model assumptions can lead to significant bias on the Hubble parameter, $H_0$, for example, explaining earlier tensions reported in the literature \citep[e.g.][]{2002astro.ph..4043K}.}.
-Since then, several groups have used N-body mock data to explore the fidelity of strong lensing reconstruction.
-\citet{2007MNRAS.380.1729L} explore the recovery of N-body models using a new non-parametric genetic algorithm.
-Such comparisons were key in the development of their novel `null-space' constraint that includes information about where there a no images in addition to where there are observed ones.
-XXX did YYY, finding ZZZ {\bf JR.
-I am sure there are many more references that ought to be added here.}.
-Here, we expand on these earlier works by considering not only the circularly averaged surface density profile of a lens, but also its shape, higher order measures of the mass recovery (a pixel-by-pixel comparison), and by considering the utility of wrapping in constraints from stellar mass estimates, or stellar kinematics.
+In this paper, we use a new non-parametric strong lens modelling framework
+\Glass\ to determine what quality and combination of lensing, stellar mass, and
+stellar kinematic constraints best constrain the projected mass profile and
+shape of a gravitational lens. This is particularly timely given the coming
+explosion in strong lensing and complimentary data. Some significant work has
+already proceeded in this direction in the literature.
+\citet{2007ApJ...667..645R} were the first to test the recovery of strong
+lensing surface density profiles using mock data generated from N-body models
+{\bf JR. Is this true?}. They found that when including time delays, circularly
+averaged surface density distributions can sufficiently well-recovered to make
+interesting comparisons with theoretical models\footnote{Cosmological
+parameters, however, are more sensitive. \citet{2007ApJ...667..645R} found that
+over-restrictive model assumptions can lead to significant bias on the Hubble
+parameter, $H_0$, for example, explaining earlier tensions reported in the
+literature \citep[e.g.][]{2002astro.ph..4043K}.}. Since then, several groups
+have used N-body mock data to explore the fidelity of strong lensing
+reconstruction. \citet{2007MNRAS.380.1729L} explore the recovery of N-body
+models using a new non-parametric genetic algorithm. Such comparisons were key
+in the development of their novel `null-space' constraint that includes
+information about where there a no images in addition to where there are
+observed ones. XXX did YYY, finding ZZZ {\bf JR. I am sure there are many more
+references that ought to be added here.}. Here, we expand on these earlier
+works by considering not only the circularly averaged surface density profile
+of a lens, but also its shape, higher order measures of the mass recovery (a
+pixel-by-pixel comparison), and by considering the utility of wrapping in
+constraints from stellar mass estimates, or stellar kinematics.
 
-We use a new lensing tool, \Glass\, that uses an adaptive grid of mass pixels to model the lens, generating thousands of models to marginalise over uncertainties.
-\Glass\ shares some heritage with an earlier code, \PixeLens\ \citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several important respects:
+We use a new lensing tool, \Glass\, that uses an adaptive grid of mass pixels
+to model the lens, generating thousands of models to marginalise over
+uncertainties. \Glass\ shares some heritage with an earlier code, \PixeLens\
+\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
+important respects:
 
@@
 
-This new functionality allows us to use model strong lens systems while wrapping in additional data constraints.
-Linear constraints -- like the stellar mass -- are applied simultaneously with the strong lensing constraints; non-linear constraints are applied in a post-processing step, where models are rejected using a likelihood analysis.
-This latter was prohibitively expensive with \PixeLens\ as only up to $\sim$1000 models could be generated in a reasonable time.
-With \Glass, we can routinely generate hundreds of thousands of models such that we can afford to discard some if they are inconsistent with independent data.
-In this first application of \Glass, we apply it to a suite of dynamically realistic mock N-body data to test the recovery of the circularly averaged mass profile of a lens and its shape.
-We will consider using strong lensing as a cosmological probe, and present the first results from \Glass\ applied to real data, in forthcoming papers.
+This new functionality allows us to use model strong lens systems while
+wrapping in additional data constraints. Linear constraints -- like the stellar
+mass -- are applied simultaneously with the strong lensing constraints;
+non-linear constraints are applied in a post-processing step, where models are
+rejected using a likelihood analysis. This latter was prohibitively expensive
+with \PixeLens\ as only up to $\sim$1000 models could be generated in a
+reasonable time. With \Glass, we can routinely generate hundreds of thousands
+of models such that we can afford to discard some if they are inconsistent with
+independent data. In this first application of \Glass, we apply it to a suite
+of dynamically realistic mock N-body data to test the recovery of the
+circularly averaged mass profile of a lens and its shape. We will consider
+using strong lensing as a cosmological probe, and present the first results
+from \Glass\ applied to real data, in forthcoming papers.
 
-This paper is organised as follows.
-In \S\ref{sec:theory}, we review the basic lensing, stellar population synthesis, and Jeans mass modelling theory we will need.
-We present some simple back-of-the-envelope calculations that illustrate what type and quality of data we are likely to need to measure mass profiles and shapes.
-In \S\ref{sec:glass}, we describe the \Glass\ lens inversion algorithm and its stellar kinematic post-processing module.
-In \S\ref{sec:mockdata}, we describe our mock N-body data and our ray tracing algorithm used to generate the images.
-In \S\ref{sec:results}, we present our results from applying \Glass\ to these mock data.
-Finally, in \S\ref{sec:conclusions} we present our conclusions.
+This paper is organised as follows. In \secref{sec:theory}, we review the basic
+lensing, stellar population synthesis, and Jeans mass modelling theory we will
+need. We present some simple back-of-the-envelope calculations that illustrate
+what type and quality of data we are likely to need to measure mass profiles
+and shapes. In \secref{sec:glass}, we describe the \Glass\ lens inversion
+algorithm and its stellar kinematic post-processing module. In
+\secref{sec:mockdata}, we describe our mock N-body data and our ray tracing
+algorithm used to generate the images. In \secref{sec:results}, we present our
+results from applying \Glass\ to these mock data. Finally, in
+\secref{sec:conclusions} we present our conclusions.
 
@@
 %
-which accounts for the gravitational lensing effect of an intervening mass (where $G$ is Newton's gravitational constant, and $c$ is the speed of light). For
-our purposes we make use of the thin mass sheet approximation and assume that
-the lensing mass is infinitely thin compared with the distance between the
-source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
-a dimensionless number that depends on cosmology.  The lens can then be thought
+which accounts for the gravitational lensing effect of an intervening mass
+(where $G$ is Newton's gravitational constant, and $c$ is the speed of light).
+For our purposes we make use of the thin mass sheet approximation and assume
+that the lensing mass is infinitely thin compared with the distance between the
+source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are
+angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is a
+dimensionless number that depends on cosmology.  The lens can then be thought
 of as a projected surface density $\Sigma$ which diverts the path of a photon
@@
 
-Since we will later want to model the density distribution with a computer it will
-be convenient to choose units that make the relevant quantities of order unity.
-We therefore measure lengths in light years, time in years, positions in
-arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
+Since we will later want to model the density distribution with a computer it
+will be convenient to choose units that make the relevant quantities of order
+unity.  We therefore measure lengths in light years, time in years, positions
+in arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
 arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to
@@
 $\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
-extremums of the surface. Note that $\nabla \tau$ is just equation \ref{eqn:lens_equation} or:
+extremums of the surface. Note that $\nabla \tau$ is just \eqnref{eqn:lens_equation} or:
 \begin{equation}
@@
 The trouble with solving the lens equation for the mass distribution is that the solutions are non-unique and degenerate -- many different solutions can give a statistically good reproduction of the data.
-To see why this is, it is instructive to simplify equation \ref{eqn:lens_equation} for a circularly symmetric lens:
+To see why this is, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens:
 %
@@
 Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits (CITES); this {\it shear term} can, in principle, however, be constrained by data (CITES).
-In \S\ref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
+In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
 We assume throughout that the shear is negligible.
@@
 %
-\PixeLens only allows for a shear term to be added to the potential (as shown
+\PixeLens\ only allows for a shear term to be added to the potential (as shown
 later in \eqnref{shear}) to account for mass external to model region. This
@@
 between images. The axes are measure in arcseconds.}
-\label{reconstruction}
+\label{arrival surfaces}
 \end{figure}

### 2013-06-13 limits/ms.tex
Fixed missing figure reference.

@@
 With the stellar mass lower bound, the improvement of the reconstruction
-quality shown in \figref{Test reconstructions} is quite dramatic for the
+quality shown in \figref{main results} is quite dramatic for the
 steepest mock galaxies (AC and BC). This is because these models are dominated

### 2013-06-25 limits/ms.tex
New versions of main results plots with full error bars and with pixel-wise chi.
More edits.

@@
 \begin{abstract}
-{\bf JR. Does \Glass\ stand for something?}\\
-We introduce a new non-parametric gravitational lens modelling tool: \Glass.
-\Glass\ uses an adaptive grid of mass pixels to model the lens, searching through hundreds of thousands of models to marginalise over model uncertainties.
-It is built on a fully modular framework that can support different basis functions, while non-lensing data constraints -- for example stellar mass estimates from stellar population synthesis modelling, or stellar kinematic data -- can also be applied.
-As a first application, we apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data -- strong lensing, stellar kinematics, and/or stellar masses -- are required to measure the circularly averaged mass profile of a lens and its shape.
+We use a new non-parametric gravitational -- \Glass -- to determine what quality of data (strong lensing, stellar kinematics, and/or stellar masses) are required to measure the circularly averaged mass profile of a lens and its shape.
+\Glass\ uses an under-constrained adaptive grid of mass pixels to model the lens, searching through thousands of models to marginalise over model uncertainties.
 Our key findings are as follows: (i) for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy; (ii) a single quad with time delays also performs well, giving a good recovery of both the mass profile and its shape; (iii) stellar masses -- for lenses where the stars dominate the central potential -- can also break the steepness degeneracy, giving a recovery almost as good as having time delay data or multiple source redshifts; (iv) stellar kinematics are similarly powerful if the data extend beyond the half light radius of the stars $r \gg r_{1/2}$ (required to integrate out the effect of the unknown velocity anisotropy, $\beta(r)$); and (v) if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right.
@@
 We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
+{\bf JR. Need to highlight also the shape recovery results here.} 
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro} %-----------------------------------------------------
-
-{\bf JR. Lots of references missing here. Need to be added. But this should get us started.}\\
-
 Since the discovery of the first gravitational lens
@@
 provides a powerful probe of the mass distribution at the heart of galaxies and
-galaxy clusters given good enough data
-\citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}.
-This in turn provides valuable constraints on the nature of dark matter
-\citep{2006ApJ...652L...5S,2013ApJ...765...25N}, on cosmological models
-\citep{2010Sci...329..924J, 2008ApJ...679...17C}, and on galaxy formation
-models \citep{2012MNRAS.424..104L}. To date, some $\sim$400 strong lenses are
+galaxy clusters \citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}, giving valuable constraints on the nature of dark matter \citep{2006ApJ...652L...5S,2013ApJ...765...25N}, cosmology
+\citep{2010Sci...329..924J, 2008ApJ...679...17C}, and galaxy formation \citep{2012MNRAS.424..104L}. To date, some $\sim$400 strong lenses are
 known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of
@@
 parameters than the available data constraints -- are invaluable in this
-respect. In non-parametric mass modelling, the lens inversion problem is
-deliberately chosen to be under-constrained
-\citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}.
-Instead of finding one `best-fit' model, we must then search for many models
+respect \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}. Here, the lens inversion problem is
+deliberately chosen to be under-constrained.
+Instead of finding one `best-fit' model, we must search for many models
 consistent with the data, exploring degeneracies between different but
@@
 degeneracies and marginalise over them; and (ii) we can determine what type and
-quality of data (including data from stellar population synthesis modelling,
-stellar kinematics, or other independent probes of the mass) are required to
-measure parameters of interest.
+quality of data are required to measure parameters of interest.
 
-\footnotetext{The word {\it plausible} encodes the key hidden gremlin in
-non-parametric methods: constraints extra to the available data (priors) are
-typically required on the solution space in order to make it finite. However,
-even rather restrictive priors are far less restrictive than the implicit
-constraints inherent in parametric mass modelling.}
+\footnotetext{Constraints extra to the available data are typically required on the solution space in order to make it finite.
+Such constraints -- priors -- are typically chosen to eliminate theoretically implausible solutions (an extreme example might be if all of the mass lies in one corner of the lens model space, or if the mass fluctuates wildly on the smallest scales probed).
+Such priors are typically far less restrictive than the implicit constraints inherent in parametric mass modelling.}
 
-In this paper, we use a new non-parametric strong lens modelling framework
-\Glass\ to determine what quality and combination of lensing, stellar mass, and
+In this paper, we use a new non-parametric strong lens modelling framework -- 
+\Glass\ -- to determine what combination of lensing, stellar mass, and
 stellar kinematic constraints best constrain the projected mass profile and
-shape of a gravitational lens. This is particularly timely given the coming
-explosion in strong lensing and complimentary data. Some significant work has
-already proceeded in this direction in the literature.
+shape of a gravitational lens. Some significant work has already proceeded in this direction in the literature.
 \citet{2007ApJ...667..645R} were the first to test the recovery of strong
@@
 parameter, $H_0$, for example, explaining earlier tensions reported in the
-literature \citep[e.g.][]{2002astro.ph..4043K}.}. Since then, several groups
+literature \citep[e.g.][]{2002ApJ...578...25K,2002astro.ph..4043K}.}. Since then, several groups
 have used N-body mock data to explore the fidelity of strong lensing
-reconstruction. \citet{2007MNRAS.380.1729L} explore the recovery of N-body
-models using a new non-parametric genetic algorithm. Such comparisons were key
-in the development of their novel `null-space' constraint that includes
-information about where there a no images in addition to where there are
-observed ones. XXX did YYY, finding ZZZ {\bf JR. I am sure there are many more
-references that ought to be added here.}. Here, we expand on these earlier
-works by considering not only the circularly averaged surface density profile
+reconstructions \citep{2007MNRAS.380.1729L, CITES}. We expand on these earlier
+works by considering not only the recovery of the circularly averaged surface density profile
 of a lens, but also its shape, higher order measures of the mass recovery (a
-pixel-by-pixel comparison), and by considering the utility of wrapping in
-constraints from stellar mass estimates, or stellar kinematics.
-
-We use a new lensing tool, \Glass\, that uses an adaptive grid of mass pixels
-to model the lens, generating thousands of models to marginalise over
-uncertainties. \Glass\ shares some heritage with an earlier code, \PixeLens\
-\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
-important respects:
-
-\begin{enumerate} 
-\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
-\item it is built on a fully modular framework that can support different basis functions;
-\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
-\item the stellar mass (if known) can be applied as a prior; and
-\item adaptive resolution can be used in regions of interest. 
-\end{enumerate}
-
-This new functionality allows us to use model strong lens systems while
-wrapping in additional data constraints. Linear constraints -- like the stellar
-mass -- are applied simultaneously with the strong lensing constraints;
-non-linear constraints are applied in a post-processing step, where models are
-rejected using a likelihood analysis. This latter was prohibitively expensive
-with \PixeLens\ as only up to $\sim$1000 models could be generated in a
-reasonable time. With \Glass, we can routinely generate hundreds of thousands
-of models such that we can afford to discard some if they are inconsistent with
-independent data. In this first application of \Glass, we apply it to a suite
-of dynamically realistic mock N-body data to test the recovery of the
-circularly averaged mass profile of a lens and its shape. We will consider
-using strong lensing as a cosmological probe, and present the first results
-from \Glass\ applied to real data, in forthcoming papers.
+pixel-by-pixel comparison), and the utility of wrapping in
+constraints from stellar mass estimates and/or stellar kinematics.
 
@@
 source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are
-angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is a
+angular diameter distances where $D_* = (c/H_0)d_*$, $H_0$ is the Hubble constant, and $d_*$ is a
 dimensionless number that depends on cosmology.  The lens can then be thought
@@
 One way to understand the lens equation is via Fermat's principle. We can think of light as travelling only 
-along extremum paths; lensed images only occur at the extrema of a virtual photon {\it arrival time surface} 
-\citep{1986ApJ...310..568B}. The arrival (or travel) time $t$ of a virtual photon depends not only on the geometric
-path it takes, but also on the general relativistic gravitational time dilation
-due to the lens at a redshift of $z_L$.  In its complete form, with all units
-and cosmology included we can write the arrival time as \citep{1986ApJ...310..568B}:
+along extremum paths where lensed images occur \citep{1986ApJ...310..568B}.
+Such paths occur at the extrema of the photon {\it arrival time surface} $t(\vec\theta)$ that depends on the geometric path the photon takes and the general relativistic gravitational time dilation
+due to a thin lens at redshift $z_L$. In its complete form, with all units
+and cosmology included, we have \citep{1986ApJ...310..568B}:
 %
@@
 %
-\begin{eqnarray}
-\tau & = & \left[(1+z_L)D_{L}\right]^{-1}ctN^2 \nonumber \\
-& = & \left[ (1+z_L) \frac{c}{H_0}d_L\right]^{-1}ctN^2 \nonumber \\
-& = & \left[ (1+z_L) d_L\right]^{-1}\nu t
+\begin{equation}
+\tau = \left[ (1+z_L) d_L\right]^{-1}\nu t
 \label{tau}
-\end{eqnarray}
+\end{equation}
 %
@@
 that there is no source distance factor involved. This will be useful later when we consider
-multiple sources.
+multiple sources. Notice that the constraint $\nabla \tau = 0$ -- i.e. extrema in the arrival time surface -- recovers the lens equation (\eqnref{eqn:lens_equation}).
 
-If we think of $\tau$ as a surface then images will be observed wherever
-$\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
-extremums of the surface. Note that $\nabla \tau$ is just \eqnref{eqn:lens_equation} or:
-\begin{equation}
-  \xi \vec\beta = \xi \vec\theta - \frac 1\pi\int \kappa_\infty\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
-\end{equation}
-
-The only observables from \eqnref{arrival time} are the image positions, and
-perhaps the stellar contribution to $\kappa_\infty$.  If the source object is
-variable, however, then the observed light curves of each image will be
-identical, but possibly shifted in time due to the different arrival times.
+The only lensing observables from \eqnref{arrival time} are the image positions. However,  if the source object is
+variable then the observed light curves of each image will be
+identical but shifted in time due to the different photon path lengths.
 The time difference between identical portions of the light curves is called
@@
 arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
-\nu$. If $\beta$ and $\kappa_\infty$ were known exactly this would allow one
-to precisely infer the Hubble constant. However, the source position is not
+\nu$. If $\beta$ and $\kappa_\infty$ could be known exactly this would allow one
+to precisely infer the angular diameter distance to the lens and thus -- via a cosmological model -- the Hubble constant. However, the source position is not
 observable and the density distribution is highly degenerate.
@@
 
-The trouble with solving the lens equation for the mass distribution is that the solutions are non-unique and degenerate -- many different solutions can give a statistically good reproduction of the data.
+The trouble with solving the lens equation for the mass distribution is that the solutions are not unique.
 To see why this is, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens:
@@
 
-For sources on-axis (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$.
-Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distances that depend on cosmological parameters (most strongly on the Hubble constant, $D_{L,S} \propto 1/H_0$).
-For fixed cosmology, a single source splitting into images in the most ideal situation gives us only an enclosed mass.
-This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case (CITES).
+For on-axis sources (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$.
+Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distance.
+For fixed cosmology and in the most ideal situation, a single source splitting into images gives us only an enclosed mass.
+This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case \citep{1985ApJ...289L...1F,2000AJ....120.1654S}.
 Thus, to measure the mass profile of a lens, we require more information.
-This can come in the form of another source at different redshift that has its own Einstein radius, giving $M(<\theta_E')$.
-Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling (CITE), stellar kinematics (CITE), or similar.
+This can come in the form of sources at different redshifts -- since each has its own Einstein radius, each constrains a different enclosed mass $M(<\theta_E')$.
+Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling \citep{2008MNRAS.383..857F}, stellar kinematics \citep{2002MNRAS.337L...6T}, or similar.
 However, even with further information, higher order degeneracies remain.
-XXX showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while YYY find twisting degeneracies exist if ZZZ.
-These higher order degeneracies have a larger effect on shape measurement than the mass profile but remain largely uncharacterised in the literature.
-Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits (CITES); this {\it shear term} can, in principle, however, be constrained by data (CITES).
+\citet{2008MNRAS.386..307L} showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while \citep{2006ApJ...653..936S} find twisting/shape degeneracies that are sensitive to the time delays.
+Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits \citep[e.g.][]{1996ApJ...468...17B}; this {\it shear term} can, in principle, however, be constrained by data \citep[e.g.][]{2002ApJ...578...25K}.
 In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
 We assume throughout that the shear is negligible.
+
+\subsection{Stellar population synthesis modelling}
+
+GOT TO HERE.
+
+\subsection{Stellar kinematics}
 
@@
 \subsection{A new lens modelling framework: \Glass}
+
+\Glass\ uses an adaptive grid of mass pixels
+to model the lens, generating thousands of models to marginalise over
+uncertainties. It shares some heritage with an earlier code, \PixeLens\
+\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
+important respects:
+
+\begin{enumerate} 
+\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
+\item it is built on a fully modular framework that can support different basis functions;
+\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
+\item the stellar mass (if known) can be applied as a prior; and
+\item adaptive resolution can be used in regions of interest. 
+\end{enumerate}
+
+This new functionality allows us to include non-lensing data constraints. Linear constraints -- like the stellar
+mass -- are applied simultaneously with the strong lensing constraints;
+non-linear constraints are applied in a post-processing step, where models are
+rejected using a likelihood analysis. This latter was prohibitively expensive
+with \PixeLens\ as only up to $\sim$1000 models could be generated in a
+reasonable time. With \Glass, we can routinely generate hundreds of thousands
+of models such that we can afford to discard some if they are inconsistent with
+independent data.
 
@@
 \begin{figure}
-\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
+\plottwo{AAchi2_profile-full.pdf}{BBchi2_profile-full.pdf}
 
-\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
+\plottwo{ACchi2_profile-full.pdf}{BCchi2_profile-full.pdf}
 \caption{The main results showing the quality of model recovery. Each panel corresponds to 
@@
 indicate where the stellar mass has been given.}
+\label{main results}
+\end{figure}
+
+\begin{figure}
+\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
+
+\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
+\caption{Profile $\chi$ with $1\sigma$ error bars.}
+\label{main results}
+\end{figure}
+
+\begin{figure}
+\plottwo{AAchi2-full.pdf}{BBchi2-full.pdf}
+
+\plottwo{ACchi2-full.pdf}{BCchi2-full.pdf}
+\caption{Pixel-wise $\chi$.}
 \label{main results}

### 2013-06-25 limits/ms.tex
More edits.

@@
 We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
-{\bf JR. Need to highlight also the shape recovery results here.} 
 \end{abstract}
@@
 
+{\bf Is ``Schneider's degeneracy" something new? Should we cite it here? -- {\tt http://adsabs.harvard.edu/abs/2013arXiv1306.4675S}}
+
 \subsection{Stellar population synthesis modelling}
 
-GOT TO HERE.
+For many galaxy lenses, the central potential is dominated by the visible matter.
+In this situation, constraints on the stellar mass distribution are invaluable.
+\citep{2008MNRAS.383..857F} demonstrate that with just photometric data in XXX bands, and an assumed initial mass function for the stars, they are able to reliably constrain the stellar mass to XXX\% accuracy.
+This gives a constraint on the full lensing mass map:
 
-\subsection{Stellar kinematics}
+\begin{equation} 
+M(\vec\theta) > M_*(\vec\theta)
+\end{equation} 
+where $M_*$ is the stellar mass (see also similar work by ZZZZZ).
+Given the above work, we assume from here on that the stellar mass for our mock N-body data can be reliably determined and used as a lower-bound constraint on our lens models.
+
+{\bf JR. Prasenjit: you know more than me about this. Can you fill in the XXX's? We should probably also say a bit more about Ignacio's methodology and why the errors are so good etc etc.}
+
+\subsection{Stellar kinematics}\label{sec:kinematics}
+
+Another useful constraint follows from the velocity of stars within the lensing galaxy. Assuming spherical symmetry, stars obey the projected Jeans equations \citep[e.g.][]{2008gady.book.....B}:
+
+\begin{equation}
+\sigma_p^2(R) = \frac{2}{I(R)}\int_R^\infty dr\nu(r)f(r)\frac{GM(r)}{r}
+\label{eqn:sphericaljeans}
+\end{equation}
+where $\sigma_p$ is the projected velocity dispersion of the stars as a function of projected radius $R$; $I(R)$ is the surface density of the stars; $\nu(r)$ is the three dimensional stellar density; $f(r)$ is a function that depends only on the velocity anisotropy $\beta(r) = 1 - \sigma_t^2/\sigma_r^2$, where $\sigma_{t,r}$ are the tangential and radial velocity dispersions respectively:
+
+\begin{equation}
+f(r) = XXX;
+\end{equation} 
+$G$ is Newton's gravitational constant; and $M(r)$ is the mass profile that we would like to measure.
+
+It is immediately clear from \eqnref{eqn:sphericaljeans} that, even assuming spherical symmetry, we have a degeneracy between the enclosed mass profile $M(r)$ and the velocity anisotropy $\beta(r)$.
+This can be understood intuitively since $\beta(r)$ measures the relative importance of radial versus circular orbits and is intrinsically difficult to constrain given only one component of the velocity vector for each star.
+Nonetheless, $\beta(r)$ can be constrained given sufficiently many stars, since radial Doppler velocities sample eccentric orbits as $r\rightarrow 0$ and tangential orbits as $r\rightarrow \infty$ (CITES).
+It can also be estimated if an independent measure of $M(r)$ is available -- for example coming from strong lensing.
+Finally, we may integrate out the effect of unknown $\beta(r)$ by performing a luminosity weighted average over all radii:
+
+\begin{equation}
+\overline{\sigma} = \frac{\int_0^\infty I(R) \sigma_p^2(R) 2\pi R dR}{\int_0^\infty I(R) 2\pi R dR}
+\label{eqn:virialaverage}
+\end{equation} 
+This produces a single robust measure of the mass $\overline{\sigma}$ that is independent of $\beta(r)$, provided that the stellar system is in a dynamic quasi-equilibrium that obeys the virial theorem (CITES).
+In practice, we need not perform the above integral to infinity (this is impractical for real data since the surface brightness at large $R$ will eventually fall below the detection limit).
+Rather, we should see \eqnref{eqn:virialaverage} as a means to understand why fitting the projected velocity dispersion profile of stars gives us a single robust mass measure that is independent of $\beta(r)$ at some critical radius, typically $\sim$ the half light radius of the stellar distribution ($r_{1/2}$; CITES).
+
+We describe our numerical solution of \eqnref{eqn:sphericaljeans} in \S\ref{sec:glasskinematics} and present tests applied to mock data in \S\ref{sec:results}.
 
@@
 \subsection{A new lens modelling framework: \Glass}
-
-\Glass\ uses an adaptive grid of mass pixels
-to model the lens, generating thousands of models to marginalise over
-uncertainties. It shares some heritage with an earlier code, \PixeLens\
-\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
-important respects:
-
-\begin{enumerate} 
-\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
-\item it is built on a fully modular framework that can support different basis functions;
-\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
-\item the stellar mass (if known) can be applied as a prior; and
-\item adaptive resolution can be used in regions of interest. 
-\end{enumerate}
-
-This new functionality allows us to include non-lensing data constraints. Linear constraints -- like the stellar
-mass -- are applied simultaneously with the strong lensing constraints;
-non-linear constraints are applied in a post-processing step, where models are
-rejected using a likelihood analysis. This latter was prohibitively expensive
-with \PixeLens\ as only up to $\sim$1000 models could be generated in a
-reasonable time. With \Glass, we can routinely generate hundreds of thousands
-of models such that we can afford to discard some if they are inconsistent with
-independent data.
 
@@
 a higher resolution can be specified that only applies to the inner pixels. These
-pixels are subdivided into a smaller grid.
+pixels are subdivided into a smaller grid. {\bf JR. I think Jonathan is now applying this by default. Is that right Jonathan?} 
 %
@@
 linear space that represents the modelling solution space. This algorithm was
-described and tested in \cite{}. \Glass\ is also multi-threaded allowing it to
+described and tested in \cite{2012MNRAS.425.3077L}. \Glass\ is also multi-threaded allowing it to
 run efficiently on many-cored machines.  The software is freely available for
@@
 
-\subsection{Discrete models}
+%\Glass\ uses an adaptive grid of mass pixels
+%to model the lens, generating thousands of models to marginalise over
+%uncertainties. It shares some heritage with an earlier code, \PixeLens\
+%\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
+%important respects: 
+%\begin{enumerate} 
+%\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
+%\item it is built on a fully modular framework that can support different basis functions;
+%\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
+%\item the stellar mass (if known) can be applied as a prior; and
+%\item adaptive resolution can be used in regions of interest. 
+%\end{enumerate}
+%This new functionality allows us to include non-lensing data constraints. Linear constraints -- like the stellar
+%mass -- are applied simultaneously with the strong lensing constraints;
+%non-linear constraints are applied in a post-processing step, where models are
+%rejected using a likelihood analysis. This latter was prohibitively expensive
+%with \PixeLens\ as only up to $\sim$1000 models could be generated in a
+%reasonable time. With \Glass, we can routinely generate hundreds of thousands
+%of models such that we can afford to discard some if they are inconsistent with
+%independent data.
 
+\subsection{Discrete models}\label{sec:discrete}
 For this paper we will restrict ourselves to using the pixelated basis set that
@@
 
-\subsection{Removing models with extra images}
-
-\subsection{A post-processing module for stellar kinematics}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Raytracing}
-\label{Raytracing}
+\subsection{Raytracing}\label{Raytracing}
 \Glass\ can also determine the position of images and time delays from 
@@
 
+\subsection{Removing models with extra images}\label{sec:glassextraimages} 
+While linear constraints can be applied on-the-fly in \Glass, non-linear constraints must be applied in post-processing.
+Models that are inconsistent with such constraints must then be statistically discarded via a likelihood analysis.
+An example of such a non-linear constraint is the spurious presence of unobserved images.
+This `null-space' prior was first proposed and explored by \citet{2006MNRAS.367.1209L} and found to be extremely powerful.
+We find that our gradient prior in \Glass\ (see \S\ref{sec:discrete}), performs much of the same function as \citeauthor{2006MNRAS.367.1209L}'s null-space prior, but some models can still rarely turn up spurious images.
+We reject these in a post-processing step, where we sweep through the model ensemble applying the ray tracing algorithm described in \ref{Raytracing}.
+Models are accepted or rejected according to the criteria:
+
+\begin{equation}
+XXX
+\end{equation} 
+Typically, this results in a rejection rate of XXX\%.
+
+\subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
+Similarly to the null-space constraint (\S\ref{sec:glassextraimages}), stellar kinematic constraints constitute a non-linear prior on the mass map and must be applied in post-processing.
+We sweep through the model ensemble performing an Abel deprojection to determine $M(r)$ from the projected surface density assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B}:
+
+\begin{equation} 
+M(r) = XXX
+\end{equation} 
+This de-projection algorithm was tested on triaxial figures in \citet{2006ApJ...652L...5S}.
+They found that for triaxialities typical of our current cosmology, the method works extremely well unless the triaxial figure is projected directly along the line of sight such that we see the galaxy or galaxy cluster `down the barrel'.
+Such a situation is unlikely, but in any case avoidable since the resultant figure appears spherical in projection.
+This leads to the seemingly counter-intuitive result that the kinematic constraints -- that rely on the above de-projection -- are most secure for systems that do not appear spherical in projection (unless independent data can confirm the three dimensional shape is indeed very round).
+
+We use the deprojected mass to numerically solve equation \ref{eqn:sphericaljeans} for constant $\beta(r)$, assuming either $\beta(r) = 1$ or $\beta(r) = 0$ at all radii to bracket the two extremum situations.
+Where the data are good enough, these two may be distinguished giving dynamical information about $\beta(r)$.
+In more typical situations, however, we seek to simply marginalise over the effect of $\beta(r)$, using the stellar kinematics as a robust measure of $M(r_{1/2})$ (see \S\ref{sec:kinematics}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{The mock data}\label{sec:mockdata}
 
-We now present a study of four mock galaxies with known analytic forms to
-confirm that \Glass is able to correclty recover the mass profile.
+We now present a study of four mock galaxies with known analytic forms. These are used to
+verify that \Glass\ is able to correctly recover the mass profile, and -- more importantly -- to determine what type and quality of data best constrain the mass profile and shape of a lens.
+
+GOT TO HERE.
 

### 2013-06-27 limits/ms.tex
Justin finished adding text/changes for now. Action items to be done listed in the conclusions.

@@
 algorithm and its stellar kinematic post-processing module. In
-\secref{sec:mockdata}, we describe our mock N-body data and our ray tracing
-algorithm used to generate the images. In \secref{sec:results}, we present our
+\secref{sec:mockdata}, we describe our mock N-body data. In \secref{sec:results}, we present our
 results from applying \Glass\ to these mock data. Finally, in
@@
 arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to
-define a proxy to the Hubble constant $\nu \equiv N^2 H_0$.
+define a proxy to the Hubble constant $\zeta \equiv N^2 H_0$.
 
@@
 \begin{equation}
-\tau = \left[ (1+z_L) d_L\right]^{-1}\nu t
+\tau = \left[ (1+z_L) d_L\right]^{-1}\zeta t
 \label{tau}
@@
 \kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
-              = \frac{d_L}{\nu}\Sigma
+              = \frac{d_L}{\zeta}\Sigma
 \end{equation}
@@
 arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
-\nu$. If $\beta$ and $\kappa_\infty$ could be known exactly this would allow one
+\zeta$. If $\beta$ and $\kappa_\infty$ could be known exactly this would allow one
 to precisely infer the angular diameter distance to the lens and thus -- via a cosmological model -- the Hubble constant. However, the source position is not
@@
 The trouble with solving the lens equation for the mass distribution is that the solutions are not unique.
-To see why this is, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens:
+To see why, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens:
 %
@@
 \citet{2008MNRAS.386..307L} showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while \citep{2006ApJ...653..936S} find twisting/shape degeneracies that are sensitive to the time delays.
-Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits \citep[e.g.][]{1996ApJ...468...17B}; this {\it shear term} can, in principle, however, be constrained by data \citep[e.g.][]{2002ApJ...578...25K}.
+Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits \citep[e.g.][]{1996ApJ...468...17B}.
+However, this {\it shear term} can be constrained by data \citep[e.g.][]{2002ApJ...578...25K}.
 In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
@@
 \begin{equation}
-\sigma_p^2(R) = \frac{2}{I(R)}\int_R^\infty dr\nu(r)f(r)\frac{GM(r)}{r}
+\sigma_p^2(R) = \frac{2}{I(R)}\int_R^\infty dr \left(1-\beta \frac{R^2}{r^2}\right) \frac{\nu \sigma_r^2 r}{\sqrt{r^2 - R^2}};
 \label{eqn:sphericaljeans}
 \end{equation}
-where $\sigma_p$ is the projected velocity dispersion of the stars as a function of projected radius $R$; $I(R)$ is the surface density of the stars; $\nu(r)$ is the three dimensional stellar density; $f(r)$ is a function that depends only on the velocity anisotropy $\beta(r) = 1 - \sigma_t^2/\sigma_r^2$, where $\sigma_{t,r}$ are the tangential and radial velocity dispersions respectively:
-
 \begin{equation} 
-f(r) = XXX;
+\sigma_r^2(r) = \frac{r^{-2\beta}}{\nu}\int_r^\infty r'^{2\beta} \nu \frac{GM(r')}{r'^2}dr'
 \end{equation} 
-$G$ is Newton's gravitational constant; and $M(r)$ is the mass profile that we would like to measure.
+where $\sigma_p$ is the projected velocity dispersion of the stars as a function of projected radius $R$; $I(R)$ is the surface density of the stars; $\nu(r)$ is the three dimensional stellar density; $\sigma_{r,t}(r)$ are the radial and tangential velocity dispersions, respectively; $\beta(r) = 1 - \sigma_t^2/\sigma_r^2 = \mathrm{const.}$ is the velocity anisotropy (here assumed to be constant); $G$ is Newton's gravitational constant; and $M(r)$ is the mass profile that we would like to measure.
 
@@
 This can be understood intuitively since $\beta(r)$ measures the relative importance of radial versus circular orbits and is intrinsically difficult to constrain given only one component of the velocity vector for each star.
-Nonetheless, $\beta(r)$ can be constrained given sufficiently many stars, since radial Doppler velocities sample eccentric orbits as $r\rightarrow 0$ and tangential orbits as $r\rightarrow \infty$ (CITES).
+Nonetheless, $\beta(r)$ can be constrained given sufficiently many stars, since radial Doppler velocities sample eccentric orbits as $r\rightarrow 0$ and tangential orbits as $r\rightarrow \infty$ \citep[e.g.][]{2002MNRAS.330..778W}.
 It can also be estimated if an independent measure of $M(r)$ is available -- for example coming from strong lensing.
@@
 \begin{equation}
-\overline{\sigma} = \frac{\int_0^\infty I(R) \sigma_p^2(R) 2\pi R dR}{\int_0^\infty I(R) 2\pi R dR}
+\overline{\sigma} = \frac{\int_0^{a_p} I(R) \sigma_p^2(R) 2\pi R dR}{\int_0^{a_p} I(R) 2\pi R dR}
 \label{eqn:virialaverage}
 \end{equation} 
-This produces a single robust measure of the mass $\overline{\sigma}$ that is independent of $\beta(r)$, provided that the stellar system is in a dynamic quasi-equilibrium that obeys the virial theorem (CITES).
-In practice, we need not perform the above integral to infinity (this is impractical for real data since the surface brightness at large $R$ will eventually fall below the detection limit).
-Rather, we should see \eqnref{eqn:virialaverage} as a means to understand why fitting the projected velocity dispersion profile of stars gives us a single robust mass measure that is independent of $\beta(r)$ at some critical radius, typically $\sim$ the half light radius of the stellar distribution ($r_{1/2}$; CITES).
+where $a_p$ is the `aperture' over which the integral is performed.
+Ideally we should take $a_p \rightarrow \infty$, however this is not practical for real data where the surface brightness of the stars falls off rapidly with $a_p$.
+In practice, $a_p > 2r_{1/2}$, where $r_{1/2}$ is the half light radius of the stars, appears to be sufficient (see \S\ref{sec:results}).
+The above average produces a single robust measure of the mass $\overline{\sigma}$ that is independent of $\beta(r)$, provided that the stellar system is in a dynamic quasi-equilibrium that obeys the virial theorem \citep{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}.
+(Such an averaging procedure was first used in a combined lensing/stellar kinematic analysis in \citealt{2002MNRAS.337L...6T}.)
 
@@
 
+{\bf JR. Jonathan to fill in this section.}
+
 \subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
 Similarly to the null-space constraint (\S\ref{sec:glassextraimages}), stellar kinematic constraints constitute a non-linear prior on the mass map and must be applied in post-processing.
-We sweep through the model ensemble performing an Abel deprojection to determine $M(r)$ from the projected surface density assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B}:
+We sweep through the model ensemble performing an Abel deprojection to determine $M(r)$ from the projected surface density assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
 
-\begin{equation} 
-M(r) = XXX
-\end{equation} 
+\begin{eqnarray} 
+M(r) & = & \frac{\zeta}{d_L} \left[2\pi\int_0^r R\kappa_\infty(R)dR - \right. \nonumber \\
+& & \left. 4\int_r^\infty R\kappa_\infty(R)f\left(\frac{R}{r}\right)dR\right]
+\end{eqnarray} 
 This de-projection algorithm was tested on triaxial figures in \citet{2006ApJ...652L...5S}.
@@
 
-We now present a study of four mock galaxies with known analytic forms. These are used to
-verify that \Glass\ is able to correctly recover the mass profile, and -- more importantly -- to determine what type and quality of data best constrain the mass profile and shape of a lens.
-
-GOT TO HERE.
+We now present a study of four mock galaxies with known analytic forms.
+These are used to verify that \Glass\ is able to correctly recover the mass profile, and -- more importantly -- to determine what type and quality of data best constrain the mass profile and shape of a lens.
 
@@
 
-The four mock galaxies we consider have been designed to test our recovery
-procedure. They are two component models where the dark matter and stellar
-profiles are allowed to be steep and shallow.  The enclosed mass in all cases
-is fixed at $M(a_\star)= 1.8\e{10}$ at the scale radius $a_\star=2$ kpc. These
-values were chosen to closely resemble B1115. We therefore place the galaxy at
+We generate four two-component mock galaxies, where the dark matter and stellar
+profiles are allowed to be both steep and shallow.  The enclosed mass in all cases
+is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. These
+values were chosen to closely resemble the lensing galaxy B1115 \citep{1980Natur.285..641W}. We place the galaxy at
 a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
@@
 
-The galaxies were
-first generated as three dimensional particle distributions with the
-tool DEHNEN-TOOL. Each component follows the profile
+The galaxies were generated as three dimensional particle distributions as in \citet{2009MNRAS.395.1079D}. Each component follows the profile:
 \begin{equation}
-\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
+\rho(m) = \frac{M}{4\pi a^3}(3-\gamma){(m/a)^{-\gamma}(1 + m/a)^{\gamma-4}}
 \label{Dehnen profile}
 \end{equation}
-where $\gamma$ is the profile index and $a$ is the scale radius.  In the
-case $\gamma=1$ this is the Hernquist profile.  The four combinations of
-profile indices are shown in \tabref{mock galaxy params}.  Note that two of
-the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
-more accurate approximation would be an NFW or Einasto profile we are not
-probing the outer regions of the halo where the difference would be most
-extreme.  The Hernquist profile is easier to generate as it has finite mass.
+where $m^2 = (x/a)^2 + (y/b)^2 + (z/c)^2$, with $[a,b,c] = ???$; $\gamma$ is the central density profile index; and $a$ is the scale radius. In the
+case $\gamma=1$ (and in the limit of spherical symmetry), this is the Hernquist profile \citep{1990ApJ...356..359H}.  The four combinations of
+profile indices are shown in \tabref{mock galaxy params}. {\bf JR. Need to add explanation of triaxial parameters here. Is the above density equation correct in fact?}
 
@@
 \hline
-AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & \\
-AC & 1 & 4 & 1 & $11^2$ & 50 kpc & \\
-BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc & \\
-BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & 
+AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & DM; shallow\\
+AC & 1 & 4 & 1 & $11^2$ & 50 kpc & DM; cuspy\\
+BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc &  Star; shallow\\
+BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & Star; cuspy
 \end{tabular}
-\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
-\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
-all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
-$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$. $\Rmap$ is the 2d projected radius used to generate the lens configurations.}
+\caption{Profile parameters for the four mock galaxies. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
+all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$\,kpc.
+$\Rmap$ is the 2D projected radius used to generate the lens configurations.
+In the notes column we describe the mock as DM or star dominated with a shallow or cuspy central dark matter density profile.}
 \label{mock galaxy params}
@@
 
-\begin{figure}
-\plotthree{MockGalProfile-a.pdf} {MockGalProfile-b.pdf} {MockGalProfile-c.pdf}
-%\plotone{MockGalProfile-a.pdf} \plotone{MockGalProfile-b.pdf} \plotone{MockGalProfile-c.pdf}
-\caption{
-\textbf{(Left)} 
-Three-dimensional density of the galaxies showing the stellar, dark matter,
-and total densities with dotted, dashed, and solid lines, respectively. The
-grey lines show the analytic forms from \eqnref{Dehnen profile}. 
-\textbf{(Middle)} 
+\begin{figure*}
+\includegraphics[width=0.33\textwidth]{MockGalProfile-a.pdf} 
+\includegraphics[width=0.33\textwidth]{MockGalProfile-b.pdf} 
+\includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
+\caption{{\bf JR. Cut the analytic profiles from this Figure. All fonts and labels should be larger. Left panel should start at 0.7kpc.}
+\textbf{Left:} 
+Density averaged in spherical shells of the four galaxy mocks: AA, AC, BB and BC, showing the stellar (dotted), dark matter (dashed),
+and total (solid) densities, respectively. Notice that the stars in models BB and BC contribute significantly to the central potential. 
+\textbf{Middle:} 
 The radially averaged two-dimensional projected density.
-The critical density for lensing at $z_L=0.31$ is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
-\textbf{(Right)}
+The critical density for lensing at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
+\textbf{Right:}
 The enclosed projected mass.
@@
 \label{mock galaxies}
-\end{figure}
+\end{figure*}
 
-In \figref{mock galaxies} we show the 3D radial density, 
+In \figref{mock galaxies}, we show the 3D radial density, 
 the 2D projected density, and the 2D enclosed mass for each
-galaxy. Solid lines represent the total mass, dashed lines the dark 
-matter, and dotted lines the stellar mass. The projected plot has
-been normalized to the critical density.
+galaxy.
 
-\subsection{Lens configurations} %--------------------------------------------------------------
+\subsection{Lens configurations}\label{sec:lensconfig} %--------------------------------------------------------------
 
 For each of the four galaxies, we used the raytracing feature of \Glass\
-described in \secref{Raytracing} to construct 12 lensing scenarios:
+described in \secref{Raytracing} to construct 12 lensing scenarios {\bf JR. We have 12 lensing scenarios, but only 6 panels in Figure 2. Is this number correct?}:
 
 \begin{enumerate}
-\item One double and one extended double.
-\item One quad and one extended quad.
-\item Two 2-source quads with varying redshift contrast.
+\item one double and one extended double;
+\item one quad and one extended quad;
+\item two 2-source quads with varying redshift contrast.
 \end{enumerate}
+The `extended' configurations use multiple point sources at the same redshift to simulate an extended source (that will produce an arc-like image).
+\figref{arrival surfaces} shows the configuration for the extended quad, along with the other cases.
 
-The extended configurations use extra sources to generate extra images that
-simulate an arc. \figref{config ex.} shows the configuration for the extended
-quad.
-
-Each of these configurations were modelled with and without time delays and with
-and without a central image. We assumed for all our tests that the lensing mass
-was radially symmetric. By construction, this is known to be true and this is
-most often the case with real galaxies, unless there is an obvious observed
-asymmetry. The central pixel was refined into a further nine pixels to capture
-any steep rise in the profile. Two of the four mock galaxies have a steeply rising
-inner profile.
-
-\section{Results}\label{sec:results}
-
-\figref{reconstruction} shows a typical reconstruction of a
-lens. The far left plot shows the ensemble average arrival time surface with
-image marked as circles and the inferred source position as a diamond. The
-center plot shows the radial density profile. The error bars cover the full
-range of models generated by \Glass. The true density profile from the mock
-data is also plotted for comparison. The vertical lines mark the radial
-position of the images. The final plot on the right is of the enclosed mass. As
-expected the error bars are smallest in the region of the images where the most
-information about the lens is present. The dip in the profile at the end of the
-profile is due to the cut off in mass in the lensing map. This is of little
-importance, though, as there is no lensing information there.
-
-\begin{figure}
-\plotthree{BCQuadR1a_TmS-a.pdf}{BCQuadR1a_TmS-b.pdf}{BCQuadR1a_TmS-c.pdf}
-\caption{A typical reconstructed lens. Here we present a single quad lens from 
-the BC mock galaxy.
-\textbf{(Left)}
-The arrival time surface. 
-\textbf{(Middle)}
-The surface density. The magenta curve represents the dark matter component,
-the yellow curve the stellar component, and the blue curve is the sum of the two.
-The black curve comes from the original mass model used to create the lens.
-The green vertical lines mark the radial positions of the images. The higher
-resolution feature of \Glass\ has been used on the central pixel allowing the
-steep profile to be captured.
-\textbf{(Right)}
-The cumulative mass.}
-\label{reconstruction}
-\end{figure}
-
-The main results from modelling these different configuration are shown black in
-\figref{main results}. Each subplot corresponds to a different galaxy and
-the vertical axis shows the range of quality.  The quality of a
-model $\M_i$ by comparing the recovered density profile $\rho_\M(r)$ against
-the profile of the mock galaxy $\rho_G(r)$.  In particular, the plots show the
-RMS quantity
-%
-\begin{equation}
-  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
-  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
-\end{equation}
-%
-
-\begin{figure}
-\plottwo{AAchi2_profile-full.pdf}{BBchi2_profile-full.pdf}
-
-\plottwo{ACchi2_profile-full.pdf}{BCchi2_profile-full.pdf}
-\caption{The main results showing the quality of model recovery. Each panel corresponds to 
-the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
-each panel are six groups of results for each of six lens morphologies. Each morphology
-considered the presence of time delays and a central image. The black markers are for tests
-that did not include the stellar mass as a lower bound constraint, while the red markers
-indicate where the stellar mass has been given.}
-\label{main results}
-\end{figure}
-
-\begin{figure}
-\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
-
-\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
-\caption{Profile $\chi$ with $1\sigma$ error bars.}
-\label{main results}
-\end{figure}
-
-\begin{figure}
-\plottwo{AAchi2-full.pdf}{BBchi2-full.pdf}
-
-\plottwo{ACchi2-full.pdf}{BCchi2-full.pdf}
-\caption{Pixel-wise $\chi$.}
-\label{main results}
-\end{figure}
-
-\begin{figure}
-\plotone{BCarrival_surfaces}
+\begin{figure*}
+\includegraphics[width=0.85\textwidth]{BCarrival_surfaces}
 \caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
@@
 \label{arrival surfaces}
-\end{figure}
+\end{figure*}
 
-The morphological complexity increases from left to right within each plot. As
+Each of these configurations were modelled with and without time delays and with
+and without a central image.
+(The central image is typically highly demagnified.
+For galaxy lenses it is very difficult to find since it lies along the sight line to the bright lensing galaxy; in clusters, however, such images have been seen (CITES)).
+We assumed for all our tests that the lensing mass
+was radially symmetric ({\bf JR. Need to better-define this symmetry here.}. For our mock data, this is known to be true; it is
+most often the case with real galaxies, unless there is an obvious observed
+asymmetry. The central pixel was refined into a further nine pixels to capture
+any steep rise in the profile. Two of the four mock galaxies have a steeply rising
+inner profile. {\bf JR. What happens if we don't assume this symmetry? We ought to add an appendix showing this for one example case.}
+
+\section{Results}\label{sec:results}
+\figref{reconstruction} shows a typical reconstruction of a
+lens. The far left plot shows the ensemble average arrival time surface with
+image marked as circles and the inferred source position as a diamond. The
+center plot shows the radial density profile. The error bars cover the full
+range of models generated by \Glass {\bf JR.
+Why do this?
+Surely 1 or 2 sigma errors make more sense?
+I've deleted the ``full ensemble" results and kept the $1\sigma$ ones instead.}.
+The true density profile from the mock
+data is also plotted for comparison. The vertical lines mark the radial
+position of the images. The final plot on the right is of the enclosed mass. As
+expected, the error bars are smallest in the region of the images where the most
+information about the lens is present. The dip in the profile at the end of the
+profile is due to the cut off in mass in the lensing map. This is of little
+importance, though, as there is no lensing information there.
+
+\begin{figure*}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-a.pdf}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-b.pdf}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-c.pdf}
+\caption{
+{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} 
+A typical reconstructed lens. Here we present results for a single quad image lensed by the BC mock galaxy.
+\textbf{Left:}
+The arrival time surface. 
+\textbf{Middle:}
+The surface density. The magenta curve represents the dark matter component,
+the yellow curve the stellar component, and the blue curve is the sum of the two.
+The black curve comes from the original mass model used to create the lens.
+The green vertical lines mark the radial positions of the images. The higher
+resolution feature of \Glass\ has been used on the central pixel allowing the
+steep profile to be captured.
+\textbf{Right:}
+The cumulative mass.}
+\label{reconstruction}
+\end{figure*}
+
+The main results from modelling these different configuration are shown in black in
+\figref{main results}. Each subplot corresponds to a different galaxy and
+the vertical axis shows the range of `quality' of recovery, defined as: 
+%
+\begin{equation}
+  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
+  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
+\end{equation}
+where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.
+
+\begin{figure*}
+\includegraphics[width=0.49\textwidth]{AAchi2_profile.pdf}
+\includegraphics[width=0.49\textwidth]{BBchi2_profile.pdf}\\
+\includegraphics[width=0.49\textwidth]{ACchi2_profile.pdf}
+\includegraphics[width=0.49\textwidth]{BCchi2_profile.pdf}
+\caption{The main results showing the quality of model recovery. Each panel corresponds to 
+the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
+each panel are six groups of results for each of six lens morphologies. Each morphology
+considered the presence of time delays and a central image. The black markers are for tests
+that did not include the stellar mass as a lower bound constraint, while the red markers
+indicate where the stellar mass has been given. Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
+\label{main results}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.49\textwidth]{AAchi2-full.pdf}
+\includegraphics[width=0.49\textwidth]{BBchi2-full.pdf}\\
+\includegraphics[width=0.49\textwidth]{ACchi2-full.pdf}
+\includegraphics[width=0.49\textwidth]{BCchi2-full.pdf}
+\caption{{\bf JR. This should be also with $1\sigma$ errors. Also need to do this plot for Claudio's shape measure.} Pixel-wise $\chi$.}
+\label{main results pixel-wise}
+\end{figure*}
+
+The abundance of strong lensing data increases from left to right within each plot. As
 a result, there is a general trend for the reconstruction quality to increase
@@
 central image are present the quality is highest. A double is known to provide
-very little constraint on the mass distribution. This is particular evident in
+very little constraint on the mass distribution. This is particularly evident in
 galaxies AC and BC where the mass profile is steepest and the reconstruction of
@@
 
-The previous tests have been conducted to show that \Glass\ performs as expected.
-Here, we present a novel constraint that can significantly improve the models. 
-The stellar mass distribution is a lower bound on the total mass and in the
-central region of a galaxy is also the dominant component. It can therefore be
-used to constrain the innermost profile. We took the stellar mass directly from
+The stellar mass distribution gives a lower bound on the total mass.
+Where the stars dominate the central potential, it can provide a powerful constraint extra to the strong lensing data.
+We took the stellar mass directly from
 the generated galaxies and projected the particles onto the pixels. \Glass\
@@
 separate equations for each pixel.
+Although we assume a perfect recovery of the stellar mass here, it is straightforward to add errors as the stellar mass constraint remains linear: $\kappa_n = \kappa_{dm,n} + \epsilon \kappa_{s,n}$, where $\epsilon \sim 1$ is an additional error parameter.
 
@@
 steepest mock galaxies (AC and BC). This is because these models are dominated
-by stars in the inner region. The other two galaxies are unaffected because the
-models were already well modeled by the dark matter alone.
+by stars in the inner region. By contrast, the other two galaxies -- where the stars contribute negligibly to the potential -- are unaffected.
 
-\subsection{Velocity anisotropy}
+\subsection{Stellar kinematics}\label{sec:results_stellar_kinematics}
 
-In addition to the lens model aspects, \Glass\ can also run post processing
-routines to analyze each model as it is produced. We have developed a number of
-routines for fitting analytic models to the lensing mass profiles. One in
-particular deprojects the 2d profile assuming a Hernquist profile for the
-light. By fixing the velocity anisotropy $\beta$ we can determine the velocity
-dispersion of the model. Of course, the true velocity dispersion is known for
-the mock galaxies and we can compare our method to those measurements.  In
-\figref{sigma-beta} we plot the recovered velocity dispersion for $\beta=0$ and $\beta=1$
-over a range of aperture sizes for the BC Quad with time delays and stellar
-mass. The stellar half mass radius is plotted in yellow and the Einstein radius
-in black. For this configuration the two radii are well separated. This plot
-demonstrates that the velocity anisotropy can be inferred by combining lens
-modelling and independent velocity dispersion measurements. The lens breaks
-the anisotropy degeneracy at a given aperture.
+As outlined in \S\ref{sec:glass}, \Glass\ can also run post processing
+routines on the model ensemble which can be used to apply non-linear constraints.
+As an example, we consider here constraints from stellar kinematics.
+The models in the \Glass\ ensemble are processed as described in \S\ref{sec:glasskinematics}.
+To illustrate the power of stellar kinematic constraints, in
+\figref{sigma-beta}, we plot the projected velocity dispersion calculated for one model model (extracted from the full ensemble) of the BC Quad with time delays and stellar mass (left), and the mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging integral (the aperture size), $a_p$ (right).
+In both cases, we calculate curves for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
+Over-plotted is the correct answer for the BC model (black).
+The stellar half mass radius (yellow) Einstein radius (black) are marked by vertical lines.
+For this configuration, these two radii are well-separated.
 
-\begin{figure}
-\plotone{BCQuadR1a_TmS-sb.pdf}
-\caption{Estimated velocity dispersion as a function of the aperture size. The
-single quad lens model for the BC mock galaxy was deprojected and the mass
-profile fit assuming a Hernquist profile for the light. The top curve (blue)
-assumes a velocity anisotropy $\beta=1$, while the lower curve (green)
-assumes $\beta=0$. Given an independent estimate of the velocity dispersion,
-lensing can be used to place constraints on the velocity anisotropy.}
+Without even sweeping through the model ensemble and formally accepting/rejecting models, \figref{sigma-beta} already illustrates what we can hope to obtain from stellar kinematics.
+The most robust constraints follow if we can integrate out the effect of $\beta$ (right panel), since this is difficult to measure.
+For large enough aperture size ($a_p > 2r_{1/2}$), the average projected dispersion converges on a single well defined value independently of $\beta$.
+Since this converged value follows from the virial theorem, it is also rather insensitive to the shape of the potential \citep{2012ApJ...754L..39A}: it constitutes a robust constraint on the lensing potential.
+On the other hand, if the mass profile is well-constrained already at $r \sim r_{1/2}$, then we can use stellar kinematics to probe $\beta$.
+This can be seen in the left panel of \figref{sigma-beta}.
+Here we see that for a well-constrained mass model, the $\beta = 1$ curve lies significantly off from the true answer that has $\beta(r) \sim 0$.
+
+We now consider formally accepting/rejecting models from the full ensemble.
+We consider two regimes of interest: a model with a double where the mass profile is poorly constrained (XXX), and a model where the mass profile is very well constrained by the lens data (YYY).
+In the former case, we use $\overline{\sigma}(2 r_{1/2})$ to probe the mass independently of $\beta(r)$.
+We accept/reject models assuming a Gaussian error on measured $\overline{\sigma}(2 r_{1/2})$ of $\pm 10$\,km/s (similarly to the data quality presented for example in \citealt{2002MNRAS.337L...6T}).
+The results are shown in \figref{main results}, blue data points.
+In the latter case, we ask whether the data favour $\beta = 0$ or $\beta = 1$ by obtaining a $\chi^2$ goodness of fit measure between the true and modelled $\sigma_p(R)$.
+We accept/reject models from the ensemble above.
+The results for $\beta$ are shown in Figure ZZZ.
+
+The results for stellar kinematics match our expectations from \S\ref{sec:kinematics}.
+Where the lens data already constrain the mass distribution at $r \sim r_{1/2}$, stellar kinematics provide valuable information about the velocity anisotropy of the stars, $\beta$ (see Figure ZZZ).
+Where the lens data poorly constrain the mass distribution at $r_{1/2}$, we may `integrate out' the effect of unknown $\beta$ to obtain a robust measure of $M(r_{1/2})$ from the stellar kinematics.
+This latter is robust to both uncertainties in $\beta(r)$ and to our assumption of spherical symmetry in the kinematic models \citep{2012ApJ...754L..39A}.
+Finally, we note that there is a third interesting case.
+If the lens models well-constrain $M(r_{1/2})$ and stellar kinematics are available, then these can be used to probe cosmological models (see \S\ref{sec:theory}).
+We explore this in more detail in a separate publication.
+
+\begin{figure*}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS-sb.pdf}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS-sb.pdf}
+\caption{{\bf Left:} {\bf JR.
+Jonathan to add.} The projected velocity dispersion calculated for one model model (extracted from the full ensemble) of the BC Quad with time delays and stellar mass.
+{\bf Right:} The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging integral (the aperture size), $a_p$.
+In both cases, we calculate curves for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
+Over-plotted is the correct answer for the BC model (black) {\bf JR.
+Jonathan to add}.
+The stellar half mass radius (yellow) Einstein radius (black) are marked by vertical lines.
+For this configuration, these two radii are well-separated.}
 \label{sigma-beta}
-\end{figure}
+\end{figure*}
 
@@
 
-extensible framework
+{\bf JR. ACTION ITEMS.
 
-accurate reconstructions through better sampling
+\begin{enumerate}
 
-where stellar mass significant, including it greatly improves accuracy
+\item More references to be added to the introduction.
+Lots of work remains to be cited.
+Were we really the first to test lensing on N-body mocks?
+Perhaps for strong lensing, but certainly not for weak.
 
-breaking the vdisp/anisotropy degeneracy.
+\item Understand ``Schneider's degeneracy". Add reference/commentary accordingly.
+
+\item Prasenjit to write/finish section on stellar population synthesis modelling.
+
+\item Jonathan to complete \S\ref{sec:glass}. Emphasise need for central adaptive grid. Add appendix showing convergence as Pixrad is increased.
+
+\item Jonathan to write section \S\ref{sec:glassextraimages} on removing models with extra images.
+
+\item Clarify amount of triaxiality (and the analytic density profile) in \S\ref{sec:mockdata}.
+
+\item Clarify number of lens configurations in \S\ref{sec:lensconfig}.
+
+\item Add appendix showing how ``radial symmetry" prior affects results. Clarify meaning of this prior with a nice figure showing the symmetry.
+
+\item Show results for $1\sigma$ and $2\sigma$ rather than full \Glass\ ensemble.
+Add results for Claudio's shape measure.
+Discuss shape throughout results section and mention more explicitly in abstract and conclusions -- what quality of data do we need to robustly constrain the shape?
+
+\item Add example plot of the projected density and recovered projected density (c.f. plots Jonathan made for my ERC proposal).
+
+\item Tidy up figures and other small items as detailed throughout -- see {\tt {\bf JR ... }}.
+
+\item Add accept/reject results for stellar kinematics (two figures) as detailed in \S\ref{sec:results_stellar_kinematics}.
+
+\end{enumerate} 
+}
 
@@
 
+\section{Pixel resolution convergence test}
+{\bf JR. Need to add an appendix showing convergence with increasing Pixrad.}
+
 \bibliographystyle{mn2e}

### 2013-06-29 shapes/paper.tex
paper update

@@
 \textbf{Misalignments between stellar and dark matter distributions}
-Figure \ref{fig:misalignment} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
+Figure \ref{fig:moneyplots} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
 For lenses with a significant stellar component inside the outermost image radius, the distributions seem to be rather aligned.
@@
 For a smaller stellar contribution this is not necessarily the case.
-The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figures \ref{fig:1115rec} or \ref{fig:tsvetkova})) and \textit{RXJ0911} (Figure \ref{fig:911}).
+The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figure \ref{fig:1115rec}) and \textit{RXJ0911} (Figure \ref{fig:911}).
 While alignments between the distributions are preferred, they do not seem to be a necessary condition.

### 2013-07-06 shapes/paper.tex
paper update

@@
 Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
-The misalignment we see is thus not affected by different time delays.
+The significant misalignment we see is thus not affected by different time delays.
 
@@
 For lenses with a significant stellar component inside the outermost image radius, the distributions seem to be rather aligned.
-It seems that if the luminous mass is comparable to the dark matter mass, then the distributions align.
+It seems that if the luminous mass is comparable to the dark matter mass, the distributions align.
 For a smaller stellar contribution this is not necessarily the case.
-The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (Figure \ref{fig:1115rec}) and \textit{RXJ0911} (Figure \ref{fig:911}).
-While alignments between the distributions are preferred, they do not seem to be a necessary condition.
+The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (also Figure \ref{fig:1115rec}) and \textit{RXJ0911}.
+While alignments between the distributions are preferred, they do not seem to be the rule.
 
 The environment might also play a role.
-Red are the systems, which are isolated or no group resp.
-cluster environment has been found, green the ones in such an environment.
+Red are the systems, which are isolated and/or no group resp.
+cluster environment has been found yet, green the ones in such an environment.
 The misaligned systems are mainly the lenses with a known environment.
-Therefore, this misalignment could be caused by the external effects.
+Therefore, misalignments could be caused by the external effects.
 
@@
 The ellipticities of the distributions versus the mass ratio are shown in Figure \ref{fig:ellipticities}.
-We see, that every dark matter halo has a lower ellipticity $\lambda_{1}/\lambda_{2}$ and is thus closer to sphericity than the luminous galaxy.
-The systems \textit{HE1104} (Figure \ref{fig:1104}) and \textit{MG2016} (Figure \ref{fig:2016}) show especially large differences.
-It is not clear what could cause these
+We see that every dark matter halo has a lower ellipticity $\lambda_{1}/\lambda_{2}$ and is thus closer to sphericity than the luminous part of the galaxy.
+The systems \textit{B0712}, \textit{B1152} \textit{HE1104}, and \textit{MG2016} show especially large differences.
+It is not clear what could cause these discrepancies.
 
 Figure \ref{fig:misalignmentellipticities} shows the misalignment versus the ellipticity of the dark matter halo.
-There seem to be five different regions.
+It is possible to roughly subdivide it into five different regions.
 Almost spherical halos with good alignment of the semi-major axes, almost spherical halos with good alignment of semi-major and semi-minor axes (maximum misalignment between the semi-major axes), more elliptical, alligned halos, a seemingly 'forbidden' region for misalignments in between, and the upper right triangle, i.e.
@@
 Alignment with the semi-minor axis might be a stable configuration for almost spherical halos, while slightly smaller misalignments are unstable.
-There also seem to be some outliers as \textit{PG1115}, \textit{SBS1520}, and \textit{HE2149}.
+The systems \textit{Q0957}, \textit{PG1115}, \textit{B1422}, \textit{MG2016}, and \textit{HE2149} should be studied more closely as they could hold valuable information to decipher these relations.
 
 \textbf{Misalignments between the dark matter distributions and environment}
-Figure \ref{fig:environment} shows the misalignment between the direction to the group or cluster centroid resp.
-the companion galaxy with the dark matter halo.
-Although the error bars are huge, we immediately see that three lenses are basically aligned with the environment.
-The four other systems show slight misalignment.
+Figure \ref{fig:environment} we look at the alignment of the semi-major axes of the dark matter halos and vectors pointing to the centroid of the group or cluster or a companion galaxy.
+Although the error bars are huge, we see that five of these ten lenses, \textit{Q0047}, \textit{B0712}, \textit{Q0957}, \textit{PG1115}, and \textit{B1422}, are probably aligned or at least consistent with the environment.
+The other half show slight misalignment.
+
 Having a closer look at these lenses shows however that at least two of them might in fact be aligned.
@@
 \textit{Q0047} does not seem to be aligned with the direction of the group centroid.
-This could be due to the fact that the lens itself is quite far away from the centroid.
 The halo of \textit{B1030} is almost spherical, so the apparent misalignment could maybe be explained.
-It is also the only lens with only one companion galaxy.
-It is possible that in this case the effect of the environment is not strong enough.
-We however certainly lack data to make any claims for the systems with just one companion galaxy.
-Then, there is also \textit{MG2016}, which is not shown here, as the centroid was not measured in this cluster.
+\textit{MG2016} also has a known environment, is however not shown in this Figure as no estimate of the cluster centroid is given.
 There is however a high galaxy density towards the south-east, where also the cluster centroid probably lies.
-Judging from Figure \ref{fig:2016}, the halo seems to be aligned with the cluster centroid.
+The halo seems to be roughly aligned with the cluster centroid.
+%Add figure of this lens
 
-We conclude that lenses in groups or cluster are maybe aligned with the centroid.
-However, as we lack the statistics and as the errors on the centroid positions are huge, this claim might be disproved.
-It is not possible at this point to make a similar statement for lenses with just one companion galaxy.
+We conclude that lenses in groups or cluster are probably aligned with the centroid, i.e.
+the center of mass, consistent with what one might expect naively.
+The light however needs not be as stated earlier.
+%%%%%%%%%%%%%%%%%%
 

### 2013-07-10 limits/ms.tex
editing introduction

@@
 \renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}}
+
+\def\Sigmacrit{\Sigma_{\rm crit}}
 
@@
 \section{Introduction}\label{sec:intro} %-----------------------------------------------------
-Since the discovery of the first gravitational lens
-\citep{1979Natur.279..381W}, lensing has become an increasingly important probe
-of the distribution of mass in the Universe
-\citep{1937ApJ....86..217Z,2012arXiv1206.1225A}. Strong lensing in particular 
-provides a powerful probe of the mass distribution at the heart of galaxies and
-galaxy clusters \citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}, giving valuable constraints on the nature of dark matter \citep{2006ApJ...652L...5S,2013ApJ...765...25N}, cosmology
-\citep{2010Sci...329..924J, 2008ApJ...679...17C}, and galaxy formation \citep{2012MNRAS.424..104L}. To date, some $\sim$400 strong lenses are
-known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of
-large ground and space based surveys, many thousands of lenses are expected to
-be discovered over the next ten years \citep{2012arXiv1206.1225A,
-2010AAS...21540115M, 2004NewAR..48.1085K}.
 
-The majority of lens modelling efforts to date have focussed on `parametric'
-modelling, where simple theoretically motived models are fit using maximum
-likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K,
-2010GReGr..42.2151K}. This is useful in that a simple model provides valuable
-physical insight. However, as data quality improves and the questions we ask of
-these data become more refined, it is important to re-asses the impact of our
-model assumptions. `Non-parameteric' methods -- that assume many more
-parameters than the available data constraints -- are invaluable in this
-respect \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}. Here, the lens inversion problem is
-deliberately chosen to be under-constrained.
-Instead of finding one `best-fit' model, we must search for many models
-consistent with the data, exploring degeneracies between different but
-plausible\footnotemark\ mass models
-\citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}. The key
-advantages of non-parametric modelling are that we can: (i) explore model
-degeneracies and marginalise over them; and (ii) we can determine what type and
-quality of data are required to measure parameters of interest.
+Strong gravitational lenses are rare.  The reason is that the line of
+sight to a light source in the universe rarely goes through a region
+such that the projected density in its sky neighbourhood exceeds the
+critical density to produce multiple images.  To date, some $\sim400$
+strong lenses are known,\footnote{See {\tt http://www.masterlens.org}
+  for a catalogue.}  but this number is expected to increase to
+several thousand over the next ten years.  The optimism derives from
+new and upcoming surveys, both
+ground-based\footnote{http://pan-starrs.ifa.hawaii.edu}$^{\rm,}$\footnote{http://www.darkenergysurvey.org}
+and spacecraft,\footnote{http://www.euclid-ec.org} together with a
+community of citizen-science volunteers examining the image data for
+candidates.\footnote{http://spacewarps.org}
 
-\footnotetext{Constraints extra to the available data are typically required on the solution space in order to make it finite.
-Such constraints -- priors -- are typically chosen to eliminate theoretically implausible solutions (an extreme example might be if all of the mass lies in one corner of the lens model space, or if the mass fluctuates wildly on the smallest scales probed).
-Such priors are typically far less restrictive than the implicit constraints inherent in parametric mass modelling.}
+Since lensing depends only on gravity, strong lenses are a rather
+unique window on dark matter, and indirectly on the cosmological model
+as well, and hence the thousands of to-be-discovered lenses are
+eagerly awaited \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}.
+Extracting results from lensing, however, will require modelling, and
+it is towards that goal that the present work is directed.
+
+To see why lens modelling is of crucial importance, let us recall the
+essential quantities that appear in lensing.  First we have the
+distances: let $D_L$, $D_S$, $D_{LS}$ be the angular-diameter
+distances to the lens, source, and from lens to source; there are all
+strictly $\propto c/H_0$.  Typically
+\begin{equation}
+D_L \approx z \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
+\end{equation}
+The critical density for multiple images is
+\begin{equation}
+\Sigmacrit = \frac{c^2 D_L}{4\pi G} \frac{D_S}{D_{LS}}
+\end{equation}
+in mass per steradian.  The separation between the lensed images is of
+order the Einstein radius $\theta_E$.  The image separation is related
+to the mass by
+\begin{equation}
+\theta_E \sim \frac{R_G}{D_L} \frac{D_{LS}}{D_S}
+\end{equation}
+where $R_G$ is the gravitational radius $GM/c^2$.  If the source is a
+quasar or otherwise rapidly variable, a time delay is the variability
+will be present
+\begin{equation}
+\Delta t \sim R_G/c \,.
+\end{equation}
+So in principle, one can not only measure the mass of the lens, one
+can use the dependence on the cosmology-dependent $D$ factors to
+extract the cosmological model and all its parameters.
+\cite{1937ApJ....86..217Z} drew attention to the former, and
+\cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the latter,
+all long before lenses were discovered.  The difficulty became
+apparent soon after the discovery of the first lens by
+\cite{1979Natur.279..381W}.  In the first ever paper on lens
+modelling, \cite{1981ApJ...244..736Y} found that many plausible mass
+distributions could reproduce the data.
+
+% Simple parametric models are usually robust on qualitative features,
+% but other aspects can be very model-dependent
+% \citep[cf.~][]{2003AJ....125.2769S}.  For example, for lensed
+% quasars, there may be several models all providing excellent fits to
+% the image data but disagreeing on the expected time delays, but they
+% almost always agree about the {\em order\/} of time delays. Thus, a
+% simple model provides valuable physical insight, but as data quality
+% improves and the questions we ask of these data become more refined,
+% it is important to re-assess the impact of our model assumptions.
+% The key advantages of non-parametric modelling are that we can: (i)
+% explore model degeneracies and marginalise over them; and (ii) we
+% can determine what type and quality of data are required to measure
+% parameters of interest.
+
+\cite{1981ApJ...244..736Y} were remarkably prescient about the
+subsequent development of lens modelling.  First, the introduced the
+technique of choosing a parametric form for the lensing mass and then
+fitting for the parameters, which is still the most common strategy
+\citep[see for example][]{2010GReGr..42.2151K,2011A&ARv..19...47K}.
+Second, they pointed out the non-uniqueness of lens models, or lensing
+degeneracies.  Third, they suggested combining lensing data with
+stellar kinematics and X-rays, to reduce the effect of the
+degeneracies.  Later work, as well as following up these suggestions,
+has introduced some ideas.  Four of these are important in the present
+work.
+\begin{itemize}
+\item In free-form models, there is no specified parametric form for
+  the mass distribution.  There are still assumptions (or priors) on
+  the mass distribution, such as smoothness or being centrally
+  concentrated
+  \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C}
+  but these are much less restrictive than parametric forms.
+  \cite{2006MNRAS.367.1209L} implemented a particular elegant prior,
+  which is that the mass distribution must be non-negative and no
+  extra images are produced.  Free-form are at present most common for
+  cluster lenses\citep{2009ApJ...690..154S,2013arXiv1304.2393S}.
+\item Model ensembles, exploring a diverse range of possible mass
+  distributions that nonetheless all fit the data, are a way of
+  cambating the non-uniqueness of models.  Model ensembles are
+  possible in parametric models \citep{1999AJ....118...14B} but are
+  more common in free-form models
+  \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.
+\item Stellar kinematics has played a role in many modelling
+  techniques.  The underlying reason is the virial theorem, which
+  relates the line of sight velocity dispersion to the Einstein radius
+  as
+\begin{equation}
+  \frac{\langle v^2_{\rm los}\rangle}{c^2} \approx
+  \frac{\theta_E}{4\pi} \frac{D_S}{D_{LS}}
+\end{equation}
+  with the relation becoming exact for isothermal lenses.  The use of
+  two-dimensional kinematics by \cite{2011MNRAS.415.2215B} is
+  especially interesting.
+\item The stellar mass in a lens can be inferred from photometry and
+  compared with the total mass
+  \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
+  Since the inferred stellar mass does depend on the assumed IMF,
+  lenses in which stellar mass dominates can be used to derive upper
+  bounds on the stellar $M/L$ \cite{2010MNRAS.409L..30F}. Lower bounds
+  on stellar $M/L$ have also been claimed \citep{2013MNRAS.428.3183D}
+  but these require upper-bound assumptions about the dark-matter
+  profile.
+\item Testing modelling strategies to see how well they recover
+  simulated lenses is increasingly recognized as essential.  Simple
+  blind tests have appeared in earlier work \citep[for example, Figure
+    2 in][]{2000AJ....119..439W}, but more recently, test against
+  dynamically simulated galaxies are favoured
+  \citep{2007ApJ...667..645R,2009MNRAS.393.1114B}.
+\end{itemize}
+There are also more modelling ideas in the literature.  One is to use
+X-ray intensity and temperature profiles as a mass constraint
+\citep[such as in][]{2013ApJ...765...25N}.  Another idea is to model
+multiple lenses simultaneously, with one or more cosmological
+parameters variable but shared between the lenses.  This strategy has
+been used to constrain $H_0$ from time delays
+\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P}.
+In principle, cosmological parameters could be constrained even from a
+single lens.  Some models have attempted this, starting from a prior
+based on the values and uncertainties from CMB fluctuations
+\citep{2010Sci...329..924J,2013arXiv1306.4732S}, but tests using
+simulated lenses are desirable.
 

### 2013-07-11 limits/ms.tex
editing intro

@@
   which is that the mass distribution must be non-negative and no
-  extra images are produced.  Free-form are at present most common for
-  cluster lenses\citep{2009ApJ...690..154S,2013arXiv1304.2393S}.
+  extra images are produced.  Free-form are more commonly used with
+  cluster lenses\citep{2009ApJ...690..154S,2013arXiv1304.2393S}, but
+  can be used with galaxy lenses as well, where their less restrictive
+  assumptions can be important.  For example, in time-delay galaxy
+  lenses parametric models led to tensions with the Hubble parameter
+  $H_0$ \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}, but
+  the less restrictive assumptions of free-form models resolved these
+  tensions \citep{2007ApJ...667..645R}.
 \item Model ensembles, exploring a diverse range of possible mass
@@
   \frac{\langle v^2_{\rm los}\rangle}{c^2} \approx
-  \frac{\theta_E}{4\pi} \frac{D_S}{D_{LS}}
+  \frac{\theta_E}{6\pi} \frac{D_S}{D_{LS}}
 \end{equation}
@@
 In principle, cosmological parameters could be constrained even from a
-single lens.  Some models have attempted this, starting from a prior
-based on the values and uncertainties from CMB fluctuations
-\citep{2010Sci...329..924J,2013arXiv1306.4732S}, but tests using
+single lens.  Some models have attempted this
+\citep{2010Sci...329..924J,2013arXiv1306.4732S} starting from a prior
+based on the values and uncertainties from the CMB, but tests using
 simulated lenses are desirable.
 
-In this paper, we use a new non-parametric strong lens modelling framework -- 
-\Glass\ -- to determine what combination of lensing, stellar mass, and
-stellar kinematic constraints best constrain the projected mass profile and
-shape of a gravitational lens. Some significant work has already proceeded in this direction in the literature.
-\citet{2007ApJ...667..645R} were the first to test the recovery of strong
-lensing surface density profiles using mock data generated from N-body models
-{\bf JR. Is this true?}. They found that when including time delays, circularly
-averaged surface density distributions can sufficiently well-recovered to make
-interesting comparisons with theoretical models\footnote{Cosmological
-parameters, however, are more sensitive. \citet{2007ApJ...667..645R} found that
-over-restrictive model assumptions can lead to significant bias on the Hubble
-parameter, $H_0$, for example, explaining earlier tensions reported in the
-literature \citep[e.g.][]{2002ApJ...578...25K,2002astro.ph..4043K}.}. Since then, several groups
-have used N-body mock data to explore the fidelity of strong lensing
-reconstructions \citep{2007MNRAS.380.1729L, CITES}. We expand on these earlier
-works by considering not only the recovery of the circularly averaged surface density profile
-of a lens, but also its shape, higher order measures of the mass recovery (a
-pixel-by-pixel comparison), and the utility of wrapping in
-constraints from stellar mass estimates and/or stellar kinematics.
-
-This paper is organised as follows. In \secref{sec:theory}, we review the basic
-lensing, stellar population synthesis, and Jeans mass modelling theory we will
-need. We present some simple back-of-the-envelope calculations that illustrate
-what type and quality of data we are likely to need to measure mass profiles
-and shapes. In \secref{sec:glass}, we describe the \Glass\ lens inversion
-algorithm and its stellar kinematic post-processing module. In
-\secref{sec:mockdata}, we describe our mock N-body data. In \secref{sec:results}, we present our
-results from applying \Glass\ to these mock data. Finally, in
-\secref{sec:conclusions} we present our conclusions.
+In this paper, we use a new program --- \Glass\ --- to determine what
+combination of lensing, stellar mass, and stellar kinematic
+constraints best constrain the projected mass profile and shape of a
+gravitational lens.  The compute-intensive core of \Glass\ is a
+parallel implementation of the high-dimensional sampling algorithm
+from \cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has
+extensible code (in software terminology, a framework) in Python,
+encoding the lens equation, a basis and priors for the mass
+distribution, and various post-processing modules.  \Glass\ is
+described in \secref{sec:glass}.  In \secref{sec:theory} before that
+we review the elements of lensing theory, stellar population
+synthesis, and stellar dynamics we will need.
+
+In \secref{sec:mockdata}, we describe our mock data.
+
+In \secref{sec:results}, we present our results from applying \Glass\ to
+these mock data.
+
+\cite{2007ApJ...667..645R} were the first to test the recovery of
+strong lensing surface density profiles using mock data generated from
+N-body models {\bf JR. Is this true?}. They found that when including
+time delays, circularly averaged surface density distributions can
+sufficiently well-recovered to make interesting comparisons with
+theoretical models Cosmological parameters, however, are more
+sensitive. Since then, several groups have used N-body mock data to
+explore the fidelity of strong lensing reconstructions
+\citep{2007MNRAS.380.1729L}. We expand on these earlier works
+by considering not only the recovery of the circularly averaged
+surface density profile of a lens, but also its shape, higher order
+measures of the mass recovery (a pixel-by-pixel comparison), and the
+utility of wrapping in constraints from stellar mass estimates and/or
+stellar kinematics.
 

### 2013-07-21 slopes/lensing_li.tex
Fei's draft

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{myaasmacros}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{amsmath}
\usepackage{epstopdf}

% Some definitions of things I always use here:
\def\ltsima{$\; \buildrel < \over \sim \;$}
\def\simlt{\lower.5ex\hbox{\ltsima}}   
\def\gtsima{$\; \buildrel > \over \sim \;$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\newcommand\bcite[1]{\citeauthor{#1} \citeyear{#1}}

% Some definitions for the priors:
\def\gprior{{\tt gprior}}
\def\cprior{{\tt cprior}}
\def\bprior{{\tt bprior}}
\def\lbprior{{\tt lbprior}}

%Some definitions for rhodm etc:
\def\vztwo{\overline{v_z^2}}
\def\vztwoi{\overline{v_{z,i}^2}}
\def\rhodisc{\rho_\mathrm{disc}(z)}
\def\rhodmext{\rho_\mathrm{dm,ext}}
\def\rhodm{\rho_\mathrm{dm}}
\def\rhoeff{\rho_\mathrm{dm}^\mathrm{eff}}
\def\nuobs{\nu_\mathrm{obs}(z)}

\title[The dark matter density profile over five decades in mass]{The dark matter density profile over five decades in mass from strong lensing}

\author[Li]{Fei Li$^1$\thanks{E-mail: lif@phys.ethz.ch}, J. I. Read$^2$, J. Coles$^3$, P. Saha$^3$\\
$^1$ICFP, D\'{e}partement de Physique de l'\'{E}cole Normale Sup\'{e}rieure, 24 rue Lhomond, 75005 Paris, France\\
$^2$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
$^3$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland
}

\begin{document}

\maketitle

\begin{abstract}
Abstract here. 
\end{abstract}

\begin{keywords}
\end{keywords}

\section{Introduction}\label{sec:introduction}

Large N-body cosmological simulations have been carried out with the goal of making statistical predictions on dark matter (DM) halo properties. The result suggests that these halos are self-similar, with universal density profiles \citep[see e.g.,][]{Navarro, Diemand, Hayashi, Merritt, Graham, Moore}. However, while different baryonic effects play a crucial role when it comes to the central slope of the dark matter halo density profile, most of cosmological simulations contain dark matter particles only due to numerical issues \cite[see][]{Mayer}.

In this work, we aim to probe observationally the central density profiles of the underlying dark matter distribution of 25 lensing systems. The motivation for non-parametric mass reconstruction and the introduction to a new algorithm on non-parametric strong lensing employing the technique of pixelated lens models are given in Section \ref{parametric}. The reconstructed dark matter projected-mass maps are presented in Section \ref{mass}. In Section \ref{profile} we compare the inner density slopes of the lens sample with the result from dark matter only structure formation simulations in $\Lambda$CDM cosmology, and we discuss our results and conclude in Section \ref{sec:conclusions}.

\section{Methodology}\label{sec:method}
\subsection{Non-parametric modeling: the GLASS algorithm}\label{parametric}
For most lensed images, it is fairly easy to fit a model galaxy lens to the image positions and hence provide a map of the total sky-projected mass \citep{IF}. But such a map, although a reasonable first approximation, will be nonunique because of degeneracies. While parametric modeling is sufficient for most purposes, it is not general enough \citep{Kneib, Nata}. Mass models motivated by numerical simulations, such as the NFW profile, invoke assumptions on the nature of the particles which are simulated. Together with the increasing complexity of models - considering different matter components and a variety of physical processes - uncertainties may pile up and introduce hard to quantify departures from real matter distributions \citep{DL}.

A way around this problem is to generate an ensemble of models, all models constrained to reproduce the observed image positions (and time delays if known) precisely. We use the GLASS code \citep{JC}, an algorithm sampling the 'model-space' with reasonable priors, with the lens model constructed as a superposition of mass pixels. Specifically, in this work we require the projected density to (i) be non-negative, (ii) be centrally concentrated, with the local density gradient pointing at most 50\degr  away from the center, and (iii) have no pixel more than twice the sum of its neighbors, the central pixel excepted. The explicit equations are given in early papers \citep{SW, Ab} for weak as well as strong lensing. The GLASS algorithm uniformly samples the model-space that satisfies all the equations and inequalities, resulting in a model-ensemble from which estimates and uncertainties can be derived.

\subsection{Disentangling matter}

As the total mass can be accessed by the GLASS program, the stellar part can be deduced using population synthesis. The stellar mass estimates are based on a comparison of surface brightness profiles with stellar mass-to-light ratios ($\Upsilon$) determined by population synthesis models for each pixel in the photometry \citep{IF,IF2}. The code used for this procedure was written by Ignacio Ferreras and relies on synthesis models and stellar spectral libraries from \citep{Bru}.

Figure \ref{f1} shows the end-product of the stellar population synthesis pipeline, a stellar surface mass map ($\Sigma _{M_s}$) in a logarithmic scale. The contours enclose pixels with stellar masses equal to or greater than the value stated in the contour labels \citep{DL}.

\begin{figure}
\begin{center}
\hspace{-7mm}\includegraphics[height=0.29\textwidth]{f1.eps}
\caption{Projected stellar surface mass map for the lens B2045 from \citet{DL}. Note that the contours enclose pixels of same or higher stellar mass. They do not refer to the total stellar mass enclosed. The box size is 31$\times$31 pixels.}
\label{f1}
\end{center}
\end{figure}

\section{Result of dark matter mass reconstruction}\label{mass}

The difference between the reconstructed total mass and the stellar mass derived above is not necessarily made up of $100\%$ dark matter. Baryons which did not form stars might be stored in large more or less clumpy dust and gas reservoirs in the galaxies \citep[e.g.][]{van}. However, in our work, the dust and gas contribution to the total mass is assumed to be negligible since our sample contains only one galaxies with observable dust lanes(1608) and one late-type galaxy(2237).

A sample of 18 lensing galaxies from the CfA-Arizona Space Telescope LEns Survey (CASTLES) and cluster ACO 2667 is used for this analysis. Fig. \ref{f2} shows the mass reconstruction result from GLASS for the lens HE2149-275 as an example. 
\begin{figure*}
\begin{center}
\hspace{-7mm}\includegraphics[height=0.27\textwidth]{f2.eps}
\caption{An ensemble of 1000 models is sampled by GLASS. Reconstructed dark matter mass map for HE2149-275 is shown in the last panel in terms of the critical mass. The first panel is the reconstructed arrival time surface, the projected density profile obtained by circularly averaging the projected-mass map is shown in the second panel (blue for total mass, black for dark matter mass and yellow for stellar mass), the enclosed projected mass is shown in the third panel.}
\label{f2}
\end{center}
\end{figure*}

\section{Dark matter density profiles} \label{profile}

Starting with the model ensemble, we circularly average each projected-mass map to obtain a $\Sigma(R)$ as shown in the second panel of Fig. \ref{f2}. We then use the ensemble of $\Sigma(R)$ to fit for the parameters in the projected generalized NFW profile parametrized with the inner logarithmic slope $\alpha$, scale length $a$ and total mass $M$
using a MCMC program. Appendix...

$M_{200}$. define $\beta$. Fig. \ref{range}. The dark matter central logarithmic density slopes from the MCMC program are shown in Fig. \ref{alpha} as a function of $M_{200}$.

\begin{figure*}
\begin{center}
\hspace{-7mm}\includegraphics[height=0.44\textwidth]{range.eps}
\caption{The solid lines show the regions between the innermost image and outermost image of the lensing systems, the half light radii are marked by the red diamonds.}
\label{range}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\hspace{-0mm}\includegraphics[height=0.30\textwidth]{Figures/alpha04.eps}
\hspace{-0mm}\includegraphics[height=0.30\textwidth]{Figures/r04.eps}\\
\hspace{-0mm}\includegraphics[height=0.30\textwidth]{Figures/alpha01.eps}
\hspace{-0mm}\includegraphics[height=0.30\textwidth]{Figures/r01.eps}\\
\hspace{-0mm}\includegraphics[height=0.30\textwidth]{Figures/alpha004.eps}
\hspace{-0mm}\includegraphics[height=0.30\textwidth]{Figures/r004.eps}\\
\caption{.}
%The dark matter central logarithmic density slope as a function of enclosed projected mass. 1-$\sigma$ errors are marked. A galaxy cluster is included in the right panel. The prediction \citep{DM} from dark matter only structure formation simulations (assuming non-relativistic cold dark matter) is marked by the horizontal red line; the dotted lines show the 1-$\sigma$ errors.
\label{alpha}
\end{center}
\end{figure*}

\section{Conclusions}\label{sec:conclusions}
Conclusions.

\section{Acknowledgements}
JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.

\bibliographystyle{mn2e}
\bibliography{../../BibTeX/refs}

\end{document}

### 2013-07-27 limits/ms.tex
pop synth

@@
 \citep{2010Sci...329..924J,2013arXiv1306.4732S} starting from a prior
-based on the values and uncertainties from the CMB, but tests using
-simulated lenses are desirable.
+based on the values and uncertainties from the CMB; tests of this
+technique simulated lenses are still awaited, in order to see how far
+the results depend on the model assumptions.
 
@@
 these mock data.
-
-\cite{2007ApJ...667..645R} were the first to test the recovery of
-strong lensing surface density profiles using mock data generated from
-N-body models {\bf JR. Is this true?}. They found that when including
-time delays, circularly averaged surface density distributions can
-sufficiently well-recovered to make interesting comparisons with
-theoretical models Cosmological parameters, however, are more
-sensitive. Since then, several groups have used N-body mock data to
-explore the fidelity of strong lensing reconstructions
-\citep{2007MNRAS.380.1729L}. We expand on these earlier works
-by considering not only the recovery of the circularly averaged
-surface density profile of a lens, but also its shape, higher order
-measures of the mass recovery (a pixel-by-pixel comparison), and the
-utility of wrapping in constraints from stellar mass estimates and/or
-stellar kinematics.
 
@@
 
-\subsection{Stellar population synthesis modelling}
-
-For many galaxy lenses, the central potential is dominated by the visible matter.
-In this situation, constraints on the stellar mass distribution are invaluable.
-\citep{2008MNRAS.383..857F} demonstrate that with just photometric data in XXX bands, and an assumed initial mass function for the stars, they are able to reliably constrain the stellar mass to XXX\% accuracy.
-This gives a constraint on the full lensing mass map:
-
-\begin{equation} 
-M(\vec\theta) > M_*(\vec\theta)
-\end{equation} 
-where $M_*$ is the stellar mass (see also similar work by ZZZZZ).
-Given the above work, we assume from here on that the stellar mass for our mock N-body data can be reliably determined and used as a lower-bound constraint on our lens models.
-
-{\bf JR. Prasenjit: you know more than me about this. Can you fill in the XXX's? We should probably also say a bit more about Ignacio's methodology and why the errors are so good etc etc.}
+\subsection{Stellar populations}
+
+For many galaxy lenses, the gravitational potential in the inner
+region is dominated by the stellar mass.  Steller mass can be
+estimated by combining photometry and colours with models of the
+stellar populations.  Such estimates are reasonably robust, even if
+the star-formation history is very uncertain: given a
+stellar-population model \citep[such as][]{2003MNRAS.344.1000B} and an
+initial mass function (IMF), the stellar mass can be inferred to 0.1
+to 0.2 dex using just two photometric bands \citep[see e.g., Figure~1
+  in][]{2008MNRAS.383..857F}.  By comparing the lensing-mass and
+stellar-mass profiles in elliptical galaxies, it is possible to
+extract the radial dependence of the baryonic vs dark-matter fraction
+\citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
+
+The major uncertainty at present in the stellar mass is probably the
+IMF.  In the lensing galaxy of the Einstein Cross, the IMF cannot be
+much more bottom-heavy than \cite{2003PASP..115..763C}, because
+otherwise the stellar mass would exceed the lensing mass
+\cite{2010MNRAS.409L..30F}.  More massive galaxies, however, do appear
+to have more of their stellar mass in low-mass stars.  This is
+indicated by molecular spectral features characteristic of low mass
+stars
+\citep{2004ApJ...614L.101C,2012ApJ...747...69C,2013MNRAS.429L..15F}.
+The \cite{2003PASP..115..763C} would, however, still provide a robust
+lower limit on the stellar mass.  Hence, also a limit on the total
+mass.  Accordingly, \Glass\ allows a constraint of the form
+\begin{equation} 
+M(\vec\theta) \geq M_{\rm stel}(\vec\theta)
+\end{equation} 
+on the total mass.
 
@@
 
-\item More references to be added to the introduction.
-Lots of work remains to be cited.
-Were we really the first to test lensing on N-body mocks?
-Perhaps for strong lensing, but certainly not for weak.
-
 \item Understand ``Schneider's degeneracy". Add reference/commentary accordingly.
-
-\item Prasenjit to write/finish section on stellar population synthesis modelling.
 
@@
 \end{document}
+
+\cite{2007ApJ...667..645R} were the first to test the recovery of
+strong lensing surface density profiles using mock data generated from
+N-body models {\bf JR. Is this true?}. They found that when including
+time delays, circularly averaged surface density distributions can
+sufficiently well-recovered to make interesting comparisons with
+theoretical models Cosmological parameters, however, are more
+sensitive. Since then, several groups have used N-body mock data to
+explore the fidelity of strong lensing reconstructions
+\citep{2007MNRAS.380.1729L}. We expand on these earlier works
+by considering not only the recovery of the circularly averaged
+surface density profile of a lens, but also its shape, higher order
+measures of the mass recovery (a pixel-by-pixel comparison), and the
+utility of wrapping in constraints from stellar mass estimates and/or
+stellar kinematics.

### 2013-07-29 limits/ms.tex
editing lensing-theory part

@@
   extra images are produced.  Free-form are more commonly used with
-  cluster lenses\citep{2009ApJ...690..154S,2013arXiv1304.2393S}, but
+  cluster lenses \citep{2009ApJ...690..154S,2013arXiv1304.2393S}, but
   can be used with galaxy lenses as well, where their less restrictive
@@
 
-\section{Theoretical Background}\label{sec:theory} %-----------------------------------------------------
-
-\subsection{Lensing basics}\label{sec:lensing_basic} %-----------------------------------------------------
-
-The lens equation:
-%
-\begin{equation}
-\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
+\section{Formulation}\label{sec:theory}
+
+\subsection{Lensing essentials}\label{sec:lensing_basic}
+
+We follow \cite{1986ApJ...310..568B} with minor differences in notation
+notation.
+
+The lens equation
+\begin{equation}
+\begin{aligned}
+\vec\beta &= \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta) \\
+\vec\alpha(\vec\theta) &= \frac{4G}{c^2D_L} \int \Sigma(\vec\theta')
+                          \frac{(\vec\theta - \vec\theta')}
+                          {\ |\vec\theta - \vec\theta'|^2} \, d^2\vec\theta'
+\end{aligned}
 \label{eqn:lens_equation}
 \end{equation}
-%
-maps an observed image position $\vec\theta$ to a source position $\vec\beta$
-via the correction factor \citep[e.g.][]{1992grle.book.....S}:
-%
-\begin{equation}
-\vec\alpha(\vec\theta) = \frac{4GD_L}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
-\end{equation}
-%
+maps an observed image position $\vec\theta$ to a source position $\vec\beta$.
+The $D$ factors are angular diameter distances, as in the previous section.
+The lens can then be thought of as a projected surface density
+$\Sigma$ which diverts the path of a photon instantaneously through
+the bending angle $\vec\alpha$.
+
 which accounts for the gravitational lensing effect of an intervening mass
@@
 angular diameter distances where $D_* = (c/H_0)d_*$, $H_0$ is the Hubble constant, and $d_*$ is a
-dimensionless number that depends on cosmology.  The lens can then be thought
-of as a projected surface density $\Sigma$ which diverts the path of a photon
-instantaneously through the bending angle $\vec\alpha$.
-
-Since we will later want to model the density distribution with a computer it
-will be convenient to choose units that make the relevant quantities of order
-unity.  We therefore measure lengths in light years, time in years, positions
-in arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
-arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to
-define a proxy to the Hubble constant $\zeta \equiv N^2 H_0$.
-
-One way to understand the lens equation is via Fermat's principle. We can think of light as travelling only 
-along extremum paths where lensed images occur \citep{1986ApJ...310..568B}.
-Such paths occur at the extrema of the photon {\it arrival time surface} $t(\vec\theta)$ that depends on the geometric path the photon takes and the general relativistic gravitational time dilation
-due to a thin lens at redshift $z_L$. In its complete form, with all units
-and cosmology included, we have \citep{1986ApJ...310..568B}:
+dimensionless number that depends on cosmology.
+
+\begin{equation}
+D_{LS} = \frac c{H_0} \frac{1+z_S}{1+z_L} \int_{z_L}^{z_S}
+                      \frac{dz}{\sqrt{\Omega_m(1+z)^3 + \Omega_\Lambda}}
+\end{equation}
+
+One way to understand the lens equation is via Fermat's principle. We
+can think of light as travelling only along extremum paths where
+lensed images occur. Such paths occur at
+the extrema of the photon {\it arrival time\/} $t(\vec\theta)$
+that depends on the geometric path the photon takes and the general
+relativistic gravitational time dilation due to a thin lens at
+redshift $z_L$.
+\begin{equation}
+\begin{aligned}
+\frac{ct(\vec\theta)}{(1+z_L)D_{L}}
+&= {\textstyle\frac12} |\vec\theta - \vec\beta|^2
+   \times \frac{D_{S}}{D_{LS}} \\
+&- \frac{4GD_L}{c^2}
+   \int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| \, d^2\vec\theta'
+\label{full arrival time}
+\end{aligned}
+\end{equation}
+
+\begin{equation}
+\kappa(\vec\theta) \equiv \frac{4\pi GD_L}{c^2} \Sigma (\vec\theta)
+\end{equation}
+
+\begin{equation}
+\kappa \sim \frac{z_L\,\Sigma}{10\rm\,kg\,m^{-2}}
+\end{equation}
+
+\begin{equation}
+\tau(\vec\theta) = {\textstyle\frac12} |\vec\theta - \vec\beta|^2
+                   \times \frac{D_{S}}{D_{LS}}
+                 - \frac1\pi \int \kappa (\vec\theta')
+                   \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
+\label{arrival time}
+\end{equation}
+The scaled arrival time $\tau$ is like a solid angle.  It is of order
+the area (in steradians) of the full lensing system --- the expression
+$\sim|\vec\theta - \vec\beta|^2$ is of order the image-separation
+squared, and the other terms are of similar size.  For this reason, is
+convenient to measure $\tau$ in arcsec$^{2}$.
+
+, with all units
+and cosmology included, we have 
 %
@@
 \begin{equation}
-\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
+\psi(\vec\theta) = 
 \label{lensing potential}
@@
 %
-\begin{equation}
-\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
-\label{arrival time}
-\end{equation}
+
 %
@@
 observable and the density distribution is highly degenerate.
+
+Degeneracy first formally noted by \cite{1985ApJ...289L...1F}.  Most
+important is mass sheet.  But in fact, there are infinitely many
+\citep{2000AJ....120.1654S}.
+Also shape degeneracies \citep{2006ApJ...653..936S,2013arXiv1306.4675S}
+Suppressed by redshift contrast
+\citep{1998AJ....116.1541A,2009ApJ...690..154S}
+but not completely \citep{2008MNRAS.386..307L}.
 

### 2013-08-02 limits/ms.tex
further edits

@@
 \renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}}
-
-\def\Sigmacrit{\Sigma_{\rm crit}}
 
@@
 \end{equation}
-The critical density for multiple images is
-\begin{equation}
-\Sigmacrit = \frac{c^2 D_L}{4\pi G} \frac{D_S}{D_{LS}}
-\end{equation}
-in mass per steradian.  The separation between the lensed images is of
-order the Einstein radius $\theta_E$.  The image separation is related
-to the mass by
+For multiple images the sky-projected density must exceed the critical
+density of $D_S/D_{LS}$ times
+\begin{equation}
+\Sigma_L = \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
+\end{equation}
+in some region.  The separation between the lensed images is of order
+the Einstein radius $\theta_E$.  The image separation is related to
+the mass by
 \begin{equation}
@@
 \end{equation}
-maps an observed image position $\vec\theta$ to a source position $\vec\beta$.
-The $D$ factors are angular diameter distances, as in the previous section.
-The lens can then be thought of as a projected surface density
-$\Sigma$ which diverts the path of a photon instantaneously through
-the bending angle $\vec\alpha$.
-
-which accounts for the gravitational lensing effect of an intervening mass
-(where $G$ is Newton's gravitational constant, and $c$ is the speed of light).
-For our purposes we make use of the thin mass sheet approximation and assume
-that the lensing mass is infinitely thin compared with the distance between the
-source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are
-angular diameter distances where $D_* = (c/H_0)d_*$, $H_0$ is the Hubble constant, and $d_*$ is a
-dimensionless number that depends on cosmology.
-
+maps an observed image position $\vec\theta$ to a source position
+$\vec\beta$.  The lens can then be thought of as a projected surface
+density $\Sigma$ which diverts the path of a photon instantaneously
+through the bending angle $\vec\alpha$.  The $D$ factors are angular
+diameter distances, as in the previous section.
 \begin{equation}
@@
 \end{equation}
-
 One way to understand the lens equation is via Fermat's principle. We
@@
 \end{equation}
-
-\begin{equation}
-\kappa(\vec\theta) \equiv \frac{4\pi GD_L}{c^2} \Sigma (\vec\theta)
-\end{equation}
-
-\begin{equation}
-\kappa \sim \frac{z_L\,\Sigma}{10\rm\,kg\,m^{-2}}
-\end{equation}
-
+The time here has been scaled to make it dimensionless.  We can make
+the density dimensionless as well, by introducing
+\begin{equation}
+\kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
+\end{equation}
+and hence rewrite \eqnref{full arrival time} as
 \begin{equation}
@@
                  - \frac1\pi \int \kappa (\vec\theta')
-                   \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
+                   \ln|\vec\theta - \vec\theta'| d^2\vec\theta'
 \label{arrival time}
@@
 
-, with all units
-and cosmology included, we have 
-%
-\begin{eqnarray}
-N^2ct(\vec\theta) & = & (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 \nonumber \\
-& & - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
-\label{eqn:full_arrival_time}
-\end{eqnarray}
-%
-where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
-has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
-delay:
-%
-\begin{equation}
-\tau = \left[ (1+z_L) d_L\right]^{-1}\zeta t
-\label{tau}
-\end{equation}
-%
-in terms of our previous definitions. If we
-further define a dimensionless density:
-%
-\begin{equation}
-\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
-              = \frac{d_L}{\zeta}\Sigma
-\end{equation}
-%
-and a lensing potential:
-%
-\begin{equation}
-\psi(\vec\theta) = 
-\label{lensing potential}
-\end{equation}
-%
-we can express \eqnref{eqn:full_arrival_time} very compactly as:
-%
-
-%
-where $\xi \equiv D_{S}/D_{LS}$. We explicitly write $\kappa_\infty$ to remind ourselves
-that there is no source distance factor involved. This will be useful later when we consider
-multiple sources. Notice that the constraint $\nabla \tau = 0$ -- i.e. extrema in the arrival time surface -- recovers the lens equation (\eqnref{eqn:lens_equation}).
-
-The only lensing observables from \eqnref{arrival time} are the image positions. However,  if the source object is
-variable then the observed light curves of each image will be
-identical but shifted in time due to the different photon path lengths.
-The time difference between identical portions of the light curves is called
-the time delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
-$\Delta t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where $\vec\theta_2$
-arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
-\zeta$. If $\beta$ and $\kappa_\infty$ could be known exactly this would allow one
-to precisely infer the angular diameter distance to the lens and thus -- via a cosmological model -- the Hubble constant. However, the source position is not
+The arrival-time surface $\tau(\theta)$ is a theoretical construct for
+understanding lensing observables, and not an observable in its own
+right.
+
+The only lensing observables from \eqnref{arrival time} are the image
+positions. However, if the source object is variable then the observed
+light curves of each image will be identical but shifted in time due
+to the different photon path lengths.  The time difference between
+identical portions of the light curves is called the time delay
+$\Delta t$ between images.  Using \eqnref{tau} the time delay $\Delta
+t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where
+$\vec\theta_2$ arrives after $\vec\theta_1$, is $\Delta t_{21} =
+\Delta \tau_{21}(1+z_L)d_L / \zeta$. If $\beta$ and $\kappa_\infty$
+could be known exactly this would allow one to precisely infer the
+angular diameter distance to the lens and thus -- via a cosmological
+model -- the Hubble constant. However, the source position is not
 observable and the density distribution is highly degenerate.
@@
 the vertical axis shows the range of `quality' of recovery, defined as: 
-%
-\begin{equation}
-  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
+\begin{equation}
+\chi^2 = \frac
+       {\Big\langle \int \left|\Delta\Sigma(\vec{\theta})\right|^2 \,
+        d^2 \vec{\theta} \Big\rangle}
+       {\int \Sigma^2(\vec{\theta}) \; d^2 \vec{\theta}}
+\end{equation}
+where the angle brackets denote averages over the model ensemble.
+%\begin{equation}
+%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
 %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
-\end{equation}
-where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.
+%\end{equation}
+%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.
 

### 2013-08-02 limits/ms.tex
more edits

@@
 
-The arrival-time surface $\tau(\theta)$ is a theoretical construct for
-understanding lensing observables, and not an observable in its own
-right.
-
-The only lensing observables from \eqnref{arrival time} are the image
-positions. However, if the source object is variable then the observed
-light curves of each image will be identical but shifted in time due
-to the different photon path lengths.  The time difference between
-identical portions of the light curves is called the time delay
-$\Delta t$ between images.  Using \eqnref{tau} the time delay $\Delta
-t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where
-$\vec\theta_2$ arrives after $\vec\theta_1$, is $\Delta t_{21} =
-\Delta \tau_{21}(1+z_L)d_L / \zeta$. If $\beta$ and $\kappa_\infty$
-could be known exactly this would allow one to precisely infer the
-angular diameter distance to the lens and thus -- via a cosmological
-model -- the Hubble constant. However, the source position is not
-observable and the density distribution is highly degenerate.
-
-Degeneracy first formally noted by \cite{1985ApJ...289L...1F}.  Most
-important is mass sheet.  But in fact, there are infinitely many
-\citep{2000AJ....120.1654S}.
-Also shape degeneracies \citep{2006ApJ...653..936S,2013arXiv1306.4675S}
-Suppressed by redshift contrast
-\citep{1998AJ....116.1541A,2009ApJ...690..154S}
-but not completely \citep{2008MNRAS.386..307L}.
-
-\subsection{Degeneracies}\label{sec:degen} %-----------------------------------------------------
-
-The trouble with solving the lens equation for the mass distribution is that the solutions are not unique.
+Lensing observations provide information only at $\vec\theta$ where
+there are images.  Hence, the arrival-time surface $\tau(\vec\theta)$
+is not itself observable.  Its usefulness lies in that observables can
+be derived from it.  Thus an image observed at $\vec\theta_1$ implies
+that $\nabla\tau(\vec\theta_1)=0$.  A measurement of time delays
+between images at $\theta_1$ and $\theta_1$ implies that
+$t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both these
+types of observations give contraints that are linear in $\kappa$ and
+$\vec\beta$.
+
+The rather complicated dependence of lensing observables on the mass
+distribution $\kappa(\vec\theta)$ has an important consequence: very
+different mass distributions can result in similar observables.  This
+is the phenomenon of lensing degeneracies.  While the non-uniqueness
+of lens models noted by \cite{1981ApJ...244..736Y} already hinted at
+degeneracies, their existence was first derived by
+\cite{1985ApJ...289L...1F}.  The most important is the so-called
+mass-sheet degeneracy, which is that image positions remain invariant
+if the $D_S/D_{LS} - \kappa(\vec\theta)$ are each multiplied by an
+arbitrary constant.  This amounts to multiplying the arrival-time
+surface by a constant factor.  In fact there are infinitely many
+degeneracies \citep{2000AJ....120.1654S} because any transformation of
+the arrival-time surface away from the images has no effect on the
+lensing observables.  In particular, there are degeneracies that
+involve the shape of the mass distribution
+\citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies tend to
+be suppressed if there are sources at very different redshifts or
+`redshift contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S},
+because the presence of different factors of $D_S/D_{LS}$ in the image
+plane makes it more difficult to change the mass distribution and the
+arrival-time surface without affecting the lensing observables.  But
+degeneracies are still present with multiple source redshifts.
+\citep{2008MNRAS.386..307L}.
+
+% The only lensing observables from \eqnref{arrival time} are the
+% image positions. However, if the source object is variable then the
+% observed light curves of each image will be identical but shifted in
+% time due to the different photon path lengths.  The time difference
+% between identical portions of the light curves is called the time
+% delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
+% $\Delta t_{21}$ between two images $\vec\theta_1$ and
+% $\vec\theta_2$, where $\vec\theta_2$ arrives after $\vec\theta_1$,
+% is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L / \zeta$. If $\beta$
+% and $\kappa_\infty$ could be known exactly this would allow one to
+% precisely infer the angular diameter distance to the lens and thus
+% -- via a cosmological model -- the Hubble constant. However, the
+% source position is not observable and the density distribution is
+% highly degenerate.
+
+% \subsection{Degeneracies}\label{sec:degen}
+%
+% The trouble with solving the lens equation for the mass distribution is that the solutions are not unique.
 To see why, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens:
 %
-\begin{equation}
-\vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
-\label{eqn:lens_equation_circ}
-\end{equation}
-%
-where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.
-
-For on-axis sources (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$.
+% \begin{equation}
+% \vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
+% \label{eqn:lens_equation_circ}
+% \end{equation}
+%
+% where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.
+
+% For on-axis sources (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$.
 Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distance.
@@
 
-{\bf Is ``Schneider's degeneracy" something new? Should we cite it here? -- {\tt http://adsabs.harvard.edu/abs/2013arXiv1306.4675S}}
+% {\bf Is ``Schneider's degeneracy" something new? Should we cite it here? -- {\tt http://adsabs.harvard.edu/abs/2013arXiv1306.4675S}}
 
@@
 
-\item Understand ``Schneider's degeneracy". Add reference/commentary accordingly.
-
 \item Jonathan to complete \S\ref{sec:glass}. Emphasise need for central adaptive grid. Add appendix showing convergence as Pixrad is increased.

### 2013-09-06 limits/ms.tex
more action items

@@
 
+\item Change variable chi to something else ($f$?) to avoid confusion
+  with $\chi^2$.
+
+\item Replace equation 20 with what you are actually doing when
+  calculating $chi$ (now $f$).
+
+\item Add plot of $chi$ ($f$) for $lambda_1/lambda_2$ and theta shape
+  parameters (c.f. what Claudio is doing).
+
+\item Check that you and Claudio average to the same projected radius
+  (one pixel past outermost image) when calculating
+  $lambda_1/lambda_2$ and $\theta$.
+
+\item Calculate aperture averaged $\sigma$ to 2 (or 3 you decide) half
+  light radii assuming $beta = 0$ for a model (double) where the mass
+  is poorly constrained by strong lensing. Accept/reject models from
+  the ensemble $\Longrightarrow$ what we learn from combined lensing
+  kinematics.
+
+\item Take a model that is well constrained by strong lensing
+  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
+  in the ensemble using the kinematics module. Compare this with the
+  true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
+  a $\chi^2$ this time!).  Show the true $\sigma_p(R)$ and overlay
+  coloured bands from the lensing model ensemble assuming $\beta = 0$
+  or $\beta = 1$.
+
 \end{enumerate} 

### 2013-09-08 limits/ms.tex
rearranged action items

@@
 the vertical axis shows the range of `quality' of recovery, defined as: 
-\begin{equation}
+\begin{equation} \label{badness}
 \chi^2 = \frac
@@
 
-{\bf JR. ACTION ITEMS.
-
-\begin{enumerate}
-
-\item Jonathan to complete \S\ref{sec:glass}. Emphasise need for central adaptive grid. Add appendix showing convergence as Pixrad is increased.
-
-\item Jonathan to write section \S\ref{sec:glassextraimages} on removing models with extra images.
-
-\item Clarify amount of triaxiality (and the analytic density profile) in \S\ref{sec:mockdata}.
-
-\item Clarify number of lens configurations in \S\ref{sec:lensconfig}.
-
-\item Add appendix showing how ``radial symmetry" prior affects results. Clarify meaning of this prior with a nice figure showing the symmetry.
-
-\item Show results for $1\sigma$ and $2\sigma$ rather than full \Glass\ ensemble.
-Add results for Claudio's shape measure.
-Discuss shape throughout results section and mention more explicitly in abstract and conclusions -- what quality of data do we need to robustly constrain the shape?
-
-\item Add example plot of the projected density and recovered projected density (c.f. plots Jonathan made for my ERC proposal).
-
-\item Tidy up figures and other small items as detailed throughout -- see {\tt {\bf JR ... }}.
-
-\item Add accept/reject results for stellar kinematics (two figures) as detailed in \S\ref{sec:results_stellar_kinematics}.
-
-\item Change variable chi to something else ($f$?) to avoid confusion
-  with $\chi^2$.
-
-\item Replace equation 20 with what you are actually doing when
-  calculating $chi$ (now $f$).
-
-\item Add plot of $chi$ ($f$) for $lambda_1/lambda_2$ and theta shape
-  parameters (c.f. what Claudio is doing).
+Various action items.
+
+\subsection{Goodness of recovery}
+
+\begin{enumerate}
+
+\item Change variable $\chi$ to something else ($f$?) to avoid
+  confusion with $\chi^2$.
+
+\item Correct equation \eqref{badness} to describe what is actually
+  calculated.
+
+\item Show results for $1\sigma$ and $2\sigma$ rather than full
+  \Glass\ ensemble.
+
+\item Add results for Claudio's shape measure. Discuss shape
+  throughout results section and mention more explicitly in abstract
+  and conclusions -- what quality of data do we need to robustly
+  constrain the shape?
+
+\item Add plot of $\chi$ ($f$) for $lambda_1/lambda_2$ and shape
+  parameters (cf. what Claudio is doing).
 
@@
 
+\end{enumerate}
+
+\subsection{Kinematics}
+
+\begin{enumerate}
+
+\item Add example plot of the projected density and recovered
+  projected density (cf. plots Jonathan made for Justin's ERC
+  proposal).
+
 \item Calculate aperture averaged $\sigma$ to 2 (or 3 you decide) half
-  light radii assuming $beta = 0$ for a model (double) where the mass
+  light radii assuming $\beta = 0$ for a model (double) where the mass
   is poorly constrained by strong lensing. Accept/reject models from
@@
 
-\end{enumerate} 
-}
+\item Add accept/reject results for stellar kinematics (two figures)
+  as detailed in \S\ref{sec:results_stellar_kinematics}.
+
+\end{enumerate}
+
+\subsection{Other}
+
+\begin{enumerate}
+
+\item Tidy up figures and other small items as detailed throughout --
+  see {\bf JR ... }
+
+\item Add appendix showing how inversion symmetry in the prior affects
+  results. Clarify meaning of this prior with a nice figure showing
+  the symmetry.
+
+\item Complete \S\ref{sec:glass}. Emphasise need for central adaptive
+  grid. Add appendix showing convergence as Pixrad is increased.
+
+\end{enumerate}
+
+\subsection{Clarifications in text}
+
+\begin{enumerate}
+
+\item Write section \S\ref{sec:glassextraimages} on removing models
+  with extra images.
+
+\item Clarify amount of triaxiality (and the analytic density profile)
+  in \S\ref{sec:mockdata}.
+
+\item Clarify number of lens configurations in \S\ref{sec:lensconfig}.
+
+\end{enumerate}
 

### 2013-09-27 limits/ms.tex
New plots and updated text.

@@
 \usepackage{graphicx}
+\usepackage{ulem} % Only necessary for striking out TODO items see \sout
 
@@
 \Glass\ is an evolution of the concepts employed by the free form modelling tool
-\PixeLens\ but completely rewritten in Python and C. The key improvements are:
+\PixeLens\ but completely rewritten in Python and C. 
+The most compute intensive
+portion was written in C but Python was chosen because of its flexibility as a 
+language and for its large scientific library support. The flexibility allows 
+\Glass\ to have quite sophisticated behavior while at the same time simplfying the 
+user experience and reducing the overall development time. One of the striking
+features is that the input file to \Glass\ is itself a Python program.
+Understanding Python is not necessary, however, to use \Glass\ but this allows
+a user to build the analysis of a model directly into the input file. \Glass\
+may also be used as an external library to other Python programs.  The software
+is freely available for download or from the author.
+
+The key scientific and technical improvements are:
 %
@@
   \setcounter{enumi}{0}
-  \item A modular framework allows new priors to be added and modified easily.
+  \item A modular framework that allows new priors to be added and modified easily.
 \end{enumerate}
@@
 a single lens object or the entire ensemble of objects. \Glass\ comes with a number
-of useful priors, but a user can write their own in the input file.
+of useful priors, the default ones will be described later, but a user can
+write their own directly in the input file, or by modifying the source code.
 %
@@
 \Glass\ currently describes the lens mass as a collection of pixels, but the code
-has been designed to support alternative methods. In particular, it is planned
-to develop a module using Bessel functions. This will require a new set of 
+has been designed to support alternative methods. In particular, there are future
+plans to develop a module using Bessel functions. This will require a new set of 
 priors that operate on these functions.
@@
 %
-By default, the mass distribution of the lens is described by uniform grid. However,
-in the central region of a lensing galaxy where the mass profile may rise steeply,
-a higher resolution can be specified that only applies to the inner pixels. These
-pixels are subdivided into a smaller grid. {\bf JR. I think Jonathan is now applying this by default. Is that right Jonathan?} 
+With the default basis set of pixels, the mass distribution of the lens is
+described by uniform grid. However, in the central region of a lensing galaxy
+where the mass profile may rise steeply, the center pixel uses a higher
+resolution. This allows the density to increase smoothly but still allow for
+a large degree of freedom within the inner region without allowing the density
+to be arbitrarily high. 
 %
@@
 is useful to capture the gross effects of a distant neighbour. \Glass\ also
-has a shear term but additional allows for additional analytic potentials to
+has a shear term but in addition allows for analytic potentials to
 be included. This can be used to model substructure or multiple neighbors close
 to the main lens. The substructure may have only a small effect if the lens is
-a single galaxy, but if the lens is group then a potential can be added for
-each of the galaxies.
+a single galaxy, but if the lens is a group then a potential can be added for
+each of the galaxies. A few standard functions are already included in \Glass\
+including those for a point mass, a power law distribution, or an isothermal (a
+particular case of the power law).
 %
@@
 linear space that represents the modelling solution space. This algorithm was
-described and tested in \cite{2012MNRAS.425.3077L}. \Glass\ is also multi-threaded allowing it to
-run efficiently on many-cored machines.  The software is freely available for
-download. One interesting aspect is that the input files are themselves Python
-programs. This allows a large amount of sophistication in setting up a lens at
-runtime and also allows \Glass\ to be used as an external library from another
-user written program.
+described and tested in \cite{2012MNRAS.425.3077L}. This algorithm is 
+multi-threaded allowing it to run efficiently on many-cored machines.
 
@@
 
+\subsection{Analysis Tools}\label{sec:tools}
+\Glass\ is not only a modeling tool but also an analysis engine. \Glass\
+provides many functions for viewing and manipulating the computed models.
+These functions can either be called from a program written by the user or 
+by using the program \textsc{viewstate.py} included with \Glass. There is
+also a tools, \textsc{lenspick.py} for creating a lens, either from an $N$-body
+simulation file, or from an analytic form. To load the simluation data, \Glass\
+uses \textsc{PynBody} and can thus load any file supported by that tool.
+
 \subsection{Discrete models}\label{sec:discrete}
@@
 \item The density must be non-negative everywhere.
-\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
+\item The density profile must have a slope everywhere $\le 0$.
 \item The local gradient everywhere must point within $45^{\circ}$ of the center.
@@
 \end{enumerate}
+
+Prior (ii) is necessary to prevent rings from forming where the inner region is
+less dense. This would be unusual for a galaxy or a cluster. Prior (vi)
+enforces a radial symmetry that requires radially opposed pixels (i.e., on
+opposite sides of the center) to be equal. This prior is particularly important
+for modelling doubles which must be symmetric. If a lens is suspected to be
+symmetric this can also significantly improve the modelling time for quads.
 
@@
 \subsection{Removing models with extra images}\label{sec:glassextraimages} 
-While linear constraints can be applied on-the-fly in \Glass, non-linear constraints must be applied in post-processing.
-Models that are inconsistent with such constraints must then be statistically discarded via a likelihood analysis.
-An example of such a non-linear constraint is the spurious presence of unobserved images.
-This `null-space' prior was first proposed and explored by \citet{2006MNRAS.367.1209L} and found to be extremely powerful.
-We find that our gradient prior in \Glass\ (see \S\ref{sec:discrete}), performs much of the same function as \citeauthor{2006MNRAS.367.1209L}'s null-space prior, but some models can still rarely turn up spurious images.
-We reject these in a post-processing step, where we sweep through the model ensemble applying the ray tracing algorithm described in \ref{Raytracing}.
-Models are accepted or rejected according to the criteria:
+While linear constraints are applied in \Glass\ by the nature of the sampling
+algorithm, non-linear constraints must be applied in post-processing. Models
+that are inconsistent with such constraints must then be statistically
+discarded via a likelihood analysis. An example of such a non-linear constraint
+is the spurious presence of unobserved images. This `null-space' prior was
+first proposed and explored by \citet{2006MNRAS.367.1209L} and found to be
+extremely powerful. We find that our gradient prior in \Glass\ (see
+\S\ref{sec:discrete}), performs much of the same function as
+\citeauthor{2006MNRAS.367.1209L}'s null-space prior, but some models can still
+rarely turn up spurious images. We reject these in a post-processing step,
+where we sweep through the model ensemble applying the ray tracing algorithm
+described in \ref{Raytracing}. Models are accepted or rejected according to the
+criteria:
 
@@
 \subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
-Similarly to the null-space constraint (\S\ref{sec:glassextraimages}), stellar kinematic constraints constitute a non-linear prior on the mass map and must be applied in post-processing.
-We sweep through the model ensemble performing an Abel deprojection to determine $M(r)$ from the projected surface density assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
+Similarly to the null-space constraint (\S\ref{sec:glassextraimages}), stellar
+kinematic constraints constitute a non-linear prior on the mass map and must be
+applied in post-processing. We sweep through the model ensemble performing an
+Abel deprojection to determine $M(r)$ from the projected surface density
+assuming spherical symmetry
+\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
 
@@
 \textbf{Left:} 
-Density averaged in spherical shells of the four galaxy mocks: AA, AC, BB and BC, showing the stellar (dotted), dark matter (dashed),
-and total (solid) densities, respectively. Notice that the stars in models BB and BC contribute significantly to the central potential. 
+Spherically averaged density profiles of the four mock galaxies showing the stellar (dotted), dark matter (dashed),
+and total (solid) densities. Notice that the stars in models Sdom/DMshallow and Sdom/DMcuspy contribute significantly to the central potential. 
 \textbf{Middle:} 
@@
 For each of the four galaxies, we used the raytracing feature of \Glass\
-described in \secref{Raytracing} to construct 12 lensing scenarios {\bf JR. We have 12 lensing scenarios, but only 6 panels in Figure 2. Is this number correct?}:
+described in \secref{Raytracing} to construct 6 basic lensing morphologies:
 
@@
 \end{enumerate}
-The `extended' configurations use multiple point sources at the same redshift to simulate an extended source (that will produce an arc-like image).
-\figref{arrival surfaces} shows the configuration for the extended quad, along with the other cases.
+The `extended' configurations use multiple point sources at the same redshift
+to simulate an extended source that will produces an arc-like image.
+\figref{arrival surfaces} shows the configuration for the extended quad, along
+with the other cases.
 
@@
 
-Each of these configurations were modelled with and without time delays and with
-and without a central image.
-(The central image is typically highly demagnified.
-For galaxy lenses it is very difficult to find since it lies along the sight line to the bright lensing galaxy; in clusters, however, such images have been seen (CITES)).
-We assumed for all our tests that the lensing mass
-was radially symmetric ({\bf JR. Need to better-define this symmetry here.}. For our mock data, this is known to be true; it is
-most often the case with real galaxies, unless there is an obvious observed
-asymmetry. The central pixel was refined into a further nine pixels to capture
-any steep rise in the profile. Two of the four mock galaxies have a steeply rising
-inner profile. {\bf JR. What happens if we don't assume this symmetry? We ought to add an appendix showing this for one example case.}
+Each of these configurations were modelled with and without time delays and
+with and without a central image, for a total of 24 test cases. (The central
+image is typically highly demagnified. For galaxy lenses it is very difficult
+to find since it lies along the sight line to the bright lensing galaxy; in
+clusters, however, such images have been seen (CITES)). We assumed for all our
+tests that the lensing mass was radially symmetric (Prior vi):
+For our mock data, this is known to be
+true; it is most often the case with real galaxies, unless there is an obvious
+observed asymmetry. The central pixel was refined into a further nine pixels to
+capture any steep rise in the profile.  Two of the four mock galaxies have a
+steeply rising inner profile. {\bf JR.  What happens if we don't assume this
+symmetry? We ought to add an appendix showing this for one example case.}
 
@@
 center plot shows the radial density profile. The error bars cover the full
-range of models generated by \Glass {\bf JR.
-Why do this?
-Surely 1 or 2 sigma errors make more sense?
-I've deleted the ``full ensemble" results and kept the $1\sigma$ ones instead.}.
-The true density profile from the mock
-data is also plotted for comparison. The vertical lines mark the radial
-position of the images. The final plot on the right is of the enclosed mass. As
-expected, the error bars are smallest in the region of the images where the most
-information about the lens is present. The dip in the profile at the end of the
-profile is due to the cut off in mass in the lensing map. This is of little
-importance, though, as there is no lensing information there.
+range of models generated by \Glass {\bf JR. Why do this? Surely 1 or 2 sigma
+errors make more sense? I've deleted the ``full ensemble'' results and kept the
+$1\sigma$ ones instead.}. The true density profile from the mock data is also
+plotted for comparison. The vertical lines mark the radial position of the
+images. The final plot on the right is of the enclosed mass. As expected, the
+error bars are smallest in the region of the images where the most information
+about the lens is present. The dip in the profile at the end of the profile is
+due to the cut off in mass in the lensing map. This is of little importance,
+though, as there is no lensing information there.
 
@@
 \caption{
-{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} 
-A typical reconstructed lens. Here we present results for a single quad image lensed by the BC mock galaxy.
+  \sout{{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} }
+A typical reconstructed lens. Here we present results for a single quad image lensed by the Sdom/DMcuspy mock galaxy.
 \textbf{Left:}
@@
 \textbf{Right:}
-The cumulative mass.}
+The cumulative mass. The error bars on both plots are $1\sigma$.}
 \label{reconstruction}
@@
 
-The main results from modelling these different configuration are shown in black in
-\figref{main results}. Each subplot corresponds to a different galaxy and
-the vertical axis shows the range of `quality' of recovery, defined as: 
+The main results from modelling these different configurations are shown in black in
+\figref{main results} and \figref{main results pixel-wise}. Each subplot corresponds to a different galaxy and
+the vertical axis shows the range of `quality' of recovery. In \figref{main results}, this quality is
+defined over radial bins of mass as
+%
 \begin{equation} \label{badness}
-\chi^2 = \frac
-       {\Big\langle \int \left|\Delta\Sigma(\vec{\theta})\right|^2 \,
-        d^2 \vec{\theta} \Big\rangle}
-       {\int \Sigma^2(\vec{\theta}) \; d^2 \vec{\theta}}
-\end{equation}
-where the angle brackets denote averages over the model ensemble.
+  f_r = \frac {\int \left|\Delta M(r)\right|\; dr } {\int M(r)\; dr}
+\end{equation}
+%
+while in \figref{main results pixel-wise} the quality is defined over all the pixels
+%
+\begin{equation} \label{badness}
+f_\theta = \frac
+       {\int \left|\Delta M(\vec\theta)\right| \; d \vec{\theta} }
+       {\int M(\vec\theta) \; d \vec\theta}
+\end{equation}
+In both cases, the delta difference is between a single recovered model and the known mock galaxy.
 %\begin{equation}
@@
 \begin{figure*}
-\includegraphics[width=0.49\textwidth]{AAchi2_profile.pdf}
-\includegraphics[width=0.49\textwidth]{BBchi2_profile.pdf}\\
-\includegraphics[width=0.49\textwidth]{ACchi2_profile.pdf}
-\includegraphics[width=0.49\textwidth]{BCchi2_profile.pdf}
+\includegraphics[width=0.49\textwidth]{AAferror_profile-1sig.pdf}
+\includegraphics[width=0.49\textwidth]{BBferror_profile-1sig.pdf}\\
+\includegraphics[width=0.49\textwidth]{ACferror_profile-1sig.pdf}
+\includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
 \caption{The main results showing the quality of model recovery. Each panel corresponds to 
@@
 each panel are six groups of results for each of six lens morphologies. Each morphology
-considered the presence of time delays and a central image. The black markers are for tests
+considered the presence of time delays (T/t) and a central image (M/m). The black markers are for tests
 that did not include the stellar mass as a lower bound constraint, while the red markers
@@
 \begin{figure*}
-\includegraphics[width=0.49\textwidth]{AAchi2-full.pdf}
-\includegraphics[width=0.49\textwidth]{BBchi2-full.pdf}\\
-\includegraphics[width=0.49\textwidth]{ACchi2-full.pdf}
-\includegraphics[width=0.49\textwidth]{BCchi2-full.pdf}
-\caption{{\bf JR. This should be also with $1\sigma$ errors. Also need to do this plot for Claudio's shape measure.} Pixel-wise $\chi$.}
+\includegraphics[width=0.49\textwidth]{AAferror-1sig.pdf}
+\includegraphics[width=0.49\textwidth]{BBferror-1sig.pdf}\\
+\includegraphics[width=0.49\textwidth]{ACferror-1sig.pdf}
+\includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
+\caption{ {\bf JR. \sout{ This should be also with $1\sigma$ errors.} Also need to do this plot for Claudio's shape measure.} \sout{Pixel-wise $\chi$.}
+The fractional error for the pixel-wise recovery of all models.
+The colors and labels are the same as in \figref{main results}.
+Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
 \label{main results pixel-wise}
@@
 a result, there is a general trend for the reconstruction quality to increase
-(and for $\chi$ to decrease). By adding more measurable information to each
+(and for $f$ to decrease). By adding more measurable information to each
 configuration the quality can also be affected. When both time delays and a
@@
 
-\item Change variable $\chi$ to something else ($f$?) to avoid
-  confusion with $\chi^2$.
-
-\item Correct equation \eqref{badness} to describe what is actually
-  calculated.
-
-\item Show results for $1\sigma$ and $2\sigma$ rather than full
-  \Glass\ ensemble.
+  \item \sout{Change variable $\chi$ to something else ($f$?) to avoid confusion with $\chi^2$.}
+
+  \item \sout{Correct equation \eqref{badness} to describe what is actually calculated.}
+
+  \item \sout{Show results for $1\sigma$ and $2\sigma$ rather than full \Glass\ ensemble.}
 
@@
 \appendix
+
+\section{Implementation Details}
+
+Since we want to model the density distribution with a computer it
+is convenient to choose units that make the relevant quantities of order
+unity.  We therefore measure lengths in light years, time in years, positions
+in arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
+arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to
+define a proxy to the Hubble constant $\zeta \equiv N^2 H_0$. We now 
+express the equations from \secref{sec:theory} in terms of these new units
+and introduce some other useful quantities.
+
+The lens equation in its complete form becomes:
+%
+\begin{eqnarray}
+N^2ct(\vec\theta) & = & (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 \nonumber \\
+& & - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
+\label{eqn:full_arrival_time}
+\end{eqnarray}
+%
+where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
+has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
+delay:
+%
+\begin{equation}
+\tau = \left[ (1+z_L) d_L\right]^{-1}\zeta t
+\label{tau}
+\end{equation}
+%
+in terms of our previous definitions. If we
+further define a dimensionless density:
+%
+\begin{equation}
+\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
+              = \frac{d_L}{\zeta}\Sigma
+\end{equation}
+%
+and a lensing potential:
+%
+\begin{equation}
+\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
+\label{lensing potential}
+\end{equation}
+%
+we can express \eqnref{eqn:full_arrival_time} very compactly as:
+%
+\begin{equation}
+\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
+\label{arrival time}
+\end{equation}
+We explicitly write $\kappa_\infty$ to remind ourselves
+that there is no source distance factor involved. This is useful when we
+consider multiple sources.
 
@@
 where $Q_n$ is the logarithm evaluated over the $n$th pixel at position $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.
-Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates such that
+Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates where 
 %

### 2013-09-27 limits/ms.tex
Fixed two overfull boxes.

@@
 \begin{table}
-\begin{tabular}{cllllllll}
-Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ & Notes\\
+\begin{tabular}{llllllll}
+Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ \\
 \hline
-AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & DM; shallow\\
-AC & 1 & 4 & 1 & $11^2$ & 50 kpc & DM; cuspy\\
-BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc &  Star; shallow\\
-BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & Star; cuspy
+DMdom/DMshallow & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
+DMdom/DMcuspy & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
+Sdom/DMshallow & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
+Sdom/DMcuspy & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
 \end{tabular}
-\caption{Profile parameters for the four mock galaxies. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
-all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$\,kpc.
-$\Rmap$ is the 2D projected radius used to generate the lens configurations.
-In the notes column we describe the mock as DM or star dominated with a shallow or cuspy central dark matter density profile.}
+\caption{Profile parameters for the four mock galaxies. The name indicates whether 
+  the galaxy is centrally dark matter or stellar dominated with a shallow or cuspy 
+  dark matter density profile.  Masses are in units of
+  $1.8\e{10}\Msun$. The scale lengths for all lenses are
+  $(a_\star,a_\mathrm{DM})=(2,20)$\,kpc. $\Rmap$ is the 2D projected radius
+used to generate the lens configurations.}
 \label{mock galaxy params}
@@
 %
-\[Q_n(x,y) = \frac12 \left[ \tilde Q_n(x_+,y_+)
-        + \tilde Q_n(x_-,y_-)
-        - \tilde Q_n(x_-,y_+)
-        - \tilde Q_n(x_+,y_-) \right]\]
+\begin{align*}
+Q_n(x,y) = \frac12 [\tilde Q_n(x_+,y_+)
+                  + \tilde Q_n(x_-,y_-) & 
+\\                - \tilde Q_n(x_-,y_+)
+                  - \tilde Q_n(x_+,y_-) ]
+\end{align*}
 %

### 2013-09-27 limits/ms.tex
Added mn2e files.

@@
 
-As outlined in \S\ref{sec:glass}, \Glass\ can also run post processing
-routines on the model ensemble which can be used to apply non-linear constraints.
-As an example, we consider here constraints from stellar kinematics.
-The models in the \Glass\ ensemble are processed as described in \S\ref{sec:glasskinematics}.
+As outlined in \S\ref{sec:glass}, \Glass\ can also run post processing routines
+on the model ensemble which can be used to apply non-linear constraints. As an
+example, we consider here constraints from stellar kinematics. The models in
+the \Glass\ ensemble are processed as described in \S\ref{sec:glasskinematics}.
 To illustrate the power of stellar kinematic constraints, in
-\figref{sigma-beta}, we plot the projected velocity dispersion calculated for one model model (extracted from the full ensemble) of the BC Quad with time delays and stellar mass (left), and the mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging integral (the aperture size), $a_p$ (right).
-In both cases, we calculate curves for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
-Over-plotted is the correct answer for the BC model (black).
-The stellar half mass radius (yellow) Einstein radius (black) are marked by vertical lines.
-For this configuration, these two radii are well-separated.
-
-Without even sweeping through the model ensemble and formally accepting/rejecting models, \figref{sigma-beta} already illustrates what we can hope to obtain from stellar kinematics.
-The most robust constraints follow if we can integrate out the effect of $\beta$ (right panel), since this is difficult to measure.
-For large enough aperture size ($a_p > 2r_{1/2}$), the average projected dispersion converges on a single well defined value independently of $\beta$.
-Since this converged value follows from the virial theorem, it is also rather insensitive to the shape of the potential \citep{2012ApJ...754L..39A}: it constitutes a robust constraint on the lensing potential.
-On the other hand, if the mass profile is well-constrained already at $r \sim r_{1/2}$, then we can use stellar kinematics to probe $\beta$.
-This can be seen in the left panel of \figref{sigma-beta}.
-Here we see that for a well-constrained mass model, the $\beta = 1$ curve lies significantly off from the true answer that has $\beta(r) \sim 0$.
-
-We now consider formally accepting/rejecting models from the full ensemble.
-We consider two regimes of interest: a model with a double where the mass profile is poorly constrained (XXX), and a model where the mass profile is very well constrained by the lens data (YYY).
-In the former case, we use $\overline{\sigma}(2 r_{1/2})$ to probe the mass independently of $\beta(r)$.
-We accept/reject models assuming a Gaussian error on measured $\overline{\sigma}(2 r_{1/2})$ of $\pm 10$\,km/s (similarly to the data quality presented for example in \citealt{2002MNRAS.337L...6T}).
-The results are shown in \figref{main results}, blue data points.
-In the latter case, we ask whether the data favour $\beta = 0$ or $\beta = 1$ by obtaining a $\chi^2$ goodness of fit measure between the true and modelled $\sigma_p(R)$.
-We accept/reject models from the ensemble above.
-The results for $\beta$ are shown in Figure ZZZ.
-
-The results for stellar kinematics match our expectations from \S\ref{sec:kinematics}.
-Where the lens data already constrain the mass distribution at $r \sim r_{1/2}$, stellar kinematics provide valuable information about the velocity anisotropy of the stars, $\beta$ (see Figure ZZZ).
-Where the lens data poorly constrain the mass distribution at $r_{1/2}$, we may `integrate out' the effect of unknown $\beta$ to obtain a robust measure of $M(r_{1/2})$ from the stellar kinematics.
-This latter is robust to both uncertainties in $\beta(r)$ and to our assumption of spherical symmetry in the kinematic models \citep{2012ApJ...754L..39A}.
-Finally, we note that there is a third interesting case.
-If the lens models well-constrain $M(r_{1/2})$ and stellar kinematics are available, then these can be used to probe cosmological models (see \S\ref{sec:theory}).
-We explore this in more detail in a separate publication.
+\figref{sigma-beta}, we plot the projected velocity dispersion calculated for
+one model model (extracted from the full ensemble) of the BC Quad with time
+delays and stellar mass (left), and the mean projected velocity dispersion
+(\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging
+integral (the aperture size), $a_p$ (right). In both cases, we calculate curves
+for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
+Over-plotted is the correct answer for the BC model (black). The stellar half
+mass radius (yellow) Einstein radius (black) are marked by vertical lines. For
+this configuration, these two radii are well-separated.
+
+Without even sweeping through the model ensemble and formally
+accepting/rejecting models, \figref{sigma-beta} already illustrates what we can
+hope to obtain from stellar kinematics. The most robust constraints follow if
+we can integrate out the effect of $\beta$ (right panel), since this is
+difficult to measure. For large enough aperture size ($a_p > 2r_{1/2}$), the
+average projected dispersion converges on a single well defined value
+independently of $\beta$. Since this converged value follows from the virial
+theorem, it is also rather insensitive to the shape of the potential
+\citep{2012ApJ...754L..39A}: it constitutes a robust constraint on the lensing
+potential. On the other hand, if the mass profile is well-constrained already
+at $r \sim r_{1/2}$, then we can use stellar kinematics to probe $\beta$. This
+can be seen in the left panel of \figref{sigma-beta}. Here we see that for a
+well-constrained mass model, the $\beta = 1$ curve lies significantly off from
+the true answer that has $\beta(r) \sim 0$.
+
+We now consider formally accepting/rejecting models from the full ensemble. We
+consider two regimes of interest: a model with a double where the mass profile
+is poorly constrained (XXX), and a model where the mass profile is very well
+constrained by the lens data (YYY). In the former case, we use
+$\overline{\sigma}(2 r_{1/2})$ to probe the mass independently of $\beta(r)$.
+We accept/reject models assuming a Gaussian error on measured
+$\overline{\sigma}(2 r_{1/2})$ of $\pm 10$\,km/s (similarly to the data quality
+presented for example in \citealt{2002MNRAS.337L...6T}). The results are shown
+in \figref{main results}, blue data points. In the latter case, we ask whether
+the data favour $\beta = 0$ or $\beta = 1$ by obtaining a $\chi^2$ goodness of
+fit measure between the true and modelled $\sigma_p(R)$. We accept/reject
+models from the ensemble above. The results for $\beta$ are shown in Figure
+ZZZ.
+
+The results for stellar kinematics match our expectations from
+\S\ref{sec:kinematics}. Where the lens data already constrain the mass
+distribution at $r \sim r_{1/2}$, stellar kinematics provide valuable
+information about the velocity anisotropy of the stars, $\beta$ (see Figure
+ZZZ). Where the lens data poorly constrain the mass distribution at $r_{1/2}$,
+we may `integrate out' the effect of unknown $\beta$ to obtain a robust measure
+of $M(r_{1/2})$ from the stellar kinematics. This latter is robust to both
+uncertainties in $\beta(r)$ and to our assumption of spherical symmetry in the
+kinematic models \citep{2012ApJ...754L..39A}. Finally, we note that there is a
+third interesting case. If the lens models well-constrain $M(r_{1/2})$ and
+stellar kinematics are available, then these can be used to probe cosmological
+models (see \S\ref{sec:theory}). We explore this in more detail in a separate
+publication.
 

### 2013-09-28 limits/ms.tex
New plots for sigma/beta comparison. New plots of recovered/true 2d mass distribution. Adjusted text.

@@
 
-The main results from modelling these different configurations are shown in black in
-\figref{main results} and \figref{main results pixel-wise}. Each subplot corresponds to a different galaxy and
-the vertical axis shows the range of `quality' of recovery. In \figref{main results}, this quality is
-defined over radial bins of mass as
+\begin{figure*}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
+\caption{ {\bf (Left)} Mock data distribution on coarse grid. {\bf (Right)} Recover ensemble average kappa distribution.}
+\label{2d mass reconstruction}
+\end{figure*}
+
 %
@@
 this.
+
+\begin{figure*}
+\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sb.pdf}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
+\caption{ 
+(Left) Projected radially averaged velocity dispersion for Sdom/DMcuspy ZConstrastR1R3 models and the mock data.
+(Right) Projected radially averaged velocity dispersion for Sdom/DMcuspy QuadR1a models and the mock data.
+}
+\label{main results pixel-wise}
+\end{figure*}
 
@@
 
-\item Add example plot of the projected density and recovered
+\item \sout{Add example plot of the projected density and recovered
   projected density (cf. plots Jonathan made for Justin's ERC
-  proposal).
+proposal).}
 
@@
 
-\item Take a model that is well constrained by strong lensing
+\item \sout{Take a model that is well constrained by strong lensing
   (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
   in the ensemble using the kinematics module. Compare this with the
-  true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
-  a $\chi^2$ this time!).  Show the true $\sigma_p(R)$ and overlay
+true $\sigma_p(R)$ from the mock data} to obtain a $\chi^2$ (actually
+  a $\chi^2$ this time!).  \sout{Show the true $\sigma_p(R)$ and overlay
   coloured bands from the lensing model ensemble assuming $\beta = 0$
-  or $\beta = 1$.
+or $\beta = 1$.}
 

### 2013-11-13 limits/ms.tex
New sigp plots and updated tex.

@@
 \includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
-\caption{{\bf JR. Cut the analytic profiles from this Figure. All fonts and labels should be larger. Left panel should start at 0.7kpc.}
+\caption{{\bf JR. \sout{Cut the analytic profiles from this Figure. All fonts and labels should be larger.} Left panel should start at 0.7kpc.}
 \textbf{Left:} 
@@
 \section{Results}\label{sec:results}
-\figref{reconstruction} shows a typical reconstruction of a
-lens. The far left plot shows the ensemble average arrival time surface with
-image marked as circles and the inferred source position as a diamond. The
-center plot shows the radial density profile. The error bars cover the full
-range of models generated by \Glass {\bf JR. Why do this? Surely 1 or 2 sigma
-errors make more sense? I've deleted the ``full ensemble'' results and kept the
-$1\sigma$ ones instead.}. The true density profile from the mock data is also
-plotted for comparison. The vertical lines mark the radial position of the
-images. The final plot on the right is of the enclosed mass. As expected, the
-error bars are smallest in the region of the images where the most information
-about the lens is present. The dip in the profile at the end of the profile is
-due to the cut off in mass in the lensing map. This is of little importance,
-though, as there is no lensing information there.
+\figref{reconstruction} shows a typical reconstruction of a lens. The far left
+plot shows the ensemble average arrival time surface with image marked as
+circles and the inferred source position as a diamond. The center plot shows
+the radial density profile. The error bars cover a $1\sigma$ range around the
+median. \sout{the full range of models generated by \Glass {\bf JR. Why do
+this? Surely 1 or 2 sigma errors make more sense? I've deleted the ``full
+ensemble'' results and kept the $1\sigma$ ones instead.}}. The true density
+profile from the mock data is also plotted for comparison. The vertical lines
+mark the radial position of the images. The final plot on the right is of the
+enclosed mass. As expected, the error bars are smallest in the region of the
+images where the most information about the lens is present. The dip in the
+profile at the end of the profile is due to the cut off in mass in the
+lensing map. This is of little importance, though, as there is no lensing
+information there.
 
@@
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
-\caption{ {\bf (Left)} Mock data distribution on coarse grid. {\bf (Right)} Recover ensemble average kappa distribution.}
+\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.}
 \label{2d mass reconstruction}
@@
 
+The main results from modeling these different configurations are shown in
+\figref{main results} and \figref{main results pixel-wise}. Each
+subplot corresponds to a different mock galaxy. We show the fractional error of the mass
+distribution for each of the test configurations with (red) and without stellar mass (black)
+In \figref{main results}, the error is defined over radial bins of mass as
 %
 \begin{equation} \label{badness}
-  f_r = \frac {\int \left|\Delta M(r)\right|\; dr } {\int M(r)\; dr}
-\end{equation}
-%
-while in \figref{main results pixel-wise} the quality is defined over all the pixels
+  f_R = \frac {\sum_r \left|M_p(r) - \tilde M_p(r)\right| } {\sum \tilde M_p(r)}
+\end{equation}
+%
+where $M_p$ is the mass in a radial bin and $\tilde M_p$ is the mass from the mock galaxy.
+In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
 %
 \begin{equation} \label{badness}
-f_\theta = \frac
-       {\int \left|\Delta M(\vec\theta)\right| \; d \vec{\theta} }
-       {\int M(\vec\theta) \; d \vec\theta}
-\end{equation}
-In both cases, the delta difference is between a single recovered model and the known mock galaxy.
+f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum \tilde M(\vec\theta)}
+\end{equation}
+%
 %\begin{equation}
@@
 \includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
-\caption{ 
-(Left) Projected radially averaged velocity dispersion for Sdom/DMcuspy ZConstrastR1R3 models and the mock data.
-(Right) Projected radially averaged velocity dispersion for Sdom/DMcuspy QuadR1a models and the mock data.
+\caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3
+  (left) and QuadR1a (right) assuming an anisotropy $B=0$ (green) and $B=0$ (blue). In both plots, the actual projected
+  velocity dispersion of the mock data (black).
   }
-\label{main results pixel-wise}
+\label{fig:sigp}
 \end{figure*}
@@
   in the ensemble using the kinematics module. Compare this with the
-true $\sigma_p(R)$ from the mock data} to obtain a $\chi^2$ (actually
-  a $\chi^2$ this time!).  \sout{Show the true $\sigma_p(R)$ and overlay
+true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
+  a $\chi^2$ this time!). Show the true $\sigma_p(R)$ and overlay
   coloured bands from the lensing model ensemble assuming $\beta = 0$
@@
 
-\item Clarify number of lens configurations in \S\ref{sec:lensconfig}.
+\item \sout{Clarify number of lens configurations in \S\ref{sec:lensconfig}.}
 

### 2013-11-14 limits/ms.tex
New sigp plots with real sigp, not sigpbar.

@@
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
-\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.}
+\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.
+XXX: Mention log scale and 0== critical density.}
 \label{2d mass reconstruction}
@@
 \begin{figure*}
-\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sb.pdf}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
+\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp_beta.pdf}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp_beta.pdf}
 \caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3

### 2013-11-14 limits/ms.tex
New sigp and sigpbar plots.
Updated sigp/sigpbar figure captions.

@@
 \begin{figure*}
-\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp_beta.pdf}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp_beta.pdf}
-\caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3
-  (left) and QuadR1a (right) assuming an anisotropy $B=0$ (green) and $B=0$ (blue). In both plots, the actual projected
-  velocity dispersion of the mock data (black).
-  }
-\label{fig:sigp}
-\end{figure*}
+\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp.pdf}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp.pdf}
+\caption{
+  Estimated projected radially averaged velocity dispersion (\eqnref{eqn:sphericaljeans}) $\sigma_p$ for two Sdom/DMcuspy models ZContrastR1R3
+  (left) and QuadR1a (right) assuming an anisotropy $\beta=0$ (blue, solid) and $\beta=1$
+  (blue, dashed).  Also shown are the equivalent curves for the mock data after
+  running it through the deprojection routines (grey). The solid black line is
+  the actual cylindrically averaged velocity dispersion of the original mock particle data.
+  The stellar half mass radius (yellow) Einstein
+radius (black) are marked by vertical lines. For this configuration, these two
+radii are well-separated.}
+  \label{fig:sigp} \end{figure*}
 
@@
 \begin{figure*}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS-sb.pdf}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS-sb.pdf}
-\caption{{\bf Left:} {\bf JR.
-Jonathan to add.} The projected velocity dispersion calculated for one model model (extracted from the full ensemble) of the BC Quad with time delays and stellar mass.
-{\bf Right:} The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging integral (the aperture size), $a_p$.
-In both cases, we calculate curves for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
-Over-plotted is the correct answer for the BC model (black) {\bf JR.
-Jonathan to add}.
-The stellar half mass radius (yellow) Einstein radius (black) are marked by vertical lines.
-For this configuration, these two radii are well-separated.}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
+\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
+\caption{{\bf Left:} 
+The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
+limit of the averaging integral (the aperture size), $a_p$
+  for two Sdom/DMcuspy models ZContrastR1R3
+  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
+  (blue, dashed).  Also shown are the equivalent curves for the mock data after
+  running it through the deprojection routines (grey). 
+\sout{Over-plotted is the correct answer for the BC model (black)
+  {\bf JR. Jonathan to add}.} 
+  The stellar half mass radius (yellow) Einstein
+radius (black) are marked by vertical lines. For this configuration, these two
+radii are well-separated.}
 \label{sigma-beta}

### 2013-11-14 limits/ms.tex
Updated kappa plots so that the color scale is consistent. Updated sigp plot. Modified density profile equation to avoid confusing variable names. Added missing citations.

@@
 physical models. The explicit implementation for these priors has been
-explained in \cite{}, but can be summarized as
+explained in \cite{2008ApJ...679...17C}, but can be summarized as
 \begin{enumerate}
@@
 \beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
-solution space polytope. Using the MCMC sampling strategy described in \cite{}
+solution space polytope. Using the MCMC sampling strategy described in \cite{2012MNRAS.425.3077L}
 we uniformly sample this space. Collectively, the sampled models are referred
@@
 
-The galaxies were generated as three dimensional particle distributions as in \citet{2009MNRAS.395.1079D}. Each component follows the profile:
-\begin{equation}
-\rho(m) = \frac{M}{4\pi a^3}(3-\gamma){(m/a)^{-\gamma}(1 + m/a)^{\gamma-4}}
+The galaxies were generated as three dimensional particle distributions as in
+\citet{2009MNRAS.395.1079D}. Each component follows the profile:
+%
+\begin{equation} 
+  \rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}} 
   \label{Dehnen profile} 
 \end{equation} 
-where $m^2 = (x/a)^2 + (y/b)^2 + (z/c)^2$, with $[a,b,c] = ???$; $\gamma$ is the central density profile index; and $a$ is the scale radius. In the
-case $\gamma=1$ (and in the limit of spherical symmetry), this is the Hernquist profile \citep{1990ApJ...356..359H}.  The four combinations of
-profile indices are shown in \tabref{mock galaxy params}. {\bf JR. Need to add explanation of triaxial parameters here. Is the above density equation correct in fact?}
+%
+where $a$ is the component scale radius mentioned in \tabref{mock galaxy params},
+$r^2 = (x/\lambda_1)^2 + (y/\lambda_2)^2 + (z/\lambda_3)^2$, and the axis
+ratios are $\lambda_1:\lambda_2:\lambda_3 = 6:4:3$.
+In the case where the central density profile index
+$\gamma$ is unity (and in the limit of spherical symmetry), this is the Hernquist
+profile \citep{1990ApJ...356..359H}.  The four combinations of profile indices
+are shown in \tabref{mock galaxy params}. {\bf JR. Need to add explanation of
+triaxial parameters here. Is the above density equation correct in fact?}
 
@@
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
-\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.
-XXX: Mention log scale and 0== critical density.}
+\caption{ The mock data distribution for Sdom/DMcuspy on a coarse grid (left)
+  and a typical recovered ensemble average $\kappa$ distribution. The contours are
+  logarithmic values, where level 0 corresponds to the critical density.}
 \label{2d mass reconstruction}

### 2013-11-14 limits/ms.tex
Fixed text.

@@
 We generate four two-component mock galaxies, where the dark matter and stellar
-profiles are allowed to be both steep and shallow.  The enclosed mass in all cases
-is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. These
+profiles are allowed to be both steep and shallow.  
+%The enclosed mass in all cases
+%is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. 
+The enclosed mass of the stars and dark matter are both fixed to be 
+$M_{*,\mathrm{DM}} = 1.8 \times 10^{10}$\,M$_\odot$ at the stellar scale radius 
+$a_* = 2$\,kpc, such that the stars and dark matter contribute equally to the total
+mass at $a_*$. The dark matter scale length is fixed for all models at $a_\mathrm{DM}
+= 20$\,kpc.
+These
 values were chosen to closely resemble the lensing galaxy B1115 \citep{1980Natur.285..641W}. We place the galaxy at
@@
 \begin{equation} \label{badness}
-  f_R = \frac {\sum_r \left|M_p(r) - \tilde M_p(r)\right| } {\sum \tilde M_p(r)}
+  f_R = \frac {\sum_i \left|M_p(i) - \tilde M_p(i)\right| } {\sum \tilde M_p(i)}
 \end{equation}

### 2014-01-08 limits/ms.tex
Added a histogram showing the distribution of axis ratios across models.

@@
 
-\item Check that you and Claudio average to the same projected radius
+\item \sout{Check that you and Claudio average to the same projected radius
   (one pixel past outermost image) when calculating
-  $lambda_1/lambda_2$ and $\theta$.
+  $lambda_1/lambda_2$ and $\theta$.}. This is correct.
 
@@
 \label{raytracing convergence tests}
+\end{figure}
+
+\begin{figure}
+\plotone{BCZContrastR1R3_TmS_shape.pdf}
+\caption{}
+\label{}
 \end{figure}

### 2014-01-20 limits/ms.tex
Added shape plots.

@@
  \leavevmode
- \columnwidth=.30\columnwidth
+ \columnwidth=.30\textwidth
  \includegraphics[width={\columnwidth}]{#1}%
@@
 
+\begin{figure*}
+\plotthree{AAExtendedDoubleR1_TmS-shape-hist-11.pdf} {AAferror_shape-1sig.pdf} {BBferror_shape-1sig.pdf}\\
+\plotthree{BCZContrastR1R3_TmS-shape-hist-212.pdf} {ACferror_shape-1sig.pdf} {BCferror_shape-1sig.pdf}
+\caption{ The two plots in the left most column show sample distributions of
+  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
+  The upper (poor) plot is from the DMdom/DMshallow galaxy, while the lower (good) plot is
+  from the Sdom/DMcuspy galaxy. The black vertical lines mark the $1\sigma$
+  region and the vertical blue line is the value of $s$ for the corresponding
+  mock galaxy. The remain four plots are similar to those in \figref{main
+  results pixel-wise} and show the fractional error of $s$ over all the models,
+with respect to the mock galaxies.}
+
+\label{main results pixel-wise}
+\end{figure*}
+
 The abundance of strong lensing data increases from left to right within each plot. As
@@
 
-\begin{figure}
-\plotone{BCZContrastR1R3_TmS_shape.pdf}
-\caption{}
-\label{}
-\end{figure}
-
 \section{Derivation of pixelated density coefficients}

### 2014-01-21 limits/ms.tex
Minor text changes and improved Figures 1,3.

@@
 encoding the lens equation, a basis and priors for the mass
-distribution, and various post-processing modules.  \Glass\ is
-described in \secref{sec:glass}.  In \secref{sec:theory} before that
-we review the elements of lensing theory, stellar population
-synthesis, and stellar dynamics we will need.
+distribution, and various post-processing and visualisation modules.  \Glass\
+is described in \secref{sec:glass}.  In \secref{sec:theory} before that we
+review the elements of lensing theory, stellar population synthesis, and
+stellar dynamics we will need.
 
@@
 
-We follow \cite{1986ApJ...310..568B} with minor differences in notation
-notation.
+We follow \cite{1986ApJ...310..568B} with minor differences in notation.
 
@@
 density $\Sigma$ which diverts the path of a photon instantaneously
-through the bending angle $\vec\alpha$.  The $D$ factors are angular
-diameter distances, as in the previous section.
+through the bending angle $\vec\alpha$.  The $D$ factors, as in the previous section, are angular
+diameter distances, which depend on the particular choice of cosmological
+parameters $\Omega$:
 \begin{equation}
@@
 
-\subsection{Setting up the triaxial N-body mocks}
+\subsection{The triaxial N-body mock galaxies}
 
@@
 \hline
-DMdom/DMshallow & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
-DMdom/DMcuspy & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
-Sdom/DMshallow & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
-Sdom/DMcuspy & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
+DM-ctr,DM-core & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
+DM-ctr,DM-cusp & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
+S-ctr,DMcore & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
+S-ctr,DMcusp & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
 \end{tabular}
@@
 true; it is most often the case with real galaxies, unless there is an obvious
-observed asymmetry. The central pixel was refined into a further nine pixels to
+observed asymmetry. The central pixel was refined into a further 25 pixels to
 capture any steep rise in the profile.  Two of the four mock galaxies have a
@@
 where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
-has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
-delay:
+has units of \Msun/lyr$^2$. We can clean this up by first writing down a dimensionless time
+delay
 %
@@
 %
-in terms of our previous definitions. If we
-further define a dimensionless density:
+in terms of our previous definitions and defining $D_L \equiv (c/H_0)d_L$. We
+further define a dimensionless density
 %
@@
 %
-and a lensing potential:
+and a lensing potential
 %
@@
 %
-we can express \eqnref{eqn:full_arrival_time} very compactly as:
+Now we can express \eqnref{eqn:full_arrival_time} very compactly as
 %
@@
 \end{equation}
+%
+where $\xi=d_S / d_{LS}$.
 We explicitly write $\kappa_\infty$ to remind ourselves

### 2014-01-21 limits/ms.tex
Plots.
Updated plots.
New plot of sigp without stellar mass.
Commented out Figure 9. Split shape plots into two.

@@
 \renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}}
+
+\newcommand{\mockAA}{{\sc Ssteep-DMshallow}}
+\newcommand{\mockAC}{{\sc Ssteep-DMsteep}}
+\newcommand{\mockBB}{{\sc Ssteep-DMshallow}}
+\newcommand{\mockBC}{{\sc Ssteep-DMsteep}}
 
@@
 \hline
-DM-ctr,DM-core & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
-DM-ctr,DM-cusp & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
-S-ctr,DMcore & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
-S-ctr,DMcusp & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
+\mockAA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
+\mockAC & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
+\mockBB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
+\mockBC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
 \end{tabular}
@@
 \begin{figure*}
-\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-a.pdf}
-\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-b.pdf}
-\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-c.pdf}
+  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-a.pdf}\hspace{-2em}
+  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-b.pdf}\hspace{-2em}
+  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-c.pdf}\\\vspace{-1em}
+  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-a.pdf}\hspace{-2em}
+  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-b.pdf}\hspace{-2em}
+  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-c.pdf}
 \caption{
@@
 \textbf{Right:}
-The cumulative mass. The error bars on both plots are $1\sigma$.}
+The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range for DM+Stars (blue).}
 \label{reconstruction}
@@
 
-\begin{figure*}
-\plotthree{AAExtendedDoubleR1_TmS-shape-hist-11.pdf} {AAferror_shape-1sig.pdf} {BBferror_shape-1sig.pdf}\\
-\plotthree{BCZContrastR1R3_TmS-shape-hist-212.pdf} {ACferror_shape-1sig.pdf} {BCferror_shape-1sig.pdf}
+\begin{figure}[h]
+\plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}
 \caption{ The two plots in the left most column show sample distributions of
@@
   region and the vertical blue line is the value of $s$ for the corresponding
-  mock galaxy. The remain four plots are similar to those in \figref{main
+mock galaxy. }
+
+\label{shape results}
+\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=0.33\textwidth]{AAferror_shape-1sig.pdf} \hspace{2cm}
+\includegraphics[width=0.33\textwidth]{BBferror_shape-1sig.pdf}\\
+\includegraphics[width=0.33\textwidth]{ACferror_shape-1sig.pdf}\hspace{2cm}
+\includegraphics[width=0.33\textwidth]{BCferror_shape-1sig.pdf}
+\caption{ The remain four plots are similar to those in \figref{main
   results pixel-wise} and show the fractional error of $s$ over all the models,
@@
 
-\label{main results pixel-wise}
+\label{shape results}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp.pdf}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp.pdf}
+\includegraphics[width=0.33\textwidth]{BC_beta.pdf}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_Tms_sigp-1.pdf}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS_sigp-2.pdf}
 \caption{
@@
 
-\begin{figure*}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
-\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
-\caption{{\bf Left:} 
-The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
-limit of the averaging integral (the aperture size), $a_p$
-  for two Sdom/DMcuspy models ZContrastR1R3
-  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
-  (blue, dashed).  Also shown are the equivalent curves for the mock data after
-  running it through the deprojection routines (grey). 
-\sout{Over-plotted is the correct answer for the BC model (black)
-  {\bf JR. Jonathan to add}.} 
-  The stellar half mass radius (yellow) Einstein
-radius (black) are marked by vertical lines. For this configuration, these two
-radii are well-separated.}
-\label{sigma-beta}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
+%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
+%\caption{{\bf Left:} 
+%The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
+%limit of the averaging integral (the aperture size), $a_p$
+%  for two Sdom/DMcuspy models ZContrastR1R3
+%  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
+%  (blue, dashed).  Also shown are the equivalent curves for the mock data after
+%  running it through the deprojection routines (grey). 
+%\sout{Over-plotted is the correct answer for the BC model (black)
+%  {\bf JR. Jonathan to add}.} 
+%  The stellar half mass radius (yellow) Einstein
+%radius (black) are marked by vertical lines. For this configuration, these two
+%radii are well-separated.}
+%\label{sigma-beta}
+%\end{figure*}
 

### 2014-01-22 limits/ms.tex
A little text clean up. Rewrote figure captions.

@@
 \usepackage{ulem} % Only necessary for striking out TODO items see \sout
+\usepackage{color} % Only necessary for hilight
 
@@
 
+\newcommand{\hilight}[1]{{\bf \color{red} #1}}
+
 \newcommand{\kpc}{\ensuremath{\mathrm{kpc}}}
@@
 \newcommand{\eqnref}[1] {Eq.~(\ref{#1})}
+\newcommand{\eqnrefp}[1] {(Eq.~\ref{#1})}
 \newcommand{\secref}[1] {\S\ref{#1}}
@@
 
-\title[\Glass]{Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens}
-\author{%
-Jonathan P. Coles 
-\and 
-Justin I. Read
-\and 
-Prasenjit Saha 
+\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
+\author[J.~P.~Coles~et~al.]{%
+Jonathan P.~Coles,$^{1,3}$\thanks{jonathan@exascale-computing.eu}%
+\newauthor%
+Justin I.~Read$^2$,%
+\newauthor%
+and Prasenjit Saha$^3$%
+%
+\\
+$^1$Exascale Research Computing Lab, Versailles Saint-Quentin-en-Yvelines University,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
+$^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
+$^3$Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland
 }
@@
 \begin{abstract}
-We use a new non-parametric gravitational -- \Glass -- to determine what quality of data (strong lensing, stellar kinematics, and/or stellar masses) are required to measure the circularly averaged mass profile of a lens and its shape.
+We use a new non-parametric gravitational modelling tool---\Glass---to determine what quality of data (strong lensing, stellar kinematics, and/or stellar masses) are required to measure the circularly averaged mass profile of a lens and its shape.
 \Glass\ uses an under-constrained adaptive grid of mass pixels to model the lens, searching through thousands of models to marginalise over model uncertainties.
@@
 distances: let $D_L$, $D_S$, $D_{LS}$ be the angular-diameter
-distances to the lens, source, and from lens to source; there are all
+distances to the lens, source, and from lens to source; they are all
 strictly $\propto c/H_0$.  Typically
@@
 where $R_G$ is the gravitational radius $GM/c^2$.  If the source is a
-quasar or otherwise rapidly variable, a time delay is the variability
-will be present
+quasar or otherwise rapidly variable, a time delay $\Delta t$ in the variability
+will be present where
 \begin{equation}
@@
 \cite{1981ApJ...244..736Y} were remarkably prescient about the
-subsequent development of lens modelling.  First, the introduced the
+subsequent development of lens modelling.  First, they introduced the
 technique of choosing a parametric form for the lensing mass and then
@@
   but these are much less restrictive than parametric forms.
-  \cite{2006MNRAS.367.1209L} implemented a particular elegant prior,
+  \cite{2006MNRAS.367.1209L} implemented a particularly elegant prior,
   which is that the mass distribution must be non-negative and no
-  extra images are produced.  Free-form are more commonly used with
+  extra images are produced.  Free-form models are more commonly used with
   cluster lenses \citep{2009ApJ...690..154S,2013arXiv1304.2393S}, but
@@
   $H_0$ \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}, but
-  the less restrictive assumptions of free-form models resolved these
+  the less restrictive assumptions of free-form models resolved those
   tensions \citep{2007ApJ...667..645R}.
@@
   distributions that nonetheless all fit the data, are a way of
-  cambating the non-uniqueness of models.  Model ensembles are
+  combating the non-uniqueness of models.  Model ensembles are
   possible in parametric models \citep{1999AJ....118...14B} but are
@@
   lenses in which stellar mass dominates can be used to derive upper
-  bounds on the stellar $M/L$ \cite{2010MNRAS.409L..30F}. Lower bounds
+  bounds on the stellar $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds
   on stellar $M/L$ have also been claimed \citep{2013MNRAS.428.3183D}
@@
   blind tests have appeared in earlier work \citep[for example, Figure
-    2 in][]{2000AJ....119..439W}, but more recently, test against
+    2 in][]{2000AJ....119..439W}, but more recently, tests against
   dynamically simulated galaxies are favoured
@@
 
-In this paper, we use a new program --- \Glass\ --- to determine what
+In this paper, we use a new program---\Glass, the Gravitational Lensing AnalysiS Software---to determine what
 combination of lensing, stellar mass, and stellar kinematic
-constraints best constrain the projected mass profile and shape of a
-gravitational lens.  The compute-intensive core of \Glass\ is a
+constraints best constrain the projected mass profile and shape of several
+gravitational lens produced from mock data.  The compute-intensive core of \Glass\ is a
 parallel implementation of the high-dimensional sampling algorithm
@@
 maps an observed image position $\vec\theta$ to a source position
-$\vec\beta$.  The lens can then be thought of as a projected surface
+$\vec\beta$.  The lens can be thought of as a projected surface
 density $\Sigma$ which diverts the path of a photon instantaneously
@@
 \end{equation}
+%
+and $D_L \equiv D_{0,L}$, $D_S \equiv D_{0,S}$.
 One way to understand the lens equation is via Fermat's principle. We
@@
 that $\nabla\tau(\vec\theta_1)=0$.  A measurement of time delays
-between images at $\theta_1$ and $\theta_1$ implies that
+between images at $\theta_1$ and $\theta_2$ implies that
 $t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both these
@@
 mass-sheet degeneracy, which is that image positions remain invariant
-if the $D_S/D_{LS} - \kappa(\vec\theta)$ are each multiplied by an
+if the $D_S/D_{LS} - \kappa(\vec\theta)$ \hilight{ $\leftarrow$ What is meant by this? Can we just write $\tau(\vec\theta)$? }are each multiplied by an
 arbitrary constant.  This amounts to multiplying the arrival-time
@@
 \citep{2004ApJ...614L.101C,2012ApJ...747...69C,2013MNRAS.429L..15F}.
-The \cite{2003PASP..115..763C} would, however, still provide a robust
-lower limit on the stellar mass.  Hence, also a limit on the total
+The \cite{2003PASP..115..763C} IMF would, however, still provide a robust
+lower limit on the stellar mass and hence, also a limit on the total
 mass.  Accordingly, \Glass\ allows a constraint of the form
@@
 \end{equation} 
-where $\sigma_p$ is the projected velocity dispersion of the stars as a function of projected radius $R$; $I(R)$ is the surface density of the stars; $\nu(r)$ is the three dimensional stellar density; $\sigma_{r,t}(r)$ are the radial and tangential velocity dispersions, respectively; $\beta(r) = 1 - \sigma_t^2/\sigma_r^2 = \mathrm{const.}$ is the velocity anisotropy (here assumed to be constant); $G$ is Newton's gravitational constant; and $M(r)$ is the mass profile that we would like to measure.
-
-It is immediately clear from \eqnref{eqn:sphericaljeans} that, even assuming spherical symmetry, we have a degeneracy between the enclosed mass profile $M(r)$ and the velocity anisotropy $\beta(r)$.
-This can be understood intuitively since $\beta(r)$ measures the relative importance of radial versus circular orbits and is intrinsically difficult to constrain given only one component of the velocity vector for each star.
-Nonetheless, $\beta(r)$ can be constrained given sufficiently many stars, since radial Doppler velocities sample eccentric orbits as $r\rightarrow 0$ and tangential orbits as $r\rightarrow \infty$ \citep[e.g.][]{2002MNRAS.330..778W}.
-It can also be estimated if an independent measure of $M(r)$ is available -- for example coming from strong lensing.
-Finally, we may integrate out the effect of unknown $\beta(r)$ by performing a luminosity weighted average over all radii:
+where $\sigma_p$ is the projected velocity dispersion of the stars as a
+function of projected radius $R$; $I(R)$ is the surface density of the stars;
+$\nu(r)$ is the three dimensional stellar density; $\sigma_{r,t}(r)$ are the
+radial and tangential velocity dispersions, respectively; $\beta(r) = 1 -
+\sigma_t^2/2\sigma_r^2 = \mathrm{const.}$ is the velocity anisotropy (here
+assumed to be constant, and not to be confused with $\vec\beta(\vec\theta)$ from
+lensing); $G$ is Newton's gravitational constant; and $M(r)$ is
+the mass profile that we would like to measure. By convension, we always write $R$ 
+for a projected radius, and $r$ for a 3d radius.
+
+It is immediately clear from \eqnref{eqn:sphericaljeans} that, even assuming
+spherical symmetry, we have a degeneracy between the enclosed mass profile
+$M(r)$ and the velocity anisotropy $\beta(r)$. This can be understood
+intuitively since $\beta(r)$ measures the relative importance of radial versus
+circular orbits and is intrinsically difficult to constrain given only one
+component of the velocity vector for each star. Nonetheless, $\beta(r)$ can be
+constrained given sufficiently many stars, since radial Doppler velocities
+sample eccentric orbits as $r\rightarrow 0$ and tangential orbits as
+$r\rightarrow \infty$ \citep[e.g.][]{2002MNRAS.330..778W}. It can also be
+estimated if an independent measure of $M(r)$ is available -- for example
+coming from strong lensing. Finally, we may integrate out the effect of unknown
+$\beta(r)$ by performing a luminosity weighted average over all radii:
 
@@
 
-\Glass\ is an evolution of the concepts employed by the free form modelling tool
+\Glass is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
 \PixeLens\ but completely rewritten in Python and C. 
@@
 language and for its large scientific library support. The flexibility allows 
-\Glass\ to have quite sophisticated behavior while at the same time simplfying the 
+\Glass\ to have quite sophisticated behavior while at the same time simplifying the 
 user experience and reducing the overall development time. One of the striking
 features is that the input file to \Glass\ is itself a Python program.
-Understanding Python is not necessary, however, to use \Glass\ but this allows
-a user to build the analysis of a model directly into the input file. \Glass\
+Understanding Python is not necessary for the most basic use, but this allows
+a user to build complex analysis of a model directly into the input file. \Glass\
 may also be used as an external library to other Python programs.  The software
-is freely available for download or from the author.
+is freely available for download or from the author%
+%
+\footnote{Currently hosted on GitHub: www.github.com/jpcoles/glass or through
+www.jpcoles.com/glass.}.
 
@@
   \setcounter{enumi}{3}
-  \item The central region can be have a higher resolution to capture steep models. 
+  \item The central region can have a higher resolution to capture steep models. 
 \end{enumerate}
@@
 With the default basis set of pixels, the mass distribution of the lens is
-described by uniform grid. However, in the central region of a lensing galaxy
+described by a uniform grid. However, in the central region of a lensing galaxy
 where the mass profile may rise steeply, the center pixel uses a higher
@@
 \PixeLens\ only allows for a shear term to be added to the potential (as shown
-later in \eqnref{shear}) to account for mass external to model region. This
+later in \eqnref{shear}) to account for mass external to the modelled region. This
 is useful to capture the gross effects of a distant neighbour. \Glass\ also
-has a shear term but in addition allows for analytic potentials to
+has a shear term but additionally allows for analytic potentials to
 be included. This can be used to model substructure or multiple neighbors close
@@
 provides many functions for viewing and manipulating the computed models.
-These functions can either be called from a program written by the user or 
-by using the program \textsc{viewstate.py} included with \Glass. There is
-also a tools, \textsc{lenspick.py} for creating a lens, either from an $N$-body
-simulation file, or from an analytic form. To load the simluation data, \Glass\
-uses \textsc{PynBody} and can thus load any file supported by that tool.
+These functions can either be called from a program written by the user or by
+using the program \textsc{viewstate.py} included with \Glass. There is also a
+tool, \textsc{lenspick.py} for creating a lens, either analytically or from an
+$N$-body simulation file. To load the simulation data, \Glass\ relies on the
+\textsc{Pynbody} library \citep{pynbody} and can thus load any file supported by that package.
 
@@
 points are solutions to the lens equation and satisfy other physically
-motivated linear priors (the sampling algorithm in \Glass\ is not the same as
+motivated linear priors (the sampling algorithm in \Glass\ is \emph{not} the same as
 employed in \PixeLens).  We therefore formulate all of our equations as
@@
 The pixels only cover a finite circular area with physical radius $\Rmap$ and
-pixel radius $\Rpix$ centered on the lensing galaxy. To account for any global
+pixel radius $\Rpix$ with the central cell centered on the lensing galaxy. To account for any global
 shearing outside this region from, e.g., a neighboring galaxy, we also add to
@@
 potentials are straightforward to add and can be included directly in the input file.
-If the stellar density has been estimated we can use this as a lower bound
+If the stellar density $\kappa_s$ has been estimated we can use this as a lower bound
 where the stellar potential is a known constant of the form \eqnref{discrete
-potential}.
+potential}, e.g., $\kappa_n = \kappa_\mathrm{DM} + \kappa_s$ for a two-component model.
 
@@
 In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
-\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
+\vec\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
 solution space polytope. Using the MCMC sampling strategy described in \cite{2012MNRAS.425.3077L}
 we uniformly sample this space. Collectively, the sampled models are referred
-to as an ensemble $\E = \{\M_i\}$, where we usually generate $\sim$1000 models. We
-will typically show the ensemble average $\Eavg$ in the plots to
-follow.
+to as an ensemble $\E = \{\M_i\}$, where we usually generate $|\E| \sim 1000$ models.
 
@@
 error is below the equivalent observational error. Time delays are then
-calculated in order from the arrival time at each image (\eqnref{tau}).
+calculated in order of the arrival time at each image (\eqnref{tau}).
 
@@
 \end{equation} 
-Typically, this results in a rejection rate of XXX\%.
+\hilight{We are not rejecting any models. Shall we remove this section, or just rewrite it?}
+\hilight{Typically, this results in a rejection rate of XXX\%}.
 
@@
 profile \citep{1990ApJ...356..359H}.  The four combinations of profile indices
-are shown in \tabref{mock galaxy params}. {\bf JR. Need to add explanation of
+are shown in \tabref{mock galaxy params}. \hilight{JR. Need to add explanation of
 triaxial parameters here. Is the above density equation correct in fact?}
@@
   $(a_\star,a_\mathrm{DM})=(2,20)$\,kpc. $\Rmap$ is the 2D projected radius
-used to generate the lens configurations.}
+used to generate the lens configurations. In the case of \mockBC, the profile is 
+sufficiently steep that the profile could be truncated at $\Rmap = 10$ kpc.}
 \label{mock galaxy params}
@@
 \includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
-\caption{{\bf JR. \sout{Cut the analytic profiles from this Figure. All fonts and labels should be larger.} Left panel should start at 0.7kpc.}
+\caption{
+Profiles of the four mock galaxies showing the stellar (dotted) and dark matter (dashed) components and the total (solid).
 \textbf{Left:} 
-Spherically averaged density profiles of the four mock galaxies showing the stellar (dotted), dark matter (dashed),
-and total (solid) densities. Notice that the stars in models Sdom/DMshallow and Sdom/DMcuspy contribute significantly to the central potential. 
+The spherically averaged density. The stars in models \mockBB{} and \mockBC{} contribute significantly to the central potential. 
 \textbf{Middle:} 
@@
 to simulate an extended source that will produces an arc-like image.
-\figref{arrival surfaces} shows the configuration for the extended quad, along
-with the other cases.
+\figref{arrival surfaces} shows the lens configurations for the \mockBC\
+galaxy.  The configurations for the other galaxies are similar. Within the
+names, the labels R1, R2, R3, refer to the redshift of the sources. We have
+chosen R1=1.72, R2=0.72, and R3=0.51 so that the radial distribution of the
+images is nearly equal.
 
@@
 \includegraphics[width=0.85\textwidth]{BCarrival_surfaces}
-\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
-the central image is shown, although not all tests include it. The central image belongs
-to only one set of images to avoid overconstraining the models. Similar colors group
-images that share a common source. In the case of the extended image systems the source
-is at the same redshift, while the redshift is varied between the systems in the 
-ZConstrast cases. Grey circles are a visual aid to help determine radial separation
-between images. The axes are measure in arcseconds.}
+\caption{The lens configurations for the six test cases using the \mockBC{}
+mock galaxy. The other mock galaxies produce similar results. Here, the central
+image is shown, although not all tests include it. The naming convention
+indicates the redshift of the sources with R1=1.72, R2=0.72, and R3=0.51.  The
+central image belongs to only to the R1 source to avoid overconstraining the
+models. Image colors represent a common source. In the case of the extended
+sources the redshift is at R1, while the redshift is varied between the systems
+in the ZConstrast cases. Grey circles are a visual aid to help determine radial
+separation between images. The axes are measure in arcseconds.}
 \label{arrival surfaces}
@@
 
-Each of these configurations were modelled with and without time delays and
-with and without a central image, for a total of 24 test cases. (The central
-image is typically highly demagnified. For galaxy lenses it is very difficult
-to find since it lies along the sight line to the bright lensing galaxy; in
-clusters, however, such images have been seen (CITES)). We assumed for all our
-tests that the lensing mass was radially symmetric (Prior vi):
-For our mock data, this is known to be
-true; it is most often the case with real galaxies, unless there is an obvious
-observed asymmetry. The central pixel was refined into a further 25 pixels to
-capture any steep rise in the profile.  Two of the four mock galaxies have a
-steeply rising inner profile. {\bf JR.  What happens if we don't assume this
-symmetry? We ought to add an appendix showing this for one example case.}
+Each of these configurations were modelled with and without time delays, with
+and without a central image, and with and without the stellar mass as a lower
+bound, for a total of 48 test cases. (The central image is typically highly
+demagnified. For galaxy lenses it is very difficult to find since it lies along
+the sight line to the bright lensing galaxy; in clusters, however, such images
+have been seen \hilight{(CITES)}). We assumed for all our tests that the
+lensing mass was radially symmetric (Prior vi): For our mock data, this is
+known to be true; it is most often the case with real galaxies, unless there is
+an obvious observed asymmetry. The central pixel was refined into a further
+$5\times5$ pixels (three extra radial positions) to capture any steep rise in
+the profile.  Two of the four mock galaxies have a steeply rising inner
+profile. \hilight{JR.  What happens if we don't assume this symmetry? We ought
+to add an appendix showing this for one example case.}
 
@@
 the radial density profile. The error bars cover a $1\sigma$ range around the
-median. \sout{the full range of models generated by \Glass {\bf JR. Why do
-this? Surely 1 or 2 sigma errors make more sense? I've deleted the ``full
-ensemble'' results and kept the $1\sigma$ ones instead.}}. The true density
-profile from the mock data is also plotted for comparison. The vertical lines
-mark the radial position of the images. The final plot on the right is of the
-enclosed mass. As expected, the error bars are smallest in the region of the
-images where the most information about the lens is present. The dip in the
-profile at the end of the profile is due to the cut off in mass in the
-lensing map. This is of little importance, though, as there is no lensing
-information there.
+median.  The true density profile from the mock data is also plotted for
+comparison. The vertical lines mark the radial position of the images. The
+final plot on the right is of the enclosed mass. As expected, the error bars
+are smallest in the region of the images where the most information about the
+lens is present. The dip in the profile at the end of the profile is due to the
+cut off in mass in the lensing map. This is of little importance, though, as
+there is no lensing information there.
 
@@
 \caption{
-  \sout{{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} }
-A typical reconstructed lens. Here we present results for a single quad image lensed by the Sdom/DMcuspy mock galaxy.
+  \hilight{Larger fonts. Do we need both examples?}
+Two typical reconstructed lens. Here we present results for a single quad image lensed by the \mockBC{} (upper) and \mockAC{} (lower) mock galaxies.
 \textbf{Left:}
-The arrival time surface. 
+The ensemble average arrival time surface, with just the isocontours for the
+saddle points drawn. The central diamonds show the reconstructed source
+position across the entire ensemble.
 \textbf{Middle:}
@@
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
-\caption{ The mock data distribution for Sdom/DMcuspy on a coarse grid (left)
-  and a typical recovered ensemble average $\kappa$ distribution. The contours are
-  logarithmic values, where level 0 corresponds to the critical density.}
+\caption{ \textbf{Left:} The mock data distribution for \mockBC{} projected onto a coarse grid.
+  \textbf{Right:} The recovered ensemble average $\kappa$ distribution for the single quad. The contours are
+  logarithmic values, where level 0 corresponds to the critical density. Contours below the critical density
+  are drawn with dashed lines.}
 \label{2d mass reconstruction}
@@
 %
-\begin{equation} \label{badness}
+\begin{equation} \label{ferror R}
   f_R = \frac {\sum_i \left|M_p(i) - \tilde M_p(i)\right| } {\sum \tilde M_p(i)}
@@
 %
-\begin{equation} \label{badness}
+\begin{equation} \label{ferror theta}
 f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum \tilde M(\vec\theta)}
@@
 \includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
-\caption{The main results showing the quality of model recovery. Each panel corresponds to 
-the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
+\caption{\hilight{Add names to plots}. Our main results showing the quality of model recovery \eqnrefp{ferror R} for all our test cases. 
+Within
 each panel are six groups of results for each of six lens morphologies. Each morphology
-considered the presence of time delays (T/t) and a central image (M/m). The black markers are for tests
+considered the presence of time delays (T,t) and a central image (M,m). The black markers are for tests
 that did not include the stellar mass as a lower bound constraint, while the red markers
-indicate where the stellar mass has been given. Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
+indicate where the stellar mass has been included. Error bars show the $1\sigma$ interval of the model ensemble.}
 \label{main results}
@@
 \includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
-\caption{ {\bf JR. \sout{ This should be also with $1\sigma$ errors.} Also need to do this plot for Claudio's shape measure.} \sout{Pixel-wise $\chi$.}
-The fractional error for the pixel-wise recovery of all models.
-The colors and labels are the same as in \figref{main results}.
-Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
+\caption{\hilight{Add names to plots.} Similar to \figref{main results}, we show here the fractional error
+for the pixel-wise recovery \eqnrefp{ferror theta} of all models. The colors and labels are the same
+as before. Error bars show the $1\sigma$ interval of the model ensemble.}
 \label{main results pixel-wise}
@@
 \plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}
-\caption{ The two plots in the left most column show sample distributions of
+\caption{ \hilight{Larger labels.} The two plots in the left most column show sample distributions of
   $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
-  The upper (poor) plot is from the DMdom/DMshallow galaxy, while the lower (good) plot is
-  from the Sdom/DMcuspy galaxy. The black vertical lines mark the $1\sigma$
+  The upper (poor) plot is from the \mockAA{} galaxy, while the lower (good) plot is
+  from the \mockBC{} galaxy. The black vertical lines mark the $2\sigma$
   region and the vertical blue line is the value of $s$ for the corresponding
@@
 \begin{figure*}
-  \includegraphics[width=0.33\textwidth]{AAferror_shape-1sig.pdf} \hspace{2cm}
-\includegraphics[width=0.33\textwidth]{BBferror_shape-1sig.pdf}\\
-\includegraphics[width=0.33\textwidth]{ACferror_shape-1sig.pdf}\hspace{2cm}
-\includegraphics[width=0.33\textwidth]{BCferror_shape-1sig.pdf}
-\caption{ The remain four plots are similar to those in \figref{main
-  results pixel-wise} and show the fractional error of $s$ over all the models,
-with respect to the mock galaxies.}
-
+\includegraphics[width=0.49\textwidth]{AAferror_shape-1sig.pdf}
+\includegraphics[width=0.49\textwidth]{BBferror_shape-1sig.pdf}\\
+\includegraphics[width=0.49\textwidth]{ACferror_shape-1sig.pdf}
+\includegraphics[width=0.49\textwidth]{BCferror_shape-1sig.pdf}
+\caption{Here we demonstrate our ability to recover the shape of the lensing mass. The shape ratio
+$\lambda_1/\lambda_2$ is measured from the principal components $\lambda_1, \lambda_2$ of the mass up to the outermost image.
+We plot the distribution of fractional error compared with the shape of the mock galaxies \eqnref{ferror shape}.}
 \label{shape results}
@@
 very little constraint on the mass distribution. This is particularly evident in
-galaxies AC and BC where the mass profile is steepest and the reconstruction of
+galaxies \mockAC{} and \mockBC{} where the mass profile is steepest and the reconstruction of
 the double is poorest. However, the addition of an arc is sufficient to correct
@@
 
+\hilight{Write about the shape plot and how we measured shape.}
+
 \begin{figure*}
-\includegraphics[width=0.33\textwidth]{BC_beta.pdf}
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_Tms_sigp-1.pdf}
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS_sigp-2.pdf}
-\caption{
-  Estimated projected radially averaged velocity dispersion (\eqnref{eqn:sphericaljeans}) $\sigma_p$ for two Sdom/DMcuspy models ZContrastR1R3
-  (left) and QuadR1a (right) assuming an anisotropy $\beta=0$ (blue, solid) and $\beta=1$
-  (blue, dashed).  Also shown are the equivalent curves for the mock data after
-  running it through the deprojection routines (grey). The solid black line is
-  the actual cylindrically averaged velocity dispersion of the original mock particle data.
-  The stellar half mass radius (yellow) Einstein
-radius (black) are marked by vertical lines. For this configuration, these two
-radii are well-separated.}
+\includegraphics[width=0.33\textwidth]{BC_beta.pdf}
+\caption{ \hilight{Larger fonts.} Estimated projected radially averaged velocity dispersion $\sigma_p$
+\eqnrefp{eqn:sphericaljeans} for two \mockBC{} models ZContrastR1R3
+(\textbf{left}) and QuadR1a (\textbf{middle}) assuming an anisotropy $\beta=0$
+(blue, solid) and $\beta=1$ (blue, dashed).  The equivalent
+curves are also shown for the projected mock data after using the same analysis routines
+(purple). The solid black line is the actual cylindrically averaged velocity
+dispersion of the original mock particle data.  The stellar half mass radius
+(yellow) Einstein radius (black) are marked by vertical lines. For this
+configuration, these two radii are well-separated. The actual variation in $\beta(r)$ is show also shown (\textbf{right}).}
+
   \label{fig:sigp} \end{figure*}
@@
 
+\hilight{This paragraph should go.}
 We now consider formally accepting/rejecting models from the full ensemble. We
 consider two regimes of interest: a model with a double where the mass profile
-is poorly constrained (XXX), and a model where the mass profile is very well
-constrained by the lens data (YYY). In the former case, we use
+is poorly constrained \hilight{(XXX)}, and a model where the mass profile is very well
+constrained by the lens data \hilight{(YYY)}. In the former case, we use
 $\overline{\sigma}(2 r_{1/2})$ to probe the mass independently of $\beta(r)$.
@@
 \plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
-\caption{(left) Test for predicted time delay convergence as $\Rmap$ changes.
-$\Rpix=45$. After about $\Rmap=20$ most of the asymmetric mass is in the map.
-(right) Test for predicted image position $\theta$ convergence as $\Rpix$
-changes. $\Rmap=20$ arcsec.}
+\caption{\textbf{Left:} Test for convergence of the predicted time delay as $\Rmap$ is increased and
+$\Rpix=45$ is held constant. After about $\Rmap=20$ most of the asymmetric mass is in the map.
+\textbf{Right:} Test for convergence of the predicted image positions $\theta$ as $\Rpix$
+changes and $\Rmap=20$ arcsec is held constant.}
 \label{raytracing convergence tests}
@@
 \section{Pixel resolution convergence test}
-{\bf JR. Need to add an appendix showing convergence with increasing Pixrad.}
+\hilight{JR. Need to add an appendix showing convergence with increasing Pixrad.}
 

### 2014-01-22 limits/ms.tex
eqnref -> eqnrefp in appropriate places.

@@
 as a set of discrete grid cells or pixels $\kappa_i$ and rewrite the potential
-(\eqnref{lensing potential}) as
+\eqnrefp{lensing potential} as
 %
@@
 error is below the equivalent observational error. Time delays are then
-calculated in order of the arrival time at each image (\eqnref{tau}).
+calculated in order of the arrival time at each image \eqnrefp{tau}.
 
@@
 writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the
-dark matter and stellar mass components in the potential (\eqnref{discrete
-potential}). Since each $\kappa_{s,n}$ is just a constant we do not add new,
+dark matter and stellar mass components in the potential \eqnrefp{discrete
+potential}. Since each $\kappa_{s,n}$ is just a constant we do not add new,
 separate equations for each pixel.
@@
 delays and stellar mass (left), and the mean projected velocity dispersion
-(\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging
+\eqnrefp{eqn:virialaverage} as a function of the upper limit of the averaging
 integral (the aperture size), $a_p$ (right). In both cases, we calculate curves

### 2014-01-23 limits/ms.tex
Added shape paragraph and short conclusion. Acknowledgments.

@@
 \begin{abstract}
-We use a new non-parametric gravitational modelling tool---\Glass---to determine what quality of data (strong lensing, stellar kinematics, and/or stellar masses) are required to measure the circularly averaged mass profile of a lens and its shape.
-\Glass\ uses an under-constrained adaptive grid of mass pixels to model the lens, searching through thousands of models to marginalise over model uncertainties.
-Our key findings are as follows: (i) for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy; (ii) a single quad with time delays also performs well, giving a good recovery of both the mass profile and its shape; (iii) stellar masses -- for lenses where the stars dominate the central potential -- can also break the steepness degeneracy, giving a recovery almost as good as having time delay data or multiple source redshifts; (iv) stellar kinematics are similarly powerful if the data extend beyond the half light radius of the stars $r \gg r_{1/2}$ (required to integrate out the effect of the unknown velocity anisotropy, $\beta(r)$); and (v) if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right.
-Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to constrain cosmological models.
-We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
+We use a new non-parametric gravitational modelling tool---\Glass---to
+determine what quality of data (strong lensing, stellar kinematics, and/or
+stellar masses) are required to measure the circularly averaged mass profile of
+a lens and its shape. \Glass\ uses an under-constrained adaptive grid of mass
+pixels to model the lens, searching through thousands of models to marginalise
+over model uncertainties. Our key findings are as follows: (i) for pure lens
+data, multiple sources with wide redshift separation give the strongest
+constraints as this breaks the well-known mass-sheet or steepness degeneracy;
+(ii) a single quad with time delays also performs well, giving a good recovery
+of both the mass profile and its shape; (iii) stellar masses -- for lenses
+where the stars dominate the central potential -- can also break the steepness
+degeneracy, giving a recovery almost as good as having time delay data or
+multiple source redshifts; (iv) stellar kinematics are similarly powerful if
+the data extend beyond the half light radius of the stars $r \gg r_{1/2}$
+(required to integrate out the effect of the unknown velocity anisotropy,
+$\beta(r)$); and (v) if the lensing data already probe the mass profile over
+the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe
+$\beta(r)$ -- an interesting dynamic quantity in its own right. Where
+information on the mass distribution from lensing and other probes becomes
+redundant, this opens up the possibility of using strong lensing to constrain
+cosmological models. We will study this, and present the first results from
+\Glass\ applied to real data, in forthcoming papers.
 \end{abstract}
@@
 where the stellar potential is a known constant of the form \eqnref{discrete
-potential}, e.g., $\kappa_n = \kappa_\mathrm{DM} + \kappa_s$ for a two-component model.
+potential}, e.g., $\kappa_n = \kappa_{\mathrm{dm},n} + \kappa_{s,n}$ for a two-component model.
 
@@
 \end{eqnarray} 
-This de-projection algorithm was tested on triaxial figures in \citet{2006ApJ...652L...5S}.
-They found that for triaxialities typical of our current cosmology, the method works extremely well unless the triaxial figure is projected directly along the line of sight such that we see the galaxy or galaxy cluster `down the barrel'.
-Such a situation is unlikely, but in any case avoidable since the resultant figure appears spherical in projection.
-This leads to the seemingly counter-intuitive result that the kinematic constraints -- that rely on the above de-projection -- are most secure for systems that do not appear spherical in projection (unless independent data can confirm the three dimensional shape is indeed very round).
-
-We use the deprojected mass to numerically solve equation \ref{eqn:sphericaljeans} for constant $\beta(r)$, assuming either $\beta(r) = 1$ or $\beta(r) = 0$ at all radii to bracket the two extremum situations.
-Where the data are good enough, these two may be distinguished giving dynamical information about $\beta(r)$.
-In more typical situations, however, we seek to simply marginalise over the effect of $\beta(r)$, using the stellar kinematics as a robust measure of $M(r_{1/2})$ (see \S\ref{sec:kinematics}).
+This de-projection algorithm was tested on triaxial figures in
+\citet{2006ApJ...652L...5S}. They found that for triaxialities typical of our
+current cosmology, the method works extremely well unless the triaxial figure
+is projected directly along the line of sight such that we see the galaxy or
+galaxy cluster `down the barrel'. Such a situation is unlikely, but in any case
+avoidable since the resultant figure appears spherical in projection. This
+leads to the seemingly counter-intuitive result that the kinematic constraints
+-- that rely on the above de-projection -- are most secure for systems that do
+not appear spherical in projection (unless independent data can confirm the
+three dimensional shape is indeed very round).
+
+We use the deprojected mass to numerically solve equation
+\ref{eqn:sphericaljeans} for constant $\beta(r)$, assuming either $\beta(r) =
+1$ or $\beta(r) = 0$ at all radii to bracket the two extremum situations. Where
+the data are good enough, these two may be distinguished giving dynamical
+information about $\beta(r)$. In more typical situations, however, we seek to
+simply marginalise over the effect of $\beta(r)$, using the stellar kinematics
+as a robust measure of $M(r_{1/2})$ (see \S\ref{sec:kinematics}).
 
@@
 
-We now present a study of four mock galaxies with known analytic forms.
-These are used to verify that \Glass\ is able to correctly recover the mass profile, and -- more importantly -- to determine what type and quality of data best constrain the mass profile and shape of a lens.
+We now present a study of four mock galaxies with known analytic forms. These
+are used to verify that \Glass\ is able to correctly recover the mass profile,
+and -- more importantly -- to determine what type and quality of data best
+constrain the mass profile and shape of a lens.
 
@@
 \begin{equation} \label{ferror R}
-  f_R = \frac {\sum_i \left|M_p(i) - \tilde M_p(i)\right| } {\sum \tilde M_p(i)}
-\end{equation}
-%
-where $M_p$ is the mass in a radial bin and $\tilde M_p$ is the mass from the mock galaxy.
+  f_R = \frac {\sum_i \left|M(i) - \tilde M(i)\right| } {\sum \tilde M(i)}
+\end{equation}
+%
+where $M$ is the mass in bin $i$ and $\tilde M$ is the mass from the mock galaxy.
 In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
@@
 \begin{equation} \label{ferror theta}
-f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum \tilde M(\vec\theta)}
+f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum_{\vec\theta} \tilde M(\vec\theta)}
 \end{equation}
@@
 
+With both $f_R$ and $f_\theta$ we only consider mass up to one radial
+position passed the outermost image, since there is no longer any lensing
+information beyond that point.
+
+The abundance of strong lensing data increases from left to right within each
+plot. As a result, there is a general trend for the reconstruction quality to
+increase (and for $f$ to decrease). By adding more measurable information to
+each configuration the quality can also be affected. When both time delays and
+a central image are present the quality is highest. A double is known to
+provide very little constraint on the mass distribution. This is particularly
+evident in galaxies \mockAC{} and \mockBC{} where the mass profile is steepest
+and the reconstruction of the double is poorest. However, the addition of an
+arc from the extended source is sufficient to correct this. \hilight{Mention the saturation of the two panels.}
+
+We can also directly measure the recoverability of the shape of the mass
+distribution by computing the eigenvalues of the inertia tensor. We define our
+shape by the ratio of these eigenvalues $s=\lambda_1/\lambda_2$, where the
+$\lambda_1$ is always the largest value. Again, we only consider mass up to one
+radial position passed the outermost image and compute our the fractional error
+%
+\begin{equation} \label{ferror shape}
+  f_\mathrm{shape} = \left|s - \tilde s\right|  / \tilde s
+\end{equation}
+%
+where $\tilde s$ is the shape of the mock galaxy. The distribution of $f_\mathrm{shape}$
+for each mock galaxy and each test case is shown in \figref{shape results}.
+
 \begin{figure}[h]
@@
 
-The abundance of strong lensing data increases from left to right within each plot. As
-a result, there is a general trend for the reconstruction quality to increase
-(and for $f$ to decrease). By adding more measurable information to each
-configuration the quality can also be affected. When both time delays and a
-central image are present the quality is highest. A double is known to provide
-very little constraint on the mass distribution. This is particularly evident in
-galaxies \mockAC{} and \mockBC{} where the mass profile is steepest and the reconstruction of
-the double is poorest. However, the addition of an arc is sufficient to correct
-this.
-
-\hilight{Write about the shape plot and how we measured shape.}
-
 \begin{figure*}
@@
 \caption{ \hilight{Larger fonts.} Estimated projected radially averaged velocity dispersion $\sigma_p$
-\eqnrefp{eqn:sphericaljeans} for two \mockBC{} models ZContrastR1R3
-(\textbf{left}) and QuadR1a (\textbf{middle}) assuming an anisotropy $\beta=0$
+\eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC{} mock galaxy without stellar mass
+(\textbf{left}) and with stellar mass (\textbf{middle}) assuming an anisotropy $\beta=0$
 (blue, solid) and $\beta=1$ (blue, dashed).  The equivalent
@@
 
+\hilight{This is a bit overstated.}
 With the stellar mass lower bound, the improvement of the reconstruction
-quality shown in \figref{main results} is quite dramatic for the
-steepest mock galaxies (AC and BC). This is because these models are dominated
+quality shown in \figref{main results} is quite dramatic for the doubles in the 
+steepest mock galaxies (\mockAC{} and \mockBC). This is because these models are dominated
 by stars in the inner region. By contrast, the other two galaxies -- where the stars contribute negligibly to the potential -- are unaffected.
@@
 To illustrate the power of stellar kinematic constraints, in
-\figref{sigma-beta}, we plot the projected velocity dispersion calculated for
-one model model (extracted from the full ensemble) of the BC Quad with time
-delays and stellar mass (left), and the mean projected velocity dispersion
-\eqnrefp{eqn:virialaverage} as a function of the upper limit of the averaging
-integral (the aperture size), $a_p$ (right). In both cases, we calculate curves
+\figref{fig:sigp}, we plot the projected velocity dispersion calculated for
+one model model (extracted from the full ensemble) of the \mockBC{} Quad with time
+delays and stellar mass (left), and the same but without stellar mass (right).
+In both cases, we calculate curves
 for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
-Over-plotted is the correct answer for the BC model (black). The stellar half
+Over-plotted is the correct answer for the \mockBC{} model (black). The stellar half
 mass radius (yellow) Einstein radius (black) are marked by vertical lines. For
@@
 
-\hilight{This paragraph should go.}
+\hilight{This paragraph should be removed.}
 We now consider formally accepting/rejecting models from the full ensemble. We
@@
 fit measure between the true and modelled $\sigma_p(R)$. We accept/reject
-models from the ensemble above. The results for $\beta$ are shown in Figure
-ZZZ.
+models from the ensemble above. The results for $\beta$ are shown in the right panel of
+\figref{fig:sigp}.
 
@@
 distribution at $r \sim r_{1/2}$, stellar kinematics provide valuable
-information about the velocity anisotropy of the stars, $\beta$ (see Figure
-ZZZ). Where the lens data poorly constrain the mass distribution at $r_{1/2}$,
+information about the velocity anisotropy of the stars, $\beta$ (see \figref{fig:sigp}). Where the lens data poorly constrain the mass distribution at $r_{1/2}$,
 we may `integrate out' the effect of unknown $\beta$ to obtain a robust measure
@@
 
-Various action items.
+We have introduced a new gravitational len modelling tool---\Glass---and used
+it to test the recovery of the mass profile and shape of mock strong lensing
+galaxies. We have also shown that with the addition of stellar mass
+constraints, one can better constrain the inner profile of galaxies,
+particularly in the case of doubles. Furthermore, by we have demonstrated our
+sensitivity to the estimates of the velocity dispersion. Improved measurements
+of the dispersion and, in particular, the velocity anisotropy could be used to
+greatly enhance our lens models.
+
+\section{Acknowledgments}\label{sec:Acknowledgements}
+
+The authors would like to thank Sarah Bryan and Walter Dehnen for creating the
+particle distributions for the mock galaxies. This work has been partially
+funded by \hilight{if we want..}
 

### 2014-01-23 limits/ms.tex
Updated figure 3 with AA plots.
Updated text.
Added more plots in fig 3. Added galaxy names to plots.

@@
 
-\newcommand{\mockAA}{{\sc Ssteep-DMshallow}}
-\newcommand{\mockAC}{{\sc Ssteep-DMsteep}}
-\newcommand{\mockBB}{{\sc Ssteep-DMshallow}}
-\newcommand{\mockBC}{{\sc Ssteep-DMsteep}}
+\newcommand{\mockAA}{{\sc star1.0-dmCore}}
+\newcommand{\mockAC}{{\sc star1.0-dmCusp}}
+\newcommand{\mockBB}{{\sc star1.5-dmCore}}
+\newcommand{\mockBC}{{\sc star1.5-dmCusp}}
 
@@
 \begin{figure*}
-  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-a.pdf}\hspace{-2em}
-  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-b.pdf}\hspace{-2em}
-  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-c.pdf}\\\vspace{-1em}
-  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-a.pdf}\hspace{-2em}
-  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-b.pdf}\hspace{-2em}
-  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-c.pdf}
+  \plotthree{BCExtendedDoubleR1_tms-a.pdf} {BCExtendedDoubleR1_tms-b.pdf} {BCExtendedDoubleR1_tms-c.pdf}
+  \plotthree{BCExtendedDoubleR1_tmS-a-1.pdf} {BCExtendedDoubleR1_tmS-b-1.pdf} {BCExtendedDoubleR1_tmS-c-1.pdf}
+  \plotthree{BCQuadR1a_Tms-a.pdf} {BCQuadR1a_Tms-b.pdf} {BCQuadR1a_Tms-c.pdf}
+  \plotthree{AAQuadR1a_Tms-a.pdf} {AAQuadR1a_Tms-b.pdf} {AAQuadR1a_Tms-c.pdf}
 \caption{
@@
 The black curve comes from the original mass model used to create the lens.
-The green vertical lines mark the radial positions of the images. The higher
+The vertical lines mark the radial positions of the images. The higher
 resolution feature of \Glass\ has been used on the central pixel allowing the
@@
 \includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
-\caption{\hilight{Add names to plots}. Our main results showing the quality of model recovery \eqnrefp{ferror R} for all our test cases. 
+\caption{Our main results showing the quality of model recovery \eqnrefp{ferror R} for all our test cases. 
 Within
@@
 \includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
-\caption{\hilight{Add names to plots.} Similar to \figref{main results}, we show here the fractional error
+\caption{Similar to \figref{main results}, we show here the fractional error
 for the pixel-wise recovery \eqnrefp{ferror theta} of all models. The colors and labels are the same
@@
 
-\begin{figure}[h]
+\begin{figure}
 \plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}

### 2014-01-26 limits/ms.tex
Fixed figure 7.
Brought over Justin's changes.

@@
 degeneracy, giving a recovery almost as good as having time delay data or
-multiple source redshifts; (iv) stellar kinematics are similarly powerful if
-the data extend beyond the half light radius of the stars $r \gg r_{1/2}$
-(required to integrate out the effect of the unknown velocity anisotropy,
-$\beta(r)$); and (v) if the lensing data already probe the mass profile over
-the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe
-$\beta(r)$ -- an interesting dynamic quantity in its own right. Where
-information on the mass distribution from lensing and other probes becomes
+multiple source redshifts; (iv) stellar kinematics provide a robust measure of the mass at the half light radius of the stars $r \gg r_{1/2}$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v) if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy
+$\beta(r)$ -- an interesting quantity in its own right. Where
+information on the mass distribution from lensing and/or other probes becomes
 redundant, this opens up the possibility of using strong lensing to constrain
@@
 
-Strong gravitational lenses are rare.  The reason is that the line of
-sight to a light source in the universe rarely goes through a region
-such that the projected density in its sky neighbourhood exceeds the
-critical density to produce multiple images.  To date, some $\sim400$
-strong lenses are known,\footnote{See {\tt http://www.masterlens.org}
-  for a catalogue.}  but this number is expected to increase to
-several thousand over the next ten years.  The optimism derives from
-new and upcoming surveys, both
+Strong gravitational lenses are rare.
+Since the discovery of the first lens Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to date\footnote{See e.g.
+{\tt http://www.masterlens.org} for a catalogue.}.
+However, this number is expected to increase to
+several thousand over the next ten years as new surveys, both
 ground-based\footnote{http://pan-starrs.ifa.hawaii.edu}$^{\rm,}$\footnote{http://www.darkenergysurvey.org}
-and spacecraft,\footnote{http://www.euclid-ec.org} together with a
+and space-based\footnote{http://www.euclid-ec.org} -- together with a
 community of citizen-science volunteers examining the image data for
-candidates.\footnote{http://spacewarps.org}
-
-Since lensing depends only on gravity, strong lenses are a rather
-unique window on dark matter, and indirectly on the cosmological model
-as well, and hence the thousands of to-be-discovered lenses are
-eagerly awaited \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}.
-Extracting results from lensing, however, will require modelling, and
-it is towards that goal that the present work is directed.
-
-To see why lens modelling is of crucial importance, let us recall the
+candidates\footnote{{\tt http://spacewarps.org}} -- come online.
+
+% since distant light source in the universe rarely goes through a region such that the projected density in its sky neighbourhood exceeds the critical density to produce multiple images.
+
+Since lensing depends only on gravity, strong lenses offer a
+unique window onto dark matter and cosmology \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}. However, 
+extracting dark matter properties or cosmological constraints from these lensing data will require sophisticated modelling.
+In particular, with an unprecedented data set imminent, it is prudent to look again at systematic errors in the lens models to determine what quality of data (in particular complementary data from stellar/gas kinematics, lens time delays and/or stellar mass constraints) are required to address problems of interest.
+It is towards that goal that this present work is directed.
+
+To see why lens modelling details are of crucial importance, let us recall the
 essential quantities that appear in lensing.  First we have the
-distances: let $D_L$, $D_S$, $D_{LS}$ be the angular-diameter
-distances to the lens, source, and from lens to source; they are all
-strictly $\propto c/H_0$.  Typically
+distances. Let $D_L$, $D_S$, $D_{LS}$ be the angular-diameter
+distances to the lens, source, and from lens to source; these are all proportional to $c/H_0$ (where $c$ is the speed of light in vacuo, and $H_0$ the Hubble constant), with additional terms that depend on the particular choice of cosmology \citep[e.g.][]{1999coph.book.....P}.
+Typically:
 \begin{equation}
@@
 \end{equation}
+where the second relation follows from the fact that the light deflection angle is maximised when the lens is equidistant between the observer and the source \citep[e.g.][]{1992grle.book.....S}.
+
+GOT TO HERE.
+
 For multiple images the sky-projected density must exceed the critical
@@
 \begin{figure}
-\plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}
+\plottwo{AAExtendedDoubleR1_TmS-shape-hist.pdf}{BCZContrastR1R3_TmS-shape-hist.pdf}
 \caption{ \hilight{Larger labels.} The two plots in the left most column show sample distributions of

### 2014-01-26 limits/ms.tex
Improved font in some plots. Updated captions.

@@
 \usepackage{color} % Only necessary for hilight
-
-\def\newblock{\hskip .11em plus .33em minus .07em}
 
@@
 \\
-$^1$Exascale Research Computing Lab, Versailles Saint-Quentin-en-Yvelines University,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
-$^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
-$^3$Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland
+$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
+$^2$\hilight{Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom} \\
+$^3$\hilight{Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland}
 }
@@
 
-%(Linear constraints are applied simultaneously with the lens constraints; non-linear constraints are applied in post-processing, with models accepted or rejected based on their likelihood.) 
-%These are quantities of key interest for probing the dark matter distribution in galaxies and galaxy clusters to test galaxy formation models and cosmology.
-
-\section{Introduction}\label{sec:intro} %-----------------------------------------------------
+\section{Introduction}\label{sec:intro}
 
@@
 
-% since distant light source in the universe rarely goes through a region such that the projected density in its sky neighbourhood exceeds the critical density to produce multiple images.
-
 Since lensing depends only on gravity, strong lenses offer a
@@
 
-GOT TO HERE.
+\hilight{GOT TO HERE. }
 
@@
 distributions could reproduce the data.
-
-% Simple parametric models are usually robust on qualitative features,
-% but other aspects can be very model-dependent
-% \citep[cf.~][]{2003AJ....125.2769S}.  For example, for lensed
-% quasars, there may be several models all providing excellent fits to
-% the image data but disagreeing on the expected time delays, but they
-% almost always agree about the {\em order\/} of time delays. Thus, a
-% simple model provides valuable physical insight, but as data quality
-% improves and the questions we ask of these data become more refined,
-% it is important to re-assess the impact of our model assumptions.
-% The key advantages of non-parametric modelling are that we can: (i)
-% explore model degeneracies and marginalise over them; and (ii) we
-% can determine what type and quality of data are required to measure
-% parameters of interest.
 
@@
   as
+%
 \begin{equation}
@@
 \end{equation}
+%
   with the relation becoming exact for isothermal lenses.  The use of
@@
 The rather complicated dependence of lensing observables on the mass
-distribution $\kappa(\vec\theta)$ has an important consequence: very
-different mass distributions can result in similar observables.  This
-is the phenomenon of lensing degeneracies.  While the non-uniqueness
-of lens models noted by \cite{1981ApJ...244..736Y} already hinted at
-degeneracies, their existence was first derived by
-\cite{1985ApJ...289L...1F}.  The most important is the so-called
-mass-sheet degeneracy, which is that image positions remain invariant
-if the $D_S/D_{LS} - \kappa(\vec\theta)$ \hilight{ $\leftarrow$ What is meant by this? Can we just write $\tau(\vec\theta)$? }are each multiplied by an
-arbitrary constant.  This amounts to multiplying the arrival-time
-surface by a constant factor.  In fact there are infinitely many
-degeneracies \citep{2000AJ....120.1654S} because any transformation of
-the arrival-time surface away from the images has no effect on the
-lensing observables.  In particular, there are degeneracies that
-involve the shape of the mass distribution
-\citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies tend to
-be suppressed if there are sources at very different redshifts or
-`redshift contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S},
-because the presence of different factors of $D_S/D_{LS}$ in the image
-plane makes it more difficult to change the mass distribution and the
-arrival-time surface without affecting the lensing observables.  But
-degeneracies are still present with multiple source redshifts.
-\citep{2008MNRAS.386..307L}.
-
-% The only lensing observables from \eqnref{arrival time} are the
-% image positions. However, if the source object is variable then the
-% observed light curves of each image will be identical but shifted in
-% time due to the different photon path lengths.  The time difference
-% between identical portions of the light curves is called the time
-% delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
-% $\Delta t_{21}$ between two images $\vec\theta_1$ and
-% $\vec\theta_2$, where $\vec\theta_2$ arrives after $\vec\theta_1$,
-% is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L / \zeta$. If $\beta$
-% and $\kappa_\infty$ could be known exactly this would allow one to
-% precisely infer the angular diameter distance to the lens and thus
-% -- via a cosmological model -- the Hubble constant. However, the
-% source position is not observable and the density distribution is
-% highly degenerate.
-
-% \subsection{Degeneracies}\label{sec:degen}
-%
-% The trouble with solving the lens equation for the mass distribution is that the solutions are not unique.
-To see why, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens:
-%
-% \begin{equation}
-% \vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
-% \label{eqn:lens_equation_circ}
-% \end{equation}
-%
-% where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.
-
-% For on-axis sources (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$.
-Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distance.
-For fixed cosmology and in the most ideal situation, a single source splitting into images gives us only an enclosed mass.
-This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case \citep{1985ApJ...289L...1F,2000AJ....120.1654S}.
-Thus, to measure the mass profile of a lens, we require more information.
-This can come in the form of sources at different redshifts -- since each has its own Einstein radius, each constrains a different enclosed mass $M(<\theta_E')$.
-Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling \citep{2008MNRAS.383..857F}, stellar kinematics \citep{2002MNRAS.337L...6T}, or similar.
-However, even with further information, higher order degeneracies remain.
-\citet{2008MNRAS.386..307L} showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while \citep{2006ApJ...653..936S} find twisting/shape degeneracies that are sensitive to the time delays.
-Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits \citep[e.g.][]{1996ApJ...468...17B}.
-However, this {\it shear term} can be constrained by data \citep[e.g.][]{2002ApJ...578...25K}.
-In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens.
-We assume throughout that the shear is negligible.
-
-% {\bf Is ``Schneider's degeneracy" something new? Should we cite it here? -- {\tt http://adsabs.harvard.edu/abs/2013arXiv1306.4675S}}
+distribution $\kappa(\vec\theta)$ has an important consequence: very different
+mass distributions can result in similar observables.  This is the phenomenon
+of lensing degeneracies.  While the non-uniqueness of lens models noted by
+\cite{1981ApJ...244..736Y} already hinted at degeneracies, their existence was
+first derived by \cite{1985ApJ...289L...1F}.  The most important is the
+so-called mass-sheet degeneracy, which is that image positions remain invariant
+if the $D_S/D_{LS} - \kappa(\vec\theta)$ \hilight{ $\leftarrow$ What is meant
+by this? Can we just write $\tau(\vec\theta)$? }are each multiplied by an
+arbitrary constant.  This amounts to multiplying the arrival-time surface by a
+constant factor.  In fact there are infinitely many degeneracies
+\citep{2000AJ....120.1654S} because any transformation of the arrival-time
+surface away from the images has no effect on the lensing observables.  In
+particular, there are degeneracies that involve the shape of the mass
+distribution \citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies
+tend to be suppressed if there are sources at very different redshifts or
+`redshift contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because
+the presence of different factors of $D_S/D_{LS}$ in the image plane makes it
+more difficult to change the mass distribution and the arrival-time surface
+without affecting the lensing observables.  But degeneracies are still present
+with multiple source redshifts.  \citep{2008MNRAS.386..307L}.
 
@@
 
-Another useful constraint follows from the velocity of stars within the lensing galaxy. Assuming spherical symmetry, stars obey the projected Jeans equations \citep[e.g.][]{2008gady.book.....B}:
+Another useful constraint follows from the velocity of stars within the lensing
+galaxy. Assuming spherical symmetry, stars obey the projected Jeans equations
+\citep[e.g.][]{2008gady.book.....B}:
 
@@
 \end{equation} 
-where $a_p$ is the `aperture' over which the integral is performed.
-Ideally we should take $a_p \rightarrow \infty$, however this is not practical for real data where the surface brightness of the stars falls off rapidly with $a_p$.
-In practice, $a_p > 2r_{1/2}$, where $r_{1/2}$ is the half light radius of the stars, appears to be sufficient (see \S\ref{sec:results}).
-The above average produces a single robust measure of the mass $\overline{\sigma}$ that is independent of $\beta(r)$, provided that the stellar system is in a dynamic quasi-equilibrium that obeys the virial theorem \citep{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}.
-(Such an averaging procedure was first used in a combined lensing/stellar kinematic analysis in \citealt{2002MNRAS.337L...6T}.)
-
-We describe our numerical solution of \eqnref{eqn:sphericaljeans} in \S\ref{sec:glasskinematics} and present tests applied to mock data in \S\ref{sec:results}.
+where $a_p$ is the `aperture' over which the integral is performed. Ideally we
+should take $a_p \rightarrow \infty$, however this is not practical for real
+data where the surface brightness of the stars falls off rapidly with $a_p$. In
+practice, $a_p > 2r_{1/2}$, where $r_{1/2}$ is the half light radius of the
+stars, appears to be sufficient (see \S\ref{sec:results}). The above average
+produces a single robust measure of the mass $\overline{\sigma}$ that is
+independent of $\beta(r)$, provided that the stellar system is in a dynamic
+quasi-equilibrium that obeys the virial theorem
+\citep{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}. (Such an
+averaging procedure was first used in a combined lensing/stellar kinematic
+analysis in \citealt{2002MNRAS.337L...6T}.)
+
+We describe our numerical solution of \eqnref{eqn:sphericaljeans} in
+\S\ref{sec:glasskinematics} and present tests applied to mock data in
+\S\ref{sec:results}.
 
@@
 %
-\footnote{Currently hosted on GitHub: www.github.com/jpcoles/glass or through
-www.jpcoles.com/glass.}.
+\footnote{http://www.jpcoles.com.}.
 
@@
 multi-threaded allowing it to run efficiently on many-cored machines.
-
-%\Glass\ uses an adaptive grid of mass pixels
-%to model the lens, generating thousands of models to marginalise over
-%uncertainties. It shares some heritage with an earlier code, \PixeLens\
-%\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
-%important respects: 
-%\begin{enumerate} 
-%\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
-%\item it is built on a fully modular framework that can support different basis functions;
-%\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
-%\item the stellar mass (if known) can be applied as a prior; and
-%\item adaptive resolution can be used in regions of interest. 
-%\end{enumerate}
-%This new functionality allows us to include non-lensing data constraints. Linear constraints -- like the stellar
-%mass -- are applied simultaneously with the strong lensing constraints;
-%non-linear constraints are applied in a post-processing step, where models are
-%rejected using a likelihood analysis. This latter was prohibitively expensive
-%with \PixeLens\ as only up to $\sim$1000 models could be generated in a
-%reasonable time. With \Glass, we can routinely generate hundreds of thousands
-%of models such that we can afford to discard some if they are inconsistent with
-%independent data.
 
@@
 potential}, e.g., $\kappa_n = \kappa_{\mathrm{dm},n} + \kappa_{s,n}$ for a two-component model.
-
-%
-%\begin{equation}
-  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
-%\end{equation}
-%
 
@@
 
-\subsection{Lens configurations}\label{sec:lensconfig} %--------------------------------------------------------------
+\subsection{Lens configurations}\label{sec:lensconfig}
 
@@
 \caption{
-  \hilight{Larger fonts. Do we need both examples?}
-Two typical reconstructed lens. Here we present results for a single quad image lensed by the \mockBC{} (upper) and \mockAC{} (lower) mock galaxies.
+    Four reconstructed lenses. The first two rows consider the same mock
+    galaxy, \mockBC, for an extended double, and highlight the improved
+    constraints on the mass distribution when a lower bound is given by the
+    stellar mass. For the reconstruction, no time delays were assumed.  The
+    third row uses again the the \mockBC{} mock galaxy, but with time delays
+    for a single quad and no stellar mass. With the added information from the
+    quad, the outer regions of the lens are the image radii are better
+    constrained. Finally, the fourth row shows another case of a quad with time
+    delays, but using the \mockAA{} mock galaxy. This galaxy has a shallower
+    stellar density index, and a core in the dark matter. Due to the priors
+    used in \Glass, the modelling favors steep solutions without additional
+    information.
 \textbf{Left:}
-The ensemble average arrival time surface, with just the isocontours for the
+The ensemble average arrival time surface with just the isocontours for the
 saddle points drawn. The central diamonds show the reconstructed source
-position across the entire ensemble.
+position.
 \textbf{Middle:}
-The surface density. The magenta curve represents the dark matter component,
-the yellow curve the stellar component, and the blue curve is the sum of the two.
-The black curve comes from the original mass model used to create the lens.
+The surface density of the dark matter (magenta), the stars (yellow), and the total (blue).
+The original mass model used to create the lens is shown in black.
 The vertical lines mark the radial positions of the images. The higher
@@
 \textbf{Right:}
-The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range for DM+Stars (blue).}
+The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range of models for DM+Stars (blue).}
 \label{reconstruction}
@@
   \textbf{Right:} The recovered ensemble average $\kappa$ distribution for the single quad. The contours are
-  logarithmic values, where level 0 corresponds to the critical density. Contours below the critical density
+  logarithmic base 10 values, where level 0 corresponds to the critical density. Contours below the critical density
   are drawn with dashed lines.}
@@
 \end{equation}
-%
-%\begin{equation}
-%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
-%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
-%\end{equation}
-%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.
 
@@
 \plottwo{AAExtendedDoubleR1_TmS-shape-hist.pdf}{BCZContrastR1R3_TmS-shape-hist.pdf}
-\caption{ \hilight{Larger labels.} The two plots in the left most column show sample distributions of
+\caption{The two plots in the left most column show sample distributions of
   $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
@@
 \includegraphics[width=0.33\textwidth]{BC_beta.pdf}
-\caption{ \hilight{Larger fonts.} Estimated projected radially averaged velocity dispersion $\sigma_p$
+\caption{ Estimated projected radially averaged velocity dispersion $\sigma_p$
 \eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC{} mock galaxy without stellar mass
@@
 
-The stellar mass distribution gives a lower bound on the total mass.
-Where the stars dominate the central potential, it can provide a powerful constraint extra to the strong lensing data.
-We took the stellar mass directly from
-the generated galaxies and projected the particles onto the pixels. \Glass\
-also offers an option to interpolate any map of stellar mass (e.g., from an
+The stellar mass distribution gives a lower bound on the total mass. Where the
+stars dominate the central potential, it can provide a powerful constraint
+extra to the strong lensing data. We took the stellar mass directly from the
+generated galaxies and projected the particles onto the pixels. \Glass\ also
+offers an option to interpolate any map of stellar mass (e.g., from an
 observation) onto the pixels. The linear constraint is added to \Glass\ by
-writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the
-dark matter and stellar mass components in the potential \eqnrefp{discrete
-potential}. Since each $\kappa_{s,n}$ is just a constant we do not add new,
-separate equations for each pixel.
-Although we assume a perfect recovery of the stellar mass here, it is straightforward to add errors as the stellar mass constraint remains linear: $\kappa_n = \kappa_{dm,n} + \epsilon \kappa_{s,n}$, where $\epsilon \sim 1$ is an additional error parameter.
+writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the dark matter
+and stellar mass components in the potential \eqnrefp{discrete potential}.
+Since each $\kappa_{s,n}$ is just a constant we do not add new, separate
+equations for each pixel. Although we assume a perfect recovery of the stellar
+mass here, it is straightforward to add errors as the stellar mass constraint
+remains linear: $\kappa_n = \kappa_{dm,n} + \epsilon \kappa_{s,n}$, where
+$\epsilon \sim 1$ is an additional error parameter.
 
@@
 quality shown in \figref{main results} is quite dramatic for the doubles in the
-steepest mock galaxies (\mockAC{} and \mockBC). This is because these models are dominated
-by stars in the inner region. By contrast, the other two galaxies -- where the stars contribute negligibly to the potential -- are unaffected.
+steepest mock galaxies (\mockAC{} and \mockBC). This is because these models
+are dominated by stars in the inner region. By contrast, the other two galaxies
+---where the stars contribute negligibly to the potential---are unaffected.
 
@@
 distribution at $r \sim r_{1/2}$, stellar kinematics provide valuable
-information about the velocity anisotropy of the stars, $\beta$ (see \figref{fig:sigp}). Where the lens data poorly constrain the mass distribution at $r_{1/2}$,
-we may `integrate out' the effect of unknown $\beta$ to obtain a robust measure
-of $M(r_{1/2})$ from the stellar kinematics. This latter is robust to both
-uncertainties in $\beta(r)$ and to our assumption of spherical symmetry in the
-kinematic models \citep{2012ApJ...754L..39A}. Finally, we note that there is a
-third interesting case. If the lens models well-constrain $M(r_{1/2})$ and
-stellar kinematics are available, then these can be used to probe cosmological
-models (see \S\ref{sec:theory}). We explore this in more detail in a separate
-publication.
-
-%\begin{figure*}
-%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
-%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
-%\caption{{\bf Left:} 
-%The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
-%limit of the averaging integral (the aperture size), $a_p$
-%  for two Sdom/DMcuspy models ZContrastR1R3
-%  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
-%  (blue, dashed).  Also shown are the equivalent curves for the mock data after
-%  running it through the deprojection routines (grey). 
-%\sout{Over-plotted is the correct answer for the BC model (black)
-%  {\bf JR. Jonathan to add}.} 
-%  The stellar half mass radius (yellow) Einstein
-%radius (black) are marked by vertical lines. For this configuration, these two
-%radii are well-separated.}
-%\label{sigma-beta}
-%\end{figure*}
-
-%\subsection{Velocity dispersions}
-%
-%\begin{itemize}
-%\item Can they predict radial profiles?
-%\item Can we constrain lensing models from predicted velocity dispersions?
-%\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
-%\item Vary $z$ of the halo, possibly orientation.
-%\item Should be able to recover $\gamma$ very well.
-%\item Use G1. Show problems with recovering $\gamma$.
-%\end{itemize}
-
-%\subsection{With/without time delays and central image} %--------------------------------------------------------------
-
-%We also considered the effect of having time delays or a central image. The
-%central image is usually highly demagnified and obscured by the lensing galaxy,
-%but in clusters the central image is observable. In this case we can imagine
-%the galaxies to be clusters since the problem is scale-free. A recontruction of
-%AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
-%which combination of time delays (T) and central image (M) was used. An
-%uppercase letter indicates the feature is turned on, and a lowercase letter
-%that it is turned off.
+information about the velocity anisotropy of the stars, $\beta$ (see
+\figref{fig:sigp}). Where the lens data poorly constrain the mass distribution
+at $r_{1/2}$, we may `integrate out' the effect of unknown $\beta$ to obtain a
+robust measure of $M(r_{1/2})$ from the stellar kinematics. This latter is
+robust to both uncertainties in $\beta(r)$ and to our assumption of spherical
+symmetry in the kinematic models \citep{2012ApJ...754L..39A}. Finally, we note
+that there is a third interesting case. If the lens models well-constrain
+$M(r_{1/2})$ and stellar kinematics are available, then these can be used to
+probe cosmological models (see \S\ref{sec:theory}). We explore this in more
+detail in a separate publication.
 
@@
 
-\section{Raytracing convergence test}
-Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
-$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
-the change in time delays as we increase $\Rmap$.  The image system is a quad
-with the central maximum image. When the projected mass begins to fall off the
-time delays stabilize. In the right panel we see the effect of changing the
-resolution of the map.  Increasing the resolution allows for more accurate
-placement of the images and after about $\Rpix=40$ the image positions change
-by less than 0.04 arcsec. The one image that continues to change is near to a
-caustic.
-
-\begin{figure}
-\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
-\caption{\textbf{Left:} Test for convergence of the predicted time delay as $\Rmap$ is increased and
-$\Rpix=45$ is held constant. After about $\Rmap=20$ most of the asymmetric mass is in the map.
-\textbf{Right:} Test for convergence of the predicted image positions $\theta$ as $\Rpix$
-changes and $\Rmap=20$ arcsec is held constant.}
-\label{raytracing convergence tests}
-\end{figure}
+%\section{Raytracing convergence test}
+%Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
+%$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
+%the change in time delays as we increase $\Rmap$.  The image system is a quad
+%with the central maximum image. When the projected mass begins to fall off the
+%time delays stabilize. In the right panel we see the effect of changing the
+%resolution of the map.  Increasing the resolution allows for more accurate
+%placement of the images and after about $\Rpix=40$ the image positions change
+%by less than 0.04 arcsec. The one image that continues to change is near to a
+%caustic.  
+%
+%\begin{figure}
+%\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
+%\caption{\textbf{Left:} Test for convergence of the predicted time delay as $\Rmap$ is increased and
+%$\Rpix=45$ is held constant. After about $\Rmap=20$ most of the asymmetric mass is in the map.
+%\textbf{Right:} Test for convergence of the predicted image positions $\theta$ as $\Rpix$
+%changes and $\Rmap=20$ arcsec is held constant.}
+%\label{raytracing convergence tests}
+%\end{figure}
 

### 2014-01-28 limits/ms.tex
Justin Changes

@@
 \newcommand{\mockBC}{{\sc star1.5-dmCusp}}
+
+%For deprojection algorithm: 
+\def\cth{\cos\theta}
+\def\sth{\sin\theta}
+\def\dth{{\rm d}\theta}
 
@@
 \begin{abstract}
-We use a new non-parametric gravitational modelling tool---\Glass---to
+We use a new non-parametric gravitational modelling tool --- \Glass\ --- to
 determine what quality of data (strong lensing, stellar kinematics, and/or
@@
 degeneracy, giving a recovery almost as good as having time delay data or
-multiple source redshifts; (iv) stellar kinematics provide a robust measure of the mass at the half light radius of the stars $r \gg r_{1/2}$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v) if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy
-$\beta(r)$ -- an interesting quantity in its own right. Where
+multiple source redshifts; (iv) stellar kinematics provide a robust measure of the mass at the half light radius of the stars $r_{1/2}$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v) if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy
+$\beta$ -- an interesting quantity in its own right. Where
 information on the mass distribution from lensing and/or other probes becomes
@@
 \end{equation}
-where the second relation follows from the fact that the light deflection angle is maximised when the lens is equidistant between the observer and the source \citep[e.g.][]{1992grle.book.....S}.
-
-\hilight{GOT TO HERE. }
-
-For multiple images the sky-projected density must exceed the critical
-density of $D_S/D_{LS}$ times
-\begin{equation}
-\Sigma_L = \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
+
+For multiple images, the sky-projected density must exceed the critical
+density \citep[e.g.][]{1992grle.book.....S}:
+
+\begin{equation}
+\Sigma_{\rm crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
 \end{equation}
 in some region.  The separation between the lensed images is of order
-the Einstein radius $\theta_E$.  The image separation is related to
-the mass by
+the Einstein radius $\theta_E$, which is related to
+the mass by:
 \begin{equation}
@@
 \end{equation}
-where $R_G$ is the gravitational radius $GM/c^2$.  If the source is a
+where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$) is the gravitational radius. If the source is a
 quasar or otherwise rapidly variable, a time delay $\Delta t$ in the variability
-will be present where
+will be present where:
 \begin{equation}
@@
 \cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the latter,
-all long before lenses were discovered.  The difficulty became
+all long before lenses were discovered.  The difficulty with actually doing this, however, became
 apparent soon after the discovery of the first lens by
@@
 \citep[see for example][]{2010GReGr..42.2151K,2011A&ARv..19...47K}.
-Second, they pointed out the non-uniqueness of lens models, or lensing
+Second, they pointed out the non-uniqueness of lens models -- lensing
 degeneracies.  Third, they suggested combining lensing data with
@@
 degeneracies.  Later work, as well as following up these suggestions,
-has introduced some ideas.  Four of these are important in the present
-work.
-\begin{itemize}
-\item In free-form models, there is no specified parametric form for
+has introduced some further new ideas.  Four of these are important for the present
+work:
+\begin{enumerate}
+\item {\bf Free-form modelling:} In `free-form' or non-parametric modelling, there is no specified parametric form for
   the mass distribution.  There are still assumptions (or priors) on
@@
   concentrated
-  \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C}
-  but these are much less restrictive than parametric forms.
-  \cite{2006MNRAS.367.1209L} implemented a particularly elegant prior,
-  which is that the mass distribution must be non-negative and no
-  extra images are produced.  Free-form models are more commonly used with
-  cluster lenses \citep{2009ApJ...690..154S,2013arXiv1304.2393S}, but
+  \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2009A&A...500..681M,2010ApJ...723.1678C}
+  but these are much less restrictive than parametric forms (\cite{2006MNRAS.367.1209L} implemented a particularly elegant prior, which is that the mass distribution must be non-negative and no
+  extra images are produced). To be concrete, we define from here on:
+
+  \begin{quote}
+  {\it Non-parametric, or `free-form' $\equiv$ more parameters than data constraints (i.e. deliberately under-constrained)}
+  \end{quote}
+
+  Being under-constrained, it is then {\it necessary} to explore model degeneracies rather than find a single `best-fit' solution. Free-form models are more commonly used with
+  cluster lenses \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S}, but
   can be used with galaxy lenses as well, where their less restrictive
   assumptions can be important.  For example, in time-delay galaxy
-  lenses parametric models led to tensions with the Hubble parameter
-  $H_0$ \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}, but
-  the less restrictive assumptions of free-form models resolved those
-  tensions \citep{2007ApJ...667..645R}.
+  lenses, parametric models have historically led to tension with independent measures of the Hubble parameter
+  $H_0$ \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are resolved once the less restrictive assumptions of free-form models are permitted \citep{2007ApJ...667..645R}.
 \item Model ensembles, exploring a diverse range of possible mass
   distributions that nonetheless all fit the data, are a way of
-  combating the non-uniqueness of models.  Model ensembles are
+  combating the non-uniqueness of models.  Such ensembles are
   possible in parametric models \citep{1999AJ....118...14B} but are
@@
   \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.
-\item Stellar kinematics has played a role in many modelling
-  techniques.  The underlying reason is the virial theorem, which
-  relates the line of sight velocity dispersion to the Einstein radius
-  as
+\item {\bf Stellar kinematic constraints:} This was first suggested by \citet{2002MNRAS.337L...6T} as a means to break lensing degeneracies and determine cosmological parameters.
+This works because stellar kinematics can provide an independent estimate of the Einstein radius, via the virial theorem:
 %
@@
   \frac{\theta_E}{6\pi} \frac{D_S}{D_{LS}}
-\end{equation}
-%
-  with the relation becoming exact for isothermal lenses.  The use of
+\label{eqn:virial}
+\end{equation}
+ where $\langle v^2_{\rm los}\rangle$ is the projected stellar velocity dispersion, and the above relation becomes exact for isothermal lenses.  The use of
   two-dimensional kinematics by \cite{2011MNRAS.415.2215B} is
   especially interesting.
-\item The stellar mass in a lens can be inferred from photometry and
+\item {\bf Stellar mass constraints:} The stellar mass in a lens can be inferred from photometry and
   compared with the total mass
   \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
-  Since the inferred stellar mass does depend on the assumed IMF,
+  Since the inferred stellar mass depends on the assumed IMF,
   lenses in which stellar mass dominates can be used to derive upper
@@
   but these require upper-bound assumptions about the dark-matter
-  profile.
-\item Testing modelling strategies to see how well they recover
-  simulated lenses is increasingly recognized as essential.  Simple
+  profile. \hilight{JR. I feel like we need more citations here and throughout. We must be skipping over an Armada of literature.}
+\item {\bf Testing modelling strategies:} Using mock data to see how well a given model can recover
+  simulated lenses is increasingly being recognised as essential.  Simple
   blind tests have appeared in earlier work \citep[for example, Figure
     2 in][]{2000AJ....119..439W}, but more recently, tests against
-  dynamically simulated galaxies are favoured
-  \citep{2007ApJ...667..645R,2009MNRAS.393.1114B}.
-\end{itemize}
-There are also more modelling ideas in the literature.  One is to use
+  dynamically simulated galaxies or clusters are favoured
+  \citep{2007ApJ...667..645R,2007MNRAS.380.1729L,2009A&A...500..681M,2009MNRAS.393.1114B,2010ApJ...723.1678C}.
+\end{enumerate}
+
+There are two further key modelling ideas in the literature that we will not touch upon in this present work: to use
 X-ray intensity and temperature profiles as a mass constraint
-\citep[such as in][]{2013ApJ...765...25N}.  Another idea is to model
+\citep[e.g.][]{2013ApJ...765...25N}; and to model
 multiple lenses simultaneously, with one or more cosmological
-parameters variable but shared between the lenses.  This strategy has
-been used to constrain $H_0$ from time delays
+parameters variable but shared between the lenses. This latter strategy has
+been used to constrain $H_0$ from time delay lenses 
 \citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P}.
-In principle, cosmological parameters could be constrained even from a
-single lens.  Some models have attempted this
-\citep{2010Sci...329..924J,2013arXiv1306.4732S} starting from a prior
-based on the values and uncertainties from the CMB; tests of this
-technique simulated lenses are still awaited, in order to see how far
-the results depend on the model assumptions.
-
-In this paper, we use a new program---\Glass, the Gravitational Lensing AnalysiS Software---to determine what
+(In principle, cosmological parameters can be constrained even from a
+single lens if the data are good enough. Some recent models have attempted this starting from a prior
+based on the Cosmic Microwave Background (CMB) radiation \citep{2010Sci...329..924J,2013arXiv1306.4732S}.)
+
+In this paper, we use a new program --- \Glass\ (Gravitational Lensing AnalysiS Software) --- to determine what
 combination of lensing, stellar mass, and stellar kinematic
@@
 distribution, and various post-processing and visualisation modules.  \Glass\
-is described in \secref{sec:glass}.  In \secref{sec:theory} before that we
-review the elements of lensing theory, stellar population synthesis, and
+is described in \secref{sec:glass}.  In \secref{sec:theory}, we
+review the key elements of lensing theory, stellar population synthesis, and
 stellar dynamics we will need.
-
 In \secref{sec:mockdata}, we describe our mock data.
-
-In \secref{sec:results}, we present our results from applying \Glass\ to
-these mock data.
-
-\section{Formulation}\label{sec:theory}
+In \secref{sec:results}, we present our results from applying \Glass\ to these mock data.
+Finally, in \S\ref{sec:conclusions} we present our conclusions.
+
+\section{Theory}\label{sec:theory}
 
@@
 
-The lens equation
+The lens equation:
 \begin{equation}
@@
 relativistic gravitational time dilation due to a thin lens at
-redshift $z_L$.
+redshift $z_L$:
 \begin{equation}
@@
 \end{equation}
-The time here has been scaled to make it dimensionless.  We can make
-the density dimensionless as well, by introducing
-\begin{equation}
-\kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
-\end{equation}
-and hence rewrite \eqnref{full arrival time} as
+We can simplify the above equation by introducing a dimensionless time $\tau$ and density $\kappa$:
+
+\begin{equation}
+\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \,\,\,;\,\,\, \kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
+\end{equation}
+and hence rewrite \eqnref{full arrival time} as:
 \begin{equation}
@@
 The scaled arrival time $\tau$ is like a solid angle. It is of order
-the area (in steradians) of the full lensing system --- the expression
-$\sim|\vec\theta - \vec\beta|^2$ is of order the image-separation
+the area (in steradians) of the full lensing system. The expression
+$|\vec\theta - \vec\beta|^2$ is of order the image-separation
 squared, and the other terms are of similar size.  For this reason, is
@@
 is not itself observable.  Its usefulness lies in that observables can
-be derived from it.  Thus an image observed at $\vec\theta_1$ implies
+be derived from it.  An image observed at $\vec\theta_1$ implies
 that $\nabla\tau(\vec\theta_1)=0$.  A measurement of time delays
@@
 so-called mass-sheet degeneracy, which is that image positions remain invariant
-if the $D_S/D_{LS} - \kappa(\vec\theta)$ \hilight{ $\leftarrow$ What is meant
-by this? Can we just write $\tau(\vec\theta)$? }are each multiplied by an
-arbitrary constant.  This amounts to multiplying the arrival-time surface by a
-constant factor.  In fact there are infinitely many degeneracies
+if $\tau(\vec\theta)$ is multiplied by an
+arbitrary constant.  This corresponds to rescaling the surface density at the images $\kappa(\vec\theta)$. In fact there are infinitely many degeneracies
 \citep{2000AJ....120.1654S} because any transformation of the arrival-time
@@
 \begin{equation} 
-\sigma_r^2(r) = \frac{r^{-2\beta}}{\nu}\int_r^\infty r'^{2\beta} \nu \frac{GM(r')}{r'^2}dr'
+\sigma_r^2(r) = \frac{r^{-2\beta}}{\nu}\int_r^\infty r'^{2\beta} \nu \frac{GM_{\rm 3D}(r')}{r'^2}dr'
 \end{equation} 
@@
 assumed to be constant, and not to be confused with $\vec\beta(\vec\theta)$ from
-lensing); $G$ is Newton's gravitational constant; and $M(r)$ is
+lensing); $G$ is Newton's gravitational constant; and $M_{\rm 3D}(r)$ is
 the mass profile that we would like to measure. By convension, we always write $R$ 
-for a projected radius, and $r$ for a 3d radius.
+for a projected radius, and $r$ for a 3D radius.
 
@@
 spherical symmetry, we have a degeneracy between the enclosed mass profile
-$M(r)$ and the velocity anisotropy $\beta(r)$. This can be understood
+$M_{\rm 3D}(r)$ and the velocity anisotropy $\beta(r)$. This can be understood
 intuitively since $\beta(r)$ measures the relative importance of radial versus
@@
 $r\rightarrow \infty$ \citep[e.g.][]{2002MNRAS.330..778W}. It can also be
-estimated if an independent measure of $M(r)$ is available -- for example
-coming from strong lensing. Finally, we may integrate out the effect of unknown
-$\beta(r)$ by performing a luminosity weighted average over all radii:
-
-\begin{equation}
-\overline{\sigma} = \frac{\int_0^{a_p} I(R) \sigma_p^2(R) 2\pi R dR}{\int_0^{a_p} I(R) 2\pi R dR}
-\label{eqn:virialaverage}
-\end{equation} 
-where $a_p$ is the `aperture' over which the integral is performed. Ideally we
-should take $a_p \rightarrow \infty$, however this is not practical for real
-data where the surface brightness of the stars falls off rapidly with $a_p$. In
-practice, $a_p > 2r_{1/2}$, where $r_{1/2}$ is the half light radius of the
-stars, appears to be sufficient (see \S\ref{sec:results}). The above average
-produces a single robust measure of the mass $\overline{\sigma}$ that is
-independent of $\beta(r)$, provided that the stellar system is in a dynamic
-quasi-equilibrium that obeys the virial theorem
-\citep{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}. (Such an
-averaging procedure was first used in a combined lensing/stellar kinematic
-analysis in \citealt{2002MNRAS.337L...6T}.)
+estimated if an independent measure of $M_{\rm 3D}(r)$ is available -- for example
+coming from strong lensing.
+
+While $M_{\rm 3D}(r)$ is difficult to measure from stellar kinematics alone, the mass within the half light radius is robustly recovered \citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A} since stellar systems in dynamic quasi-equilibrium obey the virial theorem (equation \ref{eqn:virial}).
+This means that stellar kinematics can break the steepness degeneracy if $r_{1/2} \neq r_E$, where $r_E = D_L \theta_E$ is the physical Einstein radius.
+We test this expectation in \S\ref{sec:results}.
 
@@
 
-\Glass is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
+\Glass\ is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
 \PixeLens\ but completely rewritten in Python and C. 
@@
 linear space that represents the modelling solution space. This algorithm was
-described and tested in \cite{2012MNRAS.425.3077L}. This algorithm is 
+described and tested in \cite{2012MNRAS.425.3077L}; it is 
 multi-threaded allowing it to run efficiently on many-cored machines.
@@
 \subsection{Discrete models}\label{sec:discrete}
-For this paper we will restrict ourselves to using the pixelated basis set that
+For this paper, we will restrict ourselves to using the pixelated basis set that
 has been employed in previous work and is implemented in \PixeLens. Here we
@@
 where we sweep through the model ensemble applying the ray tracing algorithm
-described in \ref{Raytracing}. Models are accepted or rejected according to the
-criteria:
-
-\begin{equation}
-XXX
-\end{equation} 
-\hilight{We are not rejecting any models. Shall we remove this section, or just rewrite it?}
-\hilight{Typically, this results in a rejection rate of XXX\%}.
-
-{\bf JR. Jonathan to fill in this section.}
+described in \ref{Raytracing}. \hilight{JR. Typically, this results in a rejection rate of XXX\% IS this working? Can we run it once and add the number here?}.
 
@@
 applied in post-processing. We sweep through the model ensemble performing an
-Abel deprojection to determine $M(r)$ from the projected surface density
-assuming spherical symmetry
-\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
+Abel deprojection to determine $M_{\rm 3D}(r)$ from the projected surface density $\Sigma(R)$
+assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
 
 \begin{eqnarray} 
-M(r) & = & \frac{\zeta}{d_L} \left[2\pi\int_0^r R\kappa_\infty(R)dR - \right. \nonumber \\
-& & \left. 4\int_r^\infty R\kappa_\infty(R)f\left(\frac{R}{r}\right)dR\right]
+M_{\rm 3D}(r) & = & M(r) - 4r^2 \int_0^{\frac{\pi}{2}} \Sigma\left(x\right) \left(\frac{1}{\cth^2} \right. \nonumber \\ 
+& & \left. - \frac{\sth}{\cth^3} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
 \end{eqnarray}
+where $M(r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
+
 This de-projection algorithm was tested on triaxial figures in
@@
 simply marginalise over the effect of $\beta(r)$, using the stellar kinematics
-as a robust measure of $M(r_{1/2})$ (see \S\ref{sec:kinematics}).
+as a robust measure of $M_{\rm 3D}(r_{1/2})$ (see \S\ref{sec:kinematics}).
 
@@
 \begin{equation} 
-  \rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}} 
+  \rho(m) = \frac{M}{4\pi a^3}(3-\gamma){(m/a)^{-\gamma}(1 + m/a)^{\gamma-4}} 
   \label{Dehnen profile} 
@@
 %
-where $a$ is the component scale radius mentioned in \tabref{mock galaxy params},
-$r^2 = (x/\lambda_1)^2 + (y/\lambda_2)^2 + (z/\lambda_3)^2$, and the axis
+where $a$ is the component scale radius mentioned in \tabref{mock galaxy params};
+$m^2 = (x/\lambda_1)^2 + (y/\lambda_2)^2 + (z/\lambda_3)^2$ is the ellipsoidal radius; and the axis
 ratios are $\lambda_1:\lambda_2:\lambda_3 = 6:4:3$.
@@
 profile \citep{1990ApJ...356..359H}.  The four combinations of profile indices
-are shown in \tabref{mock galaxy params}. \hilight{JR. Need to add explanation of
-triaxial parameters here. Is the above density equation correct in fact?}
+are shown in \tabref{mock galaxy params}.
 
@@
 central image belongs to only to the R1 source to avoid overconstraining the
-models. Image colors represent a common source. In the case of the extended
-sources the redshift is at R1, while the redshift is varied between the systems
-in the ZConstrast cases. Grey circles are a visual aid to help determine radial
-separation between images. The axes are measure in arcseconds.}
+models. Image colors represent a common source. Grey circles are a visual aid to help determine radial
+separation between images. The axes are in arcseconds.}
 \label{arrival surfaces}
@@
 
-Each of these configurations were modelled with and without time delays, with
-and without a central image, and with and without the stellar mass as a lower
+Each of these configurations were modelled with and without time delays; with
+and without a central image; and with and without the stellar mass as a lower
 bound, for a total of 48 test cases. (The central image is typically highly
@@
 the sight line to the bright lensing galaxy; in clusters, however, such images
-have been seen \hilight{(CITES)}). We assumed for all our tests that the
-lensing mass was radially symmetric (Prior vi): For our mock data, this is
+have been seen -- e.g. \citealt{2005PASJ...57L...7I}). We assumed for all our tests that the
+lensing mass was radially symmetric (Prior vi). For our mock data, this is
 known to be true; it is most often the case with real galaxies, unless there is
@@
 the profile.  Two of the four mock galaxies have a steeply rising inner
-profile. \hilight{JR.  What happens if we don't assume this symmetry? We ought
+profile. \hilight{JR.  CAN WE DO THIS? What happens if we don't assume this symmetry? We ought
 to add an appendix showing this for one example case.}
 
+In all cases, we additionally assume no external shear.
+This amounts to an assumption that any such shear field can be constrained by data (e.g.
+combining weak lensing constraints, or assuming that the shear field correlates with visible galaxies -- e.g.
+\citealt{2009A&A...500..681M,2011ApJ...726...84W}).
+
 \section{Results}\label{sec:results}
-\figref{reconstruction} shows a typical reconstruction of a lens. The far left
-plot shows the ensemble average arrival time surface with image marked as
-circles and the inferred source position as a diamond. The center plot shows
+
+\subsection{Radial profile recovery}
+
+\figref{reconstruction} shows some example reconstructions of the radial profile of our mock lenses. The left
+column shows the ensemble average arrival time surface with images marked as
+circles and the inferred source position(s) as a diamond. The centre column shows
 the radial density profile. The error bars cover a $1\sigma$ range around the
-median.  The true density profile from the mock data is also plotted for
+median; the grey bands show the full ensemble range. The true density profile from the mock data is also plotted for
 comparison. The vertical lines mark the radial position of the images. The
-final plot on the right is of the enclosed mass. As expected, the error bars
+right column shows the enclosed mass.
+From top to bottom, the rows correspond to an extended double for \mockBC; an extended double with stellar mass constraints for \mockBC; a quad with time delay data for \mockBC; and a quad with time delays for \mockAA.
+\figref{2d mass reconstruction} shows an example 2D reconstruction for \mockBC\ for a quad; we discuss shape recovery further in \S\ref{sec:shape}.
+
+As expected, the error bars
 are smallest in the region of the images where the most information about the
-lens is present. The dip in the profile at the end of the profile is due to the
+lens is present. In all cases, there is a dip in the profile at large $R$ due to the
 cut off in mass in the lensing map. This is of little importance, though, as
 there is no lensing information there.
+
+Notice that the extended double (top row) gives the poorest constraints, as expected.
+Adding stellar mass (second row) significantly improves the constraints, for this example where the stars contribute significantly to the potential.
+Moving to a quad with time delays gives constraints almost as strong as the double with stellar mass, but note that {\it focussing only on the goodness of the fit can be misleading.} In the third row of \figref{reconstruction}, we obtain a better recovery than in the bottom row for {\it precisely the same data quality}.
+This occurs because the \Glass\ prior favours steeper models consistent with \mockBC, but not \mockAA.
+It is the \Glass\ prior, rather than the data that is driving the good recovery for \mockBC\ in this example.
+This emphasises the importance of using a wide range of mock data tests to determine the role of data versus prior in strong lensing.
 
@@
     stellar density index, and a core in the dark matter. Due to the priors
-    used in \Glass, the modelling favors steep solutions without additional
+    used in \Glass, the modelling favours steep solutions without additional
     information.
 \textbf{Left:}
-The ensemble average arrival time surface with just the isocontours for the
+The ensemble average arrival time surface with just the iso-contours for the
 saddle points drawn. The central diamonds show the reconstructed source
@@
 \textbf{Middle:}
-The surface density of the dark matter (magenta), the stars (yellow), and the total (blue).
+The surface density of the dark matter (DM; magenta); the stars (yellow); and the total (blue).
 The original mass model used to create the lens is shown in black.
@@
 \textbf{Right:}
-The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range of models for DM+Stars (blue).}
+The cumulative mass. The error bars on all plots are $1\sigma$; the grey bands show the full range of models.}
 \label{reconstruction}
@@
 
-The main results from modeling these different configurations are shown in
-\figref{main results} and \figref{main results pixel-wise}. Each
-subplot corresponds to a different mock galaxy. We show the fractional error of the mass
-distribution for each of the test configurations with (red) and without stellar mass (black)
-In \figref{main results}, the error is defined over radial bins of mass as
+\figref{main results} and \figref{main results pixel-wise} show the results for our full mock data ensemble. Each
+subplot corresponds to a different mock galaxy, as marked. We show the fractional error of the mass
+distribution for each of the test configurations with (red) and without (black)
+ stellar mass. In \figref{main results}, the error is defined over radial bins of mass as:
 %
@@
 where $M$ is the mass in bin $i$ and $\tilde M$ is the mass from the mock galaxy.
-In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
+In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$:
 %
@@
 \end{equation}
+With both $f_R$ and $f_\theta$, we only consider mass up to one radial
+position passed the outermost image, since there is no longer any lensing
+information beyond that point.
 
@@
 \includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
-\caption{Our main results showing the quality of model recovery \eqnrefp{ferror R} for all our test cases. 
-Within
-each panel are six groups of results for each of six lens morphologies. Each morphology
-considered the presence of time delays (T,t) and a central image (M,m). The black markers are for tests
+\caption{Our main results showing the quality of the radially averaged model recovery \eqnrefp{ferror R} for all our test cases. 
+Within each panel are six groups of results for each of six lens morphologies. Each morphology
+considered the presence of time delays (T=yes,t=no) and a central image (M=yes,m=no). The black markers are for tests
 that did not include the stellar mass as a lower bound constraint, while the red markers
-indicate where the stellar mass has been included. Error bars show the $1\sigma$ interval of the model ensemble.}
+indicate where the stellar mass has been included. Error bars show the $1\sigma$ range of the model ensemble.}
 \label{main results}
@@
 \includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
-\caption{Similar to \figref{main results}, we show here the fractional error
-for the pixel-wise recovery \eqnrefp{ferror theta} of all models. The colors and labels are the same
-as before. Error bars show the $1\sigma$ interval of the model ensemble.}
+\caption{Similar to \figref{main results} but for the fractional error
+in the pixel-wise recovery \eqnrefp{ferror theta} of all models. The colours and labels are the same
+as previously. Error bars show the $1\sigma$ range of the model ensemble.}
 \label{main results pixel-wise}
@@
 
-With both $f_R$ and $f_\theta$ we only consider mass up to one radial
-position passed the outermost image, since there is no longer any lensing
-information beyond that point.
-
 The abundance of strong lensing data increases from left to right within each
 plot. As a result, there is a general trend for the reconstruction quality to
-increase (and for $f$ to decrease). By adding more measurable information to
-each configuration the quality can also be affected. When both time delays and
-a central image are present the quality is highest. A double is known to
+increase (and therefore for $f$ to decrease). When both time delays and
+a central image are present (TM), the quality is highest. A double is known to
 provide very little constraint on the mass distribution. This is particularly
@@
 and the reconstruction of the double is poorest. However, the addition of an
-arc from the extended source is sufficient to correct this. \hilight{Mention the saturation of the two panels.}
-
-We can also directly measure the recoverability of the shape of the mass
-distribution by computing the eigenvalues of the inertia tensor. We define our
-shape by the ratio of these eigenvalues $s=\lambda_1/\lambda_2$, where the
-$\lambda_1$ is always the largest value. Again, we only consider mass up to one
-radial position passed the outermost image and compute our the fractional error
+arc from the extended source is sufficient to correct this.
+Notice that, as in \figref{reconstruction}, the recovery for \mockBC\ quickly saturates; there is little improvement as the data improves beyond a single quad.
+This occurs because the \Glass\ sample prior in the absence of data favours steep models like \mockBC\ over shallower models like \mockAA\ (see also \figref{reconstruction}).
+
+\subsection{Shape recovery}\label{sec:shape}
+
+\figref{main results pixel-wise} already gives us important information about how well we can recover the {\it shape} of a lens.
+The trends are very similar to the radial profile recovery in \figref{main results}, suggesting that if the radial profile is well-recovered then, typically, the shape is too.
+A notable exception is for the \mockBC\ models where adding stellar mass constrains aids the shape recovery, but little-improves the radial mass profile.
+A visual example of the shape recovery is given in \figref{2d mass reconstruction}.
+
+We can also more directly probe the recovery of the shape of the mass
+distribution by defining a global measure of lens shape. We define this to be the ratio of the eigenvalues of the 2D inertia tensor:
+
+\begin{equation} 
+I_{ij} = \sum_\theta M(\vec\theta) \theta_i\theta_j \,\,\, ; \,\,\, s \equiv \lambda_1/\lambda_2
+\label{eqn:inertia}
+\end{equation}
+where $\lambda_1$ is always taken to be the largest value. As with $f_R$ and $f_\theta$, we only consider mass up to one radial position passed the outermost image and compute the fractional error as:
 %
@@
 for each mock galaxy and each test case is shown in \figref{shape results}.
-
-\begin{figure}
-\plottwo{AAExtendedDoubleR1_TmS-shape-hist.pdf}{BCZContrastR1R3_TmS-shape-hist.pdf}
-\caption{The two plots in the left most column show sample distributions of
-  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
-  The upper (poor) plot is from the \mockAA{} galaxy, while the lower (good) plot is
-  from the \mockBC{} galaxy. The black vertical lines mark the $2\sigma$
-  region and the vertical blue line is the value of $s$ for the corresponding
-mock galaxy. }
-
-\label{shape results}
-\end{figure}
+Interestingly, for this global shape parameter recovery it appears more important to have time delay data and/or a central image (T/M) than to have a quad or multiple sources with wide redshift separation.
+In all cases, the stellar mass little-aids the recovery, reflecting the fact that $s$ is heavily weighted towards the shape at the {\it edge} of the mass map, rather than at the centre where the stars may dominate the potential (see equation \ref{eqn:inertia}).
 
@@
 (yellow) Einstein radius (black) are marked by vertical lines. For this
-configuration, these two radii are well-separated. The actual variation in $\beta(r)$ is show also shown (\textbf{right}).}
-
+configuration, these two radii are well-separated. The actual variation in $\beta(r)$ is also shown (\textbf{right}).}
 \label{fig:sigp} \end{figure*}
-
 \subsection{Stellar mass}
@@
 
-\hilight{This is a bit overstated.}
-With the stellar mass lower bound, the improvement of the reconstruction
-quality shown in \figref{main results} is quite dramatic for the doubles in the
+With the stellar mass lower bound, there is a significant improvement of the reconstruction
+quality shown in \figref{main results} and \figref{main results pixel-wise} for the doubles in the
 steepest mock galaxies (\mockAC{} and \mockBC). This is because these models
 are dominated by stars in the inner region. By contrast, the other two galaxies
----where the stars contribute negligibly to the potential---are unaffected.
+ --- where the stars contribute negligibly to the potential --- are largely unaffected.
 
@@
 Without even sweeping through the model ensemble and formally
-accepting/rejecting models, \figref{sigma-beta} already illustrates what we can
-hope to obtain from stellar kinematics. The most robust constraints follow if
-we can integrate out the effect of $\beta$ (right panel), since this is
-difficult to measure. For large enough aperture size ($a_p > 2r_{1/2}$), the
-average projected dispersion converges on a single well defined value
-independently of $\beta$. Since this converged value follows from the virial
-theorem, it is also rather insensitive to the shape of the potential
-\citep{2012ApJ...754L..39A}: it constitutes a robust constraint on the lensing
-potential. On the other hand, if the mass profile is well-constrained already
-at $r \sim r_{1/2}$, then we can use stellar kinematics to probe $\beta$. This
-can be seen in the left panel of \figref{sigma-beta}. Here we see that for a
-well-constrained mass model, the $\beta = 1$ curve lies significantly off from
-the true answer that has $\beta(r) \sim 0$.
-
-\hilight{This paragraph should be removed.}
-We now consider formally accepting/rejecting models from the full ensemble. We
-consider two regimes of interest: a model with a double where the mass profile
-is poorly constrained \hilight{(XXX)}, and a model where the mass profile is very well
-constrained by the lens data \hilight{(YYY)}. In the former case, we use
-$\overline{\sigma}(2 r_{1/2})$ to probe the mass independently of $\beta(r)$.
-We accept/reject models assuming a Gaussian error on measured
-$\overline{\sigma}(2 r_{1/2})$ of $\pm 10$\,km/s (similarly to the data quality
-presented for example in \citealt{2002MNRAS.337L...6T}). The results are shown
-in \figref{main results}, blue data points. In the latter case, we ask whether
-the data favour $\beta = 0$ or $\beta = 1$ by obtaining a $\chi^2$ goodness of
-fit measure between the true and modelled $\sigma_p(R)$. We accept/reject
-models from the ensemble above. The results for $\beta$ are shown in the right panel of
-\figref{fig:sigp}.
+accepting/rejecting models, \figref{fig:sigp} already illustrates what we can obtain from stellar kinematics.
+The left plot shows the radially averaged projected velocity dispersion $\sigma_p(R)$ \eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC\ galaxy without the stellar mass constraint.
+The blue data points show the 1$\sigma$ distribution from the ensemble assuming $\beta=0$ (solid) and $\beta = 1$ (dashed); the grey bands show the full distributions.
+Also marked are the $\sigma_p(R)$ calculated from the mock data assuming $\beta=0$ (solid purple) and $\beta =1$ (dashed purple); and the true $\sigma_p(R)$ measured directly from the stars (black).
+This latter has a non-constant $\beta(r)$ (right panel) and differs also from the purple and blue curves in that these all assume spherical symmetry, whereas the stellar distribution is really triaxial.
+Such triaxiality and varying $\beta(r)$ explains why the purple curves do not match the black one.
+However, they do largely bracket the correct solution.
+More interestingly, the curves approximately cross for $\beta = 0$ at the stellar half light radius (yellow vertical line).
+This demonstrates, as has previously been reported in the literature, that $\sigma_p(R)$ gives a good estimate of the mass enclosed within $\sim$ the half light radius $M_{1/2}$ \citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W}.
+The mass {\it profile}, however, depends on $\beta$ which is poorly constrained by these data.
+If we add stellar mass constraints (middle panel), the situation is little-improved.
+The true answer already lay close to the bottom of the ensemble distribution; it now is forced to lie right at the edge.
+
+From \figref{fig:sigp}, it is clear that $\sigma_p(R)$ provides two useful pieces of information.
+Firstly, it is a powerful probe of $M_{1/2}$.
+Given a measurement of $\sigma_p(r_1/2) \sim 150$\,km/s, we could usefully reject many models in the ensemble as being overly steep in the centre.
+We would not, however, obtain a strong constraint on $\beta(r_{1/2})$.
+We could rule out $\beta(r_{1/2}) = 1$ (blue dashed line), but since our $\beta=0$ model crosses the true $\beta \sim 0.5$ line at $r_{1/2}$ it is clear that many $\beta(r)$ profiles will be consistent with the data.
+On the other hand, if we have a situation where $r_{1/2} \sim r_E$ (i.e.
+the vertical yellow and black lines in \figref{fig:sigp} overlap), then we will obtain tight constraints on $\beta$ since we then have two strong constraints on $M(r_{1/2})$ that become redundant.
+This latter situation of redundancy is also exactly what we would like to constrain cosmological parameters.
+In this case, we require a third piece of redundant information -- in this case in the form of strong lensing time delays.
+We will discuss such cosmological constraints in a forthcoming paper.
 
@@
 at $r_{1/2}$, we may `integrate out' the effect of unknown $\beta$ to obtain a
-robust measure of $M(r_{1/2})$ from the stellar kinematics. This latter is
+robust measure of $M_{\rm 3D}(r_{1/2})$ from the stellar kinematics. This latter is
 robust to both uncertainties in $\beta(r)$ and to our assumption of spherical
-symmetry in the kinematic models \citep{2012ApJ...754L..39A}. Finally, we note
-that there is a third interesting case. If the lens models well-constrain
-$M(r_{1/2})$ and stellar kinematics are available, then these can be used to
-probe cosmological models (see \S\ref{sec:theory}). We explore this in more
-detail in a separate publication.
+symmetry in the kinematic models \citep{2012ApJ...754L..39A}.
 
@@
 
-We have introduced a new gravitational len modelling tool---\Glass---and used
+We have introduced a new gravitational lens modelling tool ---\Glass--- and used
 it to test the recovery of the mass profile and shape of mock strong lensing
-galaxies. We have also shown that with the addition of stellar mass
-constraints, one can better constrain the inner profile of galaxies,
-particularly in the case of doubles. Furthermore, by we have demonstrated our
-sensitivity to the estimates of the velocity dispersion. Improved measurements
-of the dispersion and, in particular, the velocity anisotropy could be used to
-greatly enhance our lens models.
+galaxies. Our key findings are as follows:
+
+\begin{enumerate}
+\item For pure lens data, multiple sources with wide redshift separation give the strongest
+constraints as this breaks the well-known mass-sheet or steepness degeneracy;
+
+\item A single quad with time delays also performs well, giving a good recovery
+of both the mass profile and its shape;
+
+\item Stellar masses -- for lenses
+where the stars dominate the central potential -- can also break the steepness
+degeneracy, giving a recovery almost as good as having time delay data or
+multiple source redshifts;
+
+\item If the radial density profile is well-recovered, so too is the shape of a lens;
+
+\item Stellar kinematics provide a robust measure of the mass at the half light radius of the stars $M(r_{1/2})$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and
+
+\item If $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy 
+$\beta$ -- an interesting quantity in its own right.
+
+\end{enumerate}
+
+Where information on the mass distribution from lensing and/or other probes becomes
+redundant, this opens up the possibility of using strong lensing to constrain
+cosmological models. We will study this, and present the first results from
+\Glass\ applied to real data, in forthcoming papers.
 
@@
 The authors would like to thank Sarah Bryan and Walter Dehnen for creating the
-particle distributions for the mock galaxies. This work has been partially
-funded by \hilight{if we want..}
-
-\subsection{Goodness of recovery}
-
-\begin{enumerate}
-
-  \item \sout{Change variable $\chi$ to something else ($f$?) to avoid confusion with $\chi^2$.}
-
-  \item \sout{Correct equation \eqref{badness} to describe what is actually calculated.}
-
-  \item \sout{Show results for $1\sigma$ and $2\sigma$ rather than full \Glass\ ensemble.}
-
-\item Add results for Claudio's shape measure. Discuss shape
-  throughout results section and mention more explicitly in abstract
-  and conclusions -- what quality of data do we need to robustly
-  constrain the shape?
-
-\item Add plot of $\chi$ ($f$) for $lambda_1/lambda_2$ and shape
-  parameters (cf. what Claudio is doing).
-
-\item \sout{Check that you and Claudio average to the same projected radius
-  (one pixel past outermost image) when calculating
-  $lambda_1/lambda_2$ and $\theta$.}. This is correct.
-
-\end{enumerate}
-
-\subsection{Kinematics}
-
-\begin{enumerate}
-
-\item \sout{Add example plot of the projected density and recovered
-  projected density (cf. plots Jonathan made for Justin's ERC
-proposal).}
-
-\item Calculate aperture averaged $\sigma$ to 2 (or 3 you decide) half
-  light radii assuming $\beta = 0$ for a model (double) where the mass
-  is poorly constrained by strong lensing. Accept/reject models from
-  the ensemble $\Longrightarrow$ what we learn from combined lensing
-  kinematics.
-
-\item \sout{Take a model that is well constrained by strong lensing
-  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
-  in the ensemble using the kinematics module. Compare this with the
-true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
-  a $\chi^2$ this time!). Show the true $\sigma_p(R)$ and overlay
-  coloured bands from the lensing model ensemble assuming $\beta = 0$
-or $\beta = 1$.}
-
-\item Add accept/reject results for stellar kinematics (two figures)
-  as detailed in \S\ref{sec:results_stellar_kinematics}.
-
-\end{enumerate}
-
-\subsection{Other}
-
-\begin{enumerate}
-
-\item Tidy up figures and other small items as detailed throughout --
-  see {\bf JR ... }
-
-\item Add appendix showing how inversion symmetry in the prior affects
-  results. Clarify meaning of this prior with a nice figure showing
-  the symmetry.
-
-\item Complete \S\ref{sec:glass}. Emphasise need for central adaptive
-  grid. Add appendix showing convergence as Pixrad is increased.
-
-\end{enumerate}
-
-\subsection{Clarifications in text}
-
-\begin{enumerate}
-
-\item Write section \S\ref{sec:glassextraimages} on removing models
-  with extra images.
-
-\item Clarify amount of triaxiality (and the analytic density profile)
-  in \S\ref{sec:mockdata}.
-
-\item \sout{Clarify number of lens configurations in \S\ref{sec:lensconfig}.}
-
-\end{enumerate}
+particle distributions for the mock galaxies. JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
 

### 2014-01-28 limits/ms.tex
Changed to use only en dashes.

@@
 \begin{abstract}
-We use a new non-parametric gravitational modelling tool --- \Glass\ --- to
+We use a new non-parametric gravitational modelling tool -- \Glass\ -- to
 determine what quality of data (strong lensing, stellar kinematics, and/or
@@
 
-In this paper, we use a new program --- \Glass\ (Gravitational Lensing AnalysiS Software) --- to determine what
+In this paper, we use a new program -- \Glass\ (Gravitational Lensing AnalysiS Software) -- to determine what
 combination of lensing, stellar mass, and stellar kinematic
@@
 are dominated by stars in the inner region. By contrast, the other two galaxies
- --- where the stars contribute negligibly to the potential --- are largely unaffected.
+ -- where the stars contribute negligibly to the potential -- are largely unaffected.
 
@@
 
-We have introduced a new gravitational lens modelling tool ---\Glass--- and used
+We have introduced a new gravitational lens modelling tool -- Glass\ -- and used
 it to test the recovery of the mass profile and shape of mock strong lensing

### 2014-01-28 limits/ms.tex
New plots showing examples of no symmetry and changing pixrad.
Fixed up notation for inertia tensor.

@@
 The lens equation:
+%
 \begin{equation}
@@
 \end{equation}
+%
 maps an observed image position $\vec\theta$ to a source position
@@
 comparison. The vertical lines mark the radial position of the images. The
-right column shows the enclosed mass.
-From top to bottom, the rows correspond to an extended double for \mockBC; an extended double with stellar mass constraints for \mockBC; a quad with time delay data for \mockBC; and a quad with time delays for \mockAA.
-\figref{2d mass reconstruction} shows an example 2D reconstruction for \mockBC\ for a quad; we discuss shape recovery further in \S\ref{sec:shape}.
+right column shows the enclosed mass. From top to bottom, the rows correspond
+to an extended double for \mockBC; an extended double with stellar mass
+constraints for \mockBC; a quad with time delay data for \mockBC; and a quad
+with time delays for \mockAA. \figref{2d mass reconstruction} shows an example
+2D reconstruction for \mockBC\ for a quad; we discuss shape recovery further in
+\S\ref{sec:shape}.
 
@@
 
-\figref{main results pixel-wise} already gives us important information about how well we can recover the {\it shape} of a lens.
-The trends are very similar to the radial profile recovery in \figref{main results}, suggesting that if the radial profile is well-recovered then, typically, the shape is too.
-A notable exception is for the \mockBC\ models where adding stellar mass constrains aids the shape recovery, but little-improves the radial mass profile.
-A visual example of the shape recovery is given in \figref{2d mass reconstruction}.
+\figref{main results pixel-wise} already gives us important information about
+how well we can recover the {\it shape} of a lens. The trends are very similar
+to the radial profile recovery in \figref{main results}, suggesting that if the
+radial profile is well-recovered then, typically, the shape is too. A notable
+exception is for the \mockBC\ models where adding stellar mass constrains aids
+the shape recovery, but little-improves the radial mass profile. A visual
+example of the shape recovery is given in \figref{2d mass reconstruction}.
 
 We can also more directly probe the recovery of the shape of the mass
-distribution by defining a global measure of lens shape. We define this to be the ratio of the eigenvalues of the 2D inertia tensor:
-
-\begin{equation} 
-I_{ij} = \sum_\theta M(\vec\theta) \theta_i\theta_j \,\,\, ; \,\,\, s \equiv \lambda_1/\lambda_2
+distribution by defining a global measure of lens shape
+%
+\begin{equation} 
+    s \equiv \lambda_1/\lambda_2
+\end{equation} 
+%
+where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor
+%
+\begin{equation} 
+    I_{ij} = (-1)^{1-\delta_{ij}}\sum_\theta M(\vec\theta) \theta_i\theta_j 
 \label{eqn:inertia}
 \end{equation}
-where $\lambda_1$ is always taken to be the largest value. As with $f_R$ and $f_\theta$, we only consider mass up to one radial position passed the outermost image and compute the fractional error as:
+%
+where $\delta_{ij}$ is the Kronecker delta.
+We always take $\lambda_1$ to be the largest value.
+As with $f_R$ and $f_\theta$, we only consider mass up to one radial position passed the outermost image and compute the fractional error as:
 %
@@
 %
-where $\tilde s$ is the shape of the mock galaxy. The distribution of $f_\mathrm{shape}$
-for each mock galaxy and each test case is shown in \figref{shape results}.
-Interestingly, for this global shape parameter recovery it appears more important to have time delay data and/or a central image (T/M) than to have a quad or multiple sources with wide redshift separation.
-In all cases, the stellar mass little-aids the recovery, reflecting the fact that $s$ is heavily weighted towards the shape at the {\it edge} of the mass map, rather than at the centre where the stars may dominate the potential (see equation \ref{eqn:inertia}).
+where $\tilde s$ is the shape of the mock galaxy. The distribution of
+$f_\mathrm{shape}$ for each mock galaxy and each test case is shown in
+\figref{shape results}.  Interestingly, for this global shape parameter
+recovery it appears more important to have time delay data and/or a central
+image (T,M) than to have a quad or multiple sources with wide redshift
+separation. In all cases, the stellar mass little-aids the recovery, reflecting
+the fact that $s$ is heavily weighted towards the shape at the {\it edge} of
+the mass map, rather than at the centre where the stars may dominate the
+potential (see equation \ref{eqn:inertia}).
 
@@
 
+\section{No symmetric prior}
+\begin{figure*}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-kappa.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-kappa.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-c.pdf}
+\caption{No symmetry prior.}
+\label{}
+\end{figure*}
+
+\section{Pixel resolution convergence test}
+\begin{figure*}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr10_TmS-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr10_TmS-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr10_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-c.pdf} \\
+\caption{Changing pixrad. top to bottom: pixrad=10,7,6,5. We use 8 normally.}
+\label{}
+\end{figure*}
+
 \section{Pixel resolution convergence test}

### 2014-01-28 limits/ms.tex
one word change.
Justin added text to support new Appendix Figures; deleted remaining highlights.

@@
 $^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
-$^2$\hilight{Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom} \\
-$^3$\hilight{Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland}
+$^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
+$^3$Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland
 }
@@
 has a shear term but additionally allows for analytic potentials to
-be included. This can be used to model substructure or multiple neighbors close
+be included. This can be used to model substructure or multiple neighbours close
 to the main lens. The substructure may have only a small effect if the lens is
@@
 physical models. The explicit implementation for these priors has been
-explained in \cite{2008ApJ...679...17C}, but can be summarized as
+explained in \cite{2008ApJ...679...17C}, but can be summarised as
 \begin{enumerate}
@@
 where we sweep through the model ensemble applying the ray tracing algorithm
-described in \ref{Raytracing}. \hilight{JR. Typically, this results in a rejection rate of XXX\% IS this working? Can we run it once and add the number here?}.
+described in \ref{Raytracing}.
 
@@
 known to be true; it is most often the case with real galaxies, unless there is
-an obvious observed asymmetry. The central pixel was refined into a further
-$5\times5$ pixels (three extra radial positions) to capture any steep rise in
-the profile.  Two of the four mock galaxies have a steeply rising inner
-profile. \hilight{JR.  CAN WE DO THIS? What happens if we don't assume this symmetry? We ought
-to add an appendix showing this for one example case.}
+an obvious observed asymmetry.
+(We explore the effect of switching off the symmetry prior in Appendix \ref{no_symm_prior}.
+For the quads, the difference is small; for the doubles -- as expected -- the results are significantly degraded without this prior.) We use, as default, 8 pixels from the centre to the edge of the mass map; the central pixel was further refined into $5\times5$ pixels to capture any steep rise in the profile (two of the four mock galaxies have a steeply rising inner profile).
+We demonstrate that our results are robust to changing the grid resolution in Appendix \ref{pix_convergence_test}.
 
@@
 %
-where $\delta_{ij}$ is the Kronecker delta.
+and $\delta_{ij}$ is the Kronecker delta.
 We always take $\lambda_1$ to be the largest value.
@@
 
-\section{No symmetric prior}
+\section{No radial symmetry prior}\label{no_symm_prior}
+
+In this appendix, we explore the effect of the radial symmetry prior.
+\figref{fig:no_symm_prior} shows results for a single quad (top) and an extended double (bottom); both without time delay data or stellar mass constraints.
+The results for the quad a similarly good to the case with the radial prior (\figref{reconstruction}); for the double, however, the results are significantly degraded as expected.
+
 \begin{figure*}
@@
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-c.pdf}\\
 \includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-kappa.pdf}
@@
 \includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-c.pdf}
-\caption{No symmetry prior.}
-\label{}
+\caption{Results for a single quad (top) and an extended double (bottom) without the radial symmetry prior; both without time delay data or stellar mass constraints.
+Figures and symbols are as in \figref{reconstruction} and \figref{2d mass reconstruction}.}
+\label{fig:no_symm_prior}
 \end{figure*}
 
-\section{Pixel resolution convergence test}
+\section{Pixel resolution convergence test}\label{pix_convergence_test}
+
+In this Appendix, we present a convergence test of our results with the grid resolution -- pixrad.
+As default, this is set to 8 pixels from the centre of the mass map to the edge.
+As can be seen from \figref{fig:pix_convergence_test}, our results are typically well-converged for pixrad$\,\,> 5$.
+The results for pixrad$\,\,= 5$ become systematically biased away from the central regions (where we have the higher resolution adaptive mesh), because our regularisation prior combined with a low pixrad biases us towards shallow models.
+This effect diminishes with increasing resolution and is already negligible by pixrad$\,\,= 7$.
+
 \begin{figure*}
@@
 \caption{Changing pixrad. top to bottom: pixrad=10,7,6,5. We use 8 normally.}
-\label{}
+\label{fig:pix_convergence_test}
 \end{figure*}
-
-\section{Pixel resolution convergence test}
-\hilight{JR. Need to add an appendix showing convergence with increasing Pixrad.}
 
@@
 
-\cite{2007ApJ...667..645R} were the first to test the recovery of
-strong lensing surface density profiles using mock data generated from
-N-body models {\bf JR. Is this true?}. They found that when including
-time delays, circularly averaged surface density distributions can
-sufficiently well-recovered to make interesting comparisons with
-theoretical models Cosmological parameters, however, are more
-sensitive. Since then, several groups have used N-body mock data to
-explore the fidelity of strong lensing reconstructions
-\citep{2007MNRAS.380.1729L}. We expand on these earlier works
-by considering not only the recovery of the circularly averaged
-surface density profile of a lens, but also its shape, higher order
-measures of the mass recovery (a pixel-by-pixel comparison), and the
-utility of wrapping in constraints from stellar mass estimates and/or
-stellar kinematics.
+%\cite{2007ApJ...667..645R} were the first to test the recovery of
+%strong lensing surface density profiles using mock data generated from
+%N-body models {\bf JR. Is this true?}. They found that when including
+%time delays, circularly averaged surface density distributions can
+%sufficiently well-recovered to make interesting comparisons with
+%theoretical models Cosmological parameters, however, are more
+%sensitive. Since then, several groups have used N-body mock data to
+%explore the fidelity of strong lensing reconstructions
+%\citep{2007MNRAS.380.1729L}. We expand on these earlier works
+%by considering not only the recovery of the circularly averaged
+%surface density profile of a lens, but also its shape, higher order
+%measures of the mass recovery (a pixel-by-pixel comparison), and the
+%utility of wrapping in constraints from stellar mass estimates and/or
+%stellar kinematics.
+%

### 2014-01-28 limits/ms-prev.tex
a few more edits

--- 2014-01-28 limits/ms.tex
@@
 This effect diminishes with increasing resolution and is already negligible by pixrad$\,\,= 7$.
+Notice that the mass increases in size with decreasing resolution.
+This is because we always demand that there are four pixels beyond the outermost image.
 
@@
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-c.pdf} \\
-\caption{Changing pixrad. top to bottom: pixrad=10,7,6,5. We use 8 normally.}
+\caption{The effect of changing the grid resolution, pixrad.
+From top to bottom, the panels show results for a single quad without time delays, but with stellar mass constraints using pixrad$\,\, = 10,7,6,5$, respectively.
+We use 8 normally.}
 \label{fig:pix_convergence_test}

### 2014-01-29 limits/ms.tex
Some notation changes. New plots in the appendix with and without time delays. Minor text changes.

@@
 \usepackage{graphicx}
-\usepackage{ulem} % Only necessary for striking out TODO items see \sout
+%\usepackage{ulem} % Only necessary for striking out TODO items see \sout
 \usepackage{color} % Only necessary for hilight
 
+%-------------------------------------------------------------------------------
+% Macros for journal style.
+%-------------------------------------------------------------------------------
+\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}}
+
+%-------------------------------------------------------------------------------
+% Macros for notes.
+%-------------------------------------------------------------------------------
+\newcommand{\hilight}[1]{{\bf \color{red} #1}}
+
+%-------------------------------------------------------------------------------
+% Macros for common use cases.
+%-------------------------------------------------------------------------------
 \newcommand{\Glass}{{\sc Glass}}
@@
 \newcommand{\eps}{\ensuremath{\varepsilon}}
-
 \newcommand{\Eavg}{\ensuremath{\langle \E \rangle}}
-
-\newcommand{\hilight}[1]{{\bf \color{red} #1}}
+\newcommand{\Mddd}{\ensuremath{M}}
+%\newcommand{\Mddd}{\ensuremath{M_\mathrm{3D}}}
+\newcommand{\pixrad}{\ensuremath{\mathrm{\tt pixrad}}}
 
@@
 \newcommand{\e}[1]{\ensuremath{\times 10^{#1}}}
-\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}}
 
@@
 %For deprojection algorithm: 
-\def\cth{\cos\theta}
-\def\sth{\sin\theta}
+\newcommand{\cth}[1][]{\cos^{#1}\theta}
+\newcommand{\sth}[1][]{\sin^{#1}\theta}
 \def\dth{{\rm d}\theta}
+
+%-------------------------------------------------------------------------------
+% Macros for multiple plots
+%-------------------------------------------------------------------------------
 
@@
 
+%-------------------------------------------------------------------------------
+%-------------------------------------------------------------------------------
+
 \title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
@@
 $^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
-$^3$Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland
+$^3$Physik-Institut, Universit\"at Z\"urich, 190 Winterthurerstrasse, 8057, Z\"urich, Switzerland
 }
@@
 degeneracy, giving a recovery almost as good as having time delay data or
-multiple source redshifts; (iv) stellar kinematics provide a robust measure of the mass at the half light radius of the stars $r_{1/2}$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v) if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy
-$\beta$ -- an interesting quantity in its own right. Where
-information on the mass distribution from lensing and/or other probes becomes
-redundant, this opens up the possibility of using strong lensing to constrain
-cosmological models. We will study this, and present the first results from
-\Glass\ applied to real data, in forthcoming papers.
+multiple source redshifts; (iv) stellar kinematics provide a robust measure of
+the mass at the half light radius of the stars $r_{1/2}$ that can also break
+the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v)
+if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the
+stellar velocity anisotropy $\beta$ -- an interesting quantity in its own
+right. Where information on the mass distribution from lensing and/or other
+probes becomes redundant, this opens up the possibility of using strong lensing
+to constrain cosmological models. 
 \end{abstract}
@@
 
-Strong gravitational lenses are rare.
-Since the discovery of the first lens Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to date\footnote{See e.g.
-{\tt http://www.masterlens.org} for a catalogue.}.
-However, this number is expected to increase to
-several thousand over the next ten years as new surveys, both
+Strong gravitational lenses are rare. Since the discovery of the first lens
+Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
+date\footnote{See e.g. {\tt http://www.masterlens.org} for a catalogue.}.
+However, this number is expected to increase to several thousand over the next
+ten years as new surveys, both
 ground-based\footnote{http://pan-starrs.ifa.hawaii.edu}$^{\rm,}$\footnote{http://www.darkenergysurvey.org}
-and space-based\footnote{http://www.euclid-ec.org} -- together with a
-community of citizen-science volunteers examining the image data for
+and space-based\footnote{http://www.euclid-ec.org} -- together with a community
+of citizen-science volunteers examining the image data for
 candidates\footnote{{\tt http://spacewarps.org}} -- come online.
 
-Since lensing depends only on gravity, strong lenses offer a
-unique window onto dark matter and cosmology \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}. However, 
-extracting dark matter properties or cosmological constraints from these lensing data will require sophisticated modelling.
-In particular, with an unprecedented data set imminent, it is prudent to look again at systematic errors in the lens models to determine what quality of data (in particular complementary data from stellar/gas kinematics, lens time delays and/or stellar mass constraints) are required to address problems of interest.
-It is towards that goal that this present work is directed.
-
-To see why lens modelling details are of crucial importance, let us recall the
-essential quantities that appear in lensing.  First we have the
-distances. Let $D_L$, $D_S$, $D_{LS}$ be the angular-diameter
-distances to the lens, source, and from lens to source; these are all proportional to $c/H_0$ (where $c$ is the speed of light in vacuo, and $H_0$ the Hubble constant), with additional terms that depend on the particular choice of cosmology \citep[e.g.][]{1999coph.book.....P}.
-Typically:
+Since lensing depends only on gravity, strong lenses offer a unique window onto
+dark matter and cosmology \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}.
+However, extracting dark matter properties or cosmological constraints from
+these lensing data will require sophisticated modelling. In particular, with an
+unprecedented data set imminent, it is prudent to look again at systematic
+errors in the lens models to determine what quality of data (in particular
+complementary data from stellar/gas kinematics, lens time delays and/or stellar
+mass constraints) are required to address problems of interest. It is towards
+that goal that this present work is directed.
+
+To see why lens modelling details are of crucial importance, let us
+recall the essential quantities that appear in lensing.\footnote{These
+  quantities are defined more precisely in \S\ref{sec:lensing_basic}.}
+First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
+angular-diameter distances to the lens, source, and from lens to
+source; these are all proportional to $c/H_0$ but have factors
+that depend on the particular choice of cosmology.  Typically:
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 For multiple images, the sky-projected density must exceed the critical
-density \citep[e.g.][]{1992grle.book.....S}:
-
-\begin{equation}
-\Sigma_{\rm crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
-\end{equation}
+density
+%
+\begin{equation}
+\Sigma_\mathrm{crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
+\end{equation}
+%
 in some region.  The separation between the lensed images is of order
@@
 the mass by:
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$) is the gravitational radius. If the source is a
@@
 will be present where:
+%
 \begin{equation}
@@
 \end{equation}
-So in principle, one can not only measure the mass of the lens, one
-can use the dependence on the cosmology-dependent $D$ factors to
-extract the cosmological model and all its parameters.
-\cite{1937ApJ....86..217Z} drew attention to the former, and
-\cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the latter,
-all long before lenses were discovered.  The difficulty with actually doing this, however, became
-apparent soon after the discovery of the first lens by
-\cite{1979Natur.279..381W}.  In the first ever paper on lens
-modelling, \cite{1981ApJ...244..736Y} found that many plausible mass
-distributions could reproduce the data.
-
-\cite{1981ApJ...244..736Y} were remarkably prescient about the
-subsequent development of lens modelling.  First, they introduced the
-technique of choosing a parametric form for the lensing mass and then
-fitting for the parameters, which is still the most common strategy
-\citep[see for example][]{2010GReGr..42.2151K,2011A&ARv..19...47K}.
-Second, they pointed out the non-uniqueness of lens models -- lensing
-degeneracies.  Third, they suggested combining lensing data with
-stellar kinematics and X-rays, to reduce the effect of the
-degeneracies.  Later work, as well as following up these suggestions,
-has introduced some further new ideas.  Four of these are important for the present
-work:
+%
+So in principle, one can not only measure the mass of the lens, one can use the
+dependence on the cosmology-dependent $D$ factors to extract the cosmological
+model and all its parameters.  \cite{1937ApJ....86..217Z} drew attention to the
+former, and \cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the
+latter, all long before lenses were discovered.  The difficulty with actually
+doing this, however, became apparent soon after the discovery of the first lens
+by \cite{1979Natur.279..381W}.  In the first ever paper on lens modelling,
+\cite{1981ApJ...244..736Y} found that many plausible mass distributions could
+reproduce the data.
+
+\cite{1981ApJ...244..736Y} were remarkably prescient about the subsequent
+development of lens modelling.  First, they introduced the technique of
+choosing a parametric form for the lensing mass and then fitting for the
+parameters, which is still the most common strategy \citep[see for
+example][]{2010GReGr..42.2151K,2011A&ARv..19...47K}.  Second, they pointed out
+the non-uniqueness of lens models -- lensing degeneracies.  Third, they
+suggested combining lensing data with stellar kinematics and X-rays, to reduce
+the effect of the degeneracies.  Later work, as well as following up these
+suggestions, has introduced some further new ideas.  Four of these are
+important for the present work:
+%
 \begin{enumerate}
-\item {\bf Free-form modelling:} In `free-form' or non-parametric modelling, there is no specified parametric form for
-  the mass distribution.  There are still assumptions (or priors) on
-  the mass distribution, such as smoothness or being centrally
+\item {\bf Free-form modelling:} 
+    In `free-form' or non-parametric modelling, there is no specified
+    parametric form for the mass distribution.  There are still assumptions (or
+    priors) on the mass distribution, such as smoothness or being centrally
     concentrated
     \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2009A&A...500..681M,2010ApJ...723.1678C}
-  but these are much less restrictive than parametric forms (\cite{2006MNRAS.367.1209L} implemented a particularly elegant prior, which is that the mass distribution must be non-negative and no
-  extra images are produced). To be concrete, we define from here on:
+    but these are much less restrictive than parametric forms
+    (\cite{2006MNRAS.367.1209L} implemented a particularly elegant prior, which
+    is that the mass distribution must be non-negative and no extra images are
+    produced). To be concrete, we define from here on:
 
@@
 
-  Being under-constrained, it is then {\it necessary} to explore model degeneracies rather than find a single `best-fit' solution. Free-form models are more commonly used with
-  cluster lenses \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S}, but
-  can be used with galaxy lenses as well, where their less restrictive
-  assumptions can be important.  For example, in time-delay galaxy
-  lenses, parametric models have historically led to tension with independent measures of the Hubble parameter
-  $H_0$ \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are resolved once the less restrictive assumptions of free-form models are permitted \citep{2007ApJ...667..645R}.
-\item Model ensembles, exploring a diverse range of possible mass
-  distributions that nonetheless all fit the data, are a way of
-  combating the non-uniqueness of models.  Such ensembles are
-  possible in parametric models \citep{1999AJ....118...14B} but are
-  more common in free-form models
+  Being under-constrained, it is then {\it necessary} to explore model
+  degeneracies rather than find a single `best-fit' solution. Free-form models
+  are more commonly used with cluster lenses
+  \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S},
+  but can be used with galaxy lenses as well, where their less restrictive
+  assumptions can be important.  For example, in time-delay galaxy lenses,
+  parametric models have historically led to tension with independent measures
+  of the Hubble parameter $H_0$
+  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are resolved
+  once the less restrictive assumptions of free-form models are permitted
+  \citep{2007ApJ...667..645R}.  \item Model ensembles, exploring a diverse
+  range of possible mass distributions that nonetheless all fit the data,
+  are a way of combating the non-uniqueness of models.  Such ensembles are
+  possible in parametric models \citep{1999AJ....118...14B} but are more
+  common in free-form models
   \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.
-\item {\bf Stellar kinematic constraints:} This was first suggested by \citet{2002MNRAS.337L...6T} as a means to break lensing degeneracies and determine cosmological parameters.
-This works because stellar kinematics can provide an independent estimate of the Einstein radius, via the virial theorem:
-%
-\begin{equation}
-  \frac{\langle v^2_{\rm los}\rangle}{c^2} \approx
+
+\item {\bf Stellar kinematic constraints:} This was first suggested by
+    \citet{2002MNRAS.337L...6T} as a means to break lensing degeneracies and
+    determine cosmological parameters. This works because stellar kinematics
+    can provide an independent estimate of the Einstein radius, via the virial
+    theorem:
+%
+\begin{equation}
+  \frac{\langle v^2_\mathrm{los}\rangle}{c^2} \approx
   \frac{\theta_E}{6\pi} \frac{D_S}{D_{LS}}
@@
 \end{equation}
- where $\langle v^2_{\rm los}\rangle$ is the projected stellar velocity dispersion, and the above relation becomes exact for isothermal lenses.  The use of
-  two-dimensional kinematics by \cite{2011MNRAS.415.2215B} is
-  especially interesting.
-\item {\bf Stellar mass constraints:} The stellar mass in a lens can be inferred from photometry and
-  compared with the total mass
-  \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
-  Since the inferred stellar mass depends on the assumed IMF,
-  lenses in which stellar mass dominates can be used to derive upper
-  bounds on the stellar $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds
-  on stellar $M/L$ have also been claimed \citep{2013MNRAS.428.3183D}
-  but these require upper-bound assumptions about the dark-matter
-  profile. \hilight{JR. I feel like we need more citations here and throughout. We must be skipping over an Armada of literature.}
-\item {\bf Testing modelling strategies:} Using mock data to see how well a given model can recover
-  simulated lenses is increasingly being recognised as essential.  Simple
-  blind tests have appeared in earlier work \citep[for example, Figure
-    2 in][]{2000AJ....119..439W}, but more recently, tests against
-  dynamically simulated galaxies or clusters are favoured
+%
+where $\langle v^2_\mathrm{los}\rangle$ is the projected stellar velocity
+dispersion, and the above relation becomes exact for isothermal lenses.  The
+use of two-dimensional kinematics by \cite{2011MNRAS.415.2215B} is especially
+interesting.
+
+\item {\bf Stellar mass constraints:} The stellar mass in a lens can be
+    inferred from photometry and compared with the total mass
+    \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
+    the inferred stellar mass depends on the assumed IMF, lenses in which
+    stellar mass dominates can be used to derive upper bounds on the stellar
+    $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds on stellar $M/L$ have also
+    been claimed \citep{2013MNRAS.428.3183D} but these require upper-bound
+    assumptions about the dark-matter profile. \hilight{JR. I feel like we need
+    more citations here and throughout. We must be skipping over an Armada of
+literature.}
+
+\item {\bf Testing modelling strategies:} Using mock data to see how well a
+    given model can recover simulated lenses is increasingly being recognised
+    as essential.  Simple blind tests have appeared in earlier work \citep[for
+    example, Figure 2 in][]{2000AJ....119..439W}, but more recently, tests
+    against dynamically simulated galaxies or clusters are favoured
     \citep{2007ApJ...667..645R,2007MNRAS.380.1729L,2009A&A...500..681M,2009MNRAS.393.1114B,2010ApJ...723.1678C}.
@@
 
-There are two further key modelling ideas in the literature that we will not touch upon in this present work: to use
-X-ray intensity and temperature profiles as a mass constraint
-\citep[e.g.][]{2013ApJ...765...25N}; and to model
-multiple lenses simultaneously, with one or more cosmological
-parameters variable but shared between the lenses. This latter strategy has
-been used to constrain $H_0$ from time delay lenses 
-\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P}.
-(In principle, cosmological parameters can be constrained even from a
-single lens if the data are good enough. Some recent models have attempted this starting from a prior
-based on the Cosmic Microwave Background (CMB) radiation \citep{2010Sci...329..924J,2013arXiv1306.4732S}.)
-
-In this paper, we use a new program -- \Glass\ (Gravitational Lensing AnalysiS Software) -- to determine what
-combination of lensing, stellar mass, and stellar kinematic
-constraints best constrain the projected mass profile and shape of several
-gravitational lens produced from mock data.  The compute-intensive core of \Glass\ is a
-parallel implementation of the high-dimensional sampling algorithm
-from \cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has
-extensible code (in software terminology, a framework) in Python,
-encoding the lens equation, a basis and priors for the mass
+There are three further key modelling ideas in the literature that we will not
+touch upon in this present work: to use X-ray intensity and temperature
+profiles as a mass constraint \citep[e.g.][]{2013ApJ...765...25N}; and to model
+multiple lenses simultaneously, with one or more cosmological parameters
+variable but shared between the lenses. This latter strategy has been used to
+constrain $H_0$ from time delay lenses
+\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P} and
+recently the cosmological parameters $\Omega$ as well
+\citep{2014MNRAS.437..600S}.  Third, it is in principle possible to estimate
+the $\Omega$ parameters even from a single lens, if there are lensed sources at
+multiple redshifts \citep{2014MNRAS.437.2461L} or by using a strong prior
+\citep{2010Sci...329..924J,2013arXiv1306.4732S}.
+
+In this paper, we use a new program -- \Glass\ (Gravitational Lensing AnalysiS
+Software) -- to determine what combination of lensing, stellar mass, and
+stellar kinematic constraints best constrain the projected mass profile and
+shape of several gravitational lens produced from mock data.  The
+compute-intensive core of \Glass\ is a parallel implementation of the
+high-dimensional sampling algorithm from \cite{2012MNRAS.425.3077L}.  Around
+that core, \Glass\ has extensible code (in software terminology, a framework)
+in Python, encoding the lens equation, a basis and priors for the mass
 distribution, and various post-processing and visualisation modules.  \Glass\
-is described in \secref{sec:glass}.  In \secref{sec:theory}, we
-review the key elements of lensing theory, stellar population synthesis, and
-stellar dynamics we will need.
-In \secref{sec:mockdata}, we describe our mock data.
-In \secref{sec:results}, we present our results from applying \Glass\ to these mock data.
-Finally, in \S\ref{sec:conclusions} we present our conclusions.
+is described in \secref{sec:glass}.  In \secref{sec:theory}, we review the key
+elements of lensing theory, stellar population synthesis, and stellar dynamics
+we will need. In \secref{sec:mockdata}, we describe our mock data. In
+\secref{sec:results}, we present our results from applying \Glass\ to these
+mock data. Finally, in \secref{sec:conclusions} we present our conclusions.
 
@@
 
-We follow \cite{1986ApJ...310..568B} with minor differences in notation.
+In the following summary, we follow \cite{1986ApJ...310..568B} with
+some differences in notation, in particular putting back the
+speed of light $c$ and the gravitational constant $G$.
 
@@
 density $\Sigma$ which diverts the path of a photon instantaneously
-through the bending angle $\vec\alpha$.  The $D$ factors, as in the previous section, are angular
-diameter distances, which depend on the particular choice of cosmological
-parameters $\Omega$:
+through the bending angle $\vec\alpha$.  The $D$ factors, as in the
+previous section, are angular diameter distances, which depend on the
+cosmological density-parameters $\Omega$, the redshifts $z_L,z_S$ of
+the lens and the source, and the Hubble parameter $H_0$, thus
+%
 \begin{equation}
@@
 %
-and $D_L \equiv D_{0,L}$, $D_S \equiv D_{0,S}$.
-One way to understand the lens equation is via Fermat's principle. We
-can think of light as travelling only along extremum paths where
-lensed images occur. Such paths occur at
-the extrema of the photon {\it arrival time\/} $t(\vec\theta)$
-that depends on the geometric path the photon takes and the general
-relativistic gravitational time dilation due to a thin lens at
-redshift $z_L$:
+and $D_L \equiv D_{0,L}$, $D_S \equiv D_{0,S}$.  One way to understand the lens
+equation is via Fermat's principle. We can think of light as travelling only
+along extremum paths where lensed images occur.  Such paths occur at the
+extrema of the photon {\it arrival time} $t(\vec\theta)$ that depends on the
+geometric path the photon takes and the general relativistic gravitational time
+dilation due to a thin lens at redshift $z_L$:
+%
 \begin{equation}
@@
 \end{equation}
-We can simplify the above equation by introducing a dimensionless time $\tau$ and density $\kappa$:
-
-\begin{equation}
-\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \,\,\,;\,\,\, \kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
-\end{equation}
+%
+We can simplify the above equation by introducing a dimensionless time $\tau$
+and density $\kappa$: 
+%
+\begin{equation}
+\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \quad ; \quad \kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
+\end{equation}
+%
 and hence rewrite \eqnref{full arrival time} as:
+%
 \begin{equation}
@@
 \end{equation}
-The scaled arrival time $\tau$ is like a solid angle. It is of order
-the area (in steradians) of the full lensing system. The expression
-$|\vec\theta - \vec\beta|^2$ is of order the image-separation
-squared, and the other terms are of similar size.  For this reason, is
-convenient to measure $\tau$ in arcsec$^{2}$.
-
-Lensing observations provide information only at $\vec\theta$ where
-there are images.  Hence, the arrival-time surface $\tau(\vec\theta)$
-is not itself observable.  Its usefulness lies in that observables can
-be derived from it.  An image observed at $\vec\theta_1$ implies
-that $\nabla\tau(\vec\theta_1)=0$.  A measurement of time delays
-between images at $\theta_1$ and $\theta_2$ implies that
-$t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both these
-types of observations give contraints that are linear in $\kappa$ and
+%
+The scaled arrival time $\tau$ is like a solid angle. It is of order the area
+(in steradians) of the full lensing system. The expression $|\vec\theta -
+\vec\beta|^2$ is of order the image-separation squared, and the other terms are
+of similar size.  For this reason, is convenient to measure $\tau$ in
+arcsec$^{2}$.
+
+Lensing observations provide information only at $\vec\theta$ where there are
+images.  Hence, the arrival-time surface $\tau(\vec\theta)$ is not itself
+observable.  Its usefulness lies in that observables can be derived from it.
+An image observed at $\vec\theta_1$ implies that $\nabla\tau(\vec\theta_1)=0$.
+A measurement of time delays between images at $\theta_1$ and $\theta_2$
+implies that $t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both
+these types of observations give contraints that are linear in $\kappa$ and
 $\vec\beta$.
@@
 so-called mass-sheet degeneracy, which is that image positions remain invariant
-if $\tau(\vec\theta)$ is multiplied by an
-arbitrary constant.  This corresponds to rescaling the surface density at the images $\kappa(\vec\theta)$. In fact there are infinitely many degeneracies
-\citep{2000AJ....120.1654S} because any transformation of the arrival-time
-surface away from the images has no effect on the lensing observables.  In
-particular, there are degeneracies that involve the shape of the mass
-distribution \citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies
-tend to be suppressed if there are sources at very different redshifts or
-`redshift contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because
-the presence of different factors of $D_S/D_{LS}$ in the image plane makes it
-more difficult to change the mass distribution and the arrival-time surface
-without affecting the lensing observables.  But degeneracies are still present
-with multiple source redshifts.  \citep{2008MNRAS.386..307L}.
+if $\tau(\vec\theta)$ is multiplied by an arbitrary constant.  This corresponds
+to rescaling the surface density at the images $\kappa(\vec\theta)$. In fact
+there are infinitely many degeneracies \citep{2000AJ....120.1654S} because any
+transformation of the arrival-time surface away from the images has no effect
+on the lensing observables.  In particular, there are degeneracies that involve
+the shape of the mass distribution
+\citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies tend to be
+suppressed if there are sources at very different redshifts or `redshift
+contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because the presence
+of different factors of $D_S/D_{LS}$ in the image plane makes it more difficult
+to change the mass distribution and the arrival-time surface without affecting
+the lensing observables.  But degeneracies are still present with multiple
+source redshifts.  \citep{2008MNRAS.386..307L}.
 
@@
 
-For many galaxy lenses, the gravitational potential in the inner
-region is dominated by the stellar mass.  Steller mass can be
-estimated by combining photometry and colours with models of the
-stellar populations.  Such estimates are reasonably robust, even if
-the star-formation history is very uncertain: given a
-stellar-population model \citep[such as][]{2003MNRAS.344.1000B} and an
-initial mass function (IMF), the stellar mass can be inferred to 0.1
-to 0.2 dex using just two photometric bands \citep[see e.g., Figure~1
-  in][]{2008MNRAS.383..857F}.  By comparing the lensing-mass and
-stellar-mass profiles in elliptical galaxies, it is possible to
-extract the radial dependence of the baryonic vs dark-matter fraction
-\citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
-
-The major uncertainty at present in the stellar mass is probably the
-IMF.  In the lensing galaxy of the Einstein Cross, the IMF cannot be
-much more bottom-heavy than \cite{2003PASP..115..763C}, because
-otherwise the stellar mass would exceed the lensing mass
-\cite{2010MNRAS.409L..30F}.  More massive galaxies, however, do appear
-to have more of their stellar mass in low-mass stars.  This is
-indicated by molecular spectral features characteristic of low mass
-stars
+For many galaxy lenses, the gravitational potential in the inner region is
+dominated by the stellar mass.  Steller mass can be estimated by combining
+photometry and colours with models of the stellar populations.  Such estimates
+are reasonably robust, even if the star-formation history is very uncertain:
+given a stellar-population model \citep[such as][]{2003MNRAS.344.1000B} and an
+initial mass function (IMF), the stellar mass can be inferred to 0.1 to 0.2 dex
+using just two photometric bands \citep[see e.g., Figure~1 in][]{2008MNRAS.383..857F}.
+By comparing the lensing-mass and stellar-mass profiles in elliptical galaxies,
+it is possible to extract the radial dependence of the baryonic vs dark-matter
+fraction \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
+
+The major uncertainty at present in the stellar mass is probably the IMF.  In
+the lensing galaxy of the Einstein Cross, the IMF cannot be much more
+bottom-heavy than \cite{2003PASP..115..763C}, because otherwise the stellar
+mass would exceed the lensing mass \cite{2010MNRAS.409L..30F}.  More massive
+galaxies, however, do appear to have more of their stellar mass in low-mass
+stars.  This is indicated by molecular spectral features characteristic of low
+mass stars
 \citep{2004ApJ...614L.101C,2012ApJ...747...69C,2013MNRAS.429L..15F}.
@@
 mass.  Accordingly, \Glass\ allows a constraint of the form
-\begin{equation} 
-M(\vec\theta) \geq M_{\rm stel}(\vec\theta)
-\end{equation} 
+%
+\begin{equation} 
+M(\vec\theta) \geq M_\mathrm{stel}(\vec\theta)
+\end{equation} 
+%
 on the total mass.
@@
 \end{equation}
-\begin{equation} 
-\sigma_r^2(r) = \frac{r^{-2\beta}}{\nu}\int_r^\infty r'^{2\beta} \nu \frac{GM_{\rm 3D}(r')}{r'^2}dr'
-\end{equation} 
+%
+\begin{equation} 
+\sigma_r^2(r) = \frac{r^{-2\beta}}{\nu}\int_r^\infty r'^{2\beta} \nu \frac{G\Mddd(r')}{r'^2}dr'
+\end{equation} 
+%
 where $\sigma_p$ is the projected velocity dispersion of the stars as a
@@
 \sigma_t^2/2\sigma_r^2 = \mathrm{const.}$ is the velocity anisotropy (here
-assumed to be constant, and not to be confused with $\vec\beta(\vec\theta)$ from
-lensing); $G$ is Newton's gravitational constant; and $M_{\rm 3D}(r)$ is
-the mass profile that we would like to measure. By convension, we always write $R$ 
+assumed to be constant, and not to be confused with $\vec\beta(\vec\theta)$
+from lensing); $G$ is Newton's gravitational constant; and $\Mddd(r)$ is the
+mass profile that we would like to measure. By convention, we always write $R$
 for a projected radius, and $r$ for a 3D radius.
@@
 spherical symmetry, we have a degeneracy between the enclosed mass profile
-$M_{\rm 3D}(r)$ and the velocity anisotropy $\beta(r)$. This can be understood
+$\Mddd(r)$ and the velocity anisotropy $\beta(r)$. This can be understood
 intuitively since $\beta(r)$ measures the relative importance of radial versus
@@
 $r\rightarrow \infty$ \citep[e.g.][]{2002MNRAS.330..778W}. It can also be
-estimated if an independent measure of $M_{\rm 3D}(r)$ is available -- for example
+estimated if an independent measure of $\Mddd(r)$ is available -- for example
 coming from strong lensing.
 
-While $M_{\rm 3D}(r)$ is difficult to measure from stellar kinematics alone, the mass within the half light radius is robustly recovered \citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A} since stellar systems in dynamic quasi-equilibrium obey the virial theorem (equation \ref{eqn:virial}).
-This means that stellar kinematics can break the steepness degeneracy if $r_{1/2} \neq r_E$, where $r_E = D_L \theta_E$ is the physical Einstein radius.
-We test this expectation in \S\ref{sec:results}.
+While $\Mddd(r)$ is difficult to measure from stellar kinematics alone, the
+mass within the half light radius is robustly recovered
+\citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}
+since stellar systems in dynamic quasi-equilibrium obey the virial theorem
+(equation \ref{eqn:virial}). This means that stellar kinematics can break the
+steepness degeneracy if $r_{1/2} \neq r_E$, where $r_E = D_L \theta_E$ is the
+physical Einstein radius. We test this expectation in \secref{sec:results}.
 
 We describe our numerical solution of \eqnref{eqn:sphericaljeans} in
-\S\ref{sec:glasskinematics} and present tests applied to mock data in
-\S\ref{sec:results}.
+\secref{sec:glasskinematics} and present tests applied to mock data in
+\secref{sec:results}.
 
@@
 
-\Glass\ is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
-\PixeLens\ but completely rewritten in Python and C. 
-The most compute intensive
-portion was written in C but Python was chosen because of its flexibility as a 
-language and for its large scientific library support. The flexibility allows 
-\Glass\ to have quite sophisticated behavior while at the same time simplifying the 
-user experience and reducing the overall development time. One of the striking
-features is that the input file to \Glass\ is itself a Python program.
-Understanding Python is not necessary for the most basic use, but this allows
-a user to build complex analysis of a model directly into the input file. \Glass\
-may also be used as an external library to other Python programs.  The software
-is freely available for download or from the author%
-%
-\footnote{http://www.jpcoles.com.}.
+\Glass\ is the Gravitational Lensing AnalysiS Software. It extends and develops
+some of the concepts from the free form modelling tool \PixeLens\
+\citep{Saha2004,2008ApJ...679...17C}, but with all new code.  The most compute
+intensive portion was written in C but Python was chosen because of its
+flexibility as a language and for its large scientific library support. The
+flexibility allows \Glass\ to have quite sophisticated behavior while at the
+same time simplifying the user experience and reducing the overall development
+time. One of the striking features is that the input file to \Glass\ is itself
+a Python program.  Understanding Python is not necessary for the most basic
+use, but this allows a user to build complex analysis of a model directly into
+the input file. \Glass\ may furthermore be used as an external library to other
+Python programs.  {\it The software is freely available for download or from
+the first author.}%
+%
+\footnote{http://www.jpcoles.com}
 
@@
 %
-Each prior is a simple function that adds linear constraints that operate on either
-a single lens object or the entire ensemble of objects. \Glass\ comes with a number
-of useful priors, the default ones will be described later, but a user can
-write their own directly in the input file, or by modifying the source code.
+Each prior is a simple function that adds linear constraints that operate on
+either a single lens object or the entire ensemble of objects. \Glass\ comes
+with a number of useful priors, the default ones will be described later, but a
+user can write their own directly in the input file, or by modifying the source
+code.
 %
@@
 %
-\Glass\ currently describes the lens mass as a collection of pixels, but the code
-has been designed to support alternative methods. In particular, there are future
-plans to develop a module using Bessel functions. This will require a new set of 
-priors that operate on these functions.
+\Glass\ currently describes the lens mass as a collection of pixels, but the
+code has been designed to support alternative methods. In particular, there are
+future plans to develop a module using Bessel functions. This will require a
+new set of priors that operate on these functions.
 %
@@
 %
-Once \Glass\ has generated an ensemble of models given the linear constraints, any number
-of post processing functions can be applied. Not only can these functions be used to
-derive new quantities from the mass models, they can also be used as a filter to 
-accept or reject a model based on some non-linear constraint. The plotting functions
-within \Glass\ will correctly display models that have been accepted or rejected.
+Once \Glass\ has generated an ensemble of models given the linear constraints,
+any number of post processing functions can be applied. Not only can these
+functions be used to derive new quantities from the mass models, they can also
+be used as a filter to accept or reject a model based on some non-linear
+constraint. The plotting functions within \Glass\ will correctly display models
+that have been accepted or rejected.
 %
@@
 where the mass profile may rise steeply, the center pixel uses a higher
-resolution. This allows the density to increase smoothly but still allow for
-a large degree of freedom within the inner region without allowing the density
-to be arbitrarily high. 
+resolution. This allows the density to increase smoothly but still allow for a
+large degree of freedom within the inner region without allowing the density to
+be arbitrarily high. 
 %
@@
 %
-\PixeLens\ only allows for a shear term to be added to the potential (as shown
-later in \eqnref{shear}) to account for mass external to the modelled region. This
-is useful to capture the gross effects of a distant neighbour. \Glass\ also
-has a shear term but additionally allows for analytic potentials to
-be included. This can be used to model substructure or multiple neighbours close
-to the main lens. The substructure may have only a small effect if the lens is
-a single galaxy, but if the lens is a group then a potential can be added for
-each of the galaxies. A few standard functions are already included in \Glass\
-including those for a point mass, a power law distribution, or an isothermal (a
-particular case of the power law).
+A shear term can be added to the potential, as shown later in \eqnref{shear},
+to account for mass external to the modelled region. This is useful to capture
+the gross effects of a distant neighbour. \Glass\ also allows further analytic
+potential components to be included. This can be used to model substructure or
+multiple neighbours close to the main lens. The substructure may have only a
+small effect if the lens is a single galaxy, but if the lens is a group then a
+potential can be added for each of the galaxies. A few standard functions are
+already included in \Glass\ including those for a point mass, a power law
+distribution, or an isothermal (a particular case of the power law).
 %
@@
 linear space that represents the modelling solution space. This algorithm was
-described and tested in \cite{2012MNRAS.425.3077L}; it is 
-multi-threaded allowing it to run efficiently on many-cored machines.
+described and tested in \cite{2012MNRAS.425.3077L}; it is multi-threaded
+allowing it to run efficiently on many-cored machines.
 
@@
 $N$-body simulation file. To load the simulation data, \Glass\ relies on the
-\textsc{Pynbody} library \citep{pynbody} and can thus load any file supported by that package.
+\textsc{Pynbody} library \citep{pynbody} and can thus load any file supported
+by that package.
 
 \subsection{Discrete models}\label{sec:discrete}
-For this paper, we will restrict ourselves to using the pixelated basis set that
-has been employed in previous work and is implemented in \PixeLens. Here we
-will briefly review the main ideas. The algorithm for generating models in
+For this paper, we will restrict ourselves to using a pixelated basis set that
+has been employed in previous work. The algorithm for generating models in
 \Glass\ samples a convex polytope in a high dimensional space whose interior
 points are solutions to the lens equation and satisfy other physically
-motivated linear priors (the sampling algorithm in \Glass\ is \emph{not} the same as
-employed in \PixeLens).  We therefore formulate all of our equations as
+motivated linear priors.  We therefore formulate all of our equations as
 equations linear in the unknowns. We describe the density distribution $\kappa$
@@
 %
-where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
-over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
-We can find the discretized lens equation by simply taking the gradient of the
-above equations.
+where the sum runs over all the pixels and $Q_n$ is the integral of the
+logarithm over pixel $n$. The exact form for $Q$ is described in \appref{Q
+derivation}.  We can find the discretized lens equation by simply taking the
+gradient of the above equations.
 
 The pixels only cover a finite circular area with physical radius $\Rmap$ and
-pixel radius $\Rpix$ with the central cell centered on the lensing galaxy. To account for any global
-shearing outside this region from, e.g., a neighboring galaxy, we also add to
-\eqnref{discrete potential} two shearing terms
+pixel radius $\Rpix$ with the central cell centered on the lensing galaxy. To
+account for any global shearing outside this region from, e.g., a neighboring
+galaxy, we also add to \eqnref{discrete potential} two shearing terms
 %
@@
 %
-We can continue adding terms to account for other potentials. For instance,
-we may want to impose a base potential over the field, or add potentials
-from the presence of other galaxies in the field. \Glass\
-already includes potentials for a point mass or an exponential form, but custom
-potentials are straightforward to add and can be included directly in the input file.
-If the stellar density $\kappa_s$ has been estimated we can use this as a lower bound
+We can continue adding terms to account for other potentials. For instance, we
+may want to impose a base potential over the field, or add potentials from the
+presence of other galaxies in the field. \Glass\ already includes potentials
+for a point mass or an exponential form, but custom potentials are
+straightforward to add and can be included directly in the input file.  If the
+stellar density $\kappa_s$ has been estimated we can use this as a lower bound
 where the stellar potential is a known constant of the form \eqnref{discrete
-potential}, e.g., $\kappa_n = \kappa_{\mathrm{dm},n} + \kappa_{s,n}$ for a two-component model.
-
-Unfortunately, the lens equation and the arrival times alone are not enough to form a
-closed volume in the solution space. We have not imposed any strong constraints
-on the density even so much as to ensure that it is non-negative everywhere. We
-must therefore provide additional linear constraints so that we only sample
-physical models. The explicit implementation for these priors has been
-explained in \cite{2008ApJ...679...17C}, but can be summarised as
+potential}, e.g., $\kappa_n = \kappa_{\mathrm{dm},n} + \kappa_{s,n}$ for a
+two-component model.
+
+Unfortunately, the lens equation and the arrival times alone are not enough to
+form a closed volume in the solution space. We have not imposed any strong
+constraints on the density even so much as to ensure that it is non-negative
+everywhere. We must therefore provide additional linear constraints so that we
+only sample physical models. The explicit implementation for these priors has
+been explained in \cite{2008ApJ...679...17C}, but can be summarised as
+%
 \begin{enumerate}
@@
 \item Image parity is enforced.
-\item The density is radially symmetric. (Optional)
+\item The density is inversion symmetric. (Optional)
 \end{enumerate}
@@
 In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
-\vec\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
-solution space polytope. Using the MCMC sampling strategy described in \cite{2012MNRAS.425.3077L}
-we uniformly sample this space. Collectively, the sampled models are referred
-to as an ensemble $\E = \{\M_i\}$, where we usually generate $|\E| \sim 1000$ models.
+\vec\beta, \gamma_1, \gamma_2)$. A single model represents a single point in
+the solution space polytope. Using the MCMC sampling strategy described in
+\cite{2012MNRAS.425.3077L} we uniformly sample this space. Collectively, the
+sampled models are referred to as an ensemble $\E = \{\M_i\}$, where we usually
+generate $|\E| \sim 1000$ models.
 
@@
 the source plane $\vec\beta_i$ is within a user specified
-$\eps_\mathrm{accept}$ of $\vec\beta$ then $\vec\theta_i$ is 
-accepted and further refined using a root finding algorithm until the distance
-to $\vec\beta$ is nearly zero. If multiple points converge to an
+$\eps_\mathrm{accept}$ of $\vec\beta$ then $\vec\theta_i$ is accepted and
+further refined using a root finding algorithm until the distance to
+$\vec\beta$ is nearly zero. If multiple points converge to an
 $\eps_\mathrm{root}$ of each other then only one point is taken.  Care must be
@@
 extremely powerful. We find that our gradient prior in \Glass\ (see
-\S\ref{sec:discrete}), performs much of the same function as
+\secref{sec:discrete}), performs much of the same function as
 \citeauthor{2006MNRAS.367.1209L}'s null-space prior, but some models can still
@@
 \subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
-Similarly to the null-space constraint (\S\ref{sec:glassextraimages}), stellar
+Similarly to the null-space constraint (\secref{sec:glassextraimages}), stellar
 kinematic constraints constitute a non-linear prior on the mass map and must be
 applied in post-processing. We sweep through the model ensemble performing an
-Abel deprojection to determine $M_{\rm 3D}(r)$ from the projected surface density $\Sigma(R)$
-assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
-
+Abel deprojection to determine $\Mddd(r)$ from the projected surface density
+$\Sigma(R)$ assuming spherical symmetry
+\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}: 
+%
 \begin{eqnarray} 
-M_{\rm 3D}(r) & = & M(r) - 4r^2 \int_0^{\frac{\pi}{2}} \Sigma\left(x\right) \left(\frac{1}{\cth^2} \right. \nonumber \\ 
-& & \left. - \frac{\sth}{\cth^3} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
+    \Mddd(r) & = & M(<r) - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left(\frac{1}{\cth[2]} \right. \nonumber \\ 
+    & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
 \end{eqnarray}
-where $M(r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
+%
+where $M(<r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
 
@@
 
-We use the deprojected mass to numerically solve equation
-\ref{eqn:sphericaljeans} for constant $\beta(r)$, assuming either $\beta(r) =
-1$ or $\beta(r) = 0$ at all radii to bracket the two extremum situations. Where
-the data are good enough, these two may be distinguished giving dynamical
-information about $\beta(r)$. In more typical situations, however, we seek to
-simply marginalise over the effect of $\beta(r)$, using the stellar kinematics
-as a robust measure of $M_{\rm 3D}(r_{1/2})$ (see \S\ref{sec:kinematics}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We use the deprojected mass to numerically solve \eqnref{eqn:sphericaljeans}
+for constant $\beta(r)$, assuming either $\beta(r) = 1$ or $\beta(r) = 0$ at
+all radii to bracket the two extremum situations. Where the data are good
+enough, these two may be distinguished giving dynamical information about
+$\beta(r)$. In more typical situations, however, we seek to simply marginalise
+over the effect of $\beta(r)$, using the stellar kinematics as a robust measure
+of $\Mddd(r_{1/2})$ (see \secref{sec:kinematics}).
 
@@
 We generate four two-component mock galaxies, where the dark matter and stellar
-profiles are allowed to be both steep and shallow.  
-%The enclosed mass in all cases
-%is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. 
-The enclosed mass of the stars and dark matter are both fixed to be 
-$M_{*,\mathrm{DM}} = 1.8 \times 10^{10}$\,M$_\odot$ at the stellar scale radius 
-$a_* = 2$\,kpc, such that the stars and dark matter contribute equally to the total
-mass at $a_*$. The dark matter scale length is fixed for all models at $a_\mathrm{DM}
-= 20$\,kpc.
-These
-values were chosen to closely resemble the lensing galaxy B1115 \citep{1980Natur.285..641W}. We place the galaxy at
-a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
-where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
-critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
+profiles are allowed to be both steep and shallow.  The enclosed mass of the
+stars and dark matter are both fixed to be $M_{*,\mathrm{DM}} = 1.8 \times
+10^{10}$\,M$_\odot$ at the stellar scale radius $a_* = 2$\,kpc, such that the
+stars and dark matter contribute equally to the total mass at $a_*$. The dark
+matter scale length is fixed for all models at $a_\mathrm{DM} = 20$\,kpc.
+These values were chosen to closely resemble the lensing galaxy PG1115+080
+\citep{1980Natur.285..641W}. We place the galaxy at a redshift of $z_L = 0.31$
+for lensing.  Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr,
+$\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The critical density is
+$\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
 
@@
 \begin{equation} 
-  \rho(m) = \frac{M}{4\pi a^3}(3-\gamma){(m/a)^{-\gamma}(1 + m/a)^{\gamma-4}} 
+  \rho(\tilde r) = \frac{M}{4\pi a^3}(3-\gamma){(\tilde r/a)^{-\gamma}(1 + \tilde r/a)^{\gamma-4}} 
   \label{Dehnen profile} 
@@
 %
-where $a$ is the component scale radius mentioned in \tabref{mock galaxy params};
-$m^2 = (x/\lambda_1)^2 + (y/\lambda_2)^2 + (z/\lambda_3)^2$ is the ellipsoidal radius; and the axis
-ratios are $\lambda_1:\lambda_2:\lambda_3 = 6:4:3$.
-In the case where the central density profile index
-$\gamma$ is unity (and in the limit of spherical symmetry), this is the Hernquist
-profile \citep{1990ApJ...356..359H}.  The four combinations of profile indices
-are shown in \tabref{mock galaxy params}.
+where $a$ is the component scale radius mentioned in \tabref{mock galaxy
+params}; $\tilde r^2 = (x/\lambda_1)^2 + (y/\lambda_2)^2 + (z/\lambda_3)^2$ is the
+ellipsoidal radius; and the axis ratios are $\lambda_1:\lambda_2:\lambda_3 =
+6:4:3$.  In the case where the central density profile index $\gamma$ is unity
+(and in the limit of spherical symmetry), this is the Hernquist profile
+\citep{1990ApJ...356..359H}.  The four combinations of profile indices are
+shown in \tabref{mock galaxy params}.
 
@@
 
-In \figref{mock galaxies}, we show the 3D radial density, 
-the 2D projected density, and the 2D enclosed mass for each
-galaxy.
+In \figref{mock galaxies}, we show the 3D radial density, the 2D projected
+density, and the 2D enclosed mass for each galaxy.
 
@@
 central image belongs to only to the R1 source to avoid overconstraining the
-models. Image colors represent a common source. Grey circles are a visual aid to help determine radial
-separation between images. The axes are in arcseconds.}
+models. Image colors represent a common source. Grey circles are a visual aid
+to help determine radial separation between images. The axes are in
+arcseconds.}
 \label{arrival surfaces}
@@
 the sight line to the bright lensing galaxy; in clusters, however, such images
-have been seen -- e.g. \citealt{2005PASJ...57L...7I}). We assumed for all our tests that the
-lensing mass was radially symmetric (Prior vi). For our mock data, this is
-known to be true; it is most often the case with real galaxies, unless there is
-an obvious observed asymmetry.
-(We explore the effect of switching off the symmetry prior in Appendix \ref{no_symm_prior}.
-For the quads, the difference is small; for the doubles -- as expected -- the results are significantly degraded without this prior.) We use, as default, 8 pixels from the centre to the edge of the mass map; the central pixel was further refined into $5\times5$ pixels to capture any steep rise in the profile (two of the four mock galaxies have a steeply rising inner profile).
-We demonstrate that our results are robust to changing the grid resolution in Appendix \ref{pix_convergence_test}.
-
-In all cases, we additionally assume no external shear.
-This amounts to an assumption that any such shear field can be constrained by data (e.g.
-combining weak lensing constraints, or assuming that the shear field correlates with visible galaxies -- e.g.
-\citealt{2009A&A...500..681M,2011ApJ...726...84W}).
+have been seen -- e.g. \citealt{2005PASJ...57L...7I}). We assumed for all our
+tests that the lensing mass was radially symmetric (Prior vi). For our mock
+data, this is known to be true; it is most often the case with real galaxies,
+unless there is an obvious observed asymmetry. (We explore the effect of
+switching off the symmetry prior in \appref{no_symm_prior}. For the
+quads, the difference is small; for the doubles -- as expected -- the results
+are significantly degraded without this prior.) We use, by default, 8 pixels
+from the centre to the edge of the mass map; the central pixel was further
+refined into $5\times5$ pixels to capture any steep rise in the profile (two of
+the four mock galaxies have a steeply rising inner profile). We demonstrate
+that our results are robust to changing the grid resolution in 
+\appref{pix_convergence_test}.
+
+\hilight{[NOT TRUE. Almost any shear is allowed, although in practice, very little is used.]
+In all cases, we additionally assume no external shear. This amounts to an
+assumption that any such shear field can be constrained by data (e.g. combining
+weak lensing constraints, or assuming that the shear field correlates with
+visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).}
 
@@
 
-\figref{reconstruction} shows some example reconstructions of the radial profile of our mock lenses. The left
-column shows the ensemble average arrival time surface with images marked as
-circles and the inferred source position(s) as a diamond. The centre column shows
-the radial density profile. The error bars cover a $1\sigma$ range around the
-median; the grey bands show the full ensemble range. The true density profile from the mock data is also plotted for
+\figref{reconstruction} shows some example reconstructions of the radial
+profile of our mock lenses. The left column shows the ensemble average arrival
+time surface with images marked as circles and the inferred source position(s)
+as a diamond. The centre column shows the radial density profile. The error
+bars cover a $1\sigma$ range around the median; the grey bands show the full
+ensemble range. The true density profile from the mock data is also plotted for
 comparison. The vertical lines mark the radial position of the images. The
@@
 2D reconstruction for \mockBC\ for a quad; we discuss shape recovery further in
-\S\ref{sec:shape}.
-
-As expected, the error bars
-are smallest in the region of the images where the most information about the
-lens is present. In all cases, there is a dip in the profile at large $R$ due to the
-cut off in mass in the lensing map. This is of little importance, though, as
-there is no lensing information there.
-
-Notice that the extended double (top row) gives the poorest constraints, as expected.
-Adding stellar mass (second row) significantly improves the constraints, for this example where the stars contribute significantly to the potential.
-Moving to a quad with time delays gives constraints almost as strong as the double with stellar mass, but note that {\it focussing only on the goodness of the fit can be misleading.} In the third row of \figref{reconstruction}, we obtain a better recovery than in the bottom row for {\it precisely the same data quality}.
-This occurs because the \Glass\ prior favours steeper models consistent with \mockBC, but not \mockAA.
-It is the \Glass\ prior, rather than the data that is driving the good recovery for \mockBC\ in this example.
-This emphasises the importance of using a wide range of mock data tests to determine the role of data versus prior in strong lensing.
+\secref{sec:shape}.
+
+As expected, the error bars are smallest in the region of the images where the
+most information about the lens is present. In all cases, there is a dip in the
+profile at large $R$ due to the cut off in mass in the lensing map. This is of
+little importance, though, as there is no lensing information there.
+
+Notice that the extended double (top row) gives the poorest constraints, as
+expected. Adding stellar mass (second row) significantly improves the
+constraints, for this example where the stars contribute significantly to the
+potential. Moving to a quad with time delays gives constraints almost as strong
+as the double with stellar mass, but note that {\it focussing only on the
+goodness of the fit can be misleading.} In the third row of
+\figref{reconstruction}, we obtain a better recovery than in the bottom row for
+{\it precisely the same data quality}. This occurs because the \Glass\ prior
+favours steeper models consistent with \mockBC, but not \mockAA. It is the
+\Glass\ prior, rather than the data that is driving the good recovery for
+\mockBC\ in this example. This emphasises the importance of using a wide range
+of mock data tests to determine the role of data versus prior in strong
+lensing.
 
@@
 
-\figref{main results} and \figref{main results pixel-wise} show the results for our full mock data ensemble. Each
-subplot corresponds to a different mock galaxy, as marked. We show the fractional error of the mass
-distribution for each of the test configurations with (red) and without (black)
- stellar mass. In \figref{main results}, the error is defined over radial bins of mass as:
+\figref{main results} and \figref{main results pixel-wise} show the results for
+our full mock data ensemble. Each subplot corresponds to a different mock
+galaxy, as marked. We show the fractional error of the mass distribution for
+each of the test configurations with (red) and without (black) stellar mass. In
+\figref{main results}, the error is defined over radial bins of mass as:
 %
@@
 plot. As a result, there is a general trend for the reconstruction quality to
-increase (and therefore for $f$ to decrease). When both time delays and
-a central image are present (TM), the quality is highest. A double is known to
+increase (and therefore for $f$ to decrease). When both time delays and a
+central image are present (TM), the quality is highest. A double is known to
 provide very little constraint on the mass distribution. This is particularly
@@
 and the reconstruction of the double is poorest. However, the addition of an
-arc from the extended source is sufficient to correct this.
-Notice that, as in \figref{reconstruction}, the recovery for \mockBC\ quickly saturates; there is little improvement as the data improves beyond a single quad.
-This occurs because the \Glass\ sample prior in the absence of data favours steep models like \mockBC\ over shallower models like \mockAA\ (see also \figref{reconstruction}).
+arc from the extended source is sufficient to correct this. Notice that, as in
+\figref{reconstruction}, the recovery for \mockBC\ quickly saturates; there is
+little improvement as the data improves beyond a single quad. This occurs
+because the \Glass\ sample prior in the absence of data favours steep models
+like \mockBC\ over shallower models like \mockAA\ (see also
+\figref{reconstruction}).
 
@@
 %
-and $\delta_{ij}$ is the Kronecker delta.
-We always take $\lambda_1$ to be the largest value.
-As with $f_R$ and $f_\theta$, we only consider mass up to one radial position passed the outermost image and compute the fractional error as:
+and $\delta_{ij}$ is the Kronecker delta. We always take $\lambda_1$ to be the
+largest value. As with $f_R$ and $f_\theta$, we only consider mass up to one
+radial position passed the outermost image and compute the fractional error as:
 %
@@
 the mass map, rather than at the centre where the stars may dominate the
-potential (see equation \ref{eqn:inertia}).
+potential (see \eqnref{eqn:inertia}).
 
@@
 
-With the stellar mass lower bound, there is a significant improvement of the reconstruction
-quality shown in \figref{main results} and \figref{main results pixel-wise} for the doubles in the
-steepest mock galaxies (\mockAC{} and \mockBC). This is because these models
-are dominated by stars in the inner region. By contrast, the other two galaxies
- -- where the stars contribute negligibly to the potential -- are largely unaffected.
+With the stellar mass lower bound, there is a significant improvement of the
+reconstruction quality shown in \figref{main results} and \figref{main results
+pixel-wise} for the doubles in the steepest mock galaxies (\mockAC{} and
+\mockBC). This is because these models are dominated by stars in the inner
+region. By contrast, the other two galaxies -- where the stars contribute
+negligibly to the potential -- are largely unaffected.
 
@@
 
-As outlined in \S\ref{sec:glass}, \Glass\ can also run post processing routines
-on the model ensemble which can be used to apply non-linear constraints. As an
-example, we consider here constraints from stellar kinematics. The models in
-the \Glass\ ensemble are processed as described in \S\ref{sec:glasskinematics}.
-To illustrate the power of stellar kinematic constraints, in
-\figref{fig:sigp}, we plot the projected velocity dispersion calculated for
-one model model (extracted from the full ensemble) of the \mockBC{} Quad with time
-delays and stellar mass (left), and the same but without stellar mass (right).
-In both cases, we calculate curves
-for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
-Over-plotted is the correct answer for the \mockBC{} model (black). The stellar half
-mass radius (yellow) Einstein radius (black) are marked by vertical lines. For
-this configuration, these two radii are well-separated.
+As outlined in \secref{sec:glass}, \Glass\ can also run post processing
+routines on the model ensemble which can be used to apply non-linear
+constraints. As an example, we consider here constraints from stellar
+kinematics. The models in the \Glass\ ensemble are processed as described in
+\S\ref{sec:glasskinematics}.  To illustrate the power of stellar kinematic
+constraints, in \figref{fig:sigp}, we plot the projected velocity dispersion
+calculated for one model model (extracted from the full ensemble) of the
+\mockBC{} Quad with time delays and stellar mass (left), and the same but
+without stellar mass (right).  In both cases, we calculate curves for two
+extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
+Over-plotted is the correct answer for the \mockBC{} model (black). The stellar
+half mass radius (yellow) Einstein radius (black) are marked by vertical lines.
+For this configuration, these two radii are well-separated.
 
 Without even sweeping through the model ensemble and formally
-accepting/rejecting models, \figref{fig:sigp} already illustrates what we can obtain from stellar kinematics.
-The left plot shows the radially averaged projected velocity dispersion $\sigma_p(R)$ \eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC\ galaxy without the stellar mass constraint.
-The blue data points show the 1$\sigma$ distribution from the ensemble assuming $\beta=0$ (solid) and $\beta = 1$ (dashed); the grey bands show the full distributions.
-Also marked are the $\sigma_p(R)$ calculated from the mock data assuming $\beta=0$ (solid purple) and $\beta =1$ (dashed purple); and the true $\sigma_p(R)$ measured directly from the stars (black).
-This latter has a non-constant $\beta(r)$ (right panel) and differs also from the purple and blue curves in that these all assume spherical symmetry, whereas the stellar distribution is really triaxial.
-Such triaxiality and varying $\beta(r)$ explains why the purple curves do not match the black one.
-However, they do largely bracket the correct solution.
-More interestingly, the curves approximately cross for $\beta = 0$ at the stellar half light radius (yellow vertical line).
-This demonstrates, as has previously been reported in the literature, that $\sigma_p(R)$ gives a good estimate of the mass enclosed within $\sim$ the half light radius $M_{1/2}$ \citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W}.
-The mass {\it profile}, however, depends on $\beta$ which is poorly constrained by these data.
-If we add stellar mass constraints (middle panel), the situation is little-improved.
-The true answer already lay close to the bottom of the ensemble distribution; it now is forced to lie right at the edge.
-
-From \figref{fig:sigp}, it is clear that $\sigma_p(R)$ provides two useful pieces of information.
-Firstly, it is a powerful probe of $M_{1/2}$.
-Given a measurement of $\sigma_p(r_1/2) \sim 150$\,km/s, we could usefully reject many models in the ensemble as being overly steep in the centre.
-We would not, however, obtain a strong constraint on $\beta(r_{1/2})$.
-We could rule out $\beta(r_{1/2}) = 1$ (blue dashed line), but since our $\beta=0$ model crosses the true $\beta \sim 0.5$ line at $r_{1/2}$ it is clear that many $\beta(r)$ profiles will be consistent with the data.
-On the other hand, if we have a situation where $r_{1/2} \sim r_E$ (i.e.
-the vertical yellow and black lines in \figref{fig:sigp} overlap), then we will obtain tight constraints on $\beta$ since we then have two strong constraints on $M(r_{1/2})$ that become redundant.
-This latter situation of redundancy is also exactly what we would like to constrain cosmological parameters.
-In this case, we require a third piece of redundant information -- in this case in the form of strong lensing time delays.
-We will discuss such cosmological constraints in a forthcoming paper.
+accepting/rejecting models, \figref{fig:sigp} already illustrates what we can
+obtain from stellar kinematics. The left plot shows the radially averaged
+projected velocity dispersion $\sigma_p(R)$ \eqnrefp{eqn:sphericaljeans} for a
+single quad from the \mockBC\ galaxy without the stellar mass constraint. The
+blue data points show the 1$\sigma$ distribution from the ensemble assuming
+$\beta=0$ (solid) and $\beta = 1$ (dashed); the grey bands show the full
+distributions. Also marked are the $\sigma_p(R)$ calculated from the mock data
+assuming $\beta=0$ (solid purple) and $\beta =1$ (dashed purple); and the true
+$\sigma_p(R)$ measured directly from the stars (black). This latter has a
+non-constant $\beta(r)$ (right panel) and differs also from the purple and blue
+curves in that these all assume spherical symmetry, whereas the stellar
+distribution is really triaxial. Such triaxiality and varying $\beta(r)$
+explains why the purple curves do not match the black one. However, they do
+largely bracket the correct solution. More interestingly, the curves
+approximately cross for $\beta = 0$ at the stellar half light radius (yellow
+vertical line). This demonstrates, as has previously been reported in the
+literature, that $\sigma_p(R)$ gives a good estimate of the mass enclosed
+within $\sim$ the half light radius $M_{1/2}$
+\citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W}. The mass {\it
+profile}, however, depends on $\beta$ which is poorly constrained by these
+data. If we add stellar mass constraints (middle panel), the situation is
+little-improved. The true answer already lay close to the bottom of the
+ensemble distribution; it now is forced to lie right at the edge.
+
+From \figref{fig:sigp}, it is clear that $\sigma_p(R)$ provides two useful
+pieces of information. Firstly, it is a powerful probe of $M_{1/2}$. Given a
+measurement of $\sigma_p(r_1/2) \sim 150$\,km/s, we could usefully reject many
+models in the ensemble as being overly steep in the centre. We would not,
+however, obtain a strong constraint on $\beta(r_{1/2})$. We could rule out
+$\beta(r_{1/2}) = 1$ (blue dashed line), but since our $\beta=0$ model crosses
+the true $\beta \sim 0.5$ line at $r_{1/2}$ it is clear that many $\beta(r)$
+profiles will be consistent with the data. On the other hand, if we have a
+situation where $r_{1/2} \sim r_E$ (i.e. the vertical yellow and black lines in
+\figref{fig:sigp} overlap), then we will obtain tight constraints on $\beta$
+since we then have two strong constraints on $M(r_{1/2})$ that become
+redundant. This latter situation of redundancy is also exactly what we would
+like to constrain cosmological parameters. In this case, we require a third
+piece of redundant information -- in this case in the form of strong lensing
+time delays. We will discuss such cosmological constraints in a forthcoming
+paper.
 
 The results for stellar kinematics match our expectations from
-\S\ref{sec:kinematics}. Where the lens data already constrain the mass
+\secref{sec:kinematics}. Where the lens data already constrain the mass
 distribution at $r \sim r_{1/2}$, stellar kinematics provide valuable
@@
 at $r_{1/2}$, we may `integrate out' the effect of unknown $\beta$ to obtain a
-robust measure of $M_{\rm 3D}(r_{1/2})$ from the stellar kinematics. This latter is
+robust measure of $\Mddd(r_{1/2})$ from the stellar kinematics. This latter is
 robust to both uncertainties in $\beta(r)$ and to our assumption of spherical
@@
 
-We have introduced a new gravitational lens modelling tool -- Glass\ -- and used
-it to test the recovery of the mass profile and shape of mock strong lensing
-galaxies. Our key findings are as follows:
+We have introduced a new gravitational lens modelling tool -- Glass\ -- and
+used it to test the recovery of the mass profile and shape of mock strong
+lensing galaxies. Our key findings are as follows:
 
@@
 
-Where information on the mass distribution from lensing and/or other probes becomes
-redundant, this opens up the possibility of using strong lensing to constrain
-cosmological models. We will study this, and present the first results from
-\Glass\ applied to real data, in forthcoming papers.
+Where information on the mass distribution from lensing and/or other probes
+becomes redundant, this opens up the possibility of using strong lensing to
+constrain cosmological models. We will study this, and present the first
+results from \Glass\ applied to real data, in forthcoming papers.
 
@@
 The authors would like to thank Sarah Bryan and Walter Dehnen for creating the
-particle distributions for the mock galaxies. JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+particle distributions for the mock galaxies. JIR would like to acknowledge
+support from SNF grant PP00P2\_128540/1.
 
@@
 
-Since we want to model the density distribution with a computer it
-is convenient to choose units that make the relevant quantities of order
-unity.  We therefore measure lengths in light years, time in years, positions
-in arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
+Since we want to model the density distribution with a computer it is
+convenient to choose units that make the relevant quantities of order unity.
+We therefore measure lengths in light years, time in years, positions in
+arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
 arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to
-define a proxy to the Hubble constant $\zeta \equiv N^2 H_0$. We now 
-express the equations from \secref{sec:theory} in terms of these new units
-and introduce some other useful quantities.
+define a proxy to the Hubble constant $\zeta \equiv N^2 H_0$. We now express
+the equations from \secref{sec:theory} in terms of these new units and
+introduce some other useful quantities.
 
@@
 %
-where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
-has units of \Msun/lyr$^2$. We can clean this up by first writing down a dimensionless time
-delay
+where the factor of $D_L^2$ in the second term comes from the fact that
+$\Sigma$ has units of \Msun/lyr$^2$. We can clean this up by first writing down
+a dimensionless time delay
 %
@@
 %
-where $\xi=d_S / d_{LS}$.
-We explicitly write $\kappa_\infty$ to remind ourselves
-that there is no source distance factor involved. This is useful when we
-consider multiple sources.
-
-%\section{Raytracing convergence test}
-%Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
-%$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
-%the change in time delays as we increase $\Rmap$.  The image system is a quad
-%with the central maximum image. When the projected mass begins to fall off the
-%time delays stabilize. In the right panel we see the effect of changing the
-%resolution of the map.  Increasing the resolution allows for more accurate
-%placement of the images and after about $\Rpix=40$ the image positions change
-%by less than 0.04 arcsec. The one image that continues to change is near to a
-%caustic.  
-%
-%\begin{figure}
-%\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
-%\caption{\textbf{Left:} Test for convergence of the predicted time delay as $\Rmap$ is increased and
-%$\Rpix=45$ is held constant. After about $\Rmap=20$ most of the asymmetric mass is in the map.
-%\textbf{Right:} Test for convergence of the predicted image positions $\theta$ as $\Rpix$
-%changes and $\Rmap=20$ arcsec is held constant.}
-%\label{raytracing convergence tests}
-%\end{figure}
+where $\xi=d_S / d_{LS}$.  We explicitly write $\kappa_\infty$ to remind
+ourselves that there is no source distance factor involved. This is useful when
+we consider multiple sources.
 
@@
 %
-where $Q_n$ is the logarithm evaluated over the $n$th pixel at position $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.
-Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates where 
+where $Q_n$ is the logarithm evaluated over the $n$th pixel at position
+$\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.  Instead of
+working with a position vector $\vec\theta$ we work in cartesian coordinates
+where 
 %
@@
 In this appendix, we explore the effect of the radial symmetry prior.
-\figref{fig:no_symm_prior} shows results for a single quad (top) and an extended double (bottom); both without time delay data or stellar mass constraints.
-The results for the quad a similarly good to the case with the radial prior (\figref{reconstruction}); for the double, however, the results are significantly degraded as expected.
+\figref{fig:no_symm_prior} shows results for a single quad with time delays (top) and an
+extended double without time delays (bottom); in both cases, we do not use the stellar mass
+constraints. The results for the quad a similarly good to the case with the
+radial prior (\figref{reconstruction}); for the double, however, the results
+are significantly degraded as expected.
 
 \begin{figure*}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-kappa.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-a.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-c.pdf}\\
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-kappa.pdf}
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-a.pdf}
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-c.pdf}
-\caption{Results for a single quad (top) and an extended double (bottom) without the radial symmetry prior; both without time delay data or stellar mass constraints.
-Figures and symbols are as in \figref{reconstruction} and \figref{2d mass reconstruction}.}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d.pdf}\\
+%
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d-1.pdf}\\
+%
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-c.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-d.pdf}
+%
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-a-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-b-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-c-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-d-1.pdf}
+\caption{Results for a single quad (upper two rows) and an extended double (lower two rows)
+    without the radial symmetry prior; The top row of each group uses time delay data. The stellar
+    mass constraint has not been used in any of these examples. Figures and symbols are as in \figref{reconstruction} and
+    \figref{2d mass reconstruction}.}
 \label{fig:no_symm_prior}
@@
 
-In this Appendix, we present a convergence test of our results with the grid resolution -- pixrad.
-As default, this is set to 8 pixels from the centre of the mass map to the edge.
-As can be seen from \figref{fig:pix_convergence_test}, our results are typically well-converged for pixrad$\,\,> 5$.
-The results for pixrad$\,\,= 5$ become systematically biased away from the central regions (where we have the higher resolution adaptive mesh), because our regularisation prior combined with a low pixrad biases us towards shallow models.
-This effect diminishes with increasing resolution and is already negligible by pixrad$\,\,= 7$.
+In this Appendix, we present a convergence test of our results with the grid
+resolution -- \pixrad. By default, this is set to 8 pixels from the centre of
+the mass map to the edge. As can be seen from
+\figref{fig:pix_convergence_test}, our results are typically well-converged for
+$\pixrad > 5$. The results for $\pixrad = 5$ become systematically biased away
+from the central regions (where we have the higher resolution adaptive mesh),
+because our regularisation prior combined with a low \pixrad{} biases us
+towards shallow models. This effect diminishes with increasing resolution and
+is already negligible by $\pixrad = 7$. Notice that the mass increases in size
+with decreasing resolution. This is because we always demand that there are
+four pixels beyond the outermost image.
 
@@
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-c.pdf} \\
-\caption{Changing pixrad. top to bottom: pixrad=10,7,6,5. We use 8 normally.}
+\caption{The effect of changing the grid resolution parameter \pixrad. From top
+    to bottom, the panels show results for a single quad with time delays and
+    with stellar mass constraints using $\pixrad = 10,7,6,5$,
+    respectively. We always demand that there are four radial bins outside the
+    outermost image, which causes the total mass to increase with decreasing
+    \pixrad.  In this paper we have used $\pixrad = 8$ in all the
+tests.}
+
 \label{fig:pix_convergence_test}

### 2014-01-29 limits/ms.tex
Updated inertia tensor to show full expression.
edits

@@
 \begin{enumerate}
-\item {\bf Free-form modelling:} 
-    In `free-form' or non-parametric modelling, there is no specified
-    parametric form for the mass distribution.  There are still assumptions (or
-    priors) on the mass distribution, such as smoothness or being centrally
-    concentrated
+\item {\bf Free-form modelling:} In `free-form' or non-parametric
+  modelling, there is no specified parametric form for the mass
+  distribution.  There are still assumptions (or priors) on the mass
+  distribution, such as smoothness or being centrally concentrated
   \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2009A&A...500..681M,2010ApJ...723.1678C}
-    but these are much less restrictive than parametric forms
-    (\cite{2006MNRAS.367.1209L} implemented a particularly elegant prior, which
-    is that the mass distribution must be non-negative and no extra images are
-    produced). To be concrete, we define from here on:
+  but these are much less restrictive than parametric forms.  A
+  particularly elegant prior is implemented by
+  \cite{2006MNRAS.367.1209L}, requiring that the mass distribution to
+  be non-negative and no extra images allowed. To be concrete, we
+  define from here on:
 
@@
   Being under-constrained, it is then {\it necessary} to explore model
-  degeneracies rather than find a single `best-fit' solution. Free-form models
-  are more commonly used with cluster lenses
+  degeneracies rather than find a single `best-fit'
+  solution. Free-form models are more commonly used with cluster
+  lenses
   \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S},
-  but can be used with galaxy lenses as well, where their less restrictive
-  assumptions can be important.  For example, in time-delay galaxy lenses,
-  parametric models have historically led to tension with independent measures
-  of the Hubble parameter $H_0$
-  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are resolved
-  once the less restrictive assumptions of free-form models are permitted
-  \citep{2007ApJ...667..645R}.  \item Model ensembles, exploring a diverse
+  but can be used with galaxy lenses as well, where their less
+  restrictive assumptions can be important.  For example, in
+  time-delay galaxy lenses, parametric models have historically led to
+  tension with independent measures of the Hubble parameter $H_0$
+  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
+  resolved once the less restrictive assumptions of free-form models
+  are permitted \citep{2007ApJ...667..645R}.  Hybrid methods, using a
+  mass grid on top a parametric model, have also been explored
+  \citep[e.g.,][]{2010MNRAS.408.1969V}.
+
+\item Model ensembles, exploring a diverse
   range of possible mass distributions that nonetheless all fit the data,
@@
 \item {\bf Stellar kinematic constraints:} This was first suggested by
-    \citet{2002MNRAS.337L...6T} as a means to break lensing degeneracies and
-    determine cosmological parameters. This works because stellar kinematics
-    can provide an independent estimate of the Einstein radius, via the virial
-    theorem:
+  \citet{2002MNRAS.337L...6T} as a means to break lensing
+  degeneracies. This works because stellar kinematics can provide an
+  independent estimate of the Einstein radius, via the virial theorem:
 %
@@
 %
-where $\langle v^2_\mathrm{los}\rangle$ is the projected stellar velocity
-dispersion, and the above relation becomes exact for isothermal lenses.  The
-use of two-dimensional kinematics by \cite{2011MNRAS.415.2215B} is especially
-interesting.
+where $\langle v^2_\mathrm{los}\rangle$ is the projected stellar
+velocity dispersion, and the above relation becomes exact for
+isothermal lenses.  The technique has been applied to many lenses
+\citep{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
+use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is
+especially interesting.
 
@@
 %
-\begin{equation} 
-    I_{ij} = (-1)^{1-\delta_{ij}}\sum_\theta M(\vec\theta) \theta_i\theta_j 
+% \begin{gather}
+%    I_{xx} = \sum_{\vec\theta} M(\vec\theta) \theta^2_y \quad ; \quad
+%    I_{yy} = \sum_{\vec\theta} M(\vec\theta) \theta^2_x \\
+%    I_{xy} = I_{yx} = - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \nonumber
+%    \label{eqn:inertia}
+% \end{gather}
+%
+\begin{equation}
+\left(
+\begin{matrix}
+   \sum_{\vec\theta} M(\vec\theta) \theta^2_y 
+    & - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \\
+    - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y
+    & \sum_{\vec\theta} M(\vec\theta) \theta^2_x
+\end{matrix}
+\right).
     \label{eqn:inertia}
@@
 %
-and $\delta_{ij}$ is the Kronecker delta. We always take $\lambda_1$ to be the
-largest value. As with $f_R$ and $f_\theta$, we only consider mass up to one
-radial position passed the outermost image and compute the fractional error as:
+We always take $\lambda_1$ to be the largest value. As with $f_R$ and
+$f_\theta$, we only consider mass up to one radial position passed the
+outermost image and compute the fractional error as:
 %
@@
 \end{document}
-
-%\cite{2007ApJ...667..645R} were the first to test the recovery of
-%strong lensing surface density profiles using mock data generated from
-%N-body models {\bf JR. Is this true?}. They found that when including
-%time delays, circularly averaged surface density distributions can
-%sufficiently well-recovered to make interesting comparisons with
-%theoretical models Cosmological parameters, however, are more
-%sensitive. Since then, several groups have used N-body mock data to
-%explore the fidelity of strong lensing reconstructions
-%\citep{2007MNRAS.380.1729L}. We expand on these earlier works
-%by considering not only the recovery of the circularly averaged
-%surface density profile of a lens, but also its shape, higher order
-%measures of the mass recovery (a pixel-by-pixel comparison), and the
-%utility of wrapping in constraints from stellar mass estimates and/or
-%stellar kinematics.
-%

### 2014-01-29 limits/ms.tex
Justin further changes - see E-mail

@@
 \newcommand{\sth}[1][]{\sin^{#1}\theta}
-\def\dth{{\rm d}\theta}
+\def\dth{d\theta}
 
@@
 where the stars dominate the central potential -- can also break the steepness
-degeneracy, giving a recovery almost as good as having time delay data or
+degeneracy, giving a recovery for doubles almost as good as having a quad with time delay data, or
 multiple source redshifts; (iv) stellar kinematics provide a robust measure of
@@
 To see why lens modelling details are of crucial importance, let us
-recall the essential quantities that appear in lensing.\footnote{These
-  quantities are defined more precisely in \S\ref{sec:lensing_basic}.}
-First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
+recall the essential quantities that appear in lensing (see also \S\ref{sec:theory} for a more detailed exposition). First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
 angular-diameter distances to the lens, source, and from lens to
 source; these are all proportional to $c/H_0$ but have factors
-that depend on the particular choice of cosmology.  Typically:
-%
-\begin{equation}
-D_L \approx z \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
-\end{equation}
+that depend on the particular choice of cosmology\footnote{Here, $c$ is the speed of light in vacuo and $H_0$ is the Hubble parameter.}.  Typically:
+%
+\begin{equation}
+D_L \approx z_L \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
+\end{equation}
+where $z_L$ is the redshift of the lens. 
 %
 For multiple images, the sky-projected density must exceed the critical
-density
+density in some region:
 %
@@
 \end{equation}
-%
-in some region.  The separation between the lensed images is of order
+where $G$ is Newton's gravitational constant. 
+%
+The separation between the lensed images is of order
 the Einstein radius $\theta_E$, which is related to
@@
   Being under-constrained, it is then {\it necessary} to explore model
-  degeneracies rather than find a single `best-fit'
+  degeneracies rather than finding a single `best-fit'
   solution. Free-form models are more commonly used with cluster
@@
   restrictive assumptions can be important.  For example, in
-  time-delay galaxy lenses, parametric models have historically led to
-  tension with independent measures of the Hubble parameter $H_0$
+  time-delay galaxy lenses, parametric model measures of the Hubble parameter $H_0$ have historically been at 
+  tension with independent measures 
   \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
@@
 
-\item Model ensembles, exploring a diverse
+\item {\bf Model ensembles:} Model ensembles, exploring a diverse
   range of possible mass distributions that nonetheless all fit the data,
@@
   possible in parametric models \citep{1999AJ....118...14B} but are more
-  common in free-form models
+  common in free-form models, where -- since such models are deliberately under-constrained -- they become vital 
   \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.
@@
   \citet{2002MNRAS.337L...6T} as a means to break lensing
-  degeneracies. This works because stellar kinematics can provide an
+  degeneracies. The idea is that stellar kinematics can provide an
   independent estimate of the Einstein radius, via the virial theorem:
@@
 velocity dispersion, and the above relation becomes exact for
-isothermal lenses.  The technique has been applied to many lenses
-\citep{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
+isothermal lenses.
+This can then be used to probe cosmological parameters if lenses are known to be isothermal \citep[e.g.][]{2012MNRAS.424.2864C}; or to break the steepness degeneracy in the more general situation (see \S\ref{sec:kinematics}).
+The technique has since been applied to many lenses \citep[e.g.][]{2006ApJ...649..599K,2008ApJ...682..964B}.
+Going further, the
 use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is
@@
     inferred from photometry and compared with the total mass
-    \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
+    \citep[e.g.][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
     the inferred stellar mass depends on the assumed IMF, lenses in which
@@
     $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds on stellar $M/L$ have also
-    been claimed \citep{2013MNRAS.428.3183D} but these require upper-bound
-    assumptions about the dark-matter profile. \hilight{JR. I feel like we need
-    more citations here and throughout. We must be skipping over an Armada of
-literature.}
+    recently been claimed by fitting $\Lambda$CDM semi-analytic models to the tilt of the fundamental plane \citep{2013MNRAS.428.3183D}.
 
@@
 the $\Omega$ parameters even from a single lens, if there are lensed sources at
-multiple redshifts \citep{2014MNRAS.437.2461L} or by using a strong prior
+multiple redshifts \citep{2014MNRAS.437.2461L} or by using additional priors 
 \citep{2010Sci...329..924J,2013arXiv1306.4732S}.
@@
 \begin{eqnarray} 
-    \Mddd(r) & = & M(<r) - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left(\frac{1}{\cth[2]} \right. \nonumber \\ 
+    \Mddd(r) & = & 2\pi \int_0^r R \Sigma(R) dR - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left(\frac{1}{\cth[2]} \right. \nonumber \\ 
     & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
@@
 chosen R1=1.72, R2=0.72, and R3=0.51 so that the radial distribution of the
-images is nearly equal.
+images is nearly equal. For all mocks, we do not apply any external shear field.
 
@@
 
-\hilight{[NOT TRUE. Almost any shear is allowed, although in practice, very little is used.]
-In all cases, we additionally assume no external shear. This amounts to an
-assumption that any such shear field can be constrained by data (e.g. combining
+In all cases -- despite applying no external shear to the mock lenses -- we allow a broad range of external shear in our lens model reconstructions.
+\Glass\ correctly returns a small or zero shear in all cases.
+It is possible that more complex shear fields present in real lensing galaxies could introduce further degeneracies beyond those discussed here.
+However, any such shear field can, at least in principle, be constrained by data (e.g.
+combining
 weak lensing constraints, or assuming that the shear field correlates with
-visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).}
+visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).
 
@@
 We can also more directly probe the recovery of the shape of the mass
-distribution by defining a global measure of lens shape
+distribution by defining a global measure of lens shape:
 %
@@
 %
-where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor
+where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor:
 %
@@
 where the stars dominate the central potential -- can also break the steepness
-degeneracy, giving a recovery almost as good as having time delay data or
+degeneracy, giving a recovery for doubles almost as good as having a quad with time delay data, or
 multiple source redshifts;
@@
 In this appendix, we explore the effect of the radial symmetry prior.
-\figref{fig:no_symm_prior} shows results for a single quad with time delays (top) and an
-extended double without time delays (bottom); in both cases, we do not use the stellar mass
-constraints. The results for the quad a similarly good to the case with the
-radial prior (\figref{reconstruction}); for the double, however, the results
-are significantly degraded as expected.
+\figref{fig:no_symm_prior} shows results for a single quad (top two rows) and an
+extended double (bottom two rows) without the radial prior; in both cases, we do not use the stellar mass
+constraints.
+The bottom row of each group uses time delay data.
+Without time delay data or the radial symmetry prior, the results for the quad are poor -- particularly the shape recovery.
+Including time delays, the results are similar to the case with the radial prior (\figref{reconstruction} and \figref{2d mass reconstruction}).
+Similarly, for the extended double the results without time delays are poor.
+Even with time delays, the shape is not well recovered without the radial prior, as expected.
 
@@
 \caption{Results for a single quad (upper two rows) and an extended double (lower two rows)
-    without the radial symmetry prior; The top row of each group uses time delay data. The stellar
+    without the radial symmetry prior; the bottom row of each group uses time delay data. The stellar
     mass constraint has not been used in any of these examples. Figures and symbols are as in \figref{reconstruction} and

### 2014-01-29 limits/ms.tex
Minor edits.

--- 2014-01-29 limits/ms.tex
@@
 the mass at the half light radius of the stars $r_{1/2}$ that can also break
-the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v)
+the steepness degeneracy if the Einstein radius $r_E \neq r_{1/2}$; and (v)
 if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the
@@
 \begin{equation}
-\Sigma_\mathrm{crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
+\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
 \end{equation}
@@
 %
-where $\langle v^2_\mathrm{los}\rangle$ is the projected stellar
+where $\langle v^2_\mathrm{los}\rangle$ is the line of sight stellar
 velocity dispersion, and the above relation becomes exact for
@@
 \begin{equation}
-\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \quad ; \quad \kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
+\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \quad ; \quad 
+\kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_\mathrm{crit}}
 \end{equation}

### 2014-01-29 limits/ms.tex
Fixed jpc affiliation.

@@
 \\
-$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
+$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$45 avenue des Etats-Unis, 78035, Versailles, France\\
 $^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
@@
 %
-The separation between the lensed images is of order
+The angular separation between the lensed images is of order
 the Einstein radius $\theta_E$, which is related to
@@
 %
-where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$) is the gravitational radius. If the source is a
-quasar or otherwise rapidly variable, a time delay $\Delta t$ in the variability
-will be present where:
-%
-\begin{equation}
-\Delta t \sim R_G/c \,.
+where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$)
+is the gravitational radius. If the source is a quasar or otherwise rapidly
+variable, a time delay $\Delta t$ in the variability will be present where
+%
+\begin{equation}
+\Delta t \sim R_G/c
 \end{equation}
@@
 \begin{eqnarray} 
-    \Mddd(r) & = & 2\pi \int_0^r R \Sigma(R) dR - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left(\frac{1}{\cth[2]} \right. \nonumber \\ 
-    & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
+    \Mddd(r) & = & M_\mathrm{p}(<r) - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left[\frac{1}{\cth[2]} \right. \nonumber \\ 
+    & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right] \dth
 \end{eqnarray}
 %
-where $M(<r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
+where 
+%
+\begin{equation}
+    M_\mathrm{p}(<r) = 2\pi \int_0^r R \Sigma(R) dR
+\end{equation}
+%
+is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
 
@@
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
-\caption{ \textbf{Left:} The mock data distribution for \mockBC{} projected onto a coarse grid.
-  \textbf{Right:} The recovered ensemble average $\kappa$ distribution for the single quad. The contours are
-  logarithmic base 10 values, where level 0 corresponds to the critical density. Contours below the critical density
-  are drawn with dashed lines.}
+\caption{ \textbf{Left:} The mock data distribution for \mockBC{} projected
+onto a coarse grid.  \textbf{Right:} The recovered ensemble average $\kappa$
+distribution for the single quad with time delays. The contours are logarithmic
+base 10 values, where level 0 corresponds to the critical density. Contours
+below the critical density are drawn with dashed lines.}
 \label{2d mass reconstruction}
@@
 %
-% \begin{gather}
-%    I_{xx} = \sum_{\vec\theta} M(\vec\theta) \theta^2_y \quad ; \quad
-%    I_{yy} = \sum_{\vec\theta} M(\vec\theta) \theta^2_x \\
-%    I_{xy} = I_{yx} = - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \nonumber
-%    \label{eqn:inertia}
-% \end{gather}
-%
 \begin{equation}
@@
 \end{matrix}
-\right).
+\right)
     \label{eqn:inertia}
@@
 \begin{enumerate}
-\item For pure lens data, multiple sources with wide redshift separation give the strongest
-constraints as this breaks the well-known mass-sheet or steepness degeneracy;
+\item For pure lens data, multiple sources with wide redshift separation give
+    the strongest constraints as this breaks the well-known mass-sheet or
+    steepness degeneracy;
 
@@
 
-\item Stellar masses -- for lenses
-where the stars dominate the central potential -- can also break the steepness
-degeneracy, giving a recovery for doubles almost as good as having a quad with time delay data, or
-multiple source redshifts;
+\item Stellar masses -- for lenses where the stars dominate the central
+    potential -- can also break the steepness degeneracy, giving a recovery for
+    doubles almost as good as having a quad with time delay data, or multiple
+    source redshifts;
 
@@
 
-\item Stellar kinematics provide a robust measure of the mass at the half light radius of the stars $M(r_{1/2})$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and
-
-\item If $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy 
-$\beta$ -- an interesting quantity in its own right.
+\item Stellar kinematics provide a robust measure of the mass at the half light
+    radius of the stars $M(r_{1/2})$ that can also break the steepness
+    degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and
+
+\item If $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe
+    the stellar velocity anisotropy $\beta$ -- an interesting quantity in its
+    own right.
 

### 2014-01-30 limits/ms.tex
Spelling corrections.

@@
 implies that $t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both
-these types of observations give contraints that are linear in $\kappa$ and
+these types of observations give constraints that are linear in $\kappa$ and
 $\vec\beta$.
@@
 For many galaxy lenses, the gravitational potential in the inner region is
-dominated by the stellar mass.  Steller mass can be estimated by combining
+dominated by the stellar mass.  Stellar mass can be estimated by combining
 photometry and colours with models of the stellar populations.  Such estimates
@@
     stellar mass. For the reconstruction, no time delays were assumed.  The
-    third row uses again the the \mockBC{} mock galaxy, but with time delays
+    third row uses again the \mockBC{} mock galaxy, but with time delays
     for a single quad and no stellar mass. With the added information from the

### 2014-05-05 shapes/paper.tex
Added bullets what needs still needs to be done and upload of a now mostly rather old version I worked on 1.5 years ago

@@
-% Open Tasks
-%
-% --- General ---
-% - Add keywords
-% - Check universities' names
-% - Correct typos and reformulate some paragraphs
-% - ...
-%
-%
-% --- Introduction ---
-% - Citiations needed in parametric vs. nonparametric comparison part
-% - Citiations needed on effect of environment
-% - Section on how this work might be able to rule out certain alternative gravity models
-% - Describe theoretical expectations (ellipticities of dm halo and luminous part, misalignments, effect of environment)
-% - ...
-%
-%
-% --- Data ---
-% - More detailed description how the baryionic mass distribution was measured
-% - More details needed on galaxies in the sample? I don't think so though
-% - ...
-%
-%
-% --- Method ---
-% - Maybe more details on GLASS and how it works (cite Jonathan's upcoming paper)
-% - Plot showing how well the shape informations is recovered when applied to fake data
-% - Citation on why not monotonically decreasing radial density profiles are instable
-% - Generally look through method part
-% - ...
-%
-%
-% --- Results ---
-% - Interpretation of 
-% - Interpretation of ellipticities plot (why it is relevant that dm halos are significantly rounder)
-% - Interpretation of misalignment versus ellipticity plot ('forbidden region', alignment with semi-minor axis, very elliptical galaxies well aligned)
-
 \documentclass[useAMS,usenatbib]{mn2e}
@@
 
-\author[Bruderer]{Claudio Bruderer$^{1}$\thanks{E-mail: claudio.bruderer@phys.ethz.ch}, J. I. Read$^{2}$, P. Saha$^{3}$, J. Coles$^{4}$\\
+\author[Bruderer]{Claudio Bruderer$^{1}$\thanks{E-mail: claudio.bruderer@phys.ethz.ch}, J. I. Read$^{1,2}$, P. Saha$^{3}$, J. Coles$^{4}$\\
 $^{1}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
@@
 
-\textbf{Context/Background/Motivation}
+% \textbf{Context/Background/Motivation}
+% \begin{itemize}
+% \item Why interesting (lensing can constrain mass distribution (enclosed mass constraint independent from model with only few percent uncertainty e.g.
+Kochanek 1991?, Wambsganss \& Paczyński 1994?), insights into structure formation)
+% \item What is to be expected from theory (dm, alternative gravity)
+% \end{itemize}
+
+% \textbf{Anything done before?}
+% \begin{itemize}
+% \item Surely cite: \cite{1997ApJ...482..604K,1998ApJ...509..561K,2006ApJ...649..599K,2009ApJ...690..670T,2012ApJ...761..170G}
+% \end{itemize}
+
+% \textbf{New here}
+% \begin{itemize}
+% \item Statistics
+% \item Free-form modelling
+% \item group versus stellar misalignment with dm halo
+% \end{itemize}
+\textbf{Content:}
 \begin{itemize}
-\item Why interesting (lensing can constrain mass distribution (enclosed mass constraint independent from model with only few percent uncertainty e.g.
-Kochanek 1991?, Wambsganss \& Paczyński 1994?), insights into structure formation)
-\item What is to be expected from theory (dm, alternative gravity)
+\item Understand galaxy structure ($\rightarrow$ Links to galaxy evolution?)
+\item Relevant for weak lensing (Intrinsic alignments)
+\item Strong lensing reacts purely due to total mass distribution $\rightarrow$ Can disentangle light and mass
+\item Free-form modelling (or \#constraints $\ll$ \#dof)
 \end{itemize}
 
-\textbf{Anything done before?}
+\textbf{To Do:}
 \begin{itemize}
-\item Surely cite: \cite{1997ApJ...482..604K,1998ApJ...509..561K,2006ApJ...649..599K,2009ApJ...690..670T,2012ApJ...761..170G}
-\end{itemize}
-
-\textbf{New here}
-\begin{itemize}
-\item Statistics
-\item Free-form modelling
-\item group versus stellar misalignment with dm halo
+\item Rewrite introduction and change pitch to: Understand mass and light alignment, understand effect on IA
 \end{itemize}
@@
 \section{Data}\label{sec:data}
+% \begin{itemize}
+% \item SPS (Ignacio Ferreras, Dominik, etc. \citep{2011ApJ...740...97L})
+% \item Write why specifically these lenses were chosen, where they're from
+% \end{itemize}
+\textbf{Content:}
 \begin{itemize}
-\item SPS (Ignacio Ferreras, Dominik, etc. \citep{2011ApJ...740...97L})
-\item Write why specifically these lenses were chosen, where they're from
+\item Describe data set (why this data set, special features of galaxies (environment: y/n/unknonwn, elliptical/disk))
+\item Maybe lose a couple of words on SPS?
+\end{itemize}
+
+\textbf{To Do:}
+\begin{itemize}
+\item Rephrase
+\item Add maybe something on SPS
 \end{itemize}
@@
 \section{Method}\label{sec:method}
-\textbf{GLASS}
+\subsection{GLASS}
+% \textbf{GLASS}
+% \begin{itemize}
+% \item Explain GLASS briefly and link to fake data tests
+% \end{itemize}
+\textbf{Content:}
 \begin{itemize}
-\item Explain GLASS briefly and link to fake data tests
+\item Describe code briefly
+\item Mention PixeLens and two other GLASS papers
 \end{itemize}
 
-\subsection{Priors and assumptions}
+\textbf{To Do:}
 \begin{itemize}
-\item Explain what priors were chosen to model the lenses (Basically always pixrad 12, shear left free for quads, shear limited for doubles to 0.01, local gradient 50 degrees, smoothening prior 2, time delays if known.
-Exceptions are few.
-For some quads symmetry prior, for one double 0.01 was not possible therefore chose 0.1.)
-\end{itemize}
-
-\textbf{Shape measure}
-\begin{itemize}
-\item Explain shape measure
-\item Link to tests on fake data
-\item Include one plot of fake data test -> Jonathan
-\item Illustrate everything with example lens PG1115.
+\item Rephrase
+\item To avoid repetition, check what is really relevant for this paper, and for what we can just reference the other two GLASS papers
+\item Check that same parameter names are used as in the other papers
 \end{itemize}
@@
 
-\textbf{Priors and assumptions}
+\subsection{Priors and assumptions}
+% \subsection{Priors and assumptions}
+% \begin{itemize}
+% \item Explain what priors were chosen to model the lenses (Basically always pixrad 12, shear left free for quads, shear limited for doubles to 0.01, local gradient 50 degrees, smoothening prior 2, time delays if known.
+Exceptions are few.
+For some quads symmetry prior, for one double 0.01 was not possible therefore chose 0.1.)
+% \end{itemize}
+\textbf{Content:}
+\begin{itemize}
+\item Describe what priors and assumptions we used
+\end{itemize}
+
+\textbf{To Do:}
+\begin{itemize}
+\item Rephrase
+\item Maybe merge this subsection with previous subsection
+\end{itemize}
+
 We use different priors and assumptions to eliminate unphysical mass reconstructions of the lens.
@@
 
-\textbf{Shape measure}
+\subsection{Shape measure}
+% \textbf{Shape measure}
+% \begin{itemize}
+% \item Explain shape measure
+% \item Link to tests on fake data
+% \item Include one plot of fake data test -> Jonathan
+% \item Illustrate everything with example lens PG1115.
+% \end{itemize}
+\textbf{Content:}
+\begin{itemize}
+\item Describe shape measure we use (same one as second GLASS paper)
+\item Say that it has been tested with mock lenses (second GLASS paper)
+\end{itemize}
+
+\textbf{To Do:}
+\begin{itemize}
+\item Rephrase
+\item Add formula how shape is defined
+\item Summarize results of test of second GLASS paper
+\end{itemize}
 
@@
 
-Figure \ref{fig:1115rec} shows example plots of the reconstruction of the lens \textit{PG1115} illustrating this shape measure.
+% Figure \ref{fig:1115rec} shows example plots of the reconstruction of the lens \textit{PG1115} illustrating this shape measure.
 In this lens system, there is a significant misalignment between the two mass distributions.
@@
 \section{Results}\label{sec:results}
+% \begin{itemize}
+% \item Show some examples (stellar and dm contour plots, image of lens, arrival time surface, included mass)
+% \item Show money plots
+% \item Comment on a few lenses special lenses
+% \item Environmental effect?
+% \end{itemize}
+\textbf{Content:}
 \begin{itemize}
-\item Show some examples (stellar and dm contour plots, image of lens, arrival time surface, included mass)
-\item Show money plots
-\item Comment on a few lenses special lenses
-\item Environmental effect?
+\item Illustrate shape measure and reconstruction on PG1115 (with Tsevtkova time delays)
+\item Describe different misalignment plots
+\item Speculate what the plots could mean
+\end{itemize}
+
+\textbf{To Do:}
+\begin{itemize}
+\item Start from scratch for this section
+\item Use suggested structure (or think about better one)
+\item Selection of plots is probably fine, but both data points for the two different time delay estimates of PG1115
+\end{itemize}
+
+\textbf{Structure of this section}
+\begin{itemize}
+\item Reconstruction of PG1115
+\item Different ellipticities dark matter and stellar distribution
+\item Misalignment stellar and dark matter distributions
+\item Alignment dark matter and group centroid (maybe merge with previous subsection)
 \end{itemize}
@@
 
-\begin{figure*}
- \begin{center}%\hspace{-7mm}\hspace{0.8\textwidth}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_a.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_b.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_c.eps}\\
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_d.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_h.eps}\\
-  \caption{Same as Figure \ref{fig:1115rec} but using time delay estimates from \cite{1997ApJ...489...21B}.}
-  \label{fig:barkana}
- \end{center}
-\end{figure*}
+% \begin{figure*}
+%  \begin{center}%\hspace{-7mm}\hspace{0.8\textwidth}
+%   \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_a.eps}
+%   \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_b.eps}
+%   \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_c.eps}\\
+%   \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_d.eps}
+%   \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_h.eps}\\
+%   \caption{Same as Figure \ref{fig:1115rec} but using time delay estimates from \cite{1997ApJ...489...21B}.}
+%   \label{fig:barkana}
+%  \end{center}
+% \end{figure*}
 
@@
 
-\textbf{Misalignments between stellar and dark matter distributions}
+\subsection{Misalignments between stellar and dark matter distributions}
 Figure \ref{fig:moneyplots} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
@@
 
-\textbf{Ellipticities of stellar and dark matter distributions}
+\subsection{Ellipticities of stellar and dark matter distributions}
 The ellipticities of the distributions versus the mass ratio are shown in Figure \ref{fig:ellipticities}.
@@
 
-\textbf{Misalignments between the dark matter distributions and environment}
+\subsection{Misalignments between the dark matter distributions and environment}
 Figure \ref{fig:environment} we look at the alignment of the semi-major axes of the dark matter halos and vectors pointing to the centroid of the group or cluster or a companion galaxy.
@@
 \section{Conclusion}\label{sec:conclusion}
+\textbf{Content:}
 \begin{itemize}
-\item Recapitulate what were the main results
-\item Answer whether this method is promising
+\item Quick overview of what was presented
+\item State again main results
+\item Say why this results are interesting
 \item What is needed to understand such misalignments better (-> Surely need to understand environment effects better, ...)
+\end{itemize}
+
+\textbf{To Do:}
+\begin{itemize}
+\item Rephrase
+\item Maybe wait for final results
 \end{itemize}
@@
 \end{document}
+
+%%%%%%%% IGNORE THIS %%%%%%%%%%
+% Open Tasks
+%
+% --- General ---
+% - Add keywords
+% - Correct typos and reformulate some paragraphs
+% - ...
+%
+%
+% --- Introduction ---
+% - Citiations needed in parametric vs. nonparametric comparison part
+% - Citiations needed on effect of environment
+% - Section on how this work might be able to rule out certain alternative gravity models
+% - Describe theoretical expectations (ellipticities of dm halo and luminous part, misalignments, effect of environment)
+% - ...
+%
+%
+% --- Data ---
+% - More detailed description how the baryionic mass distribution was measured
+% - More details needed on galaxies in the sample? I don't think so though
+% - ...
+%
+%
+% --- Method ---
+% - Maybe more details on GLASS and how it works (cite Jonathan's upcoming paper)
+% - Plot showing how well the shape informations is recovered when applied to fake data
+% - Citation on why not monotonically decreasing radial density profiles are instable
+% - Generally look through method part
+% - ...
+%
+%
+% --- Results ---
+% - Interpretation of 
+% - Interpretation of ellipticities plot (why it is relevant that dm halos are significantly rounder)
+% - Interpretation of misalignment versus ellipticity plot ('forbidden region', alignment with semi-minor axis, very elliptical galaxies well aligned)

### 2014-06-04 limits/ms.tex
Began addressing referee's comments.

@@
 \newcommand{\pixrad}{\ensuremath{\mathrm{\tt pixrad}}}
+\newcommand{\url}[1]{\tt #1}
 
@@
 Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
-date\footnote{See e.g. {\tt http://www.masterlens.org} for a catalogue.}.
+date\footnote{See, e.g., {\url{http://masterlens.astro.utah.edu}} for a catalogue.}.
 However, this number is expected to increase to several thousand over the next
 ten years as new surveys, both
-ground-based\footnote{http://pan-starrs.ifa.hawaii.edu}$^{\rm,}$\footnote{http://www.darkenergysurvey.org}
-and space-based\footnote{http://www.euclid-ec.org} -- together with a community
+ground-based\footnote{\url{http://pan-starrs.ifa.hawaii.edu}}$^{\rm,}$\footnote{\url{http://www.darkenergysurvey.org}}
+and space-based\footnote{\url{http://www.euclid-ec.org}} -- together with a community
 of citizen-science volunteers examining the image data for
-candidates\footnote{{\tt http://spacewarps.org}} -- come online.
+candidates\footnote{\url{http://spacewarps.org}} -- come online.
 
@@
 the effect of the degeneracies.  Later work, as well as following up these
-suggestions, has introduced some further new ideas.  Four of these are
+suggestions, has introduced some further new ideas.  Five of these are
 important for the present work:
@@
 maps an observed image position $\vec\theta$ to a source position
-$\vec\beta$.  The lens can be thought of as a projected surface
-density $\Sigma$ which diverts the path of a photon instantaneously
-through the bending angle $\vec\alpha$.  The $D$ factors, as in the
-previous section, are angular diameter distances, which depend on the
-cosmological density-parameters $\Omega$, the redshifts $z_L,z_S$ of
-the lens and the source, and the Hubble parameter $H_0$, thus
+$\vec\beta$.  Using the thin lens approximation, the lens can be thought of as
+a projected surface density $\Sigma$ which diverts the path of a photon
+instantaneously through the bending angle $\vec\alpha$.  The $D$ factors, as in
+the previous section, are angular diameter distances, which depend on the
+cosmological density-parameters $\Omega$, the redshifts $z_L,z_S$ of the lens
+and the source, and the Hubble parameter $H_0$, thus
 %
@@
 &= {\textstyle\frac12} |\vec\theta - \vec\beta|^2
-   \times \frac{D_{S}}{D_{LS}} \\
+   \cdot \frac{D_{S}}{D_{LS}} \\
 &- \frac{4GD_L}{c^2}
@@
 \tau(\vec\theta) = {\textstyle\frac12} |\vec\theta - \vec\beta|^2
-                   \times \frac{D_{S}}{D_{LS}}
+                   \cdot \frac{D_{S}}{D_{LS}}
                  - \frac1\pi \int \kappa (\vec\theta')
@@
 %
-\footnote{http://www.jpcoles.com}
+\footnote{\url{http://www.jpcoles.com}}
 
@@
 to account for mass external to the modelled region. This is useful to capture
-the gross effects of a distant neighbour. \Glass\ also allows further analytic
-potential components to be included. This can be used to model substructure or
-multiple neighbours close to the main lens. The substructure may have only a
-small effect if the lens is a single galaxy, but if the lens is a group then a
+the gross effects of a distant neighbour, since there is a degeneracy between
+the ellipticity of a lens and shear field: The greater the allowed shear, the
+more circular the lens may be.  \Glass\ also allows further analytic potential
+components to be included. This can be used to model substructure or multiple
+neighbours close to the main lens. The substructure may have only a small
+effect if the lens is a single galaxy, but if the lens is a group then a
 potential can be added for each of the galaxies. A few standard functions are
@@
 \begin{enumerate}
-  \setcounter{enumi}{5}
+  \setcounter{enumi}{6}
   \item A new uniform sampling algorithm for high dimensional spaces.
@@
 generate $|\E| \sim 1000$ models.
+\hilight{Referee suggests adding some timing information here. How long does it
+take to generate 1000 models?}
 
@@
 profiles are allowed to be both steep and shallow.  The enclosed mass of the
-stars and dark matter are both fixed to be $M_{*,\mathrm{DM}} = 1.8 \times
-10^{10}$\,M$_\odot$ at the stellar scale radius $a_* = 2$\,kpc, such that the
+stars and dark matter are both fixed to be $M_{*,\mathrm{DM}} =
+1.8\e{10}$\,M$_\odot$ at the stellar scale radius $a_* = 2$\,kpc, such that the
 stars and dark matter contribute equally to the total mass at $a_*$. The dark
@@
 for lensing.  Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr,
-$\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The critical density is
+$\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The critical lensing density is
 $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
@@
 \figref{arrival surfaces} shows the lens configurations for the \mockBC\
-galaxy.  The configurations for the other galaxies are similar. Within the
-names, the labels R1, R2, R3, refer to the redshift of the sources. We have
-chosen R1=1.72, R2=0.72, and R3=0.51 so that the radial distribution of the
+galaxy. 
+The configurations for the other galaxies are similar. Within the
+names, the labels Z1, Z2, Z3 refer to the redshift of the sources. We have
+chosen Z1=1.72, Z2=0.72, and Z3=0.51 so that the radial distribution of the
 images is nearly equal. For all mocks, we do not apply any external shear field.
+Only the central image of the Z1 source is used to avoid overconstraining
+the models, otherwise all the central images would fall within the central 
+pixel and no solution exists that satisfies all locations simultaneously for
+one pixel value.
 
@@
 image is shown, although not all tests include it. The naming convention
-indicates the redshift of the sources with R1=1.72, R2=0.72, and R3=0.51.  The
-central image belongs to only to the R1 source to avoid overconstraining the
+indicates the redshift of the sources with Z1=1.72, Z2=0.72, and Z3=0.51.  The
+central image only belongs to the Z1 source to avoid overconstraining the
 models. Image colors represent a common source. Grey circles are a visual aid
@@
 
-In all cases -- despite applying no external shear to the mock lenses -- we allow a broad range of external shear in our lens model reconstructions.
-\Glass\ correctly returns a small or zero shear in all cases.
-It is possible that more complex shear fields present in real lensing galaxies could introduce further degeneracies beyond those discussed here.
-However, any such shear field can, at least in principle, be constrained by data (e.g.
-combining
-weak lensing constraints, or assuming that the shear field correlates with
-visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).
+In all cases -- despite applying no external shear to the mock lenses -- we
+allow a broad range of external shear in our lens model reconstructions.
+\Glass\ correctly returns a small or zero shear in all cases. It is possible
+that more complex shear fields present in real lensing galaxies could introduce
+further degeneracies beyond those discussed here. However, any such shear field
+can, at least in principle, be constrained by data (e.g. combining weak lensing
+constraints, or assuming that the shear field correlates with visible galaxies
+-- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).
 
@@
   \plotthree{BCExtendedDoubleR1_tmS-a-1.pdf} {BCExtendedDoubleR1_tmS-b-1.pdf} {BCExtendedDoubleR1_tmS-c-1.pdf}
-  \plotthree{BCQuadR1a_Tms-a.pdf} {BCQuadR1a_Tms-b.pdf} {BCQuadR1a_Tms-c.pdf}
-  \plotthree{AAQuadR1a_Tms-a.pdf} {AAQuadR1a_Tms-b.pdf} {AAQuadR1a_Tms-c.pdf}
 \caption{
-    Four reconstructed lenses. The first two rows consider the same mock
-    galaxy, \mockBC, for an extended double, and highlight the improved
-    constraints on the mass distribution when a lower bound is given by the
-    stellar mass. For the reconstruction, no time delays were assumed.  The
-    third row uses again the \mockBC{} mock galaxy, but with time delays
-    for a single quad and no stellar mass. With the added information from the
-    quad, the outer regions of the lens are the image radii are better
-    constrained. Finally, the fourth row shows another case of a quad with time
-    delays, but using the \mockAA{} mock galaxy. This galaxy has a shallower
-    stellar density index, and a core in the dark matter. Due to the priors
-    used in \Glass, the modelling favours steep solutions without additional
-    information.
+    Two reconstructions of the mock galaxy \mockBC for an extended
+    double without stellar mass (\textbf{Top}) and with stellar mass
+    (\textbf{Bottom}).  No time delays were assumed.  The improved constraints
+    on the mass distribution when a lower bound is given by the stellar mass is
+    evident in the reduced range of allowable models.  
 \textbf{Left:}
@@
 The surface density of the dark matter (DM; magenta); the stars (yellow); and the total (blue).
-The original mass model used to create the lens is shown in black.
+The original mass model (with stars) used to create the lens is shown in black.
 The vertical lines mark the radial positions of the images. The higher
@@
 \label{reconstruction}
+\end{figure*}
+
+\begin{figure*}
+  \plotthree{BCQuadR1a_Tms-a.pdf} {BCQuadR1a_Tms-b.pdf} {BCQuadR1a_Tms-c.pdf}
+  \plotthree{AAQuadR1a_Tms-a.pdf} {AAQuadR1a_Tms-b.pdf} {AAQuadR1a_Tms-c.pdf}
+\caption{
+    Two further reconstructions similar to \figref{reconstruction}.
+    \textbf{Top:} The mock galaxy \mockBC but including time delays for a
+    single quad and no stellar mass. With the added information from the quad,
+    the outer regions of the lens are the image radii are better constrained.
+    \textbf{Bottom:} A quad with time delays, but using the \mockAA{} mock
+    galaxy. This galaxy has a shallower stellar density index, and a core in
+    the dark matter. Due to the priors used in \Glass, the modelling favours
+    steep solutions without additional information.
+}
+\label{reconstruction 2}
 \end{figure*}
@@
 each of the test configurations with (red) and without (black) stellar mass. In
-\figref{main results}, the error is defined over radial bins of mass as:
+\figref{main results} we define the error
 %
@@
 %
-where $M$ is the mass in bin $i$ and $\tilde M$ is the mass from the mock galaxy.
+based on the mass $M(i)$ of each pixel ring $i$ and the mass $\tilde M$ from the mock galaxy. 
 In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$:
@@
 \end{equation}
-With both $f_R$ and $f_\theta$, we only consider mass up to one radial
-position passed the outermost image, since there is no longer any lensing
-information beyond that point.
+For both $f_R$ and $f_\theta$, we only consider mass up to one pixel length
+passed the outermost image, since there is no longer any lensing information
+beyond that point. This means we typically use 8 bins, linearly spaced,
+ignoring the outermost 3 bins.  The spacing changes, however, at the border
+between the high resolution region in the middle.
 
@@
 Within each panel are six groups of results for each of six lens morphologies. Each morphology
-considered the presence of time delays (T=yes,t=no) and a central image (M=yes,m=no). The black markers are for tests
+considered the presence of time delays (TD) and a central image (central). The black markers are for tests
 that did not include the stellar mass as a lower bound constraint, while the red markers
@@
 increase (and therefore for $f$ to decrease). When both time delays and a
-central image are present (TM), the quality is highest. A double is known to
+central image are present (TD+central), the quality is highest. A double is known to
 provide very little constraint on the mass distribution. This is particularly
@@
 We can also more directly probe the recovery of the shape of the mass
-distribution by defining a global measure of lens shape:
+distribution by considering the ratio of the major and minor axes $\lambda_1,
+\lambda_2$ of the inertia ellipse. If they are equal, the mass is distributed
+uniformly on the projected disc. The more dissimilar they are, the more
+elliptical the mass distribution. We define the global measure of lens shape as
 %
@@
 recovery it appears more important to have time delay data and/or a central
-image (T,M) than to have a quad or multiple sources with wide redshift
+image (TD,TD+central) than to have a quad or multiple sources with wide redshift
 separation. In all cases, the stellar mass little-aids the recovery, reflecting
@@
 equations for each pixel. Although we assume a perfect recovery of the stellar
-mass here, it is straightforward to add errors as the stellar mass constraint
-remains linear: $\kappa_n = \kappa_{dm,n} + \epsilon \kappa_{s,n}$, where
-$\epsilon \sim 1$ is an additional error parameter.
+mass with no error on the lower mass bound, it is straightforward to add errors
+as the stellar mass constraint remains linear: $\kappa_n = \kappa_{dm,n} +
+\epsilon \kappa_{s,n}$, where $\epsilon \sim 1$ is an additional error
+parameter.
 
@@
 calculated for one model model (extracted from the full ensemble) of the
-\mockBC{} Quad with time delays and stellar mass (left), and the same but
-without stellar mass (right).  In both cases, we calculate curves for two
+\mockBC{} Quad with time delays and no stellar mass (left), and the same but
+with stellar mass (middle).  In both cases, we calculate curves for two
 extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red).
@@
 The authors would like to thank Sarah Bryan and Walter Dehnen for creating the
-particle distributions for the mock galaxies. JIR would like to acknowledge
-support from SNF grant PP00P2\_128540/1.
+particle distributions for the mock galaxies, and the anonymous referee for
+many usual suggestions which has improved the manuscript. JIR would like to
+acknowledge support from SNF grant PP00P2\_128540/1.
+
+\bibliographystyle{mn2e}
+\bibliography{ms}
 
@@
 In this appendix, we explore the effect of the radial symmetry prior.
-\figref{fig:no_symm_prior} shows results for a single quad (top two rows) and an
-extended double (bottom two rows) without the radial prior; in both cases, we do not use the stellar mass
-constraints.
-The bottom row of each group uses time delay data.
-Without time delay data or the radial symmetry prior, the results for the quad are poor -- particularly the shape recovery.
-Including time delays, the results are similar to the case with the radial prior (\figref{reconstruction} and \figref{2d mass reconstruction}).
-Similarly, for the extended double the results without time delays are poor.
-Even with time delays, the shape is not well recovered without the radial prior, as expected.
+\figref{fig:no_symm_prior} shows results for a single quad (top two rows) and
+an extended double (bottom two rows) without the radial prior; in both cases,
+we do not use the stellar mass constraints. The bottom row of each group uses
+time delay data. Without time delay data or the radial symmetry prior, the
+results for the quad are poor -- particularly the shape recovery. Including
+time delays, the results are similar to the case with the radial prior
+(\figref{reconstruction} and \figref{2d mass reconstruction}). Similarly, for
+the extended double the results without time delays are poor. Even with time
+delays, the shape is not well recovered without the radial prior, as expected.
 
@@
 
-\bibliographystyle{mn2e}
-\bibliography{ms}
-
 \end{document}

### 2014-06-04 limits/ms.tex
Addressed major comment and partially the medium one.

@@
 
-In this paper, we use a new program -- \Glass\ (Gravitational Lensing AnalysiS
-Software) -- to determine what combination of lensing, stellar mass, and
+In this paper we demonstrate which combination of lensing, stellar mass, and
 stellar kinematic constraints best constrain the projected mass profile and
-shape of several gravitational lens produced from mock data.  The
-compute-intensive core of \Glass\ is a parallel implementation of the
-high-dimensional sampling algorithm from \cite{2012MNRAS.425.3077L}.  Around
-that core, \Glass\ has extensible code (in software terminology, a framework)
-in Python, encoding the lens equation, a basis and priors for the mass
-distribution, and various post-processing and visualisation modules.  \Glass\
-is described in \secref{sec:glass}.  In \secref{sec:theory}, we review the key
-elements of lensing theory, stellar population synthesis, and stellar dynamics
-we will need. In \secref{sec:mockdata}, we describe our mock data. In
+shape of several gravitational lens produced from mock data. In particular,
+we introduce the idea of using estimates of the stellar mas content to place
+lower bounds on the lensing mass.
+We also introduce a new lens modeling framework  -- \Glass\ (Gravitational
+Lensing AnalysiS Software). The compute-intensive core of \Glass\ is a parallel
+implementation of the high-dimensional sampling algorithm from
+\cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has extensible code (in
+software terminology, a framework) in Python, encoding the lens equation, a
+basis and priors for the mass distribution, and various post-processing and
+visualisation modules.
+
+\Glass\ is described in \secref{sec:glass}.  In \secref{sec:theory}, we review
+the key elements of lensing theory, stellar population synthesis, and stellar
+dynamics we will need. In \secref{sec:mockdata}, we describe our mock data. In
 \secref{sec:results}, we present our results from applying \Glass\ to these
@@
 everywhere. We must therefore provide additional linear constraints so that we
-only sample physical models. The explicit implementation for these priors has
+only sample physical models. Below we list typical constraints that \Glass\
+provides. The explicit implementation for these priors has
 been explained in \cite{2008ApJ...679...17C}, but can be summarised as
@@
 \item The density must be non-negative everywhere.
-\item The density profile must have a slope everywhere $\le 0$.
+\item The azimuthally averaged density profile must have a slope everywhere $\le 0$.
+\item Image parity is enforced.
 \item The local gradient everywhere must point within $45^{\circ}$ of the center.
 \item Density variations must be smooth.
-\item Image parity is enforced.
-\item The density is inversion symmetric. (Optional)
+\item The density is inversion symmetric.
 \end{enumerate}
 
-Prior (ii) is necessary to prevent rings from forming where the inner region is
-less dense. This would be unusual for a galaxy or a cluster. Prior (vi)
-enforces a radial symmetry that requires radially opposed pixels (i.e., on
-opposite sides of the center) to be equal. This prior is particularly important
-for modelling doubles which must be symmetric. If a lens is suspected to be
-symmetric this can also significantly improve the modelling time for quads.
+The first three of these priors are very important for creating physically
+meaningful lenses. Prior (ii) is necessary to prevent rings from forming where
+the inner region is less dense. This would be unusual for a galaxy or a
+cluster. Prior (iv) can be relaxed somewhat by increasing the angle. The
+smoothness prior (v) requires pixel values to be less than a constant factor of
+the average neighbor value. This can be relaxed by increasing the constant or
+completely disabled. For this paper, we have chosen \emph{not} to use this
+prior, and therefore allow for the presence of small density substructure.
+Prior (vi) enforces a radial symmetry that requires radially opposed pixels
+(i.e., on opposite sides of the center) to be equal. This prior is particularly
+important for modelling doubles which must be symmetric. If a lens is suspected
+to be symmetric this can also significantly improve the modelling time for
+quads.
+
+While most of these priors have been selected for modelling galaxies, there
+are several ways to address clusters or allow for the presence of substructure.
+As previously described, one can add any number of additional analytic 
+potentials inside or outside the main modelling pixelation area. For instance,
+in a cluster, one can explicitly account for galaxies with power law potentials.
+Furthermore, Priors (iv) and (v) and be relaxed or disabled. We have perfomed
+preliminary testing of these ideas several common clusters and are encouraged
+by the results. We will reserve a full analysis for a future publication.
 
@@
 sampled models are referred to as an ensemble $\E = \{\M_i\}$, where we usually
-generate $|\E| \sim 1000$ models.
-\hilight{Referee suggests adding some timing information here. How long does it
-take to generate 1000 models?}
+generate $|\E| \sim 1000$ models. One can choose to further process these
+models to impose further priors that may be difficult to enforce during the
+modeling process. For instance, non-linear constraints, or simply filtering
+of models that do not meet some criteria can be excluded, or weighted against.
+For our current analysis, we do not exclude any models.
+
+The time to generate the model ensemble is mostly a function of the size of the
+parameter space. The MCMC algorithm has a ``warm-up'' phase where it estimates
+the size and shape of each dimension in the solution space.  Once this has been
+completed, the models are sampled very quickly. In fact, there is little
+difference between generating 1,000 or 10,000 models. For our problems, the
+typical ``warm-up'' time was about 4s, and the modelling time was 20s using a
+parallel shared-memory machine with 40 cores.
 
@@
 \end{equation}
+%
 For both $f_R$ and $f_\theta$, we only consider mass up to one pixel length

### 2014-06-04 limits/ms.tex
More corrections.

@@
 
-\item {\bf Model ensembles:} Model ensembles, exploring a diverse
-  range of possible mass distributions that nonetheless all fit the data,
-  are a way of combating the non-uniqueness of models.  Such ensembles are
-  possible in parametric models \citep{1999AJ....118...14B} but are more
-  common in free-form models, where -- since such models are deliberately under-constrained -- they become vital 
+\item {\bf Model ensembles:} Model ensembles, exploring a diverse range of
+    possible mass distributions that nonetheless all fit the data, are a way of
+    combating the non-uniqueness of models.  Such ensembles are possible in
+    parametric models \citep{1999AJ....118...14B} but are more common in
+    free-form models, where -- since such models are deliberately
+    under-constrained -- they become vital
     \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.
@@
 so-called mass-sheet degeneracy, which is that image positions remain invariant
-if $\tau(\vec\theta)$ is multiplied by an arbitrary constant.  This corresponds
-to rescaling the surface density at the images $\kappa(\vec\theta)$. In fact
+if $\tau(\vec\theta)$ is multiplied by an arbitrary constant.  
+\hilight{This corresponds
+to rescaling the surface density at the images $\kappa(\vec\theta)$.} In fact
 there are infinitely many degeneracies \citep{2000AJ....120.1654S} because any

### 2014-06-13 limits/ms-prev.tex
Updated figures with 'Z' labels and better shaded errors.

--- 2014-01-28 limits/ms.tex
@@
 \newcommand{\eps}{\ensuremath{\varepsilon}}
-
 \newcommand{\Eavg}{\ensuremath{\langle \E \rangle}}
-
-\newcommand{\hilight}[1]{{\bf \color{red} #1}}
+\newcommand{\Mddd}{\ensuremath{M}}
+%\newcommand{\Mddd}{\ensuremath{M_\mathrm{3D}}}
+\newcommand{\pixrad}{\ensuremath{\mathrm{\tt pixrad}}}
+\newcommand{\url}[1]{\tt #1}
 
@@
 %For deprojection algorithm: 
-\def\cth{\cos\theta}
-\def\sth{\sin\theta}
-\def\dth{{\rm d}\theta}
+\newcommand{\cth}[1][]{\cos^{#1}\theta}
+\newcommand{\sth}[1][]{\sin^{#1}\theta}
+\def\dth{d\theta}
+
+%-------------------------------------------------------------------------------
+% Macros for multiple plots
+%-------------------------------------------------------------------------------
 
@@
 \\
-$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
-$^2$\hilight{Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom} \\
-$^3$\hilight{Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland}
+$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$45 avenue des Etats-Unis, 78035, Versailles, France\\
+$^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
+$^3$Physik-Institut, Universit\"at Z\"urich, 190 Winterthurerstrasse, 8057, Z\"urich, Switzerland
 }
@@
 where the stars dominate the central potential -- can also break the steepness
-degeneracy, giving a recovery almost as good as having time delay data or
-multiple source redshifts; (iv) stellar kinematics provide a robust measure of the mass at the half light radius of the stars $r_{1/2}$ that can also break the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v) if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the stellar velocity anisotropy
-$\beta$ -- an interesting quantity in its own right. Where
-information on the mass distribution from lensing and/or other probes becomes
-redundant, this opens up the possibility of using strong lensing to constrain
-cosmological models. We will study this, and present the first results from
-\Glass\ applied to real data, in forthcoming papers.
+degeneracy, giving a recovery for doubles almost as good as having a quad with time delay data, or
+multiple source redshifts; (iv) stellar kinematics provide a robust measure of
+the mass at the half light radius of the stars $r_{1/2}$ that can also break
+the steepness degeneracy if the Einstein radius $r_E \neq r_{1/2}$; and (v)
+if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the
+stellar velocity anisotropy $\beta$ -- an interesting quantity in its own
+right. Where information on the mass distribution from lensing and/or other
+probes becomes redundant, this opens up the possibility of using strong lensing
+to constrain cosmological models. 
 \end{abstract}
@@
 
-Strong gravitational lenses are rare.
-Since the discovery of the first lens Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to date\footnote{See e.g.
-{\tt http://www.masterlens.org} for a catalogue.}.
-However, this number is expected to increase to
-several thousand over the next ten years as new surveys, both
-ground-based\footnote{http://pan-starrs.ifa.hawaii.edu}$^{\rm,}$\footnote{http://www.darkenergysurvey.org}
-and space-based\footnote{http://www.euclid-ec.org} -- together with a
-community of citizen-science volunteers examining the image data for
-candidates\footnote{{\tt http://spacewarps.org}} -- come online.
-
-Since lensing depends only on gravity, strong lenses offer a
-unique window onto dark matter and cosmology \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}. However, 
-extracting dark matter properties or cosmological constraints from these lensing data will require sophisticated modelling.
-In particular, with an unprecedented data set imminent, it is prudent to look again at systematic errors in the lens models to determine what quality of data (in particular complementary data from stellar/gas kinematics, lens time delays and/or stellar mass constraints) are required to address problems of interest.
-It is towards that goal that this present work is directed.
-
-To see why lens modelling details are of crucial importance, let us recall the
-essential quantities that appear in lensing.  First we have the
-distances. Let $D_L$, $D_S$, $D_{LS}$ be the angular-diameter
-distances to the lens, source, and from lens to source; these are all proportional to $c/H_0$ (where $c$ is the speed of light in vacuo, and $H_0$ the Hubble constant), with additional terms that depend on the particular choice of cosmology \citep[e.g.][]{1999coph.book.....P}.
-Typically:
-\begin{equation}
-D_L \approx z \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
-\end{equation}
-
+Strong gravitational lenses are rare. Since the discovery of the first lens
+Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
+date\footnote{See, e.g., {\url{http://masterlens.astro.utah.edu}} for a catalogue.}.
+However, this number is expected to increase to several thousand over the next
+ten years as new surveys, both
+ground-based\footnote{\url{http://pan-starrs.ifa.hawaii.edu}}$^{\rm,}$\footnote{\url{http://www.darkenergysurvey.org}}
+and space-based\footnote{\url{http://www.euclid-ec.org}} -- together with a community
+of citizen-science volunteers examining the image data for
+candidates\footnote{\url{http://spacewarps.org}} -- come online.
+
+Since lensing depends only on gravity, strong lenses offer a unique window onto
+dark matter and cosmology \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}.
+However, extracting dark matter properties or cosmological constraints from
+these lensing data will require sophisticated modelling. In particular, with an
+unprecedented data set imminent, it is prudent to look again at systematic
+errors in the lens models to determine what quality of data (in particular
+complementary data from stellar/gas kinematics, lens time delays and/or stellar
+mass constraints) are required to address problems of interest. It is towards
+that goal that this present work is directed.
+
+To see why lens modelling details are of crucial importance, let us
+recall the essential quantities that appear in lensing (see also \S\ref{sec:theory} for a more detailed exposition). First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
+angular-diameter distances to the lens, source, and from lens to
+source; these are all proportional to $c/H_0$ but have factors
+that depend on the particular choice of cosmology\footnote{Here, $c$ is the speed of light in vacuo and $H_0$ is the Hubble parameter.}.  Typically:
+%
+\begin{equation}
+D_L \approx z_L \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
+\end{equation}
+where $z_L$ is the redshift of the lens. 
+%
 For multiple images, the sky-projected density must exceed the critical
-density \citep[e.g.][]{1992grle.book.....S}:
-
-\begin{equation}
-\Sigma_{\rm crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
-\end{equation}
-in some region.  The separation between the lensed images is of order
+density in some region:
+%
+\begin{equation}
+\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
+\end{equation}
+where $G$ is Newton's gravitational constant. 
+%
+The angular separation between the lensed images is of order
 the Einstein radius $\theta_E$, which is related to
 the mass by:
+%
 \begin{equation}
@@
 \end{equation}
-where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$) is the gravitational radius. If the source is a
-quasar or otherwise rapidly variable, a time delay $\Delta t$ in the variability
-will be present where:
-\begin{equation}
-\Delta t \sim R_G/c \,.
-\end{equation}
-So in principle, one can not only measure the mass of the lens, one
-can use the dependence on the cosmology-dependent $D$ factors to
-extract the cosmological model and all its parameters.
-\cite{1937ApJ....86..217Z} drew attention to the former, and
-\cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the latter,
-all long before lenses were discovered.  The difficulty with actually doing this, however, became
-apparent soon after the discovery of the first lens by
-\cite{1979Natur.279..381W}.  In the first ever paper on lens
-modelling, \cite{1981ApJ...244..736Y} found that many plausible mass
-distributions could reproduce the data.
-
-\cite{1981ApJ...244..736Y} were remarkably prescient about the
-subsequent development of lens modelling.  First, they introduced the
-technique of choosing a parametric form for the lensing mass and then
-fitting for the parameters, which is still the most common strategy
-\citep[see for example][]{2010GReGr..42.2151K,2011A&ARv..19...47K}.
-Second, they pointed out the non-uniqueness of lens models -- lensing
-degeneracies.  Third, they suggested combining lensing data with
-stellar kinematics and X-rays, to reduce the effect of the
-degeneracies.  Later work, as well as following up these suggestions,
-has introduced some further new ideas.  Four of these are important for the present
-work:
+%
+where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$)
+is the gravitational radius. If the source is a quasar or otherwise rapidly
+variable, a time delay $\Delta t$ in the variability will be present where
+%
+\begin{equation}
+\Delta t \sim R_G/c
+\end{equation}
+%
+So in principle, one can not only measure the mass of the lens, one can use the
+dependence on the cosmology-dependent $D$ factors to extract the cosmological
+model and all its parameters.  \cite{1937ApJ....86..217Z} drew attention to the
+former, and \cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the
+latter, all long before lenses were discovered.  The difficulty with actually
+doing this, however, became apparent soon after the discovery of the first lens
+by \cite{1979Natur.279..381W}.  In the first ever paper on lens modelling,
+\cite{1981ApJ...244..736Y} found that many plausible mass distributions could
+reproduce the data.
+
+\cite{1981ApJ...244..736Y} were remarkably prescient about the subsequent
+development of lens modelling.  First, they introduced the technique of
+choosing a parametric form for the lensing mass and then fitting for the
+parameters, which is still the most common strategy \citep[see for
+example][]{2010GReGr..42.2151K,2011A&ARv..19...47K}.  Second, they pointed out
+the non-uniqueness of lens models -- lensing degeneracies.  Third, they
+suggested combining lensing data with stellar kinematics and X-rays, to reduce
+the effect of the degeneracies.  Later work, as well as following up these
+suggestions, has introduced some further new ideas.  Four of these are
+important for the present work:
+%
 \begin{enumerate}
-\item {\bf Free-form modelling:} In `free-form' or non-parametric modelling, there is no specified parametric form for
-  the mass distribution.  There are still assumptions (or priors) on
-  the mass distribution, such as smoothness or being centrally
-  concentrated
+\item {\bf Free-form modelling:} In `free-form' or non-parametric
+  modelling, there is no specified parametric form for the mass
+  distribution.  There are still assumptions (or priors) on the mass
+  distribution, such as smoothness or being centrally concentrated
   \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2009A&A...500..681M,2010ApJ...723.1678C}
-  but these are much less restrictive than parametric forms (\cite{2006MNRAS.367.1209L} implemented a particularly elegant prior, which is that the mass distribution must be non-negative and no
-  extra images are produced). To be concrete, we define from here on:
+  but these are much less restrictive than parametric forms.  A
+  particularly elegant prior is implemented by
+  \cite{2006MNRAS.367.1209L}, requiring that the mass distribution to
+  be non-negative and no extra images allowed. To be concrete, we
+  define from here on:
 
@@
 
-  Being under-constrained, it is then {\it necessary} to explore model degeneracies rather than find a single `best-fit' solution. Free-form models are more commonly used with
-  cluster lenses \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S}, but
-  can be used with galaxy lenses as well, where their less restrictive
-  assumptions can be important.  For example, in time-delay galaxy
-  lenses, parametric models have historically led to tension with independent measures of the Hubble parameter
-  $H_0$ \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are resolved once the less restrictive assumptions of free-form models are permitted \citep{2007ApJ...667..645R}.
-\item Model ensembles, exploring a diverse range of possible mass
-  distributions that nonetheless all fit the data, are a way of
-  combating the non-uniqueness of models.  Such ensembles are
-  possible in parametric models \citep{1999AJ....118...14B} but are
-  more common in free-form models
+  Being under-constrained, it is then {\it necessary} to explore model
+  degeneracies rather than finding a single `best-fit'
+  solution. Free-form models are more commonly used with cluster
+  lenses
+  \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S},
+  but can be used with galaxy lenses as well, where their less
+  restrictive assumptions can be important.  For example, in
+  time-delay galaxy lenses, parametric model measures of the Hubble parameter $H_0$ have historically been at 
+  tension with independent measures 
+  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
+  resolved once the less restrictive assumptions of free-form models
+  are permitted \citep{2007ApJ...667..645R}.  Hybrid methods, using a
+  mass grid on top a parametric model, have also been explored
+  \citep[e.g.,][]{2010MNRAS.408.1969V}.
+
+\item {\bf Model ensembles:} Model ensembles, exploring a diverse
+  range of possible mass distributions that nonetheless all fit the data,
+  are a way of combating the non-uniqueness of models.  Such ensembles are
+  possible in parametric models \citep{1999AJ....118...14B} but are more
+  common in free-form models, where -- since such models are deliberately under-constrained -- they become vital 
   \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.
-\item {\bf Stellar kinematic constraints:} This was first suggested by \citet{2002MNRAS.337L...6T} as a means to break lensing degeneracies and determine cosmological parameters.
-This works because stellar kinematics can provide an independent estimate of the Einstein radius, via the virial theorem:
-%
-\begin{equation}
-  \frac{\langle v^2_{\rm los}\rangle}{c^2} \approx
+
+\item {\bf Stellar kinematic constraints:} This was first suggested by
+  \citet{2002MNRAS.337L...6T} as a means to break lensing
+  degeneracies. The idea is that stellar kinematics can provide an
+  independent estimate of the Einstein radius, via the virial theorem:
+%
+\begin{equation}
+  \frac{\langle v^2_\mathrm{los}\rangle}{c^2} \approx
   \frac{\theta_E}{6\pi} \frac{D_S}{D_{LS}}
@@
 \end{equation}
- where $\langle v^2_{\rm los}\rangle$ is the projected stellar velocity dispersion, and the above relation becomes exact for isothermal lenses.  The use of
-  two-dimensional kinematics by \cite{2011MNRAS.415.2215B} is
+%
+where $\langle v^2_\mathrm{los}\rangle$ is the line of sight stellar
+velocity dispersion, and the above relation becomes exact for
+isothermal lenses.
+This can then be used to probe cosmological parameters if lenses are known to be isothermal \citep[e.g.][]{2012MNRAS.424.2864C}; or to break the steepness degeneracy in the more general situation (see \S\ref{sec:kinematics}).
+The technique has since been applied to many lenses \citep[e.g.][]{2006ApJ...649..599K,2008ApJ...682..964B}.
+Going further, the
+use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is
 especially interesting.
-\item {\bf Stellar mass constraints:} The stellar mass in a lens can be inferred from photometry and
-  compared with the total mass
-  \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
-  Since the inferred stellar mass depends on the assumed IMF,
-  lenses in which stellar mass dominates can be used to derive upper
-  bounds on the stellar $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds
-  on stellar $M/L$ have also been claimed \citep{2013MNRAS.428.3183D}
-  but these require upper-bound assumptions about the dark-matter
-  profile. \hilight{JR. I feel like we need more citations here and throughout. We must be skipping over an Armada of literature.}
-\item {\bf Testing modelling strategies:} Using mock data to see how well a given model can recover
-  simulated lenses is increasingly being recognised as essential.  Simple
-  blind tests have appeared in earlier work \citep[for example, Figure
-    2 in][]{2000AJ....119..439W}, but more recently, tests against
-  dynamically simulated galaxies or clusters are favoured
+
+\item {\bf Stellar mass constraints:} The stellar mass in a lens can be
+    inferred from photometry and compared with the total mass
+    \citep[e.g.][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
+    the inferred stellar mass depends on the assumed IMF, lenses in which
+    stellar mass dominates can be used to derive upper bounds on the stellar
+    $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds on stellar $M/L$ have also
+    recently been claimed by fitting $\Lambda$CDM semi-analytic models to the tilt of the fundamental plane \citep{2013MNRAS.428.3183D}.
+
+\item {\bf Testing modelling strategies:} Using mock data to see how well a
+    given model can recover simulated lenses is increasingly being recognised
+    as essential.  Simple blind tests have appeared in earlier work \citep[for
+    example, Figure 2 in][]{2000AJ....119..439W}, but more recently, tests
+    against dynamically simulated galaxies or clusters are favoured
     \citep{2007ApJ...667..645R,2007MNRAS.380.1729L,2009A&A...500..681M,2009MNRAS.393.1114B,2010ApJ...723.1678C}.
@@
 
-There are two further key modelling ideas in the literature that we will not touch upon in this present work: to use
-X-ray intensity and temperature profiles as a mass constraint
-\citep[e.g.][]{2013ApJ...765...25N}; and to model
-multiple lenses simultaneously, with one or more cosmological
-parameters variable but shared between the lenses. This latter strategy has
-been used to constrain $H_0$ from time delay lenses 
-\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P}.
-(In principle, cosmological parameters can be constrained even from a
-single lens if the data are good enough. Some recent models have attempted this starting from a prior
-based on the Cosmic Microwave Background (CMB) radiation \citep{2010Sci...329..924J,2013arXiv1306.4732S}.)
-
-In this paper, we use a new program -- \Glass\ (Gravitational Lensing AnalysiS Software) -- to determine what
-combination of lensing, stellar mass, and stellar kinematic
-constraints best constrain the projected mass profile and shape of several
-gravitational lens produced from mock data.  The compute-intensive core of \Glass\ is a
-parallel implementation of the high-dimensional sampling algorithm
-from \cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has
-extensible code (in software terminology, a framework) in Python,
-encoding the lens equation, a basis and priors for the mass
+There are three further key modelling ideas in the literature that we will not
+touch upon in this present work: to use X-ray intensity and temperature
+profiles as a mass constraint \citep[e.g.][]{2013ApJ...765...25N}; and to model
+multiple lenses simultaneously, with one or more cosmological parameters
+variable but shared between the lenses. This latter strategy has been used to
+constrain $H_0$ from time delay lenses
+\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P} and
+recently the cosmological parameters $\Omega$ as well
+\citep{2014MNRAS.437..600S}.  Third, it is in principle possible to estimate
+the $\Omega$ parameters even from a single lens, if there are lensed sources at
+multiple redshifts \citep{2014MNRAS.437.2461L} or by using additional priors 
+\citep{2010Sci...329..924J,2013arXiv1306.4732S}.
+
+In this paper, we use a new program -- \Glass\ (Gravitational Lensing AnalysiS
+Software) -- to determine what combination of lensing, stellar mass, and
+stellar kinematic constraints best constrain the projected mass profile and
+shape of several gravitational lens produced from mock data.  The
+compute-intensive core of \Glass\ is a parallel implementation of the
+high-dimensional sampling algorithm from \cite{2012MNRAS.425.3077L}.  Around
+that core, \Glass\ has extensible code (in software terminology, a framework)
+in Python, encoding the lens equation, a basis and priors for the mass
 distribution, and various post-processing and visualisation modules.  \Glass\
-is described in \secref{sec:glass}.  In \secref{sec:theory}, we
-review the key elements of lensing theory, stellar population synthesis, and
-stellar dynamics we will need.
-In \secref{sec:mockdata}, we describe our mock data.
-In \secref{sec:results}, we present our results from applying \Glass\ to these mock data.
-Finally, in \S\ref{sec:conclusions} we present our conclusions.
+is described in \secref{sec:glass}.  In \secref{sec:theory}, we review the key
+elements of lensing theory, stellar population synthesis, and stellar dynamics
+we will need. In \secref{sec:mockdata}, we describe our mock data. In
+\secref{sec:results}, we present our results from applying \Glass\ to these
+mock data. Finally, in \secref{sec:conclusions} we present our conclusions.
 
@@
 \end{equation}
-We can simplify the above equation by introducing a dimensionless time $\tau$ and density $\kappa$:
-
-\begin{equation}
-\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \,\,\,;\,\,\, \kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_L}
-\end{equation}
+%
+We can simplify the above equation by introducing a dimensionless time $\tau$
+and density $\kappa$: 
+%
+\begin{equation}
+\tau(\vec\theta) = \frac{ct(\vec\theta)}{(1+z_L)D_{L}} \quad ; \quad 
+\kappa(\vec\theta) \equiv \frac{\Sigma(\vec\theta)}{\Sigma_\mathrm{crit}}
+\end{equation}
+%
 and hence rewrite \eqnref{full arrival time} as:
+%
 \begin{equation}
 \tau(\vec\theta) = {\textstyle\frac12} |\vec\theta - \vec\beta|^2
-                   \times \frac{D_{S}}{D_{LS}}
+                   \cdot \frac{D_{S}}{D_{LS}}
                  - \frac1\pi \int \kappa (\vec\theta')
@@
 \end{equation}
-The scaled arrival time $\tau$ is like a solid angle. It is of order
-the area (in steradians) of the full lensing system. The expression
-$|\vec\theta - \vec\beta|^2$ is of order the image-separation
-squared, and the other terms are of similar size.  For this reason, is
-convenient to measure $\tau$ in arcsec$^{2}$.
-
-Lensing observations provide information only at $\vec\theta$ where
-there are images.  Hence, the arrival-time surface $\tau(\vec\theta)$
-is not itself observable.  Its usefulness lies in that observables can
-be derived from it.  An image observed at $\vec\theta_1$ implies
-that $\nabla\tau(\vec\theta_1)=0$.  A measurement of time delays
-between images at $\theta_1$ and $\theta_2$ implies that
-$t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both these
-types of observations give contraints that are linear in $\kappa$ and
+%
+The scaled arrival time $\tau$ is like a solid angle. It is of order the area
+(in steradians) of the full lensing system. The expression $|\vec\theta -
+\vec\beta|^2$ is of order the image-separation squared, and the other terms are
+of similar size.  For this reason, is convenient to measure $\tau$ in
+arcsec$^{2}$.
+
+Lensing observations provide information only at $\vec\theta$ where there are
+images.  Hence, the arrival-time surface $\tau(\vec\theta)$ is not itself
+observable.  Its usefulness lies in that observables can be derived from it.
+An image observed at $\vec\theta_1$ implies that $\nabla\tau(\vec\theta_1)=0$.
+A measurement of time delays between images at $\theta_1$ and $\theta_2$
+implies that $t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both
+these types of observations give constraints that are linear in $\kappa$ and
 $\vec\beta$.
@@
 
-For many galaxy lenses, the gravitational potential in the inner
-region is dominated by the stellar mass.  Steller mass can be
-estimated by combining photometry and colours with models of the
-stellar populations.  Such estimates are reasonably robust, even if
-the star-formation history is very uncertain: given a
-stellar-population model \citep[such as][]{2003MNRAS.344.1000B} and an
-initial mass function (IMF), the stellar mass can be inferred to 0.1
-to 0.2 dex using just two photometric bands \citep[see e.g., Figure~1
-  in][]{2008MNRAS.383..857F}.  By comparing the lensing-mass and
-stellar-mass profiles in elliptical galaxies, it is possible to
-extract the radial dependence of the baryonic vs dark-matter fraction
-\citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
-
-The major uncertainty at present in the stellar mass is probably the
-IMF.  In the lensing galaxy of the Einstein Cross, the IMF cannot be
-much more bottom-heavy than \cite{2003PASP..115..763C}, because
-otherwise the stellar mass would exceed the lensing mass
-\cite{2010MNRAS.409L..30F}.  More massive galaxies, however, do appear
-to have more of their stellar mass in low-mass stars.  This is
-indicated by molecular spectral features characteristic of low mass
-stars
+For many galaxy lenses, the gravitational potential in the inner region is
+dominated by the stellar mass.  Stellar mass can be estimated by combining
+photometry and colours with models of the stellar populations.  Such estimates
+are reasonably robust, even if the star-formation history is very uncertain:
+given a stellar-population model \citep[such as][]{2003MNRAS.344.1000B} and an
+initial mass function (IMF), the stellar mass can be inferred to 0.1 to 0.2 dex
+using just two photometric bands \citep[see e.g., Figure~1 in][]{2008MNRAS.383..857F}.
+By comparing the lensing-mass and stellar-mass profiles in elliptical galaxies,
+it is possible to extract the radial dependence of the baryonic vs dark-matter
+fraction \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
+
+The major uncertainty at present in the stellar mass is probably the IMF.  In
+the lensing galaxy of the Einstein Cross, the IMF cannot be much more
+bottom-heavy than \cite{2003PASP..115..763C}, because otherwise the stellar
+mass would exceed the lensing mass \cite{2010MNRAS.409L..30F}.  More massive
+galaxies, however, do appear to have more of their stellar mass in low-mass
+stars.  This is indicated by molecular spectral features characteristic of low
+mass stars
 \citep{2004ApJ...614L.101C,2012ApJ...747...69C,2013MNRAS.429L..15F}.
@@
 
-\Glass\ is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
-\PixeLens\ but completely rewritten in Python and C. 
-The most compute intensive
-portion was written in C but Python was chosen because of its flexibility as a 
-language and for its large scientific library support. The flexibility allows 
-\Glass\ to have quite sophisticated behavior while at the same time simplifying the 
-user experience and reducing the overall development time. One of the striking
-features is that the input file to \Glass\ is itself a Python program.
-Understanding Python is not necessary for the most basic use, but this allows
-a user to build complex analysis of a model directly into the input file. \Glass\
-may also be used as an external library to other Python programs.  The software
-is freely available for download or from the author%
-%
-\footnote{http://www.jpcoles.com.}.
+\Glass\ is the Gravitational Lensing AnalysiS Software. It extends and develops
+some of the concepts from the free form modelling tool \PixeLens\
+\citep{Saha2004,2008ApJ...679...17C}, but with all new code.  The most compute
+intensive portion was written in C but Python was chosen because of its
+flexibility as a language and for its large scientific library support. The
+flexibility allows \Glass\ to have quite sophisticated behavior while at the
+same time simplifying the user experience and reducing the overall development
+time. One of the striking features is that the input file to \Glass\ is itself
+a Python program.  Understanding Python is not necessary for the most basic
+use, but this allows a user to build complex analysis of a model directly into
+the input file. \Glass\ may furthermore be used as an external library to other
+Python programs.  {\it The software is freely available for download or from
+the first author.}%
+%
+\footnote{\url{http://www.jpcoles.com}}
 
@@
 %
-\PixeLens\ only allows for a shear term to be added to the potential (as shown
-later in \eqnref{shear}) to account for mass external to the modelled region. This
-is useful to capture the gross effects of a distant neighbour. \Glass\ also
-has a shear term but additionally allows for analytic potentials to
-be included. This can be used to model substructure or multiple neighbors close
-to the main lens. The substructure may have only a small effect if the lens is
-a single galaxy, but if the lens is a group then a potential can be added for
-each of the galaxies. A few standard functions are already included in \Glass\
-including those for a point mass, a power law distribution, or an isothermal (a
-particular case of the power law).
+A shear term can be added to the potential, as shown later in \eqnref{shear},
+to account for mass external to the modelled region. This is useful to capture
+the gross effects of a distant neighbour. \Glass\ also allows further analytic
+potential components to be included. This can be used to model substructure or
+multiple neighbours close to the main lens. The substructure may have only a
+small effect if the lens is a single galaxy, but if the lens is a group then a
+potential can be added for each of the galaxies. A few standard functions are
+already included in \Glass\ including those for a point mass, a power law
+distribution, or an isothermal (a particular case of the power law).
 %
@@
 %
-We can continue adding terms to account for other potentials. For instance,
-we may want to impose a base potential over the field, or add potentials
-from the presence of other galaxies in the field. \Glass\
-already includes potentials for a point mass or an exponential form, but custom
-potentials are straightforward to add and can be included directly in the input file.
-If the stellar density $\kappa_s$ has been estimated we can use this as a lower bound
+We can continue adding terms to account for other potentials. For instance, we
+may want to impose a base potential over the field, or add potentials from the
+presence of other galaxies in the field. \Glass\ already includes potentials
+for a point mass or an exponential form, but custom potentials are
+straightforward to add and can be included directly in the input file.  If the
+stellar density $\kappa_s$ has been estimated we can use this as a lower bound
 where the stellar potential is a known constant of the form \eqnref{discrete
-potential}, e.g., $\kappa_n = \kappa_{\mathrm{dm},n} + \kappa_{s,n}$ for a two-component model.
-
-Unfortunately, the lens equation and the arrival times alone are not enough to form a
-closed volume in the solution space. We have not imposed any strong constraints
-on the density even so much as to ensure that it is non-negative everywhere. We
-must therefore provide additional linear constraints so that we only sample
-physical models. The explicit implementation for these priors has been
-explained in \cite{2008ApJ...679...17C}, but can be summarized as
+potential}, e.g., $\kappa_n = \kappa_{\mathrm{dm},n} + \kappa_{s,n}$ for a
+two-component model.
+
+Unfortunately, the lens equation and the arrival times alone are not enough to
+form a closed volume in the solution space. We have not imposed any strong
+constraints on the density even so much as to ensure that it is non-negative
+everywhere. We must therefore provide additional linear constraints so that we
+only sample physical models. The explicit implementation for these priors has
+been explained in \cite{2008ApJ...679...17C}, but can be summarised as
+%
 \begin{enumerate}
@@
 where we sweep through the model ensemble applying the ray tracing algorithm
-described in \ref{Raytracing}. \hilight{JR. Typically, this results in a rejection rate of XXX\% IS this working? Can we run it once and add the number here?}.
+described in \ref{Raytracing}.
 
 \subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
-Similarly to the null-space constraint (\S\ref{sec:glassextraimages}), stellar
+Similarly to the null-space constraint (\secref{sec:glassextraimages}), stellar
 kinematic constraints constitute a non-linear prior on the mass map and must be
 applied in post-processing. We sweep through the model ensemble performing an
-Abel deprojection to determine $M_{\rm 3D}(r)$ from the projected surface density $\Sigma(R)$
-assuming spherical symmetry \citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}:
-
+Abel deprojection to determine $\Mddd(r)$ from the projected surface density
+$\Sigma(R)$ assuming spherical symmetry
+\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}: 
+%
 \begin{eqnarray} 
-M_{\rm 3D}(r) & = & M(r) - 4r^2 \int_0^{\frac{\pi}{2}} \Sigma\left(x\right) \left(\frac{1}{\cth^2} \right. \nonumber \\ 
-& & \left. - \frac{\sth}{\cth^3} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
+    \Mddd(r) & = & M_\mathrm{p}(<r) - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left[\frac{1}{\cth[2]} \right. \nonumber \\ 
+    & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right] \dth
 \end{eqnarray}
-where $M(r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
+%
+where 
+%
+\begin{equation}
+    M_\mathrm{p}(<r) = 2\pi \int_0^r R \Sigma(R) dR
+\end{equation}
+%
+is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.
 
@@
 We generate four two-component mock galaxies, where the dark matter and stellar
-profiles are allowed to be both steep and shallow.  
-%The enclosed mass in all cases
-%is fixed at $M(a_\star)= 1.8\e{10}$\,M$_\odot$ at the scale radius $a_\star=2$\,kpc. 
-The enclosed mass of the stars and dark matter are both fixed to be 
-$M_{*,\mathrm{DM}} = 1.8 \times 10^{10}$\,M$_\odot$ at the stellar scale radius 
-$a_* = 2$\,kpc, such that the stars and dark matter contribute equally to the total
-mass at $a_*$. The dark matter scale length is fixed for all models at $a_\mathrm{DM}
-= 20$\,kpc.
-These
-values were chosen to closely resemble the lensing galaxy B1115 \citep{1980Natur.285..641W}. We place the galaxy at
-a redshift of $z_L = 0.31$ for lensing.  Throughout, we assume a cosmology
-where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The
-critical density is $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
+profiles are allowed to be both steep and shallow.  The enclosed mass of the
+stars and dark matter are both fixed to be $M_{*,\mathrm{DM}} =
+1.8\e{10}$\,M$_\odot$ at the stellar scale radius $a_* = 2$\,kpc, such that the
+stars and dark matter contribute equally to the total mass at $a_*$. The dark
+matter scale length is fixed for all models at $a_\mathrm{DM} = 20$\,kpc.
+These values were chosen to closely resemble the lensing galaxy PG1115+080
+\citep{1980Natur.285..641W}. We place the galaxy at a redshift of $z_L = 0.31$
+for lensing.  Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr,
+$\Omega_M=0.28$, and $\Omega_\Lambda=0.72$. The critical density is
+$\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
 
@@
 the sight line to the bright lensing galaxy; in clusters, however, such images
-have been seen -- e.g. \citealt{2005PASJ...57L...7I}). We assumed for all our tests that the
-lensing mass was radially symmetric (Prior vi). For our mock data, this is
-known to be true; it is most often the case with real galaxies, unless there is
-an obvious observed asymmetry. The central pixel was refined into a further
-$5\times5$ pixels (three extra radial positions) to capture any steep rise in
-the profile.  Two of the four mock galaxies have a steeply rising inner
-profile. \hilight{JR.  CAN WE DO THIS? What happens if we don't assume this symmetry? We ought
-to add an appendix showing this for one example case.}
-
-In all cases, we additionally assume no external shear.
-This amounts to an assumption that any such shear field can be constrained by data (e.g.
-combining weak lensing constraints, or assuming that the shear field correlates with visible galaxies -- e.g.
-\citealt{2009A&A...500..681M,2011ApJ...726...84W}).
+have been seen -- e.g. \citealt{2005PASJ...57L...7I}). We assumed for all our
+tests that the lensing mass was radially symmetric (Prior vi). For our mock
+data, this is known to be true; it is most often the case with real galaxies,
+unless there is an obvious observed asymmetry. (We explore the effect of
+switching off the symmetry prior in \appref{no_symm_prior}. For the
+quads, the difference is small; for the doubles -- as expected -- the results
+are significantly degraded without this prior.) We use, by default, 8 pixels
+from the centre to the edge of the mass map; the central pixel was further
+refined into $5\times5$ pixels to capture any steep rise in the profile (two of
+the four mock galaxies have a steeply rising inner profile). We demonstrate
+that our results are robust to changing the grid resolution in 
+\appref{pix_convergence_test}.
+
+In all cases -- despite applying no external shear to the mock lenses -- we allow a broad range of external shear in our lens model reconstructions.
+\Glass\ correctly returns a small or zero shear in all cases.
+It is possible that more complex shear fields present in real lensing galaxies could introduce further degeneracies beyond those discussed here.
+However, any such shear field can, at least in principle, be constrained by data (e.g.
+combining
+weak lensing constraints, or assuming that the shear field correlates with
+visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).
 
@@
 %
-where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor
-%
-\begin{equation} 
-    I_{ij} = (-1)^{1-\delta_{ij}}\sum_\theta M(\vec\theta) \theta_i\theta_j 
+where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor:
+%
+\begin{equation}
+\left(
+\begin{matrix}
+   \sum_{\vec\theta} M(\vec\theta) \theta^2_y 
+    & - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \\
+    - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y
+    & \sum_{\vec\theta} M(\vec\theta) \theta^2_x
+\end{matrix}
+\right)
     \label{eqn:inertia}
@@
 %
-where $\delta_{ij}$ is the Kronecker delta.
-We always take $\lambda_1$ to be the largest value.
-As with $f_R$ and $f_\theta$, we only consider mass up to one radial position passed the outermost image and compute the fractional error as:
+We always take $\lambda_1$ to be the largest value. As with $f_R$ and
+$f_\theta$, we only consider mass up to one radial position passed the
+outermost image and compute the fractional error as:
 %
@@
 
-We have introduced a new gravitational lens modelling tool -- Glass\ -- and used
-it to test the recovery of the mass profile and shape of mock strong lensing
-galaxies. Our key findings are as follows:
+We have introduced a new gravitational lens modelling tool -- Glass\ -- and
+used it to test the recovery of the mass profile and shape of mock strong
+lensing galaxies. Our key findings are as follows:
 
 \begin{enumerate}
-\item For pure lens data, multiple sources with wide redshift separation give the strongest
-constraints as this breaks the well-known mass-sheet or steepness degeneracy;
+\item For pure lens data, multiple sources with wide redshift separation give
+    the strongest constraints as this breaks the well-known mass-sheet or
+    steepness degeneracy;
 
@@
 
-\item Stellar masses -- for lenses
-where the stars dominate the central potential -- can also break the steepness
-degeneracy, giving a recovery almost as good as having time delay data or
-multiple source redshifts;
+\item Stellar masses -- for lenses where the stars dominate the central
+    potential -- can also break the steepness degeneracy, giving a recovery for
+    doubles almost as good as having a quad with time delay data, or multiple
+    source redshifts;
 
@@
 The authors would like to thank Sarah Bryan and Walter Dehnen for creating the
-particle distributions for the mock galaxies. JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+particle distributions for the mock galaxies, and the anonymous referee for
+many usual suggestions which has improved the manuscript. JIR would like to
+acknowledge support from SNF grant PP00P2\_128540/1.
+
+\bibliographystyle{mn2e}
+\bibliography{ms}
 
@@
 
-\section{No symmetric prior}
+\section{No radial symmetry prior}\label{no_symm_prior}
+
+In this appendix, we explore the effect of the radial symmetry prior.
+\figref{fig:no_symm_prior} shows results for a single quad (top two rows) and an
+extended double (bottom two rows) without the radial prior; in both cases, we do not use the stellar mass
+constraints.
+The bottom row of each group uses time delay data.
+Without time delay data or the radial symmetry prior, the results for the quad are poor -- particularly the shape recovery.
+Including time delays, the results are similar to the case with the radial prior (\figref{reconstruction} and \figref{2d mass reconstruction}).
+Similarly, for the extended double the results without time delays are poor.
+Even with time delays, the shape is not well recovered without the radial prior, as expected.
+
 \begin{figure*}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-kappa.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-a.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-c.pdf} \\
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-kappa.pdf}
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-a.pdf}
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-c.pdf}
-\caption{No symmetry prior.}
-\label{}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d.pdf}\\
+%
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d-1.pdf}\\
+%
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-c.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-d.pdf}
+%
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-a-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-b-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-c-1.pdf}
+\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-d-1.pdf}
+\caption{Results for a single quad (upper two rows) and an extended double (lower two rows)
+    without the radial symmetry prior; the bottom row of each group uses time delay data. The stellar
+    mass constraint has not been used in any of these examples. Figures and symbols are as in \figref{reconstruction} and
+    \figref{2d mass reconstruction}.}
+\label{fig:no_symm_prior}
 \end{figure*}
 
-\section{Pixel resolution convergence test}
+\section{Pixel resolution convergence test}\label{pix_convergence_test}
+
+In this Appendix, we present a convergence test of our results with the grid
+resolution -- \pixrad. By default, this is set to 8 pixels from the centre of
+the mass map to the edge. As can be seen from
+\figref{fig:pix_convergence_test}, our results are typically well-converged for
+$\pixrad > 5$. The results for $\pixrad = 5$ become systematically biased away
+from the central regions (where we have the higher resolution adaptive mesh),
+because our regularisation prior combined with a low \pixrad{} biases us
+towards shallow models. This effect diminishes with increasing resolution and
+is already negligible by $\pixrad = 7$. Notice that the mass increases in size
+with decreasing resolution. This is because we always demand that there are
+four pixels beyond the outermost image.
+
 \begin{figure*}
@@
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-c.pdf} \\
-\caption{Changing pixrad. top to bottom: pixrad=10,7,6,5. We use 8 normally.}
-\label{}
+\caption{The effect of changing the grid resolution parameter \pixrad. From top
+    to bottom, the panels show results for a single quad with time delays and
+    with stellar mass constraints using $\pixrad = 10,7,6,5$,
+    respectively. We always demand that there are four radial bins outside the
+    outermost image, which causes the total mass to increase with decreasing
+    \pixrad.  In this paper we have used $\pixrad = 8$ in all the
+tests.}
+
+\label{fig:pix_convergence_test}
 \end{figure*}
 
-\section{Pixel resolution convergence test}
-\hilight{JR. Need to add an appendix showing convergence with increasing Pixrad.}
-
-\bibliographystyle{mn2e}
-\bibliography{ms}
-
 \end{document}
-
-\cite{2007ApJ...667..645R} were the first to test the recovery of
-strong lensing surface density profiles using mock data generated from
-N-body models {\bf JR. Is this true?}. They found that when including
-time delays, circularly averaged surface density distributions can
-sufficiently well-recovered to make interesting comparisons with
-theoretical models Cosmological parameters, however, are more
-sensitive. Since then, several groups have used N-body mock data to
-explore the fidelity of strong lensing reconstructions
-\citep{2007MNRAS.380.1729L}. We expand on these earlier works
-by considering not only the recovery of the circularly averaged
-surface density profile of a lens, but also its shape, higher order
-measures of the mass recovery (a pixel-by-pixel comparison), and the
-utility of wrapping in constraints from stellar mass estimates and/or
-stellar kinematics.

### 2014-06-13 limits/ms.tex
Updated figures with 'Z' labels and better shaded errors.

@@
 %\usepackage{ulem} % Only necessary for striking out TODO items see \sout
-\usepackage{color} % Only necessary for hilight
+\usepackage[usenames,dvipsnames]{color} % Only necessary for hilight
 
@@
 %-------------------------------------------------------------------------------
-\newcommand{\hilight}[1]{{\bf \color{red} #1}}
+\newcommand{\hilight}[1]{{\bf \color{OliveGreen} #1}}
 
@@
 generate $|\E| \sim 1000$ models. One can choose to further process these
-models to impose further priors that may be difficult to enforce during the
+models to impose priors that may be difficult to enforce during the
 modeling process. For instance, non-linear constraints, or simply filtering
 of models that do not meet some criteria can be excluded, or weighted against.
-For our current analysis, we do not exclude any models.
+For the current analysis, we do not exclude any models and treat all models
+as equally likely.
 
@@
 completed, the models are sampled very quickly. In fact, there is little
-difference between generating 1,000 or 10,000 models. For our problems, the
-typical ``warm-up'' time was about 4s, and the modelling time was 20s using a
-parallel shared-memory machine with 40 cores.
+difference between generating 1,000 or 10,000 models, although we find little
+statistical difference after 1,000 models. For the mock lenses, the typical
+``warm-up'' time was about 4s, and the modelling time was 20s using a parallel
+shared-memory machine with 40 cores.
 
@@
 galaxy. 
-The configurations for the other galaxies are similar. Within the
-names, the labels Z1, Z2, Z3 refer to the redshift of the sources. We have
-chosen Z1=1.72, Z2=0.72, and Z3=0.51 so that the radial distribution of the
-images is nearly equal. For all mocks, we do not apply any external shear field.
-Only the central image of the Z1 source is used to avoid overconstraining
-the models, otherwise all the central images would fall within the central 
-pixel and no solution exists that satisfies all locations simultaneously for
-one pixel value.
+The configurations for the other galaxies are similar.  The labels Z1, Z2, Z3
+within the names refer to the redshift of the sources. We have chosen Z1=1.72,
+Z2=0.72, and Z3=0.51 so that the radial distribution of the images is roughly
+equally spaced. For all mocks, we do not apply any external shear field.  Only
+the central image of the Z1 source is used to avoid overconstraining the
+models, otherwise all the central images would fall within the central pixel
+and no solution exists that satisfies all locations simultaneously for one
+pixel value.
 
@@
 %
-For both $f_R$ and $f_\theta$, we only consider mass up to one pixel length
-passed the outermost image, since there is no longer any lensing information
-beyond that point. This means we typically use 8 bins, linearly spaced,
-ignoring the outermost 3 bins.  The spacing changes, however, at the border
-between the high resolution region in the middle.
+Since both error measurements consider the mass of each pixel, we are
+implicitly weighting the recovered density by the varying size of the pixels.
+The value $f_R$ emphasizes the error one would see from radial profiles, while
+$f_\theta$ is useful as a measure of how well each individual pixel is recovered.
+For both $f_R$ and $f_\theta$, we only consider mass up to one pixel length passed the
+outermost image, since there is no longer any lensing information beyond that
+point. This means we typically use 8 bins, linearly spaced, ignoring the
+outermost 3 bins.  The spacing changes, however, at the border between the high
+resolution region in the middle.
 

### 2014-07-09 limits/ms-prev.tex
New text and updated figures.

@@
 \newcommand{\pixrad}{\ensuremath{\mathrm{\tt pixrad}}}
-\newcommand{\url}[1]{\tt #1}
 
@@
 \\
-$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$45 avenue des Etats-Unis, 78035, Versailles, France\\
+$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
 $^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
@@
 Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
-date\footnote{See, e.g., {\url{http://masterlens.astro.utah.edu}} for a catalogue.}.
+date\footnote{See e.g. {\tt http://www.masterlens.org} for a catalogue.}.
 However, this number is expected to increase to several thousand over the next
 ten years as new surveys, both
-ground-based\footnote{\url{http://pan-starrs.ifa.hawaii.edu}}$^{\rm,}$\footnote{\url{http://www.darkenergysurvey.org}}
-and space-based\footnote{\url{http://www.euclid-ec.org}} -- together with a community
+ground-based\footnote{http://pan-starrs.ifa.hawaii.edu}$^{\rm,}$\footnote{http://www.darkenergysurvey.org}
+and space-based\footnote{http://www.euclid-ec.org} -- together with a community
 of citizen-science volunteers examining the image data for
-candidates\footnote{\url{http://spacewarps.org}} -- come online.
+candidates\footnote{{\tt http://spacewarps.org}} -- come online.
 
@@
 &= {\textstyle\frac12} |\vec\theta - \vec\beta|^2
-   \cdot \frac{D_{S}}{D_{LS}} \\
+   \times \frac{D_{S}}{D_{LS}} \\
 &- \frac{4GD_L}{c^2}
@@
 \tau(\vec\theta) = {\textstyle\frac12} |\vec\theta - \vec\beta|^2
-                   \cdot \frac{D_{S}}{D_{LS}}
+                   \times \frac{D_{S}}{D_{LS}}
                  - \frac1\pi \int \kappa (\vec\theta')
@@
 implies that $t(\vec\theta_1)-t(\vec\theta_2)$ is known.  Interestingly, both
-these types of observations give constraints that are linear in $\kappa$ and
+these types of observations give contraints that are linear in $\kappa$ and
 $\vec\beta$.
@@
 For many galaxy lenses, the gravitational potential in the inner region is
-dominated by the stellar mass.  Stellar mass can be estimated by combining
+dominated by the stellar mass.  Steller mass can be estimated by combining
 photometry and colours with models of the stellar populations.  Such estimates
@@
 %
-\footnote{\url{http://www.jpcoles.com}}
+\footnote{http://www.jpcoles.com}
 
@@
 profiles are allowed to be both steep and shallow.  The enclosed mass of the
-stars and dark matter are both fixed to be $M_{*,\mathrm{DM}} =
-1.8\e{10}$\,M$_\odot$ at the stellar scale radius $a_* = 2$\,kpc, such that the
+stars and dark matter are both fixed to be $M_{*,\mathrm{DM}} = 1.8 \times
+10^{10}$\,M$_\odot$ at the stellar scale radius $a_* = 2$\,kpc, such that the
 stars and dark matter contribute equally to the total mass at $a_*$. The dark
@@
     stellar mass. For the reconstruction, no time delays were assumed.  The
-    third row uses again the \mockBC{} mock galaxy, but with time delays
+    third row uses again the the \mockBC{} mock galaxy, but with time delays
     for a single quad and no stellar mass. With the added information from the
@@
 The authors would like to thank Sarah Bryan and Walter Dehnen for creating the
-particle distributions for the mock galaxies, and the anonymous referee for
-many usual suggestions which has improved the manuscript. JIR would like to
-acknowledge support from SNF grant PP00P2\_128540/1.
-
-\bibliographystyle{mn2e}
-\bibliography{ms}
+particle distributions for the mock galaxies. JIR would like to acknowledge
+support from SNF grant PP00P2\_128540/1.
 
@@
 
+\bibliographystyle{mn2e}
+\bibliography{ms}
+
 \end{document}

### 2014-07-20 shapes/paper.tex
Converted eps into pdf and changed tex-file accordingly
Added skeleton of fresh, new draft

--- 2013-07-06 shapes/paper.tex
@@
 \begin{abstract}
-Understanding the structure and properties of galaxies today is essential to understand how galaxies formed.
-This poses a larger problem to us than one might imagine.
-Especially constraining the dark matter distribution in galaxy halos is not trivial.
-There are only a few methods to directly estimate this distribution.
-One of them is strong gravitational lensing, an effect caused by all of mass.
-This phenomenon allows constraining the gravitational potential of lens galaxies and thus the mass distribution.
-With knowledge of the light distribution it is possible to disentangle the dark matter and baryonic mass components and study their properties.
-We use the newly-developped nonparametric framework \textit{GLASS} to model the mass distribution of a total of 15 strong gravitational lensing galaxies, most of which are early-type galaxies, for which we have information on the baryonic mass distribution.
-We are thus able to separate the mass components.
-By using a simple shape measure, namely the inverse of the moment of inertia tensor, we can analyze the shapes of the distributions.
-Analyzing the alignments between the semi-major axes of the distributions, we find that there can be significant misalignments and also cases of alignment between the semi-minor and semi-major axes.
-Mass thus need not follow light.
-Furthermore, the ellipticities of the dark matter distributions are always smaller than the baryonic mass distributions.
-Dark matter halos tend to be more spherical than the light distribution of the galaxy.
-We also consider the environment of the lenses.
-We find that lenses in denser environments tend to be more misaligned with either the semi-major or semi-minor axis.
-Additionally, the semi-major axis of lenses lying in groups or clusters of the dark matter halo might be oriented in direction of the centroid.
 \end{abstract}
@@
 \begin{keywords}
-asdf....
+Gravitational lensing: strong --- galaxies: structure
 \end{keywords}
@@
 \section{Introduction}\label{sec:introduction}
-
-\textbf{Context/Background/Motivation}
+\textbf{Content:}
 \begin{itemize}
-\item Why interesting (lensing can constrain mass distribution (enclosed mass constraint independent from model with only few percent uncertainty e.g.
-Kochanek 1991?, Wambsganss \& Paczyński 1994?), insights into structure formation)
-\item What is to be expected from theory (dm, alternative gravity)
+\item Understand galaxy structure
+\item Relevant to e.g. weak lensing (Intrinsic alignments) and alternative gravity theories
+\item Strong lensing reacts purely due to total mass distribution $\rightarrow$ Can disentangle light and mass
+\item Free-form modelling technique, less model bias
 \end{itemize}
 
-\textbf{Anything done before?}
+\section{Data}\label{sec:data}
+\textbf{Content:}
 \begin{itemize}
-\item Surely cite: \cite{1997ApJ...482..604K,1998ApJ...509..561K,2006ApJ...649..599K,2009ApJ...690..670T,2012ApJ...761..170G}
-\end{itemize}
-
-\textbf{New here}
-\begin{itemize}
-\item Statistics
-\item Free-form modelling
-\item group versus stellar misalignment with dm halo
-\end{itemize}
-
-Gravitational lensing is one of the few phenomena that allow probing the matter distribution directly.
-It makes no distinction between baryonic and dark matter, both components act on light rays in the same way.
-Gravitational lensing is therefore somewhat special as it allows to \textit{see} dark matter, if we are able to separate the two components.
-Therefore studying these effects allows us to probe dark matter and its properties.
-We are typically interested in measuring its distribution, how it clusters, its connection to structure formation, and of course its nature.
-With strong gravitational lensing galaxies we are effectively probing the matter distribution on relatively small scales.
-Thus, much insight could be gained in how galaxies form and how they are structured.
-
-The main challenges are however first, estimating the baryonic mass distribution such that the two components can be disentangled (see e.g.
-\cite{leier11phd}), and second, modelling the lens, i.e.
-the mass distribution.
-This work focuses purely on the second aspect.
-There are in general two classes of methods to reconstruct gravitational lenses, parametric and nonparametric methods.
-A comparison of these two classes of methods can be found in \cite{2008ApJ...681..814C}.
-Parametric methods assume a distribution, which depends only on few parameters, such that the problem is well constrained and a best-fitting model can be found.
-They are computationally cheap, but on the other hand the assumption of a distribution might bias the result (CITATION NEEDED!).
-Nonparamatric (or free-form) methods assume a set of basis functions and find valid solutions in terms of linear superpositions of these functions.
-The problem is largely underconstrained.
-Due to the fact that there is no a priori reason to prefer specific mass models, given that they all satisfy certain prior conditions and reproduce the same gravitational lensing effects, over others, the best-fitting model is of little interest.
-Much more important is to explore many models and look at the properties of all the models in the ensemble.
-Typically high-dimensional parameter spaces, which describe all allowed models, need to be sampled in a uniform and uncorrelated way to generate a representative ensemble of solutions.
-The computational cost of these methods is usually much higher \citep{2008ApJ...679...17C,2012MNRAS.425.3077L}.
-
-With these tools, we can start answering the long-standing question whether mass follows light.
-It is a well-known fact that for observations to match for example rotation curves of galaxies, the radial density profiles of baryonic mass and dark matter differ.
-The question is however whether baryonic mass and dark matter need to be aligned and the ellipticities need to agree.
-If this is not the case, then this needs to be explained by mechanism and effects that produce and sustain these different properties.
-Especially the environment of lenses might play a significant role (CITATION NEEDED!).
-It is furthermore unclear whether modified gravity theories could explain possible misalignments between mass and light.
-
-There were already attempts to analyze the alignment of light and mass.
-\cite{1997ApJ...482..604K} use Singular Isothermal Spheres (SIS) with an external shear term and Singular Isothermal Ellipsoids (SIE) (e.g.
-\cite{1994A&A...284..285K}) without external shear to model the mass distribution.
-Applying this to a sample of 17 lenses, they find a strong correlation between light and dark matter distributions, if there is no strong external perturbation, with only a small scatter of less than $10^{\circ}$.
-They find however no correlation between the axis ratios of the distributions.
-
-Later on, \cite{2006ApJ...649..599K} and \cite{2012ApJ...761..170G} analyzing lens samples of similar sizes and \cite{2009ApJ...690..670T} analyzing a lens sample containing even 70 galaxies also looked for misalignments.
-They all use SIEs to model the mass distributions.
-Only \cite{2012ApJ...761..170G} however include an external shear contribution in case more information is available.
-They neglect the external shear although \cite{1998ApJ...509..561K} find that SIEs with an independent external shear term fit the data better.
-They find reasonable alignments, the scatter is however larger than the one found in \cite{1997ApJ...482..604K}.
-\cite{2012ApJ...761..170G} find a rms scatter of $25^{\circ}$ for the whole sample.
-Even after dropping the almost spherical lenses, the rms scatter is still $18^{\circ}$.
-They attribute this to a significant external shear contribution.
-\cite{2009ApJ...690..670T} even find a significant correlation between the misalignment and the local and global environment.
-In general, lenses in overdense environments seem to be more likely to be misaligned.
-\cite{2009ApJ...690..670T} and \cite{2012ApJ...761..170G} also find a correlation with a large scatter between the ellipticities of the light and dark matter distributions.
-
-Contrary to earlier approaches, we choose to use a non-parametric modelling technique.
-We use a pixel-based (see e.g.
-\cite{1997MNRAS.292..148S}) lens reconstruction framework called \textit{GLASS} \citep{2012MNRAS.425.3077L}.
-We apply this successfully on a sample of 15 strong gravitational lensing galaxies using stellar mass data of \cite{leier11phd}.
-Thus, we can disentangle dark and luminous matter and look at the shapes and alignments of these distributions.
-We can also look at the ellipticities of the reconstructed lenses and compare them to the ones of the stellar distribution.
-Furthermore, we discuss the environments of these lenses, as they might affect some properties of gravitational lenses in a significant way \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
-We think that we have enough statistics to make claims about misalignments between the dark matter halo and the stellar mass distribution, and how the halo is oriented compared to the environment.
-
-In Section \ref{sec:data} we present the lens sample and important properties of each lens.
-In Section \ref{sec:method} we present the reconstruction method we use and our shape measure.
-Section \ref{sec:results} consists of the results of this analysis.
-We show the relations we find between misalignment, ellipticities, and the environment.
-
-\section{Data}\label{sec:data}
-\begin{itemize}
-\item SPS (Ignacio Ferreras, Dominik, etc. \citep{2011ApJ...740...97L})
-\item Write why specifically these lenses were chosen, where they're from
+\item Describe data set (why this data set, special features of galaxies (environment: y/n/unknonwn, elliptical/disk))
 \end{itemize}
@@
   \begin{center}
-  \begin{tabular}{l c c l || l c c l}
-   Lens & $z_{L}$ & $z_{S}$ & Type & Lens & $z_{L}$ & $z_{S}$ & Type\\ \hline \hline
-   Q0047 & 0.48 & 3.60 & Quad & HE1104 & 0.73 & 2.32 & Double\\
-   Q0142 & 0.49 & 2.72 & Double & PG1115 & 0.31 & 1.72 & Quad\\
-   MG0414 & 0.96 & 2.64 & Quad & B1152 & 0.44 & 1.02 & Double\\
-   B0712 & 0.41 & 1.34 & Quad & B1422 & 0.34 & 3.62 & Quad\\
-   RXJ0911 & 0.77 & 2.80 & Quad & MG2016 & 1.01 & 3.27 & Quad$^{1}$\\
-   BRI0952 & 0.63 & 4.50 & Double & B2045 & 0.87 & 1.28 & Quad\\
-   Q0957 & 0.36 & 1.41 & Double & HE2149 & 0.60 & 2.03 & Double\\
-   LBQS1009 & 0.87 & 2.74 & Double & Q2237 & 0.04 & 1.69 & Quad\\
-   B1030 & 0.60 & 1.54 & Double & & & & \\
-%   SBS1520 & 0.72 & 1.86 & Double
-%	B1600 & 0.41 & 1.59 & Double\\
+    \begin{tabular}
+      ...
     \end{tabular}
-  \caption{List of all the lenses in the sample and their properties.
-Data is taken from \textit{CASTLES} and \cite{leier11phd}.
-The angles are measured north-through-east.
-\newline $^{1}$ Two images merge, thus only three images can be resolved.}
-  \label{tab:overview}
+    \caption[width=\linewidth]{Table with lens properties}
+    \label{tab:lensproperties}
   \end{center}
@@
   \begin{center}
-  \begin{tabular}{l c c c c c c c}
-   \multirow{2}{*}{Lens} & \multirow{2}{*}{Environment$^{a}$} & \multicolumn{2}{c}{Group/Cluster centroid$^{b}$} & & \multicolumn{2}{c}{Other galaxy} & \multirow{2}{*}{References$^{c}$}\\ \cline{3-4} \cline{6-7}
-    & & $\Delta\alpha$ [''] & $\Delta\delta$ [''] & & $\Delta\alpha$ [''] & $\Delta\delta$ ['']\\ \hline \hline
-   Q0047 & G(9) & $3.6\pm15.6$ & $43.2\pm28.8$ &   & ... & ... & 1\\
-   MG0414 & 2 & ... & ... &   & $-0.4$ & $1.5$ & 2\\
-   B0712 & 2 & ... & ... &   & $47$ & $-91$ & 3\\
-   RXJ0911 & C & $-12.0$ & $-39.8$ &    & ... & ... & 4\\
-   Q0957 & C & ... & ... &   & ... & ... & 5\\
-   B1030 & 2 & ... & ... &   & $-9.8$ & $8.5$ & 6\\
-   PG1115 & G(13) & $-10.8\pm21.0$ & $-3.6\pm15.6$ &   & ... & ... & 1\\
-   B1422 & G(17) & $61.2\pm25.2$ & $-10.8\pm23.4$ &   & ... & ... & 1\\
-%   SBS1520 & G(5) & ... & ... &   & ... & ... & 7\\
-%   B1600 & G(17) & $-8.4^{d}$ & $-1.5^{d}$ &   & ... & ... & 8\\
-   B1608 & G(8) & $-0.7$ & $8.0$ &   & ... & ... & 9\\
-   MG2016 & C(69) & ... & ... &   & ... & ... & 10\\
-   HE2149 & G & $-36.6$ & $14.2$ &   & ... & ... & 11\\
+    \begin{tabular}
+      ...
     \end{tabular}
-  %$^{d}$ Only number-weighted estimates are available. \newline 
-  \caption{List of lenses lying in a group or cluster environment, or that have a companion.
-\newline $^{a}$ G stands for group, C for cluster, and 2 means that the lens has a companion galaxy.
-If known, the number of member galaxies including the lens is given.
-\newline $^{b}$ If not stated differently, the centroid positions are luminosity-weighted estimates.
-\newline $^{c}$ References for the centroid estimates we used.
-\newline 1: \cite{2011ApJ...726...84W}; 2: \cite{1993AJ....105....1S}; 3: \cite{2002AJ....123..627F}; 4: \cite{2001ApJ...555....1M}; 5: \cite{1998ApJ...504..661C}; 6: \cite{2000ApJ...536..584L}; 7: \cite{2008ApJ...673..778A}; 8: \cite{2007AJ....134..668A}; 9: \cite{2003MNRAS.344..337T}; 10: \cite{2006ApJ...646...85W}; 11: \cite{2006ApJ...646...85W}}
-  \label{tab:environment}
+    \caption[width=\linewidth]{Table with lens properties relevant for modelling (point masses, positions, time delays)}
+    \label{tab:lensmodelling}
   \end{center}
@@
 
-\begin{table*}
- \begin{center}
-  \begin{tabular}{l c c c c}
-   Lens & \multicolumn{3}{c}{Time delays [d]} & References\\ \hline \hline
-   RXJ0911 & $\Delta t_{BA}=146\pm4$ & ... & ... & 1\\
-   Q0957 & $\Delta t_{BA}=416.5\pm1.0^{a}$ & $\Delta t_{BA}=420.6\pm1.9^{b}$ & ... & 2\\
-   HE1104 & $\Delta t_{BA}=162.2^{+6.3}_{-5.9}$ & ...  & ...  & 3\\
-   PG1115 & $\Delta t_{BA}=12.0^{+2.4}_{-2.0}$ & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & ... & 4\\
-%   SBS1520 & $\Delta t_{BA}=125.8\pm2.1$ & ... & ... & 5\\
-%   B1600 & $\Delta t_{BA}=51\pm2$ & ... & ... & 6\\
-   B1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & $\Delta t_{CA}=36.0\pm1.5$ & $\Delta t_{DA}=77.0^{+2}_{-1}$ & 7\\
-   HE2149 & $\Delta t_{BA}=103\pm12$ & ... & ... & 8\\
-  \end{tabular}
-  \caption{Lenses with measured time delays.
-$\Delta t_{BA}$ corresponds to the time delay between the images A and B with A leading.
-\newline $^{a}$ measured in the g-band \newline $^{b}$ measured in the r-band \newline 1: \cite{2002ApJ...572L..11H}; 2: \cite{2012A&A...540A.132S}; 3: \cite{2008ApJ...676...80M}; 4: \cite{2010MNRAS.406.2764T}; 5: \cite{2011A&A...536A..44E}; 6: \cite{2000ApJ...544..117B}; 7: \cite{2002ApJ...581..823F}; 8: \cite{2002A&A...383...71B}}
-  \label{tab:timedelays}
- \end{center}
-\end{table*}
-
-The pixelated stellar mass maps we use, were reconstructed by \cite{leier11phd}.
-For each pixel the surface brightness was compared with stellar mass-to-light ratios, which were determined by stellar population synthesis models.
-This technique allows estimating the stellar mass in these pixels.
-Further details on this method can be found in \cite{leier11phd}, \cite{2005ApJ...623L...5F}, \cite{2008MNRAS.383..857F}.
-
-Our sample originally consisted of 21 galaxies, identical to the one in \cite{leier11phd} and \cite{2011ApJ...740...97L}.
-As the lenses \textit{HS0818+1227}, \textit{SBS1520+530}, \textit{B1600+434}, \textit{B1608+656} proved too difficult to reconstruct, we dropped them from this analysis.
-The final sample consists thus of 17 galaxies.
-Most of these lenses are early-type galaxies except \textit{B1030+074}, \textit{B1152+200}, and \textit{Q2237+030}.
-All lenses can also be found in the gravitational lens database \textit{CASTLES}.
-Characteristics and references of each lens in the sample are listed below.
-Table \ref{tab:overview} contains all the redshifts and the type of the lenses, Table \ref{tab:environment} lenses with environment information, and Table \ref{tab:timedelays} lenses with measured time delays.
-
-\textit{Q0047-2808} (hereafter \textit{Q0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
-\cite{2011ApJ...726...84W} find a group of 9 members all of which they spectroscopically confirm.
-
-\textit{Q0142-100} (hereafter \textit{Q0142}) is a passively evolving early-type galaxy according to \citep{2000ApJ...536..584L,2007A&A...465...51E}.
-
-\textit{MG0414+0534} (hereafter \textit{MG0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
-\cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens.
-Due to the proximity of this satellite, we include it as a point mass in our analysis.
-
-\textit{B0712+472} (hereafter \textit{B0712}) is an early-type galaxy \citep{1998AJ....115..377F}.
-Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}.
-There is also a group of 10 galaxies at a lower redshift.
-
-\textit{RXJ0911+0551} (hereafter \textit{RXJ0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}.
-It has measured time delays \citep{2002ApJ...572L..11H} and lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
-This cluster seems to be rather complex.
-Possibly it is not dynamically relaxed, although X-ray emission can be detected.
-Analysis of this emission yields a temperature of 2.3 keV.
-There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
-
-\textit{BRI0952-0115} (hereafter \textit{BRI0952}) is an early-type galaxy \citep{2000ApJ...536..584L,2007A&A...465...51E}.
-\cite{2006ApJ...641..169M} find that the lens lies in a poor group of 5 members.
-However, a redshift of $z=0.41$ was used.
-According to \cite{2007A&A...465...51E}, the redshift is more likely to be $z=0.632$.
-They also find a system of 2 or 3 other galaxies at a slightly higher redshift of which the lens could be part of.
-The required external shear could be explained easily by a cosmic contribution \citep{2000ApJ...536..584L}.
-Therefore, we treat this lens as an isolated object.
-
-\textit{Q0957+561} (hereafter \textit{Q0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g.
-\cite{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}).
-Due to the large image separation, large physical scales are probed.
-As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
-These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
-The lens has a measured time delay (e.g.
-\cite{2012A&A...540A.132S}).
-They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level.
-They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
-We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
-
-\textit{LBQS1009-0252} (hereafter \textit{LBQS1009}) is probably an early-type galaxy \citep{2000ApJ...536..584L}. \cite{2004A&A...428..741F} find no significant galaxy overdensity near the lens.
-
-\textit{B1030+074} (hereafter \textit{B1030}) appears to have some substructure \citep{1998MNRAS.300..649X}.
-\cite{2000ApJ...536..584L} conclude that there are two distinct galaxies.
-The main one is a red, early-type galaxy.
-The other component seems to be fitted well by an exponential disk galaxy.
-They also conclude that no firm statements about the environment can be made.
-Although there is another galaxy nearby, it is too blue to be an early-type galaxy and thus they cannot estimate its shear contribution.
-
-\textit{HE1104-1805} (hereafter \textit{HE1104}) is probably an early-type galaxy \citep{2000ApJ...536..584L,2000A&A...360..853C} and has measured time delays \citep{2008ApJ...676...80M}.
-\cite{2000ApJ...536..584L} also seem to find a group environment.
-\cite{2004A&A...428..741F} however conclude that the photometric redshift measurements of these galaxies indicate that they are at a higher redshift and rather associated with the source.
-Nonetheless, their lens models, parametric and free-form, all require strong external shear.
-
-\textit{PG1115+080} (hereafter \textit{PG1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}.
-It has measured time delays.
-We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ significantly from traditional values by e.g.
-\cite{1997ApJ...489...21B}.
-\cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W} analyzed the environment of the lens thouroughly.
-It is part of a small group of 13 members.
-\cite{2004ApJ...610..686G} detect also X-ray emission from the corresponding group, which yields a temperature of 0.8 keV.
-
-\textit{B1152+200} (hereafter \textit{B1152}) seems to have a color consistent with a late-type or an irregular galaxy \citep{2000A&A...357..115T}.
-Not much seems to be known about the environment of the lens.
-
-\textit{B1422+231} (hereafter \textit{B1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}.
-Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to be trusted too much as they deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}.
-An accurate measurement of the time delays would require time delay measurements on the scale of hours.
-\cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies.
-Using newer data \cite{2011ApJ...726...84W} find an additional member.
-\cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
-
-%\textit{SBS1520+530} (hereafter \textit{SBS1520}) is an early-type galaxy, possibly with a disc \citep{2008ApJ...673..778A}.
-It has measured time delays \citep{2011A&A...536A..44E}.
-There is some uncertainty about the redshift of the galaxy.
-\cite{2002A&A...391..481B} find that their spectroscopic redshift estimate is consistent with $z=0.71$, which was measured first by \cite{1997A&A...318L..67C}.
-Both however also find a system at $z=0.82$, which could be the main lens.
-\cite{2002A&A...391..481B} however conclude that it is not associated with the lens.
-\cite{2008ApJ...673..778A} argue that a system they find at $z=0.76$ is more likely to be the lens, and the foreground system at $z=0.71$ is just a local perturber.
-Data seems however not conclusive.
-\cite{2008ApJ...673..778A} find and spectroscopically confirm a total of 3 groups along the line of sight.
-A poor group of 5 members is at $z=0.716$, another one with 13 members is at $z=0.758$, and a third group with 10 members is at a higher redshift $z=0.818$.
-
-%\textit{B1600+434} (hereafter \textit{B1600}) is a nearly edge-on viewed late-type galaxy \citep{1997A&A...317L..39J}.
-The lens lies in a group with at least seven members, which all seem to be late-type galaxies \citep{2007AJ....134..668A}.
-
-%\textit{B1608+656} (hereafter \textit{B1608}) consists of two merging galaxies.
-The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
-The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}.
-They find a group with 8 resp.
-9 members if the merging galaxies are counted as 2.
-No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
-Along the line of sight seem to be four other groups.
-
-\textit{MG2016+112} (hereafter \textit{MG2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
-It is the farthest lens we consider in this sample.
-It lies in a cluster which consists of 69 probable member galaxies \citep{2003MNRAS.344..337T}.
-The clusters shows a high density of galaxies close to the lens in a south-east direction.
-
-\textit{B2045+265} (hereafter \textit{B2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
-\cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high.
-As the source redshift is rather low, a large lens mass is needed.
-\cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-To the west of the lens, \cite{1999AJ....117..658F} find that a group at a similar redshift as the lens.
-\cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy.
-
-\textit{HE2149-2745} (hereafter \textit{HE2149}) is an early-type galaxy \citep{2007A&A...465...51E} and has a measured time delay \citep{2002A&A...383...71B}.
-There is some uncertainty in estimating the lens' redshift.
-Initial estimates by \cite{1996A&A...315L.405W} and \cite{2000ApJ...543..131K} found a probable redshift range of $\sim0.2-0.5$.
-By cross-correlating the lens spectrum with a template spectrum of an elliptical galaxy, \cite{2002A&A...383...71B} find that the redshift probably lies in the range $0.49\leq z \leq 0.60$, with the most likely redshift $z=0.495\pm0.01$.
-\cite{2007A&A...465...51E} however find that the redshift is more likely to be $z=0.603\pm0.001$.
-This would probably make the lens part of a poor group found by \cite{2006ApJ...641..169M} and \cite{2006ApJ...646...85W}.
-They also find two other groups at lower redshifts.
-
-\textit{Q2237+030} (hereafter \textit{Q2237} or \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
-With only a redshift of $z=0.04$ it is the closest lens of the sample.
-Due to the low redshift, the probed physical scales are quite small.
-No further inquiries into the environment were made.
-
-Further information about the sample can be found in \cite{leier11phd}, \cite{2011ApJ...740...97L}, and \cite{2012A&A...538A..99S}.
-
 \section{Method}\label{sec:method}
-\textbf{GLASS}
+\textbf{Content:}
 \begin{itemize}
-\item Explain GLASS briefly and link to fake data tests
+\item Describe GLASS
+\item Describe shape measure and link it with Coles, Read and Saha 2014
 \end{itemize}
 
-\subsection{Priors and assumptions}
+\section{Results}\label{sec:results}
+\textbf{Content:}
 \begin{itemize}
-\item Explain what priors were chosen to model the lenses (Basically always pixrad 12, shear left free for quads, shear limited for doubles to 0.01, local gradient 50 degrees, smoothening prior 2, time delays if known.
-Exceptions are few.
-For some quads symmetry prior, for one double 0.01 was not possible therefore chose 0.1.)
-\end{itemize}
-
-\textbf{Shape measure}
-\begin{itemize}
-\item Explain shape measure
-\item Link to tests on fake data
-\item Include one plot of fake data test -> Jonathan
-\item Illustrate everything with example lens PG1115.
-\end{itemize}
-
-In this work we use the new free-form lens modelling framework \textit{GLASS} \citep{2012MNRAS.425.3077L}.
-As its predecessor \textit{PixeLens} \citep{2004AJ....127.2604S}, it generates a pixelated mass map of a lens reproducing the image positions perfectly.
-Using pixels the arrival time surface for a source at position $\boldsymbol\theta_{S}$, taking the geometric and Shapiro contributions to the time delay into account, can be expressed in terms of the surface mass density rescaled by the critical density $\Sigma_{crit}$ of the n-th pixel $\kappa_{n}$ and the contribution to the gravitational potential of this pixel $\psi_{n}$ \citep{1997MNRAS.292..148S}
-\begin{equation}\label{eq:arrival}
-\tau(\boldsymbol\theta)=\frac{1}{2}|\boldsymbol\theta |^{2}-\boldsymbol\theta\cdot\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\psi_{n}(\boldsymbol\theta).
-\end{equation}
-
-According to Fermat's principle, lensed images appear where the arrival time surface takes on extremal values $\nabla\tau(\boldsymbol\theta)=0$. Thus, the image positions fulfil
-\begin{equation}
-\boldsymbol\theta-\boldsymbol\theta_{S}-\displaystyle\sum\limits_{n} \kappa_{n}\alpha_{n}=0,
-\end{equation}
-where $\alpha_{n}$ is the contribution to the bending angle of the n-th pixel.
-For pixels, $\alpha_{n}$ and $\psi_{n}$ can be described by analytic formulae \citep{1997MNRAS.292..148S}.
-Reconstructing the lens, i.e.
-describing the surface mass density in every pixel, reduces thus to finding sets of coefficients $\left\{\kappa_{n}\right\}$ of these functions.
-As the number of pixels, which sets the resolution, is by far larger than the number of constraint equations in free-form modelling, this problem is highly underconstrained.
-The number of pixels is typically $\gtrsim 100$.
-We note that the equation is linear in $\kappa_{n}$.
-Also additional constraints on the lens such as individual time delays between images and their order and other priors we impose are linear.
-The volume of allowed solution is thus a high-dimensional polytope.
-
-A fundamental difficulty in mass modelling is the non-uniqueness of solutions.
-They are not only not unique, every configuration which fulfils the equation is also equally probable.
-Therefore, this polytope needs to be sampled in a uniform way to analyze the full range of solutions.
-Due to the high dimensionality, sophisticated sampling methods of such volumes are required.
-\textit{GLASS} and \textit{PixeLens} differ in the method they use to sample such spaces.
-\cite{2008ApJ...679...17C} and \cite{2012MNRAS.425.3077L} show that \textit{PixeLens} does not produce uncorrelated random samples.
-They propose therefore a new sampling algorithm.
-They prove that generic high-dimensional polytopes indeed are sampled in a much more uniform way.
-Models in \textit{GLASS} are generated using a MCMC-method with a Metropolis-Hastings algorithm.
-A new step $x_{i+1}$ of the Markov chain is accepted with the probability
-\begin{equation}
- \alpha = \mathrm{min}\left(1,\frac{P(x_{i+1})Q(x_{i},x_{i+1})}{P(x_{i})Q(x_{i+1},x_{i})}\right),
-\end{equation}
-where $P(x)$ is the probability distribution samples are drawn from and $Q(x_{i},x_{i+1})$ is the proposal density.
-As mentioned, all the valid mass configurations have the same probability, thus $P$ is a constant $\equiv1$.
-$Q$ has to be symmetric for Markov chains.
-It is usually taken to be a multivariate Gaussian $\mathcal{N}(x,\hat{\boldsymbol\Sigma})$, where $\hat{\boldsymbol\Sigma}$ is an estimate of the true covariance matrix $\boldsymbol\Sigma$.
-In principle it could be estimated by an adaptive chain during the random walk, but then the chain is no longer Markovian as it loses the reversibility property.
-Therefore, first an initial adaptive burn-in phase is run to get an good estimate $\hat{\boldsymbol\Sigma}$, before the real MCMC random walk.
-In this way, a large ensemble of models can be generated.
-The estimation of the covariance matrix is refined in \textit{GLASS} such that models are much less correlated.
-Further details and tests of the method can be found in \cite{2012MNRAS.425.3077L}.
-
-\textbf{Priors and assumptions}
-We use different priors and assumptions to eliminate unphysical mass reconstructions of the lens.
-First of all, the densities $\kappa_{n}$ need to be positive.
-As mass distributions with positive radial gradients are instable (CITATION NEEDED!), the density must always increase towards the center.
-Therefore, we require the local density gradient in every pixel except the central one to point towards the center within an angle of $50^{\circ}$.
-The radial density profile decreases monotonically, as required.
-
-To avoid large fluctuations in the density, we choose to add a smoothing prior.
-The density in any pixel except the central one is at most twice the average density of its neighboring pixels.
-If there is reason to expect an invariant distribution under a rotation by $180^{\circ}$ (e.g.
-for doubles), we impose such a symmetry prior.
-
-We also choose to include an additional external shear
-\begin{equation}
-  \gamma_{1}\left(\theta_{x}^{2}-\theta_{y}^{2}\right)+2\gamma_{2}\theta_{x}\theta_{y},
-\end{equation}
-which is added to (\ref{eq:arrival}) and the subsequent equations.
-We allow $\gamma_{1}$ and $\gamma_{2}$ to vary while fixing the maximum absolute value of the shear parameters.
-For doubles we fix the absolute value to be at most $10^{-2}$ (resp.
-$10^{-1}$ if no model could be generated for lower values ---> find out which galaxy and write this in more detail).
-
-We further assume that the lens and image positions are perfectly known.
-As the range of possible models is much larger than the errors on these quantities, this assumption is justified \citep{2006ApJ...650L..17S}.
-We also fix a time order of the images.
-Furthermore, we choose a flat concordance cosmology with $\Omega_{m}=0.28$, $\Omega_{\Lambda}=0.72$, and $H_{0}^{-1}=13.7$.
-
-\textbf{Shape measure}
-
-To get a rough estimate of the shape of the surface mass distribution we use the inverse of the moment of inertia tensor of the mass map.
-Its eigenvectors and eigenvalues track the shape of the mass distribution.
-Thus, the shape is defined by two quantities; the ratio of the eigenvalues $\lambda_{1}/\lambda_{2}$, which describes the ellipticity, and the angle of the semi-major axis $\theta$.
-This seemingly crude measure was tested on fake data and found to be working well.
-(INPUT HERE FAKE DATA TEST)
-
-Figure \ref{fig:1115rec} shows example plots of the reconstruction of the lens \textit{PG1115} illustrating this shape measure.
-In this lens system, there is a significant misalignment between the two mass distributions.
-1$\sigma$- and 2$\sigma$-uncertainties on the angle estimates are shown.
-These errors are purely statistical, estimated by the ensemble of models.
-Figure \ref{fig:1115rec} also shows the arrival time surface and total, dark, and baryonic mass distributions.
-
-\section{Results}\label{sec:results}
-\begin{itemize}
-\item Show some examples (stellar and dm contour plots, image of lens, arrival time surface, included mass)
-\item Show money plots
-\item Comment on a few lenses special lenses
-\item Environmental effect?
+\item Describe special features in reconstructed lenses
+\item Show the wedges money plot
+\item Discuss the results, especially:
+\item 1. Dark matter halos seem quite round, stars not necessarily
+\item 2. Dark matter halos are consistently more elliptical than stars
+\item 3. Rather elliptical dark matter halos are more aligned, otherwise not really a clear trend
+\item 4. There does not seem to be a trend of lenses being misaligned because of shear
 \end{itemize}
@@
 \begin{figure*}
- \begin{center}%\hspace{-7mm}\hspace{0.8\textwidth}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_a.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_b.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_c.eps}\\
-  \includegraphics[height=0.32\textwidth]{Figures/1115_d.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_h.eps}\\
-  \caption{Reconstruction of lens \textit{PG1115}.
-The plots show the mean model of the generated ensemble of models.
-The coordinate system is centered on the lens galaxy.
-(a) shows the arrival time surface.
-The green dots are the images, the red curves are isochrones, and the black curve are the lemniscate resp.
-the lima\c{c}on.
-(b) shows the total matter distribution.
-The red circle marks the circle of the outermost image.
-The green resp.
-cyan ellipses mark the shape of the dark matter resp.
-stellar distribution.
-This shape is measured as described in Section 3.3.
-In this case, the shape of the total matter distribution (black) is indistinguishable from the dark matter distribution.
-(c) shows the dark matter distribution.
-The black lines show the median semi-major resp.
-semi-minor axis with 1$\sigma$- and 2$\sigma$- uncertainties.
-The solid pink line points to the group centroid with $1\sigma$-uncertainties (dashed).
-(d) shows the luminous matter distribution.}
-  \label{fig:1115rec}
- \end{center}
+  \centering
+  \includegraphics[width=.65\linewidth]{Figures/AllLenses21.pdf}
+  \caption[width=.65\linewidth]{}
+  \label{fig:lensreconstruction1}
 \end{figure*}
@@
 \begin{figure*}
- \begin{center}%\hspace{-7mm}\hspace{0.8\textwidth}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_a.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_b.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_c.eps}\\
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_d.eps}
-  \includegraphics[height=0.32\textwidth]{Figures/1115_barkana_h.eps}\\
-  \caption{Same as Figure \ref{fig:1115rec} but using time delay estimates from \cite{1997ApJ...489...21B}.}
-  \label{fig:barkana}
- \end{center}
+  \centering
+  \includegraphics[width=.65\linewidth]{Figures/AllLenses22.pdf}
+  \caption[width=.65\linewidth]{}
+  \label{fig:lensreconstruction2}
 \end{figure*}
@@
 \begin{figure*}
- \begin{center}
- \includegraphics[height=0.49\textwidth]{Figures/b.eps}
- \includegraphics[height=0.49\textwidth]{Figures/d.eps}
- \includegraphics[height=0.49\textwidth]{Figures/e.eps}\\
- \caption{Plots of stellar and dark matter misalignments, ellipticities of the baryonic mass and dark matter distribution and a plot showing the ellipticity of the dark matter halo against the misalignment.
-Red symbols mark isolated objects or such without environment information, green symbols mark objects with at least one companion galaxy.
-In the second plot, stars denote the ellipticitie of the baryonic mass distribution, squares the ones of the dark matter halo.}
- \label{fig:moneyplots}
- \end{center}
+  \centering
+  \includegraphics[width=.65\linewidth]{Figures/wedges_shears.pdf}
+  \caption[width=.65\linewidth]{}
+  \label{fig:wedges}
 \end{figure*}
 
-\begin{figure}
- \begin{center}
- \includegraphics[height=\linewidth]{Figures/g.eps}
- \caption{Misalignment of the dark matter halo and the direction of the centroid of the environment.}
- \label{fig:environmentmisalign}
- \end{center}
-\end{figure}
-
-For every lens 10000 models were generated.
-This number allows for reasonable statistics, while not being computationally too expensive.
-In general an external shear of $\left|\gamma_{i}\right| \lesssim 10^{-1}$ is required to model quads.
-\textit{RXJ0911} and \textit{MG2016} however, need a significantly larger external shear of $\left|\gamma_{i}\right|\sim2\cdot10^{-1}$.
-This probably can be attributed to the cluster environments.
-As mentioned, the shear was limited to be $\left|\gamma_{i}\right| < 10^{-1}$ for doubles.
-The masses $M_{dm}$ and $M_{tot}=M_{dm}+M_{stellar}$ are always the masses included up to the radius of the outermost image.
-
-%Our mass modelling shows that \textit{BRI0952} and \textit{Q2237} seem to have a rather large amount of mass in baryonic mass (e.g.
-Figure \ref{fig:moneyplots}).
-Also the two very massive, very dark matter dominated lenses \textit{Q0957} and \textit{MG2016} should be mentioned.
-\textit{Q0957} is a cD-galaxy and \textit{MG2016} a giant elliptical, so this result was to be expected.
-%This can be explained for \textit{Q2237}. In \textit{Q2237} only the inner parts of the lens, where the baryonic mass dominates, are probed.
-
-Surprisingly, the shape measure we define yields are well-constrained results, as can be seen in Figures \ref{fig:1115rec} and \ref{fig:moneyplots}.
-The errors, which are purely statistical, on the ellipticities and the angles of the semi-major axis do not dominate the result.
-Lenses with almost spherical halos, i.e.
-$\lambda_{1}/\lambda_{2}\sim1$, should however be treated with caution.
-
-As mentioned in Section \ref{sec:data}, there are different time delay estimates for \textit{PG1115}.
-We find that the results do not change much when using different estimates.
-As can be seen in Figure \ref{fig:1115rec} resp.
-Figure \ref{fig:barkana}, the dark matter distribution is a bit more spherical with the time delays from \cite{2010MNRAS.406.2764T} and the uncertainty on the angle of the semi-major axis grows.
-The significant misalignment we see is thus not affected by different time delays.
-
-% The dark matter distribution in \textit{SBS1520} shows a very interesting behaviour.
-As can be seen in Figure \ref{fig:1520}, the dark matter seems to follow the baryonic mass distribution.
-Further out however, the dark matter distribution is rotated slightly.
-There is a significant misalignment between the dark matter distribution and the baryonic distribution.
-Without the central part, the misalignment would be even larger.
-This behaviour could be due to the potential disc \cite{2008ApJ...673..778A}, or caused by the many structures on the line of sight.
-
-\textbf{Misalignments between stellar and dark matter distributions}
-Figure \ref{fig:moneyplots} shows the differences between the angles of the stellar and the dark matter semi-major axes versus the ratio of the included dark matter and total mass.
-For lenses with a significant stellar component inside the outermost image radius, the distributions seem to be rather aligned.
-It seems that if the luminous mass is comparable to the dark matter mass, the distributions align.
-For a smaller stellar contribution this is not necessarily the case.
-The scatter increases and there can be significant misalignments, which can be seen especially clearly in the systems \textit{PG1115} (also Figure \ref{fig:1115rec}) and \textit{RXJ0911}.
-While alignments between the distributions are preferred, they do not seem to be the rule.
-
-The environment might also play a role.
-Red are the systems, which are isolated and/or no group resp.
-cluster environment has been found yet, green the ones in such an environment.
-The misaligned systems are mainly the lenses with a known environment.
-Therefore, misalignments could be caused by the external effects.
-
-\textbf{Ellipticities of stellar and dark matter distributions}
-The ellipticities of the distributions versus the mass ratio are shown in Figure \ref{fig:ellipticities}.
-We see that every dark matter halo has a lower ellipticity $\lambda_{1}/\lambda_{2}$ and is thus closer to sphericity than the luminous part of the galaxy.
-The systems \textit{B0712}, \textit{B1152} \textit{HE1104}, and \textit{MG2016} show especially large differences.
-It is not clear what could cause these discrepancies.
-
-Figure \ref{fig:misalignmentellipticities} shows the misalignment versus the ellipticity of the dark matter halo.
-It is possible to roughly subdivide it into five different regions.
-Almost spherical halos with good alignment of the semi-major axes, almost spherical halos with good alignment of semi-major and semi-minor axes (maximum misalignment between the semi-major axes), more elliptical, alligned halos, a seemingly 'forbidden' region for misalignments in between, and the upper right triangle, i.e.
-larger ellipticities and misalignments, which also seems forbidden.
-Understanding Figure \ref{fig:misalignmentellipticities} is certainly not trivial.
-Alignment with the semi-minor axis might be a stable configuration for almost spherical halos, while slightly smaller misalignments are unstable.
-The systems \textit{Q0957}, \textit{PG1115}, \textit{B1422}, \textit{MG2016}, and \textit{HE2149} should be studied more closely as they could hold valuable information to decipher these relations.
-
-\textbf{Misalignments between the dark matter distributions and environment}
-Figure \ref{fig:environment} we look at the alignment of the semi-major axes of the dark matter halos and vectors pointing to the centroid of the group or cluster or a companion galaxy.
-Although the error bars are huge, we see that five of these ten lenses, \textit{Q0047}, \textit{B0712}, \textit{Q0957}, \textit{PG1115}, and \textit{B1422}, are probably aligned or at least consistent with the environment.
-The other half show slight misalignment.
-
-Having a closer look at these lenses shows however that at least two of them might in fact be aligned.
-For \textit{RXJ0911} and \textit{HE2149} there are no errors on the estimates of the centroid.
-Otherwise they would probably agree very well.
-\textit{Q0047} does not seem to be aligned with the direction of the group centroid.
-The halo of \textit{B1030} is almost spherical, so the apparent misalignment could maybe be explained.
-\textit{MG2016} also has a known environment, is however not shown in this Figure as no estimate of the cluster centroid is given.
-There is however a high galaxy density towards the south-east, where also the cluster centroid probably lies.
-The halo seems to be roughly aligned with the cluster centroid.
-%Add figure of this lens
-
-We conclude that lenses in groups or cluster are probably aligned with the centroid, i.e.
-the center of mass, consistent with what one might expect naively.
-The light however needs not be as stated earlier.
-%%%%%%%%%%%%%%%%%%
-
 \section{Conclusion}\label{sec:conclusion}
-\begin{itemize}
-\item Recapitulate what were the main results
-\item Answer whether this method is promising
-\item What is needed to understand such misalignments better (-> Surely need to understand environment effects better, ...)
-\end{itemize}
-
-We used a nonparametric modelling method to reconstruct a total of 15 lenses.
-Using previously measured light maps, then converted to luminous mass maps \cite{leier11phd}, we were able to isolate the dark matter distribution.
-We used the eigenvalues and eigenvectors of the inverse of the moment of inertia tensor to characterize the shape of the light and mass distributions.
-This allowed us to analyze the alignment between these distributions and the relation between the ellipticities.
-Furthermore, we included environment information, which we related the to the misalignment.
-
-Our results can be summarized in the following way.
-If lenses lie in dense environments, mass and light need not be aligned.
-This might also be the case for lenses without known environments.
-We found more scatter than previous analyses by \cite{1997ApJ...482..604K}, \cite{2006ApJ...649..599K}, \cite{2009ApJ...690..670T}, and \cite{2012ApJ...761..170G} which all used SIEs mostly neglecting external shear to model the lenses.
-We also found that the semi-major and semi-minor axes of the distributions can be aligned, if the dark matter halos are close to sphericity.
-Up to our knowledge, this result was not obtained in other analyses.
-
-We found that dark matter halos are rounder than the luminous galaxies, i.e.
-they have a lower eigenvalue ratio $\lambda_{1}/\lambda_{2}$.
-Previous analyses found a correlation between the ellipticities \citep{2009ApJ...690..670T,2012ApJ...761..170G}, which we do not see.
-They also found a couple of cases, where the stellar distribution is more spherical than the dark matter halo.
-We claim that certain combinations of ellipticity of the dark matter halo and misalignment between light and mass seem to be forbidden.
-However, more lens systems are needed to support this claim.
-
-We suspect that the dark matter halo might be aligned with the centroid of the group or cluster it lies in.
-Due to the large uncertainties in the centroid positions however, such alignments might as well be coincidences.
-
-We want to stress again that the systems \textit{SBS1520} and \textit{PG1115}, which both show some misalignment and have time delay measurements, seem interesting enough to investigate further.
-In \textit{SBS1520} we found that the outer parts of the dark matter distribution is rotated respective to the central, which displays an interesting feature possibly due a disc.
-It is on the other hand a very complicated system with a lot of structures along the line of sight.
-\textit{PG1115} is easy to model, but still shows a clear misalignment.
-Thus, it could serve as a test for other methods that try to reproduce these misalignments.
+...
 
 \section{Acknowledgements}\label{sec:acknowledgements}
-Acknowledge Dominik Leier...
+Acknowledge Dominik Leier, ...
 
@@
 %\clearpage
-\appendix
-\section{Reconstructed Lenses}\label{sec:reconstructions}
-
-\begin{table*}
- \begin{center}
-  \begin{tabular}{l c c c c l l}
-   Lens & A & B & C & D & Symmetry & Point Masses\\ \hline \hline
-   Q0047 & 1.083 & 1.083 & 1.083 & 1.083 & Yes & $-\Delta\alpha = 2.301$ , $-\Delta\delta = 2.301$ , Mass range: $10^{7}-10^{9} \mathrm{M_{Sun}}$\\
-   Q0142 & & & & & & \\
-   MG0414 & & & & & & \\
-   B0712 & & & & & & \\
-   RXJ0911 & & & & & & \\
-   BRI0952 & & & & & & \\
-   Q0957 & & & & & & \\
-   LBQS1009 & & & & & & \\
-   B1030 & & & & & & \\
-   HE1104 & & & & & & \\
-   PG1115 & & & & & \\
-   B1152 & & & & & \\
-   B1422 & & & & & \\
-   B1608 & & & & & \\
-   MG2016 & & & & & \\
-   B2045 & & & & & \\
-   HE2149 & & & & & \\
-   Q2237 & & & & & \\
-  \end{tabular}
-  \caption{...}
-  \label{tab:lensparameters}
- \end{center}
-\end{table*}
+% \appendix
+% \section{Reconstructed Lenses}\label{sec:reconstructions}
 

### 2014-07-20 limits/ms.tex

@@
 
-\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
+%\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
+\title[Lens Recovery with \Glass]{Stellar Mass and Stellar Kinematics Can Constrain Gravitational Lens Models}
 \author[J.~P.~Coles~et~al.]{%
@@
 lower bounds on the lensing mass.
-We also introduce a new lens modeling framework  -- \Glass\ (Gravitational
-Lensing AnalysiS Software). The compute-intensive core of \Glass\ is a parallel
+We have also developed a new lens modeling framework  -- \Glass\ (Gravitational
+Lensing AnalysiS Software) which improves upon the earlier techniques. The
+key developments are
+
+\begin{enumerate}
+\item A modular framework that allows new priors to be added and modified easily.
+\item The basis functions approximating a model can be changed.
+\item Non-linear constraints can be imposed in an automated post-processing step.
+\item The central region can have a higher resolution to capture steep models.
+\item Stellar density can be used as an additional constraint.
+\item Point or extended mass objects can be placed in the field.
+\item A new uniform sampling algorithm for high dimensional spaces.
+\end{enumerate}
+
+The compute-intensive core of \Glass\ is a parallel
 implementation of the high-dimensional sampling algorithm from
@@
 
-Unfortunately, the lens equation and the arrival times alone are not enough to
-form a closed volume in the solution space. We have not imposed any strong
-constraints on the density even so much as to ensure that it is non-negative
-everywhere. We must therefore provide additional linear constraints so that we
-only sample physical models. Below we list typical constraints that \Glass\
-provides. The explicit implementation for these priors has
-been explained in \cite{2008ApJ...679...17C}, but can be summarised as
+The lens equation and the arrival times alone are not enough to form a closed
+volume in the solution space. The data alone do not even constraint the density
+to be non-negative everywhere. We therefore provide additional linear
+constraints so that only physical models are sampled. 
+\Glass\ provides a number of typical constraints similar to those discussed in
+\cite{2008ApJ...679...17C}: 
 %
@@
 cluster. Prior (iv) can be relaxed somewhat by increasing the angle. The
-smoothness prior (v) requires pixel values to be less than a constant factor of
-the average neighbor value. This can be relaxed by increasing the constant or
-completely disabled. For this paper, we have chosen \emph{not} to use this
-prior, and therefore allow for the presence of small density substructure.
-Prior (vi) enforces a radial symmetry that requires radially opposed pixels
-(i.e., on opposite sides of the center) to be equal. This prior is particularly
-important for modelling doubles which must be symmetric. If a lens is suspected
-to be symmetric this can also significantly improve the modelling time for
-quads.
+smoothness prior (v) requires pixel values to be less than a constant factor
+(normally 2) of the average neighbor value. This can be relaxed by increasing
+the constant or completely disabled. For this paper, we have chosen \emph{not}
+to use this prior, and therefore allow for the presence of small density
+substructure.  Prior (vi) enforces a radial symmetry that requires radially
+opposed pixels (i.e., on opposite sides of the center) to be equal. This prior
+is particularly important for modelling doubles which must be symmetric. If a
+lens is suspected to be symmetric this can also significantly improve the
+modelling time for quads.
 
@@
 central image only belongs to the Z1 source to avoid overconstraining the
-models. Image colors represent a common source. Grey circles are a visual aid
+models. Images of the same color share a common source. The extended source examples have been
+contructed so that the images will form arclets.
+Grey circles are a visual aid
 to help determine radial separation between images. The axes are in
@@
 \begin{equation} \label{ferror R}
-  f_R = \frac {\sum_i \left|M(i) - \tilde M(i)\right| } {\sum \tilde M(i)}
-\end{equation}
-%
-based on the mass $M(i)$ of each pixel ring $i$ and the mass $\tilde M$ from the mock galaxy. 
+  f_R = \frac {\sum_i \left|M(i) - \widehat M(i)\right| } {\sum \widehat M(i)}
+\end{equation}
+%
+based on the mass $M(i)$ of each pixel ring $i$ and the mass $\widehat M$ from the mock galaxy. 
 In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$:
@@
 \begin{equation} \label{ferror theta}
-f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum_{\vec\theta} \tilde M(\vec\theta)}
+f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \widehat M(\vec\theta)\right| } {\sum_{\vec\theta} \widehat M(\vec\theta)}
 \end{equation}
@@
 \begin{equation} \label{ferror shape}
-  f_\mathrm{shape} = \left|s - \tilde s\right|  / \tilde s
-\end{equation}
-%
-where $\tilde s$ is the shape of the mock galaxy. The distribution of
+  f_\mathrm{shape} = \left|s - \widehat s\right|  / \widehat s
+\end{equation}
+%
+where $\widehat s$ is the shape of the mock galaxy. The distribution of
 $f_\mathrm{shape}$ for each mock galaxy and each test case is shown in

### 2014-07-23 limits/ms.tex
Changes mainly to the refreee reply from Justin; not yet finished.

@@
 
+\keywords{gravitational lensing: strong, methods: numerical, methods: statistical}
+
 \section{Introduction}\label{sec:intro}
@@
 is the gravitational radius. If the source is a quasar or otherwise rapidly
-variable, a time delay $\Delta t$ in the variability will be present where
+variable, a time delay $\Delta t$ in the variability will be present where:
 %

### 2014-07-25 limits/ms.tex
Justin's changes complete. New referee reply file mostly complete. Action items (very minor) that remain marked in ./mnras/rev1-comments_reply.txt with 1120$

@@
 
-%\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
-\title[Lens Recovery with \Glass]{Stellar Mass and Stellar Kinematics Can Constrain Gravitational Lens Models}
+\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
+%\title[Lens Recovery with \Glass]{Stellar Mass and Stellar Kinematics Can Constrain Gravitational Lens Models}
 \author[J.~P.~Coles~et~al.]{%
@@
 
-\keywords{gravitational lensing: strong, methods: numerical, methods: statistical}
+\begin{keywords}
+gravitational lensing: strong, methods: numerical, methods: statistical
+\end{keywords}
 
@@
 %
-For multiple images, the sky-projected density must exceed the critical
-density in some region:
+For multiple images, the sky-projected density must exceed the critical lensing density in some region:
 %
@@
     combating the non-uniqueness of models.  Such ensembles are possible in
-    parametric models \citep{1999AJ....118...14B} but are more common in
+    parametric models \citep[e.g.][]{1999AJ....118...14B,2010Sci...329..924J} but are more common in
     free-form models, where -- since such models are deliberately
@@
 
-In this paper we demonstrate which combination of lensing, stellar mass, and
+In this paper, we introduce a new non-parametric lens modelling framework  -- \Glass\ (Gravitational
+Lensing AnalysiS Software).
+This shares some aspects with an earlier code \PixeLens \citep{Saha2004,2008ApJ...679...17C}.
+However, \Glass\ -- which contains all new code written from the ground up -- significantly improves upon \PixeLens\ in several key ways:
+
+\begin{enumerate}
+\item At the heart of \Glass\ is a new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L}.
+This allows for large ensembles of $>10,000$ models to be efficiently generated.
+\item \Glass\ provides a modular framework that allows new priors to be added and modified easily.
+\item The basis functions approximating a model can be easily changed (in this paper, we assume pixels as in \PixeLens). 
+\item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
+\item The central region of the mass map can have a higher resolution to more efficiently capture steep models.
+\item Stellar density can be used as an additional constraint on the models. 
+\item Point or extended mass objects can be placed in the field.
+\end{enumerate}
+As a first application, we use \Glass\ on mock data to determine which combination of lensing, stellar mass and/or 
 stellar kinematic constraints best constrain the projected mass profile and
-shape of several gravitational lens produced from mock data. In particular,
-we introduce the idea of using estimates of the stellar mas content to place
-lower bounds on the lensing mass.
-We have also developed a new lens modeling framework  -- \Glass\ (Gravitational
-Lensing AnalysiS Software) which improves upon the earlier techniques. The
-key developments are
-
-\begin{enumerate}
-\item A modular framework that allows new priors to be added and modified easily.
-\item The basis functions approximating a model can be changed.
-\item Non-linear constraints can be imposed in an automated post-processing step.
-\item The central region can have a higher resolution to capture steep models.
-\item Stellar density can be used as an additional constraint.
-\item Point or extended mass objects can be placed in the field.
-\item A new uniform sampling algorithm for high dimensional spaces.
-\end{enumerate}
-
-The compute-intensive core of \Glass\ is a parallel
-implementation of the high-dimensional sampling algorithm from
-\cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has extensible code (in
-software terminology, a framework) in Python, encoding the lens equation, a
-basis and priors for the mass distribution, and various post-processing and
-visualisation modules.
-
-\Glass\ is described in \secref{sec:glass}.  In \secref{sec:theory}, we review
+shape of a gravitational lens. We will apply \Glass\ to real lens data in a series of forthcoming papers.
+
+%The compute-intensive core of \Glass\ is a parallel
+%implementation of the high-dimensional sampling algorithm from
+%\cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has extensible code (in
+%software terminology, a framework) in Python, encoding the lens equation, a
+%basis and priors for the mass distribution, and various post-processing and
+%visualisation modules.
+
+This paper is organised as follows. In \secref{sec:glass}, we describe the \Glass\ code. In \secref{sec:theory}, we review
 the key elements of lensing theory, stellar population synthesis, and stellar
@@
 the lensing observables. But degeneracies are still present with multiple
-source redshifts.  \citep{2008MNRAS.386..307L}.
+source redshifts \citep{2008MNRAS.386..307L,2014arXiv1406.6152S}.
 
@@
   \setcounter{enumi}{0}
+  \item A new uniform sampling algorithm for high dimensional spaces.
+\end{enumerate}
+%
+At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
+linear space that represents the modelling solution space. This algorithm was
+described and tested in \cite{2012MNRAS.425.3077L}; it is multi-threaded
+allowing it to run efficiently on many-cored machines.
+%
+\begin{enumerate}
+  \setcounter{enumi}{1}
   \item A modular framework that allows new priors to be added and modified easily.
@@
 either a single lens object or the entire ensemble of objects. \Glass\ comes
-with a number of useful priors, the default ones will be described later, but a
+with a number of useful priors (the default ones will be described in \secref{sec:discrete}), but a
 user can write their own directly in the input file, or by modifying the source
@@
 \begin{enumerate}
-  \setcounter{enumi}{1}
+  \setcounter{enumi}{2}
   \item The basis functions approximating a model can be changed. 
@@
 \begin{enumerate}
-  \setcounter{enumi}{2}
+  \setcounter{enumi}{3}
   \item Non-linear constraints can be imposed in an automated post-processing step. 
@@
 be used as a filter to accept or reject a model based on some non-linear
-constraint. The plotting functions within \Glass\ will correctly display models
+constraint.
+For example, we can reject models that have spurious extra images (\secref{sec:glassextraimages}), or models that do not match stellar kinematic constraints (\secref{sec:glasskinematics}).
+The plotting functions within \Glass\ will correctly display models
 that have been accepted or rejected.
@@
 \begin{enumerate}
-  \setcounter{enumi}{3}
+  \setcounter{enumi}{4}
   \item The central region can have a higher resolution to capture steep models. 
@@
 \begin{enumerate}
-  \setcounter{enumi}{4}
+  \setcounter{enumi}{5}
   \item Stellar density can be used as an additional constraint.  
@@
 \begin{enumerate}
-  \setcounter{enumi}{5}
+  \setcounter{enumi}{6}
   \item Point or extended mass objects can be placed in the field.
@@
 the gross effects of a distant neighbour, since there is a degeneracy between
-the ellipticity of a lens and shear field: The greater the allowed shear, the
-more circular the lens may be.  \Glass\ also allows further analytic potential
-components to be included. This can be used to model substructure or multiple
+the ellipticity of a lens and its shear field (the greater the allowed shear, the
+more circular the lens may be). \Glass\ also allows further analytic potential
+components to be included. These can be used to model substructure or multiple
 neighbours close to the main lens. The substructure may have only a small
-effect if the lens is a single galaxy, but if the lens is a group then a
-potential can be added for each of the galaxies. A few standard functions are
+effect if the lens is a single galaxy, but if the lens is a group or cluster then a
+potential can be added for each of the known member galaxies. A few standard functions are
 already included in \Glass\ including those for a point mass, a power law
 distribution, or an isothermal (a particular case of the power law).
-%
-\begin{enumerate}
-  \setcounter{enumi}{6}
-  \item A new uniform sampling algorithm for high dimensional spaces.
-\end{enumerate}
-%
-At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
-linear space that represents the modelling solution space. This algorithm was
-described and tested in \cite{2012MNRAS.425.3077L}; it is multi-threaded
-allowing it to run efficiently on many-cored machines.
 
@@
 
-\subsection{Discrete models}\label{sec:discrete}
-For this paper, we will restrict ourselves to using a pixelated basis set that
-has been employed in previous work. The algorithm for generating models in
+\subsection{Pixelated models}\label{sec:discrete}
+For this paper, we will restrict ourselves to using a pixelated basis set as used by \PixeLens\ \citep{Saha2004,2008ApJ...679...17C}, but note that it is straightforward to add other basis function expansions to \Glass.
+The algorithm for generating models in
 \Glass\ samples a convex polytope in a high dimensional space whose interior
-points are solutions to the lens equation and satisfy other physically
-motivated linear priors.  We therefore formulate all of our equations as
+points satisfy both the lens equation and other physically
+motivated {\it linear} priors \citep{2012MNRAS.425.3077L}.
+A limitation of our sampling strategy is that only linear constraints may be applied when building the model ensemble; however, non-linear constraints can be applied in post-processing (see \secref{sec:glassextraimages} and \secref{sec:glasskinematics}).
+We therefore formulate all of our equations as
 equations linear in the unknowns. We describe the density distribution $\kappa$
 as a set of discrete grid cells or pixels $\kappa_i$ and rewrite the potential
-\eqnrefp{lensing potential} as
+\eqnrefp{lensing potential} as:
 %
@@
 account for any global shearing outside this region from, e.g., a neighboring
-galaxy, we also add to \eqnref{discrete potential} two shearing terms
+galaxy, we also add to \eqnref{discrete potential} two shearing terms:
 %
@@
 
-The lens equation and the arrival times alone are not enough to form a closed
-volume in the solution space. The data alone do not even constraint the density
-to be non-negative everywhere. We therefore provide additional linear
-constraints so that only physical models are sampled. 
-\Glass\ provides a number of typical constraints similar to those discussed in
-\cite{2008ApJ...679...17C}: 
-%
+\subsubsection{Priors}
+
+The lens equation and the arrival times alone are typically not enough to form a closed
+volume in the solution space. We therefore require additional linear
+constraints -- {\it priors}.
+Some of these are `physical' in the sense that they are unarguable -- for example demanding that the mass density is everywhere positive; others are more subjective, for example demanding that the mass map is smooth over some region.
+Such `regularisation' priors may be switched off for all or some of the mass map if the data are sufficiently constraining.
+
+The priors built in to \Glass\ are similar to those used in \PixeLens\ \citep{2008ApJ...679...17C}.
+The physical priors are always used by default; the regularisation priors are used sparingly -- i.e.
+only if the data are not sufficiently constraining to obtain sensible solutions without them:
+
+%
+\vspace{2mm}
+\noindent
+{\bf Physical priors}
 \begin{enumerate}
 \item The density must be non-negative everywhere.
+\item Image parity is enforced.
+\end{enumerate}
+
+\vspace{1mm}
+\noindent
+{\bf Regularisation priors}
+\begin{enumerate}
+\item The local gradient everywhere must point within $45^{\circ}$ of the center.
 \item The azimuthally averaged density profile must have a slope everywhere $\le 0$.
-\item Image parity is enforced.
-\item The local gradient everywhere must point within $45^{\circ}$ of the center.
-\item Density variations must be smooth.
 \item The density is inversion symmetric.
 \end{enumerate}
-
-The first three of these priors are very important for creating physically
-meaningful lenses. Prior (ii) is necessary to prevent rings from forming where
-the inner region is less dense. This would be unusual for a galaxy or a
-cluster. Prior (iv) can be relaxed somewhat by increasing the angle. The
-smoothness prior (v) requires pixel values to be less than a constant factor
-(normally 2) of the average neighbor value. This can be relaxed by increasing
-the constant or completely disabled. For this paper, we have chosen \emph{not}
-to use this prior, and therefore allow for the presence of small density
-substructure.  Prior (vi) enforces a radial symmetry that requires radially
-opposed pixels (i.e., on opposite sides of the center) to be equal. This prior
-is particularly important for modelling doubles which must be symmetric. If a
-lens is suspected to be symmetric this can also significantly improve the
-modelling time for quads.
-
-While most of these priors have been selected for modelling galaxies, there
-are several ways to address clusters or allow for the presence of substructure.
-As previously described, one can add any number of additional analytic 
-potentials inside or outside the main modelling pixelation area. For instance,
-in a cluster, one can explicitly account for galaxies with power law potentials.
-Furthermore, Priors (iv) and (v) and be relaxed or disabled. We have perfomed
-preliminary testing of these ideas several common clusters and are encouraged
-by the results. We will reserve a full analysis for a future publication.
+For typical lens data, the regularisation priors are very important for creating physically
+sensible solutions.
+Prior (i) demands that the peak in the mass density is at the centre of the mass map.
+Secondary `plateaus' in the mass map are possible, but not secondary peaks.
+Note that this prior still successfully allows merging galaxy systems to be correctly captured, provided that the two galaxies are not equally dense in projection (see, for example the \PixeLens\ model of the merger system B1608 in \citealt{2007ApJ...667..645R}); and for the successful detection of `meso-structure' in strong lensing galaxy clusters \citep{2007ApJ...663...29S}.
+Prior (ii) is arguably a physical prior sense negative azimuthally averaged density slope would be unstable \citep[e.g.][]{2008gady.book.....B}.
+Note that this prior does not preclude successful modelling of mergers or substructure unless the total projected mass in substructure is comparable to the projected mass of the host in an azimuthal annulus \citep{2007ApJ...667..645R,2007ApJ...663...29S}.
+Prior (iii) is only used for doubles that ought to be inversion symmetric and quads where inversion symmetry is clear from the image configuration.
+
+Finally, we remind the reader that all of the regularisation priors can be switched off or changed/improved depending on the data quality available.
+For clusters, substructure can be explicitly modelled by adding analytic potentials at the known locations of galaxies; furthermore the above priors can be relaxed in regions of the mass map where the data are particularly constraining (for example near the images).
+We will apply \Glass\ to a host of strong lensing clusters in forthcoming work, where we will explicitly test the prior on mock data that has significant substructure.
+
+\subsection{Building the model ensemble}
 
@@
 modeling process. For instance, non-linear constraints, or simply filtering
-of models that do not meet some criteria can be excluded, or weighted against.
-For the current analysis, we do not exclude any models and treat all models
+of models that do not meet some criteria can be excluded, or weighted against as discussed previously.
+In this paper, we do not exclude any models and treat all models
 as equally likely.
@@
 shared-memory machine with 40 cores.
+The ability to rapidly generate so many models is what allows us to then accept/reject models to apply non-linear constraints (see \secref{sec:glassextraimages} and \secref{sec:glasskinematics}).
+This is a key advantage over our earlier pixelated strong lens tool \PixeLens.
 
@@
 The radially averaged two-dimensional projected density.
-The critical density for lensing at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
+The critical lensing density at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
 \textbf{Right:}
@@
 equally spaced. For all mocks, we do not apply any external shear field.  Only
-the central image of the Z1 source is used to avoid overconstraining the
+the central image of the Z1 source is used to avoid over-constraining the
 models, otherwise all the central images would fall within the central pixel
@@
 indicates the redshift of the sources with Z1=1.72, Z2=0.72, and Z3=0.51.  The
-central image only belongs to the Z1 source to avoid overconstraining the
-models. Images of the same color share a common source. The extended source examples have been
-contructed so that the images will form arclets.
+central image only belongs to the Z1 source to avoid over-constraining the
+models (see \secref{sec:lensconfig} for further details). Images of the same colour share a common source. The extended source examples have been constructed so that the images will form arclets.
 Grey circles are a visual aid
@@
 distribution for the single quad with time delays. The contours are logarithmic
-base 10 values, where level 0 corresponds to the critical density. Contours
-below the critical density are drawn with dashed lines.}
+base 10 values, where level 0 corresponds to the critical lensing density. Contours
+below the critical lensing density are drawn with dashed lines.}
 \label{2d mass reconstruction}
@@
 each of the test configurations with (red) and without (black) stellar mass. In
-\figref{main results} we define the error
+\figref{main results} we define the error:
 %
@@
 implicitly weighting the recovered density by the varying size of the pixels.
-The value $f_R$ emphasizes the error one would see from radial profiles, while
+The value $f_R$ emphasises the error one would see from radial profiles, while
 $f_\theta$ is useful as a measure of how well each individual pixel is recovered.
@@
 uniformly on the projected disc. The more dissimilar they are, the more
-elliptical the mass distribution. We define the global measure of lens shape as
+elliptical the mass distribution. We define the global measure of lens shape as:
 %

### 2014-07-28 limits/ms.tex
New and improvied plots. Mentioned separation of sources in Figure 3 caption.

@@
 mock galaxy. The other mock galaxies produce similar results. Here, the central
-image is shown, although not all tests include it. The naming convention
-indicates the redshift of the sources with Z1=1.72, Z2=0.72, and Z3=0.51.  The
-central image only belongs to the Z1 source to avoid over-constraining the
-models (see \secref{sec:lensconfig} for further details). Images of the same colour share a common source. The extended source examples have been constructed so that the images will form arclets.
-Grey circles are a visual aid
-to help determine radial separation between images. The axes are in
-arcseconds.}
+image is shown, although not all tests include it. 
+The naming convention indicates the redshift of the
+sources with Z1=1.72, Z2=0.72, and Z3=0.51.  The central image only belongs to
+the Z1 source to avoid over-constraining the models (see
+\secref{sec:lensconfig} for further details). 
+Small diamonds identify the location of the source(s) and images of the same shape share a
+common source. The extended source examples have been constructed so that the
+images will form arclets.  The maximum separation of the sources in the source plane
+is 2.23 kpc in the extended double and 0.92 kpc in the extended quad. Grey
+circles are a visual aid to help determine radial separation between images.
+The axes are in arcseconds.}
 \label{arrival surfaces}
@@
 \caption{
-    Two reconstructions of the mock galaxy \mockBC for an extended
+    Two reconstructions of the mock galaxy \mockBC\ for an extended
     double without stellar mass (\textbf{Top}) and with stellar mass
@@
 saddle points drawn. The central diamonds show the reconstructed source
-position.
+positions.
 \textbf{Middle:}
-The surface density of the dark matter (DM; magenta); the stars (yellow); and the total (blue).
-The original mass model (with stars) used to create the lens is shown in black.
+The surface density of the dark matter (DM; magenta); the stars (yellow); and the total (black).
+The original $N$-body mass model (with stars) used to create the lens is shown in green.
 The vertical lines mark the radial positions of the images. The higher
@@
 \begin{figure*}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d.pdf}\\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_tms-appendix-a.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_tms-appendix-b.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_tms-appendix-c.pdf}
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_tms-appendix-d.pdf}\\
 %
@@
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr10_TmS-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr10_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr10_TmS-c.pdf}\\
+%
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-a.pdf}
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr7_TmS-c.pdf}\\
+%
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-a.pdf}
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr6_TmS-c.pdf}\\
+%
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-a.pdf}
 \includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-b.pdf}
-\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-c.pdf} \\
+\includegraphics[width=0.24\textwidth]{BCQuadR1a-pr5_TmS-c.pdf}\\
 \caption{The effect of changing the grid resolution parameter \pixrad. From top
@@
     outermost image, which causes the total mass to increase with decreasing
-    \pixrad.  In this paper we have used $\pixrad = 8$ in all the
+    \pixrad, and the plot to shrink with increase pixel size.  In this paper we have used $\pixrad = 8$ in all the
 tests.}

### 2014-07-28 limits/ms.tex
New Figure 9 and caption.

@@
 \caption{ Estimated projected radially averaged velocity dispersion $\sigma_p$
-\eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC{} mock galaxy without stellar mass
-(\textbf{left}) and with stellar mass (\textbf{middle}) assuming an anisotropy $\beta=0$
-(blue, solid) and $\beta=1$ (blue, dashed).  The equivalent
-curves are also shown for the projected mock data after using the same analysis routines
-(purple). The solid black line is the actual cylindrically averaged velocity
-dispersion of the original mock particle data.  The stellar half mass radius
-(yellow) Einstein radius (black) are marked by vertical lines. For this
-configuration, these two radii are well-separated. The actual variation in $\beta(r)$ is also shown (\textbf{right}).}
+\eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC{} mock galaxy
+without stellar mass (\textbf{left}) and with stellar mass (\textbf{middle})
+assuming an anisotropy $\beta=0$ (black, solid) and $\beta=1$ (black, dashed).
+Error bars are $1\sigma$ and hatched areas indicate the full range of models.
+The equivalent curves are also shown for the projected mock data after using
+the same analysis routines (purple). The solid green line is the actual
+cylindrically averaged velocity dispersion of the original mock particle data.
+The stellar half mass radius (orange) Einstein radius (black) are marked by
+vertical lines. For this configuration, these two radii are well-separated. The
+actual variation in $\beta(r)$ is also shown (\textbf{right}).}
 \label{fig:sigp} \end{figure*}

### 2014-08-11 limits/ms.tex

@@
 %\usepackage{ulem} % Only necessary for striking out TODO items see \sout
-\usepackage[usenames,dvipsnames]{color} % Only necessary for hilight
+%\usepackage[usenames,dvipsnames]{color} % Only necessary for hilight
 
@@
 %-------------------------------------------------------------------------------
-\newcommand{\hilight}[1]{{\bf \color{OliveGreen} #1}}
+%\newcommand{\hilight}[1]{{\bf \color{OliveGreen} #1}}
 
@@
 \title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
-%\title[Lens Recovery with \Glass]{Stellar Mass and Stellar Kinematics Can Constrain Gravitational Lens Models}
 \author[J.~P.~Coles~et~al.]{%
@@
 Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
-date\footnote{See, e.g., {\url{http://masterlens.astro.utah.edu}} for a catalogue.}.
-However, this number is expected to increase to several thousand over the next
-ten years as new surveys, both
+date\footnote{See, e.g., {\url{http://masterlens.astro.utah.edu}} for a
+catalogue.}.  However, this number is expected to increase to several thousand
+over the next ten years as new surveys, both
 ground-based\footnote{\url{http://pan-starrs.ifa.hawaii.edu}}$^{\rm,}$\footnote{\url{http://www.darkenergysurvey.org}}
-and space-based\footnote{\url{http://www.euclid-ec.org}} -- together with a community
-of citizen-science volunteers examining the image data for
+and space-based\footnote{\url{http://www.euclid-ec.org}} -- together with a
+community of citizen-science volunteers examining the image data for
 candidates\footnote{\url{http://spacewarps.org}} -- come online.
@@
 
-To see why lens modelling details are of crucial importance, let us
-recall the essential quantities that appear in lensing (see also \S\ref{sec:theory} for a more detailed exposition). First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
-angular-diameter distances to the lens, source, and from lens to
-source; these are all proportional to $c/H_0$ but have factors
-that depend on the particular choice of cosmology\footnote{Here, $c$ is the speed of light in vacuo and $H_0$ is the Hubble parameter.}.  Typically:
+To see why lens modelling details are of crucial importance, let us recall the
+essential quantities that appear in lensing (see also \S\ref{sec:theory} for a
+more detailed exposition). First we have the distances. Let $D_L$, $D_S$,
+$D_{LS}$ be the angular-diameter distances to the lens, source, and from lens
+to source; these are all proportional to $c/H_0$ but have factors that depend
+on the particular choice of cosmology\footnote{Here, $c$ is the speed of light
+in vacuo and $H_0$ is the Hubble parameter.}.  Typically:
 %
@@
 %
-For multiple images, the sky-projected density must exceed the critical lensing density in some region:
+For multiple images, the sky-projected density must exceed the critical lensing
+density in some region:
 %
@@
 %
-where $\langle v^2_\mathrm{los}\rangle$ is the line of sight stellar
-velocity dispersion, and the above relation becomes exact for
-isothermal lenses.
-This can then be used to probe cosmological parameters if lenses are known to be isothermal \citep[e.g.][]{2012MNRAS.424.2864C}; or to break the steepness degeneracy in the more general situation (see \S\ref{sec:kinematics}).
-The technique has since been applied to many lenses \citep[e.g.][]{2006ApJ...649..599K,2008ApJ...682..964B}.
-Going further, the
-use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is
-especially interesting.
+where $\langle v^2_\mathrm{los}\rangle$ is the line of sight stellar velocity
+dispersion, and the above relation becomes exact for isothermal lenses. This
+can then be used to probe cosmological parameters if lenses are known to be
+isothermal \citep[e.g.][]{2012MNRAS.424.2864C}; or to break the steepness
+degeneracy in the more general situation (see \S\ref{sec:kinematics}). The
+technique has since been applied to many lenses
+\citep[e.g.][]{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
+use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is especially
+interesting.
 
@@
     inferred from photometry and compared with the total mass
-    \citep[e.g.][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
-    the inferred stellar mass depends on the assumed IMF, lenses in which
+    \citep[e.g.][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
+    Since the inferred stellar mass depends on the assumed IMF, lenses in which
     stellar mass dominates can be used to derive upper bounds on the stellar
     $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds on stellar $M/L$ have also
-    recently been claimed by fitting $\Lambda$CDM semi-analytic models to the tilt of the fundamental plane \citep{2013MNRAS.428.3183D}.
+    recently been claimed by fitting $\Lambda$CDM semi-analytic models to the
+    tilt of the fundamental plane \citep{2013MNRAS.428.3183D}.
 
@@
 
-In this paper, we introduce a new non-parametric lens modelling framework  -- \Glass\ (Gravitational
-Lensing AnalysiS Software).
-This shares some aspects with an earlier code \PixeLens \citep{Saha2004,2008ApJ...679...17C}.
-However, \Glass\ -- which contains all new code written from the ground up -- significantly improves upon \PixeLens\ in several key ways:
+In this paper, we introduce a new non-parametric lens modelling framework  --
+\Glass\ (Gravitational Lensing AnalysiS Software). This shares some aspects
+with an earlier code \PixeLens \citep{Saha2004,2008ApJ...679...17C}. However,
+\Glass\ -- which contains all new code written from the ground up --
+significantly improves upon \PixeLens\ in several key ways:
 
 \begin{enumerate}
-\item At the heart of \Glass\ is a new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L}.
-This allows for large ensembles of $>10,000$ models to be efficiently generated.
-\item \Glass\ provides a modular framework that allows new priors to be added and modified easily.
-\item The basis functions approximating a model can be easily changed (in this paper, we assume pixels as in \PixeLens). 
-\item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
-\item The central region of the mass map can have a higher resolution to more efficiently capture steep models.
+\item At the heart of \Glass\ is a new uniform sampling algorithm for high
+    dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large
+    ensembles of $>10,000$ models to be efficiently generated. 
+\item \Glass\ provides a modular framework that allows new priors to be added
+    and modified easily.
+\item The basis functions approximating a model can be easily changed (in this
+    paper, we assume pixels as in \PixeLens). 
+\item With so many models in the final ensemble, we can afford to apply
+    non-linear constraints (for example stellar kinematic data; or the removal of
+    models with spurious extra images) to accept/reject models in a post-processing
+    step.
+\item The central region of the mass map can have a higher resolution to more
+    efficiently capture steep models.
 \item Stellar density can be used as an additional constraint on the models. 
@@
 \end{enumerate}
-As a first application, we use \Glass\ on mock data to determine which combination of lensing, stellar mass and/or 
-stellar kinematic constraints best constrain the projected mass profile and
-shape of a gravitational lens. We will apply \Glass\ to real lens data in a series of forthcoming papers.
-
-%The compute-intensive core of \Glass\ is a parallel
-%implementation of the high-dimensional sampling algorithm from
-%\cite{2012MNRAS.425.3077L}.  Around that core, \Glass\ has extensible code (in
-%software terminology, a framework) in Python, encoding the lens equation, a
-%basis and priors for the mass distribution, and various post-processing and
-%visualisation modules.
-
-This paper is organised as follows. In \secref{sec:glass}, we describe the \Glass\ code. In \secref{sec:theory}, we review
-the key elements of lensing theory, stellar population synthesis, and stellar
-dynamics we will need. In \secref{sec:mockdata}, we describe our mock data. In
-\secref{sec:results}, we present our results from applying \Glass\ to these
-mock data. Finally, in \secref{sec:conclusions} we present our conclusions.
+%
+As a first application, we use \Glass\ on mock data to determine which
+combination of lensing, stellar mass and/or stellar kinematic constraints best
+constrain the projected mass profile and shape of a gravitational lens. We will
+apply \Glass\ to real lens data in a series of forthcoming papers.
+
+This paper is organised as follows. In \secref{sec:glass}, we describe the
+\Glass\ code. In \secref{sec:theory}, we review the key elements of lensing
+theory, stellar population synthesis, and stellar dynamics we will need. In
+\secref{sec:mockdata}, we describe our mock data. In \secref{sec:results}, we
+present our results from applying \Glass\ to these mock data. Finally, in
+\secref{sec:conclusions} we present our conclusions.
 
@@
                    \ln|\vec\theta - \vec\theta'| d^2\vec\theta'
-\label{arrival time}
+\label{arrival time2}
 \end{equation}
@@
 if $\tau(\vec\theta)$ is multiplied by an arbitrary constant.  
-\hilight{This corresponds
-to rescaling the surface density at the images $\kappa(\vec\theta)$.} In fact
-there are infinitely many degeneracies \citep{2000AJ....120.1654S} because any
-transformation of the arrival-time surface away from the images has no effect
-on the lensing observables.  In particular, there are degeneracies that involve
-the shape of the mass distribution
-\citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies tend to be
-suppressed if there are sources at very different redshifts or `redshift
-contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because the presence
-of different factors of $D_S/D_{LS}$ in the image plane makes it more difficult
-to change the mass distribution and the arrival-time surface without affecting
-the lensing observables. But degeneracies are still present with multiple
-source redshifts \citep{2008MNRAS.386..307L,2014arXiv1406.6152S}.
+This corresponds to rescaling the surface density at the images
+$\kappa(\vec\theta)$. In fact there are infinitely many degeneracies
+\citep{2000AJ....120.1654S} because any transformation of the arrival-time
+surface away from the images has no effect on the lensing observables.  In
+particular, there are degeneracies that involve the shape of the mass
+distribution \citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies
+tend to be suppressed if there are sources at very different redshifts or
+`redshift contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because
+the presence of different factors of $D_S/D_{LS}$ in the image plane makes it
+more difficult to change the mass distribution and the arrival-time surface
+without affecting the lensing observables. But degeneracies are still present
+with multiple source redshifts \citep{2008MNRAS.386..307L,2014arXiv1406.6152S}.
 
@@
 be used as a filter to accept or reject a model based on some non-linear
-constraint.
-For example, we can reject models that have spurious extra images (\secref{sec:glassextraimages}), or models that do not match stellar kinematic constraints (\secref{sec:glasskinematics}).
-The plotting functions within \Glass\ will correctly display models
-that have been accepted or rejected.
+constraint. For example, we can reject models that have spurious extra images
+(\secref{sec:glassextraimages}), or models that do not match stellar kinematic
+constraints (\secref{sec:glasskinematics}). The plotting functions within
+\Glass\ will correctly display models that have been accepted or rejected.
 %
@@
 \subsection{Pixelated models}\label{sec:discrete}
-For this paper, we will restrict ourselves to using a pixelated basis set as used by \PixeLens\ \citep{Saha2004,2008ApJ...679...17C}, but note that it is straightforward to add other basis function expansions to \Glass.
-The algorithm for generating models in
-\Glass\ samples a convex polytope in a high dimensional space whose interior
-points satisfy both the lens equation and other physically
-motivated {\it linear} priors \citep{2012MNRAS.425.3077L}.
-A limitation of our sampling strategy is that only linear constraints may be applied when building the model ensemble; however, non-linear constraints can be applied in post-processing (see \secref{sec:glassextraimages} and \secref{sec:glasskinematics}).
-We therefore formulate all of our equations as
-equations linear in the unknowns. We describe the density distribution $\kappa$
-as a set of discrete grid cells or pixels $\kappa_i$ and rewrite the potential
+For this paper, we will restrict ourselves to using a pixelated basis set as
+used by \PixeLens\ \citep{Saha2004,2008ApJ...679...17C}, but note that it is
+straightforward to add other basis function expansions to \Glass. The algorithm
+for generating models in \Glass\ samples a convex polytope in a high
+dimensional space whose interior points satisfy both the lens equation and
+other physically motivated {\it linear} priors \citep{2012MNRAS.425.3077L}.
+A limitation of our sampling strategy is that only linear constraints may
+be applied when building the model ensemble; however, non-linear
+constraints can be applied in post-processing (see
+\secref{sec:glassextraimages} and \secref{sec:glasskinematics}). We
+therefore formulate all of our equations as equations linear in the
+unknowns. We describe the density distribution $\kappa$ as a set of
+discrete grid cells or pixels $\kappa_i$ and rewrite the potential
 \eqnrefp{lensing potential} as:
@@
 
-The lens equation and the arrival times alone are typically not enough to form a closed
-volume in the solution space. We therefore require additional linear
-constraints -- {\it priors}.
-Some of these are `physical' in the sense that they are unarguable -- for example demanding that the mass density is everywhere positive; others are more subjective, for example demanding that the mass map is smooth over some region.
-Such `regularisation' priors may be switched off for all or some of the mass map if the data are sufficiently constraining.
-
-The priors built in to \Glass\ are similar to those used in \PixeLens\ \citep{2008ApJ...679...17C}.
-The physical priors are always used by default; the regularisation priors are used sparingly -- i.e.
-only if the data are not sufficiently constraining to obtain sensible solutions without them:
+The lens equation and the arrival times alone are typically not enough to form
+a closed volume in the solution space. We therefore require additional linear
+constraints -- {\it priors}. Some of these are `physical' in the sense that
+they are unarguable -- for example demanding that the mass density is
+everywhere positive; others are more subjective, for example demanding that the
+mass map is smooth over some region. Such `regularisation' priors may be
+switched off for all or some of the mass map if the data are sufficiently
+constraining.
+
+The priors built in to \Glass\ are similar to those used in \PixeLens\
+\citep{2008ApJ...679...17C}. The physical priors are always used by default;
+the regularisation priors are used sparingly -- i.e. only if the data are not
+sufficiently constraining to obtain sensible solutions without them:
 
@@
 \end{enumerate}
-For typical lens data, the regularisation priors are very important for creating physically
-sensible solutions.
-Prior (i) demands that the peak in the mass density is at the centre of the mass map.
-Secondary `plateaus' in the mass map are possible, but not secondary peaks.
-Note that this prior still successfully allows merging galaxy systems to be correctly captured, provided that the two galaxies are not equally dense in projection (see, for example the \PixeLens\ model of the merger system B1608 in \citealt{2007ApJ...667..645R}); and for the successful detection of `meso-structure' in strong lensing galaxy clusters \citep{2007ApJ...663...29S}.
-Prior (ii) is arguably a physical prior sense negative azimuthally averaged density slope would be unstable \citep[e.g.][]{2008gady.book.....B}.
-Note that this prior does not preclude successful modelling of mergers or substructure unless the total projected mass in substructure is comparable to the projected mass of the host in an azimuthal annulus \citep{2007ApJ...667..645R,2007ApJ...663...29S}.
-Prior (iii) is only used for doubles that ought to be inversion symmetric and quads where inversion symmetry is clear from the image configuration.
-
-Finally, we remind the reader that all of the regularisation priors can be switched off or changed/improved depending on the data quality available.
-For clusters, substructure can be explicitly modelled by adding analytic potentials at the known locations of galaxies; furthermore the above priors can be relaxed in regions of the mass map where the data are particularly constraining (for example near the images).
-We will apply \Glass\ to a host of strong lensing clusters in forthcoming work, where we will explicitly test the prior on mock data that has significant substructure.
+%
+For typical lens data, the regularisation priors are very important for
+creating physically sensible solutions. Prior (i) demands that the peak in the
+mass density is at the centre of the mass map. Secondary `plateaus' in the mass
+map are possible, but not secondary peaks. Note that this prior still
+successfully allows merging galaxy systems to be correctly captured, provided
+that the two galaxies are not equally dense in projection (see, for example the
+\PixeLens\ model of the merger system B1608 in \citealt{2007ApJ...667..645R});
+and for the successful detection of `meso-structure' in strong lensing galaxy
+clusters \citep{2007ApJ...663...29S}. Prior (ii) is arguably a physical prior
+sense negative azimuthally averaged density slope would be unstable
+\citep[e.g.][]{2008gady.book.....B}. Note that this prior does not preclude
+successful modelling of mergers or substructure unless the total projected mass
+in substructure is comparable to the projected mass of the host in an azimuthal
+annulus \citep{2007ApJ...667..645R,2007ApJ...663...29S}. Prior (iii) is only
+used for doubles that ought to be inversion symmetric and quads where inversion
+symmetry is clear from the image configuration.
+
+Finally, we remind the reader that all of the regularisation priors can be
+switched off or changed/improved depending on the data quality available. For
+clusters, substructure can be explicitly modelled by adding analytic potentials
+at the known locations of galaxies; furthermore the above priors can be relaxed
+in regions of the mass map where the data are particularly constraining (for
+example near the images). We will apply \Glass\ to a host of strong lensing
+clusters in forthcoming work, where we will explicitly test the prior on mock
+data that has significant substructure.
 
@@
 generate $|\E| \sim 1000$ models. One can choose to further process these
-models to impose priors that may be difficult to enforce during the
-modeling process. For instance, non-linear constraints, or simply filtering
-of models that do not meet some criteria can be excluded, or weighted against as discussed previously.
-In this paper, we do not exclude any models and treat all models
-as equally likely.
+models to impose priors that may be difficult to enforce during the modeling
+process. For instance, non-linear constraints, or simply filtering of models
+that do not meet some criteria can be excluded, or weighted against as
+discussed previously.  In this paper, we do not exclude any models and treat
+all models as equally likely.
 
@@
 ``warm-up'' time was about 4s, and the modelling time was 20s using a parallel
-shared-memory machine with 40 cores.
-The ability to rapidly generate so many models is what allows us to then accept/reject models to apply non-linear constraints (see \secref{sec:glassextraimages} and \secref{sec:glasskinematics}).
-This is a key advantage over our earlier pixelated strong lens tool \PixeLens.
+shared-memory machine with 40 cores. The ability to rapidly generate so many
+models is what allows us to then accept/reject models to apply non-linear
+constraints (see \secref{sec:glassextraimages} and
+\secref{sec:glasskinematics}). This is a key advantage over our earlier
+pixelated strong lens tool \PixeLens.
 
@@
 profile of our mock lenses. The left column shows the ensemble average arrival
-time surface with images marked as circles and the inferred source position(s)
-as a diamond. The centre column shows the radial density profile. The error
+time surface with images marked as circles and the inferred source positions
+as diamonds. The centre column shows the radial density profile. The error
 bars cover a $1\sigma$ range around the median; the grey bands show the full
@@
 
-As expected, the error bars are smallest in the region of the images where the
-most information about the lens is present. In all cases, there is a dip in the
-profile at large $R$ due to the cut off in mass in the lensing map. This is of
-little importance, though, as there is no lensing information there.
+As expected, the accuracies and precisions are best in the range of radii with
+lensed images where the most information about the lens is present. Even in the
+weakly constrained case of the extended double where the radial profile is
+poor, the true enclosed mass $M(<R)$ is well recovered at the image radii and
+our ensemble always encompasses it. We have verified this is the case in all of
+our tests, although for brevity we have not included the plots here. In all
+cases, there is a dip in the profile at large $R$ due to the cut off in mass in
+the lensing map. This is of little importance, though, as there is no lensing
+information there.
 
@@
 \begin{figure*}
+\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
 \includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
-\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
 \caption{ \textbf{Left:} The mock data distribution for \mockBC{} projected
@@
 radial profile is well-recovered then, typically, the shape is too. A notable
-exception is for the \mockBC\ models where adding stellar mass constrains aids
+exception is for the \mockBC\ models where adding stellar mass constraints aids
 the shape recovery, but little-improves the radial mass profile. A visual
@@
 without stellar mass (\textbf{left}) and with stellar mass (\textbf{middle})
-assuming an anisotropy $\beta=0$ (black, solid) and $\beta=1$ (black, dashed).
-Error bars are $1\sigma$ and hatched areas indicate the full range of models.
+assuming an anisotropy $\beta=0$ (black triangles) and $\beta=1$ (black squares).
+Error bars are $1\sigma$ and two overlapping hatched areas indicate the full range of models.
 The equivalent curves are also shown for the projected mock data after using
-the same analysis routines (purple). The solid green line is the actual
+the same analysis routines (green). The solid blue line is the actual
 cylindrically averaged velocity dispersion of the original mock particle data.
@@
 $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.  Instead of
-working with a position vector $\vec\theta$ we work in cartesian coordinates
+working with a position vector $\vec\theta$ we work in Cartesian coordinates
 where 

### 2014-08-29 limits/ms.tex
Updated address of JPC, inserted a few references. Minor .tex changes.

@@
 \newauthor%
-Justin I.~Read$^2$,%
+Justin~I.~Read$^2$,%
 \newauthor%
-and Prasenjit Saha$^3$%
+and Prasenjit~Saha$^3$%
 %
 \\
-$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$45 avenue des Etats-Unis, 78035, Versailles, France\\
+$^1$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France \\
 $^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
@@
 \begin{abstract}
-We use a new non-parametric gravitational modelling tool -- \Glass\ -- to
+We use a new non-parametric gravitational modelling tool -- \Glass{} -- to
 determine what quality of data (strong lensing, stellar kinematics, and/or
 stellar masses) are required to measure the circularly averaged mass profile of
-a lens and its shape. \Glass\ uses an under-constrained adaptive grid of mass
+a lens and its shape. \Glass{} uses an under-constrained adaptive grid of mass
 pixels to model the lens, searching through thousands of models to marginalise
@@
 Strong gravitational lenses are rare. Since the discovery of the first lens
-Q0957+561 \citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
+Q0957+561~\citep{1979Natur.279..381W}, just $\sim400$ have been discovered to
 date\footnote{See, e.g., {\url{http://masterlens.astro.utah.edu}} for a
@@
 Since lensing depends only on gravity, strong lenses offer a unique window onto
-dark matter and cosmology \citep{2010CQGra..27w3001B,2012arXiv1206.1225A}.
+dark matter and cosmology \citep{2010CQGra..27w3001B,2013LRR....16....6A}.
 However, extracting dark matter properties or cosmological constraints from
@@
   lenses
-  \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S},
+  \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2014MNRAS.437.2642S},
   but can be used with galaxy lenses as well, where their less
@@
   tension with independent measures 
-  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
+  \citep[e.g.,][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
   resolved once the less restrictive assumptions of free-form models
@@
     combating the non-uniqueness of models.  Such ensembles are possible in
-    parametric models \citep[e.g.][]{1999AJ....118...14B,2010Sci...329..924J} but are more common in
+    parametric models \citep[e.g.,][]{1999AJ....118...14B,2010Sci...329..924J},
+    and more recently with the Hubble Frontier Fields initiative
+    \citep[e.g.,][]{}, but are more common in
     free-form models, where -- since such models are deliberately
@@
 can then be used to probe cosmological parameters if lenses are known to be
-isothermal \citep[e.g.][]{2012MNRAS.424.2864C}; or to break the steepness
+isothermal \citep[e.g.,][]{2012MNRAS.424.2864C}; or to break the steepness
 degeneracy in the more general situation (see \S\ref{sec:kinematics}). The
 technique has since been applied to many lenses
-\citep[e.g.][]{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
+\citep[e.g.,][]{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
 use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is especially
@@
     inferred from photometry and compared with the total mass
-    \citep[e.g.][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
+    \citep[e.g.,][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.
     Since the inferred stellar mass depends on the assumed IMF, lenses in which
@@
 touch upon in this present work: to use X-ray intensity and temperature
-profiles as a mass constraint \citep[e.g.][]{2013ApJ...765...25N}; and to model
+profiles as a mass constraint \citep[e.g.,][]{2013ApJ...765...25N}; and to model
 multiple lenses simultaneously, with one or more cosmological parameters
@@
 multiple redshifts \citep{2014MNRAS.437.2461L} or by using additional priors 
-\citep{2010Sci...329..924J,2013arXiv1306.4732S}.
+\citep{2010Sci...329..924J,2014ApJ...788L..35S}.
 
 In this paper, we introduce a new non-parametric lens modelling framework  --
-\Glass\ (Gravitational Lensing AnalysiS Software). This shares some aspects
-with an earlier code \PixeLens \citep{Saha2004,2008ApJ...679...17C}. However,
-\Glass\ -- which contains all new code written from the ground up --
-significantly improves upon \PixeLens\ in several key ways:
+\Glass{} (Gravitational Lensing AnalysiS Software). This shares some aspects
+with an earlier code \PixeLens{}~\citep{Saha2004,2008ApJ...679...17C}. However,
+\Glass{} -- which contains all new code written from the ground up --
+significantly improves upon \PixeLens{} in several key ways:
 
 \begin{enumerate}
-\item At the heart of \Glass\ is a new uniform sampling algorithm for high
+\item At the heart of \Glass{} is a new uniform sampling algorithm for high
     dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large
     ensembles of $>10,000$ models to be efficiently generated. 
-\item \Glass\ provides a modular framework that allows new priors to be added
+\item \Glass{} provides a modular framework that allows new priors to be added
     and modified easily.
@@
 %
-As a first application, we use \Glass\ on mock data to determine which
+As a first application, we use \Glass{} on mock data to determine which
 combination of lensing, stellar mass and/or stellar kinematic constraints best
 constrain the projected mass profile and shape of a gravitational lens. We will
-apply \Glass\ to real lens data in a series of forthcoming papers.
+apply \Glass{} to real lens data in a series of forthcoming papers.
 
 This paper is organised as follows. In \secref{sec:glass}, we describe the
-\Glass\ code. In \secref{sec:theory}, we review the key elements of lensing
+\Glass{} code. In \secref{sec:theory}, we review the key elements of lensing
 theory, stellar population synthesis, and stellar dynamics we will need. In
 \secref{sec:mockdata}, we describe our mock data. In \secref{sec:results}, we
-present our results from applying \Glass\ to these mock data. Finally, in
+present our results from applying \Glass{} to these mock data. Finally, in
 \secref{sec:conclusions} we present our conclusions.
@@
 particular, there are degeneracies that involve the shape of the mass
-distribution \citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies
+distribution \citep{2006ApJ...653..936S,2014A&A...564A.103S}.  Degeneracies
 tend to be suppressed if there are sources at very different redshifts or
@@
 without affecting the lensing observables. But degeneracies are still present
-with multiple source redshifts \citep{2008MNRAS.386..307L,2014arXiv1406.6152S}.
+with multiple source redshifts \citep{2008MNRAS.386..307L,2014A&A...568L...2S}.
 
@@
 initial mass function (IMF), the stellar mass can be inferred to 0.1 to 0.2 dex
-using just two photometric bands \citep[see e.g., Figure~1 in][]{2008MNRAS.383..857F}.
+using just two photometric bands \citep[see, e.g., Figure~1 in][]{2008MNRAS.383..857F}.
 By comparing the lensing-mass and stellar-mass profiles in elliptical galaxies,
@@
 lower limit on the stellar mass and hence, also a limit on the total
-mass.  Accordingly, \Glass\ allows a constraint of the form
+mass.  Accordingly, \Glass{} allows a constraint of the form
 %
@@
 galaxy. Assuming spherical symmetry, stars obey the projected Jeans equations
-\citep[e.g.][]{2008gady.book.....B}:
+\citep[e.g.,][]{2008gady.book.....B}:
 
@@
 sample eccentric orbits as $r\rightarrow 0$ and tangential orbits as
-$r\rightarrow \infty$ \citep[e.g.][]{2002MNRAS.330..778W}. It can also be
+$r\rightarrow \infty$ \citep[e.g.,][]{2002MNRAS.330..778W}. It can also be
 estimated if an independent measure of $\Mddd(r)$ is available -- for example
@@
 mass within the half light radius is robustly recovered
-\citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}
+\citep[e.g.,][]{2009ApJ...704.1274W,2010MNRAS.406.1220W,2012ApJ...754L..39A}
 since stellar systems in dynamic quasi-equilibrium obey the virial theorem
@@
 
-\Glass\ is the Gravitational Lensing AnalysiS Software. It extends and develops
-some of the concepts from the free form modelling tool \PixeLens\
-\citep{Saha2004,2008ApJ...679...17C}, but with all new code.  The most compute
-intensive portion was written in C but Python was chosen because of its
-flexibility as a language and for its large scientific library support. The
-flexibility allows \Glass\ to have quite sophisticated behavior while at the
-same time simplifying the user experience and reducing the overall development
-time. One of the striking features is that the input file to \Glass\ is itself
-a Python program.  Understanding Python is not necessary for the most basic
-use, but this allows a user to build complex analysis of a model directly into
-the input file. \Glass\ may furthermore be used as an external library to other
-Python programs.  {\it The software is freely available for download or from
-the first author.}%
+\Glass{} is the Gravitational Lensing AnalysiS Software. It extends and
+develops some of the concepts from the free form modelling tool
+\PixeLens{}~\citep{Saha2004,2008ApJ...679...17C}, but with all new code.  The
+most compute intensive portion was written in C but Python was chosen because
+of its flexibility as a language and for its large scientific library support.
+The flexibility allows \Glass{} to have quite sophisticated behavior while at
+the same time simplifying the user experience and reducing the overall
+development time. One of the striking features is that the input file to
+\Glass{} is itself a Python program.  Understanding Python is not necessary for
+the most basic use, but this allows a user to build complex analysis of a model
+directly into the input file. \Glass{} may furthermore be used as an external
+library to other Python programs.  {\it The software is freely available for
+download or from the first author.}%
 %
@@
 %
-At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
+At the heart of \Glass{} lies a new algorithm for sampling the high dimensional
 linear space that represents the modelling solution space. This algorithm was
@@
 Each prior is a simple function that adds linear constraints that operate on
-either a single lens object or the entire ensemble of objects. \Glass\ comes
+either a single lens object or the entire ensemble of objects. \Glass{} comes
 with a number of useful priors (the default ones will be described in \secref{sec:discrete}), but a
@@
 %
-\Glass\ currently describes the lens mass as a collection of pixels, but the
+\Glass{} currently describes the lens mass as a collection of pixels, but the
 code has been designed to support alternative methods. In particular, there are
@@
 %
-Once \Glass\ has generated an ensemble of models given the linear constraints,
+Once \Glass{} has generated an ensemble of models given the linear constraints,
 any number of post processing functions can be applied. Not only can these
@@
 constraints (\secref{sec:glasskinematics}). The plotting functions within
-\Glass\ will correctly display models that have been accepted or rejected.
+\Glass{} will correctly display models that have been accepted or rejected.
 %
@@
 the ellipticity of a lens and its shear field (the greater the allowed shear, the
-more circular the lens may be). \Glass\ also allows further analytic potential
+more circular the lens may be). \Glass{} also allows further analytic potential
 components to be included. These can be used to model substructure or multiple
@@
 potential can be added for each of the known member galaxies. A few standard functions are
-already included in \Glass\ including those for a point mass, a power law
+already included in \Glass{} including those for a point mass, a power law
 distribution, or an isothermal (a particular case of the power law).
@@
 \subsection{Analysis Tools}\label{sec:tools}
-\Glass\ is not only a modeling tool but also an analysis engine. \Glass\
+\Glass{} is not only a modeling tool but also an analysis engine. \Glass{}
 provides many functions for viewing and manipulating the computed models.
@@
 tool, \textsc{lenspick.py} for creating a lens, either analytically or from an
-$N$-body simulation file. To load the simulation data, \Glass\ relies on the
+$N$-body simulation file. To load the simulation data, \Glass{} relies on the
 \textsc{Pynbody} library \citep{pynbody} and can thus load any file supported
@@
 For this paper, we will restrict ourselves to using a pixelated basis set as
-used by \PixeLens\ \citep{Saha2004,2008ApJ...679...17C}, but note that it is
+used by \PixeLens{} \citep{Saha2004,2008ApJ...679...17C}, but note that it is
 straightforward to add other basis function expansions to \Glass. The algorithm
-for generating models in \Glass\ samples a convex polytope in a high
+for generating models in \Glass{} samples a convex polytope in a high
 dimensional space whose interior points satisfy both the lens equation and
@@
 may want to impose a base potential over the field, or add potentials from the
-presence of other galaxies in the field. \Glass\ already includes potentials
+presence of other galaxies in the field. \Glass{} already includes potentials
 for a point mass or an exponential form, but custom potentials are
@@
 
-The priors built in to \Glass\ are similar to those used in \PixeLens\
-\citep{2008ApJ...679...17C}. The physical priors are always used by default;
-the regularisation priors are used sparingly -- i.e. only if the data are not
-sufficiently constraining to obtain sensible solutions without them:
+The priors built in to \Glass{} are similar to those used in
+\PixeLens{}~\citep{2008ApJ...679...17C}. The physical priors are always used by
+default; the regularisation priors are used sparingly -- i.e. only if the data
+are not sufficiently constraining to obtain sensible solutions without them:
 
@@
 that the two galaxies are not equally dense in projection (see, for example the
-\PixeLens\ model of the merger system B1608 in \citealt{2007ApJ...667..645R});
+\PixeLens{} model of the merger system B1608 in \citealt{2007ApJ...667..645R});
 and for the successful detection of `meso-structure' in strong lensing galaxy
 clusters \citep{2007ApJ...663...29S}. Prior (ii) is arguably a physical prior
-sense negative azimuthally averaged density slope would be unstable
-\citep[e.g.][]{2008gady.book.....B}. Note that this prior does not preclude
+since a negative azimuthally averaged density slope would be unstable
+\citep[e.g.,][]{2008gady.book.....B}. Note that this prior does not preclude
 successful modelling of mergers or substructure unless the total projected mass
@@
 in regions of the mass map where the data are particularly constraining (for
-example near the images). We will apply \Glass\ to a host of strong lensing
+example near the images). We will apply \Glass{} to a host of strong lensing
 clusters in forthcoming work, where we will explicitly test the prior on mock
@@
 \subsection{Raytracing}\label{Raytracing}
-\Glass\ can also determine the position of images and time delays from
+\Glass{} can also determine the position of images and time delays from
 particle-based simulation output given a source position $\vec\beta$. This is
@@
 \subsection{Removing models with extra images}\label{sec:glassextraimages} 
-While linear constraints are applied in \Glass\ by the nature of the sampling
+While linear constraints are applied in \Glass{} by the nature of the sampling
 algorithm, non-linear constraints must be applied in post-processing. Models
@@
 first proposed and explored by \citet{2006MNRAS.367.1209L} and found to be
-extremely powerful. We find that our gradient prior in \Glass\ (see
+extremely powerful. We find that our gradient prior in \Glass{} (see
 \secref{sec:discrete}), performs much of the same function as
@@
 $\Sigma(R)$ assuming spherical symmetry
-\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}: 
+\citep[e.g.,][]{2008gady.book.....B,2008MNRAS.390.1647B}: 
 %
@@
 We now present a study of four mock galaxies with known analytic forms. These
-are used to verify that \Glass\ is able to correctly recover the mass profile,
+are used to verify that \Glass{} is able to correctly recover the mass profile,
 and -- more importantly -- to determine what type and quality of data best
@@
 
-For each of the four galaxies, we used the raytracing feature of \Glass\
+For each of the four galaxies, we used the raytracing feature of \Glass{}
 described in \secref{Raytracing} to construct 6 basic lensing morphologies:
@@
 the sight line to the bright lensing galaxy; in clusters, however, such images
-have been seen -- e.g. \citealt{2005PASJ...57L...7I}). We assumed for all our
+have been seen -- e.g., \citealt{2005PASJ...57L...7I}). We assumed for all our
 tests that the lensing mass was radially symmetric (Prior vi). For our mock
@@
 allow a broad range of external shear in our lens model reconstructions.
-\Glass\ correctly returns a small or zero shear in all cases. It is possible
+\Glass{} correctly returns a small or zero shear in all cases. It is possible
 that more complex shear fields present in real lensing galaxies could introduce
 further degeneracies beyond those discussed here. However, any such shear field
-can, at least in principle, be constrained by data (e.g. combining weak lensing
+can, at least in principle, be constrained by data (e.g., combining weak lensing
 constraints, or assuming that the shear field correlates with visible galaxies
--- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).
+-- e.g., \citealt{2009A&A...500..681M,2011ApJ...726...84W}).
 
@@
 \figref{reconstruction}, we obtain a better recovery than in the bottom row for
-{\it precisely the same data quality}. This occurs because the \Glass\ prior
+{\it precisely the same data quality}. This occurs because the \Glass{} prior
 favours steeper models consistent with \mockBC, but not \mockAA. It is the
-\Glass\ prior, rather than the data that is driving the good recovery for
+\Glass{} prior, rather than the data that is driving the good recovery for
 \mockBC\ in this example. This emphasises the importance of using a wide range
@@
 The vertical lines mark the radial positions of the images. The higher
-resolution feature of \Glass\ has been used on the central pixel allowing the
+resolution feature of \Glass{} has been used on the central pixel allowing the
 steep profile to be captured.
@@
 little improvement as the data improves beyond a single quad. This occurs
-because the \Glass\ sample prior in the absence of data favours steep models
+because the \Glass{} sample prior in the absence of data favours steep models
 like \mockBC\ over shallower models like \mockAA\ (see also
@@
 extra to the strong lensing data. We took the stellar mass directly from the
-generated galaxies and projected the particles onto the pixels. \Glass\ also
+generated galaxies and projected the particles onto the pixels. \Glass{} also
 offers an option to interpolate any map of stellar mass (e.g., from an
-observation) onto the pixels. The linear constraint is added to \Glass\ by
+observation) onto the pixels. The linear constraint is added to \Glass{} by
 writing $\kappa_n = \kappa_{dm,n} + \kappa_{s,n}$ as the sum of the dark matter
@@
 
-As outlined in \secref{sec:glass}, \Glass\ can also run post processing
+As outlined in \secref{sec:glass}, \Glass{} can also run post processing
 routines on the model ensemble which can be used to apply non-linear
 constraints. As an example, we consider here constraints from stellar
-kinematics. The models in the \Glass\ ensemble are processed as described in
+kinematics. The models in the \Glass{} ensemble are processed as described in
 \S\ref{sec:glasskinematics}.  To illustrate the power of stellar kinematic
@@
 within $\sim$ the half light radius $M_{1/2}$
-\citep[e.g.][]{2009ApJ...704.1274W,2010MNRAS.406.1220W}. The mass {\it
+\citep[e.g.,][]{2009ApJ...704.1274W,2010MNRAS.406.1220W}. The mass {\it
 profile}, however, depends on $\beta$ which is poorly constrained by these
@@
 
-We have introduced a new gravitational lens modelling tool -- Glass\ -- and
+We have introduced a new gravitational lens modelling tool -- Glass{} -- and
 used it to test the recovery of the mass profile and shape of mock strong
@@
 constrain cosmological models. We will study this, and present the first
-results from \Glass\ applied to real data, in forthcoming papers.
+results from \Glass{} applied to real data, in forthcoming papers.
 
@@
 particle distributions for the mock galaxies, and the anonymous referee for
-many usual suggestions which has improved the manuscript. JIR would like to
+many useful suggestions which has improved the manuscript. JIR would like to
 acknowledge support from SNF grant PP00P2\_128540/1.

### 2014-08-29 limits/ms.tex
Further fixes.

@@
     combating the non-uniqueness of models.  Such ensembles are possible in
-    parametric models \citep[e.g.,][]{1999AJ....118...14B,2010Sci...329..924J},
-    and more recently with the Hubble Frontier Fields initiative
-    \citep[e.g.,][]{}, but are more common in
-    free-form models, where -- since such models are deliberately
+    parametric models \citep[e.g.,][]{1999AJ....118...14B,2010Sci...329..924J,
+    2014MNRAS.444..268R,2014arXiv1405.0222J,2014arXiv1405.0011C}, but are more
+    common in free-form models, where -- since such models are deliberately
     under-constrained -- they become vital
@@
 clusters \citep{2007ApJ...663...29S}. Prior (ii) is arguably a physical prior
-since a negative azimuthally averaged density slope would be unstable
+since a positive slope in the azimuthally averaged density profile would be unstable
 \citep[e.g.,][]{2008gady.book.....B}. Note that this prior does not preclude

### 2014-09-16 shapes/paper.tex
Changed minor detail in skeleton draft
Updated some figures in the paper
Justin changes

@@
 % Some definitions of things I always use here:
-\newcommand\bcite[1]{\citeauthor{#1} \citeyear{#1}}
+\def\ltsima{$\; \buildrel < \over \sim \;$}
+\def\simlt{\lower.5ex\hbox{\ltsima}}   
+\def\gtsima{$\; \buildrel > \over \sim \;$}
+\def\simgt{\lower.5ex\hbox{\gtsima}}
 
-\title[Alignment of Light and Mass in Lensing Galaxies]{Alignment of Light and Mass in Lensing Galaxies}
+%Code definition:
+\def\Glass{{\sc Glass}}
+\def\PixeLens{{\sc PixeLens}}
+
+\title[Light versus Dark in Strong Lensing Galaxies]{Light versus Dark in Strong  Lensing Galaxies: Dark matter halos are rounder than their stars}
 
@@
 \begin{abstract}
+We measure the shape and alignment of stars and dark matter in 11 strong lensing galaxies with good quality data.
+We find that in all cases the dark matter halos are more elliptical than the light distribution over the range $R_e < R < 5R_e$.
+As we average over larger radii, the lenses become increasingly elliptical both in their dark matter and stars, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$ (where $s$ is the ratio of the largest to smallest eigenvalue of the 2D moment of inertia tensor).
+Three systems have very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment between light and dark.
+One of these -- B1608 -- is a known merging pair; we suggest that the other two (B0712 and B2016) may also be recent post-merger systems.
+Galaxies with high dark matter ellipticity and weak external shear show very strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be very highly misaligned.
+This is reassuring since isolated misaligned galaxies are expected to be unstable.
+
+Our results provide a new constraint on galaxy formation models that must explain the origin of very round dark matter halos (not expected in pure dark matter only simulations), and highly misaligned systems.
+Such misalignments also present a new challenge for alternative gravity theories in which the light and dark must necessarily be highly correlated.
 \end{abstract}
@@
 \section{Introduction}\label{sec:introduction}
-\textbf{Content:}
-\begin{itemize}
-\item Understand galaxy structure
-\item Relevant to e.g. weak lensing (Intrinsic alignments) and alternative gravity theories
-\item Strong lensing reacts purely due to total mass distribution $\rightarrow$ Can disentangle light and mass
-\item Free-form modelling technique, less model bias
-\end{itemize}
+
+The ellipticity and shape of stars relative to their host dark matter halo encodes information both about our cosmological model ($\Lambda$CDM) and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
+`Dark-matter-only' (DMO) simulations in $\Lambda$CDM predict dark matter halos that are triaxial \citep{1991ApJ...378..496D,1992ApJ...399..405W,1996ApJ...462..563N,2002ApJ...574..538J}, with mean `shape parameter' $\langle q \rangle = (b+c)/2a \sim 0.8$ (where $a > b > c$ are the long, intermediate and short axes of the figure; \citealt{2007MNRAS.378...55M}).
+This corresponds to a typically {\it prolate} halo.
+However, including `baryons' (stars and gas) in the models produces halos that are significantly rounder and -- at least for disc galaxies -- well-aligned with the light distribution \citep{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}.
+Halo shapes and alignments also constrain alternative gravity models \citep{2001MNRAS.327..552M,2004ApJ...610L..97H,2005MNRAS.361..971R,2012PhRvD..86h3507F,2013MNRAS.434.2971D}.
+If the visible light is the only source of gravity in a galaxy, then we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can, at least in principle, be broken.
+
+Strong lensing provides a unique probe of the alignment and shape of the total mass distribution in galaxies \citep[e.g.][]{1986ApJ...310..568B,1992grle.book.....S,1998ApJ...509..561K,2000ApJ...543..131K,2006ApJ...649..599K,2007AJ....134..668A,2008MNRAS.383..857F,2010ApJ...724..511A,2012MNRAS.424..104L}.
+For `red and dead' ellipticals that are largely devoid of gas, their baryonic content can be mapped through stellar population synthesis modelling of their light distribution \citep[e.g.][]{2005ApJ...623L...5F,2006ApJ...640..662T,2008MNRAS.383..857F}.
+This opens up the possibility of directly comparing the light and mass in strong lensing systems \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
+Previous work in the literature has found that the light and mass are well-aligned (though a mis-match of up to 10$^\circ$ is not uncommon; e.g.
+\citealt{2012A&A...538A..99S}).
+However, results on the ellipticity of light and mass agree less well, with \citet{2012A&A...538A..99S} finding a strong correlation and \citet{1998ApJ...509..561K} and \citet{2008MNRAS.383..857F} finding none.
+It it difficult, however, to compare the results between these different studies because they use different lens modelling techniques; different definitions of ellipticity; and different radii over which the shapes and alignments are probed.
+Furthermore, none to date have applied their methodology to mock data to determine the robustness of the results.
+
+Weak lensing can also be used to probe the shape and alignment between light and dark, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
+\citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
+They found that dark matter halos appear to be rounder then their light distributions, with some weak evidence for alignment.
+Both measurements are challenging, however, and more recent data appear to be at odds with this early work, favouring dark matter halos that are more elliptical than their stars \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
+
+Recently, we introduced a new non-parametric lens tool, \Glass\  \citep{2014arXiv1401.7990C}.
+Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass dominates the potential over the region of the images.
+In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
+We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time.
+This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter.
+Since the stars often dominate the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution.
+Our comparison between light and dark is made possible by the fact that \Glass\ uses the light distribution as a prior on the mass map, ensuring that the dark matter mass is always positive.
+
+This paper is organised as follows.
+In \S\ref{sec:glass}, we briefly review the \Glass\ code.
+In \S\ref{sec:data}, we present our data compilation with references.
+In \S\ref{sec:results}, we present our results.
+Finally, in \S\ref{sec:conclusions} we discuss the implications of these results and we present our main conclusions.
+
+\section{\Glass: A non-parametric lens tool}\label{sec:glass}
+
+\Glass\ (Gravitational Lensing AnalysiS Software) is a new `non-parametric' lens modelling framework.
+(Non-parametric here simply means that we deliberately use many more parameters than data constraints such that our system of equations is under-constrained.) \Glass\ shares some aspects
+with an earlier code \PixeLens\ \citep{Saha2004,2008ApJ...679...17C}. However,
+\Glass\ -- which contains all new code written from the ground up --
+significantly improves upon \PixeLens\ in several key ways:
+
+\begin{enumerate}
+\item At the heart of \Glass\ is a new uniform sampling algorithm for high
+    dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large
+    ensembles of $>10,000$ models to be efficiently generated. 
+\item \Glass\ provides a modular framework that allows new priors to be added
+    and modified easily.
+\item The basis functions approximating a model can be easily changed (in this
+    paper, we assume pixels as in \PixeLens). 
+\item With so many models in the final ensemble, we can afford to apply
+    non-linear constraints (for example stellar kinematic data; or the removal of
+    models with spurious extra images) to accept/reject models in a post-processing
+    step.
+\item The central region of the mass map can have a higher resolution to more
+    efficiently capture steep models.
+\item Stellar density can be used as an additional constraint on the models. 
+\item Point or extended mass objects can be placed in the field.
+\end{enumerate}
+
+\Glass\ is described in detail in the code paper: \citet{2014arXiv1401.7990C}.
+Here, we simple list the default priors we use to model each lens.
+Where the priors differ from these defaults for any given lens, this is spelled out in data Table \ref{tab:lensmodelling}:
+
+\begin{enumerate}
+
+\item {\bf JR. CLAUDIO TO ADD PRIORS HERE.}
+
+\end{enumerate}
 
 \section{Data}\label{sec:data}
+
+{\bf JR. CLAUDIO TO ADD DATA HERE.}
+
 \textbf{Content:}
@@
 \item Describe data set (why this data set, special features of galaxies (environment: y/n/unknonwn, elliptical/disk))
+
+\item {\bf JR. Claudio to add this bit?} 
 \end{itemize}
@@
   \begin{center}
-    \begin{tabular}
-      ...
+    \begin{tabular}{ll}
+       blah & blah 
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}
-      ...
+    \begin{tabular}{ll}
+    blah & blah 
     \end{tabular}
@@
 
-\section{Method}\label{sec:method}
-\textbf{Content:}
-\begin{itemize}
-\item Describe GLASS
-\item Describe shape measure and link it with Coles, Read and Saha 2014
-\end{itemize}
+\section{Results}\label{sec:results}
 
-\section{Results}\label{sec:results}
+{\bf JR. CLAUDIO OR JUSTIN TO WRITE RESULTS SECTION?} 
 \textbf{Content:}
@@
 \item 1. Dark matter halos seem quite round, stars not necessarily
-\item 2. Dark matter halos are consistently more elliptical than stars
-\item 3. Rather elliptical dark matter halos are more aligned, otherwise not really a clear trend
-\item 4. There does not seem to be a trend of lenses being misaligned because of shear
+\item 2. Both DM and stars more elliptical with increasing radius 
+\item 3. DM halos with weak shear are aligned (apart from spherical systems that don't count); strong shear systems can be highly misaligned.
+\item 4. No sensitivity to shear prior. Only one lens B2045 requires a shear prior to avoid spurious extra images; doesn't affect the shape measure though. 
+\item 5. Merger systems stand out. 
 \end{itemize}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
+  \caption[width=.65\linewidth]{}
+  \label{fig:wedges}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=.65\linewidth]{Figures/AllLenses21.pdf}
+  \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
   \caption[width=.65\linewidth]{}
+  \label{fig:wedgesall}
+\end{figure*}
+
+\section{Conclusion}\label{sec:conclusions}
+
+{\bf JR. JUSTIN TO WRITE DISCUSSION/CONCLUSIONS ONCE FINAL PLOTS ARE FINISHED.}
+
+\section{Acknowledgements}\label{sec:acknowledgements}
+We would like to thank Dominik Leier for useful discussions. JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+
+\bibliographystyle{mn2e}
+\bibliography{paper}
+
+\appendix
+\section{Reconstructed Lenses}\label{sec:reconstructions}
+
+In this appendix, we show the results of our lens modelling for each individual lens (Figures \ref{fig:lensreconstruction1}, \ref{fig:lensreconstruction2}, and \ref{fig:lensreconstruction3}).
+The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence interval of these for the dark matter map.
+Figure \ref{fig:wedges} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $s$), and the angle between the dark matter and stellar major axes.
+Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=.8\linewidth]{Figures/AllLenses31.pdf}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens.
+The panels show, from left to right: the arrival time surface (the images are marked by the green circles); the surface mass density of the dark matter; and the surface mass density of the stars.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence interval of these for the dark matter map.}
   \label{fig:lensreconstruction1}
@@
   \centering
-  \includegraphics[width=.65\linewidth]{Figures/AllLenses22.pdf}
-  \caption[width=.65\linewidth]{}
+  \includegraphics[width=.8\linewidth]{Figures/AllLenses32.pdf}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:ensreconstruction1}.}
   \label{fig:lensreconstruction2}
@@
   \centering
-  \includegraphics[width=.65\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=.65\linewidth]{}
-  \label{fig:wedges}
+  \includegraphics[width=.8\linewidth]{Figures/AllLenses33.pdf}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:ensreconstruction1}.}
+  \label{fig:lensreconstruction3}
 \end{figure*}
 
-\section{Conclusion}\label{sec:conclusion}
-...
-
-\section{Acknowledgements}\label{sec:acknowledgements}
-Acknowledge Dominik Leier, ...
-
-JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
-
-\bibliographystyle{mn2e}
-\bibliography{paper}
-
-%\clearpage
-% \appendix
-% \section{Reconstructed Lenses}\label{sec:reconstructions}
-
 \end{document}

### 2014-12-01 shapes/paper.tex
updated Figures, added tables, section with priors, copied data section from thesis

@@
 \begin{enumerate} 
+\item Observational priors (redshifts, image positions relative to lens position).
+\item Image parity is enforced.
+\item Reconstructed stellar mass map.
+\item Local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
+\item Fixed cosmology: $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
+\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
+\end{enumerate}
 
-\item {\bf JR. CLAUDIO TO ADD PRIORS HERE.}
+In case of more information, the following priors can be turned on:
 
+\begin{enumerate}
+\item[(vii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
+\item[(viii)] External point masses to model satellite galaxies outside but close to the Einstein radius.
+\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$ in case there is reason to assume the surface mass profile to be symmetric (3+1 quad configurations and the double \textit{Q0957}).
 \end{enumerate}
@@
 
+\textit{Q0047-2808} (hereafter \textit{Q0047} or \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
+\cite{2011ApJ...726...84W} find a group of 9 members all of which they spectroscopically confirm.
+
+\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
+\cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens.
+Due to the proximity of this satellite, we include it as a point mass in our analysis.
+
+\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}.
+Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}.
+There is also a group of 10 galaxies at a lower redshift.
+
+\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}.
+It has measured time delays \citep{2002ApJ...572L..11H}.
+It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
+This cluster seems to be rather complex and especially it is not spherical.
+Possibly it is not dynamically relaxed, although X-ray emission can be detected.
+Analysis of this emission yields a temperature of 2.3 keV.
+There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
+
+\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g.
+\cite{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}).
+Due to the large image separation, large physical scales are probed.
+As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
+These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
+The lens has a measured time delay, e.g.
+\citep{2012A&A...540A.132S}.
+They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level.
+They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
+We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
+
+\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}.
+It has measured time delays.
+We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ significantly from traditional values by e.g.
+\cite{1997ApJ...489...21B}.
+\cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W} analyzed the environment of the lens thouroughly.
+It is part of a small group of 13 members.
+\cite{2004ApJ...610..686G} detect also X-ray emission from the corresponding group, which yields a temperature of 0.8 keV.
+
+\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}.
+Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to be trusted too much as they deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}.
+An accurate measurement of the time delays would require time delay measurements on the scale of hours.
+\cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies.
+Using newer data, \cite{2011ApJ...726...84W} find an additional member.
+\cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
+
+\textit{B1608+656} (hereafter \textit{1608} or \textit{1608}) consists of two merging galaxies.
+The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
+The system has measured time delays \citep{2002ApJ...581..823F}.
+The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}.
+They find a group with 8 resp.
+9 members if the merging galaxies are counted as 2.
+No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
+Along the line of sight seem to be four other groups.
+
+\textit{MG2016+112} (hereafter \textit{2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
+It is the farthest lens we consider in this sample.
+It lies in a cluster which consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
+The clusters shows a high density of galaxies close to the lens in a south-east direction.
+
+\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
+\cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high.
+As the source redshift is rather low, a large lens mass is needed.
+\cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
+To the west of the lens, \cite{1999AJ....117..658F} find that a group at a similar redshift as the lens.
+\cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy.
+As the measurements are not conclusive, we chose to treat the lens as an isolated object.
+
+\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
+With only a redshift of $z=0.04$, it is the closest lens of the sample.
+Due to the low redshift, the probed physical scales are quite small.
+No further inquiries into the environment were made.
+
+Further information about the sample can be found in \cite{leier11phd}, \cite{2011ApJ...740...97L}, and \cite{2012A&A...538A..99S}.
+
 \begin{table*}
   \begin{center}
-    \begin{tabular}{ll}
-       blah & blah 
+    \begin{tabular}{l r r r r l}
+      Lens    & \multicolumn{1}{c}{$z_{L}$} & \multicolumn{1}{c}{$z_{S}$} & \multicolumn{1}{c}{$\Delta\theta$ [kpc]} & \multicolumn{1}{c}{$R_{L}$/$R_{e}$} & Environment \\ \hline
+      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9) \\
+      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... \\
+      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... \\
+      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C \\
+      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C \\
+      1115 & 0.310 & 1.72 & 10.76 & $2.94\pm0.06$ & G(13) \\
+      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17) \\
+      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & !CHECK! \\
+      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69) \\
+      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & !SEE TEXT! \\
+      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... \\
     \end{tabular}
-    \caption[width=\linewidth]{Table with lens properties}
+    \caption[width=\linewidth]{Table with lens properties \citep[see][]{2011ApJ...740...97L}. References in Section~\ref{sec:data} \texbf{expand}}
     \label{tab:lensproperties}
@@
   \begin{center}
-    \begin{tabular}{ll}
-    blah & blah 
+    \begin{tabular}{l r r r r l l}
+      Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
+      0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & None \\
+           & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
+      0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & None \\
+           & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
+      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & None \\
+           & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
+      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & None \\
+           & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
+      0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
+           & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
+      1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & None \\
+           & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
+      1422 & 1.079 & 0.357 & 0.742 & -0.205 & ... & Symm \\
+           & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
+      1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & None \\
+           & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
+      2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & None \\
+           & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
+      2045 & 1.121 & 1.409 & 1.255 & -0.507 & ... & $\gamma(0.1)$, Symm \\
+           & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
+      2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & None \\
+              & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
     \end{tabular}
-    \caption[width=\linewidth]{Table with lens properties relevant for modelling (point masses, positions, time delays)}
+    \caption[width=\linewidth]{Table with lens properties relevant for modelling (positions, time delays) \newline $^{a}$ Images A and B are a pair, C and D the other \texbf{expand}}
     \label{tab:lensmodelling}

### 2014-12-02 shapes/paper.tex

@@
 \end{enumerate}
+
+\subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
+
+{\bf JR. WE NEED TO DEFINE OUR SHAPE PARAMETER AND ANALYSIS METHOD HERE.} 
+{\bf JR. WE NEED TO ALSO DEFINE $R_e$ HERE AND EXPLAIN THAT WE AVERAGE SHAPE OVER 1-5$R_e$}
 
@@
 
-{\bf JR. JUSTIN TO WRITE DISCUSSION/CONCLUSIONS ONCE FINAL PLOTS ARE FINISHED.}
+We have measured the shape and alignment of stars and dark matter in 11 strong lensing galaxies using a new non-parametric lens tool, \Glass.
+We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential, since these have data quality good enough to determine the projected shape of their dark matter halos \citep{2014arXiv1401.7990C}.
+We measured the shape and alignment using the eigenvalues $\lambda$ and vectors of the 2D moment of inertia tensor of the stars and dark matter, defining a {\it shape parameter} $s = \lambda_{\rm max}/\lambda_{\rm min}$ (\S\ref{sec:shapemethod}).
+We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+
+Our key results are as follows:
+
+\begin{itemize}
+\item We found that in all cases the dark matter halos are more elliptical than the light distribution over the range $R_e < R < 5R_e$.
+As we average over larger radii, the lenses become increasingly elliptical both in their dark matter and stars, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$.
+
+\item Three systems have very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment between light and dark.
+One of these -- B1608 -- is a known merging pair; we suggest that the other two (B0712 and B2016) may also be recent post-merger systems.
+
+\item Galaxies with high dark matter ellipticity and weak external shear show very strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be very highly misaligned.
+This is reassuring since isolated misaligned galaxies are expected to be unstable.
+\end{itemize}
+
+Our results provide a new constraint on galaxy formation models that must explain the origin of very round dark matter halos (not expected in pure dark matter only simulations), and highly misaligned systems.
+Such misalignments also present a new challenge for alternative gravity theories in which the light and dark must necessarily be highly correlated.
 

### 2014-12-02 shapes/paper.tex
A few changes.

@@
 $^{3}$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
-$^{4}$Department of Biology and Health, Versailles Saint-Quentin-en-Yvelines University, France
+$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France
 }
@@
 \begin{abstract}
-We measure the shape and alignment of stars and dark matter in 11 strong lensing galaxies with good quality data.
-We find that in all cases the dark matter halos are more elliptical than the light distribution over the range $R_e < R < 5R_e$.
-As we average over larger radii, the lenses become increasingly elliptical both in their dark matter and stars, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$ (where $s$ is the ratio of the largest to smallest eigenvalue of the 2D moment of inertia tensor).
-Three systems have very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment between light and dark.
-One of these -- B1608 -- is a known merging pair; we suggest that the other two (B0712 and B2016) may also be recent post-merger systems.
-Galaxies with high dark matter ellipticity and weak external shear show very strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be very highly misaligned.
-This is reassuring since isolated misaligned galaxies are expected to be unstable.
+We measure the shape and alignment of stars and dark matter in 11 strong
+lensing galaxies and find that in all cases the dark matter halos are rounder
+than the light distribution over the range $R_e < R < 5R_e$.  Averaging over
+larger radii, the lenses become increasingly elliptical both in their dark
+matter and stellar components, as defined using the ratio $s$ of the largest to
+smallest eigenvalues of the 2D moment of inertia tensor of the projected
+lensing mass.  While dark matter halos are never more elliptical than $s_{dm} =
+1.15$, their stars can extend to $s_* > 1.4$ Three systems, in particular, have
+very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment
+between light and dark. One of these -- B1608 -- is a known merging pair; we
+suggest that the other two (B0712 and B2016) may also be recent post-merger
+systems.  Galaxies with high dark matter ellipticity and weak external shear
+show very strong alignment between light and dark; those with strong shear
+($\gamma \simgt 0.1$) can be very highly misaligned. This is reassuring since
+isolated misaligned galaxies are expected to be unstable.
 
-Our results provide a new constraint on galaxy formation models that must explain the origin of very round dark matter halos (not expected in pure dark matter only simulations), and highly misaligned systems.
-Such misalignments also present a new challenge for alternative gravity theories in which the light and dark must necessarily be highly correlated.
+Our results provide a new constraint on galaxy formation models that must
+explain the origin of very round dark matter halos and highly misaligned
+systems. Such misalignments also present a new challenge for alternative
+gravity theories in which the light and dark must necessarily be highly
+correlated.
+
 \end{abstract}
@@
 
-\Glass\ (Gravitational Lensing AnalysiS Software) is a new `non-parametric' lens modelling framework.
-(Non-parametric here simply means that we deliberately use many more parameters than data constraints such that our system of equations is under-constrained.) \Glass\ shares some aspects
-with an earlier code \PixeLens\ \citep{Saha2004,2008ApJ...679...17C}. However,
-\Glass\ -- which contains all new code written from the ground up --
-significantly improves upon \PixeLens\ in several key ways:
+\Glass{} is a new `non-parametric' gravitationl lens modelling framework
+\citep{2014arXiv1401.7990C} that is capable of generating a distribution of
+mass models given a set of basic assumptions, or priors.  In this context,
+non-parametric means that  many more parameters than data constraints are used
+such that system of equations describing the lensing mass distribution is
+under-constrained.  \Glass{} shares some aspects with an earlier code
+\PixeLens{} \citep{Saha2004,2008ApJ...679...17C}, but has a completely
+different code base. It key improvements upon \PixeLens{} which are relevant
+for this paper include:
 
 \begin{enumerate}
-\item At the heart of \Glass\ is a new uniform sampling algorithm for high
+\item A new uniform sampling algorithm for high
     dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large
     ensembles of $>10,000$ models to be efficiently generated. 
-\item \Glass\ provides a modular framework that allows new priors to be added
-    and modified easily.
-\item The basis functions approximating a model can be easily changed (in this
-    paper, we assume pixels as in \PixeLens). 
+%\item \Glass\ provides a modular framework that allows new priors to be added
+%    and modified easily.
+%\item The basis functions approximating a model can be easily changed (in this
+%    paper, we assume pixels as in \PixeLens). 
 \item With so many models in the final ensemble, we can afford to apply
@@
     efficiently capture steep models.
-\item Stellar density can be used as an additional constraint on the models. 
-\item Point or extended mass objects can be placed in the field.
+\item Stellar density can be used as an additional lower-bound constraint on the models. 
+%\item Point or extended mass objects can be placed in the field.
 \end{enumerate}
 
-\Glass\ is described in detail in the code paper: \citet{2014arXiv1401.7990C}.
-Here, we simple list the default priors we use to model each lens.
-Where the priors differ from these defaults for any given lens, this is spelled out in data Table \ref{tab:lensmodelling}:
+%\Glass{} is described in detail in the code paper: \citet{2014arXiv1401.7990C}.
+In this paper, the default priors used to model each lens are listed below.  Table
+\ref{tab:lensmodelling} identifies lenses for which we have modified these defaults.
+For each lens we assume:
 
@@
 \item Image parity is enforced.
-\item Reconstructed stellar mass map.
-\item Local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
-\item Fixed cosmology: $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
+\item A reconstructed stellar mass map.
+\item The local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
+\item The fixed cosmology $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
 \item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
@@
 
-In case of more information, the following priors can be turned on:
+In cases where more information is available, the following priors are also used:
 
@@
 \item[(vii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
-\item[(viii)] External point masses to model satellite galaxies outside but close to the Einstein radius.
-\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$ in case there is reason to assume the surface mass profile to be symmetric (3+1 quad configurations and the double \textit{Q0957}).
+
+\item[(viii)] External point masses to model satellite galaxies outside but
+close to the Einstein radius.
+
+\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$ where 
+the surface mass profile can be assumed to be symmetric (3+1 quad
+configurations and the double \textit{Q0957}).
+
 \end{enumerate}
@@
     \end{tabular}
-    \caption[width=\linewidth]{Table with lens properties \citep[see][]{2011ApJ...740...97L}. References in Section~\ref{sec:data} \texbf{expand}}
+    \caption[width=\linewidth]{Table with lens properties \citep[see][]{2011ApJ...740...97L}. References in Section~\ref{sec:data} \textbf{expand}}
     \label{tab:lensproperties}
@@
       Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
-      0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & None \\
+      0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & \\
            & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
-      0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & None \\
+      0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & \\
            & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
-      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & None \\
+      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
            & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
-      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & None \\
+      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
            & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
@@
            & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
-      1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & None \\
+      1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
            & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
@@
            & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
-      1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & None \\
+      1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & \\
            & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
-      2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & None \\
+      2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & \\
            & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
@@
            & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
-      2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & None \\
+      2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & \\
               & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
     \end{tabular}
-    \caption[width=\linewidth]{Table with lens properties relevant for modelling (positions, time delays) \newline $^{a}$ Images A and B are a pair, C and D the other \texbf{expand}}
+    \caption[width=\linewidth]{Table with lens properties relevant for modelling (positions, time delays) \newline $^{a}$ Images A and B are a pair, C and D the other \textbf{expand}}
     \label{tab:lensmodelling}

### 2014-12-15 shapes/paper.tex
Added captions, fixed typos, reworked data section

@@
 However, results on the ellipticity of light and mass agree less well, with \citet{2012A&A...538A..99S} finding a strong correlation and \citet{1998ApJ...509..561K} and \citet{2008MNRAS.383..857F} finding none.
-It it difficult, however, to compare the results between these different studies because they use different lens modelling techniques; different definitions of ellipticity; and different radii over which the shapes and alignments are probed.
+It is difficult, however, to compare the results between these different studies because they use different lens modelling techniques; different definitions of ellipticity; and different radii over which the shapes and alignments are probed.
 Furthermore, none to date have applied their methodology to mock data to determine the robustness of the results.
@@
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass dominates the potential over the region of the images.
-In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
+{\bf CB.
+i) is the case for all the lenses, ii) however only for a minority of the sample.
+This sentence creates therefore some tension that is not addressed however (I don't know whether we should rephrase it or add another sentence).} In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
 We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time.
@@
 
-\Glass{} is a new `non-parametric' gravitationl lens modelling framework
+\Glass{} is a new `non-parametric' gravitational lens modelling framework
 \citep{2014arXiv1401.7990C} that is capable of generating a distribution of
@@
 under-constrained.  \Glass{} shares some aspects with an earlier code
-\PixeLens{} \citep{Saha2004,2008ApJ...679...17C}, but has a completely
-different code base. It key improvements upon \PixeLens{} which are relevant
+\PixeLens{} \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely
+different code base. Its key improvements upon \PixeLens{} which are relevant
 for this paper include:
@@
 
-\item[(viii)] External point masses to model satellite galaxies outside but
+% \item[(viii)] External point masses to model satellite galaxies outside but
 close to the Einstein radius.
 
-\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$ where 
+\item[(viii)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$ where 
 the surface mass profile can be assumed to be symmetric (3+1 quad
@@
 {\bf JR. WE NEED TO ALSO DEFINE $R_e$ HERE AND EXPLAIN THAT WE AVERAGE SHAPE OVER 1-5$R_e$} 
+{\bf CB. I will write this.}
 
@@
 
-{\bf JR. CLAUDIO TO ADD DATA HERE.}
-
-\textbf{Content:}
-\begin{itemize}
-\item Describe data set (why this data set, special features of galaxies (environment: y/n/unknonwn, elliptical/disk))
-
-\item {\bf JR. Claudio to add this bit?} 
-\end{itemize}
+{\bf CB. Do we need to add a bit describing the stellar population synthesis modelling? Can maybe Prasenjit write this?}
 
 \textit{Q0047-2808} (hereafter \textit{Q0047} or \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
-\cite{2011ApJ...726...84W} find a group of 9 members all of which they spectroscopically confirm.
+\cite{2011ApJ...726...84W} find a group of 9 members all of which are spectroscopically confirmed.
 
@@
 \cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens.
-Due to the proximity of this satellite, we include it as a point mass in our analysis.
+\citep{2011MNRAS.413L..86C} however conclude that it is more likely a foreground object.
 
 \textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}.
-Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}.
+%Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}.
 There is also a group of 10 galaxies at a lower redshift.
@@
 It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
-This cluster seems to be rather complex and especially it is not spherical.
+X-ray emission can be detected and an analysis of which yields a temperature of 2.3 keV.
+There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
+%This cluster seems to be rather complex and especially it is not spherical.
 Possibly it is not dynamically relaxed, although X-ray emission can be detected.
-Analysis of this emission yields a temperature of 2.3 keV.
-There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
 
@@
 It has measured time delays.
-We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ significantly from traditional values by e.g.
+We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ from previously found values by e.g.
 \cite{1997ApJ...489...21B}.
@@
 \textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}.
-Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they are probably not to be trusted too much as they deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}.
-An accurate measurement of the time delays would require time delay measurements on the scale of hours.
+Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}.
+We choose therefore not to include them in the analysis.
 \cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies.
@@
 The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}.
-They find a group with 8 resp.
-9 members if the merging galaxies are counted as 2.
+They find a group with 8 (9 if merging galaxies are counted individually).
 No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
-Along the line of sight seem to be four other groups.
+The data seems to indicate four other groups along the line of sight.
 
@@
 \cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high.
-As the source redshift is rather low, a large lens mass is needed.
+As the source redshift is rather low, a large lens mass is required.
 \cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-To the west of the lens, \cite{1999AJ....117..658F} find that a group at a similar redshift as the lens.
+To the west of the lens, \cite{1999AJ....117..658F} find a group at a similar redshift as the lens.
 \cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy.
-As the measurements are not conclusive, we chose to treat the lens as an isolated object.
+As the measurements are inconclusive, we choose to not include this satellite.
 
@@
 With only a redshift of $z=0.04$, it is the closest lens of the sample.
-Due to the low redshift, the probed physical scales are quite small.
+Due to the low redshift, the probed physical scales are small.
 No further inquiries into the environment were made.
@@
       1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17) \\
-      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & !CHECK! \\
+      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8) \\
       2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69) \\
-      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & !SEE TEXT! \\
+      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... \\
       2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... \\
     \end{tabular}
-    \caption[width=\linewidth]{Table with lens properties \citep[see][]{2011ApJ...740...97L}. References in Section~\ref{sec:data} \textbf{expand}}
+    \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}.
+References can be found in \S\ref{sec:data}.}
     \label{tab:lensproperties}
@@
     \end{tabular}
-    \caption[width=\linewidth]{Table with lens properties relevant for modelling (positions, time delays) \newline $^{a}$ Images A and B are a pair, C and D the other \textbf{expand}}
+    \caption[width=\linewidth]{The lens properties relevant for modelling the lenses are listed (positions and time delay information).
+The images are ordered in terms of arrival time (image A has the shortest arrival time, image D the longest).
+\newline $^{a}$ The source lensed by 0957 has different component.
+Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
     \label{tab:lensmodelling}
@@
   \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=.65\linewidth]{}
+  \caption[width=.65\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$.
+The wedges display the alignment of the semi-major axes of the components.
+In case of alignment of the semi-major axes (Aligned), the wedges are vertical.
+In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
+The opening angle displays the error in the shape estimate of the dark matter halo.
+The lenses are additional color-coded in terms of the required external shear in modelling the lens.}
   \label{fig:wedges}
@@
   \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
-  \caption[width=.65\linewidth]{}
+  \caption[width=.65\linewidth]{Similar to Figure~\ref{fig:wedges}.
+In each of the subfigures however we only consider pixels within 1, 2, 3, 4, or 5 $R_e$.
+If a lens does not extend to these limiting radii, it is dropped from the analysis in this and subsequent subfigures.}
   \label{fig:wedgesall}
@@
 \begin{itemize}
-\item We found that in all cases the dark matter halos are more elliptical than the light distribution over the range $R_e < R < 5R_e$.
+\item We found that in all cases the dark matter halos are rounder than the light distribution over the range $R_e < R < 5R_e$.
 As we average over larger radii, the lenses become increasingly elliptical both in their dark matter and stars, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$.
@@
 
-\item Galaxies with high dark matter ellipticity and weak external shear show very strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be very highly misaligned.
+\item Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be highly misaligned.
 This is reassuring since isolated misaligned galaxies are expected to be unstable.

### 2014-12-15 shapes/paper.tex
added population-synthesis text

@@
 
-{\bf CB. Do we need to add a bit describing the stellar population synthesis modelling? Can maybe Prasenjit write this?}
+Stellar-mass maps are taken from \cite{2011ApJ...740...97L}.  In that
+work, the light of the galaxy images in all available HST bands was
+first fitted using using GALFIT \citep{2002AJ....124..266P}, and the
+resulting light maps were used to obtain stellar-mass maps using
+stellar population synthesis.  The latter assumed a
+\cite{2003PASP..115..763C} IMF and the stellar-population models of
+\cite{2003MNRAS.344.1000B}.  A more bottom-heavy IMF would change the
+mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the
+inferred shape of the stellar mass.
 

### 2014-12-15 shapes/paper.tex
added population-synthesis text

--- 2014-12-15 shapes/paper.tex
@@
 
-{\bf CB. Do we need to add a bit describing the stellar population synthesis modelling? Can maybe Prasenjit write this?}
+Stellar-mass maps are taken from \cite{2011ApJ...740...97L}.  In that
+work, the light of the galaxy images in all available HST bands was
+first fitted using using GALFIT \citep{2002AJ....124..266P}, and the
+resulting light maps were used to obtain stellar-mass maps using a
+synthesis of the stellar-population models of
+\cite{2003MNRAS.344.1000B}.  The population synthesis marginalised
+over the star-formation epoch and time scales and over the stellar
+metallicity.  The IMF was taken to be the log-normal form given by
+\cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the
+mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the
+inferred shape of the stellar mass.
 

### 2014-12-22 shapes/paper.tex
Added missing Sections, changed wedges Figures and generally worked on the paper

--- 2014-12-15 shapes/paper.tex
@@
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass dominates the potential over the region of the images.
-{\bf CB.
-i) is the case for all the lenses, ii) however only for a minority of the sample.
-This sentence creates therefore some tension that is not addressed however (I don't know whether we should rephrase it or add another sentence).} In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
+{\bf (CB.
+i) is the case for all the lenses except Q0957, ii) however is only the case for a minority of the sample.
+This sentence creates therefore some tension that is not addressed however (I don't know whether we should rephrase it or add another sentence))} In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
 We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time.
@@
 \citep{2014arXiv1401.7990C} that is capable of generating a distribution of
-mass models given a set of basic assumptions, or priors.  In this context,
+mass models given a set of basic assumptions, or priors.
+{\bf Hence, \Glass\ does not yield the most probable mass model.
+Rather, we can describe the distribution of all the allowed models.
+(CB: I'VE ADDED THIS SENTENCE AS I FELT SOMETHING LIKE THAT MIGHT BE NEEDED AT THIS POINT.
+IT PROBABLY NEEDS TO BE IMPROVED THOUGH)} In this context,
 non-parametric means that  many more parameters than data constraints are used
@@
 In this paper, the default priors used to model each lens are listed below.  Table
-\ref{tab:lensmodelling} identifies lenses for which we have modified these defaults.
+\ref{tab:lenspriors} identifies lenses for which we have modified these defaults.
 For each lens we assume:
@@
 \item Image parity is enforced.
-\item A reconstructed stellar mass map.
+\item A reconstructed stellar mass map as lower mass bounds in every pixel.
 \item The local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
@@
 \subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
+We employ the same shape definition as in \citep{2014arXiv1401.7990C}. The shape parameter $s$ is defined as the ratio of the two eigenvalues $\lambda_1$ and $\lambda_2$, i.e.
+\begin{equation}\label{eq:shapeestimate}
+    s \equiv \frac{\lambda_{1}}{\lambda_{2}}, \ \ \ \mathrm{where} \ \lambda_{1} \geq \lambda_{2},
+\end{equation}
+of the inertia tensor of a mass distribution $M(\boldsymbol{\theta})$
+\begin{equation}\label{eq:inertiatensor}
+    I = \begin{pmatrix} \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
+                        -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x} \end{pmatrix}.
+\end{equation}
+We use these estimators to quantify the shape of the stellar mass distribution and the dark matter distribution.
+We estimate the latter by reconstructing the total mass distribution with a lower mass prior from the stellar mass distribution and then subtracting the latter off.
+The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of the half-light radius $R_e$.
+$R_e$ is the Petrosian radius containing half of the flux of the total light distribution.
+As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
+The shape estimates do not necessarily need to be the same within different radii.
+E.g.
+there are effects as isophotal twist \citep[e.g.][and references therein]{1978ComAp...8...27B} causing differences in the shape estimates between the central and the outer parts of the system.
+{\bf (CB: THESE LAST SENTENCES PROBABLY NEED TO BE REPHRASED TOO)}
 
-{\bf JR. WE NEED TO DEFINE OUR SHAPE PARAMETER AND ANALYSIS METHOD HERE.} 
-{\bf JR. WE NEED TO ALSO DEFINE $R_e$ HERE AND EXPLAIN THAT WE AVERAGE SHAPE OVER 1-5$R_e$} 
-{\bf CB. I will write this.}
+Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image.
+Furthermore, we generate 10000 mass models for each system we consider and describe the distribution of all the individual estimates for the dark matter shapes.
+{\bf (CB: MAYBE NEEDS REPHRASING, SEE ABOVE)}
 
 \section{Data}\label{sec:data}
+Stellar-mass maps are taken from \citep{2011ApJ...740...97L}.
+In that work, the light of the galaxy images in all available HST bands was first fitted using using GALFIT \citep{2002AJ....124..266P}, and the resulting light maps were used to obtain stellar-mass maps using a synthesis of the stellar-population models of \citep{2003MNRAS.344.1000B}.
+The population synthesis marginalised over the star-formation epoch and time scales and over the stellar metallicity.
+The IMF was taken to be the log-normal form given by \citep{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the inferred shape of the stellar mass.
 
-{\bf CB. Do we need to add a bit describing the stellar population synthesis modelling? Can maybe Prasenjit write this?}
+As it is shown in \citep{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
+Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561} out of the sample presented in \citep{2011ApJ...740...97L}.
+Thus, the sample consists in total of 11 lenses.
+Each individual system is presented below.
 
-\textit{Q0047-2808} (hereafter \textit{Q0047} or \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
-\cite{2011ApJ...726...84W} find a group of 9 members all of which are spectroscopically confirmed.
+\textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
+It is part a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
 
 \textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
-\cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens.
-\citep{2011MNRAS.413L..86C} however conclude that it is more likely a foreground object.
+A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
+It however is more likely a foreground object \citep{2011MNRAS.413L..86C}.
 
 \textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}.
-%Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}.
-There is also a group of 10 galaxies at a lower redshift.
 
@@
 There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
-%This cluster seems to be rather complex and especially it is not spherical.
-Possibly it is not dynamically relaxed, although X-ray emission can be detected.
 
-\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g.
-\cite{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}).
+\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
 Due to the large image separation, large physical scales are probed.
@@
 These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
-The lens has a measured time delay, e.g.
-\citep{2012A&A...540A.132S}.
-They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level.
+The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
+They however also find a three-day lag between the g- and r-bands, a disagreement at the 2$\sigma$-level.
 They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
@@
 It has measured time delays.
-We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ from previously found values by e.g.
+In this work use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
 \cite{1997ApJ...489...21B}.
-\cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W} analyzed the environment of the lens thouroughly.
+The environment of the lens was analyzed thouroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
 It is part of a small group of 13 members.
-\cite{2004ApJ...610..686G} detect also X-ray emission from the corresponding group, which yields a temperature of 0.8 keV.
+Also X-ray emission was detected from the corresponding group, and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
 
 \textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}.
-Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}.
+Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}.
 We choose therefore not to include them in the analysis.
-\cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies.
-Using newer data, \cite{2011ApJ...726...84W} find an additional member.
+The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
+Using newer data, an additional member could be found \citep{2011ApJ...726...84W}.
 \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
 
-\textit{B1608+656} (hereafter \textit{1608} or \textit{1608}) consists of two merging galaxies.
+\textit{B1608+656} (hereafter \textit{1608}) consists of two merging galaxies.
 The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
 The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}.
-They find a group with 8 (9 if merging galaxies are counted individually).
+The environment has been analyzed and group with 8 (9 if merging galaxies are counted individually) was found \citep{2006ApJ...642...30F}.
 No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
@@
 \textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
-\cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high.
+It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, the velocity dispersion however seems too high.
 As the source redshift is rather low, a large lens mass is required.
 \cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-To the west of the lens, \cite{1999AJ....117..658F} find a group at a similar redshift as the lens.
-\cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy.
+To the west of the lens, a group was found at a similar redshift as the lens \citep{1999AJ....117..658F}.
+There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
 As the measurements are inconclusive, we choose to not include this satellite.
 
-\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
+\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}, the only non-early type lens in this sample.
 With only a redshift of $z=0.04$, it is the closest lens of the sample.
 Due to the low redshift, the probed physical scales are small.
+Therefore, the bulge component of the galaxy dominates the lens, what makes the stellar population synthesis modelling possible.
 No further inquiries into the environment were made.
+It is
 
-Further information about the sample can be found in \cite{leier11phd}, \cite{2011ApJ...740...97L}, and \cite{2012A&A...538A..99S}.
+Further information on the sample can be found in \citep{2011ApJ...740...97L,2012A&A...538A..99S}.
+The most important quantities of each system are given in Table~\ref{tab:lensproperties}.
+Due to the different angular separations of the images, different scales of the lens galaxies are probed.
 
-\begin{table*}
+\begin{table}
   \begin{center}
@@
       0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C \\
-      1115 & 0.310 & 1.72 & 10.76 & $2.94\pm0.06$ & G(13) \\
+      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13) \\
       1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17) \\
@@
     \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}.
-References can be found in \S\ref{sec:data}.}
+References can be found in \S\ref{sec:data}.
+The columns are from left to right, the lens redshift $z_L$, the redshift of the source $z_S$, the maximum angular separation between two images $\Delta\theta$, the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$, and information on the environment of the lens.
+C and G denote a known cluster resp.
+group environment.
+The number in the brackets is the number of confirmed members.}
     \label{tab:lensproperties}
   \end{center}
-\end{table*}
+\end{table}
 
-\begin{table*}
-  \begin{center}
-    \begin{tabular}{l r r r r l l}
-      Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
-      0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & \\
-           & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
-      0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & \\
-           & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
-      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
-           & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
-      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
-           & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
-      0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
-           & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
-      1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
-           & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
-      1422 & 1.079 & 0.357 & 0.742 & -0.205 & ... & Symm \\
-           & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
-      1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-           & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
-      2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & \\
-           & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
-      2045 & 1.121 & 1.409 & 1.255 & -0.507 & ... & $\gamma(0.1)$, Symm \\
-           & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
-      2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & \\
-              & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
-    \end{tabular}
-    \caption[width=\linewidth]{The lens properties relevant for modelling the lenses are listed (positions and time delay information).
+% \begin{table*}
+%   \begin{center}
+%     \begin{tabular}{l r r r r l l}
+%       Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
+%       0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & \\
+%            & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
+%       0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & \\
+%            & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
+%       0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
+%            & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
+%       0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
+%            & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
+%       0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
+%            & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
+%       1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
+%            & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
+%       1422 & 1.079 & 0.357 & 0.742 & -0.205 & ... & Symm \\
+%            & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
+%       1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & \\
+%            & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
+%       2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & \\
+%            & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
+%       2045 & 1.121 & 1.409 & 1.255 & -0.507 & ... & $\gamma(0.1)$, Symm \\
+%            & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
+%       2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & \\
+%               & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
+%     \end{tabular}
+%     \caption[width=\linewidth]{The lens properties relevant for modelling the lenses are listed (positions and time delay information).
 The images are ordered in terms of arrival time (image A has the shortest arrival time, image D the longest).
@@
 Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
-    \label{tab:lensmodelling}
+%     \label{tab:lensmodelling}
+%   \end{center}
+% \end{table*}
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l l l}
+      Lens & Time delays [days] & Additional priors \\ \hline
+      0047 & ... & ...\\
+      0414 & ... & ...\\
+      0712 & ... & ...\\
+      0712 & ... & ...\\
+      0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
+      1115 & $\Delta t_{BA}=12.0^{+2}_{-2}$ & ...\\
+           & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
+      1422 & ... & Symm \\
+      1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & ...\\
+           & $\Delta t_{CA}=36.0^{+1.5}_{-1.5}$ & \\
+           & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
+      2016 & ... & ...\\
+      2045 & ... & $\gamma(0.1)$, Symm \\
+      2237 & ... & ...\\
+    \end{tabular}
+    \caption[width=\linewidth]{Additional priors to the baseset described in \S\ref{sec:glass} are listed.
+$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$.
+The images are defined in Table~\ref{tab:lenspositions}.
+$\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
+Symm denotes that a point-symmetry prior is employed.}
+    \label{tab:lenspriors}
   \end{center}
-\end{table*}
+\end{table}
 
 \section{Results}\label{sec:results}
-
-{\bf JR. CLAUDIO OR JUSTIN TO WRITE RESULTS SECTION?} 
-\textbf{Content:}
-\begin{itemize}
-\item Describe special features in reconstructed lenses
-\item Show the wedges money plot
-\item Discuss the results, especially:
-\item 1. Dark matter halos seem quite round, stars not necessarily
-\item 2. Both DM and stars more elliptical with increasing radius 
-\item 3. DM halos with weak shear are aligned (apart from spherical systems that don't count); strong shear systems can be highly misaligned.
-\item 4. No sensitivity to shear prior. Only one lens B2045 requires a shear prior to avoid spurious extra images; doesn't affect the shape measure though. 
-\item 5. Merger systems stand out. 
-\end{itemize}
-
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=.65\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$.
+  \includegraphics[width=.8\linewidth]{Figures/wedges_shears.pdf}
+  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$.
 The wedges display the alignment of the semi-major axes of the components.
@@
 In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
-The opening angle displays the error in the shape estimate of the dark matter halo.
-The lenses are additional color-coded in terms of the required external shear in modelling the lens.}
-  \label{fig:wedges}
-\end{figure}
+The opening angle displays the statiscal error in the shape estimate of the dark matter halo.
+Both the error in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within.
+The lenses are additionally color-coded in terms of the required external shear in modelling the lens.}
+  \label{fig:wedgesall}
+\end{figure*}
 
@@
   \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
-  \caption[width=.65\linewidth]{Similar to Figure~\ref{fig:wedges}.
+  \caption[width=\linewidth]{Similar to Figure~\ref{fig:wedgesall}.
 In each of the subfigures however we only consider pixels within 1, 2, 3, 4, or 5 $R_e$.
-If a lens does not extend to these limiting radii, it is dropped from the analysis in this and subsequent subfigures.}
-  \label{fig:wedgesall}
+If the outermost image of a system lies within one of the limiting radii, the system is kept in this panel, but dropped from subsequent panels.}
+  \label{fig:wedgesradii}
 \end{figure*}
 
+{\bf (CB: In general, do we need to link the results better to previous studies?
+We mention them already in the introduction and since they're not directly comparable, I'm not sure how much emphasis should be put on the comparison.)}
+
+We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses.
+The reconstructed mass maps and the in this work used stellar mass maps \citep{2011ApJ...740...97L} are displayed in the Appendix.
+
+Figure~\ref{fig:wedgesall} displays the shapes (see \S\ref{sec:shapemethod}) and their alignment of the dark and stellar mass distribution.
+In this Figure all the distribution up to the last-image radius $R_{L}$ are probed.
+Different features are evident.
+First, the reconstructed dark matter distribution of the considered lenses is rounder than the stellar distribution.
+Second, most lenses are in the bottom-left corner.
+Thus, the dark matter distributions are typically quite round, while the stellar distributions can be rather elliptical.
+{\bf HERE MAYBE SOME SENTENCES HOW THIS RESULT IS SURPRISING}
+
+Third, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to the larger stellar ellipticity ($s_* > 1.6$) and at the same time an alignment of the dark matter and stellar distributions.
+One of those lenses, {\it1608}, is an known merger of an early-type galaxy with a probably late-type galaxy \citep{2003ApJ...584..100S}.
+We suggest that the other two systems, {\it0712} and {\it2016}, may be post-merger systems as well and therefore display those similarities with {\it1608}.
+
+Fourth, dark matter and stellar distributions with weak shear are aligned apart from {\it0047}, which is almost spherical ($s_{dm}\sim1.05$).
+We note that in {\it1115} the semi-major axes seems to be aligned with the semi-minor axes of the other component.
+Systems requiring a larger external shear, {\it0414}, {\it0911}, and {\it1422}, can display a certain misalignment between the distributions.
+The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that can cause those misalignments {\bf (CB: NEED SOME REFERENCES HERE)}.
+{\bf (CB: I'M NOT SURE WHETHER THE SHEAR FOR 0414 IS LARGE ENOUGH THAT IT COULD BE A PROBLEM THAT NOT ENVIRONMENT HAS BEEN DETECTED (THE SYSTEM IS ADDITIONALLY RATHER MISALIGNED))}
+
+We performed tests for the robustness of the shape estimate and its dependence on the shear prior.
+Only two systems, {\it1422} and {\it2045}, reacted to a stricter prior on the external shear $|\gamma|$.
+{\it1422} requires a rather large external shear ($|\gamma|\sim0.25$).
+Restricting the range of the allowed external shear values did not affect the misalignment of the dark matter and stellar mass distributions.
+It however increased the ellipticity of the reconstructed mass distribution.
+We observed a trade-off between the galaxy's ellipticity and the magnitude of the external shear.
+{\it2045} on the other hand is particularly interesting.
+Allowing the shear to roam free as for the other lenses, favours an anomalously high shear ($\gamma > 0.5$), with strong misalignment.
+However, such models also produce spurious extra images along the arc.
+We find that limiting the maximum shear $|\gamma|$ to 0.1 removes the extra images, though the lens then pushes on its maximum shear prior.
+We find that the mass map is robust against a stronger shear prior, and it thus again does not affect the alignment of the distributions.
+It produces dark matter distributions well-aligned with the stars.
+We believe that a strong shear prior for this particular lens is justified by the non-observation of the spurious extra images; none of the other lenses in our sample have a shape profile that is sensitive to our shear prior.
+
+Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are averaged within different multiples of $R_e$ in contrast to the whole distribution within the outermost image.
+It looks in general similar to Figure~\ref{fig:wedgesall}.
+{\it0957} and to some degree {\it1422} display however some signs of isophotal twist (see also Appendix).
+Additionally, there seems to be a trend that the ellipticity of the stars and potentially of the dark matter, though the latter is consistent with constant ellipticity, increases with increasing radius.
+{\bf (CB: DO WE NEED TO ADD AN INTERPRETATION WHY THIS IS?)}
+
 \section{Conclusion}\label{sec:conclusions}
-
 We have measured the shape and alignment of stars and dark matter in 11 strong lensing galaxies using a new non-parametric lens tool, \Glass.
@@
 \item We found that in all cases the dark matter halos are rounder than the light distribution over the range $R_e < R < 5R_e$.
-As we average over larger radii, the lenses become increasingly elliptical both in their dark matter and stars, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$.
+As we average over larger radii, the lenses become increasingly elliptical in their stars and potentially dark matter, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$.
 
 \item Three systems have very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment between light and dark.
-One of these -- B1608 -- is a known merging pair; we suggest that the other two (B0712 and B2016) may also be recent post-merger systems.
+One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.
 
@@
 \section{Acknowledgements}\label{sec:acknowledgements}
-We would like to thank Dominik Leier for useful discussions. JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
 
@@
 \section{Reconstructed Lenses}\label{sec:reconstructions}
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l r r r r}
+      Lens & A [''] & B [''] & C [''] & D [''] \\ \hline
+      0047 & 1.270 & -0.630 & 0.520 & -0.730 \\
+           & 0.105 & -0.995 & -1.045 & 0.705 \\
+      0414 & -0.472 & -1.061 & -1.1947 & 0.885 \\
+           & 1.277 & -0.661 & -0.255 & -0.361 \\
+      0712 & -0.013 & 0.795 & 0.747 & -0.391 \\
+           & -0.804 & -0.156 & -0.292 & 0.307 \\
+      0712 & -0.013 & 0.795 & 0.747 & -0.391 \\
+           & -0.804 & -0.156 & -0.292 & 0.307 \\
+      0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 \\
+           & 5.034 & -1.018 & 3.470 & -0.050 \\
+      1115 & 0.355 & -0.909 & -1.093 & 0.717 \\
+           & 1.322 & -0.714 & -0.260 & -0.627 \\
+      1422 & 1.079 & 0.357 & 0.742 & -0.205 \\
+           & -0.095 & 0.973 & 0.656 & -0.147 \\
+      1608 & -1.300 & -0.560 & -1.310 & 0.570 \\
+           & -0.800 & 1.160 & 0.700 & -0.080 \\
+      2016 & -1.735 & 0.335 & 0.437 & 1.268 \\
+           & 1.778 & -1.450 & -1.435 & 0.276 \\
+      2045 & 1.121 & 1.409 & 1.255 & -0.507 \\
+           & 0.824 & 0.035 & 0.576 & -0.183 \\
+      2237 & 0.598 & -0.075 & 0.791 & -0.710 \\
+           & 0.758 & -0.939 & -0.411 & 0.271 \\
+    \end{tabular}
+    \caption[width=\linewidth]{The image positions of all the systems in order of arrival time (image A has the shortest arrival time, image D the longest) are listed.
+The positions are relative to the center of the lens galaxy.
+The first row contains the RA coordinate, the second the DEC coordinate of the image.
+\newline $^{a}$ The source lensed by 0957 has different component.
+Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
+    \label{tab:lenspositions}
+  \end{center}
+\end{table}
 
-In this appendix, we show the results of our lens modelling for each individual lens (Figures \ref{fig:lensreconstruction1}, \ref{fig:lensreconstruction2}, and \ref{fig:lensreconstruction3}).
+In this Appendix, we show the results of our lens modelling for each individual lens (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
 The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence interval of these for the dark matter map.
-Figure \ref{fig:wedges} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $s$), and the angle between the dark matter and stellar major axes.
+Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $s$), and the angle between the dark matter and stellar major axes.
 Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.
+
+We note in Figure~\ref{fig:lensreconstruction2} specifically for {\it0957} and to some degree also {\it1422} twisting isophotes \citep{1978ComAp...8...27B}. {\bf (CB: DOES THIS NEED TO BE EXPANDED?)}
 
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses32.pdf}
-  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:ensreconstruction1}.}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
   \label{fig:lensreconstruction2}
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses33.pdf}
-  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:ensreconstruction1}.}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
   \label{fig:lensreconstruction3}

### 2014-12-22 shapes/paper.tex
Justin: small edits throughout. Claudio's questions answered/addressed.

@@
 
-\title[Light versus Dark in Strong Lensing Galaxies]{Light versus Dark in Strong  Lensing Galaxies: Dark matter halos are rounder than their stars}
+\title[Light versus Dark in Strong Lensing Galaxies]{Light versus Dark in Strong Lensing Galaxies: Dark matter halos that are rounder than their stars}
 
@@
 We measure the shape and alignment of stars and dark matter in 11 strong
-lensing galaxies and find that in all cases the dark matter halos are rounder
+lensing galaxies, finding in all cases that the dark matter halos are rounder
 than the light distribution over the range $R_e < R < 5R_e$.  Averaging over
@@
 Our results provide a new constraint on galaxy formation models that must
-explain the origin of very round dark matter halos and highly misaligned
-systems. Such misalignments also present a new challenge for alternative
+explain the origin of both very round dark matter halos and highly misaligned
+strong lensing systems. Such misalignments also present a new challenge for alternative
 gravity theories in which the light and dark must necessarily be highly
@@
 Halo shapes and alignments also constrain alternative gravity models \citep{2001MNRAS.327..552M,2004ApJ...610L..97H,2005MNRAS.361..971R,2012PhRvD..86h3507F,2013MNRAS.434.2971D}.
-If the visible light is the only source of gravity in a galaxy, then we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can, at least in principle, be broken.
+If the visible light is the only source of gravity in a galaxy, then we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can at least in principle be broken.
 
 Strong lensing provides a unique probe of the alignment and shape of the total mass distribution in galaxies \citep[e.g.][]{1986ApJ...310..568B,1992grle.book.....S,1998ApJ...509..561K,2000ApJ...543..131K,2006ApJ...649..599K,2007AJ....134..668A,2008MNRAS.383..857F,2010ApJ...724..511A,2012MNRAS.424..104L}.
-For `red and dead' ellipticals that are largely devoid of gas, their baryonic content can be mapped through stellar population synthesis modelling of their light distribution \citep[e.g.][]{2005ApJ...623L...5F,2006ApJ...640..662T,2008MNRAS.383..857F}.
-This opens up the possibility of directly comparing the light and mass in strong lensing systems \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
+For `red and dead' ellipticals that are largely devoid of gas, their baryonic content can be mapped through stellar population synthesis modelling of their light distribution alone \citep[e.g.][]{2005ApJ...623L...5F,2006ApJ...640..662T,2008MNRAS.383..857F}.
+Furthermore, such systems are dense enough to produce strong lensing, opening up the possibility of directly comparing the light and mass in these galaxies \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
 Previous work in the literature has found that the light and mass are well-aligned (though a mis-match of up to 10$^\circ$ is not uncommon; e.g.
@@
 Recently, we introduced a new non-parametric lens tool, \Glass\ \citep{2014arXiv1401.7990C}.
-Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass dominates the potential over the region of the images.
-{\bf (CB.
-i) is the case for all the lenses except Q0957, ii) however is only the case for a minority of the sample.
-This sentence creates therefore some tension that is not addressed however (I don't know whether we should rephrase it or add another sentence))} In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
+Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
+In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
 We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time.
@@
 \Glass{} is a new `non-parametric' gravitational lens modelling framework
-\citep{2014arXiv1401.7990C} that is capable of generating a distribution of
+\citep{2014arXiv1401.7990C} generates a distribution of
 mass models given a set of basic assumptions, or priors.
-{\bf Hence, \Glass\ does not yield the most probable mass model.
-Rather, we can describe the distribution of all the allowed models.
-(CB: I'VE ADDED THIS SENTENCE AS I FELT SOMETHING LIKE THAT MIGHT BE NEEDED AT THIS POINT.
-IT PROBABLY NEEDS TO BE IMPROVED THOUGH)} In this context,
-non-parametric means that  many more parameters than data constraints are used
+Hence, \Glass\ does not yield the most probable mass model.
+Rather, it calculates an ensemble of all allowed models given the data and assumed priors.
+In this context,
+`non-parametric' really just mean that many more parameters than data constraints are used
 such that system of equations describing the lensing mass distribution is
@@
 \item The fixed cosmology $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
-\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
+\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1]$.
 \end{enumerate}
@@
 % \item[(viii)] External point masses to model satellite galaxies outside but
-close to the Einstein radius.
+% close to the Einstein radius.
 
@@
 As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
-The shape estimates do not necessarily need to be the same within different radii.
-E.g.
-there are effects as isophotal twist \citep[e.g.][and references therein]{1978ComAp...8...27B} causing differences in the shape estimates between the central and the outer parts of the system.
-{\bf (CB: THESE LAST SENTENCES PROBABLY NEED TO BE REPHRASED TOO)}
+The shape estimates do not necessarily need to be the same within different radii -- e.g.
+effects such as isophotal twist \citep[e.g.][and references therein]{1978ComAp...8...27B} can cause differences in the shape estimates between the central and the outer parts of the system.
 
-Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image.
-Furthermore, we generate 10000 mass models for each system we consider and describe the distribution of all the individual estimates for the dark matter shapes.
-{\bf (CB: MAYBE NEEDS REPHRASING, SEE ABOVE)}
+Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image. We generate in each case an ensemble of 10,000 mass models.
 
 \section{Data}\label{sec:data}
-Stellar-mass maps are taken from \citep{2011ApJ...740...97L}.
-In that work, the light of the galaxy images in all available HST bands was first fitted using using GALFIT \citep{2002AJ....124..266P}, and the resulting light maps were used to obtain stellar-mass maps using a synthesis of the stellar-population models of \citep{2003MNRAS.344.1000B}.
-The population synthesis marginalised over the star-formation epoch and time scales and over the stellar metallicity.
+Stellar mass maps are taken from \citep{2011ApJ...740...97L}.
+In that work, the light of the galaxy images in all available HST bands was first fitted using using GALFIT \citep{2002AJ....124..266P}, and the resulting light maps were used to obtain stellar mass maps using a synthesis of the stellar-population models of \citep{2003MNRAS.344.1000B}.
+The population synthesis marginalised over the star formation epoch and time scales and over the stellar metallicity.
 The IMF was taken to be the log-normal form given by \citep{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the inferred shape of the stellar mass.
 
-As it is shown in \citep{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
+As shown in \citep{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
 Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561} out of the sample presented in \citep{2011ApJ...740...97L}.
-Thus, the sample consists in total of 11 lenses.
-Each individual system is presented below.
+This leads to a sample of 11 lenses.
+We discuss each of these systems, next.
 
@@
 A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
-It however is more likely a foreground object \citep{2011MNRAS.413L..86C}.
+It, however, is more likely a foreground object \citep{2011MNRAS.413L..86C}.
 
@@
 X-ray emission can be detected and an analysis of which yields a temperature of 2.3 keV.
-There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.
+There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
 
-\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
+\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the centre of a cluster with a high spiral galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
 Due to the large image separation, large physical scales are probed.
-As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
-These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
+As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
+These results are consistent with the centre of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
 The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
@@
 \cite{1997ApJ...489...21B}.
-The environment of the lens was analyzed thouroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
+The environment of the lens was analysed thoroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
 It is part of a small group of 13 members.
-Also X-ray emission was detected from the corresponding group, and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
+Also, X-ray emission was detected from the corresponding group and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
 
@@
 The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment has been analyzed and group with 8 (9 if merging galaxies are counted individually) was found \citep{2006ApJ...642...30F}.
+The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was found \citep{2006ApJ...642...30F}.
 No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
-The data seems to indicate four other groups along the line of sight.
+The data seem to indicate four other groups along the line of sight.
 
@@
 It is the farthest lens we consider in this sample.
-It lies in a cluster which consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
-The clusters shows a high density of galaxies close to the lens in a south-east direction.
+It lies in a cluster that consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
+The cluster shows a high density of galaxies close to the lens in a south-east direction.
 
 \textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
-It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, the velocity dispersion however seems too high.
+It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, however the velocity dispersion seems too high.
 As the source redshift is rather low, a large lens mass is required.
@@
 There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
-As the measurements are inconclusive, we choose to not include this satellite.
+As the measurements are inconclusive, we choose to not include this satellite explicitly in our models.
 
-\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}, the only non-early type lens in this sample.
-With only a redshift of $z=0.04$, it is the closest lens of the sample.
-Due to the low redshift, the probed physical scales are small.
-Therefore, the bulge component of the galaxy dominates the lens, what makes the stellar population synthesis modelling possible.
-No further inquiries into the environment were made.
-It is
+\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}, the only non early-type lens in this sample.
+With a redshift of just $z=0.04$, it is also the closest lens of the sample.
+Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
+However, this makes our stellar population synthesis model assumptions (i.e.
+that the stars are a simple stellar population) likely valid.
 
-Further information on the sample can be found in \citep{2011ApJ...740...97L,2012A&A...538A..99S}.
+Further information on the sample can be found in \citet{2011ApJ...740...97L} and \citet{2012A&A...538A..99S}.
 The most important quantities of each system are given in Table~\ref{tab:lensproperties}.
-Due to the different angular separations of the images, different scales of the lens galaxies are probed.
+Due to the different angular separations of the images and the different angular diameter distances, in each lens galaxy we necessarily probe slightly different scales.
 
@@
 The columns are from left to right, the lens redshift $z_L$, the redshift of the source $z_S$, the maximum angular separation between two images $\Delta\theta$, the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$, and information on the environment of the lens.
-C and G denote a known cluster resp.
-group environment.
+C and G denote a known cluster or group environment, respecitvely.
 The number in the brackets is the number of confirmed members.}
@@
     \end{tabular}
-    \caption[width=\linewidth]{Additional priors to the baseset described in \S\ref{sec:glass} are listed.
+    \caption[width=\linewidth]{Additional priors to the base set described in \S\ref{sec:glass} are listed.
 $\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$.
@@
 $\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
-Symm denotes that a point-symmetry prior is employed.}
+`Symm' denotes that a point-symmetry prior is employed.}
     \label{tab:lenspriors}
@@
 
-{\bf (CB: In general, do we need to link the results better to previous studies?
-We mention them already in the introduction and since they're not directly comparable, I'm not sure how much emphasis should be put on the comparison.)}
+We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses. The reconstructed stellar and dark mass maps for each individual lens are given in the Appendix.
 
-We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses.
-The reconstructed mass maps and the in this work used stellar mass maps \citep{2011ApJ...740...97L} are displayed in the Appendix.
+Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark and stellar mass distributions.
+In this Figure, the full distribution up to the last-image radius $R_{L}$ is probed.
+There are several key points to note.
+Firstly, the reconstructed dark matter distribution of all lenses considered here is rounder than the stellar distribution.
+Secondly, most lenses lie in the bottom-left corner: the dark matter distributions are typically quite round, while the stellar distributions can be rather elliptical.
+Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 1.6$).
+At the same time, they show a very strong alignment between their dark matter and stellar distributions.
+One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}.
+We suggest that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.
+Fourthly, notice that all dark matter and stellar distributions with weak shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim1.05$).
+By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
+The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
+Two systems stand out from the rest, however.
+In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned system of all lenses studied here.
+This may be explained by its external shear ($\gamma \sim 0.1$) that likely owes to its group environment (see Table \ref{tab:lensproperties}).
+The lens {\it0414} is also interesting.
+It also shows strong misalignment, yet has no sign of a group or cluster environment reported to date.
+It does show rather strong external shear, however ($\gamma \sim 0.15$), suggesting that a group or cluster environment perhaps remains to be found.
 
-Figure~\ref{fig:wedgesall} displays the shapes (see \S\ref{sec:shapemethod}) and their alignment of the dark and stellar mass distribution.
-In this Figure all the distribution up to the last-image radius $R_{L}$ are probed.
-Different features are evident.
-First, the reconstructed dark matter distribution of the considered lenses is rounder than the stellar distribution.
-Second, most lenses are in the bottom-left corner.
-Thus, the dark matter distributions are typically quite round, while the stellar distributions can be rather elliptical.
-{\bf HERE MAYBE SOME SENTENCES HOW THIS RESULT IS SURPRISING}
-
-Third, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to the larger stellar ellipticity ($s_* > 1.6$) and at the same time an alignment of the dark matter and stellar distributions.
-One of those lenses, {\it1608}, is an known merger of an early-type galaxy with a probably late-type galaxy \citep{2003ApJ...584..100S}.
-We suggest that the other two systems, {\it0712} and {\it2016}, may be post-merger systems as well and therefore display those similarities with {\it1608}.
-
-Fourth, dark matter and stellar distributions with weak shear are aligned apart from {\it0047}, which is almost spherical ($s_{dm}\sim1.05$).
-We note that in {\it1115} the semi-major axes seems to be aligned with the semi-minor axes of the other component.
-Systems requiring a larger external shear, {\it0414}, {\it0911}, and {\it1422}, can display a certain misalignment between the distributions.
-The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that can cause those misalignments {\bf (CB: NEED SOME REFERENCES HERE)}.
-{\bf (CB: I'M NOT SURE WHETHER THE SHEAR FOR 0414 IS LARGE ENOUGH THAT IT COULD BE A PROBLEM THAT NOT ENVIRONMENT HAS BEEN DETECTED (THE SYSTEM IS ADDITIONALLY RATHER MISALIGNED))}
-
-We performed tests for the robustness of the shape estimate and its dependence on the shear prior.
+We performed tests for the robustness of our shape estimate and its dependence, in particular, on the shear prior.
 Only two systems, {\it1422} and {\it2045}, reacted to a stricter prior on the external shear $|\gamma|$.
@@
 Restricting the range of the allowed external shear values did not affect the misalignment of the dark matter and stellar mass distributions.
-It however increased the ellipticity of the reconstructed mass distribution.
-We observed a trade-off between the galaxy's ellipticity and the magnitude of the external shear.
+It did, however, increase the ellipticity of the reconstructed mass distribution: we observed a trade-off between the galaxy's ellipticity and the magnitude of the external shear as might be expected.
 {\it2045} on the other hand is particularly interesting.
@@
 
-Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are averaged within different multiples of $R_e$ in contrast to the whole distribution within the outermost image.
-It looks in general similar to Figure~\ref{fig:wedgesall}.
-{\it0957} and to some degree {\it1422} display however some signs of isophotal twist (see also Appendix).
-Additionally, there seems to be a trend that the ellipticity of the stars and potentially of the dark matter, though the latter is consistent with constant ellipticity, increases with increasing radius.
-{\bf (CB: DO WE NEED TO ADD AN INTERPRETATION WHY THIS IS?)}
+Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
+Most lenses show a $\sim$ constant shape with radius appearing similar to the results in Figure~\ref{fig:wedgesall}.
+{\it0957} and to some degree {\it1422} display, however, some signs of isophotal twist (see also Appendix).
+Additionally, there appears to be a trend that the ellipticity of the stars and potentially of the dark matter (though the latter is consistent with constant ellipticity) increases with increasing radius.
 
-\section{Conclusion}\label{sec:conclusions}
+\section{Conclusions}\label{sec:conclusions}
 We have measured the shape and alignment of stars and dark matter in 11 strong lensing galaxies using a new non-parametric lens tool, \Glass.

### 2014-12-26 shapes/paper.tex
Slightly changed Figure A3

@@
 
-We note in Figure~\ref{fig:lensreconstruction2} specifically for {\it0957} and to some degree also {\it1422} twisting isophotes \citep{1978ComAp...8...27B}. {\bf (CB: DOES THIS NEED TO BE EXPANDED?)}
+We note in Figure~\ref{fig:lensreconstruction2}, specifically for {\it0957} and to some degree also {\it1422}, twisting isophotes \citep[e.g.][]{1978ComAp...8...27B}.
 

### 2015-01-20 shapes/paper.tex
Included remarks by co-authors

@@
 \usepackage{multirow}
+\usepackage{color}
 
@@
 \def\PixeLens{{\sc PixeLens}}
+\newcommand{\cb}[1]{{\color{red} \textbf{#1}}}
 
-\title[Light versus Dark in Strong Lensing Galaxies]{Light versus Dark in Strong Lensing Galaxies: Dark matter halos that are rounder than their stars}
+\title[Light versus Dark in \cb{Strong-Lens Galaxies}]{Light versus Dark in \cb{Strong-Lens Galaxies}: Dark matter halos that are rounder than their stars}
+% "Light versus dark matter in strong-lens galaxies: Dark matter halos may be rounder than their stellar distributions"
 
-\author[Bruderer]{Claudio Bruderer$^{1}$\thanks{E-mail: claudio.bruderer@phys.ethz.ch}, J. I. Read$^{1,2}$, P. Saha$^{3}$, J. Coles$^{4}$\\
-$^{1}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
+\author[Bruderer et al.]
+{\parbox{\textwidth}{Claudio Bruderer,$^{1}$\thanks{E-mail: \texttt{claudio.bruderer@phys.ethz.ch}}
+Justin I. Read,$^{1,2}$
+Prasenjit Saha,$^{3}$
+Jonathan Coles,$^{4}$
+Emilio E. Falco,$^{5}$
+Ignacio Ferreras$^{6}$ and
+Dominik Leier$^{7}$}\vspace{0.4cm}\\
+\parbox{\textwidth}{$^{1}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
 $^{2}$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
 $^{3}$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France
-}
+$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
+$^{5}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
+$^{6}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
+$^{7}$Dipartimento di Fisica e Astronomia, Università di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy}}
 
@@
 \begin{abstract}
-We measure the shape and alignment of stars and dark matter in 11 strong
-lensing galaxies, finding in all cases that the dark matter halos are rounder
-than the light distribution over the range $R_e < R < 5R_e$.  Averaging over
-larger radii, the lenses become increasingly elliptical both in their dark
-matter and stellar components, as defined using the ratio $s$ of the largest to
-smallest eigenvalues of the 2D moment of inertia tensor of the projected
-lensing mass.  While dark matter halos are never more elliptical than $s_{dm} =
-1.15$, their stars can extend to $s_* > 1.4$ Three systems, in particular, have
-very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment
-between light and dark. One of these -- B1608 -- is a known merging pair; we
-suggest that the other two (B0712 and B2016) may also be recent post-merger
-systems.  Galaxies with high dark matter ellipticity and weak external shear
-show very strong alignment between light and dark; those with strong shear
-($\gamma \simgt 0.1$) can be very highly misaligned. This is reassuring since
-isolated misaligned galaxies are expected to be unstable.
+We measure the shape and alignment of the stellar and dark matter mass distribution in 11 \cb{strong-lens galaxies}, finding in all cases that the dark matter halos are rounder than the stellar mass distribution over the range $R_e < R < 5R_e$.
+Averaging over larger radii, the lenses become increasingly elliptical both in their dark matter and stellar components, as defined \cb{using the ratio of the smallest to largest eigenvalues} of the 2D moment of inertia tensor of the projected \cb{lens mass}.
+While dark matter halos are never more elliptical \cb{than $e_{dm} = 0.3$}, their stars can extend \cb{to $e_* > 0.3$}.
+Three systems, in particular, \cb{have a high stellar ellipticity ($e_* > 0.4$)} and correspondingly high alignment between luminous and dark matter distribution.
+One of these -- B1608 -- is a known merging pair; we suggest that the other two (B0712 and B2016) may also be recent post-merger systems.
+Galaxies with high dark matter ellipticity and weak external shear show very strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be very highly misaligned.
+This is reassuring since isolated misaligned galaxies are expected to be unstable.
 
-Our results provide a new constraint on galaxy formation models that must
-explain the origin of both very round dark matter halos and highly misaligned
-strong lensing systems. Such misalignments also present a new challenge for alternative
-gravity theories in which the light and dark must necessarily be highly
-correlated.
+Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter halos and highly misaligned \cb{strong-lens systems}.
+Such misalignments also present a new challenge for alternative gravity theories in which the stellar and dark matter components must necessarily be highly correlated.
 
@@
 \begin{keywords}
-Gravitational lensing: strong --- galaxies: structure
+Gravitational lensing: strong --- galaxies: structure --- galaxies: haloes --- galaxies: formation --- galaxies: elliptical and lenticular, cD
 \end{keywords}
@@
 
-The ellipticity and shape of stars relative to their host dark matter halo encodes information both about our cosmological model ($\Lambda$CDM) and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
+The ellipticity and shape of the stellar component relative to their host dark matter halo encodes information both about our cosmological model ($\Lambda$CDM) and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
 `Dark-matter-only' (DMO) simulations in $\Lambda$CDM predict dark matter halos that are triaxial \citep{1991ApJ...378..496D,1992ApJ...399..405W,1996ApJ...462..563N,2002ApJ...574..538J}, with mean `shape parameter' $\langle q \rangle = (b+c)/2a \sim 0.8$ (where $a > b > c$ are the long, intermediate and short axes of the figure; \citealt{2007MNRAS.378...55M}).
@@
 For `red and dead' ellipticals that are largely devoid of gas, their baryonic content can be mapped through stellar population synthesis modelling of their light distribution alone \citep[e.g.][]{2005ApJ...623L...5F,2006ApJ...640..662T,2008MNRAS.383..857F}.
-Furthermore, such systems are dense enough to produce strong lensing, opening up the possibility of directly comparing the light and mass in these galaxies \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
+Furthermore, such systems are dense enough to produce strong lensing \cb{effects}, opening up the possibility of directly comparing the light and mass in these galaxies \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
 Previous work in the literature has found that the light and mass are well-aligned (though a mis-match of up to 10$^\circ$ is not uncommon; e.g.
@@
 
-Weak lensing can also be used to probe the shape and alignment between light and dark, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
+Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
 \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
-They found that dark matter halos appear to be rounder then their light distributions, with some weak evidence for alignment.
-Both measurements are challenging, however, and more recent data appear to be at odds with this early work, favouring dark matter halos that are more elliptical than their stars \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
+They found that dark matter halos appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
+Both measurements are challenging however, and more recent data appear to be at odds with this early work, favouring dark matter halos that are more elliptical than their stellar mass component \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
 
 Recently, we introduced a new non-parametric lens tool, \Glass\ \citep{2014arXiv1401.7990C}.
-Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
+Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in \cb{lens systems} if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
 In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
-We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time.
+We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these \cb{lens galaxies}, for the first time.
 This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter.
-Since the stars often dominate the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution.
-Our comparison between light and dark is made possible by the fact that \Glass\ uses the light distribution as a prior on the mass map, ensuring that the dark matter mass is always positive.
+Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution.
+Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter mass is always positive.
 
 This paper is organised as follows.
-In \S\ref{sec:glass}, we briefly review the \Glass\ code.
+In \S\ref{sec:glass}, we briefly review the \Glass\ code \cb{and define our method to assess shape and alignment of lens galaxies}.
 In \S\ref{sec:data}, we present our data compilation with references.
@@
 
-\Glass{} is a new `non-parametric' gravitational lens modelling framework
-\citep{2014arXiv1401.7990C} generates a distribution of
-mass models given a set of basic assumptions, or priors.
+\Glass\ is a new `non-parametric' gravitational lens modelling framework \citep{2014arXiv1401.7990C} that generates a distribution of mass models given a set of basic assumptions, or priors.
 Hence, \Glass\ does not yield the most probable mass model.
 Rather, it calculates an ensemble of all allowed models given the data and assumed priors.
-In this context,
-`non-parametric' really just mean that many more parameters than data constraints are used
-such that system of equations describing the lensing mass distribution is
-under-constrained. \Glass{} shares some aspects with an earlier code
-\PixeLens{} \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely
-different code base. Its key improvements upon \PixeLens{} which are relevant
-for this paper include:
+In this context, `non-parametric' really just means that many more parameters than data constraints are used such that the system of equations describing the \cb{lensing mass} distribution is under-constrained.
+\Glass\ shares some aspects with an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
+Its key improvements upon \PixeLens{} which are relevant for this paper include:
 
 \begin{enumerate}
-\item A new uniform sampling algorithm for high
-    dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large
-    ensembles of $>10,000$ models to be efficiently generated. 
-%\item \Glass\ provides a modular framework that allows new priors to be added
-%    and modified easily.
-%\item The basis functions approximating a model can be easily changed (in this
-%    paper, we assume pixels as in \PixeLens). 
-\item With so many models in the final ensemble, we can afford to apply
-    non-linear constraints (for example stellar kinematic data; or the removal of
-    models with spurious extra images) to accept/reject models in a post-processing
-    step.
-\item The central region of the mass map can have a higher resolution to more
-    efficiently capture steep models.
+\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large ensembles of $>10,000$ models to be efficiently generated. 
+\item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
+\item The central region of the mass map can have a higher resolution to more efficiently capture steep models.
 \item Stellar density can be used as an additional lower-bound constraint on the models. 
-%\item Point or extended mass objects can be placed in the field.
 \end{enumerate}
 
-%\Glass{} is described in detail in the code paper: \citet{2014arXiv1401.7990C}.
 In this paper, the default priors used to model each lens are listed below.  Table
@@
 \item A reconstructed stellar mass map as lower mass bounds in every pixel.
-\item The local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
+\item The local density gradient \cb{always points within 50$^{\circ}$ of the center of the distribution,} and the slope is at most 0 everywhere.
+In other words, the density profile peaks in the center.
 \item The fixed cosmology $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
 \item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1]$.
+\item \cb{The pixel radius is set to be 12 pixels.}
 \end{enumerate}
@@
 \begin{enumerate}
-\item[(vii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
-
-% \item[(viii)] External point masses to model satellite galaxies outside but
-% close to the Einstein radius.
-
-\item[(viii)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$ where 
-the surface mass profile can be assumed to be symmetric (3+1 quad
-configurations and the double \textit{Q0957}).
+\item[(viii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
+\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$, where the surface mass profile can be assumed to be symmetric ((3+1)-quad configurations and the double \textit{Q0957}).
 
@@
 \subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
-We employ the same shape definition as in \citep{2014arXiv1401.7990C}. The shape parameter $s$ is defined as the ratio of the two eigenvalues $\lambda_1$ and $\lambda_2$, i.e.
+\cb{We employ a shape definition related to the definition used by \cite{2014arXiv1401.7990C}.
+The ellipticity parameter $e$ is defined as} %the ratio of the two eigenvalues $\lambda_2$ and $\lambda_1$, i.e.
 \begin{equation}\label{eq:shapeestimate}
-    s \equiv \frac{\lambda_{1}}{\lambda_{2}}, \ \ \ \mathrm{where} \ \lambda_{1} \geq \lambda_{2},
+    e \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}}, \ \ \ \mathrm{where} \ \lambda_{1} \geq \lambda_{2},
 \end{equation}
@@
 The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of the half-light radius $R_e$.
-$R_e$ is the Petrosian radius containing half of the flux of the total light distribution.
-As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
+\cb{$R_e$ is the half-light radius measured with respect to the Petrosian flux.} As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
 The shape estimates do not necessarily need to be the same within different radii -- e.g.
@@
 
-Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image. We generate in each case an ensemble of 10,000 mass models.
+Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image.
+We generate in each case an ensemble of 10,000 mass models.
+\cb{Each of these models is analyzed individually, yielding a distribution of constrained quantities.}
 
 \section{Data}\label{sec:data}
-Stellar mass maps are taken from \citep{2011ApJ...740...97L}.
-In that work, the light of the galaxy images in all available HST bands was first fitted using using GALFIT \citep{2002AJ....124..266P}, and the resulting light maps were used to obtain stellar mass maps using a synthesis of the stellar-population models of \citep{2003MNRAS.344.1000B}.
-The population synthesis marginalised over the star formation epoch and time scales and over the stellar metallicity.
-The IMF was taken to be the log-normal form given by \citep{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the inferred shape of the stellar mass.
+Stellar mass maps are taken from \cite{2011ApJ...740...97L}.
+In that work, the \cb{surface brightness distribution} of the galaxy images in all available HST bands was first fitted using using GALFIT v2.03b \citep{2002AJ....124..266P}, and the resulting \cb{flux} maps were used to obtain stellar mass maps using the synthesis of the stellar-population models of \cite{2003MNRAS.344.1000B}.
+The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
+The IMF was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} \cb{but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
+We note that the effect of recent claims towards a non-universal IMF on stellar M/L is still under debate.
+While dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.}
 
+\cb{The original sample we consider, is presented in \cite{2011ApJ...740...97L} and consists of 21 lens systems.
+It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
 As shown in \citep{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
-Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561} out of the sample presented in \citep{2011ApJ...740...97L}.
+Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
 This leads to a sample of 11 lenses.
-We discuss each of these systems, next.
+We discuss each of these systems, next.}
 
 \textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
-It is part a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
+It is part of a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
 
@@
 A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
-It, however, is more likely a foreground object \citep{2011MNRAS.413L..86C}.
+It, however, is more likely a foreground object \cb{with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
+This is sufficiently distant to still contribute to the lensing effect.}
 
-\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}.
+\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \cb{\citep{1998MNRAS.296..483J,1998AJ....115..377F}.
+There is a foreground group of about 10 member galaxies at $z\sim0.3$, which could affect the modelling \citep{2002AJ....123..627F}.}
 
-\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}.
-It has measured time delays \citep{2002ApJ...572L..11H}.
+\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost \cb{spherical} early-type galaxy \cb{\citep{1997A&A...317L..13B,2012A&A...538A..99S}.} It has measured time delays \citep{2002ApJ...572L..11H}.
 It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
@@
 Due to the large image separation, large physical scales are probed.
-As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east.
+As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg.
 These results are consistent with the centre of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
@@
 
-\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}.
-It has measured time delays.
-In this work use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
+\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \cb{\citep{1980Natur.285..641W,2005ApJ...626...51Y}.} It has measured time delays \cb{\citep[see e.g.][]{1997ApJ...475L..85S}.} In this work\cb{, we} use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
 \cite{1997ApJ...489...21B}.
@@
 
-\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}.
-Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}.
+\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \cb{\citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.} Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}.
 We choose therefore not to include them in the analysis.
 The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
-Using newer data, an additional member could be found \citep{2011ApJ...726...84W}.
+Using newer data, \cb{additional members} could be found \citep{2011ApJ...726...84W}.
 \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
 
-\textit{B1608+656} (hereafter \textit{1608}) consists of two merging galaxies.
+\textit{B1608+656} (hereafter \textit{1608}) \cb{was first reported by \cite{1995ApJ...447L...5M}.
+It} consists of two merging galaxies.
 The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
@@
 The cluster shows a high density of galaxies close to the lens in a south-east direction.
+\cb{Two lensed images are closed in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.}
 
@@
 
-\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}, the only non early-type lens in this sample.
-With a redshift of just $z=0.04$, it is also the closest lens of the sample.
+\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
+With a redshift of just \cb{$z\sim0.04$} it is also the closest lens of the sample.
 Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
-However, this makes our stellar population synthesis model assumptions (i.e.
-that the stars are a simple stellar population) likely valid.
+\cb{This makes the treatment of the stellar populations easier, as derivations of M/L get complicated in the presence of star forming regions typical of disc galaxies.}
 
@@
 C and G denote a known cluster or group environment, respecitvely.
-The number in the brackets is the number of confirmed members.}
+The number in the brackets is the number of confirmed members.
+\cb{Ellipsis indicate isolated lens galaxies or such with unidentified environment.}}
     \label{tab:lensproperties}
@@
       0712 & ... & ...\\
-      0712 & ... & ...\\
+      0911 & $\Delta t_{BA}=146^{+4}_{-4}$ & Symm\\
       0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
@@
            & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-      2016 & ... & ...\\
+      2016 & ... & PixRad(16) \\
       2045 & ... & $\gamma(0.1)$, Symm \\
@@
 $\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
-`Symm' denotes that a point-symmetry prior is employed.}
+`Symm' denotes that a point-symmetry prior is employed.
+\cb{`PixRad(16)' indicates that the pixel radius was set to 16 pixels.}}
     \label{tab:lenspriors}
@@
   \includegraphics[width=.8\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$.
+  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $e_{dm}$ and the stellar component $e_{*}$.
 The wedges display the alignment of the semi-major axes of the components.
@@
 Firstly, the reconstructed dark matter distribution of all lenses considered here is rounder than the stellar distribution.
-Secondly, most lenses lie in the bottom-left corner: the dark matter distributions are typically quite round, while the stellar distributions can be rather elliptical.
-Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 1.6$).
+Secondly, most lenses lie in the bottom-left corner: the dark matter distributions \cb{have typically low eccentricities}, while the stellar distributions can be rather elliptical.
+Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar \cb{ellipticity ($e_* > 0.4$)}.
 At the same time, they show a very strong alignment between their dark matter and stellar distributions.
@@
 We suggest that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.
-Fourthly, notice that all dark matter and stellar distributions with weak shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim1.05$).
+Fourthly, notice that all dark matter and stellar distributions with weak shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost \cb{spherical ($e_{dm}\sim0.05$)}.
 By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
@@
 In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned system of all lenses studied here.
-This may be explained by its external shear ($\gamma \sim 0.1$) that likely owes to its group environment (see Table \ref{tab:lensproperties}).
-The lens {\it0414} is also interesting.
-It also shows strong misalignment, yet has no sign of a group or cluster environment reported to date.
+This may be explained by its external shear ($\gamma \sim 0.1$) \cb{emanating from its group environment} (see Table \ref{tab:lensproperties}).
+The lens {\it0414} \cb{also shows strong misalignment}, yet has no sign of a group or cluster environment reported to date.
 It does show rather strong external shear, however ($\gamma \sim 0.15$), suggesting that a group or cluster environment perhaps remains to be found.
@@
 We find that limiting the maximum shear $|\gamma|$ to 0.1 removes the extra images, though the lens then pushes on its maximum shear prior.
-We find that the mass map is robust against a stronger shear prior, and it thus again does not affect the alignment of the distributions.
-It produces dark matter distributions well-aligned with the stars.
-We believe that a strong shear prior for this particular lens is justified by the non-observation of the spurious extra images; none of the other lenses in our sample have a shape profile that is sensitive to our shear prior.
+We find that the mass map is robust against a stronger shear prior, and \cb{does not} affect the alignment of the distributions.
+\cb{It produces well-aligned dark matter and stellar distributions}.
+We believe that a strong shear prior for this particular lens is \cb{justified by the appearance of spurious extra images;} none of the other lenses in our sample \cb{are} sensitive to our shear prior.
 
 Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
-Most lenses show a $\sim$ constant shape with radius appearing similar to the results in Figure~\ref{fig:wedgesall}.
+\cb{Most lenses show an approximately constant shape} with radius appearing similar to the results in Figure~\ref{fig:wedgesall}.
 {\it0957} and to some degree {\it1422} display, however, some signs of isophotal twist (see also Appendix).
@@
 \section{Conclusions}\label{sec:conclusions}
-We have measured the shape and alignment of stars and dark matter in 11 strong lensing galaxies using a new non-parametric lens tool, \Glass.
-We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential, since these have data quality good enough to determine the projected shape of their dark matter halos \citep{2014arXiv1401.7990C}.
-We measured the shape and alignment using the eigenvalues $\lambda$ and vectors of the 2D moment of inertia tensor of the stars and dark matter, defining a {\it shape parameter} $s = \lambda_{\rm max}/\lambda_{\rm min}$ (\S\ref{sec:shapemethod}).
-We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+We have measured the shape and alignment of \cb{the stellar and dark matter distributions} in 11 \cb{lens systems} using a new non-parametric lens tool, \Glass.
+We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the \cb{central potential to determine} the projected shape of their dark matter halos \citep{2014arXiv1401.7990C}.
+We measured the shape and alignment using the eigenvalues $\lambda$ and vectors of the 2D moment of inertia tensor of the stars and dark matter, defining a {\it shape parameter} $e = 1 - \lambda_{\rm min}/\lambda_{\rm max}$ (\S\ref{sec:shapemethod}).
+We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
 
@@
 \item We found that in all cases the dark matter halos are rounder than the light distribution over the range $R_e < R < 5R_e$.
-As we average over larger radii, the lenses become increasingly elliptical in their stars and potentially dark matter, but dark matter halos are never more elliptical than $s_{dm} = 1.15$, while their stars can extend to $s_* > 1.4$.
+As we average over larger radii, the lenses\cb{, except the ones with a large stellar ellipticity,} become increasingly elliptical in their \cb{stellar distributions.
+The same trend can furthermore be seen for the dark matter, although the data are also consistent with no change in shape.
+The dark matter halos} are never more elliptical \cb{than $e_{dm} = 0.2$}, while their stars can extend \cb{to $e_* > 0.3$.}
 
-\item Three systems have very high stellar ellipticity ($s_* > 1.6$) and correspondingly high alignment between light and dark.
+\item Three systems have \cb{a high stellar ellipticity ($e_* > 0.45$)} and correspondingly high alignment between light and dark.
 One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.
 
-\item Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be highly misaligned.
+\item Galaxies with high dark matter ellipticity and weak external shear \cb{show strong alignment;} those with strong shear ($\gamma \simgt 0.1$) can be highly misaligned.
 This is reassuring since isolated misaligned galaxies are expected to be unstable.
@@
 
-Our results provide a new constraint on galaxy formation models that must explain the origin of very round dark matter halos (not expected in pure dark matter only simulations), and highly misaligned systems.
+Our results provide a new constraint on galaxy formation models that must explain the origin of \cb{low eccentricity} dark matter halos (not expected in pure dark matter only simulations), and highly misaligned systems.
 Such misalignments also present a new challenge for alternative gravity theories in which the light and dark must necessarily be highly correlated.
@@
 JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+DL's research is part of the project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n.
+259349.
 
@@
            & -0.804 & -0.156 & -0.292 & 0.307 \\
-      0712 & -0.013 & 0.795 & 0.747 & -0.391 \\
-           & -0.804 & -0.156 & -0.292 & 0.307 \\
+      0911 & 2.226 & -0.968 & -0.709 & -0.696 \\
+           & 0.278 & -0.105 & -0.507 & 0.439 \\
       0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 \\
@@
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
-The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence interval of these for the dark matter map.
-Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $s$), and the angle between the dark matter and stellar major axes.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence intervals of these for the dark matter map.
+Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $e$), and the angle between the dark matter and stellar major axes.
 Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.

### 2015-01-28 shapes/paper.tex
Updated draft

@@
 \usepackage{color}
+\usepackage{amssymb}
 
-% Some definitions of things I always use here:
-\def\ltsima{$\; \buildrel < \over \sim \;$}
-\def\simlt{\lower.5ex\hbox{\ltsima}}   
-\def\gtsima{$\; \buildrel > \over \sim \;$}
-\def\simgt{\lower.5ex\hbox{\gtsima}}
-
-%Code definition:
+% \def\ltsima{$\; \buildrel < \over \sim \;$}
+% \def\simlt{\lower.5ex\hbox{\ltsima}}
+% \def\gtsima{$\; \buildrel > \over \sim \;$}
+% \def\simgt{\lower.5ex\hbox{\gtsima}}
 \def\Glass{{\sc Glass}}
@@
 
-\title[Light versus Dark in \cb{Strong-Lens Galaxies}]{Light versus Dark in \cb{Strong-Lens Galaxies}: Dark matter halos that are rounder than their stars}
-% "Light versus dark matter in strong-lens galaxies: Dark matter halos may be rounder than their stellar distributions"
+\title[Light versus dark in strong-lens galaxies]{Light versus dark in strong-lens galaxies: Dark matter haloes that are rounder than their stars}
 
@@
 Jonathan Coles,$^{4}$
-Emilio E. Falco,$^{5}$
-Ignacio Ferreras$^{6}$ and
-Dominik Leier$^{7}$}\vspace{0.4cm}\\
-\parbox{\textwidth}{$^{1}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland\\
+\cb{Dominik Leier,$^{5}$
+Emilio E. Falco$^{6}$ and
+Ignacio Ferreras$^{7}$}}\vspace{0.4cm}\\
+\parbox{\textwidth}{$^{1}$Institute for Astronomy, Department of Physics, ETH Zurich, Wolfgang-Pauli-Strasse 27, 8093 Z\"urich, Switzerland\\
 $^{2}$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
-$^{3}$Institute for Theoretical Physics, University of Z\"urich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
+$^{3}$Institute for Theoretical Physics, University of Zurich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
 $^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
-$^{6}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{7}$Dipartimento di Fisica e Astronomia, Università di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy}}
+$^{5}$Dipartimento di Fisica e Astronomia, Universit\`{a} di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy\\
+$^{6}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
+$^{7}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK}}
 
@@
 \begin{abstract}
-We measure the shape and alignment of the stellar and dark matter mass distribution in 11 \cb{strong-lens galaxies}, finding in all cases that the dark matter halos are rounder than the stellar mass distribution over the range $R_e < R < 5R_e$.
-Averaging over larger radii, the lenses become increasingly elliptical both in their dark matter and stellar components, as defined \cb{using the ratio of the smallest to largest eigenvalues} of the 2D moment of inertia tensor of the projected \cb{lens mass}.
-While dark matter halos are never more elliptical \cb{than $e_{dm} = 0.3$}, their stars can extend \cb{to $e_* > 0.3$}.
-Three systems, in particular, \cb{have a high stellar ellipticity ($e_* > 0.4$)} and correspondingly high alignment between luminous and dark matter distribution.
-One of these -- B1608 -- is a known merging pair; we suggest that the other two (B0712 and B2016) may also be recent post-merger systems.
-Galaxies with high dark matter ellipticity and weak external shear show very strong alignment between light and dark; those with strong shear ($\gamma \simgt 0.1$) can be very highly misaligned.
+We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies, finding \cb{over the range of several multiples of the half-light radii} that the dark matter haloes are rounder than the stellar mass distributions.
+Averaging over larger radii, the \cb{ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components.} While dark matter haloes are never more elliptical than $e_{dm} = 0.3$, their stars can extend to $e_* > 0.3$.
+Three systems, in particular, have a high stellar ellipticity ($e_* > 0.4$) and correspondingly high alignment between luminous and dark matter distribution.
+One of these -- {\it B1608} -- is a known merging pair; we suggest that the other two ({\it B0712} and {\it B2016}) may also be recent post-merger systems.
+Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
 This is reassuring since isolated misaligned galaxies are expected to be unstable.
 
-Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter halos and highly misaligned \cb{strong-lens systems}.
-Such misalignments also present a new challenge for alternative gravity theories in which the stellar and dark matter components must necessarily be highly correlated.
+\cb{Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and \cb{misaligned} strong-lens systems.}
 
@@
 \begin{keywords}
-Gravitational lensing: strong --- galaxies: structure --- galaxies: haloes --- galaxies: formation --- galaxies: elliptical and lenticular, cD
+Gravitational lensing: strong -- galaxies: structure -- galaxies: haloes -- galaxies: formation -- galaxies: elliptical and lenticular, cD.
 \end{keywords}
@@
 
-The ellipticity and shape of the stellar component relative to their host dark matter halo encodes information both about our cosmological model ($\Lambda$CDM) and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
-`Dark-matter-only' (DMO) simulations in $\Lambda$CDM predict dark matter halos that are triaxial \citep{1991ApJ...378..496D,1992ApJ...399..405W,1996ApJ...462..563N,2002ApJ...574..538J}, with mean `shape parameter' $\langle q \rangle = (b+c)/2a \sim 0.8$ (where $a > b > c$ are the long, intermediate and short axes of the figure; \citealt{2007MNRAS.378...55M}).
+The ellipticity and shape of the stellar component relative to their host dark matter halo encodes information both about our \cb{current cosmological model $\Lambda$CDM} and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
+`Dark-matter-only' (DMO) simulations in $\Lambda$CDM predict dark matter haloes that are triaxial \citep{1991ApJ...378..496D,1992ApJ...399..405W,1996ApJ...462..563N,2002ApJ...574..538J}, with mean `shape parameter' $\langle q \rangle = (b+c)/2a \sim 0.8$ (where $a > b > c$ are the long, intermediate and short axes of the figure; \citealt{2007MNRAS.378...55M}).
 This corresponds to a typically {\it prolate} halo.
-However, including `baryons' (stars and gas) in the models produces halos that are significantly rounder and -- at least for disc galaxies -- well-aligned with the light distribution \citep{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}.
+However, including `baryons' (stars and gas) in the models produces haloes that are significantly rounder and -- at least for disc galaxies -- well-aligned with the light distribution \citep{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}.
 Halo shapes and alignments also constrain alternative gravity models \citep{2001MNRAS.327..552M,2004ApJ...610L..97H,2005MNRAS.361..971R,2012PhRvD..86h3507F,2013MNRAS.434.2971D}.
-If the visible light is the only source of gravity in a galaxy, then we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can at least in principle be broken.
+If the visible light is the only source of gravity in a galaxy, then we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can\cb{, at least in principle,} be broken.
 
@@
 For `red and dead' ellipticals that are largely devoid of gas, their baryonic content can be mapped through stellar population synthesis modelling of their light distribution alone \citep[e.g.][]{2005ApJ...623L...5F,2006ApJ...640..662T,2008MNRAS.383..857F}.
-Furthermore, such systems are dense enough to produce strong lensing \cb{effects}, opening up the possibility of directly comparing the light and mass in these galaxies \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
+Furthermore, such systems are dense enough to produce strong lensing effects, opening up the possibility of directly comparing the light and mass in these galaxies \citep{1998ApJ...509..561K,2008MNRAS.383..857F,2009ApJ...690..670T,2012A&A...538A..99S}.
 Previous work in the literature has found that the light and mass are well-aligned (though a mis-match of up to 10$^\circ$ is not uncommon; e.g.
@@
 \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
-They found that dark matter halos appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
-Both measurements are challenging however, and more recent data appear to be at odds with this early work, favouring dark matter halos that are more elliptical than their stellar mass component \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
+They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
+Both measurements are challenging however, and more recent data appear to be at odds with this early work\cb{, at least for galaxies in general.
+They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.}
 
 Recently, we introduced a new non-parametric lens tool, \Glass\ \citep{2014arXiv1401.7990C}.
-Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in \cb{lens systems} if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
+Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
 In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
-We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these \cb{lens galaxies}, for the first time.
+We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these lens galaxies, for the first time.
 This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter.
 Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution.
-Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter mass is always positive.
+Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter \cb{map} is always positive.
 
 This paper is organised as follows.
-In \S\ref{sec:glass}, we briefly review the \Glass\ code \cb{and define our method to assess shape and alignment of lens galaxies}.
+In \S\ref{sec:glass}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
 In \S\ref{sec:data}, we present our data compilation with references.
@@
 Rather, it calculates an ensemble of all allowed models given the data and assumed priors.
-In this context, `non-parametric' really just means that many more parameters than data constraints are used such that the system of equations describing the \cb{lensing mass} distribution is under-constrained.
+In this context, `non-parametric' really just means that many more parameters than data constraints are used such that the system of equations describing the lensing mass distribution is under-constrained.
 \Glass\ shares some aspects with an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
-Its key improvements upon \PixeLens{} which are relevant for this paper include:
+Its key improvements upon \PixeLens{} relevant for this paper include:
 
 \begin{enumerate}
-\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large ensembles of $>10,000$ models to be efficiently generated. 
+\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large ensembles of $\gtrsim$10,000 models to be efficiently generated. 
 \item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
@@
 
-In this paper, the default priors used to model each lens are listed below.  Table
-\ref{tab:lenspriors} identifies lenses for which we have modified these defaults.
-For each lens we assume:
+In this paper, the default priors used to model each lens are listed below. Table \ref{tab:lenspriors} identifies lenses for which we have modified these defaults. For each lens we assume:
 
@@
 \item A reconstructed stellar mass map as lower mass bounds in every pixel.
-\item The local density gradient \cb{always points within 50$^{\circ}$ of the center of the distribution,} and the slope is at most 0 everywhere.
-In other words, the density profile peaks in the center.
-\item The fixed cosmology $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
-\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1]$.
-\item \cb{The pixel radius is set to be 12 pixels.}
+\item The local density gradient always points within 50$^{\circ}$ of the centre of the distribution, \cb{and the slope is at least 0 everywhere.}
+\item \cb{The fixed, flat cosmology with matter density $\Omega_{m} = 0.28$, the dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.}
+\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
+\item \cb{The radius of the lens is set to be 12 pixels.}
 \end{enumerate}
@@
 \subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
-\cb{We employ a shape definition related to the definition used by \cite{2014arXiv1401.7990C}.
-The ellipticity parameter $e$ is defined as} %the ratio of the two eigenvalues $\lambda_2$ and $\lambda_1$, i.e.
+We employ a shape definition related to the definition used by \cite{2014arXiv1401.7990C}. The ellipticity parameter $e$ is defined as
 \begin{equation}\label{eq:shapeestimate}
-    e \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}}, \ \ \ \mathrm{where} \ \lambda_{1} \geq \lambda_{2},
+    e \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
 \end{equation}
-of the inertia tensor of a mass distribution $M(\boldsymbol{\theta})$
+\cb{where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues of the inertia tensor $I$ of the mass distribution $M(\boldsymbol{\theta})$. It is defined as}
 \begin{equation}\label{eq:inertiatensor}
@@
 We estimate the latter by reconstructing the total mass distribution with a lower mass prior from the stellar mass distribution and then subtracting the latter off.
-The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of the half-light radius $R_e$.
-\cb{$R_e$ is the half-light radius measured with respect to the Petrosian flux.} As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
+The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of \cb{$R_e$, defined as the half-light radius} measured with respect to the Petrosian flux.
+As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
 The shape estimates do not necessarily need to be the same within different radii -- e.g.
@@
 
-Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image.
-We generate in each case an ensemble of 10,000 mass models.
-\cb{Each of these models is analyzed individually, yielding a distribution of constrained quantities.}
+\cb{Throughout this paper, we generate in each case an ensemble of 10,000 mass models. Each of these models is analysed individually, yielding a distribution of constrained quantities.}
 
@@
 Stellar mass maps are taken from \cite{2011ApJ...740...97L}.
-In that work, the \cb{surface brightness distribution} of the galaxy images in all available HST bands was first fitted using using GALFIT v2.03b \citep{2002AJ....124..266P}, and the resulting \cb{flux} maps were used to obtain stellar mass maps using the synthesis of the stellar-population models of \cite{2003MNRAS.344.1000B}.
+In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \cite{2003MNRAS.344.1000B} were obtained.
 The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
-The IMF was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} \cb{but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
-We note that the effect of recent claims towards a non-universal IMF on stellar M/L is still under debate.
-While dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.}
+The \cb{initial mass function (IMF)} was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
+We note that the effect of recent claims towards a non-universal IMF on stellar \cb{mass-to-light ratio (M/L)} is still under debate.
+\cb{While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
+For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
+We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
+We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.}
+% also the lens system \textit{B1422+231} is incompatible with a Salpeter IMF.
+We will discuss constraints on different functional forms of the IMF and stellar M/L by strong-lens systems reconstructed non-parametrically with \Glass\ in a future publication.}
 
-\cb{The original sample we consider, is presented in \cite{2011ApJ...740...97L} and consists of 21 lens systems.
+The original sample we consider, is presented in \cite{2011ApJ...740...97L} and consists of 21 lens systems.
 It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
@@
 Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
-This leads to a sample of 11 lenses.
-We discuss each of these systems, next.}
+This \cb{yields a sample consisting} of 11 lenses.
+We discuss each of these systems, next.
 
@@
 A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
-It, however, is more likely a foreground object \cb{with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
-This is sufficiently distant to still contribute to the lensing effect.}
+It, however, is more likely a foreground object with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
+This is sufficiently distant to still contribute to the lensing effect.
 
-\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \cb{\citep{1998MNRAS.296..483J,1998AJ....115..377F}.
-There is a foreground group of about 10 member galaxies at $z\sim0.3$, which could affect the modelling \citep{2002AJ....123..627F}.}
+\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998MNRAS.296..483J,1998AJ....115..377F}.
+There is a foreground group of about 10 member galaxies at $z\sim0.3$, which could affect the modelling \citep{2002AJ....123..627F}.
 
-\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost \cb{spherical} early-type galaxy \cb{\citep{1997A&A...317L..13B,2012A&A...538A..99S}.} It has measured time delays \citep{2002ApJ...572L..11H}.
-It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}.
-X-ray emission can be detected and an analysis of which yields a temperature of 2.3 keV.
-There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
+\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
+\cb{It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.} There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
 
@@
 
-\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \cb{\citep{1980Natur.285..641W,2005ApJ...626...51Y}.} It has measured time delays \cb{\citep[see e.g.][]{1997ApJ...475L..85S}.} In this work\cb{, we} use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
+\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{1980Natur.285..641W,2005ApJ...626...51Y}.
+It has measured time delays \citep[see e.g.][]{1997ApJ...475L..85S}.
+In this work, we use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
 \cite{1997ApJ...489...21B}.
@@
 
-\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \cb{\citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.} Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}.
+\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.
+Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}.
 We choose therefore not to include them in the analysis.
 The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
-Using newer data, \cb{additional members} could be found \citep{2011ApJ...726...84W}.
+Using newer data, additional members could be \cb{identified} \citep{2011ApJ...726...84W}.
 \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
 
-\textit{B1608+656} (hereafter \textit{1608}) \cb{was first reported by \cite{1995ApJ...447L...5M}.
-It} consists of two merging galaxies.
+\textit{B1608+656} (hereafter \textit{1608}) was first reported by \cite{1995ApJ...447L...5M}.
+It consists of two merging galaxies.
 The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
 The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was found \citep{2006ApJ...642...30F}.
-No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
+The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was \cb{identified} \citep{2006ApJ...642...30F}.
+\cb{However, no} significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
 The data seem to indicate four other groups along the line of sight.
@@
 The cluster shows a high density of galaxies close to the lens in a south-east direction.
-\cb{Two lensed images are closed in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.}
+Two lensed images are \cb{very close} in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.
 
@@
 There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
-As the measurements are inconclusive, we choose to not include this satellite explicitly in our models.
+As the measurements are \cb{however} inconclusive, we choose to not include this satellite in our models.
 
 \textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
-With a redshift of just \cb{$z\sim0.04$} it is also the closest lens of the sample.
+With a redshift of just $z\sim0.04$ it is the closest lens \cb{system} of the sample.
 Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
-\cb{This makes the treatment of the stellar populations easier, as derivations of M/L get complicated in the presence of star forming regions typical of disc galaxies.}
+\cb{This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.}
 
@@
 References can be found in \S\ref{sec:data}.
-The columns are from left to right, the lens redshift $z_L$, the redshift of the source $z_S$, the maximum angular separation between two images $\Delta\theta$, the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$, and information on the environment of the lens.
+The columns are from left to right: the lens redshift $z_L$; the redshift of the source $z_S$; the maximum angular separation between two images $\Delta\theta$; the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$; and information on the environment of the lens.
 C and G denote a known cluster or group environment, respecitvely.
 The number in the brackets is the number of confirmed members.
-\cb{Ellipsis indicate isolated lens galaxies or such with unidentified environment.}}
+\cb{Ellipsis indicate lens galaxies with as of yet no detected environment.}}
     \label{tab:lensproperties}
@@
 
-% \begin{table*}
-%   \begin{center}
-%     \begin{tabular}{l r r r r l l}
-%       Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
-%       0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & \\
-%            & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
-%       0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & \\
-%            & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
-%       0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
-%            & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
-%       0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
-%            & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
-%       0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
-%            & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
-%       1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
-%            & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
-%       1422 & 1.079 & 0.357 & 0.742 & -0.205 & ... & Symm \\
-%            & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
-%       1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-%            & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
-%       2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & \\
-%            & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
-%       2045 & 1.121 & 1.409 & 1.255 & -0.507 & ... & $\gamma(0.1)$, Symm \\
-%            & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
-%       2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & \\
-%               & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
-%     \end{tabular}
-%     \caption[width=\linewidth]{The lens properties relevant for modelling the lenses are listed (positions and time delay information).
-The images are ordered in terms of arrival time (image A has the shortest arrival time, image D the longest).
-\newline $^{a}$ The source lensed by 0957 has different component.
-Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
-%     \label{tab:lensmodelling}
-%   \end{center}
-% \end{table*}
 \begin{table}
@@
     \caption[width=\linewidth]{Additional priors to the base set described in \S\ref{sec:glass} are listed.
-$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$.
-The images are defined in Table~\ref{tab:lenspositions}.
+$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$ \cb{between light from the images B and A.} The images are defined in Table~\ref{tab:lenspositions}.
 $\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
 `Symm' denotes that a point-symmetry prior is employed.
-\cb{`PixRad(16)' indicates that the pixel radius was set to 16 pixels.}}
+`PixRad(16)' indicates that the pixel radius was set to 16 pixels.}
     \label{tab:lenspriors}
@@
   \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $e_{dm}$ and the stellar component $e_{*}$.
-The wedges display the alignment of the semi-major axes of the components.
+The wedges \cb{show} the alignment of the semi-major axes of the components.
 In case of alignment of the semi-major axes (Aligned), the wedges are vertical.
 In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
-The opening angle displays the statiscal error in the shape estimate of the dark matter halo.
-Both the error in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within.
+The opening angle displays the statistical error in the shape estimate of the dark matter halo.
+Both the errors in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within.
 The lenses are additionally color-coded in terms of the required external shear in modelling the lens.}
@@
 
-Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark and stellar mass distributions.
-In this Figure, the full distribution up to the last-image radius $R_{L}$ is probed.
+Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark \cb{matter} and stellar mass distributions.
+In this Figure, the full distribution up to \cb{one pixel past the} last-image radius $R_{L}$ is probed.
 There are several key points to note.
 Firstly, the reconstructed dark matter distribution of all lenses considered here is rounder than the stellar distribution.
-Secondly, most lenses lie in the bottom-left corner: the dark matter distributions \cb{have typically low eccentricities}, while the stellar distributions can be rather elliptical.
-Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar \cb{ellipticity ($e_* > 0.4$)}.
-At the same time, they show a very strong alignment between their dark matter and stellar distributions.
+Secondly, most lenses lie in the bottom-left corner: the dark matter distributions have typically low eccentricities, while the stellar distributions can be rather elliptical.
+Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($e_* > 0.4$).
+At the same time, they show a very strong alignment between their \cb{stellar and dark matter} distributions.
 One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}.
 We suggest that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.
-Fourthly, notice that all dark matter and stellar distributions with weak shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost \cb{spherical ($e_{dm}\sim0.05$)}.
+
+Fourthly, notice that all dark matter and stellar distributions with weak \cb{external} shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.05$).
 By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
 The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
-Two systems stand out from the rest, however.
-In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned system of all lenses studied here.
-This may be explained by its external shear ($\gamma \sim 0.1$) \cb{emanating from its group environment} (see Table \ref{tab:lensproperties}).
-The lens {\it0414} \cb{also shows strong misalignment}, yet has no sign of a group or cluster environment reported to date.
+\cb{As described furthermore in \S\ref{sec:data}, {\it1422} is challenging system to model the stellar distribution.} {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
+Besides these three lens systems, one stands out from the rest, however.} In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned \cb{(anti-aligned) lens} system of all lenses studied here.
+This may be explained by its external shear ($\gamma \sim 0.1$) emanating from its group environment (see Table \ref{tab:lensproperties}).
+%The lens {\it0414} also shows strong misalignment, yet has no sign of a group or cluster environment reported to date.
 It does show rather strong external shear, however ($\gamma \sim 0.15$), suggesting that a group or cluster environment perhaps remains to be found.
@@
 We find that limiting the maximum shear $|\gamma|$ to 0.1 removes the extra images, though the lens then pushes on its maximum shear prior.
-We find that the mass map is robust against a stronger shear prior, and \cb{does not} affect the alignment of the distributions.
-\cb{It produces well-aligned dark matter and stellar distributions}.
-We believe that a strong shear prior for this particular lens is \cb{justified by the appearance of spurious extra images;} none of the other lenses in our sample \cb{are} sensitive to our shear prior.
+We find that the mass map is robust against a stronger shear prior, and does not affect the alignment of the distributions.
+It produces well-aligned dark matter and stellar distributions.
+We believe that a strong shear prior for this particular lens is justified by the appearance of spurious extra images \cb{if higher shear is allowed.} %; none of the other lenses in our sample are sensitive to our shear prior.
 
-Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
-\cb{Most lenses show an approximately constant shape} with radius appearing similar to the results in Figure~\ref{fig:wedgesall}.
+% Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
+Most lenses show an approximately constant shape with radius appearing similar to the results in Figure~\ref{fig:wedgesall}.
 {\it0957} and to some degree {\it1422} display, however, some signs of isophotal twist (see also Appendix).
 Additionally, there appears to be a trend that the ellipticity of the stars and potentially of the dark matter (though the latter is consistent with constant ellipticity) increases with increasing radius.
+Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
+\cb{There appears to be a trend that the ellipticity of the stellar distribution and increases with increasing radius the shape estimate is averaged within.
+There is potentially a similar trend for the dark matter distribution, although the samples are also consistent with a constant ellipticity.} {\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist \cb{complicating the interpretation (see also Appendix).}
 
 \section{Conclusions}\label{sec:conclusions}
-We have measured the shape and alignment of \cb{the stellar and dark matter distributions} in 11 \cb{lens systems} using a new non-parametric lens tool, \Glass.
-We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the \cb{central potential to determine} the projected shape of their dark matter halos \citep{2014arXiv1401.7990C}.
-We measured the shape and alignment using the eigenvalues $\lambda$ and vectors of the 2D moment of inertia tensor of the stars and dark matter, defining a {\it shape parameter} $e = 1 - \lambda_{\rm min}/\lambda_{\rm max}$ (\S\ref{sec:shapemethod}).
-We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
+We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014arXiv1401.7990C}.
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the \cb{stellar and dark matter distributions}, defining a {\it shape parameter} $e = 1 - \lambda_{2}/\lambda_{1}$ \cb{($\lambda_{1} \geq \lambda_{2}$; \S\ref{sec:shapemethod}).} We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
 
@@
 \begin{itemize}
-\item We found that in all cases the dark matter halos are rounder than the light distribution over the range $R_e < R < 5R_e$.
-As we average over larger radii, the lenses\cb{, except the ones with a large stellar ellipticity,} become increasingly elliptical in their \cb{stellar distributions.
+\item \cb{We found that the dark matter haloes} are rounder than the light distribution over the range $R_e < R < 5R_e$.
+As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions.
 The same trend can furthermore be seen for the dark matter, although the data are also consistent with no change in shape.
-The dark matter halos} are never more elliptical \cb{than $e_{dm} = 0.2$}, while their stars can extend \cb{to $e_* > 0.3$.}
+The dark matter haloes are never more elliptical than $e_{dm} = 0.2$, while their stars can extend to $e_* > 0.3$.
 
-\item Three systems have \cb{a high stellar ellipticity ($e_* > 0.45$)} and correspondingly high alignment between light and dark.
+\item Three systems have a high stellar ellipticity ($e_* > 0.45$) and correspondingly high alignment between light and dark.
 One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.
 
-\item Galaxies with high dark matter ellipticity and weak external shear \cb{show strong alignment;} those with strong shear ($\gamma \simgt 0.1$) can be highly misaligned.
+\item Galaxies with high dark matter ellipticity and weak external shear show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
 This is reassuring since isolated misaligned galaxies are expected to be unstable.
@@
 
-Our results provide a new constraint on galaxy formation models that must explain the origin of \cb{low eccentricity} dark matter halos (not expected in pure dark matter only simulations), and highly misaligned systems.
-Such misalignments also present a new challenge for alternative gravity theories in which the light and dark must necessarily be highly correlated.
+\cb{Our results provide a new constraint on galaxy formation models that must explain the origin of low eccentricity dark matter haloes (not expected in pure dark matter only simulations), and highly misaligned systems.
+A possible remedy is the fact that we constrain 2D projections of the lensing mass and the light distribution integrated along the line of sight.
+Such misalignments we find also present a new challenge for those alternative gravity theories in which the light is the only source of gravity in a galaxy, where light and dark must necessarily be highly correlated.}
 
 \section{Acknowledgements}\label{sec:acknowledgements}
-JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+\cb{We thank Simon Birrer for useful discussion.} JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
 DL's research is part of the project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n.
@@
     \end{tabular}
-    \caption[width=\linewidth]{The image positions of all the systems in order of arrival time (image A has the shortest arrival time, image D the longest) are listed.
-The positions are relative to the center of the lens galaxy.
+    \caption[width=\linewidth]{The image positions of all the systems \cb{are listed in order of arrival time (image A has the shortest arrival time, image D the longest).} The positions are relative to the centre of the lens galaxy.
 The first row contains the RA coordinate, the second the DEC coordinate of the image.
-\newline $^{a}$ The source lensed by 0957 has different component.
-Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
+\newline $^{a}$ The source lensed by {\it0957} has a second component.
+Images A and B are a double associated with the main galaxy component, images C and D with the lensed substructure.}
     \label{tab:lenspositions}
@@
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
-The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence intervals of these for the dark matter map.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines \cb{denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within}.
 Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $e$), and the angle between the dark matter and stellar major axes.

### 2015-01-29 shapes/paper.tex
very minor edits

@@
 Justin I. Read,$^{1,2}$
-Prasenjit Saha,$^{3}$
-Jonathan Coles,$^{4}$
-\cb{Dominik Leier,$^{5}$
-Emilio E. Falco$^{6}$ and
-Ignacio Ferreras$^{7}$}}\vspace{0.4cm}\\
+Jonathan Coles,$^{3}$
+\cb{Dominik Leier,$^{4}$
+Emilio E. Falco,$^{5}$
+Ignacio Ferreras$^{6}$} and
+Prasenjit Saha,$^{7}$}\vspace{0.4cm}\\
 \parbox{\textwidth}{$^{1}$Institute for Astronomy, Department of Physics, ETH Zurich, Wolfgang-Pauli-Strasse 27, 8093 Z\"urich, Switzerland\\
 $^{2}$Department of Physics, University of Surrey, Guildford, GU2 7XH, UK\\
-$^{3}$Institute for Theoretical Physics, University of Zurich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Dipartimento di Fisica e Astronomia, Universit\`{a} di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy\\
-$^{6}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
-$^{7}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK}}
+$^{3}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
+$^{4}$Dipartimento di Fisica e Astronomia, Universit\`{a} di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy\\
+$^{5}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
+$^{6}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
+$^{7}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}}
 
@@
 Three systems, in particular, have a high stellar ellipticity ($e_* > 0.4$) and correspondingly high alignment between luminous and dark matter distribution.
-One of these -- {\it B1608} -- is a known merging pair; we suggest that the other two ({\it B0712} and {\it B2016}) may also be recent post-merger systems.
+One of these -- {\it B1608+656} -- is a known merging pair; we suggest that the other two ({\it B0712+472} and {\it B2016+112}) may also be recent post-merger systems.
 Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
@@
 Halo shapes and alignments also constrain alternative gravity models \citep{2001MNRAS.327..552M,2004ApJ...610L..97H,2005MNRAS.361..971R,2012PhRvD..86h3507F,2013MNRAS.434.2971D}.
-If the visible light is the only source of gravity in a galaxy, then we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can\cb{, at least in principle,} be broken.
+If stars dominate the mass of the galaxy, we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can\cb{, at least in principle,} be broken.
 
@@
 
-Recently, we introduced a new non-parametric lens tool, \Glass\ \citep{2014arXiv1401.7990C}.
+Recently \cite{2014arXiv1401.7990C} introduced a new non-parametric lens tool, \Glass.
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
@@
 \item A reconstructed stellar mass map as lower mass bounds in every pixel.
-\item The local density gradient always points within 50$^{\circ}$ of the centre of the distribution, \cb{and the slope is at least 0 everywhere.}
+\item The local density gradient always points within 50$^{\circ}$ of the centre of the distribution, and the circularly-averaged density never increases outwards.
 \item \cb{The fixed, flat cosmology with matter density $\Omega_{m} = 0.28$, the dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.}
@@
 It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
-As shown in \citep{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
+As shown in \cite{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
 Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
@@
 \textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.
-Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}.
-We choose therefore not to include them in the analysis.
+Although time delays have been reported \citep{2001MNRAS.326.1403P}, it is possible that the measurements are aliases of the actual values \citep{2003AJ....126...29R} and hence are not included in our analysis.
 The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
@@
 The number in the brackets is the number of confirmed members.
-\cb{Ellipsis indicate lens galaxies with as of yet no detected environment.}}
+\cb{Ellipsis indicate lens galaxies with no group members identified so far.}}
     \label{tab:lensproperties}
@@
 The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
-\cb{As described furthermore in \S\ref{sec:data}, {\it1422} is challenging system to model the stellar distribution.} {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
-Besides these three lens systems, one stands out from the rest, however.} In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned \cb{(anti-aligned) lens} system of all lenses studied here.
+\cb{As described furthermore in \S\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.} {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
+Besides these three lens systems, one stands out from the rest, however.
+In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned \cb{(anti-aligned) lens} system of all lenses studied here.
 This may be explained by its external shear ($\gamma \sim 0.1$) emanating from its group environment (see Table \ref{tab:lensproperties}).

### 2015-01-30 shapes/paper.tex
Paper submitted

@@
 
-% \def\ltsima{$\; \buildrel < \over \sim \;$}
-% \def\simlt{\lower.5ex\hbox{\ltsima}}
-% \def\gtsima{$\; \buildrel > \over \sim \;$}
-% \def\simgt{\lower.5ex\hbox{\gtsima}}
 \def\Glass{{\sc Glass}}
 \def\PixeLens{{\sc PixeLens}}
-\newcommand{\cb}[1]{{\color{red} \textbf{#1}}}
 
@@
 Justin I. Read,$^{1,2}$
-Jonathan Coles,$^{3}$
-\cb{Dominik Leier,$^{4}$
-Emilio E. Falco,$^{5}$
-Ignacio Ferreras$^{6}$} and
-Prasenjit Saha,$^{7}$}\vspace{0.4cm}\\
+Jonathan P. Coles,$^{3,4}$
+Dominik Leier,$^{5}$
+Emilio E. Falco,$^{6}$
+Ignacio Ferreras$^{7}$ and
+Prasenjit Saha$^{4,8}$}\vspace{0.4cm}\\
 \parbox{\textwidth}{$^{1}$Institute for Astronomy, Department of Physics, ETH Zurich, Wolfgang-Pauli-Strasse 27, 8093 Z\"urich, Switzerland\\
@@
 $^{3}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{4}$Dipartimento di Fisica e Astronomia, Universit\`{a} di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy\\
-$^{5}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
-$^{6}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{7}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}}
+$^{4}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland\\
+$^{5}$Dipartimento di Fisica e Astronomia, Universit\`{a} di Bologna, viale Berti Pichat 6/2, 40127, Bologna, Italy\\
+$^{6}$Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA\\
+$^{7}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
+$^{8}$Institute for Computational Science, University of Zurich, Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}}
 
@@
 \begin{abstract}
-We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies, finding \cb{over the range of several multiples of the half-light radii} that the dark matter haloes are rounder than the stellar mass distributions.
-Averaging over larger radii, the \cb{ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components.} While dark matter haloes are never more elliptical than $e_{dm} = 0.3$, their stars can extend to $e_* > 0.3$.
-Three systems, in particular, have a high stellar ellipticity ($e_* > 0.4$) and correspondingly high alignment between luminous and dark matter distribution.
+We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies, finding over the range of several multiples of the half-light radii that the dark matter haloes are rounder than the stellar mass distributions.
+Averaging over larger radii, the ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components.
+While dark matter haloes are never more elliptical than $e_{dm} = 0.3$, their stars can extend to $e_* > 0.3$.
+Three systems, in particular, have a high stellar ellipticity ($e_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution.
 One of these -- {\it B1608+656} -- is a known merging pair; we suggest that the other two ({\it B0712+472} and {\it B2016+112}) may also be recent post-merger systems.
@@
 
-\cb{Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and \cb{misaligned} strong-lens systems.}
+Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
 
@@
 
-The ellipticity and shape of the stellar component relative to their host dark matter halo encodes information both about our \cb{current cosmological model $\Lambda$CDM} and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
+The ellipticity and shape of the stellar component relative to their host dark matter halo encodes information both about our current cosmological model $\Lambda$CDM and galaxy formation \citep[e.g.][]{1994ApJ...431..617D,2001ApJ...551..294I,2004ApJ...611L..73K,2007MNRAS.378...55M,2007arXiv0707.0737D,2012MNRAS.424L..16L,2014JPhG...41f3101R}.
 `Dark-matter-only' (DMO) simulations in $\Lambda$CDM predict dark matter haloes that are triaxial \citep{1991ApJ...378..496D,1992ApJ...399..405W,1996ApJ...462..563N,2002ApJ...574..538J}, with mean `shape parameter' $\langle q \rangle = (b+c)/2a \sim 0.8$ (where $a > b > c$ are the long, intermediate and short axes of the figure; \citealt{2007MNRAS.378...55M}).
@@
 Halo shapes and alignments also constrain alternative gravity models \citep{2001MNRAS.327..552M,2004ApJ...610L..97H,2005MNRAS.361..971R,2012PhRvD..86h3507F,2013MNRAS.434.2971D}.
-If stars dominate the mass of the galaxy, we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can\cb{, at least in principle,} be broken.
+If stars dominate the mass of the galaxy, we expect the light and mass distribution to be highly correlated; if dark matter is present, however, such correlations can, at least in principle, be broken.
 
@@
 They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
-Both measurements are challenging however, and more recent data appear to be at odds with this early work\cb{, at least for galaxies in general.
-They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.}
+Both measurements are challenging however, and more recent data appear to be at odds with this early work, at least for galaxies in general.
+They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
 
-Recently \cite{2014arXiv1401.7990C} introduced a new non-parametric lens tool, \Glass.
+Recently, \cite{2014arXiv1401.7990C} introduced a new non-parametric lens tool, \Glass.
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
@@
 Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution.
-Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter \cb{map} is always positive.
+Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter map is always positive.
 
@@
 \begin{enumerate}
-\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L}. This allows for large ensembles of $\gtrsim$10,000 models to be efficiently generated. 
+\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} is employed. This allows for large ensembles of $\gtrsim$10,000 models to be efficiently generated. 
 \item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
@@
 \item Observational priors (redshifts, image positions relative to lens position).
-\item Image parity is enforced.
-\item A reconstructed stellar mass map as lower mass bounds in every pixel.
-\item The local density gradient always points within 50$^{\circ}$ of the centre of the distribution, and the circularly-averaged density never increases outwards.
-\item \cb{The fixed, flat cosmology with matter density $\Omega_{m} = 0.28$, the dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.}
+\item Image parity to be enforced.
+\item A reconstructed stellar mass map that provides a lower mass bound to each pixel.
+\item The local density gradient to be always pointing within 50$^{\circ}$ of the centre of the distribution, and the circularly-averaged density to never increase outwards.
+\item The fixed, flat cosmology with matter density $\Omega_{m} = 0.28$, the dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.
 \item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
-\item \cb{The radius of the lens is set to be 12 pixels.}
+\item The radius of the lens to be set to 12 pixels.
 \end{enumerate}
@@
 \item[(viii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
-\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$, where the surface mass profile can be assumed to be symmetric ((3+1)-quad configurations and the double \textit{Q0957}).
+\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$, where the surface mass profile can be assumed to be symmetric ((3+1)-quad configurations and the double \textit{Q0957+561}).
 
@@
 \end{equation}
-\cb{where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues of the inertia tensor $I$ of the mass distribution $M(\boldsymbol{\theta})$. It is defined as}
+where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues of the inertia tensor $I$ of the mass distribution $M(\boldsymbol{\theta})$. It is defined as
 \begin{equation}\label{eq:inertiatensor}
@@
 We estimate the latter by reconstructing the total mass distribution with a lower mass prior from the stellar mass distribution and then subtracting the latter off.
-The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of \cb{$R_e$, defined as the half-light radius} measured with respect to the Petrosian flux.
+The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of $R_e$, defined as the half-light radius measured with respect to the Petrosian flux.
 As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
@@
 
-\cb{Throughout this paper, we generate in each case an ensemble of 10,000 mass models. Each of these models is analysed individually, yielding a distribution of constrained quantities.}
+Throughout this paper, we generate in each case an ensemble of 10,000 mass models. Each of these models is analysed individually, yielding a distribution of constrained quantities.
 
@@
 The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
-The \cb{initial mass function (IMF)} was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
-We note that the effect of recent claims towards a non-universal IMF on stellar \cb{mass-to-light ratio (M/L)} is still under debate.
-\cb{While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
+The initial mass function (IMF) was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
+We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
+While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
 For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
 We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
-We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.}
-% also the lens system \textit{B1422+231} is incompatible with a Salpeter IMF.
-We will discuss constraints on different functional forms of the IMF and stellar M/L by strong-lens systems reconstructed non-parametrically with \Glass\ in a future publication.}
+We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
 
@@
 Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
-This \cb{yields a sample consisting} of 11 lenses.
+This yields a sample consisting of 11 lenses.
 We discuss each of these systems, next.
@@
 \textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
-\cb{It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.} There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
+It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
+There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
 
@@
 The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
-Using newer data, additional members could be \cb{identified} \citep{2011ApJ...726...84W}.
+Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
 \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
@@
 The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was \cb{identified} \citep{2006ApJ...642...30F}.
-\cb{However, no} significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
+The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
+However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
 The data seem to indicate four other groups along the line of sight.
@@
 The cluster shows a high density of galaxies close to the lens in a south-east direction.
-Two lensed images are \cb{very close} in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.
+Two lensed images are very close in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.
 
@@
 There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
-As the measurements are \cb{however} inconclusive, we choose to not include this satellite in our models.
+As the measurements are however inconclusive, we choose to not include this satellite in our models.
 
 \textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
-With a redshift of just $z\sim0.04$ it is the closest lens \cb{system} of the sample.
+With a redshift of just $z\sim0.04$ it is the closest lens system of the sample.
 Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
-\cb{This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.}
+This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.
 
@@
 The number in the brackets is the number of confirmed members.
-\cb{Ellipsis indicate lens galaxies with no group members identified so far.}}
+Ellipsis indicate lens galaxies with no group members identified so far.}
     \label{tab:lensproperties}
@@
     \caption[width=\linewidth]{Additional priors to the base set described in \S\ref{sec:glass} are listed.
-$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$ \cb{between light from the images B and A.} The images are defined in Table~\ref{tab:lenspositions}.
+$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$ between light from the images B and A.
+The images are defined in Table~\ref{tab:lenspositions}.
 $\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
@@
   \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $e_{dm}$ and the stellar component $e_{*}$.
-The wedges \cb{show} the alignment of the semi-major axes of the components.
+The wedges show the alignment of the semi-major axes of the components.
 In case of alignment of the semi-major axes (Aligned), the wedges are vertical.
@@
 
-Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark \cb{matter} and stellar mass distributions.
-In this Figure, the full distribution up to \cb{one pixel past the} last-image radius $R_{L}$ is probed.
+Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions.
+In this Figure, the full distribution up to one pixel past the last-image radius $R_{L}$ is probed.
 There are several key points to note.
@@
 Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($e_* > 0.4$).
-At the same time, they show a very strong alignment between their \cb{stellar and dark matter} distributions.
+At the same time, they show a very strong alignment between their stellar and dark matter distributions.
 One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}.
@@
 
-Fourthly, notice that all dark matter and stellar distributions with weak \cb{external} shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.05$).
+Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.05$).
 By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
 The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
-\cb{As described furthermore in \S\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.} {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
+As described furthermore in \S\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
+{\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
 Besides these three lens systems, one stands out from the rest, however.
-In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned \cb{(anti-aligned) lens} system of all lenses studied here.
+In {\it1115}, the semi-major axis of the dark matter seems to be aligned with the semi-minor axis of the stellar component; it is the most strongly misaligned (anti-aligned) lens system of all lenses studied here.
 This may be explained by its external shear ($\gamma \sim 0.1$) emanating from its group environment (see Table \ref{tab:lensproperties}).
-%The lens {\it0414} also shows strong misalignment, yet has no sign of a group or cluster environment reported to date.
-It does show rather strong external shear, however ($\gamma \sim 0.15$), suggesting that a group or cluster environment perhaps remains to be found.
 
@@
 It produces well-aligned dark matter and stellar distributions.
-We believe that a strong shear prior for this particular lens is justified by the appearance of spurious extra images \cb{if higher shear is allowed.} %; none of the other lenses in our sample are sensitive to our shear prior.
+We believe that a strong shear prior for this particular lens is justified by the appearance of spurious extra images if higher shear is allowed.
 
-% Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
-Most lenses show an approximately constant shape with radius appearing similar to the results in Figure~\ref{fig:wedgesall}.
-{\it0957} and to some degree {\it1422} display, however, some signs of isophotal twist (see also Appendix).
-Additionally, there appears to be a trend that the ellipticity of the stars and potentially of the dark matter (though the latter is consistent with constant ellipticity) increases with increasing radius.
 Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
-\cb{There appears to be a trend that the ellipticity of the stellar distribution and increases with increasing radius the shape estimate is averaged within.
-There is potentially a similar trend for the dark matter distribution, although the samples are also consistent with a constant ellipticity.} {\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist \cb{complicating the interpretation (see also Appendix).}
+There appears to be a trend that the ellipticity of the stellar distribution increases with increasing radius of enclosure.
+There is potentially a similar trend for the dark matter distribution, although the samples are also consistent with a constant ellipticity.
+{\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see also Appendix).
 
@@
 We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014arXiv1401.7990C}.
-We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the \cb{stellar and dark matter distributions}, defining a {\it shape parameter} $e = 1 - \lambda_{2}/\lambda_{1}$ \cb{($\lambda_{1} \geq \lambda_{2}$; \S\ref{sec:shapemethod}).} We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $e = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see \S\ref{sec:shapemethod}).
+We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
 
@@
 \begin{itemize}
-\item \cb{We found that the dark matter haloes} are rounder than the light distribution over the range $R_e < R < 5R_e$.
+\item We found that the dark matter haloes are rounder than the light distribution over the range $1R_e < R < 5R_e$.
 As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions.
@@
 
-\cb{Our results provide a new constraint on galaxy formation models that must explain the origin of low eccentricity dark matter haloes (not expected in pure dark matter only simulations), and highly misaligned systems.
+Our results provide a new constraint on galaxy formation models that must explain the origin of low eccentricity dark matter haloes (not expected in pure dark-matter-only simulations), and highly misaligned lens systems.
 A possible remedy is the fact that we constrain 2D projections of the lensing mass and the light distribution integrated along the line of sight.
-Such misalignments we find also present a new challenge for those alternative gravity theories in which the light is the only source of gravity in a galaxy, where light and dark must necessarily be highly correlated.}
+The misalignments we identified also present a new challenge for those alternative gravity theories in which the light is the only source of gravity in a galaxy, where light and dark must necessarily be highly correlated.
 
 \section{Acknowledgements}\label{sec:acknowledgements}
-\cb{We thank Simon Birrer for useful discussion.} JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
+We thank Simon Birrer for useful discussion.
+JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
 DL's research is part of the project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n.
@@
     \end{tabular}
-    \caption[width=\linewidth]{The image positions of all the systems \cb{are listed in order of arrival time (image A has the shortest arrival time, image D the longest).} The positions are relative to the centre of the lens galaxy.
+    \caption[width=\linewidth]{The image positions of all the systems are listed in order of arrival time (image A has the shortest arrival time, image D the longest).
+The positions are relative to the centre of the lens galaxy.
 The first row contains the RA coordinate, the second the DEC coordinate of the image.
@@
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
-The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines \cb{denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within}.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within.
 Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $e$), and the angle between the dark matter and stellar major axes.

### 2015-06-22 shapes/paper.tex
edited lens-models section

@@
 \usepackage{graphicx}
-\usepackage{ulem}
+\usepackage[normalem]{ulem}
 \usepackage{amsmath}
@@
 
-Recently, \cite{2014arXiv1401.7990C} introduced a new non-parametric lens tool, \Glass.
+Recently, \cite{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass.
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
@@
 This paper is organised as follows.
-In \S\ref{sec:glass}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
+In \S\ref{sec:shapemethod}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
 In \S\ref{sec:data}, we present our data compilation with references.
@@
 
-\section{\Glass: A non-parametric lens tool}\label{sec:glass}
+\section{The lens models}\label{sec:shapemethod}
 
-\Glass\ is a new `non-parametric' gravitational lens modelling framework \citep{2014arXiv1401.7990C} that generates a distribution of mass models given a set of basic assumptions, or priors.
-Hence, \Glass\ does not yield the most probable mass model.
-Rather, it calculates an ensemble of all allowed models given the data and assumed priors.
-In this context, `non-parametric' really just means that many more parameters than data constraints are used such that the system of equations describing the lensing mass distribution is under-constrained.
-\Glass\ shares some aspects with an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
-Its key improvements upon \PixeLens{} relevant for this paper include:
+While it is possible to compute shape parameters for a lensing galaxy
+by fitting to a parametric shape to the lens, it would make the
+definition of a shape estimate dependent on the which parametric form
+was being used.  Moreover, the commonly-used parametric forms for
+modelling lensing galaxies \citep[see e.g.,][]{2001astro.ph..2341K} do
+not allow for features like twisting isodensity contours, which can
+arise from projection of triaxial ellipsoids with no intrinsic twists
+\citep[e.g.][and references therein]{1978ComAp...8...27B}.  To avoid
+these problems, we use non-parametric ellipticity estimators, defined
+as follows.
 
-\begin{enumerate}
-\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} is employed. This allows for large ensembles of $\gtrsim$10,000 models to be efficiently generated. 
-\item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
-\item The central region of the mass map can have a higher resolution to more efficiently capture steep models.
-\item Stellar density can be used as an additional lower-bound constraint on the models. 
-\end{enumerate}
-
-In this paper, the default priors used to model each lens are listed below. Table \ref{tab:lenspriors} identifies lenses for which we have modified these defaults. For each lens we assume:
-
-\begin{enumerate} 
-\item Observational priors (redshifts, image positions relative to lens position).
-\item Image parity to be enforced.
-\item A reconstructed stellar mass map that provides a lower mass bound to each pixel.
-\item The local density gradient to be always pointing within 50$^{\circ}$ of the centre of the distribution, and the circularly-averaged density to never increase outwards.
-\item The fixed, flat cosmology with matter density $\Omega_{m} = 0.28$, the dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.
-\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
-\item The radius of the lens to be set to 12 pixels.
-\end{enumerate}
-
-In cases where more information is available, the following priors are also used:
-
-\begin{enumerate}
-\item[(viii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
-\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$, where the surface mass profile can be assumed to be symmetric ((3+1)-quad configurations and the double \textit{Q0957+561}).
-
-\end{enumerate}
-
-\subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
-We employ a shape definition related to the definition used by \cite{2014arXiv1401.7990C}. The ellipticity parameter $e$ is defined as
+Lenses are modelled as free-form mass distributions, consisting of
+mass tiles or pixels.  Such lens models are also called
+non-parametric, which really just means that many more parameters than
+data constraints are used.  Thus the lens models are non-unique, and
+hence in fact ensembles of these free-form mass distributions are
+used.  From such a mass map, an inertia tensor is defined as
+\begin{equation}\label{eq:inertiatensor}
+\begin{pmatrix}
+ \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
+-\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x}
+\end{pmatrix}
+\end{equation}
+where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the
+mass in a pixel.  The eigenvectors of this inertia tensor give the
+ellipticity axes, and our ellipticity estimator is
 \begin{equation}\label{eq:shapeestimate}
@@
 \end{equation}
-where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues of the inertia tensor $I$ of the mass distribution $M(\boldsymbol{\theta})$. It is defined as
-\begin{equation}\label{eq:inertiatensor}
-    I = \begin{pmatrix} \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
-                        -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x} \end{pmatrix}.
-\end{equation}
-We use these estimators to quantify the shape of the stellar mass distribution and the dark matter distribution.
-We estimate the latter by reconstructing the total mass distribution with a lower mass prior from the stellar mass distribution and then subtracting the latter off.
-The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of $R_e$, defined as the half-light radius measured with respect to the Petrosian flux.
-As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
-The shape estimates do not necessarily need to be the same within different radii -- e.g.
-effects such as isophotal twist \citep[e.g.][and references therein]{1978ComAp...8...27B} can cause differences in the shape estimates between the central and the outer parts of the system.
+where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$)
+are the eigenvalues.  We use this ellipticity estimators to quantify
+the shapes both of the stellar-mass distribution and of the
+dark-matter distribution.  For the dark matter, only the mass
+distribution out to the radius of the outermost image is used; for the
+stellar part, the distribution with within different multiples of
+$R_e$ (defined as the half-light radius measured with respect to the
+Petrosian flux) is used.  It is necessary to have a cutoff for the
+regions used to compute the inertia tensor, or else it would be
+dominated by the outer regions where there is little information.  The
+mass pixels used in this work are at most 4\% of the diameter of the
+the full mass map.  The central region has smaller pixels, to allow
+for a density cusp at the centre.  Each model ensemble had $10^4$
+models.
 
-Throughout this paper, we generate in each case an ensemble of 10,000 mass models. Each of these models is analysed individually, yielding a distribution of constrained quantities.
+The non-parametric mass models themselves are constructed using the
+\Glass\ framework for modelling multiple-image lenses
+\citep{2014MNRAS.445.2181C}.  \Glass\ produces ensembles of mass maps,
+each of which reproduces exactly the observed image positions and
+image parities; also time delays, if measured.  The lensing data must
+be in the form of point images, which could be quasars or simply
+point-like features in otherwise extended images, but this was not a
+problem for the lenses studied in this work.  The estimated stellar
+mass (explained below in Section~\ref{sec:data}) is taken as a lower
+limit on the total mass.  The additional mass that needs to be put on
+top, in order to reproduce the lensing observables, is interpreted as
+dark matter.  (Some of that mass may actually be gas, but very little
+is expected in the early-type galaxies used in this work.)  The
+criteria of lensing observables and non-negative dark matter by
+themselves would leave the mass distribution too under-determined.
+Hence, an additional prior is used, requiring the mass distribution to
+be centrally concentrated, with the same centre as the galaxy light
+(but not necessarily the shape shape).  The precise formulation of the
+prior is given in Section~3 of \cite{2014MNRAS.445.2181C}.  Tests of
+how well the shape estimator can be recovered from lensing data are
+given in Section~5.2 and Figure~8 of that paper.
+
+We remark that \Glass\ is closely related to an earlier code
+\PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a
+completely different code base.  An important improvement is a better
+sampling algorithm for high dimensional spaces
+\citep{2012MNRAS.425.3077L} that eliminates the excessive weight
+\PixeLens\ tended to give to extreme models. \Glass\ has also been
+adapted for lens modelling in citizen science
+\citep{2015MNRAS.447.2170K}.
 
@@
 It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
-As shown in \cite{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
+As shown in \cite{2014MNRAS.445.2181C}, the recovery of the shape information of the lens is only good if there are at least four images.
 Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
@@
            & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-      2016 & ... & PixRad(16) \\
-      2045 & ... & $\gamma(0.1)$, Symm \\
+      2016 & ... & Smaller pixels \\
+      2045 & ... & $\gamma\leq 0.1$, Symm \\
       2237 & ... & ...\\
     \end{tabular}
-    \caption[width=\linewidth]{Additional priors to the base set described in \S\ref{sec:glass} are listed.
-$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$ between light from the images B and A.
-The images are defined in Table~\ref{tab:lenspositions}.
-$\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
-`Symm' denotes that a point-symmetry prior is employed.
-`PixRad(16)' indicates that the pixel radius was set to 16 pixels.}
+    \caption[width=\linewidth]{Lenses where additional data or priors
+      were used (cf.~\S\ref{sec:shapemethod}). $\Delta t_{BA}$ and so
+      on denote time delays between images as labelled in
+      Table~\ref{tab:lenspositions}; $\gamma$ refers to the allowed
+      external shear; `Symm' means that the mass map was symmetric
+      under rotation by $180^\circ$; `Smaller pixels' indicates that
+      the pixel size was 3\% rather than 4\% of the diameter of the
+      whole mass map.}
     \label{tab:lenspriors}
@@
 We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
-We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014arXiv1401.7990C}.
+We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014MNRAS.445.2181C}.
 We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $e = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see \S\ref{sec:shapemethod}).

### 2015-08-26 shapes/paper.tex
Justin added references on misalignments
Added/modified Figures, Tables, reply referee

@@
 Averaging over larger radii, the ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components.
-While dark matter haloes are never more elliptical than $e_{dm} = 0.3$, their stars can extend to $e_* > 0.3$.
-Three systems, in particular, have a high stellar ellipticity ($e_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution.
+While dark matter haloes are never more elliptical than $s_{dm} = 0.3$, their stars can extend to $s_* > 0.3$.
+Three systems, in particular, have a high stellar ellipticity ($s_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution.
 One of these -- {\it B1608+656} -- is a known merging pair; we suggest that the other two ({\it B0712+472} and {\it B2016+112}) may also be recent post-merger systems.
@@
 
-While it is possible to compute shape parameters for a lensing galaxy
-by fitting to a parametric shape to the lens, it would make the
-definition of a shape estimate dependent on the which parametric form
-was being used.  Moreover, the commonly-used parametric forms for
-modelling lensing galaxies \citep[see e.g.,][]{2001astro.ph..2341K} do
-not allow for features like twisting isodensity contours, which can
-arise from projection of triaxial ellipsoids with no intrinsic twists
-\citep[e.g.][and references therein]{1978ComAp...8...27B}.  To avoid
-these problems, we use non-parametric ellipticity estimators, defined
-as follows.
+While it is possible to compute shape parameters for a lensing galaxy by fitting to a parametric shape to the lens, it would make the definition of a shape estimate dependent on the which parametric form was being used.
+Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[see e.g.,][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}.
+To avoid these problems, we use non-parametric ellipticity estimators, defined as follows.
 
-Lenses are modelled as free-form mass distributions, consisting of
-mass tiles or pixels.  Such lens models are also called
-non-parametric, which really just means that many more parameters than
-data constraints are used.  Thus the lens models are non-unique, and
-hence in fact ensembles of these free-form mass distributions are
-used.  From such a mass map, an inertia tensor is defined as
+Lenses are modelled as free-form mass distributions, consisting of mass tiles or pixels.
+Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used.
+Thus the lens models are non-unique, and hence in fact ensembles of these free-form mass distributions are used.
+From such a mass map, an inertia tensor is defined as
 \begin{equation}\label{eq:inertiatensor}
@@
 \end{equation}
-where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the
-mass in a pixel.  The eigenvectors of this inertia tensor give the
-ellipticity axes, and our ellipticity estimator is
+where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the mass in a pixel. The eigenvectors of this inertia tensor give the ellipticity axes, and our ellipticity estimator is
 \begin{equation}\label{eq:shapeestimate}
@@
 \end{equation}
-where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$)
-are the eigenvalues.  We use this ellipticity estimators to quantify
-the shapes both of the stellar-mass distribution and of the
-dark-matter distribution.  For the dark matter, only the mass
-distribution out to the radius of the outermost image is used; for the
-stellar part, the distribution with within different multiples of
-$R_e$ (defined as the half-light radius measured with respect to the
-Petrosian flux) is used.  It is necessary to have a cutoff for the
-regions used to compute the inertia tensor, or else it would be
-dominated by the outer regions where there is little information.  The
-mass pixels used in this work are at most 4\% of the diameter of the
-the full mass map.  The central region has smaller pixels, to allow
-for a density cusp at the centre.  Each model ensemble had $10^4$
-models.
+where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues.
+We use this ellipticity estimators to quantify the shapes both of the stellar-mass distribution and of the dark-matter distribution.
+For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used.
+It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information.
+The mass pixels used in this work are at most 4\% of the diameter of the the full mass map.
+The central region has smaller pixels, to allow for a density cusp at the centre.
+Each model ensemble had $10^4$ models.
 
-The non-parametric mass models themselves are constructed using the
-\Glass\ framework for modelling multiple-image lenses
-\citep{2014MNRAS.445.2181C}.  \Glass\ produces ensembles of mass maps,
-each of which reproduces exactly the observed image positions and
-image parities; also time delays, if measured.  The lensing data must
-be in the form of point images, which could be quasars or simply
-point-like features in otherwise extended images, but this was not a
-problem for the lenses studied in this work.  The estimated stellar
-mass (explained below in Section~\ref{sec:data}) is taken as a lower
-limit on the total mass.  The additional mass that needs to be put on
-top, in order to reproduce the lensing observables, is interpreted as
-dark matter.  (Some of that mass may actually be gas, but very little
-is expected in the early-type galaxies used in this work.)  The
-criteria of lensing observables and non-negative dark matter by
-themselves would leave the mass distribution too under-determined.
-Hence, an additional prior is used, requiring the mass distribution to
-be centrally concentrated, with the same centre as the galaxy light
-(but not necessarily the shape shape).  The precise formulation of the
-prior is given in Section~3 of \cite{2014MNRAS.445.2181C}.  Tests of
-how well the shape estimator can be recovered from lensing data are
-given in Section~5.2 and Figure~8 of that paper.
+The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}.
+\Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions and image parities; also time delays, if measured.
+The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work.
+The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass.
+The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter.
+\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.)} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
+Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape).
+The precise formulation of the prior is given in Section~3 of \cite{2014MNRAS.445.2181C}.
+Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.
 
-We remark that \Glass\ is closely related to an earlier code
-\PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a
-completely different code base.  An important improvement is a better
-sampling algorithm for high dimensional spaces
-\citep{2012MNRAS.425.3077L} that eliminates the excessive weight
-\PixeLens\ tended to give to extreme models. \Glass\ has also been
-adapted for lens modelling in citizen science
-\citep{2015MNRAS.447.2170K}.
+We remark that \Glass\ is closely related to an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
+An important improvement is a better sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} that eliminates the excessive weight \PixeLens\ tended to give to extreme models.
+\Glass\ has also been adapted for lens modelling in citizen science \citep{2015MNRAS.447.2170K}.
 
@@
   \centering
-  \includegraphics[width=.8\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $e_{dm}$ and the stellar component $e_{*}$.
+  \includegraphics[width=.8\linewidth]{Figures/kappaplot.pdf}
+  \caption[width=\linewidth]{\textbf{CAPTION}}
+  \label{fig:kappaplot}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=.75\linewidth]{Figures/wedges_shears.pdf}
+  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$.
 The wedges show the alignment of the semi-major axes of the components.
@@
 Both the errors in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within.
-The lenses are additionally color-coded in terms of the required external shear in modelling the lens.}
+The lenses are additionally color-coded in terms of the required external shear in modelling the lens.
+\textbf{update}}
   \label{fig:wedgesall}
@@
 
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{l | l l l l l l}
+      Lens & $s_{*}$ & $s_{dm}$ & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm,t}}{e_{*}}$ \\ \hline
+      0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 \\
+      0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 \\
+      0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
+      0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 \\
+      0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
+      1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 \\
+      1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 \\
+      1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 \\
+      2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 \\
+      2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
+      2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 \\
+    \end{tabular}
+    \caption[width=\linewidth]{...}
+    \label{tab:ellipratios}
+  \end{center}
+\end{table*}
+
 \begin{figure*}
   \centering
-  \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
+  \includegraphics[width=.75\linewidth]{Figures/wedges.pdf}
   \caption[width=\linewidth]{Similar to Figure~\ref{fig:wedgesall}.
@@
 Secondly, most lenses lie in the bottom-left corner: the dark matter distributions have typically low eccentricities, while the stellar distributions can be rather elliptical.
-Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($e_* > 0.4$).
+Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 0.4$).
 At the same time, they show a very strong alignment between their stellar and dark matter distributions.
@@
 
-Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.05$).
+Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim0.05$).
 By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
@@
 We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014MNRAS.445.2181C}.
-We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $e = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see \S\ref{sec:shapemethod}).
-We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see \S\ref{sec:shapemethod}).
+We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
 
@@
 The same trend can furthermore be seen for the dark matter, although the data are also consistent with no change in shape.
-The dark matter haloes are never more elliptical than $e_{dm} = 0.2$, while their stars can extend to $e_* > 0.3$.
+The dark matter haloes are never more elliptical than $s_{dm} = 0.2$, while their stars can extend to $s_* > 0.3$.
 
-\item Three systems have a high stellar ellipticity ($e_* > 0.45$) and correspondingly high alignment between light and dark.
+\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark.
 One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.
@@
 \item Galaxies with high dark matter ellipticity and weak external shear show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
-This is reassuring since isolated misaligned galaxies are expected to be unstable.
+This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
 \end{itemize}
+
+%Relevant references for misalignments being unstable: 
+%- http://adsabs.harvard.edu/abs/1978MNRAS.183..779B : 1978MNRAS.183..779B
+%- http://adsabs.harvard.edu/abs/1981MNRAS.196..455B : 1981MNRAS.196..455B
+%- http://adsabs.harvard.edu/abs/1979ApJ...233..872H : 1979ApJ...233..872H
+%- http://adsabs.harvard.edu/abs/1984ApJ...276..101S : 1984ApJ...276..101S
+%- http://adsabs.harvard.edu/abs/1987A%26A...182..202R : 1987A&A...182..202R
+%- http://adsabs.harvard.edu/abs/1988A%26A...206..269M : 1988A&A...206..269M
+%- http://adsabs.harvard.edu/abs/2007ApJ...670.1027A : 2007ApJ...670.1027A
 
@@
 
+\section{Shear-Shape degeneracy}\label{sec:shearshapedeg}
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
+  \caption[width=\linewidth]{\textbf{CAPTION}}
+  \label{fig:thetascatter}
+\end{figure*}
+
 \end{document}

### 2015-08-27 shapes/paper.tex
Added captions; some (incomplete) notes in the text what needs to be done; changed one Figure slightly to be in degrees instead of radians

@@
 
-Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
+\textbf{Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
 \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
@@
 They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
+[CHANGE THIS PARAGRAPH!
+Split up into two paragraphs to first describe subtleties of the measurement, and then what the constraints are.]}
 
@@
 \begin{equation}\label{eq:shapeestimate}
-    e \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
+    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
 \end{equation}
@@
 The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter.
-\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.)} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
+\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN THERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
 Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape).
@@
 \section{Data}\label{sec:data}
+\textbf{CLAUDIO: LOOK UP THE REFERENCES ON THE LENSES TO FIND OUT SPECIFIC MISALIGNMENT/ALIGNMENT ANGLES.}
+
 Stellar mass maps are taken from \cite{2011ApJ...740...97L}.
@@
 \section{Results}\label{sec:results}
+\textbf{Just in general: Should we split up this Sections into subsections?}
+
 \begin{figure*}
@@
   \includegraphics[width=.8\linewidth]{Figures/kappaplot.pdf}
-  \caption[width=\linewidth]{\textbf{CAPTION}}
+  \caption[width=\linewidth]{Convergence $\langle\kappa\rangle$ azimuthally averaged within radii $R$.
+The green curve shows the contribution to the convergence by the dark matter in the strong lens galaxies reconstructed by \GLASS.
+The vertical lines denote the radial distances of the source images from the centre of the lens.
+We note that in the case of \textit{0957}, there are two lensed components of the source galaxy.
+Thus, the green resp.
+blue vertical lines correspond to one of the respective components.
+The dashed black lines show the expected profiles for dark matter halos that follow a NFW density profile.
+These halo masses are calibrated in order for the values of the convergence to agree at one pixel past the last image radius.}
   \label{fig:kappaplot}
@@
 The lenses are additionally color-coded in terms of the required external shear in modelling the lens.
-\textbf{update}}
+\textbf{UPDATE}}
   \label{fig:wedgesall}
@@
     \end{tabular}
-    \caption[width=\linewidth]{...}
+    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$.
+The column $\frac{e_{dm}}{e_{*}}$ contains the values of the ratios of the dark matter relative to the stellar distribution.
+The column $\frac{e_{dm,t}}{e_{*}}$ displays the corresponding ratios of the ellipticity component of the dark matter distribution projected along the stellar distribution and the stellar ellipticity and takes thus potential misalignments into account.
+The weak lensing estimates are sensitive only to this combination of the ellipticities.
+\textbf{MAYBE REFINE THIS A BIT}}
     \label{tab:ellipratios}
@@
 We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses. The reconstructed stellar and dark mass maps for each individual lens are given in the Appendix.
+
+\textbf{Add here some description on the kappa-plot and that it's basically fine except for 2237 (only bulge is probed). Shall we add the fitted halo masses as well?}
 
@@
 
+\textbf{Comment on the table with the ellipticity ratios and how it compares to the weak lensing estimates.}
+
 \section{Conclusions}\label{sec:conclusions}
@@
 \begin{itemize}
+\item \textbf{Probably add here something on the profiles}
+
 \item We found that the dark matter haloes are rounder than the light distribution over the range $1R_e < R < 5R_e$.
@@
 
+\textbf{ADD THE COMMENTED REFERENCES ON MISALIGNMENTS BEING UNSTABLE IN THE .tex-FILE IN A NEW PARAGRAPH}
 %Relevant references for misalignments being unstable: 
@@
 
-\section{Shear-Shape degeneracy}\label{sec:shearshapedeg}
+\section{Shear-Shape degeneracy [OTHER TITLE?]}\label{sec:shearshapedeg}
 \begin{figure*}
@@
   \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
-  \caption[width=\linewidth]{\textbf{CAPTION}}
+  \caption[width=\linewidth]{The distribution within the ensemble of reconstructed models in the two-dimensional plane defined by the position angle of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$.
+Each panel shows the histogram of this two-dimensional distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample.
+\textbf{[CAPTION ISN'T GREAT, MAYBE...]}}
   \label{fig:thetascatter}
@@
 
+\textbf{Add some explanatory text on this Figure. PRASENJIT, COULD YOU COMMENT ON THIS DEGENERACY PLEASE (EXPECTATION, WHAT WE SEE, WHY IT'S FINE...)}
+
 \end{document}

### 2015-09-06 shapes/paper.tex
housekeeping
Fixed various things

--- 2015-08-26 shapes/paper.tex
@@
 Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
-
 \end{abstract}
@@
 
-Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
-\citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
+Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions within galaxies.
+These galaxies however need to be `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axis of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
+For fixed radii $r$ from the galaxy's centre the exerted shear is larger in the direction of the major axis of the total mass distribution of the galaxy than in the direction of the minor axis.
+In case of alignment of the luminous and dark matter and an elliptical halo shape, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
+shape-shear intrinsic alignments (\textit{GI}-term);][]{2004PhRvD..70f3526H} and systematic effects.
+If the distributions are however misaligned or the mass distributions are spherical, the shear signal is expected to be isotropic.
+
+\textbf{\citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
 They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
@@
 They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
+\citet{2015arXiv150603536C} \citet{2015arXiv150704301S} [CLAUDIO: WILL FIX THIS PARAGRAPH]}
 
-Recently, \cite{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass.
+% Our best-fit value for the ellipticity of the surface mass density is 0.24, which translates to an axis ratio of 0.78.
+We rule out the hypothesis of no ellipticity at the 4σ confidence level, and ellipticity < 0.12 (axis ratio > 0.89) at the 2σ level.
+--> significant detection around LRG with SDSS data
+
+Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass\.
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
@@
 This paper is organised as follows.
-In \S\ref{sec:shapemethod}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
-In \S\ref{sec:data}, we present our data compilation with references.
-In \S\ref{sec:results}, we present our results.
-Finally, in \S\ref{sec:conclusions} we discuss the implications of these results and we present our main conclusions.
+In Section~\ref{sec:shapemethod}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
+In Section~\ref{sec:data}, we present our data compilation with references.
+In Section~\ref{sec:results}, we present our results.
+Finally, in Section~\ref{sec:conclusions} we discuss the implications of these results and we present our main conclusions.
 
@@
 While it is possible to compute shape parameters for a lensing galaxy by fitting to a parametric shape to the lens, it would make the definition of a shape estimate dependent on the which parametric form was being used.
-Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[see e.g.,][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}.
+Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[e.g.][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}.
 To avoid these problems, we use non-parametric ellipticity estimators, defined as follows.
@@
 \begin{equation}\label{eq:inertiatensor}
+I = 
 \begin{pmatrix}
@@
 Each model ensemble had $10^4$ models.
+Shape and orientation of the distributions are estimated for each of these models, allowing us to constrain the scatter and thus the the statistical uncertainty in these quantities.
 
@@
 The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter.
-\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.)} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
+\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN THERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
 Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape).
-The precise formulation of the prior is given in Section~3 of \cite{2014MNRAS.445.2181C}.
+The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}.
 Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.
@@
 \section{Data}\label{sec:data}
-Stellar mass maps are taken from \cite{2011ApJ...740...97L}.
-In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \cite{2003MNRAS.344.1000B} were obtained.
-The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
-The initial mass function (IMF) was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
-We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
-While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
-For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
-We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
-We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
-
-The original sample we consider, is presented in \cite{2011ApJ...740...97L} and consists of 21 lens systems.
-It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
-As shown in \cite{2014MNRAS.445.2181C}, the recovery of the shape information of the lens is only good if there are at least four images.
-Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
-This yields a sample consisting of 11 lenses.
-We discuss each of these systems, next.
-
-\textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
-It is part of a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
-
-\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
-A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
-It, however, is more likely a foreground object with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
-This is sufficiently distant to still contribute to the lensing effect.
-
-\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998MNRAS.296..483J,1998AJ....115..377F}.
-There is a foreground group of about 10 member galaxies at $z\sim0.3$, which could affect the modelling \citep{2002AJ....123..627F}.
-
-\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
-It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
-There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
-
-\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the centre of a cluster with a high spiral galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
-Due to the large image separation, large physical scales are probed.
-As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg.
-These results are consistent with the centre of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
-The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
-They however also find a three-day lag between the g- and r-bands, a disagreement at the 2$\sigma$-level.
-They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
-We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
-
-\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{1980Natur.285..641W,2005ApJ...626...51Y}.
-It has measured time delays \citep[see e.g.][]{1997ApJ...475L..85S}.
-In this work, we use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
-\cite{1997ApJ...489...21B}.
-The environment of the lens was analysed thoroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
-It is part of a small group of 13 members.
-Also, X-ray emission was detected from the corresponding group and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
-
-\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.
-Although time delays have been reported \citep{2001MNRAS.326.1403P}, it is possible that the measurements are aliases of the actual values \citep{2003AJ....126...29R} and hence are not included in our analysis.
-The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
-Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
-\cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
-
-\textit{B1608+656} (hereafter \textit{1608}) was first reported by \cite{1995ApJ...447L...5M}.
-It consists of two merging galaxies.
-The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
-The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
-However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
-The data seem to indicate four other groups along the line of sight.
-
-\textit{MG2016+112} (hereafter \textit{2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
-It is the farthest lens we consider in this sample.
-It lies in a cluster that consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
-The cluster shows a high density of galaxies close to the lens in a south-east direction.
-Two lensed images are very close in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.
-
-\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
-It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, however the velocity dispersion seems too high.
-As the source redshift is rather low, a large lens mass is required.
-\cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-To the west of the lens, a group was found at a similar redshift as the lens \citep{1999AJ....117..658F}.
-There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
-As the measurements are however inconclusive, we choose to not include this satellite in our models.
-
-\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
-With a redshift of just $z\sim0.04$ it is the closest lens system of the sample.
-Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
-This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.
-
-Further information on the sample can be found in \citet{2011ApJ...740...97L} and \citet{2012A&A...538A..99S}.
-The most important quantities of each system are given in Table~\ref{tab:lensproperties}.
-Due to the different angular separations of the images and the different angular diameter distances, in each lens galaxy we necessarily probe slightly different scales.
-
 \begin{table}
@@
     \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}.
-References can be found in \S\ref{sec:data}.
+References can be found in Section~\ref{sec:data}.
 The columns are from left to right: the lens redshift $z_L$; the redshift of the source $z_S$; the maximum angular separation between two images $\Delta\theta$; the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$; and information on the environment of the lens.
@@
 The number in the brackets is the number of confirmed members.
-Ellipsis indicate lens galaxies with no group members identified so far.}
+Ellipses indicate lens galaxies with no group members identified so far.}
     \label{tab:lensproperties}
@@
     \end{tabular}
-    \caption[width=\linewidth]{Lenses where additional data or priors
-      were used (cf.~\S\ref{sec:shapemethod}). $\Delta t_{BA}$ and so
-      on denote time delays between images as labelled in
-      Table~\ref{tab:lenspositions}; $\gamma$ refers to the allowed
-      external shear; `Symm' means that the mass map was symmetric
-      under rotation by $180^\circ$; `Smaller pixels' indicates that
-      the pixel size was 3\% rather than 4\% of the diameter of the
-      whole mass map.}
+    \caption[width=\linewidth]{Lenses where additional data or priors were used (cf.~Section~\ref{sec:shapemethod}).
+$\Delta t_{BA}$ and so on denote time delays between images as labelled in Table~\ref{tab:lenspositions}; $\gamma$ refers to the allowed external shear; `Symm' means that the mass map was symmetric under rotation by $180^\circ$; `Smaller pixels' indicates that the pixel size was 3\% rather than 4\% of the diameter of the whole mass map.}
     \label{tab:lenspriors}
@@
 
+Stellar mass maps are taken from \citet{2011ApJ...740...97L}.
+In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \citet{2003MNRAS.344.1000B} were obtained.
+The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
+The initial mass function (IMF) was taken to be the log-normal form given by \citet{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
+We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
+While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
+For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
+We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
+We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
+
+The original sample we consider, is presented in \citet{2011ApJ...740...97L} and consists of 21 lens systems.
+It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
+As shown in \citet{2014MNRAS.445.2181C}, the recovery of the shape information of the lens is only good if there are at least four images.
+Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
+This yields a sample consisting of 11 lenses.
+We discuss each of these systems, next.
+
+\textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
+It is part of a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
+
+\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
+A close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
+It, however, is more likely a foreground object with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
+
+\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998MNRAS.296..483J,1998AJ....115..377F}.
+There is a foreground group of about 10 member galaxies at $z\sim0.3$ \citep{2002AJ....123..627F}.
+
+\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
+It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
+There is furthermore a satellite galaxy to the north-west \citep{2000ApJ...544L..35K}.
+\textbf{applied to the binned event positions yields a centroid for the extended emission of where o†sets are $\Delta\alpha = -14.2''$, $\Delta\delta = -39.5''$, with respect to the centroid of component B.
+--> PA: -160.2268099}
+
+\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the centre of a cluster with a high spiral galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
+Due to the large image separation, large physical scales are probed.
+As listed in Table 3 of \citet{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg.
+These results are consistent with the centre of the X-ray emission from the cluster \citep{2002ApJ...565...96C}.
+The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
+They however also find a three-day lag between the g- and r-bands, a disagreement at the 2$\sigma$-level.
+They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
+We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
+low
+\textbf{and the cluster center based on the published position (-13.7'', -19.6'') (Angonin-Willaime 1994) et al.
+for the estimated cluster center of mass with respect to image B \citep{1994A&A...291..411A}}
+
+\textbf{The best-fit position angle (north through east) and core radius of the cluster are $59 deg$ and $15.4'' \pm 3.5''$, respectively.
+The Chandra observations of Q0957+561 therefore indicate that the cluster center is located within a core radius of the lens galaxy G1.
+Using the values for and r i provided by our analysis of the c, dc, Chandra observation of Q0957]561, we Ðnd that the cluster shear amplitude c is 0.01 0.009 (90\% confidence level), consistent with the recent model results of Keeton et al.
+(2000).
+4.3"+/-1.3" east and 3.5"+1.2"-0.6" north of image B [B =  0.182 , -1.018] --> PA: 58.6269949 \citep{2002ApJ...565...96C}}
+
+\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{1980Natur.285..641W,2005ApJ...626...51Y}.
+It has measured time delays \citep[see e.g.][]{1997ApJ...475L..85S}.
+In this work, we use recent estimates of the time delays by \citet{2010MNRAS.406.2764T} that differ from previously found values by e.g.
+\citet{1997ApJ...489...21B}.
+The environment of the lens was analysed thoroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
+It is part of a small group of 13 members.
+Also, X-ray emission was detected from the corresponding group and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
+\textbf{The maximum X-ray emission for the PG 1115+080 group is near $\Delta\alpha = -21''$ and $\Delta\delta = -14''$ relative to image C of the gravitational lens.
+$\Delta\alpha = -20.6''$ and $\Delta\delta = -15.3''$ --> PA: -126.6 deg}
+
+\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.
+Although time delays have been reported \citep{2001MNRAS.326.1403P}, it is possible that the measurements are aliases of the actual values \citep{2003AJ....126...29R} and hence are not included in our analysis.
+The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
+Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
+\citet{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
+\textbf{The maximum X-ray emission for the B1422+231 group is at about  $\Delta\alpha = 7''$ and  $\Delta\delta = -9''$ relative to image B of the gravitational lens.
+$\Delta\alpha = 6.2''$ and $\Delta\delta = -9.6''$ --> PA: 147.1 deg}
+
+\textit{B1608+656} (hereafter \textit{1608}) was first reported by \citet{1995ApJ...447L...5M}.
+It consists of two merging galaxies.
+The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
+The system has measured time delays \citep{2002ApJ...581..823F}.
+The environment has been analysed and a group with 8 (9 if the merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
+However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
+The data seem to indicate four other groups along the line of sight.
+\textbf{(Offset 25'' PA 30 deg; position-weighted) (Offset 8'' PA -5 deg; luminosity-weighted)}
+
+\textit{MG2016+112} (hereafter \textit{2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
+It is the farthest lens we consider in this sample.
+It lies in a cluster that consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
+The cluster shows a high density of galaxies close to the lens in a south-east direction.
+Two lensed images are very close in this fold lens, but could be resolved by \citet{2009MNRAS.394..174M}.
+\textbf{$\sim$ 130-140 deg}
+
+\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
+It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, however the velocity dispersion seems too high.
+As the source redshift is rather low, a large lens mass is required.
+\citet{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
+North-west of the lens, there is evidence for a group at a similar redshift as the lens \citep{1999AJ....117..658F}.
+There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
+As the measurements are however inconclusive, we choose to not include this satellite in our models.
+\textbf{$\sim$ -60 deg}
+\textbf{satellite within Einstein radius}
+
+\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
+With a redshift of just $z\sim0.04$ it is the closest lens system of the sample.
+Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
+This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.
+low
+
+Further information on the sample can be found in \citet{2011ApJ...740...97L} and \citet{2012A&A...538A..99S}.
+The most important quantities of each system are given in Table~\ref{tab:lensproperties}.
+Due to the different angular separations of the images and the different angular diameter distances, in each lens galaxy we necessarily probe slightly different scales.
+
 \section{Results}\label{sec:results}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{Figures/kappaplot.pdf}
-  \caption[width=\linewidth]{\textbf{CAPTION}}
+  \includegraphics[width=.75\linewidth]{Figures/kappaplot.pdf}
+  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution.
+The vertical lines denote the radial distances of the source images from the centre of the lens galaxies.
+We note that in the case of \textit{0957}, there are two lensed components of the source galaxy.
+Thus, the green resp.
+blue vertical lines correspond to the images of the respective components.
+The green curves show the contributions by the dark matter in the strong lens galaxies as reconstructed by \Glass.
+The dashed black lines show the corresponding profiles for dark matter halos that follow a NFW density profile.
+The parameters in the NFW distribution are calibrated in order for the values of the derived convergences $\langle\kappa\rangle$ to match the correspnding values of the reconstructed profiles at one pixel past the last image radius.}
   \label{fig:kappaplot}
@@
   \centering
-  \includegraphics[width=.75\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$.
+  \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
+  \caption[width=\linewidth]{The reconstructed lens galaxies are displayed according to the reconstructed total shapes of the dark matter halos $s_{dm}$ and the stellar components $s_{*}$.
 The wedges show the alignment of the semi-major axes of the components.
-In case of alignment of the semi-major axes (Aligned), the wedges are vertical.
+In case of alignment of the respective semi-major axes (Aligned), the wedges are vertical.
 In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
-The opening angle displays the statistical error in the shape estimate of the dark matter halo.
-Both the errors in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within.
-The lenses are additionally color-coded in terms of the required external shear in modelling the lens.
-\textbf{update}}
+The opening angle of each wedge displays the statistical error in the shape estimate of the dark matter halos.
+Both the uncertainties in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models of the ensemble of solutions lie within.
+The lens galaxies are additionally color-coded in terms of the required external shear in reconstructing the mass distribution.
+The right panel shows the region in the left panel denoted by a dashed rectangle in greater detail.}
   \label{fig:wedgesall}
@@
   \begin{center}
-    \begin{tabular}{l | l l l l l l}
-      Lens & $s_{*}$ & $s_{dm}$ & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm,t}}{e_{*}}$ \\ \hline
-      0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 \\
-      0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 \\
-      0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
-      0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 \\
-      0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
-      1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 \\
-      1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 \\
-      1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 \\
-      2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 \\
-      2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
-      2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 \\
+    \begin{tabular}{l | l l l l l l l l}
+      Lens & $s_{*}$ & $s_{dm}$ & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm,t}}{e_{*}}$ & $|\gamma|$ & $\theta_{g}$ [deg]\\ \hline
+      0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
+      0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
+      0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
+      0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
+      0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
+      1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
+      1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
+      1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
+      2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
+      2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
+      2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
     \end{tabular}
-    \caption[width=\linewidth]{...}
+    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$; $\frac{e_{dm}}{e_{*}}$ denotes the ratio of the dark matter relative to the stellar distribution; $\frac{e_{dm,t}}{e_{*}}$ refers to this ratios, where the ellipticity component of the dark matter distribution is projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.}
     \label{tab:ellipratios}
@@
 
-We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses. The reconstructed stellar and dark mass maps for each individual lens are given in the Appendix.
+We have applied \Glass\ to the data set described in Section~\ref{sec:data} consisting of 11 lenses. The reconstructed stellar and dark mass maps for each individual lens are given in the Appendix.
 
-Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions.
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l | l l}
+      Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
+      0047 & 360.7  & 9.98   \\
+      0414 & 256.9  & 12.38  \\
+      0712 & 446.5  & 15.45  \\
+      0911 & 369.1  & 22.66  \\
+      0957 & 1053.1 & 175.16 \\
+      1115 & 616.8  & 31.06  \\
+      1422 & 450.8  & 13.05  \\
+      1608 & 317.1  & 9.99   \\
+      2016 & 299.3  & 22.14  \\
+      2045 & 562.8  & 103.97 \\
+      2237 & 1961.0 & 485.26 \\
+    \end{tabular}
+    \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
+    \label{tab:virialmasses}
+  \end{center}
+\end{table}
+
+\subsection{Radial dark matter profiles}
+We compare the profiles of the reconstructed dark matter distributions of the individual strong lens galaxies with Navarro-Frenk-White-profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}
+\begin{equation}\label{eq:nfw}
+   \frac{\rho(R)}{\rho_{crit}} = \frac{\delta_{c}}{(cR/R_{vir})(1+cR/R_{vir})},
+\end{equation}
+where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology being considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
+The latter is related to $M_{vir}$ \citep{2011ApJ...740..102K}
+\begin{equation}\label{eq:concentration}
+ \begin{split}
+   c(M_{vir}, z) = & c_{0}(z)\left(\frac{M_{vir}}{10^{12}h^{-1}M_{\odot}\right)^{-0.075} \\ & \times \left[1+\left(\frac{M_{vir}}{M_{0}(z)}\right)^{0.26}\right]},
+ \end{split}
+\end{equation}
+where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters.
+The relation is constrained at specific redshifts are listed in Table 3 of \citet{2011ApJ...740..102K}.
+For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
+
+As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$, which we set with Equation~\ref{eq:concentration}, there is only one degree of freedom, $M_{vir}$.
+We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ to match one pixel past the last image radius for the reconstructed dark matter distribution and the chose NFW-profile.
+
+Figure~\ref{fig:kappaplot} displays the results, while the masses are given in Table~\ref{tab:virialmasses}.
+\textbf{[HERE SOME COMMENT ON THE MASSES WE HAVE FIT; I'VE INCLUDED THEM TEMPORARILY (!) IN TABLE~\ref{tab:virialmasses} TO DECIDE WHAT WE DO WITH THEM AND HOW WE COMMENT ON THAT SOME OF THESE MASSES ARE RATHER LARGE]}.
+Except for \textit{0047}, where only the bulge is probed and significant deviations are expected, the profiles agree broadly.
+There are slight differences in some systems ...
+\textbf{[HERE WHY WE DON'T WORRY; MAYBE LINK TO FEI LI'S RESULTS?].}
+
+\subsection{Shape and alignment of the dark matter halos}
+Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions.
 In this Figure, the full distribution up to one pixel past the last-image radius $R_{L}$ is probed.
@@
 The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
-As described furthermore in \S\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
+As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
 {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
@@
 
+\subsection{Consistency with weak lensing estimates}
+The ellipticity values $s_{*}$ and $s_{dm}$ shown in Figures~\ref{fig:wedgesall} and \ref{fig:wedgesradii} and the values of the required external shear when reconstructing the lens galaxy are listed in Table~\ref{tab:ellipratios}.
+Furthermore, the ellipticity $s$ can be converted to the ellipticity $e=(a-b)/(a+b)$, where $a$ and $b$ are the semi-major and semi-minor axes of the lens galaxy, by applying the relation
+\begin{equation}
+   e = \frac{s}{2-s}.
+\end{equation}
+
+The latter ellipticity definition is commonly used in weak lensing.
+Especially, it is employed in \citet{2015arXiv150704301S}, a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter.
+This probe however cannot constrain the $e_{dm}$ directly.
+Rather, it is sensitive to the ratio $f_{h} = e_{dm,t}/e_{*}$, where $e_{dm,t}$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
+In case of perfect alignment and identical shape, $f_{h}$ is equal to 1.
+In practive however, $f_{h}$ deviates from 1, as among other effects, which cannot be disentangled, misalignment of the two distributions and different shapes affect its value.
+
+In \citet{2015arXiv150704301S} a measurement on data from the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H}.
+The constraints in the highest mass bin of early-type galaxies ($\mathrm{log_{10}}M_{*}>11$) on the CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
+On the simulated data, including cosmic shear and realistic misalignments between the luminous and the dark matter, the constraints in the highest mass bin and for redshifts $0.4<z<0.6$ are $f_{h} = 0.359^{+0.011}_{-0.010}$.
+Due to a narrower intrinsic ellipticity distribution in the simulated data however, the latter constraints need to be corrected for with a factor $\approx 1/1.46$.
+Our results are broadly consistent with both constraints, with the exception of the galaxy merger system \textit{1608} and \textit{1115}.
+The sample is however not large enough for a more quantitative comparison.
+
 \section{Conclusions}\label{sec:conclusions}
-We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
+We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass\.
 We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014MNRAS.445.2181C}.
-We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see \S\ref{sec:shapemethod}).
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see Section~\ref{sec:shapemethod}).
 We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
@@
 \begin{itemize}
+\item \textbf{[ADD HERE SOMETHING ON THE KAPPA PROFILES?]}
+
 \item We found that the dark matter haloes are rounder than the light distribution over the range $1R_e < R < 5R_e$.
@@
 This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
+
+\item \textbf{[ADD HERE SOMETHING ON THE CONSISTENCY WITH WEAK LENSING RESULTS?]}
+
 \end{itemize}
 
+\textbf{[ADD THE COMMENTED REFERENCES ON MISALIGNMENTS BEING UNSTABLE IN THE .tex-FILE IN A NEW PARAGRAPH]}
 %Relevant references for misalignments being unstable: 
@@
 
-In this Appendix, we show the results of our lens modelling for each individual lens (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
+In this Appendix, we show the results of our lens modelling for each individual lens galaxy (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses31.pdf}
-  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens.
+  \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy.
 The panels show, from left to right: the arrival time surface (the images are marked by the green circles); the surface mass density of the dark matter; and the surface mass density of the stars.
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses32.pdf}
-  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
+  \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
   \label{fig:lensreconstruction2}
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses33.pdf}
-  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
+  \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
   \label{fig:lensreconstruction3}
@@
 
-\section{Shear-Shape degeneracy}\label{sec:shearshapedeg}
+\section{Degeneracy between $\theta_{dm}$ and $\theta_{g}$}\label{sec:shearshapedeg}
 \begin{figure*}
@@
   \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
-  \caption[width=\linewidth]{\textbf{CAPTION}}
+  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution of the ensemble of solutions.
+The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample.
+All the angles are measured north through east.}
   \label{fig:thetascatter}
@@
 
+Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy.
+We note that the constraints on the direction of the external shear are stronger than the ones on the dark matter distribution \textbf{[INSERT HERE WHY HE THINK THAT IS]}.
+A slight degeneracy between the angles is evident.
+However, \textbf{...
+[WHY THIS IS EXPECTED, AND WHY OUR MISALIGNMENT RESULT STILL HOLDS].}
+
 \end{document}

### 2015-09-07 shapes/paper.tex
Fixed typo
Added weak lensing paragraph in introduction; Reworked Data Section

@@
 In case of alignment of the luminous and dark matter and an elliptical halo shape, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
-shape-shear intrinsic alignments (\textit{GI}-term);][]{2004PhRvD..70f3526H} and systematic effects.
+intrinsic alignments][]{2004PhRvD..70f3526H} and systematic effects.
 If the distributions are however misaligned or the mass distributions are spherical, the shear signal is expected to be isotropic.
 
-\textbf{\citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
+This measurement has been perfomed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results.
+These analyses mainly differ in the data sets, the selection of lens galaxies, the estimators used, and the treatment of systematics \citep[see][]{2015arXiv150704301S}.
+Recently, \citet{2015arXiv150603536C} made this measurement on Luminous Red Galaxies (LRG) identified in the Sloan Digital Sky Survey (SDSS), and report a significant detection of dark matter halo ellipticity.
+Shortly thereafter, \citet{2015arXiv150704301S} performed this measurement on data from the Canada France Hawaii Lensing Survey (CFHTLenS).
+Furthermore, the method was tested using the Milennium Simulation \citep{2005Natur.435..629S}, while exploring the effect of cosmic shear and misalignments of the luminous and dark matter distributions.
+% \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
 They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
 Both measurements are challenging however, and more recent data appear to be at odds with this early work, at least for galaxies in general.
-They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
-\citet{2015arXiv150603536C} \citet{2015arXiv150704301S} [CLAUDIO: WILL FIX THIS PARAGRAPH]}
+They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.}
 
-% Our best-fit value for the ellipticity of the surface mass density is 0.24, which translates to an axis ratio of 0.78.
-We rule out the hypothesis of no ellipticity at the 4σ confidence level, and ellipticity < 0.12 (axis ratio > 0.89) at the 2σ level.
---> significant detection around LRG with SDSS data
+% \citet{2004ApJ...606...67H}: Red-Sequence Cluster Survey (RCS); No split of galaxy sample in red & blue (magnitude-selected); Not taking care of systematics; f=0.77 --> probably good alignment, maybe halos somewhat rounder
+% \citet{2006MNRAS.370.1008M}: Sloan-Digital Sky Survey (SDSS); Galaxy sample split based on color; Discussing systematics; f=0.10+-0.06; no definite detection of halo ellipticity
+% \citet{2007ApJ...669...21P}: CFHTLS; No split of sample (rather only test by selecting preferentially ellipticals) (magnitude-selected); not really taking care of systematics, only test; halo ellipticity ~0.3 at 2sigma level (more if ellipticals)
+% \citet{2012A&A...545A..71V}: Red-Sequence Cluster Survey (RCS2); split in red & blue (magnitude-selected); Discussing systematics; no definite detection of halo ellipticity
+% \citet{2015arXiv150603536C}: SDSS; LRGs; Discuss systematics; detect halo ellipticity
+% \citet{2015arXiv150704301S}: CFHTLenS; split in red & blue (magnitude-selected); Discussing systematics; no definite detection of halo ellipticity
 
@@
 We discuss each of these systems, next.
+We note that all the angles are measured north through east and relative to the lens galaxy.
 
@@
 It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
+The center of the cluster lies at a position angle of about -160$^{\circ}$.
 There is furthermore a satellite galaxy to the north-west \citep{2000ApJ...544L..35K}.
-\textbf{applied to the binned event positions yields a centroid for the extended emission of where o†sets are $\Delta\alpha = -14.2''$, $\Delta\delta = -39.5''$, with respect to the centroid of component B.
---> PA: -160.2268099}
 
@@
 Due to the large image separation, large physical scales are probed.
-As listed in Table 3 of \citet{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg.
-These results are consistent with the centre of the X-ray emission from the cluster \citep{2002ApJ...565...96C}.
+Identified X-ray emission furthermore locates the center of the cluster at a position angle of about 59$^{\circ}$, close to the lens galaxy \citep{2002ApJ...565...96C}.
 The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
@@
 We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
-low
-\textbf{and the cluster center based on the published position (-13.7'', -19.6'') (Angonin-Willaime 1994) et al.
-for the estimated cluster center of mass with respect to image B \citep{1994A&A...291..411A}}
-
-\textbf{The best-fit position angle (north through east) and core radius of the cluster are $59 deg$ and $15.4'' \pm 3.5''$, respectively.
-The Chandra observations of Q0957+561 therefore indicate that the cluster center is located within a core radius of the lens galaxy G1.
-Using the values for and r i provided by our analysis of the c, dc, Chandra observation of Q0957]561, we Ðnd that the cluster shear amplitude c is 0.01 0.009 (90\% confidence level), consistent with the recent model results of Keeton et al.
-(2000).
-4.3"+/-1.3" east and 3.5"+1.2"-0.6" north of image B [B =  0.182 , -1.018] --> PA: 58.6269949 \citep{2002ApJ...565...96C}}
 
@@
 It is part of a small group of 13 members.
-Also, X-ray emission was detected from the corresponding group and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
-\textbf{The maximum X-ray emission for the PG 1115+080 group is near $\Delta\alpha = -21''$ and $\Delta\delta = -14''$ relative to image C of the gravitational lens.
-$\Delta\alpha = -20.6''$ and $\Delta\delta = -15.3''$ --> PA: -126.6 deg}
+Also, X-ray emission was detected from the corresponding group at a position angle of about -127$^{\circ}$ and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
 
@@
 Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
-\citet{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
-\textbf{The maximum X-ray emission for the B1422+231 group is at about  $\Delta\alpha = 7''$ and  $\Delta\delta = -9''$ relative to image B of the gravitational lens.
-$\Delta\alpha = 6.2''$ and $\Delta\delta = -9.6''$ --> PA: 147.1 deg}
+\citet{2004ApJ...610..686G} also detect X-ray emission from the corresponding group originating from a position angle of about 147$^{\circ}$ at a temperature of 1.0 keV.
 
@@
 The environment has been analysed and a group with 8 (9 if the merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
+Furthermore, the center was identified to be at a position angle of about 30$^{\circ}$ (resp.
+-5$^{\circ}$) if the member galaxies' positions are straight averaged (resp.
+weighted by luminosity).
 However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
 The data seem to indicate four other groups along the line of sight.
-\textbf{(Offset 25'' PA 30 deg; position-weighted) (Offset 8'' PA -5 deg; luminosity-weighted)}
 
@@
 It lies in a cluster that consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
-The cluster shows a high density of galaxies close to the lens in a south-east direction.
+The cluster shows a high density of galaxies close to the lens in a south-east direction, at about $\sim130-140^{\circ}$.
 Two lensed images are very close in this fold lens, but could be resolved by \citet{2009MNRAS.394..174M}.
-\textbf{$\sim$ 130-140 deg}
 
@@
 \citet{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-North-west of the lens, there is evidence for a group at a similar redshift as the lens \citep{1999AJ....117..658F}.
-There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
+North-west of the lens at about -60$^{\circ}$, there is evidence for a group at a similar redshift as the lens \citep{1999AJ....117..658F}.
+There is furthermore evidence for a dwarf satellite galaxy within the Einstein radius of the lens system \citep{2007MNRAS.378..109M}.
 As the measurements are however inconclusive, we choose to not include this satellite in our models.
-\textbf{$\sim$ -60 deg}
-\textbf{satellite within Einstein radius}
 
@@
   \begin{center}
-    \begin{tabular}{l | l l l l l l l l}
-      Lens & $s_{*}$ & $s_{dm}$ & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm,t}}{e_{*}}$ & $|\gamma|$ & $\theta_{g}$ [deg]\\ \hline
-      0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
-      0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
-      0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
-      0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
-      0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
-      1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
-      1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
-      1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
-      2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
-      2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
-      2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
+    \begin{tabular}{l | l l l l l l l l l}
+      Lens & $s_{*}$ & $s_{dm}$ & $\phi$ [^{\circ}] & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$ & $|\gamma|$ & $\theta_{g}$ [^{\circ}] \\ \hline
+      % 0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
+      % 0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
+      % 0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
+      % 0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
+      % 0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
+      % 1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
+      % 1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
+      % 1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
+      % 2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
+      % 2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
+      % 2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
+      0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.00 & 120$\pm$5 \\
+      0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.00 & 166$\pm$4 \\
+      0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.00 & 141$\pm$3 \\
+      0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.00 & 99$\pm$2 \\
+      0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.00 & 159$\pm$8 \\
+      1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.00 & 154$\pm$3 \\
+      1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.00 & 39$\pm$1 \\
+      1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.00 & 145$\pm$2 \\
+      2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.00 & 42$\pm$4 \\
+      2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.00 & 23$\pm$7 \\
+      2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.00 & 159$\pm$4 \\
     \end{tabular}
     \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$; $\frac{e_{dm}}{e_{*}}$ denotes the ratio of the dark matter relative to the stellar distribution; $\frac{e_{dm,t}}{e_{*}}$ refers to this ratios, where the ellipticity component of the dark matter distribution is projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.}
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$; $\phi$ refers to the misalignment angle between the distributions of luminous and dark matter; $\frac{e_{dm}}{e_{*}}$ denotes the ratio of the dark matter relative to the stellar distribution; $\frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.}
     \label{tab:ellipratios}
@@
  \begin{split}
-   c(M_{vir}, z) = & c_{0}(z)\left(\frac{M_{vir}}{10^{12}h^{-1}M_{\odot}\right)^{-0.075} \\ & \times \left[1+\left(\frac{M_{vir}}{M_{0}(z)}\right)^{0.26}\right]},
+   c(M_{vir}, z) = & c_{0}(z)\left(\frac{M_{vir}}{10^{12}h^{-1}M_{\odot}}\right)^{-0.075} \\ & \times \left[1+\left(\frac{M_{vir}}{M_{0}(z)}\right)^{0.26}\right],
  \end{split}
@@
 This probe however cannot constrain the $e_{dm}$ directly.
-Rather, it is sensitive to the ratio $f_{h} = e_{dm,t}/e_{*}$, where $e_{dm,t}$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
+Rather, it is sensitive to the ratio $f_{h} = \frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$, where $\phi$ is the misalignment angle between the two distributions, and $e_{dm}\mathrm{cos} 2\phi$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
 In case of perfect alignment and identical shape, $f_{h}$ is equal to 1.
@@
 
-In \citet{2015arXiv150704301S} a measurement on data from the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H}.
+In \citet{2015arXiv150704301S} a measurement on CFHTLenS data and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H}.
 The constraints in the highest mass bin of early-type galaxies ($\mathrm{log_{10}}M_{*}>11$) on the CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
@@
 
-In this Appendix, we show the results of our lens modelling for each individual lens galaxy (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
-The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
-The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within.
-Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $e$), and the angle between the dark matter and stellar major axes.
-Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.
-
-We note in Figure~\ref{fig:lensreconstruction2}, specifically for {\it0957} and to some degree also {\it1422}, twisting isophotes \citep[e.g.][]{1978ComAp...8...27B}.
-
 \begin{figure*}
@@
 
+In this Appendix, we show the results of our lens modelling for each individual lens galaxy (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
+The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within.
+Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $e$), and the angle between the dark matter and stellar major axes.
+Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.
+
+We note in Figure~\ref{fig:lensreconstruction2}, specifically for {\it0957} and to some degree also {\it1422}, twisting isophotes \citep[e.g.][]{1978ComAp...8...27B}.
+
 \section{Degeneracy between $\theta_{dm}$ and $\theta_{g}$}\label{sec:shearshapedeg}

### 2015-09-08 shapes/paper.tex
Included reply to specific points of criticism in referee report I modified in the paper; Additional small changes to the paper

@@
 
-Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass\.
+Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass.
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
@@
 For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used.
-It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information.
+It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information \textbf{[CLAUDIO: Actually, I estimate the shapes for the luminous and dark matter in the same way.
+I only consider different Petrosian radii in Figure 3, setting different multiples of $R_e$ as a limit for both distributions.
+Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}.
 The mass pixels used in this work are at most 4\% of the diameter of the the full mass map.
 The central region has smaller pixels, to allow for a density cusp at the centre.
-Each model ensemble had $10^4$ models.
-Shape and orientation of the distributions are estimated for each of these models, allowing us to constrain the scatter and thus the the statistical uncertainty in these quantities.
+
+We estimate the orientation of the distributions of luminous and dark matter by computing the angles $\theta_{*}$ resp.
+$\theta_{dm}$ of the eigenvector corresponding to the eigenvalue $\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$) relative to the x-axis.
+The misalignment angle $\Delta\theta$ between the distributions is then defined as
+\begin{equation}
+  \Delta\theta = \theta_{dm} - \theta_{*}.
+\end{equation}
+
+Each model ensemble consists of $10^4$ models, for all of which we apply our estimators for the shape and the alignment of the distributions.
+By identifying the median value and the range 68\% of all the values lie within of this distribution of estimated values, these quantities are constrained and the statistical uncertainties estimated.
 
@@
 The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter.
-\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN THERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
+\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN HERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
 Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape).
@@
     \begin{tabular}{l | l l l l l l l l l}
-      Lens & $s_{*}$ & $s_{dm}$ & $\phi$ [^{\circ}] & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$ & $|\gamma|$ & $\theta_{g}$ [^{\circ}] \\ \hline
+      Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
       % 0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
@@
     \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$; $\phi$ refers to the misalignment angle between the distributions of luminous and dark matter; $\frac{e_{dm}}{e_{*}}$ denotes the ratio of the dark matter relative to the stellar distribution; $\frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.}
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
     \label{tab:ellipratios}
@@
 This probe however cannot constrain the $e_{dm}$ directly.
-Rather, it is sensitive to the ratio $f_{h} = \frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$, where $\phi$ is the misalignment angle between the two distributions, and $e_{dm}\mathrm{cos} 2\phi$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
+Rather, it is sensitive to the ratio $f_{h} = (e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$, where $\Delta\theta$ is the misalignment angle between the two distributions, and $e_{dm}\cdot\mathrm{cos} 2\Delta\theta$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
 In case of perfect alignment and identical shape, $f_{h}$ is equal to 1.
@@
 \item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark.
-One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.
+One of these -- {\it1608} -- is a known merging pair; we speculate on the other two lens systems ({\it0712} and {\it2016}) being recent post-merger systems as well.
 
@@
 The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample.
-All the angles are measured north through east.}
+The angles are rotated to be measured north through east here.}
   \label{fig:thetascatter}

### 2015-09-08 shapes/paperOld.tex
Included reply to specific points of criticism in referee report I modified in the paper; Additional small changes to the paper

--- 2015-09-06 shapes/paper.tex
@@
 \usepackage{graphicx}
-\usepackage[normalem]{ulem}
+\usepackage{ulem}
 \usepackage{amsmath}
@@
 Averaging over larger radii, the ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components.
-While dark matter haloes are never more elliptical than $s_{dm} = 0.3$, their stars can extend to $s_* > 0.3$.
-Three systems, in particular, have a high stellar ellipticity ($s_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution.
+While dark matter haloes are never more elliptical than $e_{dm} = 0.3$, their stars can extend to $e_* > 0.3$.
+Three systems, in particular, have a high stellar ellipticity ($e_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution.
 One of these -- {\it B1608+656} -- is a known merging pair; we suggest that the other two ({\it B0712+472} and {\it B2016+112}) may also be recent post-merger systems.
@@
 Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
+
 \end{abstract}
@@
 
-Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions within galaxies.
-These galaxies however need to be `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axis of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
-For fixed radii $r$ from the galaxy's centre the exerted shear is larger in the direction of the major axis of the total mass distribution of the galaxy than in the direction of the minor axis.
-In case of alignment of the luminous and dark matter and an elliptical halo shape, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
-shape-shear intrinsic alignments (\textit{GI}-term);][]{2004PhRvD..70f3526H} and systematic effects.
-If the distributions are however misaligned or the mass distributions are spherical, the shear signal is expected to be isotropic.
-
-\textbf{\citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
+Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions, but only for `stacked' galaxies \citep{2000astro.ph..6281B,2000ApJ...538L.113N}.
+\citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
 They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
@@
 They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.
-\citet{2015arXiv150603536C} \citet{2015arXiv150704301S} [CLAUDIO: WILL FIX THIS PARAGRAPH]}
 
-% Our best-fit value for the ellipticity of the surface mass density is 0.24, which translates to an axis ratio of 0.78.
-We rule out the hypothesis of no ellipticity at the 4σ confidence level, and ellipticity < 0.12 (axis ratio > 0.89) at the 2σ level.
---> significant detection around LRG with SDSS data
-
-Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass\.
+Recently, \cite{2014arXiv1401.7990C} introduced a new non-parametric lens tool, \Glass.
 Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
@@
 This paper is organised as follows.
-In Section~\ref{sec:shapemethod}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
-In Section~\ref{sec:data}, we present our data compilation with references.
-In Section~\ref{sec:results}, we present our results.
-Finally, in Section~\ref{sec:conclusions} we discuss the implications of these results and we present our main conclusions.
+In \S\ref{sec:glass}, we briefly review the \Glass\ code and define our method to assess shape and alignment of lens galaxies.
+In \S\ref{sec:data}, we present our data compilation with references.
+In \S\ref{sec:results}, we present our results.
+Finally, in \S\ref{sec:conclusions} we discuss the implications of these results and we present our main conclusions.
 
-\section{The lens models}\label{sec:shapemethod}
+\section{\Glass: A non-parametric lens tool}\label{sec:glass}
 
-While it is possible to compute shape parameters for a lensing galaxy by fitting to a parametric shape to the lens, it would make the definition of a shape estimate dependent on the which parametric form was being used.
-Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[e.g.][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}.
-To avoid these problems, we use non-parametric ellipticity estimators, defined as follows.
+\Glass\ is a new `non-parametric' gravitational lens modelling framework \citep{2014arXiv1401.7990C} that generates a distribution of mass models given a set of basic assumptions, or priors.
+Hence, \Glass\ does not yield the most probable mass model.
+Rather, it calculates an ensemble of all allowed models given the data and assumed priors.
+In this context, `non-parametric' really just means that many more parameters than data constraints are used such that the system of equations describing the lensing mass distribution is under-constrained.
+\Glass\ shares some aspects with an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
+Its key improvements upon \PixeLens{} relevant for this paper include:
 
-Lenses are modelled as free-form mass distributions, consisting of mass tiles or pixels.
-Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used.
-Thus the lens models are non-unique, and hence in fact ensembles of these free-form mass distributions are used.
-From such a mass map, an inertia tensor is defined as
+\begin{enumerate}
+\item A new uniform sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} is employed. This allows for large ensembles of $\gtrsim$10,000 models to be efficiently generated. 
+\item With so many models in the final ensemble, we can afford to apply non-linear constraints (for example stellar kinematic data; or the removal of models with spurious extra images) to accept/reject models in a post-processing step.
+\item The central region of the mass map can have a higher resolution to more efficiently capture steep models.
+\item Stellar density can be used as an additional lower-bound constraint on the models. 
+\end{enumerate}
+
+In this paper, the default priors used to model each lens are listed below. Table \ref{tab:lenspriors} identifies lenses for which we have modified these defaults. For each lens we assume:
+
+\begin{enumerate} 
+\item Observational priors (redshifts, image positions relative to lens position).
+\item Image parity to be enforced.
+\item A reconstructed stellar mass map that provides a lower mass bound to each pixel.
+\item The local density gradient to be always pointing within 50$^{\circ}$ of the centre of the distribution, and the circularly-averaged density to never increase outwards.
+\item The fixed, flat cosmology with matter density $\Omega_{m} = 0.28$, the dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.
+\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
+\item The radius of the lens to be set to 12 pixels.
+\end{enumerate}
+
+In cases where more information is available, the following priors are also used:
+
+\begin{enumerate}
+\item[(viii)] A flat prior on measured time delays within the $\pm 1\sigma$-interval.
+\item[(ix)] Point symmetry $\kappa(x,y) = \kappa(-x,-y)$, where the surface mass profile can be assumed to be symmetric ((3+1)-quad configurations and the double \textit{Q0957+561}).
+
+\end{enumerate}
+
+\subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
+We employ a shape definition related to the definition used by \cite{2014arXiv1401.7990C}. The ellipticity parameter $e$ is defined as
+\begin{equation}\label{eq:shapeestimate}
+    e \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
+\end{equation}
+where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues of the inertia tensor $I$ of the mass distribution $M(\boldsymbol{\theta})$. It is defined as
 \begin{equation}\label{eq:inertiatensor}
-I = 
-\begin{pmatrix}
- \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
--\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x}
-\end{pmatrix}
+    I = \begin{pmatrix} \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
+                        -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x} \end{pmatrix}.
 \end{equation}
-where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the mass in a pixel. The eigenvectors of this inertia tensor give the ellipticity axes, and our ellipticity estimator is
-\begin{equation}\label{eq:shapeestimate}
-    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
-\end{equation}
-where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues.
-We use this ellipticity estimators to quantify the shapes both of the stellar-mass distribution and of the dark-matter distribution.
-For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used.
-It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information.
-The mass pixels used in this work are at most 4\% of the diameter of the the full mass map.
-The central region has smaller pixels, to allow for a density cusp at the centre.
-Each model ensemble had $10^4$ models.
-Shape and orientation of the distributions are estimated for each of these models, allowing us to constrain the scatter and thus the the statistical uncertainty in these quantities.
+We use these estimators to quantify the shape of the stellar mass distribution and the dark matter distribution.
+We estimate the latter by reconstructing the total mass distribution with a lower mass prior from the stellar mass distribution and then subtracting the latter off.
+The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of $R_e$, defined as the half-light radius measured with respect to the Petrosian flux.
+As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius.
+The shape estimates do not necessarily need to be the same within different radii -- e.g.
+effects such as isophotal twist \citep[e.g.][and references therein]{1978ComAp...8...27B} can cause differences in the shape estimates between the central and the outer parts of the system.
 
-The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}.
-\Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions and image parities; also time delays, if measured.
-The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work.
-The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass.
-The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter.
-\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN THERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
-Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape).
-The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}.
-Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.
-
-We remark that \Glass\ is closely related to an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
-An important improvement is a better sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} that eliminates the excessive weight \PixeLens\ tended to give to extreme models.
-\Glass\ has also been adapted for lens modelling in citizen science \citep{2015MNRAS.447.2170K}.
+Throughout this paper, we generate in each case an ensemble of 10,000 mass models. Each of these models is analysed individually, yielding a distribution of constrained quantities.
 
 \section{Data}\label{sec:data}
+Stellar mass maps are taken from \cite{2011ApJ...740...97L}.
+In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \cite{2003MNRAS.344.1000B} were obtained.
+The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
+The initial mass function (IMF) was taken to be the log-normal form given by \cite{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
+We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
+While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
+For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
+We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
+We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
+
+The original sample we consider, is presented in \cite{2011ApJ...740...97L} and consists of 21 lens systems.
+It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
+As shown in \cite{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images.
+Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
+This yields a sample consisting of 11 lenses.
+We discuss each of these systems, next.
+
+\textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
+It is part of a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
+
+\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
+A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
+It, however, is more likely a foreground object with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
+This is sufficiently distant to still contribute to the lensing effect.
+
+\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998MNRAS.296..483J,1998AJ....115..377F}.
+There is a foreground group of about 10 member galaxies at $z\sim0.3$, which could affect the modelling \citep{2002AJ....123..627F}.
+
+\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
+It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
+There is also a satellite galaxy to the northwest \citep{2000ApJ...544L..35K}.
+
+\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the centre of a cluster with a high spiral galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
+Due to the large image separation, large physical scales are probed.
+As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg.
+These results are consistent with the centre of the X-ray emission from the cluster \citep{1998ApJ...504..661C}.
+The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
+They however also find a three-day lag between the g- and r-bands, a disagreement at the 2$\sigma$-level.
+They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
+We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
+
+\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{1980Natur.285..641W,2005ApJ...626...51Y}.
+It has measured time delays \citep[see e.g.][]{1997ApJ...475L..85S}.
+In this work, we use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g.
+\cite{1997ApJ...489...21B}.
+The environment of the lens was analysed thoroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
+It is part of a small group of 13 members.
+Also, X-ray emission was detected from the corresponding group and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
+
+\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.
+Although time delays have been reported \citep{2001MNRAS.326.1403P}, it is possible that the measurements are aliases of the actual values \citep{2003AJ....126...29R} and hence are not included in our analysis.
+The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
+Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
+\cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
+
+\textit{B1608+656} (hereafter \textit{1608}) was first reported by \cite{1995ApJ...447L...5M}.
+It consists of two merging galaxies.
+The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
+The system has measured time delays \citep{2002ApJ...581..823F}.
+The environment has been analysed and a group with 8 (9 if merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
+However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
+The data seem to indicate four other groups along the line of sight.
+
+\textit{MG2016+112} (hereafter \textit{2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
+It is the farthest lens we consider in this sample.
+It lies in a cluster that consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
+The cluster shows a high density of galaxies close to the lens in a south-east direction.
+Two lensed images are very close in this fold lens, but could be resolved by \cite{2009MNRAS.394..174M}.
+
+\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
+It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, however the velocity dispersion seems too high.
+As the source redshift is rather low, a large lens mass is required.
+\cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
+To the west of the lens, a group was found at a similar redshift as the lens \citep{1999AJ....117..658F}.
+There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
+As the measurements are however inconclusive, we choose to not include this satellite in our models.
+
+\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
+With a redshift of just $z\sim0.04$ it is the closest lens system of the sample.
+Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
+This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.
+
+Further information on the sample can be found in \citet{2011ApJ...740...97L} and \citet{2012A&A...538A..99S}.
+The most important quantities of each system are given in Table~\ref{tab:lensproperties}.
+Due to the different angular separations of the images and the different angular diameter distances, in each lens galaxy we necessarily probe slightly different scales.
+
 \begin{table}
@@
     \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}.
-References can be found in Section~\ref{sec:data}.
+References can be found in \S\ref{sec:data}.
 The columns are from left to right: the lens redshift $z_L$; the redshift of the source $z_S$; the maximum angular separation between two images $\Delta\theta$; the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$; and information on the environment of the lens.
@@
 The number in the brackets is the number of confirmed members.
-Ellipses indicate lens galaxies with no group members identified so far.}
+Ellipsis indicate lens galaxies with no group members identified so far.}
     \label{tab:lensproperties}
@@
            & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-      2016 & ... & Smaller pixels \\
-      2045 & ... & $\gamma\leq 0.1$, Symm \\
+      2016 & ... & PixRad(16) \\
+      2045 & ... & $\gamma(0.1)$, Symm \\
       2237 & ... & ...\\
     \end{tabular}
-    \caption[width=\linewidth]{Lenses where additional data or priors were used (cf.~Section~\ref{sec:shapemethod}).
-$\Delta t_{BA}$ and so on denote time delays between images as labelled in Table~\ref{tab:lenspositions}; $\gamma$ refers to the allowed external shear; `Symm' means that the mass map was symmetric under rotation by $180^\circ$; `Smaller pixels' indicates that the pixel size was 3\% rather than 4\% of the diameter of the whole mass map.}
+    \caption[width=\linewidth]{Additional priors to the base set described in \S\ref{sec:glass} are listed.
+$\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$ between light from the images B and A.
+The images are defined in Table~\ref{tab:lenspositions}.
+$\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$.
+`Symm' denotes that a point-symmetry prior is employed.
+`PixRad(16)' indicates that the pixel radius was set to 16 pixels.}
     \label{tab:lenspriors}
@@
 
-Stellar mass maps are taken from \citet{2011ApJ...740...97L}.
-In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \citet{2003MNRAS.344.1000B} were obtained.
-The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
-The initial mass function (IMF) was taken to be the log-normal form given by \citet{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
-We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
-While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
-For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
-We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
-We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
-
-The original sample we consider, is presented in \citet{2011ApJ...740...97L} and consists of 21 lens systems.
-It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
-As shown in \citet{2014MNRAS.445.2181C}, the recovery of the shape information of the lens is only good if there are at least four images.
-Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
-This yields a sample consisting of 11 lenses.
-We discuss each of these systems, next.
-
-\textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}.
-It is part of a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.
-
-\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}.
-A close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}.
-It, however, is more likely a foreground object with a redshift of ~0.38 \citep{2011MNRAS.413L..86C}.
-
-\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998MNRAS.296..483J,1998AJ....115..377F}.
-There is a foreground group of about 10 member galaxies at $z\sim0.3$ \citep{2002AJ....123..627F}.
-
-\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
-It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
-There is furthermore a satellite galaxy to the north-west \citep{2000ApJ...544L..35K}.
-\textbf{applied to the binned event positions yields a centroid for the extended emission of where o†sets are $\Delta\alpha = -14.2''$, $\Delta\delta = -39.5''$, with respect to the centroid of component B.
---> PA: -160.2268099}
-
-\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the centre of a cluster with a high spiral galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}.
-Due to the large image separation, large physical scales are probed.
-As listed in Table 3 of \citet{2000ApJ...542...74K}, the position angles to the centre of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg.
-These results are consistent with the centre of the X-ray emission from the cluster \citep{2002ApJ...565...96C}.
-The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
-They however also find a three-day lag between the g- and r-bands, a disagreement at the 2$\sigma$-level.
-They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion.
-We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.
-low
-\textbf{and the cluster center based on the published position (-13.7'', -19.6'') (Angonin-Willaime 1994) et al.
-for the estimated cluster center of mass with respect to image B \citep{1994A&A...291..411A}}
-
-\textbf{The best-fit position angle (north through east) and core radius of the cluster are $59 deg$ and $15.4'' \pm 3.5''$, respectively.
-The Chandra observations of Q0957+561 therefore indicate that the cluster center is located within a core radius of the lens galaxy G1.
-Using the values for and r i provided by our analysis of the c, dc, Chandra observation of Q0957]561, we Ðnd that the cluster shear amplitude c is 0.01 0.009 (90\% confidence level), consistent with the recent model results of Keeton et al.
-(2000).
-4.3"+/-1.3" east and 3.5"+1.2"-0.6" north of image B [B =  0.182 , -1.018] --> PA: 58.6269949 \citep{2002ApJ...565...96C}}
-
-\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{1980Natur.285..641W,2005ApJ...626...51Y}.
-It has measured time delays \citep[see e.g.][]{1997ApJ...475L..85S}.
-In this work, we use recent estimates of the time delays by \citet{2010MNRAS.406.2764T} that differ from previously found values by e.g.
-\citet{1997ApJ...489...21B}.
-The environment of the lens was analysed thoroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}.
-It is part of a small group of 13 members.
-Also, X-ray emission was detected from the corresponding group and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
-\textbf{The maximum X-ray emission for the PG 1115+080 group is near $\Delta\alpha = -21''$ and $\Delta\delta = -14''$ relative to image C of the gravitational lens.
-$\Delta\alpha = -20.6''$ and $\Delta\delta = -15.3''$ --> PA: -126.6 deg}
-
-\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1992MNRAS.259P...1P,1994AJ....107...28Y}.
-Although time delays have been reported \citep{2001MNRAS.326.1403P}, it is possible that the measurements are aliases of the actual values \citep{2003AJ....126...29R} and hence are not included in our analysis.
-The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}.
-Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
-\citet{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.
-\textbf{The maximum X-ray emission for the B1422+231 group is at about  $\Delta\alpha = 7''$ and  $\Delta\delta = -9''$ relative to image B of the gravitational lens.
-$\Delta\alpha = 6.2''$ and $\Delta\delta = -9.6''$ --> PA: 147.1 deg}
-
-\textit{B1608+656} (hereafter \textit{1608}) was first reported by \citet{1995ApJ...447L...5M}.
-It consists of two merging galaxies.
-The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}.
-The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment has been analysed and a group with 8 (9 if the merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
-However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
-The data seem to indicate four other groups along the line of sight.
-\textbf{(Offset 25'' PA 30 deg; position-weighted) (Offset 8'' PA -5 deg; luminosity-weighted)}
-
-\textit{MG2016+112} (hereafter \textit{2016}) is a giant elliptical galaxy \citep{1984Sci...223...46L,1986AJ.....91..991S}.
-It is the farthest lens we consider in this sample.
-It lies in a cluster that consists of 69 probable galaxies \citep{2003MNRAS.344..337T}.
-The cluster shows a high density of galaxies close to the lens in a south-east direction.
-Two lensed images are very close in this fold lens, but could be resolved by \citet{2009MNRAS.394..174M}.
-\textbf{$\sim$ 130-140 deg}
-
-\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}.
-It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, however the velocity dispersion seems too high.
-As the source redshift is rather low, a large lens mass is required.
-\citet{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-North-west of the lens, there is evidence for a group at a similar redshift as the lens \citep{1999AJ....117..658F}.
-There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}.
-As the measurements are however inconclusive, we choose to not include this satellite in our models.
-\textbf{$\sim$ -60 deg}
-\textbf{satellite within Einstein radius}
-
-\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}.
-With a redshift of just $z\sim0.04$ it is the closest lens system of the sample.
-Due to its low redshift, the probed physical scales are small, making the bulge component of the galaxy dominant.
-This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.
-low
-
-Further information on the sample can be found in \citet{2011ApJ...740...97L} and \citet{2012A&A...538A..99S}.
-The most important quantities of each system are given in Table~\ref{tab:lensproperties}.
-Due to the different angular separations of the images and the different angular diameter distances, in each lens galaxy we necessarily probe slightly different scales.
-
 \section{Results}\label{sec:results}
@@
   \centering
-  \includegraphics[width=.75\linewidth]{Figures/kappaplot.pdf}
-  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution.
-The vertical lines denote the radial distances of the source images from the centre of the lens galaxies.
-We note that in the case of \textit{0957}, there are two lensed components of the source galaxy.
-Thus, the green resp.
-blue vertical lines correspond to the images of the respective components.
-The green curves show the contributions by the dark matter in the strong lens galaxies as reconstructed by \Glass.
-The dashed black lines show the corresponding profiles for dark matter halos that follow a NFW density profile.
-The parameters in the NFW distribution are calibrated in order for the values of the derived convergences $\langle\kappa\rangle$ to match the correspnding values of the reconstructed profiles at one pixel past the last image radius.}
-  \label{fig:kappaplot}
+  \includegraphics[width=.8\linewidth]{Figures/wedges_shears.pdf}
+  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $e_{dm}$ and the stellar component $e_{*}$.
+The wedges show the alignment of the semi-major axes of the components.
+In case of alignment of the semi-major axes (Aligned), the wedges are vertical.
+In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
+The opening angle displays the statistical error in the shape estimate of the dark matter halo.
+Both the errors in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within.
+The lenses are additionally color-coded in terms of the required external shear in modelling the lens.}
+  \label{fig:wedgesall}
 \end{figure*}
@@
   \centering
-  \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=\linewidth]{The reconstructed lens galaxies are displayed according to the reconstructed total shapes of the dark matter halos $s_{dm}$ and the stellar components $s_{*}$.
-The wedges show the alignment of the semi-major axes of the components.
-In case of alignment of the respective semi-major axes (Aligned), the wedges are vertical.
-In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
-The opening angle of each wedge displays the statistical error in the shape estimate of the dark matter halos.
-Both the uncertainties in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models of the ensemble of solutions lie within.
-The lens galaxies are additionally color-coded in terms of the required external shear in reconstructing the mass distribution.
-The right panel shows the region in the left panel denoted by a dashed rectangle in greater detail.}
-  \label{fig:wedgesall}
-\end{figure*}
-
-\begin{table*}
-  \begin{center}
-    \begin{tabular}{l | l l l l l l l l}
-      Lens & $s_{*}$ & $s_{dm}$ & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm,t}}{e_{*}}$ & $|\gamma|$ & $\theta_{g}$ [deg]\\ \hline
-      0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
-      0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
-      0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
-      0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
-      0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
-      1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
-      1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
-      1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
-      2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
-      2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
-      2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
-    \end{tabular}
-    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$; $\frac{e_{dm}}{e_{*}}$ denotes the ratio of the dark matter relative to the stellar distribution; $\frac{e_{dm,t}}{e_{*}}$ refers to this ratios, where the ellipticity component of the dark matter distribution is projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.}
-    \label{tab:ellipratios}
-  \end{center}
-\end{table*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=.75\linewidth]{Figures/wedges.pdf}
+  \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
   \caption[width=\linewidth]{Similar to Figure~\ref{fig:wedgesall}.
@@
 
-We have applied \Glass\ to the data set described in Section~\ref{sec:data} consisting of 11 lenses. The reconstructed stellar and dark mass maps for each individual lens are given in the Appendix.
+We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses. The reconstructed stellar and dark mass maps for each individual lens are given in the Appendix.
 
-\begin{table}
-  \begin{center}
-    \begin{tabular}{l | l l}
-      Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
-      0047 & 360.7  & 9.98   \\
-      0414 & 256.9  & 12.38  \\
-      0712 & 446.5  & 15.45  \\
-      0911 & 369.1  & 22.66  \\
-      0957 & 1053.1 & 175.16 \\
-      1115 & 616.8  & 31.06  \\
-      1422 & 450.8  & 13.05  \\
-      1608 & 317.1  & 9.99   \\
-      2016 & 299.3  & 22.14  \\
-      2045 & 562.8  & 103.97 \\
-      2237 & 1961.0 & 485.26 \\
-    \end{tabular}
-    \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
-    \label{tab:virialmasses}
-  \end{center}
-\end{table}
-
-\subsection{Radial dark matter profiles}
-We compare the profiles of the reconstructed dark matter distributions of the individual strong lens galaxies with Navarro-Frenk-White-profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}
-\begin{equation}\label{eq:nfw}
-   \frac{\rho(R)}{\rho_{crit}} = \frac{\delta_{c}}{(cR/R_{vir})(1+cR/R_{vir})},
-\end{equation}
-where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology being considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
-The latter is related to $M_{vir}$ \citep{2011ApJ...740..102K}
-\begin{equation}\label{eq:concentration}
- \begin{split}
-   c(M_{vir}, z) = & c_{0}(z)\left(\frac{M_{vir}}{10^{12}h^{-1}M_{\odot}\right)^{-0.075} \\ & \times \left[1+\left(\frac{M_{vir}}{M_{0}(z)}\right)^{0.26}\right]},
- \end{split}
-\end{equation}
-where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters.
-The relation is constrained at specific redshifts are listed in Table 3 of \citet{2011ApJ...740..102K}.
-For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
-
-As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$, which we set with Equation~\ref{eq:concentration}, there is only one degree of freedom, $M_{vir}$.
-We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ to match one pixel past the last image radius for the reconstructed dark matter distribution and the chose NFW-profile.
-
-Figure~\ref{fig:kappaplot} displays the results, while the masses are given in Table~\ref{tab:virialmasses}.
-\textbf{[HERE SOME COMMENT ON THE MASSES WE HAVE FIT; I'VE INCLUDED THEM TEMPORARILY (!) IN TABLE~\ref{tab:virialmasses} TO DECIDE WHAT WE DO WITH THEM AND HOW WE COMMENT ON THAT SOME OF THESE MASSES ARE RATHER LARGE]}.
-Except for \textit{0047}, where only the bulge is probed and significant deviations are expected, the profiles agree broadly.
-There are slight differences in some systems ...
-\textbf{[HERE WHY WE DON'T WORRY; MAYBE LINK TO FEI LI'S RESULTS?].}
-
-\subsection{Shape and alignment of the dark matter halos}
-Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions.
+Figure~\ref{fig:wedgesall} shows our results for the shapes (see \S\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions.
 In this Figure, the full distribution up to one pixel past the last-image radius $R_{L}$ is probed.
@@
 Secondly, most lenses lie in the bottom-left corner: the dark matter distributions have typically low eccentricities, while the stellar distributions can be rather elliptical.
-Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 0.4$).
+Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($e_* > 0.4$).
 At the same time, they show a very strong alignment between their stellar and dark matter distributions.
@@
 
-Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim0.05$).
+Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.05$).
 By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
 The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
-As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
+As described furthermore in \S\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
 {\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
@@
 
-\subsection{Consistency with weak lensing estimates}
-The ellipticity values $s_{*}$ and $s_{dm}$ shown in Figures~\ref{fig:wedgesall} and \ref{fig:wedgesradii} and the values of the required external shear when reconstructing the lens galaxy are listed in Table~\ref{tab:ellipratios}.
-Furthermore, the ellipticity $s$ can be converted to the ellipticity $e=(a-b)/(a+b)$, where $a$ and $b$ are the semi-major and semi-minor axes of the lens galaxy, by applying the relation
-\begin{equation}
-   e = \frac{s}{2-s}.
-\end{equation}
-
-The latter ellipticity definition is commonly used in weak lensing.
-Especially, it is employed in \citet{2015arXiv150704301S}, a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter.
-This probe however cannot constrain the $e_{dm}$ directly.
-Rather, it is sensitive to the ratio $f_{h} = e_{dm,t}/e_{*}$, where $e_{dm,t}$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
-In case of perfect alignment and identical shape, $f_{h}$ is equal to 1.
-In practive however, $f_{h}$ deviates from 1, as among other effects, which cannot be disentangled, misalignment of the two distributions and different shapes affect its value.
-
-In \citet{2015arXiv150704301S} a measurement on data from the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H}.
-The constraints in the highest mass bin of early-type galaxies ($\mathrm{log_{10}}M_{*}>11$) on the CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
-On the simulated data, including cosmic shear and realistic misalignments between the luminous and the dark matter, the constraints in the highest mass bin and for redshifts $0.4<z<0.6$ are $f_{h} = 0.359^{+0.011}_{-0.010}$.
-Due to a narrower intrinsic ellipticity distribution in the simulated data however, the latter constraints need to be corrected for with a factor $\approx 1/1.46$.
-Our results are broadly consistent with both constraints, with the exception of the galaxy merger system \textit{1608} and \textit{1115}.
-The sample is however not large enough for a more quantitative comparison.
-
 \section{Conclusions}\label{sec:conclusions}
-We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass\.
-We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014MNRAS.445.2181C}.
-We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see Section~\ref{sec:shapemethod}).
-We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
+We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014arXiv1401.7990C}.
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $e = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see \S\ref{sec:shapemethod}).
+We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
 
@@
 \begin{itemize}
-\item \textbf{[ADD HERE SOMETHING ON THE KAPPA PROFILES?]}
-
 \item We found that the dark matter haloes are rounder than the light distribution over the range $1R_e < R < 5R_e$.
@@
 The same trend can furthermore be seen for the dark matter, although the data are also consistent with no change in shape.
-The dark matter haloes are never more elliptical than $s_{dm} = 0.2$, while their stars can extend to $s_* > 0.3$.
+The dark matter haloes are never more elliptical than $e_{dm} = 0.2$, while their stars can extend to $e_* > 0.3$.
 
-\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark.
+\item Three systems have a high stellar ellipticity ($e_* > 0.45$) and correspondingly high alignment between light and dark.
 One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.
@@
 \item Galaxies with high dark matter ellipticity and weak external shear show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
-This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
-
-\item \textbf{[ADD HERE SOMETHING ON THE CONSISTENCY WITH WEAK LENSING RESULTS?]}
-
+This is reassuring since isolated misaligned galaxies are expected to be unstable.
 \end{itemize}
-
-\textbf{[ADD THE COMMENTED REFERENCES ON MISALIGNMENTS BEING UNSTABLE IN THE .tex-FILE IN A NEW PARAGRAPH]}
-%Relevant references for misalignments being unstable: 
-%- http://adsabs.harvard.edu/abs/1978MNRAS.183..779B : 1978MNRAS.183..779B
-%- http://adsabs.harvard.edu/abs/1981MNRAS.196..455B : 1981MNRAS.196..455B
-%- http://adsabs.harvard.edu/abs/1979ApJ...233..872H : 1979ApJ...233..872H
-%- http://adsabs.harvard.edu/abs/1984ApJ...276..101S : 1984ApJ...276..101S
-%- http://adsabs.harvard.edu/abs/1987A%26A...182..202R : 1987A&A...182..202R
-%- http://adsabs.harvard.edu/abs/1988A%26A...206..269M : 1988A&A...206..269M
-%- http://adsabs.harvard.edu/abs/2007ApJ...670.1027A : 2007ApJ...670.1027A
 
@@
 
-In this Appendix, we show the results of our lens modelling for each individual lens galaxy (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
+In this Appendix, we show the results of our lens modelling for each individual lens (Figures~\ref{fig:lensreconstruction1}-\ref{fig:lensreconstruction3}).
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses31.pdf}
-  \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy.
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens.
 The panels show, from left to right: the arrival time surface (the images are marked by the green circles); the surface mass density of the dark matter; and the surface mass density of the stars.
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses32.pdf}
-  \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
   \label{fig:lensreconstruction2}
@@
   \includegraphics[width=.8\linewidth]{Figures/AllLenses33.pdf}
-  \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
+  \caption[width=.65\linewidth]{The results of our lens modelling for each individual lens. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
   \label{fig:lensreconstruction3}
@@
 
-\section{Degeneracy between $\theta_{dm}$ and $\theta_{g}$}\label{sec:shearshapedeg}
-\begin{figure*}
-  \centering
-  \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
-  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution of the ensemble of solutions.
-The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample.
-All the angles are measured north through east.}
-  \label{fig:thetascatter}
-\end{figure*}
-
-Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy.
-We note that the constraints on the direction of the external shear are stronger than the ones on the dark matter distribution \textbf{[INSERT HERE WHY HE THINK THAT IS]}.
-A slight degeneracy between the angles is evident.
-However, \textbf{...
-[WHY THIS IS EXPECTED, AND WHY OUR MISALIGNMENT RESULT STILL HOLDS].}
-
 \end{document}

### 2015-09-08 shapes/paper.tex
Polished text, fixed typos

@@
 Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions within galaxies.
-These galaxies however need to be `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axis of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
-For fixed radii $r$ from the galaxy's centre the exerted shear is larger in the direction of the major axis of the total mass distribution of the galaxy than in the direction of the minor axis.
-In case of alignment of the luminous and dark matter and an elliptical halo shape, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
+These galaxies however need to be `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axes of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
+Given an elliptical total mass distribution, the exerted shear is larger in the direction of the major axis of the distribution than in the direction of the minor axis for fixed radii $r$ from the galaxy's center.
+In case of alignment of the luminous and dark matter and an elliptical shape of the distribution of the latter, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
 intrinsic alignments][]{2004PhRvD..70f3526H} and systematic effects.
@@
 This measurement has been perfomed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results.
-These analyses mainly differ in the data sets, the selection of lens galaxies, the estimators used, and the treatment of systematics \citep[see][]{2015arXiv150704301S}.
-Recently, \citet{2015arXiv150603536C} made this measurement on Luminous Red Galaxies (LRG) identified in the Sloan Digital Sky Survey (SDSS), and report a significant detection of dark matter halo ellipticity.
-Shortly thereafter, \citet{2015arXiv150704301S} performed this measurement on data from the Canada France Hawaii Lensing Survey (CFHTLenS).
-Furthermore, the method was tested using the Milennium Simulation \citep{2005Natur.435..629S}, while exploring the effect of cosmic shear and misalignments of the luminous and dark matter distributions.
+The analyses differ mainly in the data sets, the selection of lens galaxies, the estimators employed, and the treatment of systematics \citep[see][]{2015arXiv150704301S}.
+Recently, \citet{2015arXiv150603536C} made this measurement on Luminous Red Galaxies (LRG) in the Sloan Digital Sky Survey (SDSS), and report a significant detection of dark matter halo ellipticity.
+Shortly thereafter, \citet{2015arXiv150704301S} performed this measurement on blue and red galaxies in general identified in data from the Canada France Hawaii Lensing Survey (CFHTLenS), without being able to report a definite detection of halo ellipticity.
+However, their method was tested using the Milennium Simulation \citep{2005Natur.435..629S}, while exploring the effect of cosmic shear and misalignments of the luminous and dark matter distributions.
+This allows one to understand and predict the expected signal.
 % \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
@@
 We discuss each of these systems, next.
-We note that all the angles are measured north through east and relative to the lens galaxy.
+We note that all the position angles are measured north through east and relative to the lens galaxy.
 
@@
 Furthermore, the center was identified to be at a position angle of about 30$^{\circ}$ (resp.
--5$^{\circ}$) if the member galaxies' positions are straight averaged (resp.
+-5$^{\circ}$) if the member galaxies' positions are averaged without weighting (resp.
 weighted by luminosity).
@@
 This makes the treatment of the stellar populations easier, as derivations of the stellar M/L are more difficult in the presence of star forming regions typical of disc galaxies, where there are no simple stellar populations usually assumed in SPS models.
-low
 
@@
 In case of alignment of the respective semi-major axes (Aligned), the wedges are vertical.
-In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal.
+In case of alignment of the semi-major with the semi-minor axis (Anti-Aligned), the wedges are horizontal.
 The opening angle of each wedge displays the statistical error in the shape estimate of the dark matter halos.
@@
     \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
     \label{tab:ellipratios}
@@
 \end{equation}
-where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology being considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
+where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
 The latter is related to $M_{vir}$ \citep{2011ApJ...740..102K}
@@
 where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters.
-The relation is constrained at specific redshifts are listed in Table 3 of \citet{2011ApJ...740..102K}.
+The relation is constrained at specific redshifts and the parameters are listed in Table 3 of \citet{2011ApJ...740..102K}.
 For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
 
-As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$, which we set with Equation~\ref{eq:concentration}, there is only one degree of freedom, $M_{vir}$.
-We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ to match one pixel past the last image radius for the reconstructed dark matter distribution and the chose NFW-profile.
+As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$, which we however set with Equation~\ref{eq:concentration}, there is only one degree of freedom, $M_{vir}$.
+We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ of the reconstructed dark matter distribution and the NFW-profile to match at one pixel past the last image radius.
 
@@
 The ellipticity values $s_{*}$ and $s_{dm}$ shown in Figures~\ref{fig:wedgesall} and \ref{fig:wedgesradii} and the values of the required external shear when reconstructing the lens galaxy are listed in Table~\ref{tab:ellipratios}.
-Furthermore, the ellipticity $s$ can be converted to the ellipticity $e=(a-b)/(a+b)$, where $a$ and $b$ are the semi-major and semi-minor axes of the lens galaxy, by applying the relation
+Furthermore, the ellipticity $s$ is converted to the ellipticity definition $e=(a-b)/(a+b)$, where $a$ and $b$ are the semi-major and semi-minor axes of the lens galaxy, by applying the relation
 \begin{equation}
@@
 Especially, it is employed in \citet{2015arXiv150704301S}, a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter.
-This probe however cannot constrain the $e_{dm}$ directly.
+Weak lensing as a probe however cannot constrain $e_{dm}$ directly.
 Rather, it is sensitive to the ratio $f_{h} = (e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$, where $\Delta\theta$ is the misalignment angle between the two distributions, and $e_{dm}\cdot\mathrm{cos} 2\Delta\theta$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
 In case of perfect alignment and identical shape, $f_{h}$ is equal to 1.
-In practive however, $f_{h}$ deviates from 1, as among other effects, which cannot be disentangled, misalignment of the two distributions and different shapes affect its value.
+In practive however, $f_{h}$ deviates from 1, as among other effects which cannot be disentangled, misalignment of the two distributions and different ellipticities change its value.
 
-In \citet{2015arXiv150704301S} a measurement on CFHTLenS data and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H}.
-The constraints in the highest mass bin of early-type galaxies ($\mathrm{log_{10}}M_{*}>11$) on the CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
+In \citet{2015arXiv150704301S} a measurement on CFHTLenS data and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H} is performed.
+The constraints in the highest mass bin of early-type galaxies ($\mathrm{log_{10}}M_{*}>11$) on CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
 On the simulated data, including cosmic shear and realistic misalignments between the luminous and the dark matter, the constraints in the highest mass bin and for redshifts $0.4<z<0.6$ are $f_{h} = 0.359^{+0.011}_{-0.010}$.
@@
 Our results are broadly consistent with both constraints, with the exception of the galaxy merger system \textit{1608} and \textit{1115}.
-The sample is however not large enough for a more quantitative comparison.
+The sample is however not large enough for a quantitative comparison.
 
@@
   \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
-  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution of the ensemble of solutions.
-The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample.
-The angles are rotated to be measured north through east here.}
+  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution.
+The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the ensemble of solutions.
+Here, the angles are rotated to be measured north through east.}
   \label{fig:thetascatter}
@@
 
-Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy.
+Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of the dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy.
 We note that the constraints on the direction of the external shear are stronger than the ones on the dark matter distribution \textbf{[INSERT HERE WHY HE THINK THAT IS]}.

### 2015-09-09 shapes/paper.tex
edits

@@
 Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}.
-The mass pixels used in this work are at most 4\% of the diameter of the the full mass map.
+The mass pixels used in this work are larger than image pixels, but at most 4\% of the diameter of the the full mass map.
 The central region has smaller pixels, to allow for a density cusp at the centre.
@@
 \textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN HERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
-Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape).
-The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}.
-Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.
+Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape).
+The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}.\footnote{Alternatively, see \citep{2015MNRAS.447.2170K} for a more intuitive account of \Glass.
+Section~3.2 therein summarises the prior.} Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.
 
-We remark that \Glass\ is closely related to an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
+\Glass\ is closely related to an earlier code \PixeLens\ \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely different code base.
 An important improvement is a better sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} that eliminates the excessive weight \PixeLens\ tended to give to extreme models.
-\Glass\ has also been adapted for lens modelling in citizen science \citep{2015MNRAS.447.2170K}.
 
@@
 \begin{table}
-  \begin{center}
-    \begin{tabular}{l l l}
-      Lens & Time delays [days] & Additional priors \\ \hline
-      0047 & ... & ...\\
-      0414 & ... & ...\\
-      0712 & ... & ...\\
-      0911 & $\Delta t_{BA}=146^{+4}_{-4}$ & Symm\\
-      0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
-      1115 & $\Delta t_{BA}=12.0^{+2}_{-2}$ & ...\\
+  \begin{center} \begin{tabular}{l l l l}
+      Lens & Time delays [days] & Symmetric? & Comments \\ \hline
+      0047 &  & \\
+      0414 &  & \\
+      0712 &  & \\
+      0911 & $\Delta t_{BA}=146^{+4}_{-4}$ & yes\\
+      0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & yes \\
+      1115 & $\Delta t_{BA}=12.0^{+2}_{-2}$ & \\
            & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
-      1422 & ... & Symm \\
-      1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & ...\\
+      1422 &  & yes \\
+      1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & \\
            & $\Delta t_{CA}=36.0^{+1.5}_{-1.5}$ & \\
            & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-      2016 & ... & Smaller pixels \\
-      2045 & ... & $\gamma\leq 0.1$, Symm \\
-      2237 & ... & ...\\
+      2016 &  & & Smaller pixels \\
+      2045 &  & yes & $\gamma\leq 0.1$ \\
+      2237 &  & \\
     \end{tabular}
     \caption[width=\linewidth]{Lenses where additional data or priors were used (cf.~Section~\ref{sec:shapemethod}).
-$\Delta t_{BA}$ and so on denote time delays between images as labelled in Table~\ref{tab:lenspositions}; $\gamma$ refers to the allowed external shear; `Symm' means that the mass map was symmetric under rotation by $180^\circ$; `Smaller pixels' indicates that the pixel size was 3\% rather than 4\% of the diameter of the whole mass map.}
+$\Delta t_{BA}$ and so on denote time delays between images as labelled in Table~\ref{tab:lenspositions}; $\gamma$ refers to the allowed external shear; Symmetric `yes' means the mass map is symmetric under rotation by $180^\circ$; `Smaller pixels' indicates that the mass pixels are 3\% (rather than 4\%) of the diameter of the whole mass map.}
     \label{tab:lenspriors}

### 2015-09-09 shapes/paper.tex
some fixes

--- 2015-09-08 shapes/paper.tex
@@
       Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
-      % 0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
-      % 0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
-      % 0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
-      % 0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
-      % 0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
-      % 1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
-      % 1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
-      % 1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
-      % 2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
-      % 2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
-      % 2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
       0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.00 & 120$\pm$5 \\
@@
     \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.}
     \label{tab:ellipratios}
@@
 \end{table*}
+
+% \begin{table*}
+%   \begin{center}
+%     \begin{tabular}{l | l l l l l l l l l}
+%       Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
+%       0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
+%       0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
+%       0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
+%       0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
+%       0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
+%       1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
+%       1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
+%       1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
+%       2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
+%       2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
+%       2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
+%     \end{tabular}
+%     \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
+%     \label{tab:ellipratios}
+%   \end{center}
+% \end{table*}
 
@@
 \section{Conclusions}\label{sec:conclusions}
-We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass\.
+We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
 We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014MNRAS.445.2181C}.

### 2015-09-09 shapes/paper.tex
Added environment in Table, changed layout of reply to the referee

@@
+% \RequirePackage{rotating}
 \documentclass[useAMS,usenatbib]{mn2e}
@@
 \usepackage{amssymb}
+% \usepackage{geometry}
+\usepackage{lscape}
 
@@
 
+\begin{landscape}
  \begin{table*}
   \begin{center}
-    \begin{tabular}{l | l l l l l l l l l}
-      Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
-      0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.00 & 120$\pm$5 \\
-      0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.00 & 166$\pm$4 \\
-      0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.00 & 141$\pm$3 \\
-      0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.00 & 99$\pm$2 \\
-      0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.00 & 159$\pm$8 \\
-      1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.00 & 154$\pm$3 \\
-      1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.00 & 39$\pm$1 \\
-      1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.00 & 145$\pm$2 \\
-      2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.00 & 42$\pm$4 \\
-      2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.00 & 23$\pm$7 \\
-      2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.00 & 159$\pm$4 \\
+    \begin{tabular}{l l l l l l l l l l l l l}
+      % Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ & Env \\ \hline
+      % 0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.01 & 120$\pm$5 & 360.7  & 9.98 & G(9) \\
+      % 0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.02 & 166$\pm$4 & 256.9  & 12.38 & ... \\
+      % 0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 & 446.5  & 15.45 & ... \\
+      % 0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.02 & 99$\pm$2 & 369.1  & 22.66 & C \\
+      % 0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 & 1053.1 & 175.16 & C \\
+      % 1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.01 & 154$\pm$3 & 616.8  & 31.06 & G(13) \\
+      % 1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.01 & 39$\pm$1 & 450.8  & 13.05 & G(17) \\
+      % 1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 & 317.1  & 9.99 & G(8) \\
+      % 2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 & 299.3  & 22.14 & C(69) \\
+      % 2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 & 562.8  & 103.97 & ... \\
+      % 2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.01 & 159$\pm$4 & 1961.0 & 485.26 & ... \\
+      Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ & Env \\ \hline
+      0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.01 & 120$\pm$5 & 360.7  & 9.98 & G(9) \\
+      0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.02 & 166$\pm$4 & 256.9  & 12.38 & ... \\
+      0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 & 446.5  & 15.45 & ... \\
+      0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.02 & 99$\pm$2 & 369.1  & 22.66 & C \\
+      0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 & 1053.1 & 175.16 & C \\
+      1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.01 & 154$\pm$3 & 616.8  & 31.06 & G(13) \\
+      1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.01 & 39$\pm$1 & 450.8  & 13.05 & G(17) \\
+      1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 & 317.1  & 9.99 & G(8) \\
+      2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 & 299.3  & 22.14 & C(69) \\
+      2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 & 562.8  & 103.97 & ... \\
+      2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.01 & 159$\pm$4 & 1961.0 & 485.26 & ... \\
     \end{tabular}
-    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
+    % \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
+The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.}
+    \caption{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
 The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.}
@@
  \end{table*}
+\end{landscape}
+
+% \begin{table}
+%   \begin{center}
+%     \begin{tabular}{l | l l}
+%       Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
+%       0047 & 360.7  & 9.98   \\
+%       0414 & 256.9  & 12.38  \\
+%       0712 & 446.5  & 15.45  \\
+%       0911 & 369.1  & 22.66  \\
+%       0957 & 1053.1 & 175.16 \\
+%       1115 & 616.8  & 31.06  \\
+%       1422 & 450.8  & 13.05  \\
+%       1608 & 317.1  & 9.99   \\
+%       2016 & 299.3  & 22.14  \\
+%       2045 & 562.8  & 103.97 \\
+%       2237 & 1961.0 & 485.26 \\
+%     \end{tabular}
+%     \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
+%     \label{tab:virialmasses}
+%   \end{center}
+% \end{table}
 
@@
 
-\begin{table}
-  \begin{center}
-    \begin{tabular}{l | l l}
-      Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
-      0047 & 360.7  & 9.98   \\
-      0414 & 256.9  & 12.38  \\
-      0712 & 446.5  & 15.45  \\
-      0911 & 369.1  & 22.66  \\
-      0957 & 1053.1 & 175.16 \\
-      1115 & 616.8  & 31.06  \\
-      1422 & 450.8  & 13.05  \\
-      1608 & 317.1  & 9.99   \\
-      2016 & 299.3  & 22.14  \\
-      2045 & 562.8  & 103.97 \\
-      2237 & 1961.0 & 485.26 \\
-    \end{tabular}
-    \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
-    \label{tab:virialmasses}
-  \end{center}
-\end{table}
+% \begin{table}
+%   \begin{center}
+%     \begin{tabular}{l | l l}
+%       Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
+%       0047 & 360.7  & 9.98   \\
+%       0414 & 256.9  & 12.38  \\
+%       0712 & 446.5  & 15.45  \\
+%       0911 & 369.1  & 22.66  \\
+%       0957 & 1053.1 & 175.16 \\
+%       1115 & 616.8  & 31.06  \\
+%       1422 & 450.8  & 13.05  \\
+%       1608 & 317.1  & 9.99   \\
+%       2016 & 299.3  & 22.14  \\
+%       2045 & 562.8  & 103.97 \\
+%       2237 & 1961.0 & 485.26 \\
+%     \end{tabular}
+%     \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
+%     \label{tab:virialmasses}
+%   \end{center}
+% \end{table}
 

### 2015-09-09 shapes/paper.tex
Fixed Table 3 layout, changed x-axis in Figure 1, some additional details

--- 2015-09-09 shapes/paper.tex
@@
 \section{Data}\label{sec:data}
+\setlength\tabcolsep{5pt}
 \begin{table}
   \begin{center}
-    \begin{tabular}{l r r r r l}
-      Lens & \multicolumn{1}{c}{$z_{L}$} & \multicolumn{1}{c}{$z_{S}$} & \multicolumn{1}{c}{$\Delta\theta$ [kpc]} & \multicolumn{1}{c}{$R_{L}$/$R_{e}$} & Environment \\ \hline
-      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9) \\
+    \begin{tabular}{l l l l l l}
+      Lens & $z_{L}$ & $z_{S}$ & $\Delta\phi$ [kpc] & $R_{L}/R_{e}$ & Environment \\ \hline
+      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9)$^{a}$ \\
       0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... \\
       0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... \\
-      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C \\
-      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C \\
-      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13) \\
-      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17) \\
-      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8) \\
-      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69) \\
+      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C$^{b}$ \\
+      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C$^{c}$ \\
+      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13)$^{a}$ \\
+      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17)$^{a}$ \\
+      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8)$^{d}$ \\
+      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69)$^{e}$ \\
       2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... \\
@@
 The number in the brackets is the number of confirmed members.
-Ellipses indicate lens galaxies with no group members identified so far.}
+Ellipses indicate lens galaxies with no group members identified so far.
+\newline $^{a}$ \citet{2011ApJ...726...84W}; $^{b}$ \citet{2001ApJ...555....1M}; $^{c}$ e.g.
+\citet{1992MNRAS.254P..27G}; $^{d}$ \citet{2006ApJ...642...30F}; $^{e}$ \citet{2003MNRAS.344..337T}.}
     \label{tab:lensproperties}
@@
 \end{table}
+\setlength\tabcolsep{6pt}
 
@@
       Lens & Time delays [days] & Symmetric? & Comments \\ \hline
-      0047 &  & \\
-      0414 &  & \\
-      0712 &  & \\
-      0911 & $\Delta t_{BA}=146^{+4}_{-4}$ & yes\\
-      0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & yes \\
-      1115 & $\Delta t_{BA}=12.0^{+2}_{-2}$ & \\
-           & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
-      1422 &  & yes \\
-      1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & \\
+      0047 & ... & ... & ... \\
+      0414 & ... & ... & ... \\
+      0712 & ... & ... & ... \\
+      0911 & $\Delta t_{BA}=146^{+4}_{-4}$ & yes & ... \\
+      0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & yes & ... \\
+      1115 & $\Delta t_{BA}=12.0^{+2}_{-2}$ & ... & ... \\
+           & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & ... & ... \\
+      1422 & ... & yes & ... \\
+      1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & ... & ... \\
            & $\Delta t_{CA}=36.0^{+1.5}_{-1.5}$ & \\
            & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
-      2016 &  & & Smaller pixels \\
-      2045 &  & yes & $\gamma\leq 0.1$ \\
-      2237 &  & \\
+      2016 & ... & ... & Smaller pixels \\
+      2045 & ... & yes & $\gamma\leq 0.1$ \\
+      2237 & ... & ... & ... \\
     \end{tabular}
@@
 
+\setlength\tabcolsep{5pt}
 \begin{table*}
   \begin{center}
-    \begin{tabular}{l | l l l l l l l l l}
-      Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
-      0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.00 & 120$\pm$5 \\
-      0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.00 & 166$\pm$4 \\
-      0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.00 & 141$\pm$3 \\
-      0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.00 & 99$\pm$2 \\
-      0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.00 & 159$\pm$8 \\
-      1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.00 & 154$\pm$3 \\
-      1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.00 & 39$\pm$1 \\
-      1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.00 & 145$\pm$2 \\
-      2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.00 & 42$\pm$4 \\
-      2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.00 & 23$\pm$7 \\
-      2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.00 & 159$\pm$4 \\
+    \begin{tabular}{l l l l l l l l l l l l l}
+      % \multirow{2}{*}{Lens} & \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{Env} \\
+      %  & & & & & & & & & & [kpc] & $[10^{12} \ M_{\odot}]$ & \\ \hline
+      % 0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.01 & 120$\pm$5 & 360.7  & 10.0 & G(9) \\
+      % 0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.02 & 166$\pm$4 & 256.9  & 12.4 & ... \\
+      % 0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 & 446.5  & 15.5 & ... \\
+      % 0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.02 & 99$\pm$2 & 369.1  & 22.7 & C \\
+      % 0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 & 1053.1 & 175.2 & C \\
+      % 1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.01 & 154$\pm$3 & 616.8  & 31.1 & G(13) \\
+      % 1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.01 & 39$\pm$1 & 450.8  & 13.0 & G(17) \\
+      % 1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 & 317.1  & 10.0 & G(8) \\
+      % 2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 & 299.3  & 22.1 & C(69) \\
+      % 2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 & 562.8  & 104.0 & ... \\
+      % 2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.01 & 159$\pm$4 & 1961.0 & 485.3 & ... \\
+      \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} &  \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
+       & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & & & \\ \hline
+      0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
+      0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
+      0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
+      0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
+      0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
+      1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
+      1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
+      1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
+      2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
+      2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
+      2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
     \end{tabular}
-    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.}
+    \caption{Fitted virial masses and radii and the ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
+`Env' is the `Environment' column in Table~\ref{tab:lensproperties}; $R_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle of the required external shear in the modeling of the strong lens galaxy; the ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.}
     \label{tab:ellipratios}
@@
 \end{table*}
+\setlength\tabcolsep{6pt}
 
-% \begin{table*}
+% \begin{table}
 %   \begin{center}
-%     \begin{tabular}{l | l l l l l l l l l}
-%       Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
-%       0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
-%       0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
-%       0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
-%       0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
-%       0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
-%       1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
-%       1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
-%       1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
-%       2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
-%       2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
-%       2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
+%     \begin{tabular}{l | l l}
+%       Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
+%       0047 & 360.7  & 9.98   \\
+%       0414 & 256.9  & 12.38  \\
+%       0712 & 446.5  & 15.45  \\
+%       0911 & 369.1  & 22.66  \\
+%       0957 & 1053.1 & 175.16 \\
+%       1115 & 616.8  & 31.06  \\
+%       1422 & 450.8  & 13.05  \\
+%       1608 & 317.1  & 9.99   \\
+%       2016 & 299.3  & 22.14  \\
+%       2045 & 562.8  & 103.97 \\
+%       2237 & 1961.0 & 485.26 \\
 %     \end{tabular}
-%     \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modeling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
-%     \label{tab:ellipratios}
+%     \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
+%     \label{tab:virialmasses}
 %   \end{center}
-% \end{table*}
+% \end{table}
 
@@
 
-\begin{table}
-  \begin{center}
-    \begin{tabular}{l | l l}
-      Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
-      0047 & 360.7  & 9.98   \\
-      0414 & 256.9  & 12.38  \\
-      0712 & 446.5  & 15.45  \\
-      0911 & 369.1  & 22.66  \\
-      0957 & 1053.1 & 175.16 \\
-      1115 & 616.8  & 31.06  \\
-      1422 & 450.8  & 13.05  \\
-      1608 & 317.1  & 9.99   \\
-      2016 & 299.3  & 22.14  \\
-      2045 & 562.8  & 103.97 \\
-      2237 & 1961.0 & 485.26 \\
-    \end{tabular}
-    \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
-    \label{tab:virialmasses}
-  \end{center}
-\end{table}
-
-\subsection{Radial dark matter profiles}
+\subsection{Radial dark matter profiles}\label{sec:radialprofiles}
 We compare the profiles of the reconstructed dark matter distributions of the individual strong lens galaxies with Navarro-Frenk-White-profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}
@@
 
-Figure~\ref{fig:kappaplot} displays the results, while the masses are given in Table~\ref{tab:virialmasses}.
-\textbf{[HERE SOME COMMENT ON THE MASSES WE HAVE FIT; I'VE INCLUDED THEM TEMPORARILY (!) IN TABLE~\ref{tab:virialmasses} TO DECIDE WHAT WE DO WITH THEM AND HOW WE COMMENT ON THAT SOME OF THESE MASSES ARE RATHER LARGE]}.
+Figure~\ref{fig:kappaplot} displays the results, while the masses are given in Table~\ref{tab:ellipratios}.
+\textbf{[HERE SOME COMMENT ON THE MASSES WE HAVE FIT; I'VE INCLUDED THEM TEMPORARILY (!) IN TABLE~\ref{tab:ellipratios} TO DECIDE WHAT WE DO WITH THEM AND HOW WE COMMENT ON THAT SOME OF THESE MASSES ARE RATHER LARGE]}.
 Except for \textit{0047}, where only the bulge is probed and significant deviations are expected, the profiles agree broadly.
@@
   \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
-  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution.
+  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the induced position angle of the required external shear $\theta_{g}$ of each reconstructed mass distribution.
 The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the ensemble of solutions.

### 2015-09-17 shapes/paper.tex
Justin's edits

@@
 \begin{abstract}
-We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies, finding over the range of several multiples of the half-light radii that the dark matter haloes are rounder than the stellar mass distributions.
-Averaging over larger radii, the ellipticity, as defined using the ratio of the semi-minor and semi-major axes, increases both in their dark matter and stellar components.
-While dark matter haloes are never more elliptical than $s_{dm} = 0.3$, their stars can extend to $s_* > 0.3$.
-Three systems, in particular, have a high stellar ellipticity ($s_* > 0.4$) and correspondingly a high alignment between the luminous and the dark matter distribution.
-One of these -- {\it B1608+656} -- is a known merging pair; we suggest that the other two ({\it B0712+472} and {\it B2016+112}) may also be recent post-merger systems.
+We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies.
+We show that the projected dark matter density profile in these systems -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy.
+Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling.
+We find that over several half-light radii, the dark matter haloes of these lenses are rounder than their stellar mass distributions.
+While the haloes are never more elliptical than $s_{dm} = 0.3$ (where $s$ is defined such that $s=0$ is spherical and $s=1$ is infinitely flattened), their stars can extend to $s_* > 0.3$.
 Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
 This is reassuring since isolated misaligned galaxies are expected to be unstable.
-
-Our results provide a new constraint on galaxy formation models that must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
+Our results provide a new constraint on galaxy formation models.
+For a given cosmology, these must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
+{\bf JR.
+I hope you agree with my analysis of the radial profiles.
+I've spotted a very cute little result here already and thought we should highlight it.
+I discuss it further in the results and conclusions.
+Also, we now define $s$ to be the `ellipticity'.
+But later on when discussing weak lensing we define a different ellipticity parameter $e$.
+The referee took us to task on this also I think.
+Are there really two different definitions of ellipticity in the literature?
+If so, perhaps we should clarify this up-front when we define $s$.
+Alternatively, if $s$ is unique to our paper then why not just change $s \rightarrow e$ throughout?
+Or we could call our $s$ parameter the `shape parameter' and $e$ the `ellipticity'.
+I have no strong view on which is best, but it's a bit confusing as it is right now}.
 \end{abstract}
@@
 Weak lensing can also be used to probe the shape and alignment between the luminous and dark matter distributions within galaxies.
-These galaxies however need to be `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axes of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
-Given an elliptical total mass distribution, the exerted shear is larger in the direction of the major axis of the distribution than in the direction of the minor axis for fixed radii $r$ from the galaxy's center.
+However, this requires that the galaxies are `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axes of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
+This will lead to an isotropic mean shear around galaxies if the mass distributions are spherical, or if dark and light are randomly aligned.
+The weak lensing measurement has been performed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results.
+The analyses differ mainly in the data sets used; the selection of lens galaxies; the estimators employed; and the treatment of systematics \citep[see e.g.][]{2015arXiv150704301S}.
+For example, \citet{2015arXiv150603536C} have recently made the measurement on Luminous Red Galaxies (LRG) taken from the Sloan Digital Sky Survey (SDSS) reporting a significant detection of dark matter halo ellipticity; while \citet{2015arXiv150704301S} performed a similar measurement on blue and red galaxies from the Canada France Hawaii Lensing Survey (CFHTLenS) finding no definite detection.
+Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} show that it is challenging to detect halo ellipticity using current weak lensing surveys.
+This suggests that when fully accounting for survey biases and systematics, the measurement is not yet possible.
+{\bf JR.
+Is this correct?
+I found the discussion here ambiguous previously.}
+
+%Given an elliptical total mass distribution, the exerted shear is larger in the direction of the major axis of the distribution than in the direction of the minor axis for fixed radii $r$ from the galaxy's center.
 In case of alignment of the luminous and dark matter and an elliptical shape of the distribution of the latter, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
 intrinsic alignments][]{2004PhRvD..70f3526H} and systematic effects.
-If the distributions are however misaligned or the mass distributions are spherical, the shear signal is expected to be isotropic.
 
-This measurement has been perfomed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results.
-The analyses differ mainly in the data sets, the selection of lens galaxies, the estimators employed, and the treatment of systematics \citep[see][]{2015arXiv150704301S}.
-Recently, \citet{2015arXiv150603536C} made this measurement on Luminous Red Galaxies (LRG) in the Sloan Digital Sky Survey (SDSS), and report a significant detection of dark matter halo ellipticity.
-Shortly thereafter, \citet{2015arXiv150704301S} performed this measurement on blue and red galaxies in general identified in data from the Canada France Hawaii Lensing Survey (CFHTLenS), without being able to report a definite detection of halo ellipticity.
-However, their method was tested using the Milennium Simulation \citep{2005Natur.435..629S}, while exploring the effect of cosmic shear and misalignments of the luminous and dark matter distributions.
-This allows one to understand and predict the expected signal.
 % \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
@@
 Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass.
-Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
+Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential.
 In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies.
@@
 
-While it is possible to compute shape parameters for a lensing galaxy by fitting to a parametric shape to the lens, it would make the definition of a shape estimate dependent on the which parametric form was being used.
-Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[e.g.][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}.
+While it is possible to compute shape parameters for a lensing galaxy by fitting a parametric shape to the lens, it makes the definition of a shape estimate dependent on the parametric form being used.
+Moreover, the commonly-used parametric forms for modelling lensing galaxies \citep[e.g.][]{2001astro.ph..2341K} do not allow for features like twisting isodensity contours, which can arise from the projection of triaxial ellipsoids with no intrinsic twists \citep[e.g.][and references therein]{1978ComAp...8...27B}.
 To avoid these problems, we use non-parametric ellipticity estimators, defined as follows.
@@
 Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used.
-Thus the lens models are non-unique, and hence in fact ensembles of these free-form mass distributions are used.
-From such a mass map, an inertia tensor is defined as
+Thus the lens models are non-unique, and hence we build {\it ensembles} of these free-form mass distributions.
+From such a mass map, an inertia tensor is defined as:
 \begin{equation}\label{eq:inertiatensor}
@@
 where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues.
-We use this ellipticity estimators to quantify the shapes both of the stellar-mass distribution and of the dark-matter distribution.
-For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used.
+We use this ellipticity estimator to quantify the shapes both of the stellar-mass distribution $s_*$ and of the dark-matter distribution $s_{dm}$.
+By default, we use the dark and stellar mass distributions out to the outermost lensing image.
+In Figure \ref{fig:wedgesradii}, we explore the effect of averaging instead over multiples of the half-light radius $R_e$.
+The mass pixels used in this work are larger than image pixels, but at most 4\% of the diameter of the the full mass map.
+The central region has smaller pixels, to allow for a density cusp at the centre.
+
+%For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stars, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used.
 It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information \textbf{[CLAUDIO: Actually, I estimate the shapes for the luminous and dark matter in the same way.
@@
 Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}.
-The mass pixels used in this work are larger than image pixels, but at most 4\% of the diameter of the the full mass map.
-The central region has smaller pixels, to allow for a density cusp at the centre.
 
-We estimate the orientation of the distributions of luminous and dark matter by computing the angles $\theta_{*}$ resp.
-$\theta_{dm}$ of the eigenvector corresponding to the eigenvalue $\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$) relative to the x-axis.
-The misalignment angle $\Delta\theta$ between the distributions is then defined as
+We estimate the orientation of the distributions of luminous and dark matter by computing the angles $\theta_{*}$ and $\theta_{dm}$ of the eigenvector corresponding to the eigenvalue $\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$) relative to the $x$-axis.
+The misalignment angle $\Delta\theta$ between the distributions is then defined as:
 \begin{equation}
@@
 
-Each model ensemble consists of $10^4$ models, for all of which we apply our estimators for the shape and the alignment of the distributions.
-By identifying the median value and the range 68\% of all the values lie within of this distribution of estimated values, these quantities are constrained and the statistical uncertainties estimated.
+Each model ensemble consists of $10^4$ models.
+We apply our shape and alignment estimators to each model, in this way obtaining the median and 68\% confidence intervals of $s$ and $\Delta \theta$, for each lens.
 
 The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}.
-\Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions and image parities; also time delays, if measured.
+\Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions, image parities and time delays (if measured).
 The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work.
@@
 The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter.
-\textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN HERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined.
-Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape).
-The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}.\footnote{Alternatively, see \citep{2015MNRAS.447.2170K} for a more intuitive account of \Glass.
-Section~3.2 therein summarises the prior.} Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.
+The lensing observables and assumed non-negative dark matter by themselves leave the mass distribution under-determined.
+Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the same shape).
+The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} (alternatively, see \citep{2015MNRAS.447.2170K}; section~3.2 for a more intuitive account of \Glass).
+Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of \citet{2014MNRAS.445.2181C}.
 
@@
 Stellar mass maps are taken from \citet{2011ApJ...740...97L}.
-In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}, and with the resulting flux maps stellar mass maps using the synthesis of the stellar-population (SPS) models of \citet{2003MNRAS.344.1000B} were obtained.
+In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}.
+This was then converted to a stellar mass map using the stellar-population synthesis (SPS) models of \citet{2003MNRAS.344.1000B}.
 The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
@@
 We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
-While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
+While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L, depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
 For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
-We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that Salpeter IMF is too heavy and gives no solutions.
+We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that a Salpeter IMF is too heavy and gives no solutions.
 We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
@@
 We note that all the position angles are measured north through east and relative to the lens galaxy.
+
+\subsection{The individual lenses}
 
@@
 The vertical lines denote the radial distances of the source images from the centre of the lens galaxies.
-We note that in the case of \textit{0957}, there are two lensed components of the source galaxy.
-Thus, the green resp.
-blue vertical lines correspond to the images of the respective components.
+For \textit{0957}, there are two lensed components of the source galaxy denoted by the green and blue vertical lines.
 The green curves show the contributions by the dark matter in the strong lens galaxies as reconstructed by \Glass.
 The dashed black lines show the corresponding profiles for dark matter halos that follow a NFW density profile.
-The parameters in the NFW distribution are calibrated in order for the values of the derived convergences $\langle\kappa\rangle$ to match the correspnding values of the reconstructed profiles at one pixel past the last image radius.}
+The parameters in the NFW distribution are calibrated such that the convergence $\langle\kappa\rangle$ matches the corresponding values of the reconstructed profiles at one pixel past the last image radius.
+Notice that those lenses where the outermost image is within $\sim 10$\,kpc appear contracted as compared to an NFW profile; those where the outermost image is further out $> 10$\,kpc are well fit by the NFW form.
+In all cases there is a sharp fall off in the \Glass\ dark matter profile at large radii due to the edge of the mass map.}
   \label{fig:kappaplot}
@@
 \subsection{Radial dark matter profiles}\label{sec:radialprofiles}
-We compare the profiles of the reconstructed dark matter distributions of the individual strong lens galaxies with Navarro-Frenk-White-profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}
+Before discussing the shapes and alignments, we first measure the dark matter profiles of the strong lens galaxies, comparing these with projected Navarro-Frenk-White profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}:
 \begin{equation}\label{eq:nfw}
@@
 where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
-The latter is related to $M_{vir}$ \citep{2011ApJ...740..102K}
+The concentration is well-correlated with $M_{vir}$ with some redshift dependence \citep{2011ApJ...740..102K}:
 \begin{equation}\label{eq:concentration}
@@
 \end{equation}
-where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters.
-The relation is constrained at specific redshifts and the parameters are listed in Table 3 of \citet{2011ApJ...740..102K}.
+where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters (see Table 3 of \citet{2011ApJ...740..102K}).
 For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
+{\bf JR.
+If this is projected mass, then wouldn't it be better to use $\Sigma$ rather than $\rho$.
+Also, we should explain that $\rho_{\rm crit}(z)$ is the critical density of the universe, not to be confused with the critical lensing surface density.
+It is also a function of redshift (I presume we change this also with the lens redshift).
+We should also define $\delta_c$.
+Finally, I would recommend Awriting down the relationship between $\rho(R) \equiv \Sigma(R)$ and $\langle \kappa(R)\rangle$.}
 
-As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$, which we however set with Equation~\ref{eq:concentration}, there is only one degree of freedom, $M_{vir}$.
+As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$ is well-correlated with $M_{vir}$ (equation~\ref{eq:concentration}), there is only one degree of freedom, $M_{vir}$.
 We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ of the reconstructed dark matter distribution and the NFW-profile to match at one pixel past the last image radius.
 
-Figure~\ref{fig:kappaplot} displays the results, while the masses are given in Table~\ref{tab:ellipratios}.
-\textbf{[HERE SOME COMMENT ON THE MASSES WE HAVE FIT; I'VE INCLUDED THEM TEMPORARILY (!) IN TABLE~\ref{tab:ellipratios} TO DECIDE WHAT WE DO WITH THEM AND HOW WE COMMENT ON THAT SOME OF THESE MASSES ARE RATHER LARGE]}.
-Except for \textit{0047}, where only the bulge is probed and significant deviations are expected, the profiles agree broadly.
-There are slight differences in some systems ...
-\textbf{[HERE WHY WE DON'T WORRY; MAYBE LINK TO FEI LI'S RESULTS?].}
+Figure~\ref{fig:kappaplot} displays the results, while the virial masses (derived following the above procedure) are given in Table~\ref{tab:ellipratios}.
+In all cases the dark matter distribution either follows the NFW profile or is steeper, as expected if dark halos contract in response to baryon cooling and star formation \citep[e.g.][]{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}.
+At large radii, there is in all cases a sharp fall off in the \Glass\ dark matter density profiles.
+This owes to the edge of the mass map and for this reason we should not trust the reconstructed profiles outside of the outermost image.
+Interestingly, there is significant scatter from galaxy to galaxy in the shape of the azimuthally averaged dark matter density profile.
+This appears to correlate well with the physical radii probed.
+The galaxies that most closely follow an NFW profile -- \textit{0911}, \textit{0957}, \textit{0414}, \textit{1608}, \textit{2016}, \textit{2045} -- all have an outermost image at radii $> 10$\,kpc.
+The other lenses -- \textit{0047}, \textit{0712}, \textit{1115}, \textit{1422}, \textit{2237} -- probe smaller radii and show signs of contraction with respect to NFW.
+In the most extreme example -- \textit{2237} -- the outermost image probes only the bulge region of this galaxy ($\sim 0.8$\,kpc).
+The dark matter profile is substantially steeper than NFW while the derived virial mass is implausibly large (since we have not accounted for any such contraction in deriving it; see Table \ref{tab:ellipratios}).
+Our results suggest that the dark matter halos in these lensing galaxies are broadly consistent with contracted NFW profiles.
+Lenses with close-in images -- that are expected to inhabit less massive dark matter halos -- show more apparent contraction.
+There could be several explanations for this behaviour.
+It could be a selection effect where lower mass galaxies can only strong lens if they are substantially contracted; it could owe to more massive halos being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems.
+We will explore such questions in a forthcoming paper where we will present the dark matter radial profiles of a larger sample of lenses, considering varying stellar initial mass function, and explicitly modelling dark matter contraction.
 
@@
 One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}.
-We suggest that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.
+We speculate that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.
 
@@
 As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
-{\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
+{\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C} {\bf JR.
+I didn't understand this sentence.
+Maybe rephrase?}.
 Besides these three lens systems, one stands out from the rest, however.
@@
 
+\section{Discussion}
+
 \subsection{Consistency with weak lensing estimates}
@@
 Due to a narrower intrinsic ellipticity distribution in the simulated data however, the latter constraints need to be corrected for with a factor $\approx 1/1.46$.
-Our results are broadly consistent with both constraints, with the exception of the galaxy merger system \textit{1608} and \textit{1115}.
-The sample is however not large enough for a quantitative comparison.
+Our results are broadly consistent with both constraints, with the exception of the galaxy merger system \textit{1608} and the interesting and highly misaligned lens \textit{1115}.
+Our sample is, however, not large enough for a quantitative comparison.
 
-\section{Conclusions}\label{sec:conclusions}
-We have measured the shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
-We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential to determine the projected shape of their dark matter haloes \citep{2014MNRAS.445.2181C}.
-We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see Section~\ref{sec:shapemethod}).
-We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+\subsection{The lack of isolated misaligned lenses}
 
-Our key results are as follows:
+Our lens sample is small -- just 11 strong lensing systems -- yet it is interesting that we find no lens with strong misalignment and weak external shear.
+This is perhaps to be expected.
+\citet{XXX} show that YYY.
 
-\begin{itemize}
-\item \textbf{[ADD HERE SOMETHING ON THE KAPPA PROFILES?]}
-
-\item We found that the dark matter haloes are rounder than the light distribution over the range $1R_e < R < 5R_e$.
-As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions.
-The same trend can furthermore be seen for the dark matter, although the data are also consistent with no change in shape.
-The dark matter haloes are never more elliptical than $s_{dm} = 0.2$, while their stars can extend to $s_* > 0.3$.
-
-\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark.
-One of these -- {\it1608} -- is a known merging pair; we speculate on the other two lens systems ({\it0712} and {\it2016}) being recent post-merger systems as well.
-
-\item Galaxies with high dark matter ellipticity and weak external shear show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
-This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
-
-\item \textbf{[ADD HERE SOMETHING ON THE CONSISTENCY WITH WEAK LENSING RESULTS?]}
-
-\end{itemize}
-
-\textbf{[ADD THE COMMENTED REFERENCES ON MISALIGNMENTS BEING UNSTABLE IN THE .tex-FILE IN A NEW PARAGRAPH]}
+\textbf{JR.
+I think comparisons with weak lensing have a section of their own and don't need to go in the conclusions.
+I moved them to this discussion section, though, to ensure that they stand out.
+I added a new subsection in discussion also about misalignments and stability (above).
+This should deal with that issue.}
 %Relevant references for misalignments being unstable: 
@@
 %- http://adsabs.harvard.edu/abs/2007ApJ...670.1027A : 2007ApJ...670.1027A
+% AND :: 1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D
+
+\section{Conclusions}\label{sec:conclusions}
+We have measured the radial density profile, shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
+We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential.
+In a previous paper, we showed that data of this quality are required to determine the projected shape of dark matter haloes \citep{2014MNRAS.445.2181C}.
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see Section~\ref{sec:shapemethod}).
+We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+
+Our key results are as follows:
+
+\begin{itemize}
+\item The projected dark matter density profile in these systems -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy.
+Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling.
+There could be several explanations for this behaviour.
+It could be a selection effect where lower mass galaxies (expected to have closer-in images) can only strong lens if they are substantially contracted; it could owe to more massive halos (with further out images) being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems.
+We will explore such questions in a forthcoming paper.
+
+\item The dark matter haloes of all lenses in our sample are rounder than the light distribution over the range $1R_e < R < 5R_e$.
+As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions.
+The same trend can be seen also for the dark matter, though the effect is not statistically significant.
+The dark matter haloes are never more elliptical than $s_{dm} = 0.2$, while their stars can extend to $s_* > 0.3$.
+
+\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark.
+One of these -- {\it1608} -- is a known merging pair.
+We speculate that the other two lens systems ({\it0712} and {\it2016}) may also be recent post-merger systems.
+
+\item Galaxies with high dark matter ellipticity and weak external shear show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
+This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
+
+\end{itemize}
 
 Our results provide a new constraint on galaxy formation models that must explain the origin of low eccentricity dark matter haloes (not expected in pure dark-matter-only simulations), and highly misaligned lens systems.
-A possible remedy is the fact that we constrain 2D projections of the lensing mass and the light distribution integrated along the line of sight.
-The misalignments we identified also present a new challenge for those alternative gravity theories in which the light is the only source of gravity in a galaxy, where light and dark must necessarily be highly correlated.
+Such misalignments also present a new challenge for those alternative gravity theories in which light is the only source of gravity, since in such models light and dark must necessarily be highly correlated.
 

### 2015-09-18 shapes/paper.tex
Small changes to the abstract by Justin

@@
 \begin{abstract}
-We measure the shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies.
-We show that the projected dark matter density profile in these systems -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy.
+We measure the projected density profile, shape and alignment of the stellar and dark matter mass distribution in 11 strong-lens galaxies.
+We find that the projected dark matter density profile -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy.
 Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling.
@@
 This is perhaps to be expected.
-\citet{XXX} show that YYY.
-
-\textbf{JR.
-I think comparisons with weak lensing have a section of their own and don't need to go in the conclusions.
-I moved them to this discussion section, though, to ensure that they stand out.
-I added a new subsection in discussion also about misalignments and stability (above).
-This should deal with that issue.}
-%Relevant references for misalignments being unstable: 
-%- http://adsabs.harvard.edu/abs/1978MNRAS.183..779B : 1978MNRAS.183..779B
-%- http://adsabs.harvard.edu/abs/1981MNRAS.196..455B : 1981MNRAS.196..455B
-%- http://adsabs.harvard.edu/abs/1979ApJ...233..872H : 1979ApJ...233..872H
-%- http://adsabs.harvard.edu/abs/1984ApJ...276..101S : 1984ApJ...276..101S
-%- http://adsabs.harvard.edu/abs/1987A%26A...182..202R : 1987A&A...182..202R
-%- http://adsabs.harvard.edu/abs/1988A%26A...206..269M : 1988A&A...206..269M
-%- http://adsabs.harvard.edu/abs/2007ApJ...670.1027A : 2007ApJ...670.1027A
-% AND :: 1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D
+\citet{1979ApJ...233..872H} were the first to study the stability of orbits within triaxial figures, likely the physical situation in real elliptical galaxies.
+They found that while stable periodic orbits exist in all three symmetry planes of a triaxial figure, tube orbits about the intermediate axis are unstable.
+\citet{1985MNRAS.215..731D} studied the case of orbits misaligned to all three symmetry planes.
+They found that while misaligned stable orbits can be found, they exit only for limited ranges of the Hamiltonian.
+\citet{1988A&A...206..269M} extended these results to rotating triaxial figures showing that once rotation is included such orbits become even rarer.
+These early results are supported by more recent numerical work.
+\citet{2013MNRAS.434.2971D} show that discs can never form perpendicular to the intermediate axis, in good agreement with earlier work by \citet{1979ApJ...233..872H}.
+However, they find that discs can survive off-axis if gas is present, since gas cooling can maintain the misalignment.
+\citet{2015MNRAS.452.4094D} go on to show that if this gas supply is switched off (as is the case for giant elliptical galaxies), then continuing collisionless minor mergers/interactions bring the disc rapidly into alignment with its host halo.
+Taken together, these results suggest that alignment between light and dark should be the norm for isolated gas-free triaxial galaxies.
 
 \section{Conclusions}\label{sec:conclusions}
-We have measured the radial density profile, shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
+We have measured the projected radial density profile, shape and alignment of the stellar and dark matter distributions in 11 lens systems using a new non-parametric lens tool, \Glass.
 We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential.

### 2015-09-19 shapes/paper.tex
Fixed half of Justin's highlighted points

@@
 I have no strong view on which is best, but it's a bit confusing as it is right now}.
+{\bf CB. Yes, will change that.}
 \end{abstract}
@@
 However, this requires that the galaxies are `stacked' \citep{2000astro.ph..6281B,2000ApJ...538L.113N}, typically by aligning the major axes of the light distribution \citep[e.g.][]{2004ApJ...606...67H}.
-This will lead to an isotropic mean shear around galaxies if the mass distributions are spherical, or if dark and light are randomly aligned.
+This will lead, in absence of contaminating effects \citep[e.g.
+intrinsic alignments][]{2004PhRvD..70f3526H}, to an isotropic mean shear around galaxies if the mass distributions are spherical, or if dark and light are randomly aligned.
 The weak lensing measurement has been performed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results.
@@
 For example, \citet{2015arXiv150603536C} have recently made the measurement on Luminous Red Galaxies (LRG) taken from the Sloan Digital Sky Survey (SDSS) reporting a significant detection of dark matter halo ellipticity; while \citet{2015arXiv150704301S} performed a similar measurement on blue and red galaxies from the Canada France Hawaii Lensing Survey (CFHTLenS) finding no definite detection.
-Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} show that it is challenging to detect halo ellipticity using current weak lensing surveys.
-This suggests that when fully accounting for survey biases and systematics, the measurement is not yet possible.
-{\bf JR.
-Is this correct?
-I found the discussion here ambiguous previously.}
+Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} however characterize the expected signal assuming different misalignment models between the luminous and dark matter.
 
@@
 \end{equation}
-where $\rho_{crit}$ and $\delta_{c}$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
+where the critical density of the universe $\rho_{crit}(z)$ and $\delta_{c}(z)$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
 The concentration is well-correlated with $M_{vir}$ with some redshift dependence \citep{2011ApJ...740..102K}:
@@
 If this is projected mass, then wouldn't it be better to use $\Sigma$ rather than $\rho$.
-Also, we should explain that $\rho_{\rm crit}(z)$ is the critical density of the universe, not to be confused with the critical lensing surface density.
 It is also a function of redshift (I presume we change this also with the lens redshift).
@@
 Finally, I would recommend Awriting down the relationship between $\rho(R) \equiv \Sigma(R)$ and $\langle \kappa(R)\rangle$.}
+
+{\bf CB. Yes, will change that.}
 
@@
 As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
-{\it0414} has a perturbed along the line of sight contributing to the lensing effect \citep{2011MNRAS.413L..86C} {\bf JR.
-I didn't understand this sentence.
-Maybe rephrase?}.
+Along the line of sight to the lens system {\it0414} there has furthermore another galaxy been found, which contributes to the lensing effect \citep{2011MNRAS.413L..86C}.
 Besides these three lens systems, one stands out from the rest, however.

### 2015-09-20 shapes/paper.tex
Changed second part of Justin's suggestions

@@
 We find that over several half-light radii, the dark matter haloes of these lenses are rounder than their stellar mass distributions.
-While the haloes are never more elliptical than $s_{dm} = 0.3$ (where $s$ is defined such that $s=0$ is spherical and $s=1$ is infinitely flattened), their stars can extend to $s_* > 0.3$.
+While the haloes are never more elliptical than $e_{dm} = 0.2$, their stars can extend to $e_* > 0.2$.
 Galaxies with high dark matter ellipticity and weak external shear show strong alignment between light and dark; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
@@
 For a given cosmology, these must explain the origin of both very round dark matter haloes and misaligned strong-lens systems.
-{\bf JR.
-I hope you agree with my analysis of the radial profiles.
-I've spotted a very cute little result here already and thought we should highlight it.
-I discuss it further in the results and conclusions.
-Also, we now define $s$ to be the `ellipticity'.
-But later on when discussing weak lensing we define a different ellipticity parameter $e$.
-The referee took us to task on this also I think.
-Are there really two different definitions of ellipticity in the literature?
-If so, perhaps we should clarify this up-front when we define $s$.
-Alternatively, if $s$ is unique to our paper then why not just change $s \rightarrow e$ throughout?
-Or we could call our $s$ parameter the `shape parameter' and $e$ the `ellipticity'.
-I have no strong view on which is best, but it's a bit confusing as it is right now}.
-{\bf CB. Yes, will change that.}
 \end{abstract}
@@
 \begin{equation}\label{eq:shapeestimate}
-    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
+    e \equiv \frac{\lambda_{1}-\lambda_{2}}{\lambda_{1}+\lambda_{2}},
 \end{equation}
 where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues.
-We use this ellipticity estimator to quantify the shapes both of the stellar-mass distribution $s_*$ and of the dark-matter distribution $s_{dm}$.
+We use this ellipticity estimator to quantify the shapes both of the stellar-mass distribution $e_*$ and of the dark-matter distribution $e_{dm}$.
 By default, we use the dark and stellar mass distributions out to the outermost lensing image.
@@
 The central region has smaller pixels, to allow for a density cusp at the centre.
-
-%For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stars, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used.
-It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information \textbf{[CLAUDIO: Actually, I estimate the shapes for the luminous and dark matter in the same way.
-I only consider different Petrosian radii in Figure 3, setting different multiples of $R_e$ as a limit for both distributions.
-Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}.
 
@@
 Each model ensemble consists of $10^4$ models.
-We apply our shape and alignment estimators to each model, in this way obtaining the median and 68\% confidence intervals of $s$ and $\Delta \theta$, for each lens.
+We apply our shape and alignment estimators to each model, in this way obtaining the median and 68\% confidence intervals of $e$ and $\Delta \theta$, for each lens.
 
@@
   \centering
-  \includegraphics[width=.75\linewidth]{Figures/kappaplot.pdf}
+  \includegraphics[width=.7\linewidth]{Figures/kappaplot.pdf}
   \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution.
@@
   \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=\linewidth]{The reconstructed lens galaxies are displayed according to the reconstructed total shapes of the dark matter halos $s_{dm}$ and the stellar components $s_{*}$.
+  \caption[width=\linewidth]{The reconstructed lens galaxies are displayed according to the reconstructed total shapes of the dark matter halos $e_{dm}$ and the stellar components $e_{*}$.
 The wedges show the alignment of the semi-major axes of the components.
@@
 
-\setlength\tabcolsep{5pt}
+% \setlength\tabcolsep{5pt}
 \begin{table*}
   \begin{center}
-    \begin{tabular}{l l l l l l l l l l l l l}
-      % \multirow{2}{*}{Lens} & \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{Env} \\
-      %  & & & & & & & & & & [kpc] & $[10^{12} \ M_{\odot}]$ & \\ \hline
-      % 0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.01 & 120$\pm$5 & 360.7  & 10.0 & G(9) \\
-      % 0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.02 & 166$\pm$4 & 256.9  & 12.4 & ... \\
-      % 0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 & 446.5  & 15.5 & ... \\
-      % 0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.02 & 99$\pm$2 & 369.1  & 22.7 & C \\
-      % 0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 & 1053.1 & 175.2 & C \\
-      % 1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.01 & 154$\pm$3 & 616.8  & 31.1 & G(13) \\
-      % 1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.01 & 39$\pm$1 & 450.8  & 13.0 & G(17) \\
-      % 1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 & 317.1  & 10.0 & G(8) \\
-      % 2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 & 299.3  & 22.1 & C(69) \\
-      % 2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 & 562.8  & 104.0 & ... \\
-      % 2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.01 & 159$\pm$4 & 1961.0 & 485.3 & ... \\
-      \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} &  \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
-       & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & & & \\ \hline
-      0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
-      0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
-      0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
-      0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
-      0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
-      1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
-      1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
-      1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
-      2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
-      2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
-      2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
+    \begin{tabular}{l l l l l l l l l l l}
+      % \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} &  \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
+      %  & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & & & \\ \hline
+      % 0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
+      % 0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
+      % 0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
+      % 0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
+      % 0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
+      % 1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
+      % 1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
+      % 1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
+      % 2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
+      % 2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
+      % 2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
+      \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
+       & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & \\ \hline
+      0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
+      0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
+      0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
+      0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
+      0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
+      1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
+      1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
+      1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
+      2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
+      2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
+      2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
     \end{tabular}
     \caption{Fitted virial masses and radii and the ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-`Env' is the `Environment' column in Table~\ref{tab:lensproperties}; $R_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle of the required external shear in the modeling of the strong lens galaxy; the ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.}
+`Env' is the `Environment' column in Table~\ref{tab:lensproperties}; $R_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.}
     \label{tab:ellipratios}
@@
 \end{table*}
-\setlength\tabcolsep{6pt}
-
-% \begin{table}
-%   \begin{center}
-%     \begin{tabular}{l | l l}
-%       Lens & $R_{vir}$ [kpc] & $M_{vir} \ [10^{12} \ M_{\odot}]$ \\ \hline
-%       0047 & 360.7  & 9.98   \\
-%       0414 & 256.9  & 12.38  \\
-%       0712 & 446.5  & 15.45  \\
-%       0911 & 369.1  & 22.66  \\
-%       0957 & 1053.1 & 175.16 \\
-%       1115 & 616.8  & 31.06  \\
-%       1422 & 450.8  & 13.05  \\
-%       1608 & 317.1  & 9.99   \\
-%       2016 & 299.3  & 22.14  \\
-%       2045 & 562.8  & 103.97 \\
-%       2237 & 1961.0 & 485.26 \\
-%     \end{tabular}
-%     \caption[width=\linewidth]{\textbf{[TEMPORARY; IF WE KEEP THIS IN SOME FORM, PROBABLY AS ADDITIONAL COLUMNS TO TABLE~\ref{tab:ellipratios}]}}
-%     \label{tab:virialmasses}
-%   \end{center}
-% \end{table}
+% \setlength\tabcolsep{6pt}
 
@@
 \subsection{Radial dark matter profiles}\label{sec:radialprofiles}
-Before discussing the shapes and alignments, we first measure the dark matter profiles of the strong lens galaxies, comparing these with projected Navarro-Frenk-White profiles \citep[NFW;][]{1996ApJ...462..563N} truncated at the virial radius $R_{vir}$ \citep{2011ApJ...740..102K}:
+Before discussing the shapes and alignments, we first measure the dark matter profiles of the strong lens galaxies, comparing these with Navarro-Frenk-White profiles \citep[NFW;][]{1996ApJ...462..563N}, given by \citep{2011ApJ...740..102K}:
 \begin{equation}\label{eq:nfw}
@@
 \end{equation}
-where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters (see Table 3 of \citet{2011ApJ...740..102K}).
-For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
-{\bf JR.
-If this is projected mass, then wouldn't it be better to use $\Sigma$ rather than $\rho$.
-It is also a function of redshift (I presume we change this also with the lens redshift).
-We should also define $\delta_c$.
-Finally, I would recommend Awriting down the relationship between $\rho(R) \equiv \Sigma(R)$ and $\langle \kappa(R)\rangle$.}
+where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters (see Table 3 of \citet{2011ApJ...740..102K}). For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
 
-{\bf CB. Yes, will change that.}
+For a NFW-profile truncated at the virial radius $R_{vir}$, the projected surface mass density $\Sigma(x)$, where $x = cR/R_{vir}$, can be expressed as \citep{2009JCAP...01..015B}:
+\begin{equation}
+ \begin{aligned}
+  \Sigma(x) = & \frac{M_1}{R_{vir}^2}\frac{c^4}{2\pi(c^2+1)^2}\left[\frac{c^2+1}{x^2-1}[1-F(x)]+2F(x) \right. \\
+  & \left. -\frac{\pi}{\sqrt{c^2+x^2}}+\frac{c^2-1}{c\sqrt{c^2+x^2}}L(x)\right],
+ \end{aligned}
+\end{equation}
+where
+\begin{equation}
+  M_{vir} = M_{1} \frac{\tau^2}{(\tau^2+1)^2}\left[(\tau^2-1)\mathrm{ln}\tau+\tau\pi-(\tau^2+1)\right]
+\end{equation}
+and
+\begin{equation}
+  F(x) = \frac{\mathrm{cos}^{-1}(1/x)}{\sqrt{x^2-1}} \ \ \mathrm{and} \ \ L(x) = \mathrm{ln}\left(\frac{x}{\sqrt{c^2+x^2}+c}\right).
+\end{equation}
+% \begin{equation}
+%   L(x) = \mathrm{ln}\left(\frac{x}{\sqrt{c^2+x^2}+c}\right).
+% \end{equation}
+Finally, the convergence $\kappa(x)=\Sigma(x)/\Sigma_{crit}$, where $\Sigma_{crit}$ is the critical surface density at the lens' redshift. The convergence is then azimuthally averaged.
 
@@
 \subsection{Shape and alignment of the dark matter halos}
-Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions.
+Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions, while the values are listed in Table~\ref{tab:ellipratios}.
 In this Figure, the full distribution up to one pixel past the last-image radius $R_{L}$ is probed.
@@
 Secondly, most lenses lie in the bottom-left corner: the dark matter distributions have typically low eccentricities, while the stellar distributions can be rather elliptical.
-Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($s_* > 0.4$).
+Thirdly, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to their larger stellar ellipticity ($e_* > 0.25$).
 At the same time, they show a very strong alignment between their stellar and dark matter distributions.
@@
 
-Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($s_{dm}\sim0.05$).
+Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.02$).
 By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
@@
 \subsection{Consistency with weak lensing estimates}
-The ellipticity values $s_{*}$ and $s_{dm}$ shown in Figures~\ref{fig:wedgesall} and \ref{fig:wedgesradii} and the values of the required external shear when reconstructing the lens galaxy are listed in Table~\ref{tab:ellipratios}.
-Furthermore, the ellipticity $s$ is converted to the ellipticity definition $e=(a-b)/(a+b)$, where $a$ and $b$ are the semi-major and semi-minor axes of the lens galaxy, by applying the relation
-\begin{equation}
-   e = \frac{s}{2-s}.
-\end{equation}
-
-The latter ellipticity definition is commonly used in weak lensing.
-Especially, it is employed in \citet{2015arXiv150704301S}, a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter.
+In a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter \citep{2015arXiv150704301S}.
 Weak lensing as a probe however cannot constrain $e_{dm}$ directly.
@@
 In a previous paper, we showed that data of this quality are required to determine the projected shape of dark matter haloes \citep{2014MNRAS.445.2181C}.
-We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining a {\it shape parameter} $s = 1 - \lambda_{2}/\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$; see Section~\ref{sec:shapemethod}).
-We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
+We measured the shape and alignment using the eigenvalues $\lambda_i$ and eigenvectors of the 2D moment of inertia tensor of the stellar and dark matter distributions, defining an estimator of the ellipticity $e = (\lambda_{1}-\lambda_{2})/(\lambda_{1}-\lambda_{2})$ ($\lambda_{1} \geq \lambda_{2}$; see Section~\ref{sec:shapemethod}).
+We averaged $e$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.
 
@@
 The same trend can be seen also for the dark matter, though the effect is not statistically significant.
-The dark matter haloes are never more elliptical than $s_{dm} = 0.2$, while their stars can extend to $s_* > 0.3$.
+The dark matter haloes are never more elliptical than $e_{dm} = 0.2$, while their stars can extend to $e_* > 0.2$.
 
-\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark.
+\item Three systems have a high stellar ellipticity ($e_* > 0.25$) and correspondingly high alignment between light and dark.
 One of these -- {\it1608} -- is a known merging pair.
@@
 The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within.
-Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the shape parameter $e$), and the angle between the dark matter and stellar major axes.
+Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the ellipticity $e$), and the angle between the dark matter and stellar major axes.
 Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.

### 2015-09-22 shapes/paper.tex
Claudio fixes

@@
 We find that the projected dark matter density profile -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy.
-Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling.
+Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark haloes contract due to baryonic cooling.
 We find that over several half-light radii, the dark matter haloes of these lenses are rounder than their stellar mass distributions.
@@
 This will lead, in absence of contaminating effects \citep[e.g.
-intrinsic alignments][]{2004PhRvD..70f3526H}, to an isotropic mean shear around galaxies if the mass distributions are spherical, or if dark and light are randomly aligned.
+intrinsic alignments;][]{2004PhRvD..70f3526H}, to an isotropic mean shear around galaxies if the mass distributions are spherical, or if dark and light are randomly aligned.
 The weak lensing measurement has been performed on data by various groups \citep[][]{2004ApJ...606...67H,2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V} with inconclusive results.
@@
 For example, \citet{2015arXiv150603536C} have recently made the measurement on Luminous Red Galaxies (LRG) taken from the Sloan Digital Sky Survey (SDSS) reporting a significant detection of dark matter halo ellipticity; while \citet{2015arXiv150704301S} performed a similar measurement on blue and red galaxies from the Canada France Hawaii Lensing Survey (CFHTLenS) finding no definite detection.
-Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} however characterize the expected signal assuming different misalignment models between the luminous and dark matter.
+% Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} however characterize the expected signal assuming different misalignment models between the luminous and dark matter.
 
@@
 
-% \citet{2004ApJ...606...67H}: Red-Sequence Cluster Survey (RCS); No split of galaxy sample in red & blue (magnitude-selected); Not taking care of systematics; f=0.77 --> probably good alignment, maybe halos somewhat rounder
+% \citet{2004ApJ...606...67H}: Red-Sequence Cluster Survey (RCS); No split of galaxy sample in red & blue (magnitude-selected); Not taking care of systematics; f=0.77 --> probably good alignment, maybe haloes somewhat rounder
 % \citet{2006MNRAS.370.1008M}: Sloan-Digital Sky Survey (SDSS); Galaxy sample split based on color; Discussing systematics; f=0.10+-0.06; no definite detection of halo ellipticity
@@
 In Section~\ref{sec:results}, we present our results.
-Finally, in Section~\ref{sec:conclusions} we discuss the implications of these results and we present our main conclusions.
+We discuss the implications of these results in Section~\ref{sec:discussion}.
+Finally, we conclude in Section~\ref{sec:conclusions}.
 
@@
 The misalignment angle $\Delta\theta$ between the distributions is then defined as:
-\begin{equation}
+\begin{equation}\label{eq:misalignment}
   \Delta\theta = \theta_{dm} - \theta_{*}.
@@
 Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the same shape).
-The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} (alternatively, see \citep{2015MNRAS.447.2170K}; section~3.2 for a more intuitive account of \Glass).
-Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of \citet{2014MNRAS.445.2181C}.
+The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} \citep[alternatively, for a more intuitive account of \Glass\ see Section~3.2 of][]{2015MNRAS.447.2170K}.
+Tests of how well the shape can be recovered from lensing data are given in Section~5.2 and Figure~8 of \citet{2014MNRAS.445.2181C}.
 
@@
 The columns are from left to right: the lens redshift $z_L$; the redshift of the source $z_S$; the maximum angular separation between two images $\Delta\theta$; the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$; and information on the environment of the lens.
-C and G denote a known cluster or group environment, respecitvely.
+C and G denote a known cluster or group environment, respectively.
 The number in the brackets is the number of confirmed members.
@@
 
-\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost spherical early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
+\textit{RXJ0911+0551} (hereafter \textit{0911}) is an early-type galaxy \citep{1997A&A...317L..13B,2012A&A...538A..99S}, and has measured time delays \citep{2002ApJ...572L..11H}.
 It lies on the outskirts of a cluster of which X-ray emission can be detected yielding a temperature of 2.3 keV \citep{2001ApJ...555....1M}.
@@
 The system has measured time delays \citep{2002ApJ...581..823F}.
-The environment has been analysed and a group with 8 (9 if the merging galaxies are counted individually) was identified \citep{2006ApJ...642...30F}.
+The environment has been analysed and a group of 8 (9 if the merging galaxies are counted individually) member galaxies was identified \citep{2006ApJ...642...30F}.
 Furthermore, the center was identified to be at a position angle of about 30$^{\circ}$ (resp.
@@
 However, no significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}.
-The data seem to indicate four other groups along the line of sight.
+The data seem to indicate four other groups along the line-of-sight.
 
@@
 The green curves show the contributions by the dark matter in the strong lens galaxies as reconstructed by \Glass.
-The dashed black lines show the corresponding profiles for dark matter halos that follow a NFW density profile.
+The dashed black lines show the corresponding profiles for dark matter haloes that follow a NFW density profile.
 The parameters in the NFW distribution are calibrated such that the convergence $\langle\kappa\rangle$ matches the corresponding values of the reconstructed profiles at one pixel past the last image radius.
@@
   \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
-  \caption[width=\linewidth]{The reconstructed lens galaxies are displayed according to the reconstructed total shapes of the dark matter halos $e_{dm}$ and the stellar components $e_{*}$.
+  \caption[width=\linewidth]{The reconstructed lens galaxies are displayed according to the reconstructed total shapes of the dark matter haloes $e_{dm}$ and the stellar components $e_{*}$.
 The wedges show the alignment of the semi-major axes of the components.
@@
 In case of alignment of the semi-major with the semi-minor axis (Anti-Aligned), the wedges are horizontal.
-The opening angle of each wedge displays the statistical error in the shape estimate of the dark matter halos.
+The opening angle of each wedge displays the statistical error in the shape estimate of the dark matter haloes.
 Both the uncertainties in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models of the ensemble of solutions lie within.
@@
 
+Throughout this work we consider a fixed, flat cosmological model with matter density $\Omega_{m} = 0.28$, dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.
+
 \subsection{Radial dark matter profiles}\label{sec:radialprofiles}
-Before discussing the shapes and alignments, we first measure the dark matter profiles of the strong lens galaxies, comparing these with Navarro-Frenk-White profiles \citep[NFW;][]{1996ApJ...462..563N}, given by \citep{2011ApJ...740..102K}:
+Before discussing the shapes and alignments, we first measure the dark matter profiles of the strong lens galaxies, comparing these with Navarro-Frenk-White profiles \citep[NFW;][]{1996ApJ...462..563N} given by \citep{2011ApJ...740..102K}:
 \begin{equation}\label{eq:nfw}
@@
 \end{equation}
-where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters (see Table 3 of \citet{2011ApJ...740..102K}). For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
+where $c_{0}(z)$ and $M_{0}(z)$ are fitting parameters \citep[see Table 3 of][]{2011ApJ...740..102K}. For each lens galaxy we choose the parameters at the redshift closest to the lens redshift.
 
-For a NFW-profile truncated at the virial radius $R_{vir}$, the projected surface mass density $\Sigma(x)$, where $x = cR/R_{vir}$, can be expressed as \citep{2009JCAP...01..015B}:
+For a NFW profile truncated at the virial radius $R_{vir}$, the projected surface mass density $\Sigma(x)$, where $x = cR/R_{vir}$, can be expressed as \citep{2009JCAP...01..015B}:
 \begin{equation}
  \begin{aligned}
-  \Sigma(x) = & \frac{M_1}{R_{vir}^2}\frac{c^4}{2\pi(c^2+1)^2}\left[\frac{c^2+1}{x^2-1}[1-F(x)]+2F(x) \right. \\
-  & \left. -\frac{\pi}{\sqrt{c^2+x^2}}+\frac{c^2-1}{c\sqrt{c^2+x^2}}L(x)\right],
+  \Sigma(x) = & \frac{M_1}{R_{vir}^2}\frac{c^4}{2\pi(c^2+1)^2}\left\{\frac{c^2+1}{x^2-1}[1-F(x)]+2F(x) \right. \\
+  & \left. -\frac{\pi}{\sqrt{c^2+x^2}}+\frac{c^2-1}{c\sqrt{c^2+x^2}}L(x)\right\},
  \end{aligned}
@@
 % \end{equation}
-Finally, the convergence $\kappa(x)=\Sigma(x)/\Sigma_{crit}$, where $\Sigma_{crit}$ is the critical surface density at the lens' redshift. The convergence is then azimuthally averaged.
+The convergence $\kappa(x)=\Sigma(x)/\Sigma_{crit}$ can then be computed, where $\Sigma_{crit}$ is the critical surface density at the lens' redshift.
+Finally, $\langle\kappa(R)\rangle$ is obtained by azimuthally averaging.
 
-As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$ is well-correlated with $M_{vir}$ (equation~\ref{eq:concentration}), there is only one degree of freedom, $M_{vir}$.
+As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$ is well-correlated with $M_{vir}$ (Eq.~\ref{eq:concentration}), there is only one degree of freedom, $M_{vir}$.
 We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ of the reconstructed dark matter distribution and the NFW-profile to match at one pixel past the last image radius.
@@
 Figure~\ref{fig:kappaplot} displays the results, while the virial masses (derived following the above procedure) are given in Table~\ref{tab:ellipratios}.
-In all cases the dark matter distribution either follows the NFW profile or is steeper, as expected if dark halos contract in response to baryon cooling and star formation \citep[e.g.][]{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}.
+In all cases the dark matter distribution either follows the NFW profile or is steeper, as expected if dark haloes contract in response to baryon cooling and star formation \citep[e.g.][]{1991ApJ...377..365K,1994ApJ...431..617D,2007arXiv0707.0737D}.
 At large radii, there is in all cases a sharp fall off in the \Glass\ dark matter density profiles.
@@
 The dark matter profile is substantially steeper than NFW while the derived virial mass is implausibly large (since we have not accounted for any such contraction in deriving it; see Table \ref{tab:ellipratios}).
-Our results suggest that the dark matter halos in these lensing galaxies are broadly consistent with contracted NFW profiles.
-Lenses with close-in images -- that are expected to inhabit less massive dark matter halos -- show more apparent contraction.
+Our results suggest that the dark matter haloes in these lensing galaxies are broadly consistent with contracted NFW profiles.
+Lenses with close-in images -- that are expected to inhabit less massive dark matter haloes -- show more apparent contraction.
 There could be several explanations for this behaviour.
-It could be a selection effect where lower mass galaxies can only strong lens if they are substantially contracted; it could owe to more massive halos being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems.
+It could be a selection effect where lower mass galaxies can only strong lens if they are substantially contracted; it could owe to more massive haloes being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems.
 We will explore such questions in a forthcoming paper where we will present the dark matter radial profiles of a larger sample of lenses, considering varying stellar initial mass function, and explicitly modelling dark matter contraction.
 
-\subsection{Shape and alignment of the dark matter halos}
+\subsection{Shape and alignment of the dark matter haloes}
 Figure~\ref{fig:wedgesall} shows our results for the shapes (see Section~\ref{sec:shapemethod}) and alignments of the dark matter and stellar mass distributions, while the values are listed in Table~\ref{tab:ellipratios}.
@@
 At the same time, they show a very strong alignment between their stellar and dark matter distributions.
-One of these lenses ({\it1608}) is an known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}.
+One of these lenses ({\it1608}) is a known merger of an early-type galaxy with a probable late-type galaxy \citep{2003ApJ...584..100S}.
 We speculate that the other two systems, {\it0712} and {\it2016}, may also be post-merger systems, explaining their similarities with {\it1608}.
@@
 As described furthermore in Section~\ref{sec:data}, {\it1422} is a challenging system to model the stellar distribution.
-Along the line of sight to the lens system {\it0414} there has furthermore another galaxy been found, which contributes to the lensing effect \citep{2011MNRAS.413L..86C}.
+For {\it0414} there is another galaxy along the line-of-sight contributing to the lensing effect \citep{2011MNRAS.413L..86C}.
 Besides these three lens systems, one stands out from the rest, however.
@@
 Restricting the range of the allowed external shear values did not affect the misalignment of the dark matter and stellar mass distributions.
-It did, however, increase the ellipticity of the reconstructed mass distribution: we observed a trade-off between the galaxy's ellipticity and the magnitude of the external shear as might be expected.
+It did, however, increase the ellipticity of the reconstructed mass distribution: we observed a trade-off between the galaxy's ellipticity and the magnitude of the external shear.
 {\it2045} on the other hand is particularly interesting.
@@
 However, such models also produce spurious extra images along the arc.
-We find that limiting the maximum shear $|\gamma|$ to 0.1 removes the extra images, though the lens then pushes on its maximum shear prior.
+By limiting the maximum shear $|\gamma|$ to 0.1 the extra images are removed, though the lens then pushes on its maximum shear prior.
 We find that the mass map is robust against a stronger shear prior, and does not affect the alignment of the distributions.
@@
 {\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see also Appendix).
+\textbf{CB: Do we need to say more here? C.f. referee report}
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
 \subsection{Consistency with weak lensing estimates}
-In a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter \citep{2015arXiv150704301S}.
-Weak lensing as a probe however cannot constrain $e_{dm}$ directly.
-Rather, it is sensitive to the ratio $f_{h} = (e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$, where $\Delta\theta$ is the misalignment angle between the two distributions, and $e_{dm}\cdot\mathrm{cos} 2\Delta\theta$ is the component of the ellipticity of the dark matter halo projected along the light distribution.
+In contrast to strong lensing, weak lensing as a probe cannot constrain $e_{dm}$ directly.
+Rather, it is sensitive to the ratio $f_{h} = (e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$, where $\Delta\theta$ is the misalignment angle between the two distributions, and $e_{dm}\cdot\mathrm{cos} 2\Delta\theta$ the component of the dark matter ellipticity projected along the light distribution.
 In case of perfect alignment and identical shape, $f_{h}$ is equal to 1.
-In practive however, $f_{h}$ deviates from 1, as among other effects which cannot be disentangled, misalignment of the two distributions and different ellipticities change its value.
+In practice however, $f_{h}$ deviates from 1, as among other effects misalignment of the two distributions and different ellipticities, which cannot be disentangled, change its value.
 
-In \citet{2015arXiv150704301S} a measurement on CFHTLenS data and on data from the Milennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H} is performed.
-The constraints in the highest mass bin of early-type galaxies ($\mathrm{log_{10}}M_{*}>11$) on CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
-On the simulated data, including cosmic shear and realistic misalignments between the luminous and the dark matter, the constraints in the highest mass bin and for redshifts $0.4<z<0.6$ are $f_{h} = 0.359^{+0.011}_{-0.010}$.
-Due to a narrower intrinsic ellipticity distribution in the simulated data however, the latter constraints need to be corrected for with a factor $\approx 1/1.46$.
+We compare our results presented in the previous Section with the most recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter by \citet{2015arXiv150704301S}.
+They perform a measurement on CFHTLenS data and on data from the Millennium Simulation \citep{2005Natur.435..629S} with a ray-tracing through by \citet{2009A&A...499...31H}.
+The constraints on the early-type galaxies in the highest mass bin ($\mathrm{log_{10}}M_{*}>11$) on CFHTLenS data are $f_{h}=-0.04^{+0.25}_{-0.25}$.
+On the simulated data, including cosmic shear and misalignments between the luminous and the dark matter, the constraints in the highest mass bin and for redshifts $0.4<z<0.6$ are $f_{h} = 0.359^{+0.011}_{-0.010}$.
+Due to a narrower intrinsic ellipticity distribution in the simulated data however, the latter constraints need to be corrected for with a factor $\sim$1/1.46.
 Our results are broadly consistent with both constraints, with the exception of the galaxy merger system \textit{1608} and the interesting and highly misaligned lens \textit{1115}.
@@
 \item The projected dark matter density profile in these systems -- under the assumption of a Chabrier stellar initial mass function -- shows significant variation from galaxy to galaxy.
-Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark halos contract due to baryonic cooling.
+Those with an outermost image beyond $\sim 10$\,kpc are very well fit by a projected NFW profile; those with images within 10\,kpc appear to be more concentrated than NFW, as expected if their dark haloes contract due to baryonic cooling.
 There could be several explanations for this behaviour.
-It could be a selection effect where lower mass galaxies (expected to have closer-in images) can only strong lens if they are substantially contracted; it could owe to more massive halos (with further out images) being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems.
+It could be a selection effect where lower mass galaxies (expected to have closer-in images) can only strong lens if they are substantially contracted; it could owe to more massive haloes (with further out images) being less affected by baryons; or it could be that we simply cannot yet resolve the contraction at the centre of the more massive systems.
 We will explore such questions in a forthcoming paper.
@@
 
-Our results provide a new constraint on galaxy formation models that must explain the origin of low eccentricity dark matter haloes (not expected in pure dark-matter-only simulations), and highly misaligned lens systems.
+Dark matter haloes can contract due to baryonic cooling \citep[e.g.][]{1986ApJ...301...27B} or expand due to energetic feedback from supernovae \citep[e.g.][]{2005MNRAS.356..107R} or AGN \citep[e.g.][]{2012MNRAS.422.3081M}.
+The latest simulations for elliptical galaxies forming in $\Lambda$CDM without AGN feedback suggest that contraction should win \citep{2015MNRAS.453.2447D}, consistent with the results we find here.
+Thus, our results provide a new constraint on galaxy formation models and may provide an interesting new constraint on AGN feedback models as well.
+
+Furthermore, the origin of low eccentricity dark matter haloes (not expected in pure dark-matter-only simulations) and highly misaligned lens systems must be explained.
 Such misalignments also present a new challenge for those alternative gravity theories in which light is the only source of gravity, since in such models light and dark must necessarily be highly correlated.
@@
 The panels show, from left to right: the arrival time surface (the images are marked by the green circles); the surface mass density of the dark matter; and the surface mass density of the stars.
-The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines the 68\% confidence interval of these for the dark matter map.}
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dashed lines the 68\% confidence interval of these for the dark matter map.}
   \label{fig:lensreconstruction1}
@@
 The panels show, from left to right: the arrival time surface; the surface mass density of the dark matter; and the surface mass density of the stars.
-The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dotted lines denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within.
-Figure \ref{fig:wedgesall} is constructed from the ratio of largest to smallest eigenvalue in each case (to measure the ellipticity $e$), and the angle between the dark matter and stellar major axes.
+The solid lines mark the eigenvalues and eigenvectors of the 2D moment of inertia tensor in each case; the dashed lines denote the ranges 68\% of all the eigenvectors of the dark matter distribution corresponding to an individual model lie within.
+Figures~\ref{fig:wedgesall} \& \ref{fig:wedgesradii} are constructed from a combination of the eigenvalues (Eq.~\ref{eq:shapeestimate}), and the angle between the dark matter and stellar major axes (Eq.~\ref{eq:misalignment}).
 Note that the angular scale is always the same for the dark matter and stellar maps, but varies between the different lenses as marked on the Figure axes.
@@
 Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of the dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy.
-We note that the constraints on the direction of the external shear are stronger than the ones on the dark matter distribution \textbf{[INSERT HERE WHY HE THINK THAT IS]}.
+We note that the constraints on the direction of the external shear are stronger than the ones on the dark matter distribution \textbf{[INSERT HERE WHY WE THINK THAT IS]}.
 A slight degeneracy between the angles is evident.

### 2015-09-22 shapes/paper.tex
Tiny fix

@@
 Finally, we conclude in Section~\ref{sec:conclusions}.
+
+Throughout this work we assume a flat $\Lambda$CDM model with matter density $\Omega_{m} = 0.28$, dark energy density $\Omega_{\Lambda} = 0.72$, and inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.
 
@@
 
-Throughout this work we consider a fixed, flat cosmological model with matter density $\Omega_{m} = 0.28$, dark energy density $\Omega_{\Lambda} = 0.72$, and the inverse Hubble constant $H_{0}^{-1} = 13.7$ Gyr.
-
 \subsection{Radial dark matter profiles}\label{sec:radialprofiles}

### 2015-09-22 shapes/paper.tex
Changes in referee report and the paper

@@
 \subsection{The lack of isolated misaligned lenses}
-
+\textbf{CB: MY MAIN PROBLEM IS ACTUALLY THAT `ISOLATED' AND `WEAK EXTERNAL SHEAR' ARE USED SYNONYMOUSLY IN THIS PARAGRAPH, THE ABSTRACT, AND THE LAST BULLET POINT IN THE CONCLUSIONS.
+I THOUGHT QUITE A WHILE HOW TO FIX THIS, BUT NOTHING CONVINCED ME.}
 Our lens sample is small -- just 11 strong lensing systems -- yet it is interesting that we find no lens with strong misalignment and weak external shear.
@@
 This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
+\textbf{CB: ISOLATED MISALIGNED GALAXIES (see above)}
 

### 2015-09-24 shapes/paper.tex
Changes by Justin and suggested by Justin

--- 2015-09-22 shapes/paper.tex
@@
 \section{Data}\label{sec:data}
-\setlength\tabcolsep{5pt}
+\setlength\tabcolsep{4pt}
 \begin{table}
   \begin{center}
-    \begin{tabular}{l l l l l l}
-      Lens & $z_{L}$ & $z_{S}$ & $\Delta\phi$ [kpc] & $R_{L}/R_{e}$ & Environment \\ \hline
-      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9)$^{a}$ \\
-      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... \\
-      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... \\
-      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C$^{b}$ \\
-      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C$^{c}$ \\
-      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13)$^{a}$ \\
-      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17)$^{a}$ \\
-      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8)$^{d}$ \\
-      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69)$^{e}$ \\
-      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... \\
-      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... \\
+    \begin{tabular}{l l l l l l l}
+      \multirow{2}{*}{Lens} & \multirow{2}{*}{$z_{L}$} & \multirow{2}{*}{$z_{S}$} & $\Delta\phi$ & \multirow{2}{*}{$R_{L}/R_{e}$} & \multirow{2}{*}{Env} & \multirow{2}{*}{$\theta_{Env}$ [$^{\circ}$]} \\
+       & & & [kpc] & & & \\ \hline
+      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9)$^{a}$ & ... \\
+      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... & ... \\
+      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... & ... \\
+      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C$^{b}$ & -160$^{b}$ \\
+      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C$^{c}$ & 60$^{f}$ \\
+      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13)$^{a}$ & -125$^{g}$ \\
+      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17)$^{a}$ & 145$^{g}$ \\
+      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8)$^{d}$ & 30 resp. -5$^{d,f}$\\
+      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69)$^{e}$ & 130 - 140$^{e}$ \\
+      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... & ... \\
+      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... & ... \\
     \end{tabular}
@@
 \newline $^{a}$ \citet{2011ApJ...726...84W}; $^{b}$ \citet{2001ApJ...555....1M}; $^{c}$ e.g.
-\citet{1992MNRAS.254P..27G}; $^{d}$ \citet{2006ApJ...642...30F}; $^{e}$ \citet{2003MNRAS.344..337T}.}
+\citet{1992MNRAS.254P..27G}; $^{d}$ \citet{2006ApJ...642...30F}; $^{e}$ \citet{2003MNRAS.344..337T}; $^{f}$ \citet{2002ApJ...565...96C}; $^{g}$ \citet{2004ApJ...610..686G}.
+\newline $^{f}$ The position angle is given for the unweighted resp.
+the luminosity-weighted centroid estimation.}
     \label{tab:lensproperties}
@@
 \end{table}
-\setlength\tabcolsep{6pt}
 
+\setlength\tabcolsep{5pt}
 \begin{table}
@@
 Due to the large image separation, large physical scales are probed.
-Identified X-ray emission furthermore locates the center of the cluster at a position angle of about 59$^{\circ}$, close to the lens galaxy \citep{2002ApJ...565...96C}.
+Identified X-ray emission furthermore locates the center of the cluster at a position angle of about 60$^{\circ}$, close to the lens galaxy \citep{2002ApJ...565...96C}.
 The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}.
@@
 It is part of a small group of 13 members.
-Also, X-ray emission was detected from the corresponding group at a position angle of about -127$^{\circ}$ and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
+Also, X-ray emission was detected from the corresponding group at a position angle of about -125$^{\circ}$ and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.
 
@@
 Using newer data, additional members could be identified \citep{2011ApJ...726...84W}.
-\citet{2004ApJ...610..686G} also detect X-ray emission from the corresponding group originating from a position angle of about 147$^{\circ}$ at a temperature of 1.0 keV.
+\citet{2004ApJ...610..686G} also detect X-ray emission from the corresponding group originating from a position angle of about 145$^{\circ}$ at a temperature of 1.0 keV.
 
@@
 \citet{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy.
-North-west of the lens at about -60$^{\circ}$, there is evidence for a group at a similar redshift as the lens \citep{1999AJ....117..658F}.
+North-west of the lens there is evidence for a potential group at a similar redshift as the lens \citep{1999AJ....117..658F}.
 There is furthermore evidence for a dwarf satellite galaxy within the Einstein radius of the lens system \citep{2007MNRAS.378..109M}.
@@
   \includegraphics[width=.7\linewidth]{Figures/kappaplot.pdf}
-  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution.
+  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $r$ of the dark matter distribution.
 The vertical lines denote the radial distances of the source images from the centre of the lens galaxies.
@@
   \begin{center}
-    \begin{tabular}{l l l l l l l l l l l}
+    \begin{tabular}{l l l l l l l l l l l l}
       % \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} &  \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
@@
       % 2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
-      \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
-       & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & \\ \hline
-      0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
-      0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
-      0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
-      0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
-      0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
-      1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
-      1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
-      1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
-      2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
-      2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
-      2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
+
+      % \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $r_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
+      %  & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & \\ \hline
+      % 0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
+      % 0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
+      % 0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
+      % 0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
+      % 0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
+      % 1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
+      % 1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
+      % 1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
+      % 2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
+      % 2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
+      % 2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
+
+      \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & \multirow{2}{*}{$\theta_{Env}$ [$^{\circ}$]} & $r_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
+       & & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & \\ \hline
+      0047 & G(9) & ... & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
+      0414 & ... & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
+      0712 & ... & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
+      0911 & C & -160 & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
+      0957 & C & 59 & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
+      1115 & G(13) & -127 & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
+      1422 & G(17) & 147 & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
+      1608 & G(8) & 30 resp. -5$^{a}$ & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
+      2016 & C(69) & $130-140$ & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
+      2045 & ... & -60 & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
+      2237 & ... & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
     \end{tabular}
     \caption{Fitted virial masses and radii and the ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-`Env' is the `Environment' column in Table~\ref{tab:lensproperties}; $R_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.}
+`Env' is the `Environment' column in Table~\ref{tab:lensproperties} and ; $r_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle (measured north through east) of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.
+\newline $^{a}$ brrr}
     \label{tab:ellipratios}
@@
 \begin{equation}\label{eq:nfw}
-   \frac{\rho(R)}{\rho_{crit}} = \frac{\delta_{c}}{(cR/R_{vir})(1+cR/R_{vir})},
+   \frac{\rho(r)}{\rho_{crit}} = \frac{\delta_{c}}{(cr/r_{vir})(1+cr/r_{vir})^2},
 \end{equation}
-where the critical density of the universe $\rho_{crit}(z)$ and $\delta_{c}(z)$ are parameters set by the cosmology considered, $R$ is the radius from the centre, and $c$ is the concentration parameter.
+where the critical density of the universe $\rho_{crit}(z)$ and $\delta_{c}(z)$ are parameters set by the cosmology considered, $r$ is the radius from the centre, and $c$ is the concentration parameter.
 The concentration is well-correlated with $M_{vir}$ with some redshift dependence \citep{2011ApJ...740..102K}:
@@
 
-For a NFW profile truncated at the virial radius $R_{vir}$, the projected surface mass density $\Sigma(x)$, where $x = cR/R_{vir}$, can be expressed as \citep{2009JCAP...01..015B}:
+For a circular NFW profile truncated at the virial radius $r_{vir}$, the projected surface mass density $\Sigma(x)$, where $x = cr/r_{vir}$, can be expressed as \citep{2009JCAP...01..015B}:
 \begin{equation}
  \begin{aligned}
-  \Sigma(x) = & \frac{M_1}{R_{vir}^2}\frac{c^4}{2\pi(c^2+1)^2}\left\{\frac{c^2+1}{x^2-1}[1-F(x)]+2F(x) \right. \\
+  \Sigma(x) = & \frac{M_1}{r_{vir}^2}\frac{c^4}{2\pi(c^2+1)^2}\left\{\frac{c^2+1}{x^2-1}[1-F(x)]+2F(x) \right. \\
   & \left. -\frac{\pi}{\sqrt{c^2+x^2}}+\frac{c^2-1}{c\sqrt{c^2+x^2}}L(x)\right\},
@@
 \end{equation}
-% \begin{equation}
-%   L(x) = \mathrm{ln}\left(\frac{x}{\sqrt{c^2+x^2}+c}\right).
-% \end{equation}
 The convergence $\kappa(x)=\Sigma(x)/\Sigma_{crit}$ can then be computed, where $\Sigma_{crit}$ is the critical surface density at the lens' redshift.
@@
 
-As the virial radius $R_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$ is well-correlated with $M_{vir}$ (Eq.~\ref{eq:concentration}), there is only one degree of freedom, $M_{vir}$.
+As the virial radius $r_{vir}$ is related to the virial mass $M_{vir}$ and the concentration parameter $c$ is well-correlated with $M_{vir}$ (Eq.~\ref{eq:concentration}), there is only one degree of freedom, $M_{vir}$.
 We calibrate the mass in order for the derived convergence profiles $\langle\kappa(R)\rangle$ of the reconstructed dark matter distribution and the NFW-profile to match at one pixel past the last image radius.
@@
 
-Fourthly, notice that all dark matter and stellar distributions with weak external shear (see the contour bar that displays the shear $\gamma$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.02$).
-By contrast, systems requiring a larger external shear ({\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
+Fourthly, notice that all dark matter and stellar distributions with weak external shear ($\gamma < 0.1$) are aligned apart from {\it0047} which is almost spherical ($e_{dm}\sim0.02$).
+By contrast, systems requiring a larger external shear ($\gamma > 0.1$; {\it0414}, {\it0911}, and {\it1422}) can display a sizeable misalignment between the distributions.
 The latter two systems are located in dense environments (see Table~\ref{tab:lensproperties}) that are likely responsible for these misalignments.
@@
 We believe that a strong shear prior for this particular lens is justified by the appearance of spurious extra images if higher shear is allowed.
+We furthermore explore potential degeneracies between the estimation of the shape and the required external shear in the Appendix.
+As shown in Figure~\ref{fig:thetascatter} the degeneracy can be largely broken for most lenses.
 
@@
 {\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see also Appendix).
-\textbf{CB: Do we need to say more here? C.f. referee report}
 
@@
 \subsection{The lack of isolated misaligned lenses}
-
-Our lens sample is small -- just 11 strong lensing systems -- yet it is interesting that we find no lens with strong misalignment and weak external shear.
+Our lens sample is small -- just 11 strong lensing systems -- yet it is interesting that we find no lens with strong misalignment and weak external shear ($\gamma < 0.1$).
 This is perhaps to be expected.
@@
 \citet{2015MNRAS.452.4094D} go on to show that if this gas supply is switched off (as is the case for giant elliptical galaxies), then continuing collisionless minor mergers/interactions bring the disc rapidly into alignment with its host halo.
-Taken together, these results suggest that alignment between light and dark should be the norm for isolated gas-free triaxial galaxies.
+Taken together, these results suggest that alignment between light and dark should be the norm for isolated gas-free triaxial galaxies, where here we define `isolated' as having external shear $\gamma < 0.1$.
 
@@
 
-\item The dark matter haloes of all lenses in our sample are rounder than the light distribution over the range $1R_e < R < 5R_e$.
+\item The dark matter haloes of all lenses in our sample are rounder than the light distribution over the range $1R_e < r < 5R_e$.
 As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions.
@@
 
-\item Galaxies with high dark matter ellipticity and weak external shear show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
+\item Galaxies with high dark matter ellipticity and weak external shear ($\gamma < 0.1$) show strong alignment; those with strong shear ($\gamma \gtrsim 0.1$) can be highly misaligned.
 This is reassuring since isolated misaligned galaxies are expected to be unstable \citep[e.g.][]{1979ApJ...233..872H,1988A&A...206..269M,2007ApJ...670.1027A,2015arXiv150203429D}.
+We find that lenses with external shear $\gamma < 0.1$ appear to be sufficiently isolated that their luminous and dark matter distributions are well-aligned.
 
@@
 
+Our results on the shape and radial profile of the dark matter haloes in these lenses provide new constraints on galaxy formation models.
 Dark matter haloes can contract due to baryonic cooling \citep[e.g.][]{1986ApJ...301...27B} or expand due to energetic feedback from supernovae \citep[e.g.][]{2005MNRAS.356..107R} or AGN \citep[e.g.][]{2012MNRAS.422.3081M}.
-The latest simulations for elliptical galaxies forming in $\Lambda$CDM without AGN feedback suggest that contraction should win \citep{2015MNRAS.453.2447D}, consistent with the results we find here.
-Thus, our results provide a new constraint on galaxy formation models and may provide an interesting new constraint on AGN feedback models as well.
-
-Furthermore, the origin of low eccentricity dark matter haloes (not expected in pure dark-matter-only simulations) and highly misaligned lens systems must be explained.
-Such misalignments also present a new challenge for those alternative gravity theories in which light is the only source of gravity, since in such models light and dark must necessarily be highly correlated.
+The latest simulations for elliptical galaxies forming in $\Lambda$CDM without AGN feedback suggest that contraction should win \citep{2015MNRAS.453.2447D}.
+Under the assumption of a Chabrier IMF, our results imply that AGN do not play a major role in the lower mass lenses (since these are contracted with respect to NFW), but perhaps do act to counterbalance contraction in the more massive lenses.
+For the shape and alignment of lens galaxies, the models must reproduce rather round dark matter halos within $5r_e$, and misaligned stellar and dark matter distributions in lenses with strong external shear ($\gamma > 0.1$).
+It will be interesting to see whether the latest galaxy formation models reproduce this naturally, or it poses a challenge.
+Finally, we note that strong misalignments may be problematic for those alternative gravity theories in which light is the only source of gravity, since in such models light and dark must necessarily be highly correlated.
 
@@
 Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of the dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy.
-We note that the constraints on the direction of the external shear are stronger than the ones on the dark matter distribution \textbf{[INSERT HERE WHY WE THINK THAT IS]}.
-A slight degeneracy between the angles is evident.
-However, \textbf{...
-[WHY THIS IS EXPECTED, AND WHY OUR MISALIGNMENT RESULT STILL HOLDS].}
+We note that the constraints on the direction of the external shear are stronger than on the dark matter distribution.
+There is a slight degeneracy between the two quantities, it can however for most lenses be largely broken.
+\textbf{CB: Do we need more here, i.e.
+on why this degeneracy can be broken?}
 

### 2015-09-29 shapes/paper.tex
Claudio changes (almost done)

@@
 For example, \citet{2015arXiv150603536C} have recently made the measurement on Luminous Red Galaxies (LRG) taken from the Sloan Digital Sky Survey (SDSS) reporting a significant detection of dark matter halo ellipticity; while \citet{2015arXiv150704301S} performed a similar measurement on blue and red galaxies from the Canada France Hawaii Lensing Survey (CFHTLenS) finding no definite detection.
-% Using mock data from the Millennium Simulation \citep{2005Natur.435..629S}, \citet{2015arXiv150704301S} however characterize the expected signal assuming different misalignment models between the luminous and dark matter.
-
-%Given an elliptical total mass distribution, the exerted shear is larger in the direction of the major axis of the distribution than in the direction of the minor axis for fixed radii $r$ from the galaxy's center.
-In case of alignment of the luminous and dark matter and an elliptical shape of the distribution of the latter, the azimuthal distribution of this signal is thus expected to be anisotropic in absence of contaminating effects \citep[e.g.
-intrinsic alignments][]{2004PhRvD..70f3526H} and systematic effects.
-
-% \citet{2004ApJ...606...67H} applied this idea to data from the Red-Sequence Cluster Survey (RCS) to measure the first weak lensing signal of halo flattening.
-They found that dark matter haloes appear to be rounder than the stellar mass distribution, with some weak evidence for alignment.
-Both measurements are challenging however, and more recent data appear to be at odds with this early work, at least for galaxies in general.
-They however are in agreement concerning `red' galaxies, which are predominantly early-type galaxies, also favouring dark matter haloes that are more elliptical than their stellar mass components \citep{2006MNRAS.370.1008M,2007ApJ...669...21P,2012A&A...545A..71V}.}
-
-% \citet{2004ApJ...606...67H}: Red-Sequence Cluster Survey (RCS); No split of galaxy sample in red & blue (magnitude-selected); Not taking care of systematics; f=0.77 --> probably good alignment, maybe haloes somewhat rounder
-% \citet{2006MNRAS.370.1008M}: Sloan-Digital Sky Survey (SDSS); Galaxy sample split based on color; Discussing systematics; f=0.10+-0.06; no definite detection of halo ellipticity
-% \citet{2007ApJ...669...21P}: CFHTLS; No split of sample (rather only test by selecting preferentially ellipticals) (magnitude-selected); not really taking care of systematics, only test; halo ellipticity ~0.3 at 2sigma level (more if ellipticals)
-% \citet{2012A&A...545A..71V}: Red-Sequence Cluster Survey (RCS2); split in red & blue (magnitude-selected); Discussing systematics; no definite detection of halo ellipticity
-% \citet{2015arXiv150603536C}: SDSS; LRGs; Discuss systematics; detect halo ellipticity
-% \citet{2015arXiv150704301S}: CFHTLenS; split in red & blue (magnitude-selected); Discussing systematics; no definite detection of halo ellipticity
 
@@
 
-% \setlength\tabcolsep{5pt}
 \begin{table*}
@@
     \begin{tabular}{l l l l l l l l l l l l}
-      % \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $R_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} &  \multirow{2}{*}{$s_{*}$} & \multirow{2}{*}{$s_{dm}$} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
-      %  & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & & & \\ \hline
-      % 0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
-      % 0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
-      % 0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
-      % 0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
-      % 0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
-      % 1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
-      % 1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
-      % 1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
-      % 2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
-      % 2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
-      % 2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
-
-      % \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & $r_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
-      %  & & [kpc] & $[10^{12} \ M_{\odot}]$ & & & & & & & \\ \hline
-      % 0047 & G(9) & 360.7 & 10.0 & 0.07$\pm$0.01 & 120$\pm$5 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 \\
-      % 0414 & ... & 256.9 & 12.4 & 0.17$\pm$0.02 & 166$\pm$4 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 \\
-      % 0712 & ... & 446.5 & 15.5 & 0.17$\pm$0.01 & 141$\pm$3 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 \\
-      % 0911 & C & 369.1 & 22.7 & 0.28$\pm$0.02 & 99$\pm$2 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 \\
-      % 0957 & C & 1053.1 & 175.2 & 0.09$\pm$0.03 & 159$\pm$8 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 \\
-      % 1115 & G(13) & 616.8 & 31.1 & 0.11$\pm$0.01 & 154$\pm$3 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 \\
-      % 1422 & G(17) & 450.8 & 13.0 & 0.26$\pm$0.01 & 39$\pm$1 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 \\
-      % 1608 & G(8) & 317.1 & 10.0 & 0.19$\pm$0.01 & 145$\pm$2 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 \\
-      % 2016 & C(69) & 299.3 & 22.1 & 0.14$\pm$0.02 & 42$\pm$4 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 \\
-      % 2045 & ... & 562.8 & 104.0 & 0.11$\pm$0.02 & 23$\pm$7 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 \\
-      % 2237 & ... & 1961.0 & 485.3 & 0.06$\pm$0.01 & 159$\pm$4 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 \\
-
       \multirow{2}{*}{Lens} & \multirow{2}{*}{Env} & \multirow{2}{*}{$\theta_{Env}$ [$^{\circ}$]} & $r_{vir}$ & $M_{vir}$ & \multirow{2}{*}{$|\gamma|$} & \multirow{2}{*}{$\theta_{g}$ [$^{\circ}$]} & \multirow{2}{*}{$\Delta\theta$ [$^{\circ}$]} & \multirow{2}{*}{$e_{*}$} & \multirow{2}{*}{$e_{dm}$} & \multirow{2}{*}{$e_{dm}/e_{*}$} & \multirow{2}{*}{$f_h$} \\
@@
 \end{table*}
-% \setlength\tabcolsep{6pt}
 
@@
 Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$.
-There appears to be a trend that the ellipticity of the stellar distribution increases with increasing radius of enclosure.
-There is potentially a similar trend for the dark matter distribution, although the samples are also consistent with a constant ellipticity.
-{\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see also Appendix).
+As the inertia tensor defined in Eq.~\ref{eq:inertiatensor} scales depends on the square of the radius, averaging up to different limiting radii could potentially yield different results.
+We observe that the shape estimator is robust to these changes.
+However, we note that there appears to be a slight trend that the ellipticity of the stellar distribution increases with increasing radius of enclosure.
+Whether this trend persists with data of a higher quality remains to be seen.
+There is potentially a similar trend for the dark matter distribution, although the samples are consistent with a constant ellipticity as well.
+{\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see Appendix).
 
@@
 
-\item The dark matter haloes of all lenses in our sample are rounder than the light distribution over the range $1R_e < r < 5R_e$.
-As we average over larger radii, the lenses, except the ones with a large stellar ellipticity, become increasingly elliptical in their stellar distributions.
-The same trend can be seen also for the dark matter, though the effect is not statistically significant.
+\item The dark matter haloes of all lenses in our sample are rounder than the light distribution over the range $1R_e < R < 5R_e$.
+As we average over larger radii, there is a slight trend for the lenses, except the ones with a large stellar ellipticity, to become increasingly elliptical in their stellar distributions.
+A similar behaviour can be seen also for the dark matter, though the effect is not statistically significant.
 The dark matter haloes are never more elliptical than $e_{dm} = 0.2$, while their stars can extend to $e_* > 0.2$.
@@
 Our results on the shape and radial profile of the dark matter haloes in these lenses provide new constraints on galaxy formation models.
-Dark matter haloes can contract due to baryonic cooling \citep[e.g.][]{1986ApJ...301...27B} or expand due to energetic feedback from supernovae \citep[e.g.][]{2005MNRAS.356..107R} or AGN \citep[e.g.][]{2012MNRAS.422.3081M}.
+Dark matter haloes can contract due to baryonic cooling \citep[e.g.][]{1986ApJ...301...27B} or expand due to energetic feedback \citep[for a recent review see][]{2014Natur.506..171P, 2015arXiv150202036O} from supernovae \citep[e.g.][]{2005MNRAS.356..107R, 2015arXiv150804143R} or AGN \citep[e.g.][]{2012MNRAS.422.3081M}.
 The latest simulations for elliptical galaxies forming in $\Lambda$CDM without AGN feedback suggest that contraction should win \citep{2015MNRAS.453.2447D}.
-Under the assumption of a Chabrier IMF, our results imply that AGN do not play a major role in the lower mass lenses (since these are contracted with respect to NFW), but perhaps do act to counterbalance contraction in the more massive lenses.
-For the shape and alignment of lens galaxies, the models must reproduce rather round dark matter halos within $5r_e$, and misaligned stellar and dark matter distributions in lenses with strong external shear ($\gamma > 0.1$).
+Under the assumption of a Chabrier IMF, our results imply that AGN do not play a major role in the lower mass lenses in our sample (since these are contracted with respect to NFW), but perhaps do act to counterbalance contraction in the more massive lenses.
+For the shape and alignment of lens galaxies, the models must reproduce rather round dark matter halos within $5R_e$, and misaligned stellar and dark matter distributions in lenses with strong external shear ($\gamma > 0.1$).
 It will be interesting to see whether the latest galaxy formation models reproduce this naturally, or it poses a challenge.

### 2015-09-29 shapes/paper.tex
small edits

@@
 The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} \citep[alternatively, for a more intuitive account of \Glass\ see Section~3.2 of][]{2015MNRAS.447.2170K}.
-Tests of how well the shape can be recovered from lensing data are given in Section~5.2 and Figure~8 of \citet{2014MNRAS.445.2181C}.
 
@@
 An important improvement is a better sampling algorithm for high dimensional spaces \citep{2012MNRAS.425.3077L} that eliminates the excessive weight \PixeLens\ tended to give to extreme models.
+
+Most relevant to the present work are Section~5.2 and Figure~8 of
+\citet{2014MNRAS.445.2181C}, showing the recovery of
+$\lambda_2/\lambda_1$.  The typical errors in this quantity are
+10--20\%.
 
@@
 There is potentially a similar trend for the dark matter distribution, although the samples are consistent with a constant ellipticity as well.
-{\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see Appendix).
+{\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see Appendix \ref{sec:shearshapedeg}).
 
@@
 We note that the constraints on the direction of the external shear are stronger than on the dark matter distribution.
-There is a slight degeneracy between the two quantities, it can however for most lenses be largely broken.
-\textbf{CB: Do we need more here, i.e.
-on why this degeneracy can be broken?}
+There is a weak degeneracy between the two quantities, it can however for most lenses be largely broken.
+This is expected, since internal ellipticity and external shear tend to have similar effects, but are not an exact degeneracy \cite[cf.][]{1999A&A...349..108D}.
 

### 2015-09-29 shapes/paper.tex
Final paper version

@@
 \section{The lens models}\label{sec:shapemethod}
+\setlength\tabcolsep{7pt}
+\begin{table*}
+  \begin{center}
+    \begin{tabular}{l l l l l l l l}
+      \multirow{2}{*}{Lens} & \multirow{2}{*}{$z_{L}$} & \multirow{2}{*}{$z_{S}$} & $\Delta\phi$ & \multirow{2}{*}{$R_{L}/R_{e}$} & $M_s(<2R_e)$ & \multirow{2}{*}{Env} & \multirow{2}{*}{$\theta_{Env}$ [$^{\circ}$]} \\
+       & & & [kpc] & & [$10^{10}M_{\odot}$] & & \\ \hline
+      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & $11.58\pm0.43$ & G(9)$^{a}$ & ... \\
+      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & $19.90\pm2.29$ & ... & ... \\
+      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & $5.46\pm0.52$ & ... & ... \\
+      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & $14.52\pm1.87$ & C$^{b}$ & -160$^{b}$ \\
+      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & $20.92\pm0.96$ & C$^{c}$ & 60$^{f}$ \\
+      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & $5.61\pm1.19$ & G(13)$^{a}$ & -125$^{g}$ \\
+      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & $2.91\pm0.45$ & G(17)$^{a}$ & 145$^{g}$ \\
+      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & $27.99\pm1.63$ & G(8)$^{d}$ & 30 resp. -5$^{d,f}$\\
+      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & $6.34\pm1.99$ & C(69)$^{e}$ & 130 - 140$^{e}$ \\
+      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & $14.05\pm1.03$ & ... & ... \\
+      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & $1.15\pm0.12$ & ... & ... \\
+    \end{tabular}
+    \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}.
+References can be found in Section~\ref{sec:data}.
+The columns are from left to right: the lens redshift $z_L$; the redshift of the source $z_S$; the maximum angular separation between two images $\Delta\theta$; the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$; the stellar mass $M_s$ within $2R_e$; information on the environment of the lens; and the position angle to the centroid of the corresponding group/cluster (measured north through east).
+C and G denote a known cluster or group environment, respectively.
+The number in the brackets is the number of confirmed members.
+Ellipses indicate lens galaxies with no group members identified so far.
+\newline $^{a}$ \citet{2011ApJ...726...84W}; $^{b}$ \citet{2001ApJ...555....1M}; $^{c}$ e.g.
+\citet{1992MNRAS.254P..27G}; $^{d}$ \citet{2006ApJ...642...30F}; $^{e}$ \citet{2003MNRAS.344..337T}; $^{f}$ \citet{2002ApJ...565...96C}; $^{g}$ \citet{2004ApJ...610..686G}.
+\newline $^{f}$ The position angle is given for the unweighted resp.
+the luminosity-weighted centroid estimation.}
+    \label{tab:lensproperties}
+  \end{center}
+\end{table*}
 
@@
 \section{Data}\label{sec:data}
-\setlength\tabcolsep{4pt}
-\begin{table}
-  \begin{center}
-    \begin{tabular}{l l l l l l l}
-      \multirow{2}{*}{Lens} & \multirow{2}{*}{$z_{L}$} & \multirow{2}{*}{$z_{S}$} & $\Delta\phi$ & \multirow{2}{*}{$R_{L}/R_{e}$} & \multirow{2}{*}{Env} & \multirow{2}{*}{$\theta_{Env}$ [$^{\circ}$]} \\
-       & & & [kpc] & & & \\ \hline
-      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9)$^{a}$ & ... \\
-      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... & ... \\
-      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... & ... \\
-      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C$^{b}$ & -160$^{b}$ \\
-      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C$^{c}$ & 60$^{f}$ \\
-      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13)$^{a}$ & -125$^{g}$ \\
-      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17)$^{a}$ & 145$^{g}$ \\
-      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8)$^{d}$ & 30 resp. -5$^{d,f}$\\
-      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69)$^{e}$ & 130 - 140$^{e}$ \\
-      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... & ... \\
-      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... & ... \\
-    \end{tabular}
-    \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}.
-References can be found in Section~\ref{sec:data}.
-The columns are from left to right: the lens redshift $z_L$; the redshift of the source $z_S$; the maximum angular separation between two images $\Delta\theta$; the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$; and information on the environment of the lens.
-C and G denote a known cluster or group environment, respectively.
-The number in the brackets is the number of confirmed members.
-Ellipses indicate lens galaxies with no group members identified so far.
-\newline $^{a}$ \citet{2011ApJ...726...84W}; $^{b}$ \citet{2001ApJ...555....1M}; $^{c}$ e.g.
-\citet{1992MNRAS.254P..27G}; $^{d}$ \citet{2006ApJ...642...30F}; $^{e}$ \citet{2003MNRAS.344..337T}; $^{f}$ \citet{2002ApJ...565...96C}; $^{g}$ \citet{2004ApJ...610..686G}.
-\newline $^{f}$ The position angle is given for the unweighted resp.
-the luminosity-weighted centroid estimation.}
-    \label{tab:lensproperties}
-  \end{center}
-\end{table}
+Stellar mass maps are taken from \citet{2011ApJ...740...97L}.
+In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}.
+This was then converted to a stellar mass map using the stellar-population synthesis (SPS) models of \citet{2003MNRAS.344.1000B}.
+The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
+The initial mass function (IMF) was taken to be the log-normal form given by \citet{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
+We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
+While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L, depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
+For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
+We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that a Salpeter IMF is too heavy and gives no solutions.
+We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
 
+The original sample we consider, is presented in \citet{2011ApJ...740...97L} and consists of 21 lens systems.
+It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
+As shown in \citet{2014MNRAS.445.2181C}, the recovery of the shape information of the lens is only good if there are at least four images.
+Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
+This yields a sample consisting of 11 lenses.
+We discuss each of these systems, next.
+We note that all the position angles are measured north through east and relative to the lens galaxy.
+
+\subsection{The individual lenses}
 \setlength\tabcolsep{5pt}
@@
 \setlength\tabcolsep{6pt}
-
-Stellar mass maps are taken from \citet{2011ApJ...740...97L}.
-In that work, the surface brightness distribution of the galaxy images in all available HST bands was first fitted using {\sc Galfit v2.03b} \citep{2002AJ....124..266P}.
-This was then converted to a stellar mass map using the stellar-population synthesis (SPS) models of \citet{2003MNRAS.344.1000B}.
-The population synthesis is marginalised over the star formation epoch and time scales and over the stellar metallicity.
-The initial mass function (IMF) was taken to be the log-normal form given by \citet{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the shape of the inferred stellar mass distribution \citep[unless the IMF presents significant intrinsic deviations locally, see e.g.][]{2015MNRAS.447.1033M}.
-We note that the effect of recent claims towards a non-universal IMF on stellar mass-to-light ratio (M/L) is still under debate.
-While for massive elliptical galaxies, dynamical studies seem to point at contributions at the level of the Salpeter IMF or slightly heavier \citep{2013MNRAS.432.1862C}, spectral line strength constraints can still accommodate a wider range of the stellar M/L, depending on the functional form of the IMF \citep{2013MNRAS.429L..15F}.
-For at least one lens in our sample, \textit{Q2237+030}, the lensing estimates on the mass distribution are inconsistent with a Salpeter IMF \citep{2010MNRAS.409L..30F}.
-We additionally tested varying the IMF for one lens ({\it B1422+231}), finding that a Salpeter IMF is too heavy and gives no solutions.
-We will perform a more systematic study of the IMF and varying stellar M/L in a forthcoming publication.
-
-The original sample we consider, is presented in \citet{2011ApJ...740...97L} and consists of 21 lens systems.
-It is a subsample of the CfA-Arizona Space Telescope LEns Survey\footnote{http://www.cfa.harvard.edu/castles/} (CASTLES) sample.
-As shown in \citet{2014MNRAS.445.2181C}, the recovery of the shape information of the lens is only good if there are at least four images.
-Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561}.
-This yields a sample consisting of 11 lenses.
-We discuss each of these systems, next.
-We note that all the position angles are measured north through east and relative to the lens galaxy.
-
-\subsection{The individual lenses}
 
@@
   \includegraphics[width=.7\linewidth]{Figures/kappaplot.pdf}
-  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $r$ of the dark matter distribution.
+  \caption[width=\linewidth]{Azimuthally averaged convergence $\langle\kappa\rangle$ within radii $R$ of the dark matter distribution.
 The vertical lines denote the radial distances of the source images from the centre of the lens galaxies.
@@
     \caption{Fitted virial masses and radii and the ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios.
-`Env' is the `Environment' column in Table~\ref{tab:lensproperties} and ; $r_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle (measured north through east) of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.
+`Env' and $\theta_{Env}$ are the `Environment' resp.
+$\theta_{Env}$ columns in Table~\ref{tab:lensproperties}; $r_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle (measured north through east) of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.
 \newline $^{a}$ brrr}
@@
 Our results on the shape and radial profile of the dark matter haloes in these lenses provide new constraints on galaxy formation models.
-Dark matter haloes can contract due to baryonic cooling \citep[e.g.][]{1986ApJ...301...27B} or expand due to energetic feedback \citep[for a recent review see][]{2014Natur.506..171P, 2015arXiv150202036O} from supernovae \citep[e.g.][]{2005MNRAS.356..107R, 2015arXiv150804143R} or AGN \citep[e.g.][]{2012MNRAS.422.3081M}.
+Dark matter haloes can contract due to baryonic cooling \citep[e.g.][]{1986ApJ...301...27B} or expand due to energetic feedback from supernovae \citep[e.g.][]{2005MNRAS.356..107R,2012MNRAS.421.3464P,2014Natur.506..171P,2015arXiv150202036O,2015arXiv150804143R} or AGN \citep[e.g.][]{2012MNRAS.422.3081M}.
 The latest simulations for elliptical galaxies forming in $\Lambda$CDM without AGN feedback suggest that contraction should win \citep{2015MNRAS.453.2447D}.
@@
 \section{Acknowledgements}\label{sec:acknowledgements}
-We thank Simon Birrer for useful discussion.
+We thank Simon Birrer and William Hartley for useful discussion.
 JIR would like to acknowledge support from SNF grant PP00P2\_128540/1.
@@
   \centering
-  \includegraphics[width=.8\linewidth]{Figures/AllLenses31.pdf}
+  \includegraphics[width=.83\linewidth]{Figures/AllLenses31.pdf}
   \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy.
@@
   \centering
-  \includegraphics[width=.8\linewidth]{Figures/AllLenses32.pdf}
+  \includegraphics[width=.83\linewidth]{Figures/AllLenses32.pdf}
   \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{Figures/AllLenses33.pdf}
+  \includegraphics[width=.83\linewidth]{Figures/AllLenses33.pdf}
   \caption[width=.65\linewidth]{The results of our reconstruction of each individual lens galaxy. Lines and symbols are as in Figure \ref{fig:lensreconstruction1}.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
+  \includegraphics[width=.93\linewidth]{Figures/theta_scatter.pdf}
   \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the induced position angle of the required external shear $\theta_{g}$ of each reconstructed mass distribution.

### 2015-09-29 shapes/reply_referee_1.txt
Final changes

We would like to thank the referee for a constructive and helpful report that has improved our paper. We have now addressed all of the referee's previous concerns and we hope that the paper is now ready for publication. We respond to each point in turn, next.

| Examples of lack of clarity:

| - The authors state that "isolated misaligned galaxies are expected to
|   be unstable" but they do not cite any references. What do the authors
|   mean by misalignment (e.g., mass or angular momentum)? Debattista et al.
|   (2013) showed that disc galaxies with their spins along the intermediate
|   axis aren't stable, but they also showed that when gas is present a disc
|   can survive for a very long time if it is off of one of the symmetry
|   planes of the halo. Debattista et al. (2015, arXiv:1502.03429) simulated
|   disc formation with gas and found that discs can have essentially arbitrary
|   orientations. There is some observational evidence from the observed
|   locations of satellite galaxies (e.g., Agustsson & Brainerd 2010) and the
|   intrinsic alignments of galaxies (e.g., Singh et al. 2014, arXiv:1411.1755
|   and references therein) that dark matter mass and light may not be well
|   aligned in disc galaxies (i.e., the intrinsic alignment signal is most
|   robustly detected for red galaxies, not blue galaxies).

We have now clarified this in a new section (5.2) on the lack of misalignment in isolated lenses. We more carefully define "isolated" as having external shear $\gamma < 0.1$, and we now discuss the fact that gas rich galaxies can maintain misalignments over long times, while gas poor galaxies cannot. Our lenses are all early types except 2237 for which we probe only the bulge region. Thus we expect them to be gas poor "red" galaxies that are, in the absence of external shear, aligned.

| - The authors say that they assume "the local density gradient to be
|   always pointing within 50 degree of the centre of the
|   distribution". What does this mean? They also say that "the radius
|   of the lens is set to be 12 pixels". What does this mean? What is
|   the radius of the lens? (The optical radius perhaps?) Presumably
|   the pixels refer to what is used in the lens reconstruction but
|   this is not stated sufficiently clearly.

Section 2 (which describes the method) has now been rewritten and is hopefully clearer. The unclear part about the local density gradient has been replaced with detailed references. On the mass-pixel size, we now explain that they are at most 4% of the diameter of the full mass map, while the stellar/dark mass map extends to the outermost image. More explicit details of the methodology are covered in Coles et al. 2014.

| - The authors do not specify the physical radii over which they are
|   attempting to constrain the dark matter mass. How does the scale being
|   probed compare to, say, the virial radius that might be expected?

We have included an additional Figure (Figure 1), which besides addressing other questions as well, illustrates the range in physical scales probed for every lens system. Furthermore, as we elaborate below, we have calibrated NFW profiles to match the convergence profile of the reconstructed distribution at the Einstein radius. The virial masses and the corresponding virial radii derived in this way are now given in Table 3.

| - It is not clear what form the best-fitting gravitational potentials of
|   the dark matter halos turn out to be. Are they consistent with some
|   reasonable expectation for galaxy formation (say, elliptical NFW or
|   elliptical isothermal), or are they something completely different to
|   naive theoretical expectations?

We planned to present the radial dark matter profile of these lenses as part of a larger sample in a separate paper. However, we agree with the referee that it is useful to present these here also. We have addressed this issue by including several new Sections and Figures: Firstly, Section 4.1 was added. It compares the projected dark matter profile of each individual lens with an NFW profile, assuming the cosmic mean concentration parameter. Secondly, Figure 1 has been included displaying the reconstructed azimuthally averaged convergence and the NFW profiles as a comparison. We derive virial masses and radii by matching NFW profiles to the measured projected dark matter mass profiles at the outermost image. The values derived in this way are given in Table 3. As can be seen, our lenses are all well fit by an NFW profile or are steeper, as expected if halos contract in response to gas cooling. We have added these new results also to the abstract and conclusions. An interesting new result that arose from this is that those lenses with an outermost image inside ~10kpc appear to be contracted with respect to NFW; while those with an outermost image >10kpc are rather well fit by the NFW form. We discuss potential reasons for this, but defer further analysis to a separate publication (where we will vary, for example, the stellar IMF).

| - It is not clear how the best-fitting values for the halo shape and
|   degree of alignment with the stellar light are determined. Similarly
|   it is not clear how the error bars on these values (and their significance)
|   were determined.

We have reworked Section 2 significantly to explicitly describe our estimators and the statistical uncertainties for the shape and orientation of the distribution. These quantities are estimated, as now explained in the text, by computing the eigenvalues and eigenvectors of the inertia tensor (see Eq. 1). Shape and orientation (resp. misalignment) are then estimated by combining the two eigenvalues resp. the angle of the eigenvector corresponding to the larger eigenvalue relative to the x-axis (see Eq. 2 and 3). As Glass gives an ensemble of solutions, these quantities are estimated for each solution. Based on these distributions, the quantities are constrained and the statistical uncertainties estimated.

| - Regarding 0957, the authors say "the position angles to the center of
|   the cluster of earlier lens constructions ... " which is too vague. What
|   the authors mean is the position angle of the external shear. Throughout,
|   the authors need to specify "the position angle of _______" (i.e., by
|   explicitly filling in the blank) so that readers can understand what
|   they're trying to say.

We have made this clearer along the lines suggested by the referee. We now add these angles also to Table 3 and more carefully explain that this position angle can be directly compared to the external shear angle.

| - Figure 1 attempts to compile all of the main results into one figure, and
|   it is extraordinarily difficult to disentangle this information. The bulk
|   of the data points lie on top of each other and it's not even possible to
|   tell which point and error bar corresponds to which lens system. At a minimum,
|   the authors need to include an additional table that lists, for each lens, the
|   values and error bars for e*, edm, the offset between the major axis of the
|   light and the major axis of the dark matter halo, and the external shear.

We thank the referee for the suggestions on how to avoid this slight over-compression of information in this key Figure. We have made several changes to improve this. First, we have added a second panel to this Figure, zooming into the region where the most points lie. Second, by changing the color scheme, understanding this third dimension in this Figure (external shear) becomes easier. Third, we provide the reader, as suggested, with all the values (Table 3). The ellipticities, for which we give the statistical uncertainties (see above), are now given using the ellipticity definition e=(a-b)/(a+b), which is more common in weak lensing. By changing the employed ellipticity definition, the comparison with the weak lensing results is facilitated (see below).

| - The authors do not make clear (with a statement of a value for γ)
|   for what they consider to be a "weak" external shear. To me, a
|   shear of more than a few percent is a relatively large external
|   shear, suggesting the presence of a larger mass concentration
|   within which the primary lens is embedded. That is, it seems that
|   even where no cluster/group members are currently known, there is
|   an external shear that could be explained by the presence of a
|   group/cluster environment (if I'm reading the colors in Figure 1
|   correctly).

The corresponding Sections have been adjusted and we now state clearly (see e.g. Abstract) that an external shear larger than >~0.1 is considered strong. Thus, the lens sample splits into two subsets, i.e. 6 lenses with a strong external shear, 5 with weak and intermediate external shear (see Table 3). For the lenses with a known and constrained environment, the direction of external shear (see Table 3) is consistent with the centre of the group/cluster (see Table 2). We agree with the referee that even an external shear of gamma ~ 0.08 might be considered "strong". However, we find that our lenses show qualitatively different behaviour for gamma < 0.1 and gamma > 0.1 and hence set the dividing line at gamma ~ 0.1.

| - The authors do not address how the direction of the external shear
|   compares to the orientation of the dark matter halo of the lens
|   galaxy, nor is there a full discussion how the magnitude of the
|   external shear compares with the inferred shape of the dark matter
|   halo.

Appendix B has been added to discuss the degeneracy between DM ellipticity and external-shear. Figure B1 now plots the scatter (over the model ensemble of each lens) of the orientations of DM vs external-shear. As can be seen, while there is some degeneracy between shape and shear, the degeneracy is largely broken and we are able to obtain good estimates of both. This finding and the dependence of the shape estimation on the shear prior are discussed explicitly in Section 4.2.

| Misinterpretation of previously published work:

| - It’s not correct that weak lensing can directly probe the orientation of the
|   dark matter mass relative to the luminous lens galaxies. The only way in which
|   one can even search for an anisotropy in the shear profile is to use the
|   symmetry axes of the luminous lens galaxies because you don’t know the
|   orientation of the symmetry axes of the dark matter. That is, the only sensible
|   way to stack the lenses is to use the major axes of the luminous galaxies. If
|   the signal you observe is isotropic, this could be telling you that the halos
|   are round or it could be telling you that mass and light are not well aligned
|   in your lens galaxies. You can’t disentangle those two possibilities from the
|   observations alone.

| - It’s not correct that Hoekstra et al. (2004) found “some weak evidence for
|   alignment”. Hoekstra et al. (2004) concluded that there must be quite good
|   alignment of mass and light for them to have detected a signal at all (for the
|   reason stated above). This is stated in their abstract.

| - It’s not correct that Mandelbaum et al. (2006) found that the halos of red
|   galaxies were flatter than their stellar distributions. They found the halos to
|   be rounder than the luminous galaxies in all cases (power law and NFW mass models).
|   This is stated in their abstract.

| - Given that Parker et al. (2007) do not quote error bars on their estimates of the
|   halo ellipticity, it’s not correct to say that they concluded the halos of red
|   galaxies were flatter than their stellar distributions. All of their halo
|   ellipticities are quoted with a “tilde” out front (e.g., ~0.3 and ~0.4). If a
|   proper error analysis were done, it could easily be found that these approximate
|   central values were consistent with the ellipticities of the stellar distributions.
|   Parker et al. (2007) put error bars on the shear anisotropy only and, properly, their
|   “2σ” statement in the abstract refers to their constraint on the shear anisotropy,
|   not the inferred halo ellipticity. In the full text they make it clear that they find
|   a 2σ detection of “non-sphericity”, which is not the same as a 2σ measurement of a
|   value of the projected ellipticity.

We thank the referee for these good points of criticism. We have revised the whole paragraph to give a more adequate description of the difficulties of this measurement and the results on data. We now describe what exactly can be constrained, which is, as pointed out by the referee, the projected dark matter ellipticity and thus cannot be directly interpreted as the ellipticity of the dark matter halo. Furthermore, the most recent observational constraints including the papers submitted in the meantime by Clampitt & Jain, 2015 and Schrabback et al., 2015 are presented.

| Additional Comments

| - The authors have not provided a sufficient description of GLASS
|   and its reliability for the reader. As it stands, the reader needs
|   to go to Coles et al. (2014) for too much relevant
|   information. Manuscripts need to be sufficiently independent of
|   one another that an “educated” reader need not be intimately
|   familiar with a preceding manuscript in order to understand and
|   evaluate the present manuscript.

As noted above, this Section has been rewritten to be more self-contained. It still refers the reader to Coles et al (2014) for precise formulations and tests, but without making it essential to consult the earlier work (unless interested in these explicit details and test results).

| - Nowhere in this manuscript do the authors make a compelling case
|   (through, e.g., model testing) that GLASS yields reliable results
|   for the quantities they seek.  Perhaps that has been done in
|   another manuscript but, if so, such tests have not been referenced
|   here explicitly. Because most of the lenses are clearly not
|   isolated, there is a concern about how the inferred external shear
|   may correlate with the inferred halo shape and orientation. The
|   authors need to demonstrate with reasonable theoretical models
|   that the magnitude and orientation of external shears in the range
|   of, say, 0.0 to 0.25 do not significantly affect the conclusions
|   regarding the shape and orientation of the dark matter halo of the
|   lens galaxy.

The revised Section 2 refers to Section 5.2 and Figure 8 of Coles et al (2014) which tests recovery of the shape estimators.

As noted above, Appendix B has been added to discuss relation between the orientation of the dark matter vs the direction of external shear.

| - In the concluding section, the authors restate their results but do not discuss them
|   in context with previous, similar work and known theoretical expectations. This is
|   important, and needs to be done – even when different techniques are used in the
|   observational analyses.

We agree that the paper can be improved in comparing our results to results using different techniques. To satisfy this, we have included a Discussion Section (Section 5). In this Section, we elaborate on the constraints from weak lensing. Especially, we compare our results explicitly to the study by Schrabback et al., 2015, submitted to MNRAS a short time ago, which is the most recent weak lensing measurement of halo ellipticity/misalignment, and furthermore studies the expected signal using the Milennium simulations. We facilitate this comparison furthermore by consistently using the same ellipticity definition as in Schrabback et al (see above), and computing the combination of ellipticities weak lensing can probe, i.e. f_h = e_dm / e_s, where e_dm is the dark ellipticity in direction of the light distribution and e_s is the ellipticity of the latter.

As we elaborate in the first Subsection 5.1, our constraints are broadly consistent with the most recent measurement on CFHTLenS data and the predictions from the Milennium simulation.

In a second Subsection, we discuss the theoretical expectations of misalignments in isolated galaxies. We find that the lenses requiring a weak external shear, even though some do have a known environment, are not misaligned, consistent with theoretical considerations.

| - Figure 2 is not terribly useful. None of the panels is independent, and it
|   appears from the error bars that most of the points that were computed using
|   a larger radius are not much different from the points that were computed
|   using a smaller radius. While it would be terrific to know how the ellipticity
|   and alignments vary with distance from the lens, that question needs to be
|   answered with independent data points (i.e., independent annuli in the
|   analysis) and I don’t think the authors’ data is sufficient for the task.

As the inertia tensor depends on the square of the radius, changes in the estimated shape are conceivable when changing the radius of enclosure (different multiples of R_e). Thus, this Figure serve to some degree to assess the robustness of the estimated shape.

While we agree with the referee that our data is not sufficient to conclusively identify the trend of the increasing ellipticity of the stellar distribution with increasing radius we observe, it is interesting to find out whether it persists.

| - The authors posit that 0712 and 2016 are post merger-systems, but that seems
|   to be based solely on their lensing reconstructions and nothing else. Such an
|   extrapolation from one known post-merger lensing system with similar properties
|   (1608) doesn’t seem warranted.

We agree with the referee that the paper in its previous form may have put too much emphasis on this statement. We make now clear in the Conclusions, where we reiterate on our results, that this is a speculation based on the close similarities to the known merger system 1608. We have removed reference to this from the abstract.

### 2015-09-29 shapes/paper.tex
Final changes

@@
 `Env' and $\theta_{Env}$ are the `Environment' resp.
-$\theta_{Env}$ columns in Table~\ref{tab:lensproperties}; $r_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle (measured north through east) of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.
-\newline $^{a}$ brrr}
+$\theta_{Env}$ columns in Table~\ref{tab:lensproperties}; $r_{vir}$ and $M_{vir}$ are the virial radii and masses of the fitted NFW-profiles (see Section~\ref{sec:radialprofiles}); $|\gamma|$ and $\theta_{g}$ denote magnitude and induced position angle (measured north through east) of the required external shear in the modeling of the strong lens galaxy; the ellipticities $e_{*}$ and $e_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the ellipticities of the dark matter relative to the stellar distribution; and $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution.}
     \label{tab:ellipratios}
